### 2018-04-13 article_springer/article_springer.Rmd
minor changes in introduction

---
title: Peaks Over Threshold for Bursty Time Series
# titlerunning: Inference for Heavy-Tailed CTRMs
thanks: |
    Peter Straka was supported by the 
    Discovery Early Career Research Award DE160101147 on the Project 
    "Predicting Extremes when Events Occur in Bursts" by the Australian
    Research Council.
    Katharina Hees was supported by 
    the DAAD co-financed by the German Federal Ministry of Education and 
    Research (BMBF).

authors: 
- name: "Katharina Hees"
  address: University of Dortmund
  email: hees@statistik.uni-dortmund.de

- name: "Smarak Nayak"
  address: National Australia Bank
  email: smarak.nayak@nab.com.au

- name: "Peter Straka*"
  address: UNSW Sydney
  email: p.straka@unsw.edu.au

authorrunning: K. Hees, S. Nayak & P. Straka

keywords:
- heavy tails
- renewal process
- extreme value theory
- peaks over threshold

abstract: |
  In many complex systems studied in statistical physics, 
  inter-arrival times between events such as solar flares, trades and 
  neuron voltages follow a heavy-tailed 
  distribution. The set of event times is fractal-like, being dense in some 
  time windows and empty in others, a phenomenon which has been dubbed 
  "bursty".

  This article generalizes the Peaks Over Threshold (POT) model to the setting 
  where inter-event times are heavy-tailed and i.i.d.. For high thresholds and 
  infinite-mean waiting times, we show that the times between threshold 
  crossings are Mittag-Leffler distributed, and thus form a "fractional 
  Poisson Process" which generalizes the standard Poisson Process.
  We model threshold crossing times and threshold exceedances jointly, and
  provide graphical means of estimating model parameters and assessing 
  model fit. Finally, we study two real-world, bursty time series, and 
  show how to extract parameter estimates as well as estimates for the time 
  of the next threshold crossing.

bibliography: CTRMstats.bib

output: rticles::springer_article

params:
  tail: 0.8
  n: 10000

---

```{r get-rticles, eval=FALSE, include=FALSE}
# use this rticles version: 
devtools::install_github("strakaps/rticles", 
                         ref = "724aeb88d005e2f7befc37328633e7cb2bc1cce0")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  cache = TRUE,
  message = FALSE,
  fig.height = 3, out.width = '\\textwidth'
  )
library(CTRM)
```

# Introduction

Time series displaying temporally inhomogeneous behaviour have received 
strong interest in the recent statistical physics literature 
[@Barabasi2005; @Oliveira2005; @Vasquez2006; @Vazquez2007; @Omi2011; 
@Min2010; @Karsai2011; @Bagrow2013]. They have been observed in the context 
of earthquakes, sunspots, neuronal activity and human communication [see 
@Karsai2012; @Vajna2013; @MeerschaertStoev08 for a list of references]. 
Such time series exhibit high activity in some 'bursty' intervals, which 
alternate with other, quiet intervals.  Although several mechanisms are 
plausible explanations for bursty behaviour (most prominently self-exciting
point processes [@hawkes1971point]), there seems to be one salient feature 
which very typically indicates the departure from temporal homogeneity: a 
heavy-tailed distribution of waiting times [@Vasquez2006; @Karsai2012; 
@Vajna2013]. As we show below in simulations, a simple renewal process with
heavy-tailed waiting times can capture this type of dynamics. For many 
systems, the renewal property is appropriate; a simple test of the absence 
of correlations in a succession of waiting times can be undertaken by 
randomly reshuffling the waiting times [@Karsai2012].

Often a magnitude, or mark can be assigned to each event in the renewal process, 
such as for earthquakes, solar flares or neuron voltages. 
Extreme value theory provides models for the distribution of the events
with the largest magnitude. 
A commonly made assumption in POT models is that times between 
events are either fixed 
or light-tailed, and this entails that the 
threshold crossing times form a Poisson process [@beirlantBook]. 
Then as one increases the threshold and thus decreases the threshold 
crossing probability $p$, the Poisson process is rarefied, i.e. its 
intensity decreases _linearly_ with $p$.

As will be shown below, in the heavy-tailed waiting time scenario threshold 
crossing times form a _fractional Poisson process_ 
[@Laskin2003; @Meerschaert2010b], which is a 
renewal process with Mittag-Leffler distributed waiting times. 
The family of Mittag-Leffler distributions nests the exponential 
distribution [@Haubold11], and hence the fractional Poisson process
generalizes the standard Poisson process. 
Again as the threshold size increases and the threshold crossing
probability $p$ decreases, the fractional Poisson process is rarefied: 
The scale parameter of the Mittag-Leffler inter-arrival times of 
threshold crossing times increases, increases, but _superlinearly_; 
see the Theorem below.

Maxima of events which occur according to a renewal process with
heavy-tailed waiting times have been studied under 
the names "Continuous Time Random Maxima process" (CTRM) 
[@Benson2007; @MeerschaertStoev08; @Hees16; @Hees17], 
"Max-Renewal process" [@Silvestrov2002a; @ST04; @Basrak2014], 
and "Shock process"
[@Esary1973; @Sumita1983; @Sumita1984; @Sumita1985; @Anderson1987; @Gut1999].
The existing literature focuses on probabilistic results surrounding these 
models. 
In this work, however, we introduce a method of inference for this type of 
model, which is seemingly not available in the literature.

We review the CTRM, or max-renewal model, in Section 2, and 
derive a scaling limit theorem for inter-exceedance times in Sections 3 &
4. 
A statistical procedure to estimate model parameters via stability plots 
is outlined in Section 5, and diagnostic plots for model criticism are 
discussed in Section 6. 
In Section 7, we give case studies for simulated data as well as for a
real-world dataset, with a discussion in Section 8. 
All statistical computations have been done in R, and all code, data, as 
well as the source code for this manuscript has been organized into an R 
software package, available at <https://github.com/strakaps/CTRM>.

# CTRMs

![\label{fig:ctrm} A CTRM sample path.](just-tikz-figure0.pdf)

Continuous Time Random Maxima (CTRM), or Max-Renewal processes, track the 
largest event in a renewal sequence of events [@Basrak2014; 
@MeerschaertStoev08; @Hees16]:

**Definition (CTRM):**

: Let $(W,J), (W_1, J_1), (W_2, J_2), \ldots$ be i.i.d. pairs of random 
variables, where the $W_k > 0$ are interpreted as the *waiting times* or 
inter-arrival times and $J_k \in [x_L, x_R]$ as the *event magnitudes* 
or marks
($x_L \in [-\infty, +\infty), x_R \in (-\infty, +\infty]$). 
The renewal process associated with the $W_k$ is 
$$N(t) = \max\{n: W_1 + \ldots + W_n \le t\},$$
and the running maximum is $M(n) := \bigvee_{k=1}^n J_k$. Then the process
$$V(t)=M(N(t)) = \bigvee_{k=1}^{N(t)} J_k, \quad t \ge 0.$$
is called a CTRM (Continuous Time Random Maxima) process. 
If $W$ and $J$ are independent, the CTRM is said to be *uncoupled*. 
We let $M(0) = x_L$.

Figure \ref{fig:ctrm} shows a CTRM sample path.
The alternative case where one considers the maximum of the first 
$(N(t)+1)$'s event is called an *OCTRM process* (Overshooting Continuous 
Time Random Maxima; or *Model II* by @Sumita1983). 
The conceptual difference between CTRM and OCTRM is the order of waiting 
times and events, which is $W_1,J_1,W_2,J_2,..$ for the CTRM and 
$J_1,W_1,J_2,W_2,...$ for the OCTRM. 
In the uncoupled case, unsurprisingly CTRM and OCTRM are asymptotically 
equivalent. 
In the coupled case, however, their distributions 
can be dramatically different [@Hees16].

The main purpose of this article is to introduce and discuss a method for 
fitting data to an uncoupled CTRM, based on the following observable data:

**Definition:**

: The random variables
$$X(\ell) = V(T(\ell)) - \ell, \quad 
T(\ell) = \inf\{t: V(t) > \ell\}, 
\quad \ell \in (x_L, x_R)$$
are called the *exceedance* resp. *time until exceedance* of level $\ell$.

#### POT-like approach.
Since we assume the uncoupled case, $X(\ell)$ and $T(\ell)$ are 
independent. 
To see this, note that $X(\ell)$ is, in distribution, simply equal to
$J | J > \ell$, independent of any waiting time $W_k$. 
For our inference on the CTRM model, we extract realizations of 
$X(\ell)$ and $T(\ell)$ from time series data by considering thresholds 
$\ell$ ranging over some interval $[\ell_0, x_R)$. 
(A reasonable default value for $\ell_0$ is the $95$-th
percentile of $J$.)
Write $X(\ell,i)$ for the $i$-th exceedance of level $\ell$, 
and $T(\ell,i)$ for the inter-arrival time between
$X(\ell,i-1)$ and $X(\ell,i)$. 
Thus for any threshold $\ell \in [\ell_0, x_R)$,
we construct sequences $\{T(\ell,i)\}_{i}$ and 
$\{X(\ell,i)\}_{i}$. 
These sequences are i.i.d. because a renewal occurs at each threshold
crossing time, and independent because $W_k$ and $J_k$ are uncoupled.
Extracting the exceedances $X(\ell)$ for inference is a standard procedure
known as the Peaks Over Threshold (POT) approach in extreme value theory
[@beirlantBook].
Figure \ref{fig:thresholdedBursty} illustrates the exceedances 
$X(\ell, i)$ in red and the times until exceedance $T(\ell, i)$ as the 
preceding intervals marked by blue crosses.

```{r thresholdedBursty, message=FALSE, fig.cap="\\label{fig:thresholdedBursty}Exceedances (red) and Times until Exceedance (durations between blue crosses) for a given threshold $\\ell$ (dashed line)."}
#rpareto <- function(n,tail){
#          if(tail<=0) stop("tail must be positive")
#          rp <- (runif(n)/gamma(1-tail))^(-1/tail)
#          rp}
tail <- params$tail
n <- params$n 
sigma <- (cos(pi*tail/2))^(1/tail)
times <- cumsum(stabledist::rstable(n, tail, 1, sigma, pm=1))
#times<-cumsum(rpareto(n,tail))
magnitudes <- extRemes::revd(n, scale = 1, shape = 0)
sim_ctrm <- ctrm(data.frame(times, magnitudes))
plot(sim_ctrm, p = 0.005)
```

A standard result from extreme value theory provides the asymptotic 
distribution of $X(\ell)$ as $\ell \uparrow x_R$. For later use, we also 
include the scaling limit of the cumulative maximum $M(n)$.

**Theorem GEV** (e.g. Chapter 2 & Section 5.3, @beirlantBook):

: Suppose the distribution of $J_k$ is continuous. Then there
exist non-decreasing norming functions $a(c)$ and $d(c)$ such that
as $c \to \infty$, the running maximum\footnote{We extend $M(n)$ 
continuously to $[0, +\infty)$ via $M(c) := M(\lfloor c \rfloor)$ where 
$\lfloor c \rfloor$ is the 
greatest integer not greater than $c$.} 
$M(c)$ converges weakly 
to a *Generalized Extreme Value Distribution* with shape
parameter
$\xi$:
\begin{align}
[M(c) - d(c)] / a(c) \stackrel{d}{\to} A, 
\quad
\mathbf P(A \le z) = G(z | \xi) = \exp\left(-[1+\xi z]^{-1/\xi}\right),\label{eq:GEV}
\end{align}
defined for all $z$ such that $1 + \xi z > 0$. 
This definition extends continuously to $\xi = 0$ via 
$$G(z | 0) = \exp(-\exp(-x)).$$
For $\mu$ and $\sigma > 0$, we write ${\rm GEV}(\xi, \mu, \sigma)$ for the 
probability distribution of the random variable $\sigma A + \mu$.

    Moreover, asymptotically as $\ell \uparrow x_R$,
$$\mathbf P(J - \ell > y | J > \ell) 
\sim 1 - H(y),$$
where 
$$H(y) = \begin{cases}
1 - (1+ \xi y / \tilde \sigma)^{-1/\xi}, & y \in (0,\infty) \text{ if } \xi > 0,\\
1 - \exp(-y/\tilde \sigma), & y \in (0,\infty) \text{ if } \xi = 0,\\
1 - (1+ \xi y / \tilde \sigma)^{-1/\xi}, & y \in (0, -\sigma / \xi) \text{ if } \xi < 0
\end{cases}$$

    and where $\tilde \sigma := \sigma + \xi(\ell-\mu)$.
The CDF $H(y)$ is said to belong to the *Generalised Pareto family*
$GP(\xi,\bar \sigma)$.

# CTRM Scaling limits

## Waiting times

We will assume that the waiting times $W_k$ have infinite mean,
i.e. a tail parameter $\beta \in (0,1)$ and regularly varying tail probabilities:
$\mathbf P(W > t) \sim L(t) t^{-\beta}$ as $t \uparrow \infty$ for
some slowly varying function $L(t)$. As usually, $f(t) \sim g(t)$
means that the quotient of $f(t)$ and $g(t)$ converges to $1$. The
law of the $W$ then lies in the domain of attraction of a stable law,
in the sense that the distributional limit 
\begin{align} \label{eq:Wscale}
\frac{W_1 + \ldots + W_n}{b(n)} \overset{d}{\longrightarrow} D, 
\quad n \to \infty
\end{align}
exists, for a regularly varying scaling function
\begin{equation} \label{eq:bScale}
b \in {\rm RV}_\infty(1/\beta)
\end{equation}
[See e.g. Section 2.9.2 in @beirlantBook for a short introduction to 
regular variation]. 
The limit is then a positively skewed stable distribution, 
whose scale parameter is $1$ if $b(n)$ is chosen accordingly
[see e.g. Section 3.7 in @MeerschaertSikorskii]. 
This distribution is most concisely defined via its Laplace transform
\begin{align} \label{theD}
\mathbf E[\exp(-sD)] = \exp(-s^\beta).
\end{align}
Moreover, the following functional limit theorem holds 
[see e.g. Remark 4.17 in @MeerschaertSikorskii]: 
\[
(W_1 + \ldots + W_{\lfloor ct \rfloor})/b(c) \overset{d}{\longrightarrow} D(t), \quad c \to \infty
\] 
with convergence in the Skorokhod $J_1$ topology. The limit
$D(t)$ is a stable subordinator, i.e. an increasing Levy process with
Laplace transform $\exp(-t s^\beta)$.

It is well known [see e.g. @limitCTRW] that the renewal
process then satisfies the functional limit
$$
N(ct)/ \tilde b(c) \stackrel{d}{\to} E(t) = \inf\{r: D(r) > t\}, 
\quad c \to \infty
$$
for a scaling function $\tilde b(c) \in {\rm RV}_\infty(\beta)$ which is asymptotically inverse to $b(c)$, in the sense of @seneta (p.20): 
$$
b(\tilde b(c)) \sim c \sim \tilde b(b(c)).
$$
[also see Prop 4.15 in @MeerschaertSikorskii]. 
The limit process $E(t)$ is called the _inverse stable subordinator_ [@invSubord].

## Magnitudes and Extreme Value Distributions

The extremal limit theorem then allows for an extension to functional 
(i.e. pathwise) limits: assume that the norming sequences $a(c)$ and 
$d(c)$ are as in Theorem GEV. Then 
$$
[M(ct) - d(c)] / a(c) \stackrel{d}{\to} A(t),
\quad c \to \infty.
$$
Here convergence holds weakly in Skorokhod's $J_1$ topology, and the limit
process $A(t)$ is an _extremal process_, with
finite-dimensional distributions given by
\begin{align}
\label{eq:fin-dim-A}
\mathbf P(A(t_i)\leq x_i,1\leq i \leq d) 
= F_A(\wedge_{i=1}^d x_i)^{t_1} 
F_A(\wedge_{i=2}^d x_i)^{t_2-t_1}
\ldots F_A(x_d)^{t_d-t_{d-1}},
\end{align}
where $F_A(x)$ is a GEV distribution [see e.g. @resnick2013extreme].

## CTRM limit

The CTRM $V(t)$ results from the running maximum $M(n)$ via a time change by the renewal process $n = N(t)$. This is also reflected in its corresponding limit process:

**Theorem MS1** [@MeerschaertStoev08]:

: The CTRM process $V(t) = M(N(t))$ satisfies the following functional scaling limit in the Skorokhod $J_1$ topology: 
$$
[V(ct) - d(\tilde b(c))] / a(\tilde b(c)) \stackrel{d}{\to} 
A(E(t)), \quad c \to \infty.
$$

The distribution of the _hitting time_ of a level $\ell^*$ by the limit 
process $A(E(t))$ is also known, and we give it below for the convenience 
of the reader:

**Theorem MS2** [@MeerschaertStoev08]:

: Let $F_A$ be the CDF of a GEV distribution, and let $A(t)$ be the
extremal process corresponding to $F_A$ via \eqref{eq:fin-dim-A}. 
For a given threshold $\ell^*$ in the support of $F_A$,
the hitting time
$$
B(\ell^*) = \inf\{t: A(E(t)) > \ell^*\} 
$$
is equal in distribution to $(-\log F_A(\ell^*))^{-1/\beta} X^{1/\beta} D$,
where $X \sim {\rm Exp}(1)$ and $D$ (defined in \eqref{theD}) are 
independent.

The Mittag-Leffler distribution with parameter $\beta \in (0,1]$ is 
a heavy-tailed positive distribution if $\beta < 1$; for $\beta = 1$, 
it specializes to the Exponential distribution. 
For $\sigma > 0$, we write ${\rm ML}(\beta, \sigma)$ for the distribution 
of $\sigma Y$, where $Y$ has Laplace transform 
$\mathbf E[\exp(-s Y)] = 1/(1+s^\beta)$. Due to e.g. Theorem 19.1 in 
@Haubold11, the exceedance time from Theorem MS2 can be written as 
\begin{align} \label{eq:hitting-ML}
B(\ell^*) \sim {\rm ML}\left(\beta, (-\log F_A(\ell^*))^{-1/\beta}\right)
\end{align}

# Scaling limit of Exceedance Times

In classical extreme value theory, there are two main approaches for 
the inference on GEV distributions: Block
Maxima and Peaks-Over-Threshold (POT). Block 
Maxima subdivide the time line into 'blocks' of equal length, 
and the maximum of each block is taken as realization of the random 
variable $M_n$. 
This approach is not appropriate for CTRM data, because maxima in 
same-sized blocks will not be i.i.d.
As mentioned in Section 2, the POT approach *does* extract i.i.d. $X(\ell)$ 
(and $T(\ell)$), and can hence be directly used for the inference on 
the extreme values of $J_k$. 
Figure \ref{fig:GP-simulated} shows an example for the so-called 
"threshold-selection" plots for data drawn from the standard Gumbel 
distribution. 
For a range of thresholds, maximum likelihood estimators of the shape and 
scale parameters in the GP distribution are computed and plotted. 
Note that the scale parameter is transformed so that it appears independent
of the threshold [see e.g. Section 4.3.4 in @ColesBook].

```{r GPD-simulated-data, warning=FALSE, fig.cap="\\label{fig:GP-simulated}Stability plot for the shape and scale parameters of the generalized Pareto distribution. Here, the magnitudes are standard Gumbel, hence $\\xi = 0$ and $\\sigma = 1$. Plots were generated using the POT package in R [@R-POT]."}
par(mfrow = c(1,2))
JJ <- coredata.ctrm(sim_ctrm)
u.range <- quantile(x = JJ, probs = c(0.75, 0.95))
POT::tcplot(JJ, u.range = u.range)
# extRemes::threshrange.plot(mrp("getMags"), type = "GP", set.panels = FALSE)
```

For the remainder of this article, we focus on statistical inference 
for the inter-exceedance times $T(\ell)$ of the threshold crossings. 
In our setting, the inter-exceedance times follow a fractional 
Poisson process instead of a standard Poisson process, which is how our
approach generalizes the standard POT approach.

**Theorem:**

: Let $b(c)$ be the scaling function \eqref{eq:bScale},
and let $\ell$ be a threshold from the support $[x_L, x_R]$ of $J$. 
Furthermore let $p := \mathbf P(J > \ell)$. Under the assumption \eqref{eq:Wscale} and the assumptions of the GEV Theorem, we have 
\begin{equation} \label{eq:Tellscale}
T(\ell) / b(1/p) \to {\rm ML}(\beta, 1) \text{ as } \ell \uparrow x_R.
\end{equation}

*Proof:*
Let the scaling functions $a(c)$ and $d(c)$ be as in Section 
\ref{magnitudes-and-extreme-value-distributions}, and assume WLOG 
$\ell = a(n) \ell^* + d(n)$ for some arbitrary but fixed $\ell^*$, out of the support of $A$. 
We first note that due to \eqref{eq:GEV}
\begin{equation} 
F_J (a(c) \ell^* + d(c))^c \stackrel{d}{\to} F_A(\ell^*), \text{ as } c \to \infty.
\end{equation}
\noindent Taking the logarithm on each side and using the relationship  $z-1 \sim \log(z)$ as $z \to 1$, we get
\begin{equation}
c (1-F_J(a(c) \ell^*+d(c))) \stackrel{d}{\to} - \log F_A(\ell^*).
\end{equation}
\noindent Hence we have 
\begin{equation}
c \cdot p \stackrel{d}{\to} - \log F_A(\ell^*) \label{eq:np_conv}
\end{equation}
\noindent as $\ell \uparrow x_R$.
Now we get
\begin{align}
\begin{split}
\mathbf P \left[T(\ell)/b(1/p) > t \right]
&= \mathbf P[V(b(1/p) t) \leq \ell] \label{eq:proofTheo}
= \mathbf P[V(b(1/p)) \le a(c) \ell^* + d(c)]\\
&= \mathbf P\left(\frac{V(b(1/p)/b(c) \cdot b(c) \cdot t)-d(c)}{a(c)} \le \ell^*\right) \\
&\stackrel{d}{\to} \mathbf P(A(E(-\log F_A(l))^{-1/\beta} t) \leq \ell^*),
\end{split}
\end{align}
where the convergence follows due to Theorem MS1 (with $c$ replaced by $b(c)$) and the fact that
\begin{equation}
\frac{b(1/p)}{b(c)} 
= \frac{b(1/cp \cdot c)}{b(c)} 
\sim (cp)^{-1/\beta}
\to \left( -\log F_A(l)\right)^{-1/\beta} 
\text{ as } c \to \infty.\label{eq:proofTheo2}
\end{equation}
In \eqref{eq:proofTheo2} we used \eqref{eq:np_conv} and 
$b \in RV(1/\beta)$, which means that 
$b(\lambda c) / b(c) \rightarrow \lambda^{1/\beta}$ as 
$c \rightarrow \infty$ uniformly in $\lambda$ on each compact subset of 
$(0,\infty)$. 
The limit in \eqref{eq:proofTheo} is equal to
$$\mathbf P \left( \left( -\log(F_A(\ell^{*})) \right)^ {1/\beta} B(\ell^*) > t\right).$$ 
Due to Theorem MS2 and \eqref{eq:hitting-ML}, we know that 
$(-\log F_A (\ell^*))^{1/\beta} B(\ell^*)$ is $ML(\beta,1)$ distributed, 
and hence the theorem follows.

**Remark:**

: By the above theorem, the inter-exceedance times are i.i.d. and
approximately Mittag-Leffler distributed, which means that the exceedance
times form a *fractional Poisson process* [@Laskin2003]. 
Since the Mittag-Leffler distribution nests the exponential distribution 
(the special case where $\beta = 1$), the fractional Poisson process 
generalizes the standard Poisson process. 
As the threshold height increases, the threshold crossing events are 
effectively "thinned out", and the thinned (or rarefied) processes retain
the characteristics of a fractional Poisson process [@Gorenflo2010], 
with a growing scale parameter $b(1/p)$.

**Remark:**

: A fractional Poisson process can be represented as a
standard Poisson process $N(t)$, time-changed by an inverse stable 
subordinator $E(t)$ [@Meerschaert2010b]. 
This pattern can be made sense of in our context: 
The exceedance times for a standard extreme value process $A(t)$ form a 
standard Poisson process $N(t)$. Accordingly, the exceedance times 
of the CTRM limit $A(E(t))$ must be $N(E(t))$, a fractional Poisson 
process.

# Inference on Exceedance times

Equation \eqref{eq:Tellscale} implies that for large $\ell$ we may 
approximate the distribution of $T(\ell)$ with an 
${\rm ML}(\beta, b(1/p))$ distribution.
Building on the POT (Peaks Over Threshold) method, we propose the 
following estimation procedure for the distribution of $T(\ell)$:

1. For varying thresholds $\ell \uparrow x_R$, extract datasets of
  exceedance times $\{T(\ell, i)\}_i$.

2. Fit a Mittag-Leffler distribution to each dataset, which
  results in the $\ell$-dependent estimates $\{\hat\beta(\ell)\}_\ell$ and 
  $\{\hat \sigma(\ell)\}_\ell$.

3. Plot $\ell$ vs.\ $\hat \beta(\ell)$. As $\ell$ increases towards $x_R$, 
  $\hat \beta(\ell)$ *stabilizes* around a constant $\hat \beta$. 
  Use $\hat \beta$ as an estimate for the tail parameter $\beta$ of the
  Mittag-Leffler distribution of exceedance times.

4. Approximate $p \approx |\{k: J_k > \ell\}| / n$. 
  Recall that $b(c)$ is regularly varying with parameter $1/\beta$, and 
  hence has the representation $b(c) = L(c) c^{1/\beta}$ for some 
  slowly varying function $L(c)$. 
  Assuming that the variation of $L(c)$ is negligible, we hence 
  plot $\ell$ vs.\ $p^{1/\hat \beta} \hat \sigma(\ell)$. 
  Again as $\ell$ increases towards $x_R$, 
  $p^{1/\hat \beta} \hat \sigma(\ell)$ is expected to stabilize around a constant 
  $\hat \sigma_0$. 
  We then use $p^{-1/\hat \beta} \hat \sigma_0$ as an estimate of the scale 
  parameter of the Mittag-Leffler distribution of exceedance times for
  the level $\ell$.

The above approach, though theoretically sound, benefits from the following
practical adjustments:

* We choose $\ell$ from the order statistics, i.e. $\ell$ is the $k$-th
  largest of the observations $X_j$, where $k$ runs from 
  $k_\text{min}, k_\text{min} + 1, \ldots, k_\text{max}$. 
  The datasets are then of length $k-1$.
* We use $k$ rather than $\ell$ for the horizontal axis of our plots. 
* In Step 4, rather than plotting $p^{1/\hat \beta} \hat \sigma(\ell)$
  we plot $k^{1/\hat \beta} \hat \sigma(\ell)$. This changes 
  $\hat \sigma_0$ by the multiplicative constant $n^{1/\hat \beta}$, 
  but has the advantage that
  $\hat \sigma_0$ does not change if one pre-processes the data by 
  removing all observations below a certain threshold.

The estimates $\hat \beta$ and $\hat \sigma_0$ give an estimate of the 
distribution of exceedance times, dependent on the threshold $\ell$:
\begin{align*}
T(\ell) \sim {\rm ML}(\hat \beta, k^{-1/\hat \beta} \hat \sigma_0).
\end{align*}
For quick estimates of the Mittag-Leffler parameters the method of
log-transformed moments by @Cahoy2013 was used.

# Checking Model Assumptions

The CTRM model is based on three main assumptions, which are repeated 
below. For each assumption, we suggest one means of checking if it holds:

I.i.d.:
: The pairs $(W_i, J_i)$ are i.i.d. An indication if this is true is given 
  by an auto-correlation plot for the logarithms (to ensure finite moments) 
  of the two time series.

Uncoupled:
: Each $W_i$ is independent of each $J_i$. We propose an empirical copula
  plot to check for any dependence.

Heavy tails:
: The waiting times are heavy-tailed with tail parameter 
  $\beta \in (0,1)$. A Hill plot can confirm this assumption.

The motivation behind a CTRM model is to fit extreme observations
and their inter-arrival times. 
Observations below a certain threshold may be interpreted as noise and 
discarded.
Since the signal rather than the noise needs to satisfy our modelling 
assumptions, we suggest that the above model assumptions are checked 
*after* the noisy small observations are discarded.

# Application to data

## Simulated Data

To test our inference method, we have simulated `r params$n` 
independent
waiting time and magnitude pairs $(W_k, J_k)$. In order to have exact 
analytical values available for $\beta$ and $\sigma_0$, a distribution for 
$W_k$ needs to be chosen for which $b(n)$ from \eqref{eq:Wscale} is known. 
If we choose $W_k \stackrel{d}{=} D$, where $D$ is as in \eqref{theD}, 
then due to the stability property we have the *equality* of distribution
$W_1 + \ldots + W_n \stackrel{d}{=} b(n) D$, 
for $b(n) = n^{1/\beta}$. 
Using the parametrisation of @SamorodnitskyTaqqu, a few lines of 
calculation (see e.g. the vignette on parametrisation in @MittagLeffleR) 
show that $D$ must have the stable distribution 
$S_\beta(\cos(\pi \beta/2)^{1/\beta}, +1, 0)$, which is 
implemented in the R package `stabledist` by @stabledist.

```{r make-caption}
caption = "
Tail and scale estimates for simulated data, with waiting times drawn from 
the stable distribution $S_\\beta(\\cos(\\pi \\beta/2)^{1/\\beta}, +1, 0)$ 
with $\\beta = 0.8$. Dashed lines are 95\\% 
confidence intervals, dotted 
lines are the known theoretical values ($0.8$ and $10000^{1/0.8}$).
\\label{fig:sim}
"
```

```{r simulated-example, message=FALSE, fig.cap=caption}
k_max <- 500 
thin_sim_ctrm <- thin(ctrm = sim_ctrm, k = k_max)
par(mfrow=c(1,2))
MLestimates(ctrm = thin_sim_ctrm, tail = tail, scale = n^(1/tail))
```

By \eqref{eq:Tellscale}, the distribution 
of $T(\ell)$ is approximately 
${\rm ML}(\beta, p^{-1/\beta}) 
= {\rm ML}(\beta, k^{-1/\beta} n^{1/\beta})$, which means 
$\sigma_0 = n^{1/\beta}$.
The distribution of $J_k$ is irrelevant for the inference on $\beta$ and 
$\sigma_0$ (we have chosen unit exponential random variables). 
Figure \ref{fig:sim} displays plots of $\hat \beta(\ell)$ and 
$\hat \sigma(\ell)$ vs. $k$, the number of exceedances as $\ell$ traverses 
the largest observations $J_i$. 
Dotted lines show 95% confidence intervals, which are derived from the 
asymptotic normality of the log-moments estimators [@Cahoy2013] and the $\delta$-method [@MittagLeffleR].
The dashed lines show the actual values of $\beta$ resp.\ $\sigma_0$, 
showing that our inference method effectively identifies the 
right parameters.

## Bitcoin trading volumes

```{r bitcoin-data, fig.cap="\\label{fig:bitcoin-data}Time Series of 'Bitcoin days destroyed', a measure for the traded volume of bitcoins."}
bitcoin_ctrm <- ctrm(bitcoin)
plot(bitcoin_ctrm, p = 0.02)
```

We study the daily trade volumes of Bitcoin since 2009, provided by 
Blockchain and downloaded from Data 
Market\footnote{\url{https://datamarket.com/data/list/?q=provider:blockchain}}. 
Although the observations are regular (daily), extremes in the trade volumes
occur in bursts, which can be seen over timescales of months and years 
(Figure \ref{fig:bitcoin-data}).

```{r bitcoin-data-tail-scale, message=FALSE, fig.cap="\\label{fig:bitcoin-tail-scale}Tail and scale plot of the bitcoin data."}
thin_bitcoin_ctrm <- thin(ctrm = bitcoin_ctrm, k = 250)
par(mfrow=c(1,2))
MLestimates(thin_bitcoin_ctrm, tail = 0.9, scale = 2 * 1E3)
```

Figure \ref{fig:bitcoin-tail-scale} shows plots identifying the candidates
$\beta = 0.9$ and $\sigma_0 = 2000$ for 
the tail and scale parameters of the exceedance time distribution. 
That is, exceedances of a threshold $\ell$ at the $k$-th largest observed 
magnitude are distributed as 
$$T(\ell) = \text{ML}(0.9, 2000 * k^{-1/0.9}).$$ 
A QQ plot (Figure \ref{fig:bitcoin-diag}) of the exceedance times at the 
level of the 200th 
largest event lends credence to a heavy-tailed distribution with tail
parameter near the value $1$.

## Solar Flare Data

```{r solar-flare-data, fig.cap="\\label{fig:solar-flare-data}The solar flare time series data."}
flares_ctrm <- ctrm(flares)
plot(flares_ctrm, p = 0.01)
```

The "complete Hard X Ray Burst Spectrometer event list" 
\footnote{\url{https://umbra.nascom.nasa.gov/smm/hxrbs.html}} 
@HXRBS is a 
comprehensive reference for all measurements of the Hard X 
Ray Burst Spectrometer on NASA's Solar Maximum Mission from the time of 
launch on Feb 14, 1980 to the end of the mission in Dec 1989. 12,776 
events were detected, with the "vast 
majority being solar flares". The list includes the start time, peak time, 
duration, and peak rate of each event. We have used "start time" as the 
variable for event times, and "peak rate" as the variable for event 
magnitudes (Figure \ref{fig:solar-flare-data}).

```{r solar-flare-tail-scale, message=FALSE, fig.cap="\\label{fig:flares}Stability plots for the tail and scale parameter of the Mittag-Leffler distribution of the Solar Flare dataset."}
thin_flares_ctrm <- thin(ctrm = flares_ctrm, k = 150)
par(mfrow=c(1,2))
MLestimates(thin_flares_ctrm, tail = tail, scale = 2.5 * 1E7)
```

Figure \ref{fig:flares} shows the fitted tail and scale parameters 
of the Mittag-Leffler distribution. The dotted line for the tail 
parameter is at $\beta = 0.85$, yielding the plot of (transformed) scale 
estimates $\hat \sigma_0 = k^{1/0.85} \hat \sigma(\ell)$. 
We suggest the estimate $\sigma_0 = 2.5 \times 10^7$ seconds 
$\approx 289$ days. 
The exceedance times of a threshold $\ell$ as high as the $k$-measurement 
are hence Mittag-Leffler distributed as
$$ T(\ell) \sim {\rm ML}(0.85, 289  k^{-1/0.85} \text{ days}).$$

# Discussion

Comparing plots of the simulated data in Figure \ref{fig:thresholdedBursty}
with plots of the 
empirical data \ref{fig:bitcoin-data} and \ref{fig:solar-flare-data}, 
it can be seen that the empirical data show long time intervals without 
*any* event occurring, whereas for real-world data events appear to happen 
continuously. 
This seeming discrepancy vanishes, however, when all but the $k_\text{max}$
largest observations are discarded. 
We repeat that the CTRM model focuses on extreme events and interprets 
smaller events as noise.

The CTRM model, moreover, assumes a "pure" power-law for the event 
inter-arrival times. 
Real datasets, however, are often exponentially 
tapered or truncated, see e.g. the discussion of tempered power-law 
distributions by @MeerschaertRoyQin and the truncated Pareto distribution 
by @Aban06. 
This means that the fit to a power-law
distribution may seem adequate for medium-size time scales, 
but that at very large time-scales the power-law character of the 
distribution can weaken or disappear.
This behaviour seems to appear in both the Bitcoin data and the Solar-Flare
data: the Hill plot for the tail parameter is increasing towards lighter
tails as the threshold reaches very high values. 
This may mean that the CTRM model may overestimate the heaviness of the
tail of the waiting time distribution; or that a CTRM base on a *tempered* 
power-law renewal process might be a more realistic model.

# Conclusion

We have proposed the CTRM model for the extremes of "bursty" events. 
Burstiness is a phenomenon of intermittency which has received a lot of 
attention in the recent statistical physics literature. 
The CTRM model is a straightforward generalization of the POT (Peaks over 
Threshold) model, for which the inter-arrival times between threshold 
crossings are exponentially distributed. 
If the Mittag-Leffler tail parameter of the CTRM equals $1$, then the 
CTRM model reproduces this behaviour exactly, showing that the CTRM model 
nests the POT model.

The scale parameter $\sigma$ of the inter-event distribution follows a 
power-law $\sigma \propto p^{-1/\beta}$, where $\beta \in (0,1)$ is the 
tail parameter of the inter-event distribution and $p$ the probability 
that an event crosses a given threshold. 
From this power law, we have constructed "stability plots", from which 
estimates of $\beta$ and $\sigma$ can be read off.

We have demonstrated the applicability of the CTRM model with two 
real-world datasets. 
Although the CTRM model possibly overestimates the heaviness of the tail 
of the inter-arrival distribution, it clearly captures that 
the inter-arrival times of threshold crossings scale non-linearly with 
the treshold crossing probability, and follow a clearly non-Poissonian 
behaviour. 
Thus we have shown that the CTRM model is a useful tool for the modelling 
of extremes of bursty events, which requires very little computation and 
which allows for straightforward ways of checking and criticizing model 
assumptions. 
The analyses from this paper are readily reproduced via the R package 
`CTRM`, available at \url{https://github.com/strakaps/CTRM}.

## Acknowledgements

The authors would like to thank Peter Scheffler for insights on 
stochastic process limits for CTRMs, and Gurtek Gill who helped create
the MittagLeffleR R-package.

\newpage

### 2018-04-16 article_springer/article_springer.Rmd
defer derivation of scaling limit to appendix

@@
 
+preamble: |
+  \usepackage{amssymb}
 ---
@@
 library(CTRM)
+library(magrittr)
 ```
@@
 
-We review the CTRM, or max-renewal model, in Section 2, and 
+We review the marked renewal process in Section 2, and 
 derive a scaling limit theorem for inter-exceedance times in Sections 3 &
@@
 
-# CTRMs
+# Marked Renewal Process (MRP)
 
-![\label{fig:ctrm} A CTRM sample path.](just-tikz-figure0.pdf)
-
-Continuous Time Random Maxima (CTRM), or Max-Renewal processes, track the 
-largest event in a renewal sequence of events [@Basrak2014; 
-@MeerschaertStoev08; @Hees16]:
-
-**Definition (CTRM):**
+**Definition:**
 
@@
 ($x_L \in [-\infty, +\infty), x_R \in (-\infty, +\infty]$). 
-The renewal process associated with the $W_k$ is 
-$$N(t) = \max\{n: W_1 + \ldots + W_n \le t\},$$
-and the running maximum is $M(n) := \bigvee_{k=1}^n J_k$. Then the process
-$$V(t)=M(N(t)) = \bigvee_{k=1}^{N(t)} J_k, \quad t \ge 0.$$
-is called a CTRM (Continuous Time Random Maxima) process. 
-If $W$ and $J$ are independent, the CTRM is said to be *uncoupled*. 
-We let $M(0) = x_L$.
+If $W$ and $J$ are independent, the MRP is said to be *uncoupled*.
 
-Figure \ref{fig:ctrm} shows a CTRM sample path.
-The alternative case where one considers the maximum of the first 
-$(N(t)+1)$'s event is called an *OCTRM process* (Overshooting Continuous 
-Time Random Maxima; or *Model II* by @Sumita1983). 
-The conceptual difference between CTRM and OCTRM is the order of waiting 
-times and events, which is $W_1,J_1,W_2,J_2,..$ for the CTRM and 
-$J_1,W_1,J_2,W_2,...$ for the OCTRM. 
-In the uncoupled case, unsurprisingly CTRM and OCTRM are asymptotically 
-equivalent. 
-In the coupled case, however, their distributions 
-can be dramatically different [@Hees16].
+In this setup, the $k$ magnitude $J_k$ occurs at time
+$T_k = W_1 + \ldots + W_k$. 
+Based on this simple model, we derive the following two random variables:
 
-The main purpose of this article is to introduce and discuss a method for 
-fitting data to an uncoupled CTRM, based on the following observable data:
+**Definition (MRP):**
 
-**Definition:**
-
-: The random variables
-$$X(\ell) = V(T(\ell)) - \ell, \quad 
-T(\ell) = \inf\{t: V(t) > \ell\}, 
-\quad \ell \in (x_L, x_R)$$
+: Given a threshold $\ell \in (x_L, x_R)$, 
+consider the stopping time 
+$$\tau(\ell) := \min\{k: J_k > \ell\},\quad \ell \in (x_L, x_R).$$
+The random variables
+$$X(\ell) = J_{\tau(\ell)} - \ell, \quad 
+T(\ell) = \sum_{k=1}^{\tau(\ell)} W_k$$
 are called the *exceedance* resp. *time until exceedance* of level $\ell$.
 
-#### POT-like approach.
-Since we assume the uncoupled case, $X(\ell)$ and $T(\ell)$ are 
-independent. 
-To see this, note that $X(\ell)$ is, in distribution, simply equal to
-$J | J > \ell$, independent of any waiting time $W_k$. 
-For our inference on the CTRM model, we extract realizations of 
-$X(\ell)$ and $T(\ell)$ from time series data by considering thresholds 
-$\ell$ ranging over some interval $[\ell_0, x_R)$. 
-(A reasonable default value for $\ell_0$ is the $95$-th
-percentile of $J$.)
-Write $X(\ell,i)$ for the $i$-th exceedance of level $\ell$, 
-and $T(\ell,i)$ for the inter-arrival time between
-$X(\ell,i-1)$ and $X(\ell,i)$. 
-Thus for any threshold $\ell \in [\ell_0, x_R)$,
-we construct sequences $\{T(\ell,i)\}_{i}$ and 
-$\{X(\ell,i)\}_{i}$. 
-These sequences are i.i.d. because a renewal occurs at each threshold
-crossing time, and independent because $W_k$ and $J_k$ are uncoupled.
-Extracting the exceedances $X(\ell)$ for inference is a standard procedure
-known as the Peaks Over Threshold (POT) approach in extreme value theory
-[@beirlantBook].
-Figure \ref{fig:thresholdedBursty} illustrates the exceedances 
-$X(\ell, i)$ in red and the times until exceedance $T(\ell, i)$ as the 
-preceding intervals marked by blue crosses.
+By restarting the MRP at $\tau(\ell)$, one can inductively construct the
+two i.i.d. sequences $T(\ell,n)$ and $X(\ell, n)$, $n \in \mathbb N$.
+Moreover, since we assume the uncoupled case, the two sequences are independent.[^1]
 
-```{r thresholdedBursty, message=FALSE, fig.cap="\\label{fig:thresholdedBursty}Exceedances (red) and Times until Exceedance (durations between blue crosses) for a given threshold $\\ell$ (dashed line)."}
+[^1]: (To see why, note that $X(\ell)$ is, in distribution, simply equal to 
+  $J | J > \ell$, independent of any waiting time $W_k$.)
+
+```{r thresholdedBursty, message=FALSE, fig.height=7, fig.cap="\\label{fig:thresholdedBursty}Exceedances (red) and Times until Exceedance (durations between blue crosses) for a given threshold $\\ell$ (dashed line)."}
 #rpareto <- function(n,tail){
@@
 sim_ctrm <- ctrm(data.frame(times, magnitudes)) 
-plot(sim_ctrm, p = 0.005)
+par(mfrow = c(2,1))
+plot(sim_ctrm, p = 0.01, main = "Simulated MRP") 
+flares %>% ctrm() %>% plot(p = 0.02, log = 'y', main = "HXRBS data") 
 ```
 
-A standard result from extreme value theory provides the asymptotic 
-distribution of $X(\ell)$ as $\ell \uparrow x_R$. For later use, we also 
-include the scaling limit of the cumulative maximum $M(n)$.
+Figure \ref{fig:thresholdedBursty} shows a simulated dataset in the top 
+panel, where $W$ has a stable distribution with tail parameter 
+$\beta =$ `r params$tail` (and skewness $1$ and location $0$), and 
+where $J$ is from a standard Gumbel distribution. In the bottom panel, 
+we plot a time series of solar flare intensities derived from a NASA
+dataset [@HXRBS][^*]. Clearly, the simulated data exhibit long intervals 
+_without any_ events, whereas in the real-world dataset events appear 
+continuously. The threshold exceedances, however, appear to have the same 
+statistical behaviour in both models. Observations below a threshold are 
+commonly discarded in Extreme Value Theory; the MRP models 
+interprets these observations as noise and filters them out.
 
-**Theorem GEV** (e.g. Chapter 2 & Section 5.3, @beirlantBook):
-
-: Suppose the distribution of $J_k$ is continuous. Then there
-exist non-decreasing norming functions $a(c)$ and $d(c)$ such that
-as $c \to \infty$, the running maximum\footnote{We extend $M(n)$ 
-continuously to $[0, +\infty)$ via $M(c) := M(\lfloor c \rfloor)$ where 
-$\lfloor c \rfloor$ is the 
-greatest integer not greater than $c$.} 
-$M(c)$ converges weakly 
-to a *Generalized Extreme Value Distribution* with shape
-parameter
-$\xi$:
-\begin{align}
-[M(c) - d(c)] / a(c) \stackrel{d}{\to} A, 
-\quad
-\mathbf P(A \le z) = G(z | \xi) = \exp\left(-[1+\xi z]^{-1/\xi}\right),\label{eq:GEV}
-\end{align}
-defined for all $z$ such that $1 + \xi z > 0$. 
-This definition extends continuously to $\xi = 0$ via 
-$$G(z | 0) = \exp(-\exp(-x)).$$
-For $\mu$ and $\sigma > 0$, we write ${\rm GEV}(\xi, \mu, \sigma)$ for the 
-probability distribution of the random variable $\sigma A + \mu$.
-
-    Moreover, asymptotically as $\ell \uparrow x_R$,
-$$\mathbf P(J - \ell > y | J > \ell) 
-\sim 1 - H(y),$$
-where 
-$$H(y) = \begin{cases}
-1 - (1+ \xi y / \tilde \sigma)^{-1/\xi}, & y \in (0,\infty) \text{ if } \xi > 0,\\
-1 - \exp(-y/\tilde \sigma), & y \in (0,\infty) \text{ if } \xi = 0,\\
-1 - (1+ \xi y / \tilde \sigma)^{-1/\xi}, & y \in (0, -\sigma / \xi) \text{ if } \xi < 0
-\end{cases}$$
-
-    and where $\tilde \sigma := \sigma + \xi(\ell-\mu)$.
-The CDF $H(y)$ is said to belong to the *Generalised Pareto family*
-$GP(\xi,\bar \sigma)$.
-
-# CTRM Scaling limits
-
-## Waiting times
-
-We will assume that the waiting times $W_k$ have infinite mean,
-i.e. a tail parameter $\beta \in (0,1)$ and regularly varying tail probabilities:
-$\mathbf P(W > t) \sim L(t) t^{-\beta}$ as $t \uparrow \infty$ for
-some slowly varying function $L(t)$. As usually, $f(t) \sim g(t)$
-means that the quotient of $f(t)$ and $g(t)$ converges to $1$. The
-law of the $W$ then lies in the domain of attraction of a stable law,
-in the sense that the distributional limit 
-\begin{align} \label{eq:Wscale}
-\frac{W_1 + \ldots + W_n}{b(n)} \overset{d}{\longrightarrow} D, 
-\quad n \to \infty
-\end{align}
-exists, for a regularly varying scaling function
-\begin{equation} \label{eq:bScale}
-b \in {\rm RV}_\infty(1/\beta)
-\end{equation}
-[See e.g. Section 2.9.2 in @beirlantBook for a short introduction to 
-regular variation]. 
-The limit is then a positively skewed stable distribution, 
-whose scale parameter is $1$ if $b(n)$ is chosen accordingly
-[see e.g. Section 3.7 in @MeerschaertSikorskii]. 
-This distribution is most concisely defined via its Laplace transform
-\begin{align} \label{theD}
-\mathbf E[\exp(-sD)] = \exp(-s^\beta).
-\end{align}
-Moreover, the following functional limit theorem holds 
-[see e.g. Remark 4.17 in @MeerschaertSikorskii]: 
-\[
-(W_1 + \ldots + W_{\lfloor ct \rfloor})/b(c) \overset{d}{\longrightarrow} D(t), \quad c \to \infty
-\] 
-with convergence in the Skorokhod $J_1$ topology. The limit
-$D(t)$ is a stable subordinator, i.e. an increasing Levy process with
-Laplace transform $\exp(-t s^\beta)$.
-
-It is well known [see e.g. @limitCTRW] that the renewal
-process then satisfies the functional limit
-$$
-N(ct)/ \tilde b(c) \stackrel{d}{\to} E(t) = \inf\{r: D(r) > t\}, 
-\quad c \to \infty
-$$
-for a scaling function $\tilde b(c) \in {\rm RV}_\infty(\beta)$ which is asymptotically inverse to $b(c)$, in the sense of @seneta (p.20): 
-$$
-b(\tilde b(c)) \sim c \sim \tilde b(b(c)).
-$$
-[also see Prop 4.15 in @MeerschaertSikorskii]. 
-The limit process $E(t)$ is called the _inverse stable subordinator_ [@invSubord].
-
-## Magnitudes and Extreme Value Distributions
-
-The extremal limit theorem then allows for an extension to functional 
-(i.e. pathwise) limits: assume that the norming sequences $a(c)$ and 
-$d(c)$ are as in Theorem GEV. Then 
-$$
-[M(ct) - d(c)] / a(c) \stackrel{d}{\to} A(t),
-\quad c \to \infty.
-$$
-Here convergence holds weakly in Skorokhod's $J_1$ topology, and the limit
-process $A(t)$ is an _extremal process_, with
-finite-dimensional distributions given by
-\begin{align}
-\label{eq:fin-dim-A}
-\mathbf P(A(t_i)\leq x_i,1\leq i \leq d) 
-= F_A(\wedge_{i=1}^d x_i)^{t_1} 
-F_A(\wedge_{i=2}^d x_i)^{t_2-t_1}
-\ldots F_A(x_d)^{t_d-t_{d-1}},
-\end{align}
-where $F_A(x)$ is a GEV distribution [see e.g. @resnick2013extreme].
-
-## CTRM limit
-
-The CTRM $V(t)$ results from the running maximum $M(n)$ via a time change by the renewal process $n = N(t)$. This is also reflected in its corresponding limit process:
-
-**Theorem MS1** [@MeerschaertStoev08]:
-
-: The CTRM process $V(t) = M(N(t))$ satisfies the following functional scaling limit in the Skorokhod $J_1$ topology: 
-$$
-[V(ct) - d(\tilde b(c))] / a(\tilde b(c)) \stackrel{d}{\to} 
-A(E(t)), \quad c \to \infty.
-$$
-
-The distribution of the _hitting time_ of a level $\ell^*$ by the limit 
-process $A(E(t))$ is also known, and we give it below for the convenience 
-of the reader:
-
-**Theorem MS2** [@MeerschaertStoev08]:
-
-: Let $F_A$ be the CDF of a GEV distribution, and let $A(t)$ be the
-extremal process corresponding to $F_A$ via \eqref{eq:fin-dim-A}. 
-For a given threshold $\ell^*$ in the support of $F_A$,
-the hitting time
-$$
-B(\ell^*) = \inf\{t: A(E(t)) > \ell^*\} 
-$$
-is equal in distribution to $(-\log F_A(\ell^*))^{-1/\beta} X^{1/\beta} D$,
-where $X \sim {\rm Exp}(1)$ and $D$ (defined in \eqref{theD}) are 
-independent.
-
-The Mittag-Leffler distribution with parameter $\beta \in (0,1]$ is 
-a heavy-tailed positive distribution if $\beta < 1$; for $\beta = 1$, 
-it specializes to the Exponential distribution. 
-For $\sigma > 0$, we write ${\rm ML}(\beta, \sigma)$ for the distribution 
-of $\sigma Y$, where $Y$ has Laplace transform 
-$\mathbf E[\exp(-s Y)] = 1/(1+s^\beta)$. Due to e.g. Theorem 19.1 in 
-@Haubold11, the exceedance time from Theorem MS2 can be written as 
-\begin{align} \label{eq:hitting-ML}
-B(\ell^*) \sim {\rm ML}\left(\beta, (-\log F_A(\ell^*))^{-1/\beta}\right)
-\end{align}
+[^*]: The "complete Hard X Ray Burst Spectrometer event list" 
+is a comprehensive reference for all measurements of the Hard X 
+Ray Burst Spectrometer on NASA's Solar Maximum Mission from the time of 
+launch on Feb 14, 1980 to the end of the mission in Dec 1989. 12,776 
+events were detected, with the "vast 
+majority being solar flares". The list includes the start time, peak time, 
+duration, and peak rate of each event. We have used "start time" as the 
+variable for event times, and "peak rate" as the variable for event 
+magnitudes.
 
@@
 
+\appendix
+
+For our inference on the CTRM model, we extract realizations of 
+$X(\ell)$ and $T(\ell)$ from time series data by considering thresholds 
+$\ell$ ranging over some interval $[\ell_0, x_R)$. 
+(A reasonable default value for $\ell_0$ is the $95$-th
+percentile of $J$.)
+Write $X(\ell,i)$ for the $i$-th exceedance of level $\ell$, 
+and $T(\ell,i)$ for the inter-arrival time between
+$X(\ell,i-1)$ and $X(\ell,i)$. 
+Thus for any threshold $\ell \in [\ell_0, x_R)$,
+we construct sequences $\{T(\ell,i)\}_{i}$ and 
+$\{X(\ell,i)\}_{i}$. 
+These sequences are i.i.d. because a renewal occurs at each threshold
+crossing time, and independent because $W_k$ and $J_k$ are uncoupled.
+Extracting the exceedances $X(\ell)$ for inference is a standard procedure
+known as the Peaks Over Threshold (POT) approach in extreme value theory
+[@beirlantBook].
+Figure \ref{fig:thresholdedBursty} illustrates the exceedances 
+$X(\ell, i)$ in red and the times until exceedance $T(\ell, i)$ as the 
+preceding intervals marked by blue crosses.
+
+A standard result from extreme value theory provides the asymptotic 
+distribution of $X(\ell)$ as $\ell \uparrow x_R$. For later use, we also 
+include the scaling limit of the cumulative maximum $M(n)$.
+
+**Theorem GEV** (e.g. Chapter 2 & Section 5.3, @beirlantBook):
+
+: Suppose the distribution of $J_k$ is continuous. Then there
+exist non-decreasing norming functions $a(c)$ and $d(c)$ such that
+as $c \to \infty$, the running maximum\footnote{We extend $M(n)$ 
+continuously to $[0, +\infty)$ via $M(c) := M(\lfloor c \rfloor)$ where 
+$\lfloor c \rfloor$ is the 
+greatest integer not greater than $c$.} 
+$M(c)$ converges weakly 
+to a *Generalized Extreme Value Distribution* with shape
+parameter
+$\xi$:
+\begin{align}
+[M(c) - d(c)] / a(c) \stackrel{d}{\to} A, 
+\quad
+\mathbf P(A \le z) = G(z | \xi) = \exp\left(-[1+\xi z]^{-1/\xi}\right),\label{eq:GEV}
+\end{align}
+defined for all $z$ such that $1 + \xi z > 0$. 
+This definition extends continuously to $\xi = 0$ via 
+$$G(z | 0) = \exp(-\exp(-x)).$$
+For $\mu$ and $\sigma > 0$, we write ${\rm GEV}(\xi, \mu, \sigma)$ for the 
+probability distribution of the random variable $\sigma A + \mu$.
+
+    Moreover, asymptotically as $\ell \uparrow x_R$,
+$$\mathbf P(J - \ell > y | J > \ell) 
+\sim 1 - H(y),$$
+where 
+$$H(y) = \begin{cases}
+1 - (1+ \xi y / \tilde \sigma)^{-1/\xi}, & y \in (0,\infty) \text{ if } \xi > 0,\\
+1 - \exp(-y/\tilde \sigma), & y \in (0,\infty) \text{ if } \xi = 0,\\
+1 - (1+ \xi y / \tilde \sigma)^{-1/\xi}, & y \in (0, -\sigma / \xi) \text{ if } \xi < 0
+\end{cases}$$
+
+    and where $\tilde \sigma := \sigma + \xi(\ell-\mu)$.
+The CDF $H(y)$ is said to belong to the *Generalised Pareto family*
+$GP(\xi,\bar \sigma)$.
+
+# CTRM Scaling limits
+
+## Waiting times
+
+We will assume that the waiting times $W_k$ have infinite mean,
+i.e. a tail parameter $\beta \in (0,1)$ and regularly varying tail probabilities:
+$\mathbf P(W > t) \sim L(t) t^{-\beta}$ as $t \uparrow \infty$ for
+some slowly varying function $L(t)$. As usually, $f(t) \sim g(t)$
+means that the quotient of $f(t)$ and $g(t)$ converges to $1$. The
+law of the $W$ then lies in the domain of attraction of a stable law,
+in the sense that the distributional limit 
+\begin{align} \label{eq:Wscale}
+\frac{W_1 + \ldots + W_n}{b(n)} \overset{d}{\longrightarrow} D, 
+\quad n \to \infty
+\end{align}
+exists, for a regularly varying scaling function
+\begin{equation} \label{eq:bScale}
+b \in {\rm RV}_\infty(1/\beta)
+\end{equation}
+[See e.g. Section 2.9.2 in @beirlantBook for a short introduction to 
+regular variation]. 
+The limit is then a positively skewed stable distribution, 
+whose scale parameter is $1$ if $b(n)$ is chosen accordingly
+[see e.g. Section 3.7 in @MeerschaertSikorskii]. 
+This distribution is most concisely defined via its Laplace transform
+\begin{align} \label{theD}
+\mathbf E[\exp(-sD)] = \exp(-s^\beta).
+\end{align}
+Moreover, the following functional limit theorem holds 
+[see e.g. Remark 4.17 in @MeerschaertSikorskii]: 
+\[
+(W_1 + \ldots + W_{\lfloor ct \rfloor})/b(c) \overset{d}{\longrightarrow} D(t), \quad c \to \infty
+\] 
+with convergence in the Skorokhod $J_1$ topology. The limit
+$D(t)$ is a stable subordinator, i.e. an increasing Levy process with
+Laplace transform $\exp(-t s^\beta)$.
+
+It is well known [see e.g. @limitCTRW] that the renewal
+process then satisfies the functional limit
+$$
+N(ct)/ \tilde b(c) \stackrel{d}{\to} E(t) = \inf\{r: D(r) > t\}, 
+\quad c \to \infty
+$$
+for a scaling function $\tilde b(c) \in {\rm RV}_\infty(\beta)$ which is asymptotically inverse to $b(c)$, in the sense of @seneta (p.20): 
+$$
+b(\tilde b(c)) \sim c \sim \tilde b(b(c)).
+$$
+[also see Prop 4.15 in @MeerschaertSikorskii]. 
+The limit process $E(t)$ is called the _inverse stable subordinator_ [@invSubord].
+
+## Magnitudes and Extreme Value Distributions
+
+The extremal limit theorem then allows for an extension to functional 
+(i.e. pathwise) limits: assume that the norming sequences $a(c)$ and 
+$d(c)$ are as in Theorem GEV. Then 
+$$
+[M(ct) - d(c)] / a(c) \stackrel{d}{\to} A(t),
+\quad c \to \infty.
+$$
+Here convergence holds weakly in Skorokhod's $J_1$ topology, and the limit
+process $A(t)$ is an _extremal process_, with
+finite-dimensional distributions given by
+\begin{align}
+\label{eq:fin-dim-A}
+\mathbf P(A(t_i)\leq x_i,1\leq i \leq d) 
+= F_A(\wedge_{i=1}^d x_i)^{t_1} 
+F_A(\wedge_{i=2}^d x_i)^{t_2-t_1}
+\ldots F_A(x_d)^{t_d-t_{d-1}},
+\end{align}
+where $F_A(x)$ is a GEV distribution [see e.g. @resnick2013extreme].
+
+## CTRM limit
+
+The CTRM $V(t)$ results from the running maximum $M(n)$ via a time change by the renewal process $n = N(t)$. This is also reflected in its corresponding limit process:
+
+**Theorem MS1** [@MeerschaertStoev08]:
+
+: The CTRM process $V(t) = M(N(t))$ satisfies the following functional scaling limit in the Skorokhod $J_1$ topology: 
+$$
+[V(ct) - d(\tilde b(c))] / a(\tilde b(c)) \stackrel{d}{\to} 
+A(E(t)), \quad c \to \infty.
+$$
+
+The distribution of the _hitting time_ of a level $\ell^*$ by the limit 
+process $A(E(t))$ is also known, and we give it below for the convenience 
+of the reader:
+
+**Theorem MS2** [@MeerschaertStoev08]:
+
+: Let $F_A$ be the CDF of a GEV distribution, and let $A(t)$ be the
+extremal process corresponding to $F_A$ via \eqref{eq:fin-dim-A}. 
+For a given threshold $\ell^*$ in the support of $F_A$,
+the hitting time
+$$
+B(\ell^*) = \inf\{t: A(E(t)) > \ell^*\} 
+$$
+is equal in distribution to $(-\log F_A(\ell^*))^{-1/\beta} X^{1/\beta} D$,
+where $X \sim {\rm Exp}(1)$ and $D$ (defined in \eqref{theD}) are 
+independent.
+
+The Mittag-Leffler distribution with parameter $\beta \in (0,1]$ is 
+a heavy-tailed positive distribution if $\beta < 1$; for $\beta = 1$, 
+it specializes to the Exponential distribution. 
+For $\sigma > 0$, we write ${\rm ML}(\beta, \sigma)$ for the distribution 
+of $\sigma Y$, where $Y$ has Laplace transform 
+$\mathbf E[\exp(-s Y)] = 1/(1+s^\beta)$. Due to e.g. Theorem 19.1 in 
+@Haubold11, the exceedance time from Theorem MS2 can be written as 
+\begin{align} \label{eq:hitting-ML}
+B(\ell^*) \sim {\rm ML}\left(\beta, (-\log F_A(\ell^*))^{-1/\beta}\right)
+\end{align}
+
 \newpage

### 2018-04-16 article_springer/article_springer.Rmd
remove block maxima discussion

@@
 
-[^1]: (To see why, note that $X(\ell)$ is, in distribution, simply equal to 
-  $J | J > \ell$, independent of any waiting time $W_k$.)
+[^1]: To see why, note that $X(\ell)$ is, in distribution, simply equal to 
+  $J | J > \ell$, independent of any waiting time $W_k$.
 
@@
 statistical behaviour in both models. Observations below a threshold are 
-commonly discarded in Extreme Value Theory; the MRP models 
+commonly discarded in Extreme Value Theory; likewise, our MRP model
 interprets these observations as noise and filters them out.
@@
 # Scaling limit of Exceedance Times
-
-In classical extreme value theory, there are two main approaches for 
-the inference on GEV distributions: Block
-Maxima and Peaks-Over-Threshold (POT). Block 
-Maxima subdivide the time line into 'blocks' of equal length, 
-and the maximum of each block is taken as realization of the random 
-variable $M_n$. 
-This approach is not appropriate for CTRM data, because maxima in 
-same-sized blocks will not be i.i.d.
-As mentioned in Section 2, the POT approach *does* extract i.i.d. $X(\ell)$ 
-(and $T(\ell)$), and can hence be directly used for the inference on 
-the extreme values of $J_k$. 
-Figure \ref{fig:GP-simulated} shows an example for the so-called 
-"threshold-selection" plots for data drawn from the standard Gumbel 
-distribution. 
-For a range of thresholds, maximum likelihood estimators of the shape and 
-scale parameters in the GP distribution are computed and plotted. 
-Note that the scale parameter is transformed so that it appears independent
-of the threshold [see e.g. Section 4.3.4 in @ColesBook].
-
-```{r GPD-simulated-data, warning=FALSE, fig.cap="\\label{fig:GP-simulated}Stability plot for the shape and scale parameters of the generalized Pareto distribution.
-Here, the magnitudes are standard Gumbel, hence $\\xi = 0$ and $\\sigma = 1$.
-Plots were generated using the POT package in R [@R-POT]."}
-par(mfrow = c(1,2))
-JJ <- coredata.ctrm(sim_ctrm)
-u.range <- quantile(x = JJ, probs = c(0.75, 0.95))
-POT::tcplot(JJ, u.range = u.range)
-# extRemes::threshrange.plot(mrp("getMags"), type = "GP", set.panels = FALSE)
-```
-
-For the remainder of this article, we focus on statistical inference 
-for the inter-exceedance times $T(\ell)$ of the threshold crossings. 
-In our setting, the inter-exceedance times follow a fractional 
-Poisson process instead of a standard Poisson process, which is how our
-approach generalizes the standard POT approach.
 

### 2018-04-16 article_springer/article_springer.Rmd
Simplify section on scaling limit of exceedance time

@@
 
+In this section we state the key theorem below (a proof is in the appendix). 
+For more details on regular variation and stable limit theorems, we 
+recommend the book by @MeerschaertSikorskii.
+
 **Theorem:**
 
-: Let $b(c)$ be the scaling function \eqref{eq:bScale},
-and let $\ell$ be a threshold from the support $[x_L, x_R]$ of $J$. 
-Furthermore let $p := \mathbf P(J > \ell)$. Under the assumption \eqref{eq:Wscale} and the assumptions of the GEV Theorem, we have 
-\begin{equation} \label{eq:Tellscale}
-T(\ell) / b(1/p) \to {\rm ML}(\beta, 1) \text{ as } \ell \uparrow x_R.
-\end{equation}
+: Let the waiting times $J_k$ be in the domain of attraction of a 
+positively skewed sum-stable law with stability parameter $0 < \beta < 1$; 
+more precisely,
+$$
+\frac{W_1 + \ldots + W_n}{b(n)} \overset{d}{\longrightarrow} D, 
+\quad n \to \infty
+$$
+for a function $b(n)$ which is regularly varying at $\infty$ with 
+parameter $1/\beta$, and where $\mathbf E[\exp(-sD)] = \exp(-s^\beta)$. 
+Write $p := \mathbf P(J > \ell)$. Then the weak convergence
+$$
+\frac{T(\ell)} {b(1/p)} \to W_\beta \quad \text{ as } \quad \ell \uparrow x_R
+$$
+holds, where the Mittag-Leffler random variable $W_\beta$ is defined on 
+the positive real numbers via 
+$$
+\mathbf E[\exp(-sW_\beta)] = \frac{1}{1+s^\beta}.
+$$
 
-*Proof:*
-Let the scaling functions $a(c)$ and $d(c)$ be as in Section 
-\ref{magnitudes-and-extreme-value-distributions}, and assume WLOG 
-$\ell = a(n) \ell^* + d(n)$ for some arbitrary but fixed $\ell^*$, out of the support of $A$. 
-We first note that due to \eqref{eq:GEV}
-\begin{equation} 
-F_J (a(c) \ell^* + d(c))^c \stackrel{d}{\to} F_A(\ell^*), \text{ as } c \to \infty.
-\end{equation}
-\noindent Taking the logarithm on each side and using the relationship  $z-1 \sim \log(z)$ as $z \to 1$, we get
-\begin{equation}
-c (1-F_J(a(c) \ell^*+d(c))) \stackrel{d}{\to} - \log F_A(\ell^*).
-\end{equation}
-\noindent Hence we have 
-\begin{equation}
-c \cdot p \stackrel{d}{\to} - \log F_A(\ell^*) \label{eq:np_conv}
-\end{equation}
-\noindent as $\ell \uparrow x_R$.
-Now we get
-\begin{align}
-\begin{split}
-\mathbf P \left[T(\ell)/b(1/p) > t \right]
-&= \mathbf P[V(b(1/p) t) \leq \ell] \label{eq:proofTheo}
-= \mathbf P[V(b(1/p)) \le a(c) \ell^* + d(c)]\\
-&= \mathbf P\left(\frac{V(b(1/p)/b(c) \cdot b(c) \cdot t)-d(c)}{a(c)} \le \ell^*\right) \\
-&\stackrel{d}{\to} \mathbf P(A(E(-\log F_A(l))^{-1/\beta} t) \leq \ell^*),
-\end{split}
-\end{align}
-where the convergence follows due to Theorem MS1 (with $c$ replaced by $b(c)$) and the fact that
-\begin{equation}
-\frac{b(1/p)}{b(c)} 
-= \frac{b(1/cp \cdot c)}{b(c)} 
-\sim (cp)^{-1/\beta}
-\to \left( -\log F_A(l)\right)^{-1/\beta} 
-\text{ as } c \to \infty.\label{eq:proofTheo2}
-\end{equation}
-In \eqref{eq:proofTheo2} we used \eqref{eq:np_conv} and 
-$b \in RV(1/\beta)$, which means that 
-$b(\lambda c) / b(c) \rightarrow \lambda^{1/\beta}$ as 
-$c \rightarrow \infty$ uniformly in $\lambda$ on each compact subset of 
-$(0,\infty)$. 
-The limit in \eqref{eq:proofTheo} is equal to
-$$\mathbf P \left( \left( -\log(F_A(\ell^{*})) \right)^ {1/\beta} B(\ell^*) > t\right).$$ 
-Due to Theorem MS2 and \eqref{eq:hitting-ML}, we know that 
-$(-\log F_A (\ell^*))^{1/\beta} B(\ell^*)$ is $ML(\beta,1)$ distributed, 
-and hence the theorem follows.
-
-**Remark:**
-
-: By the above theorem, the inter-exceedance times are i.i.d. and
-approximately Mittag-Leffler distributed, which means that the exceedance
-times form a *fractional Poisson process* [@Laskin2003]. 
-Since the Mittag-Leffler distribution nests the exponential distribution 
-(the special case where $\beta = 1$), the fractional Poisson process 
-generalizes the standard Poisson process. 
-As the threshold height increases, the threshold crossing events are 
-effectively "thinned out", and the thinned (or rarefied) processes retain
-the characteristics of a fractional Poisson process [@Gorenflo2010], 
-with a growing scale parameter $b(1/p)$.
-
-**Remark:**
-
-: A fractional Poisson process can be represented as a
-standard Poisson process $N(t)$, time-changed by an inverse stable 
-subordinator $E(t)$ [@Meerschaert2010b]. 
-This pattern can be made sense of in our context: 
-The exceedance times for a standard extreme value process $A(t)$ form a 
-standard Poisson process $N(t)$. Accordingly, the exceedance times 
-of the CTRM limit $A(E(t))$ must be $N(E(t))$, a fractional Poisson 
-process.
+\noindent In general, for $\sigma > 0$ we write ${\rm ML}(\beta, \sigma)$ for the 
+distribution of $\sigma W_\beta$. 
+The Mittag-Leffler distribution with parameter $\beta \in (0,1]$ is 
+a heavy-tailed positive distribution for $\beta < 1$, with infinite mean. 
+However, as $\beta \uparrow 1$, ${\rm ML}(\beta, \sigma)$ converges 
+weakly to the exponential distribution ${\rm Exp}(\sigma)$.
+This means that although its moments are all infinite, the Mittag-Leffler
+distribution may (if $\beta$ is close to 1) be indistinguishable from the 
+exponential distribution, from the point of view of applied statistics. 
+For a detailed reference on the Mittag-Leffler distribution, see e.g. 
+@Haubold11.
 
@@
 ```{r make-caption}
-caption = "
-Tail and scale estimates for simulated data, with waiting times drawn from 
-the stable distribution $S_\\beta(\\cos(\\pi \\beta/2)^{1/\\beta}, +1, 0)$ 
-with $\\beta = 0.8$. Dashed lines are 95\\% 
-confidence intervals, dotted 
-lines are the known theoretical values ($0.8$ and $10000^{1/0.8}$).
-\\label{fig:sim}
-"
+caption = "Tail and scale estimates for simulated data, with waiting times drawn from the stable distribution $S_\\beta(\\cos(\\pi \\beta/2)^{1/\\beta}, +1, 0)$ with $\\beta = 0.8$.
+Dashed lines are 95\\% confidence intervals, dotted lines are the known theoretical values ($0.8$ and $10000^{1/0.8}$).
+\\label{fig:sim}"
 ```
@@
 
-The Mittag-Leffler distribution with parameter $\beta \in (0,1]$ is 
-a heavy-tailed positive distribution if $\beta < 1$; for $\beta = 1$, 
-it specializes to the Exponential distribution. 
-For $\sigma > 0$, we write ${\rm ML}(\beta, \sigma)$ for the distribution 
-of $\sigma Y$, where $Y$ has Laplace transform 
-$\mathbf E[\exp(-s Y)] = 1/(1+s^\beta)$. Due to e.g. Theorem 19.1 in 
-@Haubold11, the exceedance time from Theorem MS2 can be written as 
-\begin{align} \label{eq:hitting-ML}
-B(\ell^*) \sim {\rm ML}\left(\beta, (-\log F_A(\ell^*))^{-1/\beta}\right)
+*Proof:*
+Let the scaling functions $a(c)$ and $d(c)$ be as in Section 
+\ref{magnitudes-and-extreme-value-distributions}, and assume WLOG 
+$\ell = a(n) \ell^* + d(n)$ for some arbitrary but fixed $\ell^*$, out of the support of $A$. 
+We first note that due to \eqref{eq:GEV}
+\begin{equation} 
+F_J (a(c) \ell^* + d(c))^c \stackrel{d}{\to} F_A(\ell^*), \text{ as } c \to \infty.
+\end{equation}
+\noindent Taking the logarithm on each side and using the relationship  $z-1 \sim \log(z)$ as $z \to 1$, we get
+\begin{equation}
+c (1-F_J(a(c) \ell^*+d(c))) \stackrel{d}{\to} - \log F_A(\ell^*).
+\end{equation}
+\noindent Hence we have 
+\begin{equation}
+c \cdot p \stackrel{d}{\to} - \log F_A(\ell^*) \label{eq:np_conv}
+\end{equation}
+\noindent as $\ell \uparrow x_R$.
+Now we get
+\begin{align}
+\begin{split}
+\mathbf P \left[T(\ell)/b(1/p) > t \right]
+&= \mathbf P[V(b(1/p) t) \leq \ell] \label{eq:proofTheo}
+= \mathbf P[V(b(1/p)) \le a(c) \ell^* + d(c)]\\
+&= \mathbf P\left(\frac{V(b(1/p)/b(c) \cdot b(c) \cdot t)-d(c)}{a(c)} \le \ell^*\right) \\
+&\stackrel{d}{\to} \mathbf P(A(E(-\log F_A(l))^{-1/\beta} t) \leq \ell^*),
+\end{split}
 \end{align}
+where the convergence follows due to Theorem MS1 (with $c$ replaced by $b(c)$) and the fact that
+\begin{equation}
+\frac{b(1/p)}{b(c)} 
+= \frac{b(1/cp \cdot c)}{b(c)} 
+\sim (cp)^{-1/\beta}
+\to \left( -\log F_A(l)\right)^{-1/\beta} 
+\text{ as } c \to \infty.\label{eq:proofTheo2}
+\end{equation}
+In \eqref{eq:proofTheo2} we used \eqref{eq:np_conv} and 
+$b \in RV(1/\beta)$, which means that 
+$b(\lambda c) / b(c) \rightarrow \lambda^{1/\beta}$ as 
+$c \rightarrow \infty$ uniformly in $\lambda$ on each compact subset of 
+$(0,\infty)$. 
+The limit in \eqref{eq:proofTheo} is equal to
+$$\mathbf P \left( \left( -\log(F_A(\ell^{*})) \right)^ {1/\beta} B(\ell^*) > t\right).$$ 
+Due to Theorem MS2 and \eqref{eq:hitting-ML}, we know that 
+$(-\log F_A (\ell^*))^{1/\beta} B(\ell^*)$ is $ML(\beta,1)$ distributed, 
+and hence the theorem follows.
+
+**Remark:**
+
+: By the above theorem, the inter-exceedance times are i.i.d. and
+approximately Mittag-Leffler distributed, which means that the exceedance
+times form a *fractional Poisson process* [@Laskin2003]. 
+Since the Mittag-Leffler distribution nests the exponential distribution 
+(the special case where $\beta = 1$), the fractional Poisson process 
+generalizes the standard Poisson process. 
+As the threshold height increases, the threshold crossing events are 
+effectively "thinned out", and the thinned (or rarefied) processes retain
+the characteristics of a fractional Poisson process [@Gorenflo2010], 
+with a growing scale parameter $b(1/p)$.
+
+**Remark:**
+
+: A fractional Poisson process can be represented as a
+standard Poisson process $N(t)$, time-changed by an inverse stable 
+subordinator $E(t)$ [@Meerschaert2010b]. 
+This pattern can be made sense of in our context: 
+The exceedance times for a standard extreme value process $A(t)$ form a 
+standard Poisson process $N(t)$. Accordingly, the exceedance times 
+of the CTRM limit $A(E(t))$ must be $N(E(t))$, a fractional Poisson 
+process.
 

### 2018-04-16 article_springer/article_springer.Rmd
proof with details on subordination

@@
 @Haubold11.
+
+_Proof of Theorem:_
+We interpret the threshold crossing time as the hitting time of the 
+underlying CTRM (Continuous Time Random Maxima) or "max-renewal process", 
+and utilize a result by @MeerschaertStoev08. 
+The running maximum process is defined as 
+$$
+M_J(t) := J_1 \vee \ldots \vee J_{\lfloor t \rfloor},
+$$
+and as we assume the $J_k$ have a continuous distribution, there exist 
+norming functions $a(c)$ and $d(c)$ such that 
+$$
+\frac{M_J(t) - d(t)}{a(t)} \stackrel{d}{\longrightarrow} A, \quad t \to \infty
+$$
+where $A$ is a random variable with a generalized extreme value distribution. 
+The underlying CTRM is then defined via 
+$$
+X(t) = M_J(N(t)), \quad t \ge 0
+$$
+where $N(t)$ is the renewal process associated with the waiting times 
+$W_k$: 
+$$
+N(t) = \max\{n: W_1 + \ldots + W_n \le t\}.
+$$
+Now a key observation is that
+$$
+T(\ell) = \inf\{t: V(t) > \ell\}, 
+$$
+and that 
+$$
+T(\ell) > t \quad \text{ if and only if } \quad V(t) \le \ell.
+$$
+By [Theorem 3.1, @MeerschaertStoev08], we have the stochastic process 
+convergence 
+$$
+\frac{V(ct) - d(\tilde b(c))}{a(\tilde b(c))} \stackrel{d}{\longrightarrow} 
+A(E(t)), \quad t > 0.
+$$
+where:
+
+* $A(t)$ is the extremal process such that $A(1) \stackrel{d}{=} A$, 
+* $E(t) = \inf\{u: D(u) > t\}$ is an inverse subordinator, 
+  associated with the Levy process $D(t)$ that satisfies 
+  $D(1) \stackrel{d}{=} D$,
+* $\tilde b(c)$ is a regularly varying norming function which is
+  _inverse_ to $b(c)$: $b(\tilde b(c)) \sim c \sim \tilde b(b(c))$.
+
+Now 
+\begin{align}
+\begin{split}
+\mathbf P \left[T(\ell)/b(1/p) > t \right]
+&= \mathbf P[V(b(1/p) t) \leq \ell] \label{eq:proofTheo}
+= \mathbf P[V(b(1/p)) \le a(c) \ell^* + d(c)]\\
+&= \mathbf P\left(\frac{V(b(1/p)/b(c) \cdot b(c) \cdot t)-d(c)}{a(c)} \le \ell^*\right) \\
+&\stackrel{d}{\to} \mathbf P(A(E(-\log F_A(l))^{-1/\beta} t) \leq \ell^*),
+\end{split}
+\end{align}
+where the convergence follows due to Theorem MS1 (with $c$ replaced by $b(c)$) and the fact that
+\begin{equation}
+\frac{b(1/p)}{b(c)} 
+= \frac{b(1/cp \cdot c)}{b(c)} 
+\sim (cp)^{-1/\beta}
+\to \left( -\log F_A(l)\right)^{-1/\beta} 
+\text{ as } c \to \infty.\label{eq:proofTheo2}
+\end{equation}
+In \eqref{eq:proofTheo2} we used \eqref{eq:np_conv} and 
+$b \in RV(1/\beta)$, which means that 
+$b(\lambda c) / b(c) \rightarrow \lambda^{1/\beta}$ as 
+$c \rightarrow \infty$ uniformly in $\lambda$ on each compact subset of 
+$(0,\infty)$. 
+The limit in \eqref{eq:proofTheo} is equal to
+$$\mathbf P \left( \left( -\log(F_A(\ell^{*})) \right)^ {1/\beta} B(\ell^*) > t\right).$$ 
+Due to Theorem MS2 and \eqref{eq:hitting-ML}, we know that 
+$(-\log F_A (\ell^*))^{1/\beta} B(\ell^*)$ is $ML(\beta,1)$ distributed, 
+and hence the theorem follows.
+
+# Statistics of the Mittag-Leffler distribution
 
@@
 Now we get
-\begin{align}
-\begin{split}
-\mathbf P \left[T(\ell)/b(1/p) > t \right]
-&= \mathbf P[V(b(1/p) t) \leq \ell] \label{eq:proofTheo}
-= \mathbf P[V(b(1/p)) \le a(c) \ell^* + d(c)]\\
-&= \mathbf P\left(\frac{V(b(1/p)/b(c) \cdot b(c) \cdot t)-d(c)}{a(c)} \le \ell^*\right) \\
-&\stackrel{d}{\to} \mathbf P(A(E(-\log F_A(l))^{-1/\beta} t) \leq \ell^*),
-\end{split}
-\end{align}
-where the convergence follows due to Theorem MS1 (with $c$ replaced by $b(c)$) and the fact that
-\begin{equation}
-\frac{b(1/p)}{b(c)} 
-= \frac{b(1/cp \cdot c)}{b(c)} 
-\sim (cp)^{-1/\beta}
-\to \left( -\log F_A(l)\right)^{-1/\beta} 
-\text{ as } c \to \infty.\label{eq:proofTheo2}
-\end{equation}
-In \eqref{eq:proofTheo2} we used \eqref{eq:np_conv} and 
-$b \in RV(1/\beta)$, which means that 
-$b(\lambda c) / b(c) \rightarrow \lambda^{1/\beta}$ as 
-$c \rightarrow \infty$ uniformly in $\lambda$ on each compact subset of 
-$(0,\infty)$. 
-The limit in \eqref{eq:proofTheo} is equal to
-$$\mathbf P \left( \left( -\log(F_A(\ell^{*})) \right)^ {1/\beta} B(\ell^*) > t\right).$$ 
-Due to Theorem MS2 and \eqref{eq:hitting-ML}, we know that 
-$(-\log F_A (\ell^*))^{1/\beta} B(\ell^*)$ is $ML(\beta,1)$ distributed, 
-and hence the theorem follows.
 

### 2018-04-16 article_springer/article_springer.Rmd
simplified proof

--- 2018-04-16 article_springer/article_springer.Rmd
@@
 @Haubold11.
+
+_Proof of Theorem:_
+We interpret the threshold crossing time as the hitting time of the 
+underlying CTRM (Continuous Time Random Maxima) or "max-renewal process", 
+and then utilize a result by @MeerschaertStoev08. 
+The running maximum process is defined as 
+$$
+M_J(c) := J_1 \vee \ldots \vee J_{\lfloor c \rfloor},
+$$
+and since we assume that the $J_k$ have a continuous distribution, there exist 
+norming functions $a(c)$ and $d(c)$ such that 
+$$
+\mathbf P\left[ \frac{M_J(c) - d(c)}{a(c)} \le \ell^* \right] 
+\stackrel{d}{\longrightarrow} F(\ell^*), \quad t \to \infty
+$$
+where $F$ is a generalized extreme value distribution, and $\ell^*$ is any 
+value from the support of $F$.
+
+The underlying CTRM is then defined via 
+$$
+M(t) = M_J(N(t)), \quad t \ge 0
+$$
+where $N(t)$ is the renewal process associated with the waiting times 
+$W_k$: 
+$$
+N(t) = \max\{n: W_1 + \ldots + W_n \le t\}.
+$$
+Now a key observation is that
+$$
+T(\ell) = \inf\{t: V(t) > \ell\}, 
+$$
+and that 
+$$
+T(\ell) > t \quad \text{ if and only if } \quad V(t) \le \ell.
+$$
+By [Theorem 3.1, @MeerschaertStoev08], we have the stochastic process 
+convergence 
+$$
+\frac{M(ct) - d(\tilde b(c))}{a(\tilde b(c))} \stackrel{d}{\longrightarrow} 
+M(t), \quad t > 0.
+$$
+where $M(t)$ is a time-changed ("subordinated") extremal process, and where 
+$\tilde b(c)$ is a regularly varying norming function which is
+_inverse_ to $b(c)$, in the sense that 
+$b(\tilde b(c)) \sim c \sim \tilde b(b(c))$.
+
+Without loss of generality, we choose $\ell^*$ such that $F(\ell^*) = 1/e$, 
+and let $\ell = a(\tilde b(c)) \ell^* + d(\tilde b(c))$. 
+We may then calculate 
+$$
+\mathbf P\left[ \frac{T(\ell)}{b(1/p)} > t \right]
+= \mathbf P[T(\ell) > b(1/p) t]
+= \mathbf P[M(ct) \le \ell]
+= \ldots
+$$
+where we have substituted $c = b(1/p)$, 
+$$
+\ldots
+= \mathbf P\left[ \frac{M(ct) - d(\tilde b(c))}{a(\tilde b(c))} 
+\le \frac{\ell - d(\tilde b(c))}{a(\tilde b(c))} \right]
+\longrightarrow \mathbf P\left[ M(t) \le \ell^* \right]
+= \ldots
+$$
+Defining the hitting time of level $\ell^*$ by $M(t)$ as 
+$$
+\xi_{\ell^*} := \inf\{t: M(t) > \ell^*\}
+$$
+we then have 
+$$
+\ldots = \mathbf P[\xi_{\ell^*} > t] 
+= \mathbf P[(-\log F(\ell^*))^{-1/\beta} X^{1/\beta} D]
+$$
+by [Proposition 4.2, @MeerschaertStoev08]. Using [Theorem 19.1, @Haubold11], 
+we see that $X^{1/\beta} D \sim {\rm ML}(\beta, 1)$, concluding the proof.
+
+# Statistics of the Mittag-Leffler distribution
 

### 2018-04-17 article_springer/article_springer.Rmd
"Statistics of the Mittag-Leffler Distribution"

--- 2018-04-16 article_springer/article_springer.Rmd
@@
 
-output: rticles::springer_article
+output: 
+  rticles::springer_article: 
+    fig_caption: yes
 
@@
 library(CTRM)
+library(MittagLeffleR)
 library(magrittr)
@@
 
-# Scaling limit of Exceedance Times
+# Scaling limit of Exceedance Times {#sec:scaling}
 
@@
 
+#### _Proof of Theorem:_
+We interpret the threshold crossing time $T(\ell)$ as the hitting time of the 
+underlying CTRM (Continuous Time Random Maxima) or "max-renewal process", 
+and then utilize a result by @MeerschaertStoev08. 
+The running maximum process is defined as 
+$$
+M(c) := J_1 \vee \ldots \vee J_{\lfloor c \rfloor},
+$$
+and since we assume that the $J_k$ have a continuous distribution, there exist 
+norming functions $a(c)$ and $d(c)$ such that 
+$$
+\mathbf P\left[ \frac{M(c) - d(c)}{a(c)} \le \ell^* \right] 
+\longrightarrow F(\ell^*), \quad t \to \infty
+$$
+where $F$ is a generalized extreme value distribution, and $\ell^*$ is any 
+value from the support of $F$. 
+The CTRM process is then defined via 
+$$
+V(t) = M(N(t)), \quad t \ge 0
+$$
+where $N(t)$ is the renewal process associated with the waiting times 
+$W_k$: 
+$$
+N(t) = \max\{n: W_1 + \ldots + W_n \le t\}.
+$$
+Now a key observation is that
+$$
+T(\ell) = \inf\{t: V(t) > \ell\}, 
+$$
+and that 
+$$
+T(\ell) > t \quad \text{ if and only if } \quad V(t) \le \ell.
+$$
+By [Theorem 3.1, @MeerschaertStoev08], we have the stochastic process 
+convergence 
+$$
+\frac{V(ct) - d(\tilde b(c))}{a(\tilde b(c))} 
+\stackrel{d}{\longrightarrow} Y(t), \quad t > 0.
+$$
+where $Y(t)$ is a time-changed ("subordinated") extremal process, and where 
+$\tilde b(c)$ is a regularly varying norming function which is
+_inverse_ to $b(c)$, in the sense that 
+$b(\tilde b(c)) \sim c \sim \tilde b(b(c))$.
+
+Without loss of generality, we choose $\ell^*$ such that $F(\ell^*) = 1/e$, 
+and let $\ell = a(\tilde b(c)) \ell^* + d(\tilde b(c))$. 
+We may then calculate 
+$$
+\mathbf P\left[ \frac{T(\ell)}{b(1/p)} > t \right]
+= \mathbf P[T(\ell) > b(1/p) t]
+= \mathbf P[V(ct) \le \ell]
+= \ldots
+$$
+where we have substituted $c = b(1/p)$, 
+$$
+\ldots
+= \mathbf P\left[ \frac{V(ct) - d(\tilde b(c))}{a(\tilde b(c))} 
+\le \frac{\ell - d(\tilde b(c))}{a(\tilde b(c))} \right]
+\longrightarrow \mathbf P\left[ Y(t) \le \ell^* \right]
+= \ldots
+$$
+Defining the hitting time of level $\ell^*$ by $Y(t)$ as 
+$\xi_{\ell^*} := \inf\{t: Y(t) > \ell^*\}$,
+we then have 
+$$
+\ldots = \mathbf P[\xi_{\ell^*} > t] 
+= \mathbf P[(-\log F(\ell^*))^{-1/\beta} X^{1/\beta} D > t]
+$$
+by [Proposition 4.2, @MeerschaertStoev08], where $X$ is an exponential 
+random variable with mean $1$. 
+Using [Theorem 19.1, @Haubold11], we see that 
+$X^{1/\beta} D \sim {\rm ML}(\beta, 1)$, concluding the proof. 
+\qed
+
+# Inference for the Mittag-Leffler distribution
+
+```{r fig:QQ-est, fig.cap="QQ-estimator plots for various datasets.\\label{fig:QQ-est}", fig.height=7, fig.width=7}
+par(mfrow = c(2,2))
+flares_exponent <- flares %>% ctrm() %>% thin(k=500) %>% qqestplot(static=TRUE, main = "QQ-static, flare magnitudes")
+ML_exponent <- MittagLeffleR::rml(500, 0.8) %>% qqestplot(static=TRUE, main = "QQ-static, Mittag-Leffler data")
+ML_exponent2 <- MittagLeffleR::rml(500, 0.8) %>% qqestplot(static=FALSE, top_k = 15, conf.int = TRUE, main = "lala")
+exp_exponent <- rexp(500) %>% qqestplot(static=TRUE, main = "QQ-static, Exponential data")
+```
+
+Since the Mittag-Leffler distribution is heavy-tailed, many researchers 
+would intuitively give the highest importance to the tail behaviour of the 
+distribution, and 
+estimate the exponent of the tail function with established methods such 
+as the Hill estimator. The QQ-estimator [@Kratz96] is closely related to 
+the Hill estimator and fits a 
+least squares line through the logarithms of the ordered statistics 
+(y-axis) and the corresponding quantiles of the exponential distribution 
+(x-axis), and returns the reciprocal slope as the estimate of the tail 
+exponent.
+For instance, the left panel in Figure \ref{fig:QQ-plots} shows the 
+(static) QQ-estimator for the magnitudes of the solar flare data, returning 
+a good fit to a Pareto distribution with tail parameter 
+`r round(flares_exponent, 2)`.
+
+However, as described nicely by @Resnick97, the less 
+similar a heavy-tailed distribution is to a Pareto distribution, the less
+useful a Hill estimator is. 
+The top-right panel of \ref{fig:QQ-plots}, for instance, shows the 
+QQ-estimator plot for $2000$ draws from the Mittag-Leffler distribution with 
+tail parameter $0.8$. The stretched exponential shape means 
+that the Mittag-Leffler distribution has more probability near $0$ than 
+the Pareto distribution, severely biasing the estimator downwards 
+(`r round(ML_exponent, 2)`). Hence a cutoff needs to be introduced, 
+above which the tail exponent is fitted: The dynamic QQ-estimator 
+plots the static QQ-estimates (y-axis) for different cutoffs (x-axis)
+(see bottom-left panel). There is no apparent interval of stability, 
+which could be taken to indicate a reasonable estimate for the true 
+tail exponent $0.8$. 
+Even worse, from a QQ-estimator point of view, there is no striking 
+difference between the infinite mean ${\rm ML}(0.8,1)$ distribution and 
+the light-tailed ${\rm Exp}(1)$ distribution (see bottom-right panel). 
+In particular, if only few 
+(e.g. $<100$) data are available, then the static QQ-estimator plots look 
+virtually interchangeable.
+
+Hence if there is some prior expectation that the data are drawn from the 
+Mittag-Leffler distribution
+(as is the the case for threshold exceedance times),
+then we recommend avoiding QQ-estimators and Hill plots altogether, 
+and instead examining QQ-plots directly 
+(see Figure \ref{fig:QQ-plots}). 
+The scale parameter $\sigma$ is irrelevant for a QQ-Plot. 
+The tail parameter $\beta$ can be estimated quickly via the log-moment 
+method by @Cahoy2013, or via maximum likelihood. 
+Both estimators are implemented in the R package `MittagLeffleR` 
+[@MittagLeffleR].
+
+```{r QQ-plots, fig.cap="QQ Plots for Mittag-Leffler data (left; $\\beta = 0.8$) and threshold crossing times / magnitudes for the solar flare data (middle / right; threshold is set at the 500th order statistic, $\\beta = 0.83$).
+Threshold crossing times appear to fit the Mittag-Leffler distribution well, whereas the Magnitudes appear to fit a Pareto distribution better (\\ref{fig:QQ-est}).
+"}
+par(mfrow = c(1, 3))
+rml(n = 500, tail = 0.8) %>% mlqqplot(tail = 0.8, log = 'xy', main = "Mittag-Leffler data")
+flares_arrivals <- flares %>% ctrm() %>% thin(k = 500) %>% interarrival()
+flares_arrivals_MLparam <- (flares_arrivals %>% mlmle())$par
+mlqqplot(flares_arrivals, 
+         tail = flares_arrivals_MLparam["tail"], 
+         scale = flares_arrivals_MLparam["scale"],
+         log = 'xy', 
+         main = "Threshold crossing times")
+flares %>% ctrm() %>% thin(k = 500) %>% coredata() %>% 
+  mlqqplot(tail = 0.8, log = 'xy', main = "Magnitudes")
+```
+
 # Inference on Exceedance times
 
-Equation \eqref{eq:Tellscale} implies that for large $\ell$ we may 
+The Theorem in the [previous Section](#sec:scaling) implies that for high 
+$\ell$ we may 
 approximate the distribution of $T(\ell)$ with an 

### 2018-04-17 article_springer/article_springer.Rmd
link to MittagLeffleR package on GitHub

@@
                          ref = "724aeb88d005e2f7befc37328633e7cb2bc1cce0")
+# use the newest MittagLeffleR version:
+devtools::install_github("strakaps/MittagLeffleR")
 ```

### 2018-04-17 article_springer/article_springer.Rmd
likelihood ratio test

@@
 difference between the infinite mean ${\rm ML}(0.8,1)$ distribution and 
-the light-tailed ${\rm Exp}(1)$ distribution (see bottom-right panel). 
-In particular, if only few 
-(e.g. $<100$) data are available, then the static QQ-estimator plots look 
-virtually interchangeable.
+the light-tailed ${\rm Exp}(1)$ distribution (compare the right two panels). 
+In particular, if only few (e.g. $<100$) data are available, 
+then the static QQ-estimator plots look interchangeable for the two 
+distributions.
+
+```{r likelihood-ratio-test}
+flares_arrivals <- flares %>% ctrm() %>% thin(k = 500) %>% interarrival()
+mlmle_out <- mlmle(data = flares_arrivals)
+```
 
@@
 [@MittagLeffleR]. 
+Since the exponential distribution is nested in the Mittag-Leffler 
+family of distributions, a standard likelihood ratio test can be 
+performed, with the exponential distribution as a null model against 
+a Mittag-Leffler distribution as the alternative. 
+As an example, the threshold crossing times for the solar flare dataset
+yield a difference in deviance of 
+$\approx$ `r round(2 * (mlmle_out$loglik - mlmle_out$null_loglik))`, 
+which evaluates to a strongly significant $\chi^2_1$ test statistic 
+(p-value = $10^{`r round(log10(mlmle_out$p_value))`}$) for the null
+hypothesis $\beta = 1$.
 
@@
 rml(n = 500, tail = 0.8) %>% mlqqplot(tail = 0.8, log = 'xy', main = "Mittag-Leffler data")
-flares_arrivals <- flares %>% ctrm() %>% thin(k = 500) %>% interarrival()
 flares_arrivals_MLparam <- (flares_arrivals %>% mlmle())$par

### 2018-04-18 article_springer/article_springer.Rmd
diagnostics section

@@
 
-The Theorem in the [previous Section](#sec:scaling) implies that for high 
-$\ell$ we may 
+```{r solar-flare-tail-scale, message=FALSE, fig.height=4.5, fig.width=8, fig.cap="\\label{fig:flares}Stability plots for the tail and scale parameter of the Mittag-Leffler distribution of the Solar Flare dataset.
+Dotted horizontal lines are at $\\beta = 0.85$ and $\\sigma_0 = 3 \\times 10^7$."}
+thin_flares_ctrm <- flares %>% ctrm() %>% thin(k = 700)
+par(mfrow=c(1,2))
+MLestimates(thin_flares_ctrm, tail = 0.9, scale = 3 * 1E7)
+```
+
+The Theorem in Section \ref{sec:scaling} implies that for high 
+threshold $\ell$ we may 
 approximate the distribution of $T(\ell)$ with an 
-${\rm ML}(\beta, b(1/p))$ distribution.
+${\rm ML}(\beta, b(1/p))$ distribution, 
+where $b(\,)$ varies regularly at $\infty$ with parameter $1/\beta$.
 Building on the POT (Peaks Over Threshold) method, we propose the 
@@
 
-1. For varying thresholds $\ell \uparrow x_R$, extract datasets of
-  exceedance times $\{T(\ell, i)\}_i$.
+1. For a range of thresholds $\ell$ near the largest order statistics, 
+  extract datasets of exceedance times $\{T(\ell, i)\}_i$.
 
-2. Fit a Mittag-Leffler distribution to each dataset, which
-  results in the $\ell$-dependent estimates $\{\hat\beta(\ell)\}_\ell$ and 
+2. For each choice of threshold $\ell$, 
+  fit a Mittag-Leffler distribution to the resulting dataset
+  $\{T(\ell, i)\}_i$. 
+  This results in the estimates $\{\hat\beta(\ell)\}_\ell$ and 
   $\{\hat \sigma(\ell)\}_\ell$.
@@
 The above approach, though theoretically sound, benefits from the following
-practical adjustments:
+practical adjustments (compare with Figure \ref{fig:flares}):
 
@@
 \end{align*}
-For quick estimates of the Mittag-Leffler parameters the method of
-log-transformed moments by @Cahoy2013 was used.
+For quick estimates of the Mittag-Leffler parameters we have used 
+the method of log-transformed moments by @Cahoy2013.
 
@@
 
-The CTRM model is based on three main assumptions, which are repeated 
+```{r flare-diagnostics-1, fig.height=7, fig.cap="Diagnostic plots for the solar flare data: auto-correlation function.\\label{fig:flare-diagnostics-1}"}
+flares_ctrm <- flares %>% ctrm() %>% thin(k = 200)
+acf(flares_ctrm)
+```
+
+```{r flare-diagnostics-2, fig.height=7, fig.cap="Diagnostic plots for the solar flare data: empirical copula and QQ Plot. \\label{fig:flare-diagnostics-2}"}
+par(mfrow = c(2,2))
+empcopula(flares_ctrm)
+mlqqplot(flares_ctrm, log = 'xy', tail = 0.8, main = "Mittag-Leffler QQ Plot")
+```
+
+The MRP model is based on three main assumptions, which are repeated 
 below. For each assumption, we suggest one means of checking if it holds:
@@
 I.i.d.:
-: The pairs $(W_i, J_i)$ are i.i.d. An indication if this is true is given 
+: After removing the "noise observations" below the smallest threshold 
+  $\ell_0$, the pair sequence $(T(\ell_0, i), X(\ell_0,i))$ is i.i.d. 
+  An indication if this is true is given 
   by an auto-correlation plot for the logarithms (to ensure finite moments) 
@@
 Uncoupled:
-: Each $W_i$ is independent of each $J_i$. We propose an empirical copula
+: Each $T(\ell, i)$ is independent of each $X(\ell, i)$. We propose an empirical copula
   plot to check for any dependence.
 
-Heavy tails:
-: The waiting times are heavy-tailed with tail parameter 
-  $\beta \in (0,1)$. A Hill plot can confirm this assumption.
+${\rm ML}(\beta, \sigma)$ distribution of $T(\ell, i)$:
+: Apply a cutoff at the lowest threshold $\ell_0$, 
+  extract the threshold crossing times, 
+  and create a QQ Plot for the Mittag-Leffler distribution. 
+  Use a log-Moment estimate of the tail parameter for the theoretical / population 
+  quantiles of the plot.
 
-The motivation behind a CTRM model is to fit extreme observations
-and their inter-arrival times. 
-Observations below a certain threshold may be interpreted as noise and 
-discarded.
-Since the signal rather than the noise needs to satisfy our modelling 
-assumptions, we suggest that the above model assumptions are checked 
-*after* the noisy small observations are discarded.
+Figures \ref{fig:flare-diagnostics-1} and \ref{fig:flare-diagnostics-2} 
+show the diagnostic plots for a 
+minimum threshold chosen at the 200th order statistic. 
+There is some residual autocorrelation for the sequence of threshold 
+exceedance times that is not accounted for by the MRP model. 
+The fit with a Mittag-Leffler distribution ($\beta = 0.8$) is good, and 
+there is no apparent dependence between threshold exceedance times and 
+event magnitudes.
 
@@
 magnitudes (Figure \ref{fig:solar-flare-data}).
-
-```{r solar-flare-tail-scale, message=FALSE, fig.cap="\\label{fig:flares}Stability plots for the tail and scale parameter of the Mittag-Leffler distribution of the Solar Flare dataset."}
-thin_flares_ctrm <- thin(ctrm = flares_ctrm, k = 150)
-par(mfrow=c(1,2))
-MLestimates(thin_flares_ctrm, tail = tail, scale = 2.5 * 1E7)
-```
 

### 2018-04-18 article_springer/article_springer.Rmd
created a bunch of time prediction plots

@@
 exceedance times that is not accounted for by the MRP model. 
-The fit with a Mittag-Leffler distribution ($\beta = 0.8$) is good, and 
-there is no apparent dependence between threshold exceedance times and 
-event magnitudes.
+The fit with a Mittag-Leffler distribution ($\beta = 0.8$) is good, 
+though there are signs that the power-law tail tapers off for very large 
+inter-threshold crossing times. 
+There is no apparent dependence between threshold exceedance times and 
+event magnitudes seen in the copula plot.
+
+# Predicting the time of the next threshold crossing
+
+According to Figure \ref{fig:flares}, for a threshold $\ell$ at the $k$-th order 
+statistic, the fitted threshold exceedance time distribution is 
+$$
+T_\ell \sim {\rm ML}(\beta, k^{1/\beta} \sigma_0), 
+$$
+where $\beta = 0.85$ and $\sigma_0 = 3.0 \times 10^7 {\rm sec}$. 
+Unlike the exponential distribution, the Mittag-Leffler distribution is not 
+memoryless, and the probability density of the time $t$ until the next threshold 
+crossing will depend on the time $t_0$ elapsed since the last threshold crossing.
+This density equals 
+$$
+p(t|\beta, \sigma_0, \ell, t_0) = \frac{f(t + t_0 | \beta, k^{1/\beta} \sigma_0)}{\mathbf P[T_\ell > t_0]}
+$$
+where $f(\,\cdot\, | \beta, k^{1/\beta} \sigma_0)$ is the probability density of 
+${\rm ML}(\beta, k^{1/\beta} \sigma_0)$.
+
+Conditional on the last threshold being
+
+```{r, fig.height=7}
+tail <- 0.7
+scale <- 1
+t_0 <- c(0, 1, 10)
+from <- 0.1
+to <- 100 * scale
+xx <- exp(seq(from = log(from), to = log(to), length.out = 100))
+par(mfrow = c(2,2))
+plot(xx, rep(1, length(xx)), ylim = c(0.001,1), type = 'n', log = 'xy', 
+     xlab = 't', ylab = 'p')
+for (k in 1:length(t_0)) {
+  cond <- pml(q = t_0[k], tail = tail, scale = scale, lower.tail = FALSE)
+  yy <- dml(x = xx + t_0[k], tail = tail, scale = scale) / cond
+  lines(xx,yy, col = k+1, lty = k)
+}
+legend("topright", c("t_0 = 0", "t_0 = 1", "t_0 = 10"), col = 2:4, lty = 1:3)
+
+plot(xx, rep(1, length(xx)), ylim = c(0.001,1), type = 'n', log = 'xy', 
+     xlab = 't', ylab = 'p')
+betas <- c(0.8, 0.95, 0.99)
+t_0 <- 1
+for (k in 1:length(betas)) {
+  cond <- pml(q = t_0, tail = betas[k], scale = scale, lower.tail = FALSE)
+  yy <- dml(x = xx + t_0, tail = betas[k], scale = scale) / cond
+  lines(xx, yy, col = k+1, lty = k)
+}
+legend("topright", c("beta = 0.8", "beta = 0.95", "beta = 0.99"), col = 2:4, lty = 1:3)
+```
+
+```{r}
+betas <- c(0.7, 0.8, 0.95, 0.99)
+t_0 <- 1
+plot(xx, rep(1, length(xx)), ylim = c(0.001,1), type = 'n', log = 'xy', 
+     xlab = 't', ylab = 'p')
+for (k in 1:length(betas)) {
+  yy <- dml(x = xx, tail = betas[k], scale = scale) / pml(
+    q = xx,
+    tail = betas[k],
+    scale = scale,
+    lower.tail = FALSE
+  )
+  lines(xx,yy, col = k+1, lty = k)
+}
+legend("topright", c("beta = 0.8", "beta = 0.95", "beta = 0.99"), col = 2:5, lty = 1:4)
+
+```
 

### 2018-04-18 article_springer/article_springer.Rmd
pick 2 of the three plots

--- 2018-04-18 article_springer/article_springer.Rmd
@@
 exceedance times that is not accounted for by the MRP model. 
-The fit with a Mittag-Leffler distribution ($\beta = 0.8$) is good, and 
-there is no apparent dependence between threshold exceedance times and 
-event magnitudes.
+The fit with a Mittag-Leffler distribution ($\beta = 0.8$) is good, 
+though there are signs that the power-law tail tapers off for very large 
+inter-threshold crossing times. 
+There is no apparent dependence between threshold exceedance times and 
+event magnitudes seen in the copula plot.
+
+# Predicting the time of the next threshold crossing
+
+According to Figure \ref{fig:flares}, for a threshold $\ell$ at the $k$-th order 
+statistic, the fitted threshold exceedance time distribution is 
+$$
+T_\ell \sim {\rm ML}(\beta, k^{1/\beta} \sigma_0), 
+$$
+where $\beta = 0.85$ and $\sigma_0 = 3.0 \times 10^7 {\rm sec}$. 
+Unlike the exponential distribution, the Mittag-Leffler distribution is not 
+memoryless, and the probability density of the time $t$ until the next threshold 
+crossing will depend on the time $t_0$ elapsed since the last threshold crossing.
+This density equals 
+$$
+p(t|\beta, \sigma_0, \ell, t_0) = \frac{f(t + t_0 | \beta, k^{1/\beta} \sigma_0)}{\mathbf P[T_\ell > t_0]}
+$$
+where $f(\,\cdot\, | \beta, k^{1/\beta} \sigma_0)$ is the probability density of 
+${\rm ML}(\beta, k^{1/\beta} \sigma_0)$. 
+The more time has passed without a threshold crossing, the more the probability 
+distribution shifts towards larger values for the next crossing
+(see Figure \ref{fig:hazard}, left panel). 
+The hazard rate 
+$$
+h(t) = \frac{f(t| \beta, k^{1/\beta} \sigma_0))}{\int_t^\infty f(\tau| \beta, k^{1/\beta} \sigma_0))\,d\tau}
+$$
+represents the risk of a threshold crossing per unit time, and is a 
+decreasing function for the Mittag-Leffler distribution. 
+The closer $\beta$ is to $1$, the more the hazard rate mimics that of an 
+exponential distribution (a constant function, see Figure \ref{fig:hazard}, 
+right panel).
+
+Conditional on the last threshold being
+
+```{r hazard, fig.height=7, fig.cap="Left: Conditional distribution of time until next threshold crossing, depending on elapsed time since last crossing ($\\beta = 0.8$, $\\sigma_0 = 1$).
+Right: Hazard rate depending on tail parameter $\\beta$.\\label{fig:hazard}"}
+tail <- 0.7
+scale <- 1
+t_0 <- c(0, 1, 10)
+from <- 0.1
+to <- 100 * scale
+xx <- exp(seq(from = log(from), to = log(to), length.out = 100))
+par(mfrow = c(2,2))
+plot(xx, rep(1, length(xx)), ylim = c(0.001,1), type = 'n', log = 'xy', 
+     xlab = 't', ylab = 'p')
+for (k in 1:length(t_0)) {
+  cond <- pml(q = t_0[k], tail = tail, scale = scale, lower.tail = FALSE)
+  yy <- dml(x = xx + t_0[k], tail = tail, scale = scale) / cond
+  lines(xx,yy, col = k+1, lty = k)
+}
+legend("bottomleft", c("t_0 = 0", "t_0 = 1", "t_0 = 10"), col = 2:4, lty = 1:3)
+
+betas <- c(0.7, 0.8, 0.95, 0.99)
+t_0 <- 1
+plot(xx, rep(1, length(xx)), ylim = c(0.001,2), type = 'n', log = 'xy', 
+     xlab = 't', ylab = 'h')
+for (k in 1:length(betas)) {
+  yy <- dml(x = xx, tail = betas[k], scale = scale) / pml(
+    q = xx,
+    tail = betas[k],
+    scale = scale,
+    lower.tail = FALSE
+  )
+  lines(xx,yy, col = k+1, lty = k)
+}
+legend("bottomleft", c("beta = 0.7", "beta = 0.8", "beta = 0.95", "beta = 0.99"), col = 2:5, lty = 1:4)
+
+```
 

### 2018-04-18 article_springer/article_springer.Rmd
add threshold selection literature

@@
 
-Conditional on the last threshold being
-
-```{r hazard, fig.height=7, fig.cap="Left: Conditional distribution of time until next threshold crossing, depending on elapsed time since last crossing ($\\beta = 0.8$, $\\sigma_0 = 1$).
+```{r hazard, fig.height=7, fig.cap="Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\\beta = 0.8$, $\\sigma_0 = 1$).
 Right: Hazard rate depending on tail parameter $\\beta$.\\label{fig:hazard}"}
@@
 ```
+
+It is beyond the scope of the current paper to incorporate parameter 
+uncertainty into our predictive distribution for the next threshold crossing; 
+however, methods as described by @Scarrott12 and @Lee15 are likely 
+to extend to our setting.
 

### 2018-04-18 article_springer/article_springer.Rmd
write conclusion & appendix

@@
   Poisson Process" which generalizes the standard Poisson Process.
-  We model threshold crossing times and threshold exceedances jointly, and
-  provide graphical means of estimating model parameters and assessing 
-  model fit. Finally, we study two real-world, bursty time series, and 
-  show how to extract parameter estimates as well as estimates for the time 
-  of the next threshold crossing.
+  We provide graphical means of estimating model parameters and assessing 
+  model fit. Along the way, we apply our inference method to a real-world
+  bursty time series, and 
+  show how the Mittag-Leffler distribution has a memory which affects 
+  the predictive distribution of the next extreme event.
 
@@
 We review the marked renewal process in Section 2, and 
-derive a scaling limit theorem for inter-exceedance times in Sections 3 &
-4. 
-A statistical procedure to estimate model parameters via stability plots 
-is outlined in Section 5, and diagnostic plots for model criticism are 
-discussed in Section 6. 
-In Section 7, we give case studies for simulated data as well as for a
-real-world dataset, with a discussion in Section 8. 
+derive a scaling limit theorem for inter-exceedance times in Section 3.
+We give a statistical procedure to estimate model parameters via stability plots 
+in Section 5, but to set the stage we first discuss inference for the 
+Mittag-Leffler distribution in Section 4. 
+Diagnostic plots for model criticism are discussed in Section 6. 
+In Section 7, we discuss the non-memorylessness property of the 
+Mittag-Leffler distribution, and how it affects the predictive distribution 
+for the next threshold crossing event. 
+Section 8 concludes.
 All statistical computations have been done in R, and all code, data, as 
@@
 more precisely,
-$$
+\begin{align} \label{eq:stability}
 \frac{W_1 + \ldots + W_n}{b(n)} \overset{d}{\longrightarrow} D, 
 \quad n \to \infty
-$$
+\end{align}
 for a function $b(n)$ which is regularly varying at $\infty$ with 
@@
 
+**Remark:**
+: If $\beta = 1$, the result of the Theorem above is standard, see e.g. 
+Equation (2.2) in @Gut1999.
+
 # Inference for the Mittag-Leffler distribution
@@
 ```{r solar-flare-tail-scale, message=FALSE, fig.height=4.5, fig.width=8, fig.cap="\\label{fig:flares}Stability plots for the tail and scale parameter of the Mittag-Leffler distribution of the Solar Flare dataset.
-Dotted horizontal lines are at $\\beta = 0.85$ and $\\sigma_0 = 3 \\times 10^7$."}
+Dotted horizontal lines are at $\\beta = 0.85$ and $\\sigma_0 = 3 \\times 10^7$ seconds $\\approx 0.95$ years."}
 thin_flares_ctrm <- flares %>% ctrm() %>% thin(k = 700)
@@
 
-# Application to data
+# Discussion & Conclusion
 
-## Simulated Data
+We have extended the POT (Peaks over Threshold) model, a mainstay of 
+extreme value theory, to "bursty" time series, which have been studied 
+intensively in statistical physics. 
+Burstiness is characterized by power-law waiting times between events, 
+and we have shown that the Mittag-Leffler distribution arises naturally 
+as a scaling limit for the inter-exceedance times of high thresholds. 
+Moreover, we have derived the following non-linear scaling behaviour: 
+$\sigma \sim p^{-1/\beta}$, 
+where $\sigma$ is the scale parameter of the distribution of threshold 
+exceedance times, 
+$p$ is the fraction of magnitudes above the threshold, 
+and $\beta$ the exponent of the power law.
 
-To test our inference method, we have simulated `r params$n` 
+The "anomalous" scaling behaviour in the bursty setting entails two 
+phenomena: 
+i) a heavy tail of the interarrival time distribution of 
+threshold crossings (long rests), and 
+ii) a high propensity for more threshold crossing events immediately after 
+each threshold crossing event (bursts). 
+The Mittag-Leffler distribution captures both phenomena, due to its heavy
+tail as well as its streteched exponential (peaked) asymptotics for small 
+times. 
+It generalizes the exponential distribution, and 
+in the solar flare data example, this generalization 
+is warranted, because the likelihood-ratio test is strongly significant.
+
+When we introduced the MRP model, we assumed that all events are i.i.d. 
+This assumption is likely sufficient but not necessary for our limit theorem to hold. 
+Morevoer, any data below a (minimum) threshold $\ell_0$ is discarded in 
+our inference procedure, and hence need not satisfy the i.i.d. assumption.
+For the purposes of statistical inference, we merely require that the 
+inter-threshold-crossing times are i.i.d.
+
+For some bursty time series, the current MRP model may be too rigid, 
+because often the heavy-tailed character of the inter-arrival time
+distribution does not hold at all time scales; rather, it often applies at 
+short and intermediate time scales, and is truncated or tempered 
+(reverting to an exponential distribution) at 
+very long time scales, see e.g. @MeerschaertRoyQin and @Aban06. 
+In such situations, a "tempered" Mittag-Leffler distribution may provide 
+a more realistic fit, which we aim to introduce in follow-up work.
+
+## Acknowledgements {-}
+
+The authors would like to thank Prof. Peter Scheffler for insights on 
+stochastic process limits for CTRMs, and Gurtek Gill who helped create
+the MittagLeffleR R-package.
+
+\appendix
+
+# Validating our inference method on simulated data
+
+To test our inference method via stability plots, we have simulated `r params$n` 
 independent
-waiting time and magnitude pairs $(W_k, J_k)$. In order to have exact 
+waiting time and magnitude pairs $(W_k, J_k)$ (see upper panel in 
+Figure \ref{fig:thresholdedBursty}). In order to have exact 
 analytical values available for $\beta$ and $\sigma_0$, a distribution for 
-$W_k$ needs to be chosen for which $b(n)$ from \eqref{eq:Wscale} is known. 
-If we choose $W_k \stackrel{d}{=} D$, where $D$ is as in \eqref{theD}, 
+$W_k$ needs to be chosen for which $b(n)$ from \eqref{eq:stability} is known. 
+If we choose $W_k \stackrel{d}{=} D$, where $D$ is as in \eqref{eq:stability}, 
 then due to the stability property we have the *equality* of distribution
@@
 
-By \eqref{eq:Tellscale}, the distribution 
+By the Theorem, the distribution 
 of $T(\ell)$ is approximately 
-${\rm ML}(\beta, p^{-1/\beta}) 
-= {\rm ML}(\beta, k^{-1/\beta} n^{1/\beta})$, which means 
+$$
+{\rm ML}(\beta, p^{-1/\beta}) 
+= {\rm ML}(\beta, k^{-1/\beta} n^{1/\beta}),
+$$
+which means 
 $\sigma_0 = n^{1/\beta}$.
@@
 Figure \ref{fig:sim} displays plots of $\hat \beta(\ell)$ and 
-$\hat \sigma(\ell)$ vs. $k$, the number of exceedances as $\ell$ traverses 
-the largest observations $J_i$. 
+$\hat \sigma(\ell)$ vs. $k$; recall that $k$ is the index of the order
+statistics of $J_k$ at which the threshold $\ell$ is placed. 
 Dotted lines show 95% confidence intervals, which are derived from the 
@@
 The dashed lines show the actual values of $\beta$ resp.\ $\sigma_0$, 
-showing that our inference method effectively identifies the 
-right parameters.
+showing that our inference method identifies the 
+parameters correctly.
 
-## Bitcoin trading volumes
-
-```{r bitcoin-data, fig.cap="\\label{fig:bitcoin-data}Time Series of 'Bitcoin days destroyed', a measure for the traded volume of bitcoins."}
-bitcoin_ctrm <- ctrm(bitcoin)
-plot(bitcoin_ctrm, p = 0.02)
-```
-
-We study the daily trade volumes of Bitcoin since 2009, provided by 
-Blockchain and downloaded from Data 
-Market\footnote{\url{https://datamarket.com/data/list/?q=provider:blockchain}}. 
-Although the observations are regular (daily), extremes in the trade volumes
-occur in bursts, which can be seen over timescales of months and years 
-(Figure \ref{fig:bitcoin-data}).
-
-```{r bitcoin-data-tail-scale, message=FALSE, fig.cap="\\label{fig:bitcoin-tail-scale}Tail and scale plot of the bitcoin data."}
-thin_bitcoin_ctrm <- thin(ctrm = bitcoin_ctrm, k = 250)
-par(mfrow=c(1,2))
-MLestimates(thin_bitcoin_ctrm, tail = 0.9, scale = 2 * 1E3)
-```
-
-Figure \ref{fig:bitcoin-tail-scale} shows plots identifying the candidates
-$\beta = 0.9$ and $\sigma_0 = 2000$ for 
-the tail and scale parameters of the exceedance time distribution. 
-That is, exceedances of a threshold $\ell$ at the $k$-th largest observed 
-magnitude are distributed as 
-$$T(\ell) = \text{ML}(0.9, 2000 * k^{-1/0.9}).$$ 
-A QQ plot (Figure \ref{fig:bitcoin-diag}) of the exceedance times at the 
-level of the 200th 
-largest event lends credence to a heavy-tailed distribution with tail
-parameter near the value $1$.
-
-## Solar Flare Data
-
-```{r solar-flare-data, fig.cap="\\label{fig:solar-flare-data}The solar flare time series data."}
-flares_ctrm <- ctrm(flares)
-plot(flares_ctrm, p = 0.01)
-```
-
-The "complete Hard X Ray Burst Spectrometer event list" 
-\footnote{\url{https://umbra.nascom.nasa.gov/smm/hxrbs.html}} 
-@HXRBS is a 
-comprehensive reference for all measurements of the Hard X 
-Ray Burst Spectrometer on NASA's Solar Maximum Mission from the time of 
-launch on Feb 14, 1980 to the end of the mission in Dec 1989. 12,776 
-events were detected, with the "vast 
-majority being solar flares". The list includes the start time, peak time, 
-duration, and peak rate of each event. We have used "start time" as the 
-variable for event times, and "peak rate" as the variable for event 
-magnitudes (Figure \ref{fig:solar-flare-data}).
-
-Figure \ref{fig:flares} shows the fitted tail and scale parameters 
-of the Mittag-Leffler distribution. The dotted line for the tail 
-parameter is at $\beta = 0.85$, yielding the plot of (transformed) scale 
-estimates $\hat \sigma_0 = k^{1/0.85} \hat \sigma(\ell)$. 
-We suggest the estimate $\sigma_0 = 2.5 \times 10^7$ seconds 
-$\approx 289$ days. 
-The exceedance times of a threshold $\ell$ as high as the $k$-measurement 
-are hence Mittag-Leffler distributed as
-$$ T(\ell) \sim {\rm ML}(0.85, 289  k^{-1/0.85} \text{ days}).$$
-
-# Discussion
-
-Comparing plots of the simulated data in Figure \ref{fig:thresholdedBursty}
-with plots of the 
-empirical data \ref{fig:bitcoin-data} and \ref{fig:solar-flare-data}, 
-it can be seen that the empirical data show long time intervals without 
-*any* event occurring, whereas for real-world data events appear to happen 
-continuously. 
-This seeming discrepancy vanishes, however, when all but the $k_\text{max}$
-largest observations are discarded. 
-We repeat that the CTRM model focuses on extreme events and interprets 
-smaller events as noise.
-
-The CTRM model, moreover, assumes a "pure" power-law for the event 
-inter-arrival times. 
-Real datasets, however, are often exponentially 
-tapered or truncated, see e.g. the discussion of tempered power-law 
-distributions by @MeerschaertRoyQin and the truncated Pareto distribution 
-by @Aban06. 
-This means that the fit to a power-law
-distribution may seem adequate for medium-size time scales, 
-but that at very large time-scales the power-law character of the 
-distribution can weaken or disappear.
-This behaviour seems to appear in both the Bitcoin data and the Solar-Flare
-data: the Hill plot for the tail parameter is increasing towards lighter
-tails as the threshold reaches very high values. 
-This may mean that the CTRM model may overestimate the heaviness of the
-tail of the waiting time distribution; or that a CTRM base on a *tempered* 
-power-law renewal process might be a more realistic model.
-
-# Conclusion
-
-We have proposed the CTRM model for the extremes of "bursty" events. 
-Burstiness is a phenomenon of intermittency which has received a lot of 
-attention in the recent statistical physics literature. 
-The CTRM model is a straightforward generalization of the POT (Peaks over 
-Threshold) model, for which the inter-arrival times between threshold 
-crossings are exponentially distributed. 
-If the Mittag-Leffler tail parameter of the CTRM equals $1$, then the 
-CTRM model reproduces this behaviour exactly, showing that the CTRM model 
-nests the POT model.
-
-The scale parameter $\sigma$ of the inter-event distribution follows a 
-power-law $\sigma \propto p^{-1/\beta}$, where $\beta \in (0,1)$ is the 
-tail parameter of the inter-event distribution and $p$ the probability 
-that an event crosses a given threshold. 
-From this power law, we have constructed "stability plots", from which 
-estimates of $\beta$ and $\sigma$ can be read off.
-
-We have demonstrated the applicability of the CTRM model with two 
-real-world datasets. 
-Although the CTRM model possibly overestimates the heaviness of the tail 
-of the inter-arrival distribution, it clearly captures that 
-the inter-arrival times of threshold crossings scale non-linearly with 
-the treshold crossing probability, and follow a clearly non-Poissonian 
-behaviour. 
-Thus we have shown that the CTRM model is a useful tool for the modelling 
-of extremes of bursty events, which requires very little computation and 
-which allows for straightforward ways of checking and criticizing model 
-assumptions. 
-The analyses from this paper are readily reproduced via the R package 
-`CTRM`, available at \url{https://github.com/strakaps/CTRM}.
-
-## Acknowledgements
-
-The authors would like to thank Peter Scheffler for insights on 
-stochastic process limits for CTRMs, and Gurtek Gill who helped create
-the MittagLeffleR R-package.
-
-\appendix
-
-For our inference on the CTRM model, we extract realizations of 
-$X(\ell)$ and $T(\ell)$ from time series data by considering thresholds 
-$\ell$ ranging over some interval $[\ell_0, x_R)$. 
-(A reasonable default value for $\ell_0$ is the $95$-th
-percentile of $J$.)
-Write $X(\ell,i)$ for the $i$-th exceedance of level $\ell$, 
-and $T(\ell,i)$ for the inter-arrival time between
-$X(\ell,i-1)$ and $X(\ell,i)$. 
-Thus for any threshold $\ell \in [\ell_0, x_R)$,
-we construct sequences $\{T(\ell,i)\}_{i}$ and 
-$\{X(\ell,i)\}_{i}$. 
-These sequences are i.i.d. because a renewal occurs at each threshold
-crossing time, and independent because $W_k$ and $J_k$ are uncoupled.
-Extracting the exceedances $X(\ell)$ for inference is a standard procedure
-known as the Peaks Over Threshold (POT) approach in extreme value theory
-[@beirlantBook].
-Figure \ref{fig:thresholdedBursty} illustrates the exceedances 
-$X(\ell, i)$ in red and the times until exceedance $T(\ell, i)$ as the 
-preceding intervals marked by blue crosses.
-
-A standard result from extreme value theory provides the asymptotic 
-distribution of $X(\ell)$ as $\ell \uparrow x_R$. For later use, we also 
-include the scaling limit of the cumulative maximum $M(n)$.
-
-**Theorem GEV** (e.g. Chapter 2 & Section 5.3, @beirlantBook):
-
-: Suppose the distribution of $J_k$ is continuous. Then there
-exist non-decreasing norming functions $a(c)$ and $d(c)$ such that
-as $c \to \infty$, the running maximum\footnote{We extend $M(n)$ 
-continuously to $[0, +\infty)$ via $M(c) := M(\lfloor c \rfloor)$ where 
-$\lfloor c \rfloor$ is the 
-greatest integer not greater than $c$.} 
-$M(c)$ converges weakly 
-to a *Generalized Extreme Value Distribution* with shape
-parameter
-$\xi$:
-\begin{align}
-[M(c) - d(c)] / a(c) \stackrel{d}{\to} A, 
-\quad
-\mathbf P(A \le z) = G(z | \xi) = \exp\left(-[1+\xi z]^{-1/\xi}\right),\label{eq:GEV}
-\end{align}
-defined for all $z$ such that $1 + \xi z > 0$. 
-This definition extends continuously to $\xi = 0$ via 
-$$G(z | 0) = \exp(-\exp(-x)).$$
-For $\mu$ and $\sigma > 0$, we write ${\rm GEV}(\xi, \mu, \sigma)$ for the 
-probability distribution of the random variable $\sigma A + \mu$.
-
-    Moreover, asymptotically as $\ell \uparrow x_R$,
-$$\mathbf P(J - \ell > y | J > \ell) 
-\sim 1 - H(y),$$
-where 
-$$H(y) = \begin{cases}
-1 - (1+ \xi y / \tilde \sigma)^{-1/\xi}, & y \in (0,\infty) \text{ if } \xi > 0,\\
-1 - \exp(-y/\tilde \sigma), & y \in (0,\infty) \text{ if } \xi = 0,\\
-1 - (1+ \xi y / \tilde \sigma)^{-1/\xi}, & y \in (0, -\sigma / \xi) \text{ if } \xi < 0
-\end{cases}$$
-
-    and where $\tilde \sigma := \sigma + \xi(\ell-\mu)$.
-The CDF $H(y)$ is said to belong to the *Generalised Pareto family*
-$GP(\xi,\bar \sigma)$.
-
-# CTRM Scaling limits
-
-## Waiting times
-
-We will assume that the waiting times $W_k$ have infinite mean,
-i.e. a tail parameter $\beta \in (0,1)$ and regularly varying tail probabilities:
-$\mathbf P(W > t) \sim L(t) t^{-\beta}$ as $t \uparrow \infty$ for
-some slowly varying function $L(t)$. As usually, $f(t) \sim g(t)$
-means that the quotient of $f(t)$ and $g(t)$ converges to $1$. The
-law of the $W$ then lies in the domain of attraction of a stable law,
-in the sense that the distributional limit 
-\begin{align} \label{eq:Wscale}
-\frac{W_1 + \ldots + W_n}{b(n)} \overset{d}{\longrightarrow} D, 
-\quad n \to \infty
-\end{align}
-exists, for a regularly varying scaling function
-\begin{equation} \label{eq:bScale}
-b \in {\rm RV}_\infty(1/\beta)
-\end{equation}
-[See e.g. Section 2.9.2 in @beirlantBook for a short introduction to 
-regular variation]. 
-The limit is then a positively skewed stable distribution, 
-whose scale parameter is $1$ if $b(n)$ is chosen accordingly
-[see e.g. Section 3.7 in @MeerschaertSikorskii]. 
-This distribution is most concisely defined via its Laplace transform
-\begin{align} \label{theD}
-\mathbf E[\exp(-sD)] = \exp(-s^\beta).
-\end{align}
-Moreover, the following functional limit theorem holds 
-[see e.g. Remark 4.17 in @MeerschaertSikorskii]: 
-\[
-(W_1 + \ldots + W_{\lfloor ct \rfloor})/b(c) \overset{d}{\longrightarrow} D(t), \quad c \to \infty
-\] 
-with convergence in the Skorokhod $J_1$ topology. The limit
-$D(t)$ is a stable subordinator, i.e. an increasing Levy process with
-Laplace transform $\exp(-t s^\beta)$.
-
-It is well known [see e.g. @limitCTRW] that the renewal
-process then satisfies the functional limit
-$$
-N(ct)/ \tilde b(c) \stackrel{d}{\to} E(t) = \inf\{r: D(r) > t\}, 
-\quad c \to \infty
-$$
-for a scaling function $\tilde b(c) \in {\rm RV}_\infty(\beta)$ which is asymptotically inverse to $b(c)$, in the sense of @seneta (p.20): 
-$$
-b(\tilde b(c)) \sim c \sim \tilde b(b(c)).
-$$
-[also see Prop 4.15 in @MeerschaertSikorskii]. 
-The limit process $E(t)$ is called the _inverse stable subordinator_ [@invSubord].
-
-## Magnitudes and Extreme Value Distributions
-
-The extremal limit theorem then allows for an extension to functional 
-(i.e. pathwise) limits: assume that the norming sequences $a(c)$ and 
-$d(c)$ are as in Theorem GEV. Then 
-$$
-[M(ct) - d(c)] / a(c) \stackrel{d}{\to} A(t),
-\quad c \to \infty.
-$$
-Here convergence holds weakly in Skorokhod's $J_1$ topology, and the limit
-process $A(t)$ is an _extremal process_, with
-finite-dimensional distributions given by
-\begin{align}
-\label{eq:fin-dim-A}
-\mathbf P(A(t_i)\leq x_i,1\leq i \leq d) 
-= F_A(\wedge_{i=1}^d x_i)^{t_1} 
-F_A(\wedge_{i=2}^d x_i)^{t_2-t_1}
-\ldots F_A(x_d)^{t_d-t_{d-1}},
-\end{align}
-where $F_A(x)$ is a GEV distribution [see e.g. @resnick2013extreme].
-
-## CTRM limit
-
-The CTRM $V(t)$ results from the running maximum $M(n)$ via a time change by the renewal process $n = N(t)$. This is also reflected in its corresponding limit process:
-
-**Theorem MS1** [@MeerschaertStoev08]:
-
-: The CTRM process $V(t) = M(N(t))$ satisfies the following functional scaling limit in the Skorokhod $J_1$ topology: 
-$$
-[V(ct) - d(\tilde b(c))] / a(\tilde b(c)) \stackrel{d}{\to} 
-A(E(t)), \quad c \to \infty.
-$$
-
-The distribution of the _hitting time_ of a level $\ell^*$ by the limit 
-process $A(E(t))$ is also known, and we give it below for the convenience 
-of the reader:
-
-**Theorem MS2** [@MeerschaertStoev08]:
-
-: Let $F_A$ be the CDF of a GEV distribution, and let $A(t)$ be the
-extremal process corresponding to $F_A$ via \eqref{eq:fin-dim-A}. 
-For a given threshold $\ell^*$ in the support of $F_A$,
-the hitting time
-$$
-B(\ell^*) = \inf\{t: A(E(t)) > \ell^*\} 
-$$
-is equal in distribution to $(-\log F_A(\ell^*))^{-1/\beta} X^{1/\beta} D$,
-where $X \sim {\rm Exp}(1)$ and $D$ (defined in \eqref{theD}) are 
-independent.
-
-*Proof:*
-Let the scaling functions $a(c)$ and $d(c)$ be as in Section 
-\ref{magnitudes-and-extreme-value-distributions}, and assume WLOG 
-$\ell = a(n) \ell^* + d(n)$ for some arbitrary but fixed $\ell^*$, out of the support of $A$. 
-We first note that due to \eqref{eq:GEV}
-\begin{equation} 
-F_J (a(c) \ell^* + d(c))^c \stackrel{d}{\to} F_A(\ell^*), \text{ as } c \to \infty.
-\end{equation}
-\noindent Taking the logarithm on each side and using the relationship  $z-1 \sim \log(z)$ as $z \to 1$, we get
-\begin{equation}
-c (1-F_J(a(c) \ell^*+d(c))) \stackrel{d}{\to} - \log F_A(\ell^*).
-\end{equation}
-\noindent Hence we have 
-\begin{equation}
-c \cdot p \stackrel{d}{\to} - \log F_A(\ell^*) \label{eq:np_conv}
-\end{equation}
-\noindent as $\ell \uparrow x_R$.
-Now we get
-
-**Remark:**
-
-: By the above theorem, the inter-exceedance times are i.i.d. and
-approximately Mittag-Leffler distributed, which means that the exceedance
-times form a *fractional Poisson process* [@Laskin2003]. 
-Since the Mittag-Leffler distribution nests the exponential distribution 
-(the special case where $\beta = 1$), the fractional Poisson process 
-generalizes the standard Poisson process. 
-As the threshold height increases, the threshold crossing events are 
-effectively "thinned out", and the thinned (or rarefied) processes retain
-the characteristics of a fractional Poisson process [@Gorenflo2010], 
-with a growing scale parameter $b(1/p)$.
-
-**Remark:**
-
-: A fractional Poisson process can be represented as a
-standard Poisson process $N(t)$, time-changed by an inverse stable 
-subordinator $E(t)$ [@Meerschaert2010b]. 
-This pattern can be made sense of in our context: 
-The exceedance times for a standard extreme value process $A(t)$ form a 
-standard Poisson process $N(t)$. Accordingly, the exceedance times 
-of the CTRM limit $A(E(t))$ must be $N(E(t))$, a fractional Poisson 
-process.
-
-\newpage
+# References {-}

### 2018-04-19 article_springer/article_springer.Rmd
get packages in preamble

@@
 
-```{r get-rticles, eval=FALSE, include=FALSE}
+```{r get-rticles, eval=FALSE, include=FALSE, cache=TRUE}
 # use this rticles version: 
@@
 devtools::install_github("strakaps/MittagLeffleR")
+library(MittagLeffleR)
+devtools::install_github("UNSW-MATH/CTRM")
+library(CTRM)
 ```

### 2018-04-20 article_springer/article_springer.Rmd

@@
 The scale parameter of the Mittag-Leffler inter-arrival times of 
-threshold crossing times increases, increases, but _superlinearly_; 
+threshold crossing times increases, but _superlinearly_; 
 see the Theorem below.
@@
 = \mathbf P[V(ct) \le \ell]
-= \ldots
 $$
-where we have substituted $c = b(1/p)$, 
+where we have substituted $c = b(1/p)$. Moreover 
 $$
-\ldots
+\mathbf P[V(ct) \le \ell]
 = \mathbf P\left[ \frac{V(ct) - d(\tilde b(c))}{a(\tilde b(c))} 
@@
 \longrightarrow \mathbf P\left[ Y(t) \le \ell^* \right]
-= \ldots
 $$
@@
 $$
-\ldots = \mathbf P[\xi_{\ell^*} > t] 
+P\left[ Y(t) \le \ell^* \right] = \mathbf P[\xi_{\ell^*} > t] 
 = \mathbf P[(-\log F(\ell^*))^{-1/\beta} X^{1/\beta} D > t]
@@
 
-I.i.d.:
+i.i.d.:
 : After removing the "noise observations" below the smallest threshold 
@@
 The Mittag-Leffler distribution captures both phenomena, due to its heavy
-tail as well as its streteched exponential (peaked) asymptotics for small 
+tail as well as its stretched exponential (peaked) asymptotics for small 
 times. 

### 2018-04-20 article_springer/article_springer.Rmd
minor changes

--- 2018-04-19 article_springer/article_springer.Rmd
@@
   This article generalizes the Peaks Over Threshold (POT) model to the setting 
-  where inter-event times are heavy-tailed and i.i.d.. For high thresholds and 
+  where inter-event times are heavy-tailed. For high thresholds and 
   infinite-mean waiting times, we show that the times between threshold 
@@
 Section 8 concludes.
-All statistical computations have been done in R, and all code, data, as 
+For all statistical computations we have used R [@R], and all code, data, as 
 well as the source code for this manuscript has been organized into an R 
-software package, available at <https://github.com/strakaps/CTRM>.
+software package, available at <https://github.com/UNSW-MATH/CTRM>.
 
@@
 
-**Definition:**
+**Definition (MRP):**
 
@@
 
-In this setup, the $k$ magnitude $J_k$ occurs at time
+In this setup, the $k$-th magnitude $J_k$ occurs at time
 $T_k = W_1 + \ldots + W_k$. 
@@
 
-**Definition (MRP):**
+**Definition:**
 
@@
 _without any_ events, whereas in the real-world dataset events appear 
-continuously. The threshold exceedances, however, appear to have the same 
+continuously. The threshold exceedances, however, appear to have similar
 statistical behaviour in both models. Observations below a threshold are 
@@
 
-In this section we state the key theorem below (a proof is in the appendix). 
-For more details on regular variation and stable limit theorems, we 
+In this section we state and prove the key theorem, see below.
+For an accessible introduction to regular variation and stable limit theorems, we 
 recommend the book by @MeerschaertSikorskii.
@@
 
-\noindent In general, for $\sigma > 0$ we write ${\rm ML}(\beta, \sigma)$ for the 
-distribution of $\sigma W_\beta$. 
+\noindent For a scale parameter $\sigma > 0$, we write 
+${\rm ML}(\beta, \sigma)$ for the distribution of $\sigma W_\beta$. 
 The Mittag-Leffler distribution with parameter $\beta \in (0,1]$ is 
@@
 (y-axis) and the corresponding quantiles of the exponential distribution 
-(x-axis), and returns the reciprocal slope as the estimate of the tail 
+(x-axis). The reciprocal slope is returned as the estimate of the tail 
 exponent.
@@
 useful a Hill estimator is. 
-The top-right panel of \ref{fig:QQ-plots}, for instance, shows the 
+The top-right panel of Figure \ref{fig:QQ-plots}, for instance, shows the 
 QQ-estimator plot for $2000$ draws from the Mittag-Leffler distribution with 
@@
 plots the static QQ-estimates (y-axis) for different cutoffs (x-axis)
-(see bottom-left panel). There is no apparent interval of stability, 
+(see bottom-left panel of Figure \ref{fig:QQ-est}). There is no apparent interval of stability, 
 which could be taken to indicate a reasonable estimate for the true 

### 2018-04-21 article_springer/article_springer.Rmd
minor changes

@@
 Section 8 concludes.
-For all statistical computations we have used R [@R], and all code, data, as 
-well as the source code for this manuscript has been organized into an R 
-software package, available at <https://github.com/UNSW-MATH/CTRM>.
+For all statistical computations we have used R [@R]. 
+Code used for the analysis in this article has been organized into 
+an R package `CTRM` (<https://github.com/UNSW-MATH/CTRM>).
+The source code for this manuscript is available online at <https://github.com/UNSW-MATH/bursty-POT>.
 
@@
 
-```{r thresholdedBursty, message=FALSE, fig.height=7, fig.cap="\\label{fig:thresholdedBursty}Exceedances (red) and Times until Exceedance (durations between blue crosses) for a given threshold $\\ell$ (dashed line)."}
+```{r thresholdedBursty, message=FALSE, fig.height=7, fig.width=9, fig.cap="\\label{fig:thresholdedBursty}Exceedances (red) and Times until Exceedance (durations between blue crosses) for a given threshold $\\ell$ (dashed line)."}
 #rpareto <- function(n,tail){
@@
 For a detailed reference on the Mittag-Leffler distribution, see e.g. 
-@Haubold11.
+@Haubold11, and for algorithms, see e.g. the R package `MittagLeffleR`
+[@MittagLeffleR].
 
@@
 
-```{r fig:QQ-est, fig.cap="QQ-estimator plots for various datasets.\\label{fig:QQ-est}", fig.height=7, fig.width=7}
-par(mfrow = c(2,2))
-flares_exponent <- flares %>% ctrm() %>% thin(k=500) %>% qqestplot(static=TRUE, main = "QQ-static, flare magnitudes")
-ML_exponent <- MittagLeffleR::rml(500, 0.8) %>% qqestplot(static=TRUE, main = "QQ-static, Mittag-Leffler data")
-ML_exponent2 <- MittagLeffleR::rml(500, 0.8) %>% qqestplot(static=FALSE, top_k = 15, conf.int = TRUE, main = "lala")
-exp_exponent <- rexp(500) %>% qqestplot(static=TRUE, main = "QQ-static, Exponential data")
+```{r fig:QQ-plots, fig.cap="Pareto vs.
+Mittag-Leffler distribution, both with same tail exponent 0.8.
+Top row: solar flare magnitudes data, fitting nicely with a Pareto distribution.
+Bottom row: simulated Mittag-Leffler data.
+Left column: static QQ-Estimator plots, assessing a fit against the Pareto distribution.
+Centre column: dynamic QQ-Estimator plots.
+Right column: a usual QQ-Plot based on Mittag-Leffler quantiles.\\label{fig:QQ-plots}", fig.height=5.5, fig.width=7}
+par(mfrow = c(2,3))
+
+flare_mags <- flares %>% ctrm() %>% thin(k=500) %>% coredata()
+flares_exponent <- flare_mags %>% qqestplot_static()
+
+flare_mags %>% tea::qqestplot(conf.int = TRUE)
+abline(h = 0.8, lty = 2, col = 2)
+
+flare_mags %>% mlqqplot(tail = 0.8, log = 'xy')
+(flare_mags %>% MittagLeffleR::logMomentEstimator())[1:2] -> MLparams
+flare_mags %>% qqline(distribution = function(p) qml(p, tail = 0.8, scale = MLparams[2]))
+
+ML_data <- MittagLeffleR::rml(500, 0.8)
+ML_exponent <- ML_data %>% qqestplot_static()
+
+ML_exponent2 <- ML_data %>% tea::qqestplot(conf.int = TRUE)
+abline(h=0.8, lty = 2, col = 2)
+
+ML_data %>% mlqqplot(0.8, log = 'xy')
+qqline(ML_data, distribution = function(p) qml(p, 0.8), col = 2)
+
 ```
@@
 exponent.
-For instance, the left panel in Figure \ref{fig:QQ-plots} shows the 
+For instance, the top-left panel in Figure \ref{fig:QQ-plots} shows the 
 (static) QQ-estimator for the magnitudes of the solar flare data, returning 
 a good fit to a Pareto distribution with tail parameter 
-`r round(flares_exponent, 2)`.
+`r round(flares_exponent, 2)`. The dynamic QQ-estimator plot (top-center panel)
+plots the tail exponent estimate for the largest values at cutoffs 
+varying up to the 5th order statistic, and the region of stability at 
+0.8 indicates a recommended estimate.
 
@@
 similar a heavy-tailed distribution is to a Pareto distribution, the less
-useful a Hill estimator is. 
-The top-right panel of Figure \ref{fig:QQ-plots}, for instance, shows the 
-QQ-estimator plot for $2000$ draws from the Mittag-Leffler distribution with 
+useful a Hill or QQ-Plot estimator becomes. 
+The bottom-left panel of Figure \ref{fig:QQ-plots}, for instance, shows the 
+static QQ-estimator plot for $2000$ draws from the Mittag-Leffler distribution with 
 tail parameter $0.8$. The stretched exponential shape means 
@@
 the Pareto distribution, severely biasing the estimator downwards 
-(`r round(ML_exponent, 2)`). Hence a cutoff needs to be introduced, 
-above which the tail exponent is fitted: The dynamic QQ-estimator 
-plots the static QQ-estimates (y-axis) for different cutoffs (x-axis)
-(see bottom-left panel of Figure \ref{fig:QQ-est}). There is no apparent interval of stability, 
-which could be taken to indicate a reasonable estimate for the true 
-tail exponent $0.8$. 
-Even worse, from a QQ-estimator point of view, there is no striking 
-difference between the infinite mean ${\rm ML}(0.8,1)$ distribution and 
-the light-tailed ${\rm Exp}(1)$ distribution (compare the right two panels). 
-In particular, if only few (e.g. $<100$) data are available, 
-then the static QQ-estimator plots look interchangeable for the two 
-distributions.
+(`r round(ML_exponent, 2)`). 
+Even by looking at different cutoffs via the dynamic QQ-estimator plot 
+(bottom-center panel) one hardly identifies $0.8$ as a stable value, and 
+thus as a clear candidate for a tail parameter estimate.
+
+QQ-estimators, and the closely related Hill estimator, are hence not 
+suitable to detect a heavy-tailed Mittag-Leffler distribution. Indeed, 
+QQ-estimator plots of exponentially distributed data are virtually 
+indistinguishable from the bottom-left panel. This shows that 
+_Mittag-Leffler distributed data may look like exponentially distributed 
+data if examined via a QQ-estimator_.
 
@@
 and instead examining QQ-plots directly 
-(see Figure \ref{fig:QQ-plots}). 
+(see Figure \ref{fig:QQ-plots}, right column). 
 The scale parameter $\sigma$ is irrelevant for a QQ-Plot. 
@@
 method by @Cahoy2013, or via maximum likelihood. 
-Both estimators are implemented in the R package `MittagLeffleR` 
+Both estimators are implemented in `MittagLeffleR` 
 [@MittagLeffleR]. 
@@
 hypothesis $\beta = 1$.
-
-```{r QQ-plots, fig.cap="QQ Plots for Mittag-Leffler data (left; $\\beta = 0.8$) and threshold crossing times / magnitudes for the solar flare data (middle / right; threshold is set at the 500th order statistic, $\\beta = 0.83$).
-Threshold crossing times appear to fit the Mittag-Leffler distribution well, whereas the Magnitudes appear to fit a Pareto distribution better (\\ref{fig:QQ-est}).
-"}
-par(mfrow = c(1, 3))
-rml(n = 500, tail = 0.8) %>% mlqqplot(tail = 0.8, log = 'xy', main = "Mittag-Leffler data")
-flares_arrivals_MLparam <- (flares_arrivals %>% mlmle())$par
-mlqqplot(flares_arrivals, 
-         tail = flares_arrivals_MLparam["tail"], 
-         scale = flares_arrivals_MLparam["scale"],
-         log = 'xy', 
-         main = "Threshold crossing times")
-flares %>% ctrm() %>% thin(k = 500) %>% coredata() %>% 
-  mlqqplot(tail = 0.8, log = 'xy', main = "Magnitudes")
-```
 
@@
 the method of log-transformed moments by @Cahoy2013.
+We have verified the validity of our estimation algorithm  via simulations, 
+see the appendix.
 
@@
 empcopula(flares_ctrm)
-mlqqplot(flares_ctrm, log = 'xy', tail = 0.8, main = "Mittag-Leffler QQ Plot")
+flares_ctrm %>% interarrival() %>% mlqqplot(log = 'xy', tail = 0.8, main = "Mittag-Leffler QQ Plot")
 ```
@@
 par(mfrow=c(1,2))
-MLestimates(ctrm = thin_sim_ctrm, tail = tail, scale = n^(1/tail))
+MLestimates(ctrm = thin_sim_ctrm, tail = params$tail, scale = n^(1/params$tail))
 ```

### 2018-04-23 article_springer/article_springer.Rmd
model is now called CTRE + minor changes

@@
   bursty time series, and 
-  show how the Mittag-Leffler distribution has a memory which affects 
-  the predictive distribution of the next extreme event.
+  show how the memory of the Mittag-Leffler distribution affects 
+  the predictive distribution for the time until the next extreme event.
 
@@
 an R package `CTRM` (<https://github.com/UNSW-MATH/CTRM>).
-The source code for this manuscript is available online at <https://github.com/UNSW-MATH/bursty-POT>.
+The source code for the figures generated in this manuscript is 
+available online at <https://github.com/UNSW-MATH/bursty-POT>.
 
-# Marked Renewal Process (MRP)
+# Continuous Time Random Exceedances (CTRE)
+
+As a model for extreme observations, we use a Marked Renewal Process (MRP):
 
@@
 : Let $(W,J), (W_1, J_1), (W_2, J_2), \ldots$ be i.i.d. pairs of random 
-variables, where the $W_k > 0$ are interpreted as the *waiting times* or 
-inter-arrival times and $J_k \in [x_L, x_R]$ as the *event magnitudes* 
-or marks
+variables, where the $W_k > 0$ are interpreted as the *waiting times* 
+and $J_k \in [x_L, x_R]$ as the *event magnitudes* 
 ($x_L \in [-\infty, +\infty), x_R \in (-\infty, +\infty]$). 
-If $W$ and $J$ are independent, the MRP is said to be *uncoupled*.
+If $W$ and $J$ are independent, the Marked Renewal Process is said to be *uncoupled*. 
+\qed
 
-In this setup, the $k$-th magnitude $J_k$ occurs at time
+Note that the $k$-th magnitude $J_k$ occurs at time
 $T_k = W_1 + \ldots + W_k$. 
-Based on this simple model, we derive the following two random variables:
+Based on an MRP, we define the Continuous Time Random Exceedance model
+(CTRE) as follows:
 
-**Definition:**
+**Definition (CTRE):**
 
@@
 $$\tau(\ell) := \min\{k: J_k > \ell\},\quad \ell \in (x_L, x_R).$$
-The random variables
+Define the pair of random variables $(X(\ell), T(\ell))$ via 
 $$X(\ell) = J_{\tau(\ell)} - \ell, \quad 
-T(\ell) = \sum_{k=1}^{\tau(\ell)} W_k$$
-are called the *exceedance* resp. *time until exceedance* of level $\ell$.
-
-By restarting the MRP at $\tau(\ell)$, one can inductively construct the
-two i.i.d. sequences $T(\ell,n)$ and $X(\ell, n)$, $n \in \mathbb N$.
-Moreover, since we assume the uncoupled case, the two sequences are independent.[^1]
-
-[^1]: To see why, note that $X(\ell)$ is, in distribution, simply equal to 
-  $J | J > \ell$, independent of any waiting time $W_k$.
+T(\ell) = \sum_{k=1}^{\tau(\ell)} W_k.$$
+By restarting the MRP at $\tau(\ell)$, inductively define the
+two i.i.d. sequences $T(\ell,n)$ and $X(\ell, n)$, $n \in \mathbb N$, 
+called the "interarrival times" and the "exceedances", respectively.
+The pair sequence $(T(\ell, n), W(\ell, n))_{n \in \mathbb N}$ is called 
+a Continuous Time Random Exceedance model (CTRE). 
+If the underlying MRP is uncoupled, then the CTRE is also called 
+uncoupled. 
+\qed
 
 ```{r thresholdedBursty, message=FALSE, fig.height=7, fig.width=9, fig.cap="\\label{fig:thresholdedBursty}Exceedances (red) and Times until Exceedance (durations between blue crosses) for a given threshold $\\ell$ (dashed line)."}
-#rpareto <- function(n,tail){
-#          if(tail<=0) stop("tail must be positive")
-#          rp <- (runif(n)/gamma(1-tail))^(-1/tail)
-#          rp}
 tail <- params$tail
@@
 
+In this article, we restrict ourselves to the uncoupled case, where
+the two sequences $X(\ell, n)_{n \in \mathbb N}$
+and $T(\ell, n)_{n \in \mathbb N}$ are independent.[^1]
 Figure \ref{fig:thresholdedBursty} shows a simulated dataset in the top 
@@
 statistical behaviour in both models. Observations below a threshold are 
-commonly discarded in Extreme Value Theory; likewise, our MRP model
+commonly discarded in Extreme Value Theory; likewise, the CTRE model
 interprets these observations as noise and filters them out.
+
+[^1]: To see why, note that $X(\ell)$ is, in distribution, simply equal to 
+  $J | J > \ell$, independent of any waiting time $W_k$.
 
@@
 $$
+\qed
 
@@
 distribution may (if $\beta$ is close to 1) be indistinguishable from the 
-exponential distribution, from the point of view of applied statistics. 
+exponential distribution, for the purposes of applied statistics. 
 For a detailed reference on the Mittag-Leffler distribution, see e.g. 
@@
 
-flare_mags <- flares %>% ctrm() %>% thin(k=500) %>% coredata()
+flare_mags <- flares %>% ctrm() %>% thin(k=500) %>% magnitudes()
 flares_exponent <- flare_mags %>% qqestplot_static()
@@
 Even by looking at different cutoffs via the dynamic QQ-estimator plot 
-(bottom-center panel) one hardly identifies $0.8$ as a stable value, and 
-thus as a clear candidate for a tail parameter estimate.
+(bottom-center panel) one hardly identifies $0.8$ as a clear candidate for 
+a tail parameter estimate.
 
 QQ-estimators, and the closely related Hill estimator, are hence not 
-suitable to detect a heavy-tailed Mittag-Leffler distribution. Indeed, 
+suitable to detect a heavy-tailed Mittag-Leffler distribution. Moreover, 
 QQ-estimator plots of exponentially distributed data are virtually 
@@
 then we recommend avoiding QQ-estimators and Hill plots altogether, 
-and instead examining QQ-plots directly 
+and instead examining QQ-plots directly, on a logarithmic scale 
 (see Figure \ref{fig:QQ-plots}, right column).
@@
 As an example, the threshold crossing times for the solar flare dataset
+(Figure \ref{fig:flare-diagnostics-2}, right panel)
 yield a difference in deviance of 
@@
 
-The Theorem in Section \ref{sec:scaling} implies that for high 
+The Theorem in Section \ref{sec:scaling} implies that for a high 
 threshold $\ell$ we may 
@@
 ```{r flare-diagnostics-1, fig.height=7, fig.cap="Diagnostic plots for the solar flare data: auto-correlation function.\\label{fig:flare-diagnostics-1}"}
-flares_ctrm <- flares %>% ctrm() %>% thin(k = 200)
+flares_ctrm <- flares %>% ctrm() %>% thin(k = 150)
 acf(flares_ctrm)
@@
 
-The MRP model is based on three main assumptions, which are repeated 
+The CTRE model is based on three main assumptions, which are repeated 
 below. For each assumption, we suggest one means of checking if it holds:
@@
 There is some residual autocorrelation for the sequence of threshold 
-exceedance times that is not accounted for by the MRP model. 
+exceedance times that is not accounted for by the CTRE model. 
 The fit with a Mittag-Leffler distribution ($\beta = 0.8$) is good, 
@@
 
-When we introduced the MRP model, we assumed that all events are i.i.d. 
+When we introduced the CTRE model, we assumed that all events are i.i.d. 
 This assumption is likely sufficient but not necessary for our limit theorem to hold. 
@@
 
-For some bursty time series, the current MRP model may be too rigid, 
+For some bursty time series, the current CTRE model may be too rigid, 
 because often the heavy-tailed character of the inter-arrival time

### 2018-04-23 article_springer/article_springer.Rmd
Change CTRM => CTRE and ctrm => ctre throughout

@@
 ---
-title: Peaks Over Threshold for Bursty Time Series
-# titlerunning: Inference for Heavy-Tailed CTRMs
+title: "Peaks Over Threshold for Bursty Time Series"
+# titlerunning: "CTRE: POT for Bursty Time Series"
 thanks: |
@@
 library(MittagLeffleR)
-devtools::install_github("UNSW-MATH/CTRM")
-library(CTRM)
+devtools::install_github("UNSW-MATH/CTRE")
+library(CTRE)
 ```
@@
   )
-library(CTRM)
+library(CTRE)
 library(MittagLeffleR)
@@
 Code used for the analysis in this article has been organized into 
-an R package `CTRM` (<https://github.com/UNSW-MATH/CTRM>).
+an R package `CTRE` (<https://github.com/UNSW-MATH/CTRE>).
 The source code for the figures generated in this manuscript is 
@@
 magnitudes <- extRemes::revd(n, scale = 1, shape = 0)
-sim_ctrm <- ctrm(data.frame(times, magnitudes)) 
+sim_ctre <- ctre(data.frame(times, magnitudes)) 
 par(mfrow = c(2,1))
-plot(sim_ctrm, p = 0.01, main = "Simulated MRP") 
-flares %>% ctrm() %>% plot(p = 0.02, log = 'y', main = "HXRBS data") 
+plot(sim_ctre, p = 0.01, main = "Simulated MRP") 
+flares %>% ctre() %>% plot(p = 0.02, log = 'y', main = "HXRBS data") 
 ```
@@
 
-flare_mags <- flares %>% ctrm() %>% thin(k=500) %>% magnitudes()
+flare_mags <- flares %>% ctre() %>% thin(k=500) %>% magnitudes()
 flares_exponent <- flare_mags %>% qqestplot_static()
@@
 ```{r likelihood-ratio-test}
-flares_arrivals <- flares %>% ctrm() %>% thin(k = 500) %>% interarrival()
+flares_arrivals <- flares %>% ctre() %>% thin(k = 500) %>% interarrival()
 mlmle_out <- mlmle(data = flares_arrivals)
@@
 Dotted horizontal lines are at $\\beta = 0.85$ and $\\sigma_0 = 3 \\times 10^7$ seconds $\\approx 0.95$ years."}
-thin_flares_ctrm <- flares %>% ctrm() %>% thin(k = 700)
+thin_flares_ctre <- flares %>% ctre() %>% thin(k = 700)
 par(mfrow=c(1,2))
-MLestimates(thin_flares_ctrm, tail = 0.9, scale = 3 * 1E7)
+MLestimates(thin_flares_ctre, tail = 0.9, scale = 3 * 1E7)
 ```
@@
 ```{r flare-diagnostics-1, fig.height=7, fig.cap="Diagnostic plots for the solar flare data: auto-correlation function.\\label{fig:flare-diagnostics-1}"}
-flares_ctrm <- flares %>% ctrm() %>% thin(k = 150)
-acf(flares_ctrm)
+flares_ctre <- flares %>% ctre() %>% thin(k = 150)
+acf(flares_ctre)
 ```
@@
 par(mfrow = c(2,2))
-empcopula(flares_ctrm)
-flares_ctrm %>% interarrival() %>% mlqqplot(log = 'xy', tail = 0.8, main = "Mittag-Leffler QQ Plot")
+empcopula(flares_ctre)
+flares_ctre %>% interarrival() %>% mlqqplot(log = 'xy', tail = 0.8, main = "Mittag-Leffler QQ Plot")
 ```
@@
 k_max <- 500 
-thin_sim_ctrm <- thin(ctrm = sim_ctrm, k = k_max)
+thin_sim_ctre <- thin(ctre = sim_ctre, k = k_max)
 par(mfrow=c(1,2))
-MLestimates(ctrm = thin_sim_ctrm, tail = params$tail, scale = n^(1/params$tail))
+MLestimates(ctre = thin_sim_ctre, tail = params$tail, scale = n^(1/params$tail))
 ```

### 2018-04-24 article_springer/article_springer.Rmd

@@
 # use this rticles version: 
-devtools::install_github("strakaps/rticles", 
-                         ref = "724aeb88d005e2f7befc37328633e7cb2bc1cce0")
+devtools::install_github("rstudio/rticles")
 # use the newest MittagLeffleR version:
-devtools::install_github("strakaps/MittagLeffleR")
+devtools::install_github("UNSW-MATH/MittagLeffleR")
 library(MittagLeffleR)
@@
 plausible explanations for bursty behaviour (most prominently self-exciting
-point processes [@hawkes1971point]), there seems to be one salient feature 
+point process by @hawkes1971point), there seems to be one salient feature 
 which very typically indicates the departure from temporal homogeneity: a 
@@
 such as for earthquakes, solar flares or neuron voltages. 
-Extreme value theory provides models for the distribution of the events
-with the largest magnitude. 
+The Peaks-Over-Threshold model [POT, see e.g. @ColesBook] applies a
+threshold to the magnitudes, and fits a Generalized Pareto distribution 
+to the threshold exceedances. 
 A commonly made assumption in POT models is that times between 
@@
 or light-tailed, and this entails that the 
-threshold crossing times form a Poisson process [@beirlantBook]. 
+threshold crossing times form a Poisson process [@Hsing88]. 
 Then as one increases the threshold and thus decreases the threshold 
 crossing probability $p$, the Poisson process is rarefied, i.e. its 
-intensity decreases _linearly_ with $p$.
+intensity decreases _linearly_ with $p$ [see e.g. @beirlantBook].
 
@@
 Mittag-Leffler distribution in Section 4. 
+(A simulation study of the effectiveness of our statistical procedure is 
+given in the appendix.)
 Diagnostic plots for model criticism are discussed in Section 6. 
-In Section 7, we discuss the non-memorylessness property of the 
+In Section 7, we discuss the memory property of the 
 Mittag-Leffler distribution, and how it affects the predictive distribution 
-for the next threshold crossing event. 
+for the time until the next threshold crossing event. 
 Section 8 concludes. 
 For all statistical computations we have used R [@R]. 
-Code used for the analysis in this article has been organized into 
+All code and data used for the analysis in this article has been organized into 
 an R package `CTRE` (<https://github.com/UNSW-MATH/CTRE>).

### 2018-04-24 article_springer/article_springer.Rmd
add something about cluster of extremes

@@
 This assumption is likely sufficient but not necessary for our limit theorem to hold. 
-Morevoer, any data below a (minimum) threshold $\ell_0$ is discarded in 
+Moreover, any data below a (minimum) threshold $\ell_0$ is discarded in 
 our inference procedure, and hence need not satisfy the i.i.d. assumption.
 For the purposes of statistical inference, we merely require that the 
-inter-threshold-crossing times are i.i.d.
+inter-threshold-crossing times are i.i.d. However, it might be interesting 
+to generalize our theory to the case of a stationary sequence of magnitudes.
+In case of fixed times between observations, the distribution of the sequence of (correctly normalized) inter-exceedance times converges under certain (mixing) conditions to a mixture of an exponential distribution and a point mass in zero [@ferro2003inference].
+Hence, this also leads to a model for extreme events that occur in cluster.
+Allowing for both, dependence between the magnitudes and heavy tailed waiting times, could maybe further improve modelling of extreme events like earthquakes, that occur in clusters.
 

### 2018-04-24 article_springer/article_springer.tex
add something about cluster of extremes

% !TeX program = pdfLaTeX
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{amsmath}
\usepackage{graphicx}

\usepackage[hyphens]{url} % not crucial - just used below for the URL
\usepackage{hyperref}
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%

%% load any required packages here
\usepackage{amssymb}

\begin{document}

\title{Peaks Over Threshold for Bursty Time Series \thanks{Peter Straka was supported by the Discovery Early Career Research Award
DE160101147 on the Project ``Predicting Extremes when Events Occur in
Bursts'' by the Australian Research Council. Katharina Hees was
supported by the DAAD co-financed by the German Federal Ministry of
Education and Research (BMBF).} }

\author{  Katharina Hees \and  Smarak Nayak \and  Peter Straka* \and  }

    \authorrunning{ K. Hees, S. Nayak \& P. Straka }

\institute{
        Katharina Hees \at
     University of Dortmund \\
     \email{\href{mailto:hees@statistik.uni-dortmund.de}{\nolinkurl{hees@statistik.uni-dortmund.de}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Smarak Nayak \at
     National Australia Bank \\
     \email{\href{mailto:smarak.nayak@nab.com.au}{\nolinkurl{smarak.nayak@nab.com.au}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Peter Straka* \at
     UNSW Sydney \\
     \email{\href{mailto:p.straka@unsw.edu.au}{\nolinkurl{p.straka@unsw.edu.au}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
    }

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
In many complex systems studied in statistical physics, inter-arrival
times between events such as solar flares, trades and neuron voltages
follow a heavy-tailed distribution. The set of event times is
fractal-like, being dense in some time windows and empty in others, a
phenomenon which has been dubbed ``bursty''.

This article generalizes the Peaks Over Threshold (POT) model to the
setting where inter-event times are heavy-tailed. For high thresholds
and infinite-mean waiting times, we show that the times between
threshold crossings are Mittag-Leffler distributed, and thus form a
``fractional Poisson Process'' which generalizes the standard Poisson
Process. We provide graphical means of estimating model parameters and
assessing model fit. Along the way, we apply our inference method to a
real-world bursty time series, and show how the memory of the
Mittag-Leffler distribution affects the predictive distribution for the
time until the next extreme event.
\\
\keywords{
        heavy tails \and
        renewal process \and
        extreme value theory \and
        peaks over threshold \and
    }

\end{abstract}

\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

\section{Introduction}\label{introduction}

Time series displaying temporally inhomogeneous behaviour have received
strong interest in the recent statistical physics literature (Barabási
2005; J. Oliveira and Barabási 2005; Vasquez et al. 2006; Vazquez et al.
2007; Omi and Shinomoto 2011; Min, Goh, and Vazquez 2011; Karsai et al.
2011; Bagrow and Brockmann 2013). They have been observed in the context
of earthquakes, sunspots, neuronal activity and human communication (see
Karsai et al. 2012; Vajna, Tóth, and Kertész 2013; Mark M Meerschaert
and Stoev 2008 for a list of references). Such time series exhibit high
activity in some `bursty' intervals, which alternate with other, quiet
intervals. Although several mechanisms are plausible explanations for
bursty behaviour (most prominently self-exciting point process by Hawkes
(1971)), there seems to be one salient feature which very typically
indicates the departure from temporal homogeneity: a heavy-tailed
distribution of waiting times (Vasquez et al. 2006; Karsai et al. 2012;
Vajna, Tóth, and Kertész 2013). As we show below in simulations, a
simple renewal process with heavy-tailed waiting times can capture this
type of dynamics. For many systems, the renewal property is appropriate;
a simple test of the absence of correlations in a succession of waiting
times can be undertaken by randomly reshuffling the waiting times
(Karsai et al. 2012).

Often a magnitude, or mark can be assigned to each event in the renewal
process, such as for earthquakes, solar flares or neuron voltages. The
Peaks-Over-Threshold model (POT, see e.g. Coles 2001) applies a
threshold to the magnitudes, and fits a Generalized Pareto distribution
to the threshold exceedances. A commonly made assumption in POT models
is that times between events are either fixed or light-tailed, and this
entails that the threshold crossing times form a Poisson process (Hsing,
Hüsler, and Leadbetter 1988). Then as one increases the threshold and
thus decreases the threshold crossing probability \(p\), the Poisson
process is rarefied, i.e.~its intensity decreases \emph{linearly} with
\(p\) (see e.g. Beirlant et al. 2006).

As will be shown below, in the heavy-tailed waiting time scenario
threshold crossing times form a \emph{fractional Poisson process}
(Laskin 2003; Mark M Meerschaert, Nane, and Vellaisamy 2011), which is a
renewal process with Mittag-Leffler distributed waiting times. The
family of Mittag-Leffler distributions nests the exponential
distribution (Haubold, Mathai, and Saxena 2011), and hence the
fractional Poisson process generalizes the standard Poisson process.
Again as the threshold size increases and the threshold crossing
probability \(p\) decreases, the fractional Poisson process is rarefied:
The scale parameter of the Mittag-Leffler inter-arrival times of
threshold crossing times increases, but \emph{superlinearly}; see the
Theorem below.

Maxima of events which occur according to a renewal process with
heavy-tailed waiting times have been studied under the names
``Continuous Time Random Maxima process'' (CTRM) (Benson, Schumer, and
Meerschaert 2007; Mark M Meerschaert and Stoev 2008; Hees and Scheffler
2016; Hees and Scheffler 2017), ``Max-Renewal process'' (Silvestrov
2002; Silvestrov and Teugels 2004; Basrak and Špoljarić 2015), and
``Shock process'' (Esary and Marshall 1973; Shanthikumar and Sumita
1983; Shanthikumar and Sumita 1984; Shanthikumar and Sumita 1985;
Anderson 1987; Gut and Hüsler 1999). The existing literature focuses on
probabilistic results surrounding these models. In this work, however,
we introduce a method of inference for this type of model, which is
seemingly not available in the literature.

We review the marked renewal process in Section 2, and derive a scaling
limit theorem for inter-exceedance times in Section 3. We give a
statistical procedure to estimate model parameters via stability plots
in Section 5, but to set the stage we first discuss inference for the
Mittag-Leffler distribution in Section 4. (A simulation study of the
effectiveness of our statistical procedure is given in the appendix.)
Diagnostic plots for model criticism are discussed in Section 6. In
Section 7, we discuss the memory property of the Mittag-Leffler
distribution, and how it affects the predictive distribution for the
time until the next threshold crossing event. Section 8 concludes. For
all statistical computations we have used R (R Core Team 2018). All code
and data used for the analysis in this article has been organized into
an R package \texttt{CTRE} (\url{https://github.com/UNSW-MATH/CTRE}).
The source code for the figures generated in this manuscript is
available online at \url{https://github.com/UNSW-MATH/bursty-POT}.

\section{Continuous Time Random Exceedances
(CTRE)}\label{continuous-time-random-exceedances-ctre}

As a model for extreme observations, we use a Marked Renewal Process
(MRP):

\begin{description}
\item[\textbf{Definition (MRP):}]
Let \((W,J), (W_1, J_1), (W_2, J_2), \ldots\) be i.i.d. pairs of random
variables, where the \(W_k > 0\) are interpreted as the \emph{waiting
times} and \(J_k \in [x_L, x_R]\) as the \emph{event magnitudes}
(\(x_L \in [-\infty, +\infty), x_R \in (-\infty, +\infty]\)). If \(W\)
and \(J\) are independent, the Marked Renewal Process is said to be
\emph{uncoupled}. \qed
\end{description}

Note that the \(k\)-th magnitude \(J_k\) occurs at time
\(T_k = W_1 + \ldots + W_k\). Based on an MRP, we define the Continuous
Time Random Exceedance model (CTRE) as follows:

\begin{description}
\item[\textbf{Definition (CTRE):}]
Given a threshold \(\ell \in (x_L, x_R)\), consider the stopping time
\[\tau(\ell) := \min\{k: J_k > \ell\},\quad \ell \in (x_L, x_R).\]
Define the pair of random variables \((X(\ell), T(\ell))\) via
\[X(\ell) = J_{\tau(\ell)} - \ell, \quad 
T(\ell) = \sum_{k=1}^{\tau(\ell)} W_k.\] By restarting the MRP at
\(\tau(\ell)\), inductively define the two i.i.d. sequences
\(T(\ell,n)\) and \(X(\ell, n)\), \(n \in \mathbb N\), called the
``interarrival times'' and the ``exceedances'', respectively. The pair
sequence \((T(\ell, n), W(\ell, n))_{n \in \mathbb N}\) is called a
Continuous Time Random Exceedance model (CTRE). If the underlying MRP is
uncoupled, then the CTRE is also called uncoupled. \qed
\end{description}

\begin{figure}
\includegraphics[width=\textwidth]{article_springer_files/figure-latex/thresholdedBursty-1} \caption{\label{fig:thresholdedBursty}Exceedances (red) and Times until Exceedance (durations between blue crosses) for a given threshold $\ell$ (dashed line).}\label{fig:thresholdedBursty}
\end{figure}

In this article, we restrict ourselves to the uncoupled case, where the
two sequences \(X(\ell, n)_{n \in \mathbb N}\) and
\(T(\ell, n)_{n \in \mathbb N}\) are independent.\footnote{To see why,
  note that \(X(\ell)\) is, in distribution, simply equal to
  \(J | J > \ell\), independent of any waiting time \(W_k\).} Figure
\ref{fig:thresholdedBursty} shows a simulated dataset in the top panel,
where \(W\) has a stable distribution with tail parameter \(\beta =\)
0.8 (and skewness \(1\) and location \(0\)), and where \(J\) is from a
standard Gumbel distribution. In the bottom panel, we plot a time series
of solar flare intensities derived from a NASA dataset (Dennis et al.
1991)\footnote{The ``complete Hard X Ray Burst Spectrometer event list''
  is a comprehensive reference for all measurements of the Hard X Ray
  Burst Spectrometer on NASA's Solar Maximum Mission from the time of
  launch on Feb 14, 1980 to the end of the mission in Dec 1989. 12,776
  events were detected, with the ``vast majority being solar flares''.
  The list includes the start time, peak time, duration, and peak rate
  of each event. We have used ``start time'' as the variable for event
  times, and ``peak rate'' as the variable for event magnitudes.}.
Clearly, the simulated data exhibit long intervals \emph{without any}
events, whereas in the real-world dataset events appear continuously.
The threshold exceedances, however, appear to have similar statistical
behaviour in both models. Observations below a threshold are commonly
discarded in Extreme Value Theory; likewise, the CTRE model interprets
these observations as noise and filters them out.

\section{Scaling limit of Exceedance Times}\label{sec:scaling}

In this section we state and prove the key theorem, see below. For an
accessible introduction to regular variation and stable limit theorems,
we recommend the book by Mark M Meerschaert and Sikorskii (2012).

\begin{description}
\tightlist
\item[\textbf{Theorem:}]
Let the waiting times \(J_k\) be in the domain of attraction of a
positively skewed sum-stable law with stability parameter
\(0 < \beta < 1\); more precisely,

\begin{align} \label{eq:stability}
\frac{W_1 + \ldots + W_n}{b(n)} \overset{d}{\longrightarrow} D, 
\quad n \to \infty
\end{align}

for a function \(b(n)\) which is regularly varying at \(\infty\) with
parameter \(1/\beta\), and where
\(\mathbf E[\exp(-sD)] = \exp(-s^\beta)\). Write
\(p := \mathbf P(J > \ell)\). Then the weak convergence \[
\frac{T(\ell)} {b(1/p)} \to W_\beta \quad \text{ as } \quad \ell \uparrow x_R
\] holds, where the Mittag-Leffler random variable \(W_\beta\) is
defined on the positive real numbers via \[
\mathbf E[\exp(-sW_\beta)] = \frac{1}{1+s^\beta}.
\] \qed
\end{description}

\noindent For a scale parameter \(\sigma > 0\), we write
\({\rm ML}(\beta, \sigma)\) for the distribution of \(\sigma W_\beta\).
The Mittag-Leffler distribution with parameter \(\beta \in (0,1]\) is a
heavy-tailed positive distribution for \(\beta < 1\), with infinite
mean. However, as \(\beta \uparrow 1\), \({\rm ML}(\beta, \sigma)\)
converges weakly to the exponential distribution \({\rm Exp}(\sigma)\).
This means that although its moments are all infinite, the
Mittag-Leffler distribution may (if \(\beta\) is close to 1) be
indistinguishable from the exponential distribution, for the purposes of
applied statistics. For a detailed reference on the Mittag-Leffler
distribution, see e.g. Haubold, Mathai, and Saxena (2011), and for
algorithms, see e.g.~the R package \texttt{MittagLeffleR} (Gill and
Straka 2017).

\paragraph{\texorpdfstring{\emph{Proof of
Theorem:}}{Proof of Theorem:}}\label{proof-of-theorem}

We interpret the threshold crossing time \(T(\ell)\) as the hitting time
of the underlying CTRM (Continuous Time Random Maxima) or ``max-renewal
process'', and then utilize a result by Mark M Meerschaert and Stoev
(2008). The running maximum process is defined as \[
M(c) := J_1 \vee \ldots \vee J_{\lfloor c \rfloor},
\] and since we assume that the \(J_k\) have a continuous distribution,
there exist norming functions \(a(c)\) and \(d(c)\) such that \[
\mathbf P\left[ \frac{M(c) - d(c)}{a(c)} \le \ell^* \right] 
\longrightarrow F(\ell^*), \quad t \to \infty
\] where \(F\) is a generalized extreme value distribution, and
\(\ell^*\) is any value from the support of \(F\). The CTRM process is
then defined via \[
V(t) = M(N(t)), \quad t \ge 0
\] where \(N(t)\) is the renewal process associated with the waiting
times \(W_k\): \[
N(t) = \max\{n: W_1 + \ldots + W_n \le t\}.
\] Now a key observation is that \[
T(\ell) = \inf\{t: V(t) > \ell\}, 
\] and that \[
T(\ell) > t \quad \text{ if and only if } \quad V(t) \le \ell.
\] By (Theorem 3.1, Mark M Meerschaert and Stoev 2008), we have the
stochastic process convergence \[
\frac{V(ct) - d(\tilde b(c))}{a(\tilde b(c))} 
\stackrel{d}{\longrightarrow} Y(t), \quad t > 0.
\] where \(Y(t)\) is a time-changed (``subordinated'') extremal process,
and where \(\tilde b(c)\) is a regularly varying norming function which
is \emph{inverse} to \(b(c)\), in the sense that
\(b(\tilde b(c)) \sim c \sim \tilde b(b(c))\).

Without loss of generality, we choose \(\ell^*\) such that
\(F(\ell^*) = 1/e\), and let
\(\ell = a(\tilde b(c)) \ell^* + d(\tilde b(c))\). We may then calculate
\[
\mathbf P\left[ \frac{T(\ell)}{b(1/p)} > t \right]
= \mathbf P[T(\ell) > b(1/p) t]
= \mathbf P[V(ct) \le \ell]
\] where we have substituted \(c = b(1/p)\). Moreover \[
\mathbf P[V(ct) \le \ell]
= \mathbf P\left[ \frac{V(ct) - d(\tilde b(c))}{a(\tilde b(c))} 
\le \frac{\ell - d(\tilde b(c))}{a(\tilde b(c))} \right]
\longrightarrow \mathbf P\left[ Y(t) \le \ell^* \right]
\] Defining the hitting time of level \(\ell^*\) by \(Y(t)\) as
\(\xi_{\ell^*} := \inf\{t: Y(t) > \ell^*\}\), we then have \[
P\left[ Y(t) \le \ell^* \right] = \mathbf P[\xi_{\ell^*} > t] 
= \mathbf P[(-\log F(\ell^*))^{-1/\beta} X^{1/\beta} D > t]
\] by (Proposition 4.2, Mark M Meerschaert and Stoev 2008), where \(X\)
is an exponential random variable with mean \(1\). Using (Theorem 19.1,
Haubold, Mathai, and Saxena 2011), we see that
\(X^{1/\beta} D \sim {\rm ML}(\beta, 1)\), concluding the proof. \qed

\begin{description}
\tightlist
\item[\textbf{Remark:}]
If \(\beta = 1\), the result of the Theorem above is standard, see e.g.
Equation (2.2) in Gut and Hüsler (1999).
\end{description}

\section{Inference for the Mittag-Leffler
distribution}\label{inference-for-the-mittag-leffler-distribution}

\begin{figure}
\includegraphics[width=\textwidth]{article_springer_files/figure-latex/fig:QQ-plots-1} \caption{Pareto vs. Mittag-Leffler distribution, both with same tail exponent 0.8. Top row: solar flare magnitudes data, fitting nicely with a Pareto distribution. Bottom row: simulated Mittag-Leffler data. Left column: static QQ-Estimator plots, assessing a fit against the Pareto distribution. Centre column: dynamic QQ-Estimator plots. Right column: a usual QQ-Plot based on Mittag-Leffler quantiles.\label{fig:QQ-plots}}\label{fig:fig:QQ-plots}
\end{figure}

Since the Mittag-Leffler distribution is heavy-tailed, many researchers
would intuitively give the highest importance to the tail behaviour of
the distribution, and estimate the exponent of the tail function with
established methods such as the Hill estimator. The QQ-estimator (Kratz
and Resnick 1996) is closely related to the Hill estimator and fits a
least squares line through the logarithms of the ordered statistics
(y-axis) and the corresponding quantiles of the exponential distribution
(x-axis). The reciprocal slope is returned as the estimate of the tail
exponent. For instance, the top-left panel in Figure \ref{fig:QQ-plots}
shows the (static) QQ-estimator for the magnitudes of the solar flare
data, returning a good fit to a Pareto distribution with tail parameter
0.79. The dynamic QQ-estimator plot (top-center panel) plots the tail
exponent estimate for the largest values at cutoffs varying up to the
5th order statistic, and the region of stability at 0.8 indicates a
recommended estimate.

However, as described nicely by Resnick (1997), the less similar a
heavy-tailed distribution is to a Pareto distribution, the less useful a
Hill or QQ-Plot estimator becomes. The bottom-left panel of Figure
\ref{fig:QQ-plots}, for instance, shows the static QQ-estimator plot for
\(2000\) draws from the Mittag-Leffler distribution with tail parameter
\(0.8\). The stretched exponential shape means that the Mittag-Leffler
distribution has more probability near \(0\) than the Pareto
distribution, severely biasing the estimator downwards (0.62). Even by
looking at different cutoffs via the dynamic QQ-estimator plot
(bottom-center panel) one hardly identifies \(0.8\) as a clear candidate
for a tail parameter estimate.

QQ-estimators, and the closely related Hill estimator, are hence not
suitable to detect a heavy-tailed Mittag-Leffler distribution. Moreover,
QQ-estimator plots of exponentially distributed data are virtually
indistinguishable from the bottom-left panel. This shows that
\emph{Mittag-Leffler distributed data may look like exponentially
distributed data if examined via a QQ-estimator}.

Hence if there is some prior expectation that the data are drawn from
the Mittag-Leffler distribution (as is the the case for threshold
exceedance times), then we recommend avoiding QQ-estimators and Hill
plots altogether, and instead examining QQ-plots directly, on a
logarithmic scale (see Figure \ref{fig:QQ-plots}, right column). The
scale parameter \(\sigma\) is irrelevant for a QQ-Plot. The tail
parameter \(\beta\) can be estimated quickly via the log-moment method
by Cahoy (2013), or via maximum likelihood. Both estimators are
implemented in \texttt{MittagLeffleR} (Gill and Straka 2017). Since the
exponential distribution is nested in the Mittag-Leffler family of
distributions, a standard likelihood ratio test can be performed, with
the exponential distribution as a null model against a Mittag-Leffler
distribution as the alternative. As an example, the threshold crossing
times for the solar flare dataset (Figure \ref{fig:flare-diagnostics-2},
right panel) yield a difference in deviance of \(\approx\) 324, which
evaluates to a strongly significant \(\chi^2_1\) test statistic (p-value
= \(10^{-72}\)) for the null hypothesis \(\beta = 1\).

\section{Inference on Exceedance
times}\label{inference-on-exceedance-times}

\begin{figure}
\includegraphics[width=\textwidth]{article_springer_files/figure-latex/solar-flare-tail-scale-1} \caption{\label{fig:flares}Stability plots for the tail and scale parameter of the Mittag-Leffler distribution of the Solar Flare dataset. Dotted horizontal lines are at $\beta = 0.85$ and $\sigma_0 = 3 \times 10^7$ seconds $\approx 0.95$ years.}\label{fig:solar-flare-tail-scale}
\end{figure}

The Theorem in Section \ref{sec:scaling} implies that for a high
threshold \(\ell\) we may approximate the distribution of \(T(\ell)\)
with an \({\rm ML}(\beta, b(1/p))\) distribution, where \(b(\,)\) varies
regularly at \(\infty\) with parameter \(1/\beta\). Building on the POT
(Peaks Over Threshold) method, we propose the following estimation
procedure for the distribution of \(T(\ell)\):

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  For a range of thresholds \(\ell\) near the largest order statistics,
  extract datasets of exceedance times \(\{T(\ell, i)\}_i\).
\item
  For each choice of threshold \(\ell\), fit a Mittag-Leffler
  distribution to the resulting dataset \(\{T(\ell, i)\}_i\). This
  results in the estimates \(\{\hat\beta(\ell)\}_\ell\) and
  \(\{\hat \sigma(\ell)\}_\ell\).
\item
  Plot \(\ell\) vs.~\(\hat \beta(\ell)\). As \(\ell\) increases towards
  \(x_R\), \(\hat \beta(\ell)\) \emph{stabilizes} around a constant
  \(\hat \beta\). Use \(\hat \beta\) as an estimate for the tail
  parameter \(\beta\) of the Mittag-Leffler distribution of exceedance
  times.
\item
  Approximate \(p \approx |\{k: J_k > \ell\}| / n\). Recall that
  \(b(c)\) is regularly varying with parameter \(1/\beta\), and hence
  has the representation \(b(c) = L(c) c^{1/\beta}\) for some slowly
  varying function \(L(c)\). Assuming that the variation of \(L(c)\) is
  negligible, we hence plot \(\ell\)
  vs.~\(p^{1/\hat \beta} \hat \sigma(\ell)\). Again as \(\ell\)
  increases towards \(x_R\), \(p^{1/\hat \beta} \hat \sigma(\ell)\) is
  expected to stabilize around a constant \(\hat \sigma_0\). We then use
  \(p^{-1/\hat \beta} \hat \sigma_0\) as an estimate of the scale
  parameter of the Mittag-Leffler distribution of exceedance times for
  the level \(\ell\).
\end{enumerate}

The above approach, though theoretically sound, benefits from the
following practical adjustments (compare with Figure \ref{fig:flares}):

\begin{itemize}
\tightlist
\item
  We choose \(\ell\) from the order statistics, i.e. \(\ell\) is the
  \(k\)-th largest of the observations \(X_j\), where \(k\) runs from
  \(k_\text{min}, k_\text{min} + 1, \ldots, k_\text{max}\). The datasets
  are then of length \(k-1\).
\item
  We use \(k\) rather than \(\ell\) for the horizontal axis of our
  plots.
\item
  In Step 4, rather than plotting \(p^{1/\hat \beta} \hat \sigma(\ell)\)
  we plot \(k^{1/\hat \beta} \hat \sigma(\ell)\). This changes
  \(\hat \sigma_0\) by the multiplicative constant \(n^{1/\hat \beta}\),
  but has the advantage that \(\hat \sigma_0\) does not change if one
  pre-processes the data by removing all observations below a certain
  threshold.
\end{itemize}

The estimates \(\hat \beta\) and \(\hat \sigma_0\) give an estimate of
the distribution of exceedance times, dependent on the threshold
\(\ell\):

\begin{align*}
T(\ell) \sim {\rm ML}(\hat \beta, k^{-1/\hat \beta} \hat \sigma_0).
\end{align*}

For quick estimates of the Mittag-Leffler parameters we have used the
method of log-transformed moments by Cahoy (2013). We have verified the
validity of our estimation algorithm via simulations, see the appendix.

\section{Checking Model Assumptions}\label{checking-model-assumptions}

\begin{figure}
\includegraphics[width=\textwidth]{article_springer_files/figure-latex/flare-diagnostics-1-1} \caption{Diagnostic plots for the solar flare data: auto-correlation function.\label{fig:flare-diagnostics-1}}\label{fig:flare-diagnostics-1}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{article_springer_files/figure-latex/flare-diagnostics-2-1} \caption{Diagnostic plots for the solar flare data: empirical copula and QQ Plot. \label{fig:flare-diagnostics-2}}\label{fig:flare-diagnostics-2}
\end{figure}

The CTRE model is based on three main assumptions, which are repeated
below. For each assumption, we suggest one means of checking if it
holds:

\begin{description}
\tightlist
\item[i.i.d.:]
After removing the ``noise observations'' below the smallest threshold
\(\ell_0\), the pair sequence \((T(\ell_0, i), X(\ell_0,i))\) is i.i.d.
An indication if this is true is given by an auto-correlation plot for
the logarithms (to ensure finite moments) of the two time series.
\item[Uncoupled:]
Each \(T(\ell, i)\) is independent of each \(X(\ell, i)\). We propose an
empirical copula plot to check for any dependence.
\item[\({\rm ML}(\beta, \sigma)\) distribution of \(T(\ell, i)\):]
Apply a cutoff at the lowest threshold \(\ell_0\), extract the threshold
crossing times, and create a QQ Plot for the Mittag-Leffler
distribution. Use a log-Moment estimate of the tail parameter for the
theoretical / population quantiles of the plot.
\end{description}

Figures \ref{fig:flare-diagnostics-1} and \ref{fig:flare-diagnostics-2}
show the diagnostic plots for a minimum threshold chosen at the 200th
order statistic. There is some residual autocorrelation for the sequence
of threshold exceedance times that is not accounted for by the CTRE
model. The fit with a Mittag-Leffler distribution (\(\beta = 0.8\)) is
good, though there are signs that the power-law tail tapers off for very
large inter-threshold crossing times. There is no apparent dependence
between threshold exceedance times and event magnitudes seen in the
copula plot.

\section{Predicting the time of the next threshold
crossing}\label{predicting-the-time-of-the-next-threshold-crossing}

According to Figure \ref{fig:flares}, for a threshold \(\ell\) at the
\(k\)-th order statistic, the fitted threshold exceedance time
distribution is \[
T_\ell \sim {\rm ML}(\beta, k^{1/\beta} \sigma_0), 
\] where \(\beta = 0.85\) and \(\sigma_0 = 3.0 \times 10^7 {\rm sec}\).
Unlike the exponential distribution, the Mittag-Leffler distribution is
not memoryless, and the probability density of the time \(t\) until the
next threshold crossing will depend on the time \(t_0\) elapsed since
the last threshold crossing. This density equals \[
p(t|\beta, \sigma_0, \ell, t_0) = \frac{f(t + t_0 | \beta, k^{1/\beta} \sigma_0)}{\mathbf P[T_\ell > t_0]}
\] where \(f(\,\cdot\, | \beta, k^{1/\beta} \sigma_0)\) is the
probability density of \({\rm ML}(\beta, k^{1/\beta} \sigma_0)\). The
more time has passed without a threshold crossing, the more the
probability distribution shifts towards larger values for the next
crossing (see Figure \ref{fig:hazard}, left panel). The hazard rate \[
h(t) = \frac{f(t| \beta, k^{1/\beta} \sigma_0))}{\int_t^\infty f(\tau| \beta, k^{1/\beta} \sigma_0))\,d\tau}
\] represents the risk of a threshold crossing per unit time, and is a
decreasing function for the Mittag-Leffler distribution. The closer
\(\beta\) is to \(1\), the more the hazard rate mimics that of an
exponential distribution (a constant function, see Figure
\ref{fig:hazard}, right panel).

\begin{figure}
\includegraphics[width=\textwidth]{article_springer_files/figure-latex/hazard-1} \caption{Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\beta = 0.8$, $\sigma_0 = 1$). Right: Hazard rate depending on tail parameter $\beta$.\label{fig:hazard}}\label{fig:hazard}
\end{figure}

It is beyond the scope of the current paper to incorporate parameter
uncertainty into our predictive distribution for the next threshold
crossing; however, methods as described by Scarrott and Macdonald (2012)
and Lee, Fan, and Sisson (2015) are likely to extend to our setting.

\section{Discussion \& Conclusion}\label{discussion-conclusion}

We have extended the POT (Peaks over Threshold) model, a mainstay of
extreme value theory, to ``bursty'' time series, which have been studied
intensively in statistical physics. Burstiness is characterized by
power-law waiting times between events, and we have shown that the
Mittag-Leffler distribution arises naturally as a scaling limit for the
inter-exceedance times of high thresholds. Moreover, we have derived the
following non-linear scaling behaviour: \(\sigma \sim p^{-1/\beta}\),
where \(\sigma\) is the scale parameter of the distribution of threshold
exceedance times, \(p\) is the fraction of magnitudes above the
threshold, and \(\beta\) the exponent of the power law.

The ``anomalous'' scaling behaviour in the bursty setting entails two
phenomena: i) a heavy tail of the interarrival time distribution of
threshold crossings (long rests), and ii) a high propensity for more
threshold crossing events immediately after each threshold crossing
event (bursts). The Mittag-Leffler distribution captures both phenomena,
due to its heavy tail as well as its stretched exponential (peaked)
asymptotics for small times. It generalizes the exponential
distribution, and in the solar flare data example, this generalization
is warranted, because the likelihood-ratio test is strongly significant.

When we introduced the CTRE model, we assumed that all events are i.i.d.
This assumption is likely sufficient but not necessary for our limit
theorem to hold. Moreover, any data below a (minimum) threshold
\(\ell_0\) is discarded in our inference procedure, and hence need not
satisfy the i.i.d. assumption. For the purposes of statistical
inference, we merely require that the inter-threshold-crossing times are
i.i.d. However, it might be interesting to generalize our theory to the
case of a stationary sequence of magnitudes. In case of fixed times
between observations, the distribution of the sequence of (correctly
normalized) inter-exceedance times converges under certain (mixing)
conditions to a mixture of an exponential distribution and a point mass
in zero (Ferro and Segers 2003). Hence, this also leads to a model for
extreme events that occur in cluster. Allowing for both, dependence
between the magnitudes and heavy tailed waiting times, could maybe
further improve modelling of extreme events like earthquakes, that occur
in clusters.

For some bursty time series, the current CTRE model may be too rigid,
because often the heavy-tailed character of the inter-arrival time
distribution does not hold at all time scales; rather, it often applies
at short and intermediate time scales, and is truncated or tempered
(reverting to an exponential distribution) at very long time scales, see
e.g. Mark M. Meerschaert, Roy, and Shao (2012) and Aban, Meerschaert,
and Panorska (2006). In such situations, a ``tempered'' Mittag-Leffler
distribution may provide a more realistic fit, which we aim to introduce
in follow-up work.

\subsection*{Acknowledgements}\label{acknowledgements}
\addcontentsline{toc}{subsection}{Acknowledgements}

The authors would like to thank Prof.~Peter Scheffler for insights on
stochastic process limits for CTRMs, and Gurtek Gill who helped create
the MittagLeffleR R-package.

\appendix

\section{Validating our inference method on simulated
data}\label{validating-our-inference-method-on-simulated-data}

To test our inference method via stability plots, we have simulated
10000 independent waiting time and magnitude pairs \((W_k, J_k)\) (see
upper panel in Figure \ref{fig:thresholdedBursty}). In order to have
exact analytical values available for \(\beta\) and \(\sigma_0\), a
distribution for \(W_k\) needs to be chosen for which \(b(n)\) from
\eqref{eq:stability} is known. If we choose \(W_k \stackrel{d}{=} D\),
where \(D\) is as in \eqref{eq:stability}, then due to the stability
property we have the \emph{equality} of distribution
\(W_1 + \ldots + W_n \stackrel{d}{=} b(n) D\), for
\(b(n) = n^{1/\beta}\). Using the parametrisation of Samorodnitsky and
Taqqu (1994), a few lines of calculation (see e.g.~the vignette on
parametrisation in Gill and Straka (2017)) show that \(D\) must have the
stable distribution \(S_\beta(\cos(\pi \beta/2)^{1/\beta}, +1, 0)\),
which is implemented in the R package \texttt{stabledist} by Wuertz,
Maechler, and members. (2016).

\begin{figure}
\includegraphics[width=\textwidth]{article_springer_files/figure-latex/simulated-example-1} \caption{Tail and scale estimates for simulated data, with waiting times drawn from the stable distribution $S_\beta(\cos(\pi \beta/2)^{1/\beta}, +1, 0)$ with $\beta = 0.8$. Dashed lines are 95\% confidence intervals, dotted lines are the known theoretical values ($0.8$ and $10000^{1/0.8}$). \label{fig:sim}}\label{fig:simulated-example}
\end{figure}

By the Theorem, the distribution of \(T(\ell)\) is approximately \[
{\rm ML}(\beta, p^{-1/\beta}) 
= {\rm ML}(\beta, k^{-1/\beta} n^{1/\beta}),
\] which means \(\sigma_0 = n^{1/\beta}\). The distribution of \(J_k\)
is irrelevant for the inference on \(\beta\) and \(\sigma_0\) (we have
chosen unit exponential random variables). Figure \ref{fig:sim} displays
plots of \(\hat \beta(\ell)\) and \(\hat \sigma(\ell)\) vs. \(k\);
recall that \(k\) is the index of the order statistics of \(J_k\) at
which the threshold \(\ell\) is placed. Dotted lines show 95\%
confidence intervals, which are derived from the asymptotic normality of
the log-moments estimators (Cahoy 2013) and the \(\delta\)-method (Gill
and Straka 2017). The dashed lines show the actual values of \(\beta\)
resp.~\(\sigma_0\), showing that our inference method identifies the
parameters correctly.

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\hypertarget{ref-Aban06}{}
Aban, Inmaculada B, Mark M Meerschaert, and Anna K Panorska. 2006.
``Parameter Estimation for the Truncated Pareto Distribution.'' \emph{J.
Am. Stat. Assoc.} 101 (473): 270--77.
doi:\href{https://doi.org/10.1198/016214505000000411}{10.1198/016214505000000411}.

\hypertarget{ref-Anderson1987}{}
Anderson, Kevin K. 1987. ``Limit Theorems for General Shock Models with
Infinite Mean Intershock Times.'' \emph{J. Appl. Probab.} 24 (2):
449--56. \url{http://www.jstor.org/stable/3214268}.

\hypertarget{ref-Bagrow2013}{}
Bagrow, James P., and Dirk Brockmann. 2013. ``Natural emergence of
clusters and bursts in network evolution.'' \emph{Phys. Rev. X} 3 (2):
1--6.
doi:\href{https://doi.org/10.1103/PhysRevX.3.021016}{10.1103/PhysRevX.3.021016}.

\hypertarget{ref-Barabasi2005}{}
Barabási, Albert László. 2005. ``The origin of bursts and heavy tails in
human dynamics.'' \emph{Nature} 435 (May): 207--11.
doi:\href{https://doi.org/10.1038/nature03459}{10.1038/nature03459}.

\hypertarget{ref-Basrak2014}{}
Basrak, Bojan, and Drago Špoljarić. 2015. ``Extremes of random variables
observed in renewal times.'' \emph{Stat. Probab. Lett.} 97. Elsevier
B.V.: 216--21.
doi:\href{https://doi.org/10.1016/j.spl.2014.11.025}{10.1016/j.spl.2014.11.025}.

\hypertarget{ref-beirlantBook}{}
Beirlant, Jan, Yuri Goegebeur, Johan Segers, and Jozef Teugels. 2006.
\emph{Statistics of extremes: theory and applications}. John Wiley \&
Sons.

\hypertarget{ref-Benson2007}{}
Benson, David A, Rina Schumer, and Mark M Meerschaert. 2007.
``Recurrence of extreme events with power-law interarrival times.''
\emph{Geophys. Res. Lett.} 34 (l16404): DOI:10.1029/2007GL030767.
doi:\href{https://doi.org/10.1029/2007GL030767}{10.1029/2007GL030767}.

\hypertarget{ref-Cahoy2013}{}
Cahoy, Dexter O. 2013. ``Estimation of Mittag-Leffler Parameters.''
\emph{Commun. Stat. - Simul. Comput.} 42 (2): 303--15.
doi:\href{https://doi.org/10.1080/03610918.2011.640094}{10.1080/03610918.2011.640094}.

\hypertarget{ref-ColesBook}{}
Coles, S. 2001. \emph{An Introduction to Statistical Modelling of
Extreme Values}. London: Springer-Verlag.

\hypertarget{ref-HXRBS}{}
Dennis, Brian R, L E Orwig, G S Kennard, G J Labow, R A Schwartz, A R
Shaver, and A K Tolbert. 1991. ``The complete Hard X Ray Burst
Spectrometer event list, 1980-1989.''
\url{https://umbra.nascom.nasa.gov/smm/hxrbs.html}.

\hypertarget{ref-Esary1973}{}
Esary, J. D., and A. W. Marshall. 1973. ``Shock Models and Wear
Processes.''
doi:\href{https://doi.org/10.1214/aop/1176996891}{10.1214/aop/1176996891}.

\hypertarget{ref-ferro2003inference}{}
Ferro, Christopher AT, and Johan Segers. 2003. ``Inference for Clusters
of Extreme Values.'' \emph{Journal of the Royal Statistical Society:
Series B (Statistical Methodology)} 65 (2). Wiley Online Library:
545--56.

\hypertarget{ref-MittagLeffleR}{}
Gill, Gurtek, and Peter Straka. 2017. \emph{MittagLeffleR: Using the
Mittag-Leffler Distributions in R}.
\url{https://strakaps.github.io/MittagLeffleR/}.

\hypertarget{ref-Gut1999}{}
Gut, Allan, and Jürg Hüsler. 1999. ``Extreme Shock Models.''
\emph{Extremes}, no. 1983: 295--307.
\url{http://link.springer.com/article/10.1023/A:1009959004020}.

\hypertarget{ref-Haubold11}{}
Haubold, H.J., A. M. Mathai, and R. K. Saxena. 2011. ``Mittag-Leffler
Functions and Their Applications.'' \emph{J. Appl. Math.} 2011: 1--51.
doi:\href{https://doi.org/10.1155/2011/298628}{10.1155/2011/298628}.

\hypertarget{ref-hawkes1971point}{}
Hawkes, Alan G. 1971. ``Point spectra of some mutually exciting point
processes.'' \emph{J. R. Stat. Soc. Ser. B Stat. Methodol.} JSTOR,
438--43.

\hypertarget{ref-Hees16}{}
Hees, Katharina, and Hans-Peter Scheffler. 2016. ``On joint sum/max
stability and sum/max domains of attraction,'' June, 1--31.
\url{http://arxiv.org/abs/1606.03109}.

\hypertarget{ref-Hees17}{}
---------. 2017. ``Coupled Continuous Time Random Maxima.''
\emph{Extremes}, no. June (September). Extremes: 1--24.
doi:\href{https://doi.org/10.1007/s10687-017-0304-6}{10.1007/s10687-017-0304-6}.

\hypertarget{ref-Hsing88}{}
Hsing, T, J Hüsler, and M R Leadbetter. 1988. ``On the Exceedance Point
Process for a Stationary Sequence'' 78: 97--112.

\hypertarget{ref-Karsai2012}{}
Karsai, Márton, Kimmo Kaski, Albert László Barabási, and János Kertész.
2012. ``Universal features of correlated bursty behaviour.'' \emph{Sci.
Rep.} 2.
doi:\href{https://doi.org/10.1038/srep00397}{10.1038/srep00397}.

\hypertarget{ref-Karsai2011}{}
Karsai, Márton, M. Kivelä, R. K. Pan, K. Kaski, J. Kertész, Albert
László Barabási, and J. Saramäki. 2011. ``Small but slow world: How
network topology and burstiness slow down spreading.'' \emph{Phys. Rev.
E - Stat. Nonlinear, Soft Matter Phys.} 83: 1--4.
doi:\href{https://doi.org/10.1103/PhysRevE.83.025102}{10.1103/PhysRevE.83.025102}.

\hypertarget{ref-Kratz96}{}
Kratz, Marie, and Sidney I. Resnick. 1996. ``The qq-estimator and heavy
tails.'' \emph{Commun. Stat. Part C Stoch. Model.} 12 (4): 699--724.
doi:\href{https://doi.org/10.1080/15326349608807407}{10.1080/15326349608807407}.

\hypertarget{ref-Laskin2003}{}
Laskin, Nick. 2003. ``Fractional Poisson process.'' \emph{Commun.
Nonlinear Sci. Numer. Simul.} 8 (3-4): 201--13.
doi:\href{https://doi.org/10.1016/S1007-5704(03)00037-6}{10.1016/S1007-5704(03)00037-6}.

\hypertarget{ref-Lee15}{}
Lee, J., Y. Fan, and S. A. Sisson. 2015. ``Bayesian threshold selection
for extremal models using measures of surprise.'' \emph{Comput. Stat.
Data Anal.} 85. Elsevier B.V.: 84--99.
doi:\href{https://doi.org/10.1016/j.csda.2014.12.004}{10.1016/j.csda.2014.12.004}.

\hypertarget{ref-MeerschaertSikorskii}{}
Meerschaert, Mark M, and Alla Sikorskii. 2012. \emph{Stochastic Models
for Fractional Calculus}. Vol. 43. Walter de Gruyter.

\hypertarget{ref-MeerschaertStoev08}{}
Meerschaert, Mark M, and Stilian A Stoev. 2008. ``Extremal limit
theorems for observations separated by random power law waiting times.''
\emph{J. Stat. Plan. Inference} 139 (7): 2175--88.
doi:\href{https://doi.org/10.1016/j.jspi.2008.10.005}{10.1016/j.jspi.2008.10.005}.

\hypertarget{ref-Meerschaert2010b}{}
Meerschaert, Mark M, Erkan Nane, and P. Vellaisamy. 2011. ``The
fractional Poisson process and the inverse stable subordinator.''
\emph{Electron. J. Probab.} 16: 1600--1620.
doi:\href{https://doi.org/10.1214/EJP.v16-920}{10.1214/EJP.v16-920}.

\hypertarget{ref-MeerschaertRoyQin}{}
Meerschaert, Mark M., Parthanil Roy, and Qin Shao. 2012. ``Parameter
estimation for exponentially tempered power law distributions.''
\emph{Commun. Stat. - Theory Methods} 41 (10): 1839--56.
doi:\href{https://doi.org/10.1080/03610926.2011.552828}{10.1080/03610926.2011.552828}.

\hypertarget{ref-Min2010}{}
Min, Byungjoon, K. I. Goh, and Alexei Vazquez. 2011. ``Spreading
dynamics following bursty human activity patterns.'' \emph{Phys. Rev. E
- Stat. Nonlinear, Soft Matter Phys.} 83 (3): 2--5.
doi:\href{https://doi.org/10.1103/PhysRevE.83.036102}{10.1103/PhysRevE.83.036102}.

\hypertarget{ref-Oliveira2005}{}
Oliveira, J, and Albert László Barabási. 2005. ``Darwin and Einstein
correspondence patterns.'' \emph{Nature} 437 (October): 1251.
doi:\href{https://doi.org/10.0138/4371251a}{10.0138/4371251a}.

\hypertarget{ref-Omi2011}{}
Omi, Takahiro, and Shigeru Shinomoto. 2011. ``Optimizing Time Histograms
for Non-Poissonian Spike Trains.'' \emph{Neural Comput.} 23 (12):
3125--44.
doi:\href{https://doi.org/10.1162/NECO_a_00213}{10.1162/NECO\_a\_00213}.

\hypertarget{ref-R}{}
R Core Team. 2018. \emph{R: A Language and Environment for Statistical
Computing}. Vienna, Austria: R Foundation for Statistical Computing.
\url{https://www.R-project.org/}.

\hypertarget{ref-Resnick97}{}
Resnick, Sidney I. 1997. ``Heavy tail modeling and teletraffic data.''
\emph{Ann. Stat.} 25 (5): 1805--49.
doi:\href{https://doi.org/10.1214/aos/1069362376}{10.1214/aos/1069362376}.

\hypertarget{ref-SamorodnitskyTaqqu}{}
Samorodnitsky, Gennady, and Murad S Taqqu. 1994. \emph{Stable
Non-Gaussian Random Processes: Stochastic Models with Infinite
Variance}. Stochastic Modeling. London: Chapman Hall.

\hypertarget{ref-Scarrott12}{}
Scarrott, Carl, and Anna Macdonald. 2012. ``A REVIEW OF EXTREME VALUE
THRESHOLD ESTIMATION AND UNCERTAINTY QUANTIFICATION.'' \emph{REVSTAT --
Stat. J.} 10 (1): 33--60.

\hypertarget{ref-Sumita1983}{}
Shanthikumar, J. George, and Ushio Sumita. 1983. ``General shock models
associated with correlated renewal sequences.'' \emph{J. Appl. Probab.}
20 (3): 600--614. \url{http://www.jstor.org/stable/3213896}.

\hypertarget{ref-Sumita1984}{}
---------. 1984. ``Distribution Properties of the System Failure Time in
a General Shock Model.'' \emph{Adv. Appl. Probab.} 16 (2): 363--77.
\url{http://www.jstor.org/stable/1427074}.

\hypertarget{ref-Sumita1985}{}
---------. 1985. ``A class of correlated cumulative shock models.''
\emph{Adv. Appl. Probab.} 17 (2): 347--66.
\url{http://www.jstor.org/stable/1427145}.

\hypertarget{ref-Silvestrov2002a}{}
Silvestrov, Dmitrii S. 2002. \emph{Limit Theorems for Randomly Stopped
Stochastic Processes}. Springer (Berlin, Heidelberg).

\hypertarget{ref-ST04}{}
Silvestrov, Dmitrii S, and Jozef L. Teugels. 2004. ``Limit theorems for
mixed max-sum processes with renewal stopping.'' \emph{Ann. Appl.
Probab.} 14 (4): 1838--68.
doi:\href{https://doi.org/10.1214/105051604000000215}{10.1214/105051604000000215}.

\hypertarget{ref-Vajna2013}{}
Vajna, Szabolcs, Bálint Tóth, and János Kertész. 2013. ``Modelling
bursty time series.'' \emph{New J. Phys.} 15 (10): 103023.
doi:\href{https://doi.org/10.1088/1367-2630/15/10/103023}{10.1088/1367-2630/15/10/103023}.

\hypertarget{ref-Vasquez2006}{}
Vasquez, a, J G Oliveira, Z Dezso, K-I Goh, I Kondor, and Albert László
Barabási. 2006. ``Modeling bursts and heavy tails in human dynamics.''
\emph{Phys. Rev. E} 73: 361271--3612718.

\hypertarget{ref-Vazquez2007}{}
Vazquez, Alexei, Balázs Rácz, András Lukács, and Albert László Barabási.
2007. ``Impact of non-poissonian activity patterns on spreading
processes.'' \emph{Phys. Rev. Lett.} 98 (APRIL): 1--4.
doi:\href{https://doi.org/10.1103/PhysRevLett.98.158702}{10.1103/PhysRevLett.98.158702}.

\hypertarget{ref-stabledist}{}
Wuertz, Diethelm, Martin Maechler, and Rmetrics core team members. 2016.
\emph{Stabledist: Stable Distribution Functions}.
\url{https://CRAN.R-project.org/package=stabledist}.

\bibliographystyle{spbasic}
\bibliography{CTRMstats.bib}

\end{document}

### 2018-04-24 article_springer/article_springer.Rmd

@@
 statistical behaviour in both models. Observations below a threshold are 
-commonly discarded in Extreme Value Theory; likewise, the CTRE model
+commonly discarded in Extreme Value Theory (POT approach); likewise, the CTRE model
 interprets these observations as noise and filters them out.

### 2018-04-24 article_springer/article_springer.Rmd
changes for submission

--- 2018-04-24 article_springer/article_springer.Rmd
@@
 
-```{r fig:QQ-plots, fig.cap="Pareto vs.
+```{r QQ-plots, fig.cap="Pareto vs.
 Mittag-Leffler distribution, both with same tail exponent 0.8.
@@
 
-```{r solar-flare-tail-scale, message=FALSE, fig.height=4.5, fig.width=8, fig.cap="\\label{fig:flares}Stability plots for the tail and scale parameter of the Mittag-Leffler distribution of the Solar Flare dataset.
+```{r solar-flare-tail-scale, message=FALSE, fig.cap="\\label{fig:flares}Stability plots for the tail and scale parameter of the Mittag-Leffler distribution of the Solar Flare dataset.
 Dotted horizontal lines are at $\\beta = 0.85$ and $\\sigma_0 = 3 \\times 10^7$ seconds $\\approx 0.95$ years."}
@@
 
-```{r flare-diagnostics-2, fig.height=7, fig.cap="Diagnostic plots for the solar flare data: empirical copula and QQ Plot. \\label{fig:flare-diagnostics-2}"}
-par(mfrow = c(2,2))
+```{r flare-diagnostics-2, fig.cap="Diagnostic plots for the solar flare data: empirical copula and QQ Plot. \\label{fig:flare-diagnostics-2}"}
+par(mfrow=c(1,2))
 empcopula(flares_ctre)
@@
 
-```{r hazard, fig.height=7, fig.cap="Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\\beta = 0.8$, $\\sigma_0 = 1$).
+```{r hazard, fig.height=3.5 , fig.cap="Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\\beta = 0.8$, $\\sigma_0 = 1$).
 Right: Hazard rate depending on tail parameter $\\beta$.\\label{fig:hazard}"}
@@
 xx <- exp(seq(from = log(from), to = log(to), length.out = 100))
-par(mfrow = c(2,2))
+par(mfrow=c(1,2))
 plot(xx, rep(1, length(xx)), ylim = c(0.001,1), type = 'n', log = 'xy', 
@@
 and $\beta$ the exponent of the power law. 
-
-The "anomalous" scaling behaviour in the bursty setting entails two 
+This "anomalous" scaling behaviour in the bursty setting entails two 
 phenomena: 
@@
 This assumption is likely sufficient but not necessary for our limit theorem to hold. 
-Morevoer, any data below a (minimum) threshold $\ell_0$ is discarded in 
-our inference procedure, and hence need not satisfy the i.i.d. assumption.
+Moreover, any data below a (minimum) threshold $\ell_0$ is discarded for 
+CTREs, and hence need not satisfy the i.i.d. assumption.
 For the purposes of statistical inference, we merely require that the 
@@
 
-For some bursty time series, the current CTRE model may be too rigid, 
+The bursty CTRE approach to model "non-Poissonian" threshold crossing times
+should be contrasted with the (now standard) approach of clusters of 
+extremes, see e.g. @ferro2003inference. In this approach, i.i.d. event 
+sequences of magnitudes are generalized to stationary sequences of
+event magnitudes (subject to a mixing condition). The two approaches are 
+fundamentally different: A clustering model assumes that each event 
+belongs to one particular (latent) group of events. For bursts, however,
+the aim is to identify an underlying scale-free pattern in the event 
+dynamics, which is often characteristic of complex systems.
+It is an interesting open problem to develop quality criteria, based
+e.g. on measures of surprise [@Lee15], which guide an applied statistician in 
+the choice between a clustering and a CTRE approach for a particular 
+problem. Moreover, we believe it may be possible to unify the two approaches
+by considering CTREs based on MRPs with a _stationary_, rather than 
+i.i.d., sequence of magnitudes.
+
+Finally, a purely scale-free pattern for event times may be too rigid an 
+assumption for some bursty time series, 
 because often the heavy-tailed character of the inter-arrival time
-distribution does not hold at all time scales; rather, it often applies at 
-short and intermediate time scales, and is truncated or tempered 
-(reverting to an exponential distribution) at 
-very long time scales, see e.g. @MeerschaertRoyQin and @Aban06. 
+distribution does not hold at all time scales; rather, it applies at 
+short and intermediate time scales, and is truncated (or tempered, 
+reverting to an exponential distribution) at 
+very long time scales [see e.g. @MeerschaertRoyQin; and @Aban06]. 
 In such situations, a "tempered" Mittag-Leffler distribution may provide 

### 2018-04-24 article_springer/article_springer.tex
changes for submission

@@
 behaviour in both models. Observations below a threshold are commonly
-discarded in Extreme Value Theory; likewise, the CTRE model interprets
-these observations as noise and filters them out.
+discarded in Extreme Value Theory (POT approach); likewise, the CTRE
+model interprets these observations as noise and filters them out.
 
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{article_springer_files/figure-latex/fig:QQ-plots-1} \caption{Pareto vs.
+\includegraphics[width=\textwidth]{article_springer_files/figure-latex/QQ-plots-1} \caption{Pareto vs.
 Mittag-Leffler distribution, both with same tail exponent 0.8.
@@
 Centre column: dynamic QQ-Estimator plots.
-Right column: a usual QQ-Plot based on Mittag-Leffler quantiles.\label{fig:QQ-plots}}\label{fig:fig:QQ-plots}
+Right column: a usual QQ-Plot based on Mittag-Leffler quantiles.\label{fig:QQ-plots}}\label{fig:QQ-plots}
 \end{figure}
@@
 distribution has more probability near \(0\) than the Pareto
-distribution, severely biasing the estimator downwards (0.62). Even by
+distribution, severely biasing the estimator downwards (0.67). Even by
 looking at different cutoffs via the dynamic QQ-estimator plot
@@
 exceedance times, \(p\) is the fraction of magnitudes above the
-threshold, and \(\beta\) the exponent of the power law.
-
-The ``anomalous'' scaling behaviour in the bursty setting entails two
+threshold, and \(\beta\) the exponent of the power law. This
+``anomalous'' scaling behaviour in the bursty setting entails two
 phenomena: i) a heavy tail of the interarrival time distribution of
@@
 theorem to hold. Moreover, any data below a (minimum) threshold
-\(\ell_0\) is discarded in our inference procedure, and hence need not
-satisfy the i.i.d. assumption. For the purposes of statistical
-inference, we merely require that the inter-threshold-crossing times are
-i.i.d. However, it might be interesting to generalize our theory to the
-case of a stationary sequence of magnitudes. In case of fixed times
-between observations, the distribution of the sequence of (correctly
-normalized) inter-exceedance times converges under certain (mixing)
-conditions to a mixture of an exponential distribution and a point mass
-in zero (Ferro and Segers 2003). Hence, this also leads to a model for
-extreme events that occur in cluster. Allowing for both, dependence
-between the magnitudes and heavy tailed waiting times, could maybe
-further improve modelling of extreme events like earthquakes, that occur
-in clusters.
+\(\ell_0\) is discarded for CTREs, and hence need not satisfy the i.i.d.
+assumption. For the purposes of statistical inference, we merely require
+that the inter-threshold-crossing times are i.i.d.
 
-For some bursty time series, the current CTRE model may be too rigid,
-because often the heavy-tailed character of the inter-arrival time
-distribution does not hold at all time scales; rather, it often applies
-at short and intermediate time scales, and is truncated or tempered
-(reverting to an exponential distribution) at very long time scales, see
-e.g. Mark M. Meerschaert, Roy, and Shao (2012) and Aban, Meerschaert,
-and Panorska (2006). In such situations, a ``tempered'' Mittag-Leffler
-distribution may provide a more realistic fit, which we aim to introduce
-in follow-up work.
+The bursty CTRE approach to model ``non-Poissonian'' threshold crossing
+times should be contrasted with the (now standard) approach of clusters
+of extremes, see e.g. Ferro and Segers (2003). In this approach, i.i.d.
+event sequences of magnitudes are generalized to stationary sequences of
+event magnitudes (subject to a mixing condition). The two approaches are
+fundamentally different: A clustering model assumes that each event
+belongs to one particular (latent) group of events. For bursts, however,
+the aim is to identify an underlying scale-free pattern in the event
+dynamics, which is often characteristic of complex systems. It is an
+interesting open problem to develop quality criteria, based e.g.~on
+measures of surprise (Lee, Fan, and Sisson 2015), which guide an applied
+statistician in the choice between a clustering and a CTRE approach for
+a particular problem. Moreover, we believe it may be possible to unify
+the two approaches by considering CTREs based on MRPs with a
+\emph{stationary}, rather than i.i.d., sequence of magnitudes.
+
+Finally, a purely scale-free pattern for event times may be too rigid an
+assumption for some bursty time series, because often the heavy-tailed
+character of the inter-arrival time distribution does not hold at all
+time scales; rather, it applies at short and intermediate time scales,
+and is truncated (or tempered, reverting to an exponential distribution)
+at very long time scales (see e.g. Mark M. Meerschaert, Roy, and Shao
+2012; and Aban, Meerschaert, and Panorska 2006). In such situations, a
+``tempered'' Mittag-Leffler distribution may provide a more realistic
+fit, which we aim to introduce in follow-up work.
 

### 2018-04-24 article_springer/article_springer_submissionfile.tex
changes for submission

--- 2018-04-24 article_springer/article_springer.tex
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{article_springer_files/figure-latex/QQ-plots-1} \caption{Pareto vs.
+\includegraphics[width=\textwidth]{article_springer_files/figure-latex/fig:QQ-plots-1} \caption{Pareto vs.
 Mittag-Leffler distribution, both with same tail exponent 0.8.
@@
 Centre column: dynamic QQ-Estimator plots.
-Right column: a usual QQ-Plot based on Mittag-Leffler quantiles.\label{fig:QQ-plots}}\label{fig:QQ-plots}
+Right column: a usual QQ-Plot based on Mittag-Leffler quantiles.\label{fig:QQ-plots}}\label{fig:fig:QQ-plots}
 \end{figure}
@@
 the MittagLeffleR R-package.
+\newpage
+
+\section*{Appendix}
 
@@
 
-\begin{figure}
+\begin{figure}[b]
 \includegraphics[width=\textwidth]{article_springer_files/figure-latex/simulated-example-1} \caption{Tail and scale estimates for simulated data, with waiting times drawn from the stable distribution $S_\beta(\cos(\pi \beta/2)^{1/\beta}, +1, 0)$ with $\beta = 0.8$.
@@
 
-\section*{References}\label{references}
-\addcontentsline{toc}{section}{References}
+%\section*{References}\label{references}
+%\addcontentsline{toc}{section}{References}
+\bibliography{CTRMstats}
+\bibliographystyle{spbasic}
 
@@
 
+\pagebreak
+
 \hypertarget{ref-MeerschaertStoev08}{}
@@
 
-\bibliographystyle{spbasic}
-\bibliography{CTRMstats.bib}
-
 \end{document}

### 2018-05-08 article_springer/article_springer.Rmd
change fig height for nicer html rendering

@@
     Research (BMBF). 
+authors:
 
-authors: 
 - name: "Katharina Hees"
@@
   email: hees@statistik.uni-dortmund.de
-
 - name: "Smarak Nayak"
@@
   email: smarak.nayak@nab.com.au
-
 - name: "Peter Straka*"
@@
   email: p.straka@unsw.edu.au 
-
 authorrunning: K. Hees, S. Nayak & P. Straka
-
 keywords:
@@
 - peaks over threshold
-
 abstract: |
@@
   the predictive distribution for the time until the next extreme event. 
-
 bibliography: CTRMstats.bib
-
 output: 
+  html_document: default
   rticles::springer_article: 
     fig_caption: yes
-
 params:
@@
   n: 10000
-
 preamble: |
@@
 
-```{r QQ-plots, fig.cap="Pareto vs.
+```{r fig:QQ-plots, fig.cap="Pareto vs.
 Mittag-Leffler distribution, both with same tail exponent 0.8.
@@
 
-```{r solar-flare-tail-scale, message=FALSE, fig.cap="\\label{fig:flares}Stability plots for the tail and scale parameter of the Mittag-Leffler distribution of the Solar Flare dataset.
+```{r solar-flare-tail-scale, message=FALSE, fig.height=4.5, fig.width=8, fig.cap="\\label{fig:flares}Stability plots for the tail and scale parameter of the Mittag-Leffler distribution of the Solar Flare dataset.
 Dotted horizontal lines are at $\\beta = 0.85$ and $\\sigma_0 = 3 \\times 10^7$ seconds $\\approx 0.95$ years."}
@@
 
-```{r flare-diagnostics-2, fig.cap="Diagnostic plots for the solar flare data: empirical copula and QQ Plot. \\label{fig:flare-diagnostics-2}"}
-par(mfrow=c(1,2))
+```{r flare-diagnostics-2, fig.height=4, fig.cap="Diagnostic plots for the solar flare data: empirical copula and QQ Plot. \\label{fig:flare-diagnostics-2}"}
+par(mfrow = c(1,2))
 empcopula(flares_ctre)
@@
 
-```{r hazard, fig.height=3.5 , fig.cap="Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\\beta = 0.8$, $\\sigma_0 = 1$).
+```{r hazard, fig.height=4, fig.cap="Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\\beta = 0.8$, $\\sigma_0 = 1$).
 Right: Hazard rate depending on tail parameter $\\beta$.\\label{fig:hazard}"}
@@
 xx <- exp(seq(from = log(from), to = log(to), length.out = 100))
-par(mfrow=c(1,2))
+par(mfrow = c(1,2))
 plot(xx, rep(1, length(xx)), ylim = c(0.001,1), type = 'n', log = 'xy', 

### 2018-05-08 article_springer/index.Rmd
set up for rmarkdown::render_site()

--- 2018-05-08 article_springer/article_springer.Rmd
@@
 output: 
-  html_document: default
+  html_document: 
+    toc: true
+    toc_float: true
+    theme: journal
   rticles::springer_article: 
@@
 
-```{r get-rticles, eval=FALSE, include=FALSE, cache=TRUE}
-# use this rticles version: 
-devtools::install_github("rstudio/rticles")
-# use the newest MittagLeffleR version:
-devtools::install_github("UNSW-MATH/MittagLeffleR")
-library(MittagLeffleR)
-devtools::install_github("UNSW-MATH/CTRE")
-library(CTRE)
-```
-
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(
-  echo = FALSE,
-  cache = TRUE,
-  message = FALSE,
-  fig.height = 3, out.width = '\\textwidth'
-  )
-library(CTRE)
-library(MittagLeffleR)
-library(magrittr)
-```
-
-# Introduction
-
-Time series displaying temporally inhomogeneous behaviour have received 
-strong interest in the recent statistical physics literature 
-[@Barabasi2005; @Oliveira2005; @Vasquez2006; @Vazquez2007; @Omi2011; 
-@Min2010; @Karsai2011; @Bagrow2013]. They have been observed in the context 
-of earthquakes, sunspots, neuronal activity and human communication [see 
-@Karsai2012; @Vajna2013; @MeerschaertStoev08 for a list of references]. 
-Such time series exhibit high activity in some 'bursty' intervals, which 
-alternate with other, quiet intervals.  Although several mechanisms are 
-plausible explanations for bursty behaviour (most prominently self-exciting
-point process by @hawkes1971point), there seems to be one salient feature 
-which very typically indicates the departure from temporal homogeneity: a 
-heavy-tailed distribution of waiting times [@Vasquez2006; @Karsai2012; 
-@Vajna2013]. As we show below in simulations, a simple renewal process with
-heavy-tailed waiting times can capture this type of dynamics. For many 
-systems, the renewal property is appropriate; a simple test of the absence 
-of correlations in a succession of waiting times can be undertaken by 
-randomly reshuffling the waiting times [@Karsai2012].
-
-Often a magnitude, or mark can be assigned to each event in the renewal process, 
-such as for earthquakes, solar flares or neuron voltages. 
-The Peaks-Over-Threshold model [POT, see e.g. @ColesBook] applies a
-threshold to the magnitudes, and fits a Generalized Pareto distribution 
-to the threshold exceedances. 
-A commonly made assumption in POT models is that times between 
-events are either fixed 
-or light-tailed, and this entails that the 
-threshold crossing times form a Poisson process [@Hsing88]. 
-Then as one increases the threshold and thus decreases the threshold 
-crossing probability $p$, the Poisson process is rarefied, i.e. its 
-intensity decreases _linearly_ with $p$ [see e.g. @beirlantBook].
-
-As will be shown below, in the heavy-tailed waiting time scenario threshold 
-crossing times form a _fractional Poisson process_ 
-[@Laskin2003; @Meerschaert2010b], which is a 
-renewal process with Mittag-Leffler distributed waiting times. 
-The family of Mittag-Leffler distributions nests the exponential 
-distribution [@Haubold11], and hence the fractional Poisson process
-generalizes the standard Poisson process. 
-Again as the threshold size increases and the threshold crossing
-probability $p$ decreases, the fractional Poisson process is rarefied: 
-The scale parameter of the Mittag-Leffler inter-arrival times of 
-threshold crossing times increases, but _superlinearly_; 
-see the Theorem below.
-
-Maxima of events which occur according to a renewal process with
-heavy-tailed waiting times have been studied under 
-the names "Continuous Time Random Maxima process" (CTRM) 
-[@Benson2007; @MeerschaertStoev08; @Hees16; @Hees17], 
-"Max-Renewal process" [@Silvestrov2002a; @ST04; @Basrak2014], 
-and "Shock process"
-[@Esary1973; @Sumita1983; @Sumita1984; @Sumita1985; @Anderson1987; @Gut1999].
-The existing literature focuses on probabilistic results surrounding these 
-models. 
-In this work, however, we introduce a method of inference for this type of 
-model, which is seemingly not available in the literature.
-
-We review the marked renewal process in Section 2, and 
-derive a scaling limit theorem for inter-exceedance times in Section 3.
-We give a statistical procedure to estimate model parameters via stability plots 
-in Section 5, but to set the stage we first discuss inference for the 
-Mittag-Leffler distribution in Section 4. 
-(A simulation study of the effectiveness of our statistical procedure is 
-given in the appendix.)
-Diagnostic plots for model criticism are discussed in Section 6. 
-In Section 7, we discuss the memory property of the 
-Mittag-Leffler distribution, and how it affects the predictive distribution 
-for the time until the next threshold crossing event. 
-Section 8 concludes. 
-For all statistical computations we have used R [@R]. 
-All code and data used for the analysis in this article has been organized into 
-an R package `CTRE` (<https://github.com/UNSW-MATH/CTRE>).
-The source code for the figures generated in this manuscript is 
-available online at <https://github.com/UNSW-MATH/bursty-POT>.
-
-# Continuous Time Random Exceedances (CTRE)
-
-As a model for extreme observations, we use a Marked Renewal Process (MRP):
-
-**Definition (MRP):**
-
-: Let $(W,J), (W_1, J_1), (W_2, J_2), \ldots$ be i.i.d. pairs of random 
-variables, where the $W_k > 0$ are interpreted as the *waiting times* 
-and $J_k \in [x_L, x_R]$ as the *event magnitudes* 
-($x_L \in [-\infty, +\infty), x_R \in (-\infty, +\infty]$). 
-If $W$ and $J$ are independent, the Marked Renewal Process is said to be *uncoupled*. 
-\qed
-
-Note that the $k$-th magnitude $J_k$ occurs at time
-$T_k = W_1 + \ldots + W_k$. 
-Based on an MRP, we define the Continuous Time Random Exceedance model
-(CTRE) as follows:
-
-**Definition (CTRE):**
-
-: Given a threshold $\ell \in (x_L, x_R)$, 
-consider the stopping time 
-$$\tau(\ell) := \min\{k: J_k > \ell\},\quad \ell \in (x_L, x_R).$$
-Define the pair of random variables $(X(\ell), T(\ell))$ via 
-$$X(\ell) = J_{\tau(\ell)} - \ell, \quad 
-T(\ell) = \sum_{k=1}^{\tau(\ell)} W_k.$$
-By restarting the MRP at $\tau(\ell)$, inductively define the
-two i.i.d. sequences $T(\ell,n)$ and $X(\ell, n)$, $n \in \mathbb N$, 
-called the "interarrival times" and the "exceedances", respectively.
-The pair sequence $(T(\ell, n), W(\ell, n))_{n \in \mathbb N}$ is called 
-a Continuous Time Random Exceedance model (CTRE). 
-If the underlying MRP is uncoupled, then the CTRE is also called 
-uncoupled. 
-\qed
-
-```{r thresholdedBursty, message=FALSE, fig.height=7, fig.width=9, fig.cap="\\label{fig:thresholdedBursty}Exceedances (red) and Times until Exceedance (durations between blue crosses) for a given threshold $\\ell$ (dashed line)."}
-tail <- params$tail
-n <- params$n 
-sigma <- (cos(pi*tail/2))^(1/tail)
-times <- cumsum(stabledist::rstable(n, tail, 1, sigma, pm=1))
-#times<-cumsum(rpareto(n,tail))
-magnitudes <- extRemes::revd(n, scale = 1, shape = 0)
-sim_ctre <- ctre(data.frame(times, magnitudes)) 
-par(mfrow = c(2,1))
-plot(sim_ctre, p = 0.01, main = "Simulated MRP") 
-flares %>% ctre() %>% plot(p = 0.02, log = 'y', main = "HXRBS data") 
-```
-
-In this article, we restrict ourselves to the uncoupled case, where
-the two sequences $X(\ell, n)_{n \in \mathbb N}$
-and $T(\ell, n)_{n \in \mathbb N}$ are independent.[^1]
-Figure \ref{fig:thresholdedBursty} shows a simulated dataset in the top 
-panel, where $W$ has a stable distribution with tail parameter 
-$\beta =$ `r params$tail` (and skewness $1$ and location $0$), and 
-where $J$ is from a standard Gumbel distribution. In the bottom panel, 
-we plot a time series of solar flare intensities derived from a NASA
-dataset [@HXRBS][^*]. Clearly, the simulated data exhibit long intervals 
-_without any_ events, whereas in the real-world dataset events appear 
-continuously. The threshold exceedances, however, appear to have similar
-statistical behaviour in both models. Observations below a threshold are 
-commonly discarded in Extreme Value Theory (POT approach); likewise, the CTRE model
-interprets these observations as noise and filters them out.
-
-[^1]: To see why, note that $X(\ell)$ is, in distribution, simply equal to 
-  $J | J > \ell$, independent of any waiting time $W_k$.
-
-[^*]: The "complete Hard X Ray Burst Spectrometer event list" 
-is a comprehensive reference for all measurements of the Hard X 
-Ray Burst Spectrometer on NASA's Solar Maximum Mission from the time of 
-launch on Feb 14, 1980 to the end of the mission in Dec 1989. 12,776 
-events were detected, with the "vast 
-majority being solar flares". The list includes the start time, peak time, 
-duration, and peak rate of each event. We have used "start time" as the 
-variable for event times, and "peak rate" as the variable for event 
-magnitudes.
-
-# Scaling limit of Exceedance Times {#sec:scaling}
-
-In this section we state and prove the key theorem, see below.
-For an accessible introduction to regular variation and stable limit theorems, we 
-recommend the book by @MeerschaertSikorskii.
-
-**Theorem:**
-
-: Let the waiting times $J_k$ be in the domain of attraction of a 
-positively skewed sum-stable law with stability parameter $0 < \beta < 1$; 
-more precisely,
-\begin{align} \label{eq:stability}
-\frac{W_1 + \ldots + W_n}{b(n)} \overset{d}{\longrightarrow} D, 
-\quad n \to \infty
-\end{align}
-for a function $b(n)$ which is regularly varying at $\infty$ with 
-parameter $1/\beta$, and where $\mathbf E[\exp(-sD)] = \exp(-s^\beta)$. 
-Write $p := \mathbf P(J > \ell)$. Then the weak convergence
-$$
-\frac{T(\ell)} {b(1/p)} \to W_\beta \quad \text{ as } \quad \ell \uparrow x_R
-$$
-holds, where the Mittag-Leffler random variable $W_\beta$ is defined on 
-the positive real numbers via 
-$$
-\mathbf E[\exp(-sW_\beta)] = \frac{1}{1+s^\beta}.
-$$
-\qed
-
-\noindent For a scale parameter $\sigma > 0$, we write 
-${\rm ML}(\beta, \sigma)$ for the distribution of $\sigma W_\beta$. 
-The Mittag-Leffler distribution with parameter $\beta \in (0,1]$ is 
-a heavy-tailed positive distribution for $\beta < 1$, with infinite mean. 
-However, as $\beta \uparrow 1$, ${\rm ML}(\beta, \sigma)$ converges 
-weakly to the exponential distribution ${\rm Exp}(\sigma)$.
-This means that although its moments are all infinite, the Mittag-Leffler
-distribution may (if $\beta$ is close to 1) be indistinguishable from the 
-exponential distribution, for the purposes of applied statistics. 
-For a detailed reference on the Mittag-Leffler distribution, see e.g. 
-@Haubold11, and for algorithms, see e.g. the R package `MittagLeffleR`
-[@MittagLeffleR].
-
-#### _Proof of Theorem:_
-We interpret the threshold crossing time $T(\ell)$ as the hitting time of the 
-underlying CTRM (Continuous Time Random Maxima) or "max-renewal process", 
-and then utilize a result by @MeerschaertStoev08. 
-The running maximum process is defined as 
-$$
-M(c) := J_1 \vee \ldots \vee J_{\lfloor c \rfloor},
-$$
-and since we assume that the $J_k$ have a continuous distribution, there exist 
-norming functions $a(c)$ and $d(c)$ such that 
-$$
-\mathbf P\left[ \frac{M(c) - d(c)}{a(c)} \le \ell^* \right] 
-\longrightarrow F(\ell^*), \quad t \to \infty
-$$
-where $F$ is a generalized extreme value distribution, and $\ell^*$ is any 
-value from the support of $F$. 
-The CTRM process is then defined via 
-$$
-V(t) = M(N(t)), \quad t \ge 0
-$$
-where $N(t)$ is the renewal process associated with the waiting times 
-$W_k$: 
-$$
-N(t) = \max\{n: W_1 + \ldots + W_n \le t\}.
-$$
-Now a key observation is that
-$$
-T(\ell) = \inf\{t: V(t) > \ell\}, 
-$$
-and that 
-$$
-T(\ell) > t \quad \text{ if and only if } \quad V(t) \le \ell.
-$$
-By [Theorem 3.1, @MeerschaertStoev08], we have the stochastic process 
-convergence 
-$$
-\frac{V(ct) - d(\tilde b(c))}{a(\tilde b(c))} 
-\stackrel{d}{\longrightarrow} Y(t), \quad t > 0.
-$$
-where $Y(t)$ is a time-changed ("subordinated") extremal process, and where 
-$\tilde b(c)$ is a regularly varying norming function which is
-_inverse_ to $b(c)$, in the sense that 
-$b(\tilde b(c)) \sim c \sim \tilde b(b(c))$.
-
-Without loss of generality, we choose $\ell^*$ such that $F(\ell^*) = 1/e$, 
-and let $\ell = a(\tilde b(c)) \ell^* + d(\tilde b(c))$. 
-We may then calculate 
-$$
-\mathbf P\left[ \frac{T(\ell)}{b(1/p)} > t \right]
-= \mathbf P[T(\ell) > b(1/p) t]
-= \mathbf P[V(ct) \le \ell]
-$$
-where we have substituted $c = b(1/p)$. Moreover 
-$$
-\mathbf P[V(ct) \le \ell]
-= \mathbf P\left[ \frac{V(ct) - d(\tilde b(c))}{a(\tilde b(c))} 
-\le \frac{\ell - d(\tilde b(c))}{a(\tilde b(c))} \right]
-\longrightarrow \mathbf P\left[ Y(t) \le \ell^* \right]
-$$
-Defining the hitting time of level $\ell^*$ by $Y(t)$ as 
-$\xi_{\ell^*} := \inf\{t: Y(t) > \ell^*\}$,
-we then have 
-$$
-P\left[ Y(t) \le \ell^* \right] = \mathbf P[\xi_{\ell^*} > t] 
-= \mathbf P[(-\log F(\ell^*))^{-1/\beta} X^{1/\beta} D > t]
-$$
-by [Proposition 4.2, @MeerschaertStoev08], where $X$ is an exponential 
-random variable with mean $1$. 
-Using [Theorem 19.1, @Haubold11], we see that 
-$X^{1/\beta} D \sim {\rm ML}(\beta, 1)$, concluding the proof. 
-\qed
-
-**Remark:**
-: If $\beta = 1$, the result of the Theorem above is standard, see e.g. 
-Equation (2.2) in @Gut1999.
-
-# Inference for the Mittag-Leffler distribution
-
-```{r fig:QQ-plots, fig.cap="Pareto vs.
-Mittag-Leffler distribution, both with same tail exponent 0.8.
-Top row: solar flare magnitudes data, fitting nicely with a Pareto distribution.
-Bottom row: simulated Mittag-Leffler data.
-Left column: static QQ-Estimator plots, assessing a fit against the Pareto distribution.
-Centre column: dynamic QQ-Estimator plots.
-Right column: a usual QQ-Plot based on Mittag-Leffler quantiles.\\label{fig:QQ-plots}", fig.height=5.5, fig.width=7}
-par(mfrow = c(2,3))
-
-flare_mags <- flares %>% ctre() %>% thin(k=500) %>% magnitudes()
-flares_exponent <- flare_mags %>% qqestplot_static()
-
-flare_mags %>% tea::qqestplot(conf.int = TRUE)
-abline(h = 0.8, lty = 2, col = 2)
-
-flare_mags %>% mlqqplot(tail = 0.8, log = 'xy')
-(flare_mags %>% MittagLeffleR::logMomentEstimator())[1:2] -> MLparams
-flare_mags %>% qqline(distribution = function(p) qml(p, tail = 0.8, scale = MLparams[2]))
-
-ML_data <- MittagLeffleR::rml(500, 0.8)
-ML_exponent <- ML_data %>% qqestplot_static()
-
-ML_exponent2 <- ML_data %>% tea::qqestplot(conf.int = TRUE)
-abline(h=0.8, lty = 2, col = 2)
-
-ML_data %>% mlqqplot(0.8, log = 'xy')
-qqline(ML_data, distribution = function(p) qml(p, 0.8), col = 2)
+```{r, child="article_springer.Rmd"}
 
 ```
-
-Since the Mittag-Leffler distribution is heavy-tailed, many researchers 
-would intuitively give the highest importance to the tail behaviour of the 
-distribution, and 
-estimate the exponent of the tail function with established methods such 
-as the Hill estimator. The QQ-estimator [@Kratz96] is closely related to 
-the Hill estimator and fits a 
-least squares line through the logarithms of the ordered statistics 
-(y-axis) and the corresponding quantiles of the exponential distribution 
-(x-axis). The reciprocal slope is returned as the estimate of the tail 
-exponent.
-For instance, the top-left panel in Figure \ref{fig:QQ-plots} shows the 
-(static) QQ-estimator for the magnitudes of the solar flare data, returning 
-a good fit to a Pareto distribution with tail parameter 
-`r round(flares_exponent, 2)`. The dynamic QQ-estimator plot (top-center panel)
-plots the tail exponent estimate for the largest values at cutoffs 
-varying up to the 5th order statistic, and the region of stability at 
-0.8 indicates a recommended estimate.
-
-However, as described nicely by @Resnick97, the less 
-similar a heavy-tailed distribution is to a Pareto distribution, the less
-useful a Hill or QQ-Plot estimator becomes. 
-The bottom-left panel of Figure \ref{fig:QQ-plots}, for instance, shows the 
-static QQ-estimator plot for $2000$ draws from the Mittag-Leffler distribution with 
-tail parameter $0.8$. The stretched exponential shape means 
-that the Mittag-Leffler distribution has more probability near $0$ than 
-the Pareto distribution, severely biasing the estimator downwards 
-(`r round(ML_exponent, 2)`). 
-Even by looking at different cutoffs via the dynamic QQ-estimator plot 
-(bottom-center panel) one hardly identifies $0.8$ as a clear candidate for 
-a tail parameter estimate.
-
-QQ-estimators, and the closely related Hill estimator, are hence not 
-suitable to detect a heavy-tailed Mittag-Leffler distribution. Moreover, 
-QQ-estimator plots of exponentially distributed data are virtually 
-indistinguishable from the bottom-left panel. This shows that 
-_Mittag-Leffler distributed data may look like exponentially distributed 
-data if examined via a QQ-estimator_.
-
-```{r likelihood-ratio-test}
-flares_arrivals <- flares %>% ctre() %>% thin(k = 500) %>% interarrival()
-mlmle_out <- mlmle(data = flares_arrivals)
-```
-
-Hence if there is some prior expectation that the data are drawn from the 
-Mittag-Leffler distribution
-(as is the the case for threshold exceedance times),
-then we recommend avoiding QQ-estimators and Hill plots altogether, 
-and instead examining QQ-plots directly, on a logarithmic scale 
-(see Figure \ref{fig:QQ-plots}, right column).
-The scale parameter $\sigma$ is irrelevant for a QQ-Plot. 
-The tail parameter $\beta$ can be estimated quickly via the log-moment 
-method by @Cahoy2013, or via maximum likelihood. 
-Both estimators are implemented in `MittagLeffleR` 
-[@MittagLeffleR]. 
-Since the exponential distribution is nested in the Mittag-Leffler 
-family of distributions, a standard likelihood ratio test can be 
-performed, with the exponential distribution as a null model against 
-a Mittag-Leffler distribution as the alternative. 
-As an example, the threshold crossing times for the solar flare dataset
-(Figure \ref{fig:flare-diagnostics-2}, right panel)
-yield a difference in deviance of 
-$\approx$ `r round(2 * (mlmle_out$loglik - mlmle_out$null_loglik))`, 
-which evaluates to a strongly significant $\chi^2_1$ test statistic 
-(p-value = $10^{`r round(log10(mlmle_out$p_value))`}$) for the null
-hypothesis $\beta = 1$.
-
-# Inference on Exceedance times
-
-```{r solar-flare-tail-scale, message=FALSE, fig.height=4.5, fig.width=8, fig.cap="\\label{fig:flares}Stability plots for the tail and scale parameter of the Mittag-Leffler distribution of the Solar Flare dataset.
-Dotted horizontal lines are at $\\beta = 0.85$ and $\\sigma_0 = 3 \\times 10^7$ seconds $\\approx 0.95$ years."}
-thin_flares_ctre <- flares %>% ctre() %>% thin(k = 700)
-par(mfrow=c(1,2))
-MLestimates(thin_flares_ctre, tail = 0.9, scale = 3 * 1E7)
-```
-
-The Theorem in Section \ref{sec:scaling} implies that for a high 
-threshold $\ell$ we may 
-approximate the distribution of $T(\ell)$ with an 
-${\rm ML}(\beta, b(1/p))$ distribution, 
-where $b(\,)$ varies regularly at $\infty$ with parameter $1/\beta$.
-Building on the POT (Peaks Over Threshold) method, we propose the 
-following estimation procedure for the distribution of $T(\ell)$:
-
-1. For a range of thresholds $\ell$ near the largest order statistics, 
-  extract datasets of exceedance times $\{T(\ell, i)\}_i$.
-
-2. For each choice of threshold $\ell$, 
-  fit a Mittag-Leffler distribution to the resulting dataset
-  $\{T(\ell, i)\}_i$. 
-  This results in the estimates $\{\hat\beta(\ell)\}_\ell$ and 
-  $\{\hat \sigma(\ell)\}_\ell$.
-
-3. Plot $\ell$ vs.\ $\hat \beta(\ell)$. As $\ell$ increases towards $x_R$, 
-  $\hat \beta(\ell)$ *stabilizes* around a constant $\hat \beta$. 
-  Use $\hat \beta$ as an estimate for the tail parameter $\beta$ of the
-  Mittag-Leffler distribution of exceedance times.
-
-4. Approximate $p \approx |\{k: J_k > \ell\}| / n$. 
-  Recall that $b(c)$ is regularly varying with parameter $1/\beta$, and 
-  hence has the representation $b(c) = L(c) c^{1/\beta}$ for some 
-  slowly varying function $L(c)$. 
-  Assuming that the variation of $L(c)$ is negligible, we hence 
-  plot $\ell$ vs.\ $p^{1/\hat \beta} \hat \sigma(\ell)$. 
-  Again as $\ell$ increases towards $x_R$, 
-  $p^{1/\hat \beta} \hat \sigma(\ell)$ is expected to stabilize around a constant 
-  $\hat \sigma_0$. 
-  We then use $p^{-1/\hat \beta} \hat \sigma_0$ as an estimate of the scale 
-  parameter of the Mittag-Leffler distribution of exceedance times for
-  the level $\ell$.
-
-The above approach, though theoretically sound, benefits from the following
-practical adjustments (compare with Figure \ref{fig:flares}):
-
-* We choose $\ell$ from the order statistics, i.e. $\ell$ is the $k$-th
-  largest of the observations $X_j$, where $k$ runs from 
-  $k_\text{min}, k_\text{min} + 1, \ldots, k_\text{max}$. 
-  The datasets are then of length $k-1$.
-* We use $k$ rather than $\ell$ for the horizontal axis of our plots. 
-* In Step 4, rather than plotting $p^{1/\hat \beta} \hat \sigma(\ell)$
-  we plot $k^{1/\hat \beta} \hat \sigma(\ell)$. This changes 
-  $\hat \sigma_0$ by the multiplicative constant $n^{1/\hat \beta}$, 
-  but has the advantage that
-  $\hat \sigma_0$ does not change if one pre-processes the data by 
-  removing all observations below a certain threshold.
-
-The estimates $\hat \beta$ and $\hat \sigma_0$ give an estimate of the 
-distribution of exceedance times, dependent on the threshold $\ell$:
-\begin{align*}
-T(\ell) \sim {\rm ML}(\hat \beta, k^{-1/\hat \beta} \hat \sigma_0).
-\end{align*}
-For quick estimates of the Mittag-Leffler parameters we have used 
-the method of log-transformed moments by @Cahoy2013.
-We have verified the validity of our estimation algorithm  via simulations, 
-see the appendix.
-
-# Checking Model Assumptions
-
-```{r flare-diagnostics-1, fig.height=7, fig.cap="Diagnostic plots for the solar flare data: auto-correlation function.\\label{fig:flare-diagnostics-1}"}
-flares_ctre <- flares %>% ctre() %>% thin(k = 150)
-acf(flares_ctre)
-```
-
-```{r flare-diagnostics-2, fig.height=4, fig.cap="Diagnostic plots for the solar flare data: empirical copula and QQ Plot. \\label{fig:flare-diagnostics-2}"}
-par(mfrow = c(1,2))
-empcopula(flares_ctre)
-flares_ctre %>% interarrival() %>% mlqqplot(log = 'xy', tail = 0.8, main = "Mittag-Leffler QQ Plot")
-```
-
-The CTRE model is based on three main assumptions, which are repeated 
-below. For each assumption, we suggest one means of checking if it holds:
-
-i.i.d.:
-: After removing the "noise observations" below the smallest threshold 
-  $\ell_0$, the pair sequence $(T(\ell_0, i), X(\ell_0,i))$ is i.i.d. 
-  An indication if this is true is given 
-  by an auto-correlation plot for the logarithms (to ensure finite moments) 
-  of the two time series.
-
-Uncoupled:
-: Each $T(\ell, i)$ is independent of each $X(\ell, i)$. We propose an empirical copula
-  plot to check for any dependence.
-
-${\rm ML}(\beta, \sigma)$ distribution of $T(\ell, i)$:
-: Apply a cutoff at the lowest threshold $\ell_0$, 
-  extract the threshold crossing times, 
-  and create a QQ Plot for the Mittag-Leffler distribution. 
-  Use a log-Moment estimate of the tail parameter for the theoretical / population 
-  quantiles of the plot.
-
-Figures \ref{fig:flare-diagnostics-1} and \ref{fig:flare-diagnostics-2} 
-show the diagnostic plots for a 
-minimum threshold chosen at the 200th order statistic. 
-There is some residual autocorrelation for the sequence of threshold 
-exceedance times that is not accounted for by the CTRE model. 
-The fit with a Mittag-Leffler distribution ($\beta = 0.8$) is good, 
-though there are signs that the power-law tail tapers off for very large 
-inter-threshold crossing times. 
-There is no apparent dependence between threshold exceedance times and 
-event magnitudes seen in the copula plot.
-
-# Predicting the time of the next threshold crossing
-
-According to Figure \ref{fig:flares}, for a threshold $\ell$ at the $k$-th order 
-statistic, the fitted threshold exceedance time distribution is 
-$$
-T_\ell \sim {\rm ML}(\beta, k^{1/\beta} \sigma_0), 
-$$
-where $\beta = 0.85$ and $\sigma_0 = 3.0 \times 10^7 {\rm sec}$. 
-Unlike the exponential distribution, the Mittag-Leffler distribution is not 
-memoryless, and the probability density of the time $t$ until the next threshold 
-crossing will depend on the time $t_0$ elapsed since the last threshold crossing.
-This density equals 
-$$
-p(t|\beta, \sigma_0, \ell, t_0) = \frac{f(t + t_0 | \beta, k^{1/\beta} \sigma_0)}{\mathbf P[T_\ell > t_0]}
-$$
-where $f(\,\cdot\, | \beta, k^{1/\beta} \sigma_0)$ is the probability density of 
-${\rm ML}(\beta, k^{1/\beta} \sigma_0)$. 
-The more time has passed without a threshold crossing, the more the probability 
-distribution shifts towards larger values for the next crossing
-(see Figure \ref{fig:hazard}, left panel). 
-The hazard rate 
-$$
-h(t) = \frac{f(t| \beta, k^{1/\beta} \sigma_0))}{\int_t^\infty f(\tau| \beta, k^{1/\beta} \sigma_0))\,d\tau}
-$$
-represents the risk of a threshold crossing per unit time, and is a 
-decreasing function for the Mittag-Leffler distribution. 
-The closer $\beta$ is to $1$, the more the hazard rate mimics that of an 
-exponential distribution (a constant function, see Figure \ref{fig:hazard}, 
-right panel).
-
-```{r hazard, fig.height=4, fig.cap="Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\\beta = 0.8$, $\\sigma_0 = 1$).
-Right: Hazard rate depending on tail parameter $\\beta$.\\label{fig:hazard}"}
-tail <- 0.7
-scale <- 1
-t_0 <- c(0, 1, 10)
-from <- 0.1
-to <- 100 * scale
-xx <- exp(seq(from = log(from), to = log(to), length.out = 100))
-par(mfrow = c(1,2))
-plot(xx, rep(1, length(xx)), ylim = c(0.001,1), type = 'n', log = 'xy', 
-     xlab = 't', ylab = 'p')
-for (k in 1:length(t_0)) {
-  cond <- pml(q = t_0[k], tail = tail, scale = scale, lower.tail = FALSE)
-  yy <- dml(x = xx + t_0[k], tail = tail, scale = scale) / cond
-  lines(xx,yy, col = k+1, lty = k)
-}
-legend("bottomleft", c("t_0 = 0", "t_0 = 1", "t_0 = 10"), col = 2:4, lty = 1:3)
-
-betas <- c(0.7, 0.8, 0.95, 0.99)
-t_0 <- 1
-plot(xx, rep(1, length(xx)), ylim = c(0.001,2), type = 'n', log = 'xy', 
-     xlab = 't', ylab = 'h')
-for (k in 1:length(betas)) {
-  yy <- dml(x = xx, tail = betas[k], scale = scale) / pml(
-    q = xx,
-    tail = betas[k],
-    scale = scale,
-    lower.tail = FALSE
-  )
-  lines(xx,yy, col = k+1, lty = k)
-}
-legend("bottomleft", c("beta = 0.7", "beta = 0.8", "beta = 0.95", "beta = 0.99"), col = 2:5, lty = 1:4)
-
-```
-
-It is beyond the scope of the current paper to incorporate parameter 
-uncertainty into our predictive distribution for the next threshold crossing; 
-however, methods as described by @Scarrott12 and @Lee15 are likely 
-to extend to our setting.
-
-# Discussion & Conclusion
-
-We have extended the POT (Peaks over Threshold) model, a mainstay of 
-extreme value theory, to "bursty" time series, which have been studied 
-intensively in statistical physics. 
-Burstiness is characterized by power-law waiting times between events, 
-and we have shown that the Mittag-Leffler distribution arises naturally 
-as a scaling limit for the inter-exceedance times of high thresholds. 
-Moreover, we have derived the following non-linear scaling behaviour: 
-$\sigma \sim p^{-1/\beta}$, 
-where $\sigma$ is the scale parameter of the distribution of threshold 
-exceedance times, 
-$p$ is the fraction of magnitudes above the threshold, 
-and $\beta$ the exponent of the power law. 
-This "anomalous" scaling behaviour in the bursty setting entails two 
-phenomena: 
-i) a heavy tail of the interarrival time distribution of 
-threshold crossings (long rests), and 
-ii) a high propensity for more threshold crossing events immediately after 
-each threshold crossing event (bursts). 
-The Mittag-Leffler distribution captures both phenomena, due to its heavy
-tail as well as its stretched exponential (peaked) asymptotics for small 
-times. 
-It generalizes the exponential distribution, and 
-in the solar flare data example, this generalization 
-is warranted, because the likelihood-ratio test is strongly significant.
-
-When we introduced the CTRE model, we assumed that all events are i.i.d. 
-This assumption is likely sufficient but not necessary for our limit theorem to hold. 
-Moreover, any data below a (minimum) threshold $\ell_0$ is discarded for 
-CTREs, and hence need not satisfy the i.i.d. assumption.
-For the purposes of statistical inference, we merely require that the 
-inter-threshold-crossing times are i.i.d.
-
-The bursty CTRE approach to model "non-Poissonian" threshold crossing times
-should be contrasted with the (now standard) approach of clusters of 
-extremes, see e.g. @ferro2003inference. In this approach, i.i.d. event 
-sequences of magnitudes are generalized to stationary sequences of
-event magnitudes (subject to a mixing condition). The two approaches are 
-fundamentally different: A clustering model assumes that each event 
-belongs to one particular (latent) group of events. For bursts, however,
-the aim is to identify an underlying scale-free pattern in the event 
-dynamics, which is often characteristic of complex systems.
-It is an interesting open problem to develop quality criteria, based
-e.g. on measures of surprise [@Lee15], which guide an applied statistician in 
-the choice between a clustering and a CTRE approach for a particular 
-problem. Moreover, we believe it may be possible to unify the two approaches
-by considering CTREs based on MRPs with a _stationary_, rather than 
-i.i.d., sequence of magnitudes.
-
-Finally, a purely scale-free pattern for event times may be too rigid an 
-assumption for some bursty time series, 
-because often the heavy-tailed character of the inter-arrival time
-distribution does not hold at all time scales; rather, it applies at 
-short and intermediate time scales, and is truncated (or tempered, 
-reverting to an exponential distribution) at 
-very long time scales [see e.g. @MeerschaertRoyQin; and @Aban06]. 
-In such situations, a "tempered" Mittag-Leffler distribution may provide 
-a more realistic fit, which we aim to introduce in follow-up work.
-
-## Acknowledgements {-}
-
-The authors would like to thank Prof. Peter Scheffler for insights on 
-stochastic process limits for CTRMs, and Gurtek Gill who helped create
-the MittagLeffleR R-package.
-
-\appendix
-
-# Validating our inference method on simulated data
-
-To test our inference method via stability plots, we have simulated `r params$n` 
-independent
-waiting time and magnitude pairs $(W_k, J_k)$ (see upper panel in 
-Figure \ref{fig:thresholdedBursty}). In order to have exact 
-analytical values available for $\beta$ and $\sigma_0$, a distribution for 
-$W_k$ needs to be chosen for which $b(n)$ from \eqref{eq:stability} is known. 
-If we choose $W_k \stackrel{d}{=} D$, where $D$ is as in \eqref{eq:stability}, 
-then due to the stability property we have the *equality* of distribution
-$W_1 + \ldots + W_n \stackrel{d}{=} b(n) D$, 
-for $b(n) = n^{1/\beta}$. 
-Using the parametrisation of @SamorodnitskyTaqqu, a few lines of 
-calculation (see e.g. the vignette on parametrisation in @MittagLeffleR) 
-show that $D$ must have the stable distribution 
-$S_\beta(\cos(\pi \beta/2)^{1/\beta}, +1, 0)$, which is 
-implemented in the R package `stabledist` by @stabledist.
-
-```{r make-caption}
-caption = "Tail and scale estimates for simulated data, with waiting times drawn from the stable distribution $S_\\beta(\\cos(\\pi \\beta/2)^{1/\\beta}, +1, 0)$ with $\\beta = 0.8$.
-Dashed lines are 95\\% confidence intervals, dotted lines are the known theoretical values ($0.8$ and $10000^{1/0.8}$).
-\\label{fig:sim}"
-```
-
-```{r simulated-example, message=FALSE, fig.cap=caption}
-k_max <- 500 
-thin_sim_ctre <- thin(ctre = sim_ctre, k = k_max)
-par(mfrow=c(1,2))
-MLestimates(ctre = thin_sim_ctre, tail = params$tail, scale = n^(1/params$tail))
-```
-
-By the Theorem, the distribution 
-of $T(\ell)$ is approximately 
-$$
-{\rm ML}(\beta, p^{-1/\beta}) 
-= {\rm ML}(\beta, k^{-1/\beta} n^{1/\beta}),
-$$
-which means 
-$\sigma_0 = n^{1/\beta}$.
-The distribution of $J_k$ is irrelevant for the inference on $\beta$ and 
-$\sigma_0$ (we have chosen unit exponential random variables). 
-Figure \ref{fig:sim} displays plots of $\hat \beta(\ell)$ and 
-$\hat \sigma(\ell)$ vs. $k$; recall that $k$ is the index of the order
-statistics of $J_k$ at which the threshold $\ell$ is placed. 
-Dotted lines show 95% confidence intervals, which are derived from the 
-asymptotic normality of the log-moments estimators [@Cahoy2013] and the $\delta$-method [@MittagLeffleR].
-The dashed lines show the actual values of $\beta$ resp.\ $\sigma_0$, 
-showing that our inference method identifies the 
-parameters correctly.
-
-# References {-}

### 2018-05-08 article_springer/index.Rmd
manually add authors, keywords & grant

@@
     Research (BMBF). 
+author: 
+  - Katharina Hees, TU Dortmund
+  - Smarak Nayak, National Australia Bank
+  - Peter Straka, UNSW Sydney
+
 authors:
@@
 - name: "Katharina Hees"
-  address: University of Dortmund
+  address: TU Dortmund
   email: hees@statistik.uni-dortmund.de
@@
 
+Keywords:
+
+: _heavy tails, renewal process, extreme value theory, peaks over threshold_
+
+Thanks:
+
+: * Peter Straka was supported by the 
+Discovery Early Career Research Award DE160101147 on the Project 
+"Predicting Extremes when Events Occur in Bursts" by the Australian
+Research Council.
+* Katharina Hees was supported by 
+the DAAD co-financed by the German Federal Ministry of Education and 
+Research (BMBF).
+
 ```{r, child="article_springer.Rmd"}

### 2018-05-09 article_springer/index.Rmd
html_document2()

@@
   - Peter Straka, UNSW Sydney
-
 authors:
@@
 bibliography: CTRMstats.bib
+site: bookdown::bookdown_site
 output: 
+  bookdown::html_document2: default 
   html_document: 

### 2018-05-09 article_springer/article_springer.Rmd
\ref{ => \@ref(

@@
 and $T(\ell, n)_{n \in \mathbb N}$ are independent.[^1]
-Figure \ref{fig:thresholdedBursty} shows a simulated dataset in the top 
+Figure \@ref(fig:thresholdedBursty) shows a simulated dataset in the top 
 panel, where $W$ has a stable distribution with tail parameter 
@@
 exponent.
-For instance, the top-left panel in Figure \ref{fig:QQ-plots} shows the 
+For instance, the top-left panel in Figure \@ref(fig:QQ-plots) shows the 
 (static) QQ-estimator for the magnitudes of the solar flare data, returning 
@@
 useful a Hill or QQ-Plot estimator becomes. 
-The bottom-left panel of Figure \ref{fig:QQ-plots}, for instance, shows the 
+The bottom-left panel of Figure \@ref(fig:QQ-plots), for instance, shows the 
 static QQ-estimator plot for $2000$ draws from the Mittag-Leffler distribution with 
@@
 and instead examining QQ-plots directly, on a logarithmic scale 
-(see Figure \ref{fig:QQ-plots}, right column).
+(see Figure \@ref(fig:QQ-plots), right column).
 The scale parameter $\sigma$ is irrelevant for a QQ-Plot. 
@@
 As an example, the threshold crossing times for the solar flare dataset
-(Figure \ref{fig:flare-diagnostics-2}, right panel)
+(Figure \@ref(fig:flare-diagnostics-2), right panel)
 yield a difference in deviance of 
@@
 
-The Theorem in Section \ref{sec:scaling} implies that for a high 
+The Theorem in Section \@ref(sec:scaling) implies that for a high 
 threshold $\ell$ we may 
@@
 The above approach, though theoretically sound, benefits from the following
-practical adjustments (compare with Figure \ref{fig:flares}):
+practical adjustments (compare with Figure \@ref(fig:flares)):
 
@@
 
-Figures \ref{fig:flare-diagnostics-1} and \ref{fig:flare-diagnostics-2} 
+Figures \@ref(fig:flare-diagnostics-1) and \@ref(fig:flare-diagnostics-2) 
 show the diagnostic plots for a 
@@
 
-According to Figure \ref{fig:flares}, for a threshold $\ell$ at the $k$-th order 
+According to Figure \@ref(fig:flares), for a threshold $\ell$ at the $k$-th order 
 statistic, the fitted threshold exceedance time distribution is 
@@
 distribution shifts towards larger values for the next crossing
-(see Figure \ref{fig:hazard}, left panel). 
+(see Figure \@ref(fig:hazard), left panel). 
 The hazard rate 
@@
 The closer $\beta$ is to $1$, the more the hazard rate mimics that of an 
-exponential distribution (a constant function, see Figure \ref{fig:hazard}, 
+exponential distribution (a constant function, see Figure \@ref(fig:hazard), 
 right panel).
@@
 waiting time and magnitude pairs $(W_k, J_k)$ (see upper panel in 
-Figure \ref{fig:thresholdedBursty}). In order to have exact 
+Figure \@ref(fig:thresholdedBursty). In order to have exact 
 analytical values available for $\beta$ and $\sigma_0$, a distribution for 
@@
 $\sigma_0$ (we have chosen unit exponential random variables). 
-Figure \ref{fig:sim} displays plots of $\hat \beta(\ell)$ and 
+Figure \@ref(fig:sim) displays plots of $\hat \beta(\ell)$ and 
 $\hat \sigma(\ell)$ vs. $k$; recall that $k$ is the index of the order

### 2018-05-09 article_springer/index.Rmd
update docs

@@
 output: 
-  bookdown::html_document2: default 
-  html_document: 
+  bookdown::html_document2: 
     toc: true
@@
     theme: journal
-  rticles::springer_article: 
-    fig_caption: yes
+    self_contained: true
 params:

### 2018-05-09 article_springer/index.Rmd
change output_dir

@@
     self_contained: true
+output_dir: docs
+output_file: index.html
 params:

### 2018-05-09 article_springer/article_springer.Rmd
fix cross-refs

@@
 
-#### _Proof of Theorem:_
+#### _Proof of Theorem:_ {-}
 We interpret the threshold crossing time $T(\ell)$ as the hitting time of the 
@@
 
-```{r solar-flare-tail-scale, message=FALSE, fig.height=4.5, fig.width=8, fig.cap="\\label{fig:flares}Stability plots for the tail and scale parameter of the Mittag-Leffler distribution of the Solar Flare dataset.
+```{r flares, message=FALSE, fig.height=4.5, fig.width=8, fig.cap="\\label{fig:flares}Stability plots for the tail and scale parameter of the Mittag-Leffler distribution of the Solar Flare dataset.
 Dotted horizontal lines are at $\\beta = 0.85$ and $\\sigma_0 = 3 \\times 10^7$ seconds $\\approx 0.95$ years."}
@@
 
-```{r simulated-example, message=FALSE, fig.cap=caption}
+```{r sim, message=FALSE, fig.cap=caption}
 k_max <- 500 

### 2018-05-09 article_springer/index.Rmd
nochmal würfeln

--- 2018-05-09 article_springer/index.Rmd
@@
 bibliography: CTRMstats.bib
-site: bookdown::bookdown_site
 output: 
   bookdown::html_document2: 
-    toc: true
-    toc_float: true
     theme: journal
-    self_contained: true
 params:

### 2018-05-09 article_springer/article_springer.Rmd
fix \eqref

@@
 more precisely,
-\begin{align} \label{eq:stability}
+\begin{align}
 \frac{W_1 + \ldots + W_n}{b(n)} \overset{d}{\longrightarrow} D, 
 \quad n \to \infty
+(\#eq:stability)
 \end{align}
@@
 analytical values available for $\beta$ and $\sigma_0$, a distribution for 
-$W_k$ needs to be chosen for which $b(n)$ from \eqref{eq:stability} is known. 
-If we choose $W_k \stackrel{d}{=} D$, where $D$ is as in \eqref{eq:stability}, 
+$W_k$ needs to be chosen for which $b(n)$ from \@ref(eq:stability) is known. 
+If we choose $W_k \stackrel{d}{=} D$, where $D$ is as in \@ref(eq:stability), 
 then due to the stability property we have the *equality* of distribution

### 2018-05-10 article_springer/index.Rmd
fix \eqref
add toc
link to pdf

@@
 bibliography: CTRMstats.bib
+site: bookdown::bookdown_site
 output: 
   bookdown::html_document2: 
-    theme: journal
+    toc: true
+    toc_float: true
+    theme: readable
 params:
@@
 
+(You can download a [pdf version of this paper](https://arxiv.org/pdf/1802.05218).)
+
 ```{r, child="article_springer.Rmd"}

### 2018-05-10 article_springer/index.Rmd
link citations

@@
     theme: readable
+biblio-style: "apalike"
+link-citations: true
 params:

### 2018-05-11 article_springer/article_springer.Rmd
crucial typo

@@
 $$
-T_\ell \sim {\rm ML}(\beta, k^{1/\beta} \sigma_0), 
+T_\ell \sim {\rm ML}(\beta, k^{-1/\beta} \sigma_0), 
 $$
@@
 $$
-p(t|\beta, \sigma_0, \ell, t_0) = \frac{f(t + t_0 | \beta, k^{1/\beta} \sigma_0)}{\mathbf P[T_\ell > t_0]}
+p(t|\beta, \sigma_0, \ell, t_0) = \frac{f(t + t_0 | \beta, k^{-1/\beta} \sigma_0)}{\mathbf P[T_\ell > t_0]}
 $$
@@
 $$
-h(t) = \frac{f(t| \beta, k^{1/\beta} \sigma_0))}{\int_t^\infty f(\tau| \beta, k^{1/\beta} \sigma_0))\,d\tau}
+h(t) = \frac{f(t| \beta, k^{1/\beta} \sigma_0))}{\int_t^\infty f(\tau| \beta, k^{-1/\beta} \sigma_0))\,d\tau}
 $$

### 2018-06-07 article_springer/article_springer.Rmd
revert article_springer.Rmd to v2 status

--- 2018-05-09 article_springer/article_springer.Rmd
@@
     Research (BMBF).
+
 authors: 
-
 - name: "Katharina Hees"
@@
   email: hees@statistik.uni-dortmund.de
+
 - name: "Smarak Nayak"
@@
   email: smarak.nayak@nab.com.au
+
 - name: "Peter Straka*"
@@
   email: p.straka@unsw.edu.au
+
 authorrunning: K. Hees, S. Nayak & P. Straka
+
 keywords:
@@
 - peaks over threshold
+
 abstract: |
@@
   the predictive distribution for the time until the next extreme event.
+
 bibliography: CTRMstats.bib
+
 output: 
-  html_document: default
   rticles::springer_article: 
     fig_caption: yes
+
 params:
@@
   n: 10000
+
 preamble: |
@@
 and $T(\ell, n)_{n \in \mathbb N}$ are independent.[^1]
-Figure \@ref(fig:thresholdedBursty) shows a simulated dataset in the top 
+Figure \ref{fig:thresholdedBursty} shows a simulated dataset in the top 
 panel, where $W$ has a stable distribution with tail parameter 
@@
 
-#### _Proof of Theorem:_ {-}
+#### _Proof of Theorem:_
 We interpret the threshold crossing time $T(\ell)$ as the hitting time of the 
@@
 exponent.
-For instance, the top-left panel in Figure \@ref(fig:QQ-plots) shows the 
+For instance, the top-left panel in Figure \ref{fig:QQ-plots} shows the 
 (static) QQ-estimator for the magnitudes of the solar flare data, returning 
@@
 useful a Hill or QQ-Plot estimator becomes. 
-The bottom-left panel of Figure \@ref(fig:QQ-plots), for instance, shows the 
+The bottom-left panel of Figure \ref{fig:QQ-plots}, for instance, shows the 
 static QQ-estimator plot for $2000$ draws from the Mittag-Leffler distribution with 
@@
 and instead examining QQ-plots directly, on a logarithmic scale 
-(see Figure \@ref(fig:QQ-plots), right column).
+(see Figure \ref{fig:QQ-plots}, right column).
 The scale parameter $\sigma$ is irrelevant for a QQ-Plot. 
@@
 As an example, the threshold crossing times for the solar flare dataset
-(Figure \@ref(fig:flare-diagnostics-2), right panel)
+(Figure \ref{fig:flare-diagnostics-2}, right panel)
 yield a difference in deviance of 
@@
 
-```{r flares, message=FALSE, fig.height=4.5, fig.width=8, fig.cap="\\label{fig:flares}Stability plots for the tail and scale parameter of the Mittag-Leffler distribution of the Solar Flare dataset.
+```{r solar-flare-tail-scale, message=FALSE, fig.height=4.5, fig.width=8, fig.cap="\\label{fig:flares}Stability plots for the tail and scale parameter of the Mittag-Leffler distribution of the Solar Flare dataset.
 Dotted horizontal lines are at $\\beta = 0.85$ and $\\sigma_0 = 3 \\times 10^7$ seconds $\\approx 0.95$ years."}
@@
 
-The Theorem in Section \@ref(sec:scaling) implies that for a high 
+The Theorem in Section \ref{sec:scaling} implies that for a high 
 threshold $\ell$ we may 
@@
 The above approach, though theoretically sound, benefits from the following
-practical adjustments (compare with Figure \@ref(fig:flares)):
+practical adjustments (compare with Figure \ref{fig:flares}):
 
@@
 
-```{r flare-diagnostics-2, fig.height=4, fig.cap="Diagnostic plots for the solar flare data: empirical copula and QQ Plot. \\label{fig:flare-diagnostics-2}"}
-par(mfrow = c(1,2))
+```{r flare-diagnostics-2, fig.height=7, fig.cap="Diagnostic plots for the solar flare data: empirical copula and QQ Plot. \\label{fig:flare-diagnostics-2}"}
+par(mfrow = c(2,2))
 empcopula(flares_ctre)
@@
 
-Figures \@ref(fig:flare-diagnostics-1) and \@ref(fig:flare-diagnostics-2) 
+Figures \ref{fig:flare-diagnostics-1} and \ref{fig:flare-diagnostics-2} 
 show the diagnostic plots for a 
@@
 
-According to Figure \@ref(fig:flares), for a threshold $\ell$ at the $k$-th order 
+According to Figure \ref{fig:flares}, for a threshold $\ell$ at the $k$-th order 
 statistic, the fitted threshold exceedance time distribution is 
@@
 distribution shifts towards larger values for the next crossing
-(see Figure \@ref(fig:hazard), left panel). 
+(see Figure \ref{fig:hazard}, left panel). 
 The hazard rate 
@@
 The closer $\beta$ is to $1$, the more the hazard rate mimics that of an 
-exponential distribution (a constant function, see Figure \@ref(fig:hazard), 
+exponential distribution (a constant function, see Figure \ref{fig:hazard}, 
 right panel).
 
-```{r hazard, fig.height=4, fig.cap="Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\\beta = 0.8$, $\\sigma_0 = 1$).
+```{r hazard, fig.height=7, fig.cap="Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\\beta = 0.8$, $\\sigma_0 = 1$).
 Right: Hazard rate depending on tail parameter $\\beta$.\\label{fig:hazard}"}
@@
 xx <- exp(seq(from = log(from), to = log(to), length.out = 100))
-par(mfrow = c(1,2))
+par(mfrow = c(2,2))
 plot(xx, rep(1, length(xx)), ylim = c(0.001,1), type = 'n', log = 'xy', 
@@
 waiting time and magnitude pairs $(W_k, J_k)$ (see upper panel in 
-Figure \@ref(fig:thresholdedBursty). In order to have exact 
+Figure \ref{fig:thresholdedBursty}). In order to have exact 
 analytical values available for $\beta$ and $\sigma_0$, a distribution for 
@@
 
-```{r sim, message=FALSE, fig.cap=caption}
+```{r simulated-example, message=FALSE, fig.cap=caption}
 k_max <- 500 
@@
 $\sigma_0$ (we have chosen unit exponential random variables). 
-Figure \@ref(fig:sim) displays plots of $\hat \beta(\ell)$ and 
+Figure \ref{fig:sim} displays plots of $\hat \beta(\ell)$ and 
 $\hat \sigma(\ell)$ vs. $k$; recall that $k$ is the index of the order

### 2018-06-28 article_springer/article_springer.Rmd
see, Pareto doesn't work either
points 1+2 addressed

@@
 
-  This article generalizes the Peaks Over Threshold (POT) model to the setting 
-  where inter-event times are heavy-tailed. For high thresholds and 
+  This article provides a new model for the threshold inter-exceedance _times_;
+  the threshold exceedances are modeled via the standard 
+  Peaks Over Threshold (POT) method.
+  For high thresholds and 
   infinite-mean waiting times, we show that the times between threshold 
   crossings are Mittag-Leffler distributed, and thus form a "fractional 
-  Poisson Process" which generalizes the standard Poisson Process.
+  Poisson Process" which generalizes the standard Poisson Process of threshold
+  exceedances.
   We provide graphical means of estimating model parameters and assessing 
@@
 
-flare_mags <- flares %>% ctre() %>% thin(k=500) %>% magnitudes()
+flare_mags <- actuar::rpareto(n = 500, shape = 0.8, scale = 1)
 flares_exponent <- flare_mags %>% qqestplot_static()

### 2018-10-24 article_springer/article_springer.Rmd
Change Chapter 4 (still in progress)

@@
 
-# Inference for the Mittag-Leffler distribution
+# Model Choice and inference for the Mittag-Leffler distribution
 
@@
 
-Since the Mittag-Leffler distribution is heavy-tailed, many researchers 
-would intuitively give the highest importance to the tail behaviour of the 
-distribution, and 
-estimate the exponent of the tail function with established methods such 
-as the Hill estimator. The QQ-estimator [@Kratz96] is closely related to 
-the Hill estimator and fits a 
-least squares line through the logarithms of the ordered statistics 
-(y-axis) and the corresponding quantiles of the exponential distribution 
-(x-axis). The reciprocal slope is returned as the estimate of the tail 
-exponent.
-For instance, the top-left panel in Figure \ref{fig:QQ-plots} shows the 
-(static) QQ-estimator for the magnitudes of the solar flare data, returning 
-a good fit to a Pareto distribution with tail parameter 
-`r round(flares_exponent, 2)`. The dynamic QQ-estimator plot (top-center panel)
-plots the tail exponent estimate for the largest values at cutoffs 
-varying up to the 5th order statistic, and the region of stability at 
-0.8 indicates a recommended estimate.
+Since the Mittag-Leffler distribution is heavy-tailed, many researchers would intuitively give the highest importance to the tail behaviour of the distribution, and estimate the exponent of the tail function with established methods such as the Hill estimator.
+The other option is to use estimators specifically for the tail parameter of a Mittag-Leffler distribution.
+The first method for parameter estimation was the fractional moment estimator proposed by [@kozubowski2001].
+One drawback of this method is that constant priors for the tail parameter are needed for the calculation of the estimates.
+[@Cahoy2010] proposed an estimator based on the log-Moments which doesn't need prior knowledge.
+Furthermore, they showed in a simulation study that he log-Moments estimator outclasses the fractional moment estimator regarding bias and root mean squared error (RMSE).
+Due to the form of the density function there exists no closed form for the Maximum Likelihood estimator (MLE).
+In the RPackage `MittagLeffleR` Maximum Likelihood estimation is implemented via numerical optimization.
+The MLE outperforms the log-ent estimator regarding bias and RMSE for big enough sample sizes, but is extremely computational intensive.
+In figure XX one can see that both mehtods work quite well even for very low sample sizes.
 
-However, as described nicely by @Resnick97, the less 
-similar a heavy-tailed distribution is to a Pareto distribution, the less
-useful a Hill or QQ-Plot estimator becomes. 
-The bottom-left panel of Figure \ref{fig:QQ-plots}, for instance, shows the 
-static QQ-estimator plot for $2000$ draws from the Mittag-Leffler distribution with 
-tail parameter $0.8$. The stretched exponential shape means 
-that the Mittag-Leffler distribution has more probability near $0$ than 
-the Pareto distribution, severely biasing the estimator downwards 
-(`r round(ML_exponent, 2)`). 
-Even by looking at different cutoffs via the dynamic QQ-estimator plot 
-(bottom-center panel) one hardly identifies $0.8$ as a clear candidate for 
-a tail parameter estimate.
+```{r pressure, echo=FALSE, fig.cap="A caption", out.width = '100%'}
+knitr::include_graphics("temp.pdf")
+```
+<!-- The QQ-estimator [@Kratz96] is closely related to  -->
+<!-- the Hill estimator and fits a  -->
+<!-- least squares line through the logarithms of the ordered statistics  -->
+<!-- (y-axis) and the corresponding quantiles of the exponential distribution  -->
+<!-- (x-axis). The reciprocal slope is returned as the estimate of the tail  -->
+<!-- exponent. -->
+<!-- For instance, the top-left panel in Figure \ref{fig:QQ-plots} shows the  -->
+<!-- (static) QQ-estimator for the magnitudes of the solar flare data, returning  -->
+<!-- a good fit to a Pareto distribution with tail parameter  -->
+<!-- `r round(flares_exponent, 2)`. The dynamic QQ-estimator plot (top-center panel) -->
+<!-- plots the tail exponent estimate for the largest values at cutoffs  -->
+<!-- varying up to the 5th order statistic, and the region of stability at  -->
+<!-- 0.8 indicates a recommended estimate. -->
 
-QQ-estimators, and the closely related Hill estimator, are hence not 
-suitable to detect a heavy-tailed Mittag-Leffler distribution. Moreover, 
-QQ-estimator plots of exponentially distributed data are virtually 
-indistinguishable from the bottom-left panel. This shows that 
-_Mittag-Leffler distributed data may look like exponentially distributed 
-data if examined via a QQ-estimator_.
+<!-- However, as described nicely by @Resnick97, the less  -->
+<!-- similar a heavy-tailed distribution is to a Pareto distribution, the less -->
+<!-- useful a Hill or QQ-Plot estimator becomes.  -->
+<!-- The bottom-left panel of Figure \ref{fig:QQ-plots}, for instance, shows the  -->
+<!-- static QQ-estimator plot for $2000$ draws from the Mittag-Leffler distribution with  -->
+<!-- tail parameter $0.8$. The stretched exponential shape means  -->
+<!-- that the Mittag-Leffler distribution has more probability near $0$ than  -->
+<!-- the Pareto distribution, severely biasing the estimator downwards  -->
+<!-- (`r round(ML_exponent, 2)`).  -->
+<!-- Even by looking at different cutoffs via the dynamic QQ-estimator plot  -->
+<!-- (bottom-center panel) one hardly identifies $0.8$ as a clear candidate for  -->
+<!-- a tail parameter estimate. -->
+
+<!-- QQ-estimators, and the closely related Hill estimator, are hence not  -->
+<!-- suitable to detect a heavy-tailed Mittag-Leffler distribution. Moreover,  -->
+<!-- QQ-estimator plots of exponentially distributed data are virtually  -->
+<!-- indistinguishable from the bottom-left panel. This shows that  -->
+<!-- _Mittag-Leffler distributed data may look like exponentially distributed  -->
+<!-- data if examined via a QQ-estimator_.  -->
 
@@
 ```
+<!--Anpassen:
+<!-- Hence if there is some prior expectation that the data are drawn from the  -->
+<!-- Mittag-Leffler distribution -->
+<!-- (as is the the case for threshold exceedance times), -->
+<!-- then we recommend avoiding QQ-estimators and Hill plots altogether,  -->
+<!-- and instead examining QQ-plots directly, on a logarithmic scale  -->
+<!-- (see Figure \ref{fig:QQ-plots}, right column). -->
+<!-- The scale parameter $\sigma$ is irrelevant for a QQ-Plot.  -->
+<!-- The tail parameter $\beta$ can be estimated quickly via the log-moment  -->
+<!-- method by @Cahoy2013, or via maximum likelihood.  -->
+<!-- Both estimators are implemented in `MittagLeffleR`  -->
+<!-- [@MittagLeffleR].  -->
 
-Hence if there is some prior expectation that the data are drawn from the 
-Mittag-Leffler distribution
-(as is the the case for threshold exceedance times),
-then we recommend avoiding QQ-estimators and Hill plots altogether, 
-and instead examining QQ-plots directly, on a logarithmic scale 
-(see Figure \ref{fig:QQ-plots}, right column).
-The scale parameter $\sigma$ is irrelevant for a QQ-Plot. 
-The tail parameter $\beta$ can be estimated quickly via the log-moment 
-method by @Cahoy2013, or via maximum likelihood. 
-Both estimators are implemented in `MittagLeffleR` 
-[@MittagLeffleR]. 
 Since the exponential distribution is nested in the Mittag-Leffler 
-family of distributions, a standard likelihood ratio test can be 
-performed, with the exponential distribution as a null model against 
-a Mittag-Leffler distribution as the alternative. 
-As an example, the threshold crossing times for the solar flare dataset
-(Figure \ref{fig:flare-diagnostics-2}, right panel)
-yield a difference in deviance of 
-$\approx$ `r round(2 * (mlmle_out$loglik - mlmle_out$null_loglik))`, 
-which evaluates to a strongly significant $\chi^2_1$ test statistic 
-(p-value = $10^{`r round(log10(mlmle_out$p_value))`}$) for the null
-hypothesis $\beta = 1$.
+family of distributions, an appropriate way to choose between a model with exponential and Mittag-Leffler inter-exceedance times seems to be a Likelihood ratio test.
+Although the two models are nested, the assymptotic distribution seems no to be chi-squared since under $H_0$ the paremter $\beta$ of Mittag-Leffler distribution is equal to zreo which is on the boundary of the parameter space $(0,1]$.
+<!-- Anpassen:
+<!-- As an example, the threshold crossing times for the solar flare dataset -->
+<!-- (Figure \ref{fig:flare-diagnostics-2}, right panel) -->
+<!-- yield .  -->
 

### 2018-10-24 article_springer/article_springer.Rmd
Chapter 4 & Simulation study (still in progress)

@@
 
-Since the Mittag-Leffler distribution is heavy-tailed, many researchers would intuitively give the highest importance to the tail behaviour of the distribution, and estimate the exponent of the tail function with established methods such as the Hill estimator.
-The other option is to use estimators specifically for the tail parameter of a Mittag-Leffler distribution.
-The first method for parameter estimation was the fractional moment estimator proposed by [@kozubowski2001].
+The first method proposed for parameter estimation of the Mittag-Leffler distribution was the fractional moment estimator by [@kozubowski2001].
 One drawback of this method is that constant priors for the tail parameter are needed for the calculation of the estimates.
@@
 In figure XX one can see that both mehtods work quite well even for very low sample sizes.
+Since the Mittag-Leffler distribution is heavy-tailed, many researchers would intuitively give the highest importance to the tail behaviour of the distribution.
+Of course, one can also use established tail exponent estimators such as the Hill estimator.
+However, these methods are less statistically efficient since they only use a portion of the information contained in the data, as was already mentionded by [@kozubowski2001].
+Addtionally they need a specification of a tuning parameter.
 
-```{r pressure, echo=FALSE, fig.cap="A caption", out.width = '100%'}
-knitr::include_graphics("temp.pdf")
+In XX we plotted a Hill plot for differet k's where .....
+
+```{r pressure, echo=FALSE, fig.cap="MSE for sample sizes n=30, 100, 200 for the tail and scale estimations via log-moments and maximum likelihood estimation", out.width = '100%'}
+knitr::include_graphics("MSE_n25_100_200.pdf")
 ```
@@
 
-Since the exponential distribution is nested in the Mittag-Leffler 
-family of distributions, an appropriate way to choose between a model with exponential and Mittag-Leffler inter-exceedance times seems to be a Likelihood ratio test.
-Although the two models are nested, the assymptotic distribution seems no to be chi-squared since under $H_0$ the paremter $\beta$ of Mittag-Leffler distribution is equal to zreo which is on the boundary of the parameter space $(0,1]$.
+Since the exponential distribution is nested in the Mittag-Leffler family of distributions, an appropriate way to choose between a model with exponential and Mittag-Leffler inter-exceedance times seems to be a Likelihood ratio test.
+Although the two models are nested, the assymptotic distribution seems not to be $\chi^2_1$ since under $H_0$ the paremter $\beta$ of Mittag-Leffler distribution is equal to zero which is on the boundary of the parameter space $(0,1]$.
+
+```{r LRT power, echo=FALSE, fig.cap="Type One error for bootstrapped LRT for different sample sizes", out.width = '100%'}
+knitr::include_graphics("Plots_LRT_boot.pdf")
+```
+
+```{r LRT type one error, echo=FALSE, fig.cap="Type One error for bootstrapped LRT for different sample sizes", out.width = '100%'}
+knitr::include_graphics("Plots_LRT_boot_typeOneError.pdf")
+```
+
 <!-- Anpassen:
@@
 
+# Simulation study
+
+To test our inference method via stability plots, we have simulated `r params$n` 
+independent waiting time and magnitude pairs $(W_k, J_k)$ (see upper panel in 
+Figure \ref{fig:thresholdedBursty}). In order to have exact 
+analytical values available for $\beta$ and $\sigma_0$, a distribution for 
+$W_k$ needs to be chosen for which $b(n)$ from \eqref{eq:stability} is known. 
+If we choose $W_k \stackrel{d}{=} D$, where $D$ is as in \eqref{eq:stability}, 
+then due to the stability property we have the *equality* of distribution
+$W_1 + \ldots + W_n \stackrel{d}{=} b(n) D$, 
+for $b(n) = n^{1/\beta}$. 
+Using the parametrisation of @SamorodnitskyTaqqu, a few lines of 
+calculation (see e.g. the vignette on parametrisation in @MittagLeffleR) 
+show that $D$ must have the stable distribution 
+$S_\beta(\cos(\pi \beta/2)^{1/\beta}, +1, 0)$, which is 
+implemented in the R package `stabledist` by @stabledist.
+
+```{r make-caption}
+caption = "Tail and scale estimates for simulated data, with waiting times drawn from the stable distribution $S_\\beta(\\cos(\\pi \\beta/2)^{1/\\beta}, +1, 0)$ with $\\beta = 0.8$.
+Dashed lines are 95\\% confidence intervals, dotted lines are the known theoretical values ($0.8$ and $10000^{1/0.8}$).
+\\label{fig:sim}"
+```
+
+```{r simulated-example, message=FALSE, fig.cap=caption}
+k_max <- 500 
+thin_sim_ctre <- thin(ctre = sim_ctre, k = k_max)
+par(mfrow=c(1,2))
+MLestimates(ctre = thin_sim_ctre, tail = params$tail, scale = n^(1/params$tail))
+```
+
+By the Theorem, the distribution 
+of $T(\ell)$ is approximately 
+$$
+{\rm ML}(\beta, p^{-1/\beta}) 
+= {\rm ML}(\beta, k^{-1/\beta} n^{1/\beta}),
+$$
+which means 
+$\sigma_0 = n^{1/\beta}$.
+The distribution of $J_k$ is irrelevant for the inference on $\beta$ and 
+$\sigma_0$ (we have chosen unit exponential random variables). 
+Figure \ref{fig:sim} displays plots of $\hat \beta(\ell)$ and 
+$\hat \sigma(\ell)$ vs. $k$; recall that $k$ is the index of the order
+statistics of $J_k$ at which the threshold $\ell$ is placed. 
+Dotted lines show 95% confidence intervals, which are derived from the 
+asymptotic normality of the log-moments estimators [@Cahoy2013] and the $\delta$-method [@MittagLeffleR].
+The dashed lines show the actual values of $\beta$ resp.\ $\sigma_0$, 
+showing that our inference method identifies the 
+parameters correctly.
+
 # Discussion & Conclusion
@@
 
-\appendix
-
-# Validating our inference method on simulated data
-
-To test our inference method via stability plots, we have simulated `r params$n` 
-independent
-waiting time and magnitude pairs $(W_k, J_k)$ (see upper panel in 
-Figure \ref{fig:thresholdedBursty}). In order to have exact 
-analytical values available for $\beta$ and $\sigma_0$, a distribution for 
-$W_k$ needs to be chosen for which $b(n)$ from \eqref{eq:stability} is known. 
-If we choose $W_k \stackrel{d}{=} D$, where $D$ is as in \eqref{eq:stability}, 
-then due to the stability property we have the *equality* of distribution
-$W_1 + \ldots + W_n \stackrel{d}{=} b(n) D$, 
-for $b(n) = n^{1/\beta}$. 
-Using the parametrisation of @SamorodnitskyTaqqu, a few lines of 
-calculation (see e.g. the vignette on parametrisation in @MittagLeffleR) 
-show that $D$ must have the stable distribution 
-$S_\beta(\cos(\pi \beta/2)^{1/\beta}, +1, 0)$, which is 
-implemented in the R package `stabledist` by @stabledist.
-
-```{r make-caption}
-caption = "Tail and scale estimates for simulated data, with waiting times drawn from the stable distribution $S_\\beta(\\cos(\\pi \\beta/2)^{1/\\beta}, +1, 0)$ with $\\beta = 0.8$.
-Dashed lines are 95\\% confidence intervals, dotted lines are the known theoretical values ($0.8$ and $10000^{1/0.8}$).
-\\label{fig:sim}"
-```
-
-```{r simulated-example, message=FALSE, fig.cap=caption}
-k_max <- 500 
-thin_sim_ctre <- thin(ctre = sim_ctre, k = k_max)
-par(mfrow=c(1,2))
-MLestimates(ctre = thin_sim_ctre, tail = params$tail, scale = n^(1/params$tail))
-```
-
-By the Theorem, the distribution 
-of $T(\ell)$ is approximately 
-$$
-{\rm ML}(\beta, p^{-1/\beta}) 
-= {\rm ML}(\beta, k^{-1/\beta} n^{1/\beta}),
-$$
-which means 
-$\sigma_0 = n^{1/\beta}$.
-The distribution of $J_k$ is irrelevant for the inference on $\beta$ and 
-$\sigma_0$ (we have chosen unit exponential random variables). 
-Figure \ref{fig:sim} displays plots of $\hat \beta(\ell)$ and 
-$\hat \sigma(\ell)$ vs. $k$; recall that $k$ is the index of the order
-statistics of $J_k$ at which the threshold $\ell$ is placed. 
-Dotted lines show 95% confidence intervals, which are derived from the 
-asymptotic normality of the log-moments estimators [@Cahoy2013] and the $\delta$-method [@MittagLeffleR].
-The dashed lines show the actual values of $\beta$ resp.\ $\sigma_0$, 
-showing that our inference method identifies the 
-parameters correctly.
-
 # References {-}

### 2018-10-30 article_springer/article_springer.Rmd
Restructurings, new title, Data Sexample section

@@
 ---
-title: "Peaks Over Threshold for Bursty Time Series"
+title: "Statistical Inference for inter-arrival times of extreme events in bursty time series"
 # titlerunning: "CTRE: POT for Bursty Time Series"
@@
 - name: "Katharina Hees"
-  address: University of Dortmund
-  email: hees@statistik.uni-dortmund.de
+  address: TU Dortmund University
+  email: hees@statistik.tu-dortmund.de
 
@@
 bibliography: CTRMstats.bib
-
 output: 
-  rticles::springer_article: 
+       rticles::elsevier_article:
                 fig_caption: yes
+                number_sections: true
 
@@
   \usepackage{amssymb}
+  \usepackage{natbib}
+
 ---
@@
 library(CTRE)
+setwd("~/GitHub/bursty-POT/article_springer")
+Sys.setenv(TEXINPUTS=getwd(),
+           BIBINPUTS=getwd(),
+           BSTINPUTS=getwd())
 ```
@@
 library(magrittr)
+set.seed(12345)
 ```
@@
 in Section 5, but to set the stage we first discuss inference for the 
-Mittag-Leffler distribution in Section 4. 
-(A simulation study of the effectiveness of our statistical procedure is 
-given in the appendix.)
-Diagnostic plots for model criticism are discussed in Section 6. 
-In Section 7, we discuss the memory property of the 
+Mittag-Leffler distribution in Section 4. In Section 6, we discuss the memory property of the 
 Mittag-Leffler distribution, and how it affects the predictive distribution 
 for the time until the next threshold crossing event.
-Section 8 concludes. 
+A simulation study of the effectiveness of our statistical procedure is given in Section 7.
+In Section 8 we apply our method to a real data set.
+Finally we close with a discussion and conclusion in Section 8.
 For all statistical computations we have used R [@R]. 
@@
 
-As a model for extreme observations, we use a Marked Renewal Process (MRP):
+In this section we will As a model for extreme observations, we use a Marked Renewal Process (MRP):
 
@@
 If $W$ and $J$ are independent, the Marked Renewal Process is said to be *uncoupled*.
-\qed
 
@@
 uncoupled.
-\qed
 
@@
 sigma <- (cos(pi*tail/2))^(1/tail)
+
 times <- cumsum(stabledist::rstable(n, tail, 1, sigma, pm=1))
@@
 
-In this article, we restrict ourselves to the uncoupled case, where
-the two sequences $X(\ell, n)_{n \in \mathbb N}$
-and $T(\ell, n)_{n \in \mathbb N}$ are independent.[^1]
-Figure \ref{fig:thresholdedBursty} shows a simulated dataset in the top 
-panel, where $W$ has a stable distribution with tail parameter 
-$\beta =$ `r params$tail` (and skewness $1$ and location $0$), and 
-where $J$ is from a standard Gumbel distribution. In the bottom panel, 
-we plot a time series of solar flare intensities derived from a NASA
-dataset [@HXRBS][^*]. Clearly, the simulated data exhibit long intervals 
-_without any_ events, whereas in the real-world dataset events appear 
-continuously. The threshold exceedances, however, appear to have similar
-statistical behaviour in both models. Observations below a threshold are 
-commonly discarded in Extreme Value Theory (POT approach); likewise, the CTRE model
-interprets these observations as noise and filters them out.
-
-[^1]: To see why, note that $X(\ell)$ is, in distribution, simply equal to 
-  $J | J > \ell$, independent of any waiting time $W_k$.
-
-[^*]: The "complete Hard X Ray Burst Spectrometer event list" 
-is a comprehensive reference for all measurements of the Hard X 
-Ray Burst Spectrometer on NASA's Solar Maximum Mission from the time of 
-launch on Feb 14, 1980 to the end of the mission in Dec 1989. 12,776 
-events were detected, with the "vast 
-majority being solar flares". The list includes the start time, peak time, 
-duration, and peak rate of each event. We have used "start time" as the 
-variable for event times, and "peak rate" as the variable for event 
-magnitudes.
+In this article, we restrict ourselves to the uncoupled case, where W and J are independent.
+Then the two sequences $X(\ell, n)_{n \in \mathbb N}$ and $T(\ell, n)_{n \in \mathbb N}$ are independent as well.
+To see why, note that $X(\ell)$ is, in distribution, simply equal to $J | J > \ell$, independent of any waiting time $W_k$.
+Figure \ref{fig:thresholdedBursty} shows a simulated dataset in the top panel, where $W$ has a stable distribution with tail parameter $\beta =$ `r params$tail` (and skewness $1$ and location $0$), and where $J$ is from a standard Gumbel distribution.
+In the bottom panel, we plot a time series of solar flare intensities derived from a NASA dataset [@HXRBS] which we will later examine more closely (see Section 8).
+Clearly, the simulated data exhibit long intervals
+_without any_ events, whereas in the real-world dataset events appear continuously.
+The threshold exceedances, however, appear to have similar statistical behaviour in both models.
+Observations below a threshold are commonly discarded in Extreme Value Theory (POT approach); likewise, the CTRE model interprets these observations as noise and filters them out.
 
@@
 
-In this section we state and prove the key theorem, see below.
-For an accessible introduction to regular variation and stable limit theorems, we 
-recommend the book by @MeerschaertSikorskii.
+In this section we state and prove the key theorem, see below. For an accessible introduction to regular variation and stable limit theorems, we recommend the book by @MeerschaertSikorskii.
 
@@
 
-: Let the waiting times $J_k$ be in the domain of attraction of a 
-positively skewed sum-stable law with stability parameter $0 < \beta < 1$; 
-more precisely,
+: Let the waiting times $J_k$ be in the domain of attraction of a positively skewed sum-stable law with stability parameter $0 < \beta < 1$; more precisely,
 \begin{align} \label{eq:stability}
@@
 \end{align}
-for a function $b(n)$ which is regularly varying at $\infty$ with 
-parameter $1/\beta$, and where $\mathbf E[\exp(-sD)] = \exp(-s^\beta)$. 
-Write $p := \mathbf P(J > \ell)$. Then the weak convergence
+for a function $b(n)$ which is regularly varying at $\infty$ with parameter $1/\beta$, and where $\mathbf E[\exp(-sD)] = \exp(-s^\beta)$. Write $p := \mathbf P(J > \ell)$. Then the weak convergence
 $$
@@
 $$
-\qed
 
-\noindent For a scale parameter $\sigma > 0$, we write 
-${\rm ML}(\beta, \sigma)$ for the distribution of $\sigma W_\beta$. 
-The Mittag-Leffler distribution with parameter $\beta \in (0,1]$ is 
-a heavy-tailed positive distribution for $\beta < 1$, with infinite mean. 
-However, as $\beta \uparrow 1$, ${\rm ML}(\beta, \sigma)$ converges 
-weakly to the exponential distribution ${\rm Exp}(\sigma)$.
-This means that although its moments are all infinite, the Mittag-Leffler
-distribution may (if $\beta$ is close to 1) be indistinguishable from the 
-exponential distribution, for the purposes of applied statistics. 
-For a detailed reference on the Mittag-Leffler distribution, see e.g. 
-@Haubold11, and for algorithms, see e.g. the R package `MittagLeffleR`
-[@MittagLeffleR].
-
-#### _Proof of Theorem:_
-We interpret the threshold crossing time $T(\ell)$ as the hitting time of the 
+*Proof of Theorem:* We interpret the threshold crossing time $T(\ell)$ as the hitting time of the 
 underlying CTRM (Continuous Time Random Maxima) or "max-renewal process", 
@@
 
+For a scale parameter $\sigma > 0$, we write ${\rm ML}(\beta, \sigma)$ for the distribution of $\sigma W_\beta$. The Mittag-Leffler distribution with parameter $\beta \in (0,1]$ is 
+a heavy-tailed positive distribution for $\beta < 1$, with infinite mean. 
+However, as $\beta \uparrow 1$, ${\rm ML}(\beta, \sigma)$ converges 
+weakly to the exponential distribution ${\rm Exp}(\sigma)$.
+This means that although its moments are all infinite, the Mittag-Leffler
+distribution may (if $\beta$ is close to 1) be indistinguishable from the 
+exponential distribution, for the purposes of applied statistics. 
+For a detailed reference on the Mittag-Leffler distribution, see e.g. 
+@Haubold11, and for algorithms, see e.g. the R package `MittagLeffleR`
+[@MittagLeffleR].
+
 **Remark:**
+
 : If $\beta = 1$, the result of the Theorem above is standard, see e.g. 
@@
 
-```{r fig:QQ-plots, fig.cap="Pareto vs.
-Mittag-Leffler distribution, both with same tail exponent 0.8.
-Top row: solar flare magnitudes data, fitting nicely with a Pareto distribution.
-Bottom row: simulated Mittag-Leffler data.
-Left column: static QQ-Estimator plots, assessing a fit against the Pareto distribution.
-Centre column: dynamic QQ-Estimator plots.
-Right column: a usual QQ-Plot based on Mittag-Leffler quantiles.\\label{fig:QQ-plots}", fig.height=5.5, fig.width=7}
-par(mfrow = c(2,3))
-
-flare_mags <- actuar::rpareto(n = 500, shape = 0.8, scale = 1)
-flares_exponent <- flare_mags %>% qqestplot_static()
-
-flare_mags %>% tea::qqestplot(conf.int = TRUE)
-abline(h = 0.8, lty = 2, col = 2)
-
-flare_mags %>% mlqqplot(tail = 0.8, log = 'xy')
-(flare_mags %>% MittagLeffleR::logMomentEstimator())[1:2] -> MLparams
-flare_mags %>% qqline(distribution = function(p) qml(p, tail = 0.8, scale = MLparams[2]))
-
-ML_data <- MittagLeffleR::rml(500, 0.8)
-ML_exponent <- ML_data %>% qqestplot_static()
-
-ML_exponent2 <- ML_data %>% tea::qqestplot(conf.int = TRUE)
-abline(h=0.8, lty = 2, col = 2)
-
-ML_data %>% mlqqplot(0.8, log = 'xy')
-qqline(ML_data, distribution = function(p) qml(p, 0.8), col = 2)
-
-```
+In the classical POT approach a GPD distribution is fitted to the data.
+Due to the Theorem in the last Section we know that for high threshholds the waiting times between the exceedances are Mittag-Leffler distributed in case of heavy tailed waiting times.
+Hence, we discuss in this section first parameter estimation for Mittag-Leffler distributions.
 
@@
 [@Cahoy2010] proposed an estimator based on the log-Moments which doesn't need prior knowledge.
-Furthermore, they showed in a simulation study that he log-Moments estimator outclasses the fractional moment estimator regarding bias and root mean squared error (RMSE).
+Furthermore, they showed in a simulation study that the log-Moments estimator outclasses the fractional moment estimator regarding bias and root mean squared error (RMSE).
 Due to the form of the density function there exists no closed form for the Maximum Likelihood estimator (MLE).
 In the RPackage `MittagLeffleR` Maximum Likelihood estimation is implemented via numerical optimization.
-The MLE outperforms the log-ent estimator regarding bias and RMSE for big enough sample sizes, but is extremely computational intensive.
-In figure XX one can see that both mehtods work quite well even for very low sample sizes.
+The MLE outperforms the log-moment estimator regarding bias and RMSE for big enough sample sizes, but is extremely computational intensive and the differences in bias and RMSE between the two methods are very small.
+In Figure \ref{fig:MSE} one can see that both methods work quite well even for very low sample sizes.
 Since the Mittag-Leffler distribution is heavy-tailed, many researchers would intuitively give the highest importance to the tail behaviour of the distribution.
@@
 Addtionally they need a specification of a tuning parameter.
+In XX one can see a Hill plot for differet k's.
 
-In XX we plotted a Hill plot for differet k's where .....
-
-```{r pressure, echo=FALSE, fig.cap="MSE for sample sizes n=30, 100, 200 for the tail and scale estimations via log-moments and maximum likelihood estimation", out.width = '100%'}
+```{r MSE, echo=FALSE, fig.height=12, fig.cap="\\label{fig:MSE} MSE for sample sizes n=30, 100, 200 for the tail and scale estimations via log-moments and maximum likelihood estimation", out.width = '100%'}
 knitr::include_graphics("MSE_n25_100_200.pdf")
 ```
-<!-- The QQ-estimator [@Kratz96] is closely related to  -->
-<!-- the Hill estimator and fits a  -->
-<!-- least squares line through the logarithms of the ordered statistics  -->
-<!-- (y-axis) and the corresponding quantiles of the exponential distribution  -->
-<!-- (x-axis). The reciprocal slope is returned as the estimate of the tail  -->
-<!-- exponent. -->
-<!-- For instance, the top-left panel in Figure \ref{fig:QQ-plots} shows the  -->
-<!-- (static) QQ-estimator for the magnitudes of the solar flare data, returning  -->
-<!-- a good fit to a Pareto distribution with tail parameter  -->
-<!-- `r round(flares_exponent, 2)`. The dynamic QQ-estimator plot (top-center panel) -->
-<!-- plots the tail exponent estimate for the largest values at cutoffs  -->
-<!-- varying up to the 5th order statistic, and the region of stability at  -->
-<!-- 0.8 indicates a recommended estimate. -->
-
-<!-- However, as described nicely by @Resnick97, the less  -->
-<!-- similar a heavy-tailed distribution is to a Pareto distribution, the less -->
-<!-- useful a Hill or QQ-Plot estimator becomes.  -->
-<!-- The bottom-left panel of Figure \ref{fig:QQ-plots}, for instance, shows the  -->
-<!-- static QQ-estimator plot for $2000$ draws from the Mittag-Leffler distribution with  -->
-<!-- tail parameter $0.8$. The stretched exponential shape means  -->
-<!-- that the Mittag-Leffler distribution has more probability near $0$ than  -->
-<!-- the Pareto distribution, severely biasing the estimator downwards  -->
-<!-- (`r round(ML_exponent, 2)`).  -->
-<!-- Even by looking at different cutoffs via the dynamic QQ-estimator plot  -->
-<!-- (bottom-center panel) one hardly identifies $0.8$ as a clear candidate for  -->
-<!-- a tail parameter estimate. -->
-
-<!-- QQ-estimators, and the closely related Hill estimator, are hence not  -->
-<!-- suitable to detect a heavy-tailed Mittag-Leffler distribution. Moreover,  -->
-<!-- QQ-estimator plots of exponentially distributed data are virtually  -->
-<!-- indistinguishable from the bottom-left panel. This shows that  -->
-<!-- _Mittag-Leffler distributed data may look like exponentially distributed  -->
-<!-- data if examined via a QQ-estimator_.  -->
 
@@
 ```
-<!--Anpassen:
-<!-- Hence if there is some prior expectation that the data are drawn from the  -->
-<!-- Mittag-Leffler distribution -->
-<!-- (as is the the case for threshold exceedance times), -->
-<!-- then we recommend avoiding QQ-estimators and Hill plots altogether,  -->
-<!-- and instead examining QQ-plots directly, on a logarithmic scale  -->
-<!-- (see Figure \ref{fig:QQ-plots}, right column). -->
-<!-- The scale parameter $\sigma$ is irrelevant for a QQ-Plot.  -->
-<!-- The tail parameter $\beta$ can be estimated quickly via the log-moment  -->
-<!-- method by @Cahoy2013, or via maximum likelihood.  -->
-<!-- Both estimators are implemented in `MittagLeffleR`  -->
-<!-- [@MittagLeffleR].  -->
 
 Since the exponential distribution is nested in the Mittag-Leffler family of distributions, an appropriate way to choose between a model with exponential and Mittag-Leffler inter-exceedance times seems to be a Likelihood ratio test.
-Although the two models are nested, the assymptotic distribution seems not to be $\chi^2_1$ since under $H_0$ the paremter $\beta$ of Mittag-Leffler distribution is equal to zero which is on the boundary of the parameter space $(0,1]$.
+Although the two models are nested, the assymptotic distribution is not $\chi^2_1$-distributed, the classical Wilks Theorem doesn't apply since under $H_0$ the paremter $\beta$ of Mittag-Leffler distribution is equal to zero which is on the boundary of the parameter space $(0,1]$.
+We used a bootstrapped likelihood ratio test.
+In figure XX one can see the power for different tail parameters.
+As expected the power gets smaller for tail parameters close to one, since the Mittag-Leffler distribution converges for $\beta \rightarrow 1$ to an exponetial distribution.
+For tail parameters close to one it is hard to differentiate a Mittag-Lefller distribution from a exponential distribution.
 
@@
 
-<!-- Anpassen:
-<!-- As an example, the threshold crossing times for the solar flare dataset -->
-<!-- (Figure \ref{fig:flare-diagnostics-2}, right panel) -->
-<!-- yield .  -->
-
 # Inference on Exceedance times
-
-```{r solar-flare-tail-scale, message=FALSE, fig.height=4.5, fig.width=8, fig.cap="\\label{fig:flares}Stability plots for the tail and scale parameter of the Mittag-Leffler distribution of the Solar Flare dataset.
-Dotted horizontal lines are at $\\beta = 0.85$ and $\\sigma_0 = 3 \\times 10^7$ seconds $\\approx 0.95$ years."}
-thin_flares_ctre <- flares %>% ctre() %>% thin(k = 700)
-par(mfrow=c(1,2))
-MLestimates(thin_flares_ctre, tail = 0.9, scale = 3 * 1E7)
-```
 
@@
   The datasets are then of length $k-1$.
+
 * We use $k$ rather than $\ell$ for the horizontal axis of our plots.
+
 * In Step 4, rather than plotting $p^{1/\hat \beta} \hat \sigma(\ell)$
@@
 see the appendix.
-
-# Checking Model Assumptions
-
-```{r flare-diagnostics-1, fig.height=7, fig.cap="Diagnostic plots for the solar flare data: auto-correlation function.\\label{fig:flare-diagnostics-1}"}
-flares_ctre <- flares %>% ctre() %>% thin(k = 150)
-acf(flares_ctre)
-```
-
-```{r flare-diagnostics-2, fig.height=7, fig.cap="Diagnostic plots for the solar flare data: empirical copula and QQ Plot. \\label{fig:flare-diagnostics-2}"}
-par(mfrow = c(2,2))
-empcopula(flares_ctre)
-flares_ctre %>% interarrival() %>% mlqqplot(log = 'xy', tail = 0.8, main = "Mittag-Leffler QQ Plot")
-```
-
-The CTRE model is based on three main assumptions, which are repeated 
-below. For each assumption, we suggest one means of checking if it holds:
-
-i.i.d.:
-: After removing the "noise observations" below the smallest threshold 
-  $\ell_0$, the pair sequence $(T(\ell_0, i), X(\ell_0,i))$ is i.i.d. 
-  An indication if this is true is given 
-  by an auto-correlation plot for the logarithms (to ensure finite moments) 
-  of the two time series.
-
-Uncoupled:
-: Each $T(\ell, i)$ is independent of each $X(\ell, i)$. We propose an empirical copula
-  plot to check for any dependence.
-
-${\rm ML}(\beta, \sigma)$ distribution of $T(\ell, i)$:
-: Apply a cutoff at the lowest threshold $\ell_0$, 
-  extract the threshold crossing times, 
-  and create a QQ Plot for the Mittag-Leffler distribution. 
-  Use a log-Moment estimate of the tail parameter for the theoretical / population 
-  quantiles of the plot.
-
-Figures \ref{fig:flare-diagnostics-1} and \ref{fig:flare-diagnostics-2} 
-show the diagnostic plots for a 
-minimum threshold chosen at the 200th order statistic. 
-There is some residual autocorrelation for the sequence of threshold 
-exceedance times that is not accounted for by the CTRE model. 
-The fit with a Mittag-Leffler distribution ($\beta = 0.8$) is good, 
-though there are signs that the power-law tail tapers off for very large 
-inter-threshold crossing times. 
-There is no apparent dependence between threshold exceedance times and 
-event magnitudes seen in the copula plot.
 
@@
 decreasing function for the Mittag-Leffler distribution. 
-The closer $\beta$ is to $1$, the more the hazard rate mimics that of an 
-exponential distribution (a constant function, see Figure \ref{fig:hazard}, 
-right panel).
-
-```{r hazard, fig.height=7, fig.cap="Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\\beta = 0.8$, $\\sigma_0 = 1$).
+```{r hazard, fig.height=5, fig.cap="Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\\beta = 0.8$, $\\sigma_0 = 1$).
 Right: Hazard rate depending on tail parameter $\\beta$.\\label{fig:hazard}"}
@@
 xx <- exp(seq(from = log(from), to = log(to), length.out = 100))
-par(mfrow = c(2,2))
+par(mfrow = c(1,2))
 plot(xx, rep(1, length(xx)), ylim = c(0.001,1), type = 'n', log = 'xy', 
@@
 ```
+The closer $\beta$ is to $1$, the more the hazard rate mimics that of an 
+exponential distribution (a constant function, see Figure \ref{fig:hazard}, 
+right panel).
 
@@
 
-To test our inference method via stability plots, we have simulated `r params$n` 
+To test our inference method via stability plots, we have simulated 
 independent waiting time and magnitude pairs $(W_k, J_k)$ (see upper panel in 
-Figure \ref{fig:thresholdedBursty}). In order to have exact 
+Figure \ref{fig:thresholdedBursty}) for three different situations: stable waiting times, Pareto waitings times and Exponential waiting times. In order to have exact 
 analytical values available for $\beta$ and $\sigma_0$, a distribution for 
@@
 
+# Data example
+
+The "complete Hard X Ray Burst Spectrometer event list" 
+is a comprehensive reference for all measurements of the Hard X 
+Ray Burst Spectrometer on NASA's Solar Maximum Mission from the time of 
+launch on Feb 14, 1980 to the end of the mission in Dec 1989. 12,776 
+events were detected, with the "vast 
+majority being solar flares". The list includes the start time, peak time, 
+duration, and peak rate of each event. We have used "start time" as the 
+variable for event times, and "peak rate" as the variable for event 
+magnitudes.
+
+## Checking Model Assumptions
+
+The CTRE model is based on three main assumptions, which are repeated 
+below. For each assumption, we suggest one means of checking if it holds:
+
+i.i.d.:
+
+: After removing the "noise observations" below the smallest threshold 
+  $\ell_0$, the pair sequence $(T(\ell_0, i), X(\ell_0,i))$ is i.i.d. 
+  An indication if this is true is given 
+  by an auto-correlation plot for the logarithms (to ensure finite moments) 
+  of the two time series.
+
+Uncoupled:
+
+: Each $T(\ell, i)$ is independent of each $X(\ell, i)$. We propose an empirical copula
+  plot to check for any dependence.
+
+${\rm ML}(\beta, \sigma)$ distribution of $T(\ell, i)$:
+
+: Apply a cutoff at the lowest threshold $\ell_0$, 
+  extract the threshold crossing times, 
+  and create a QQ Plot for the Mittag-Leffler distribution. 
+  Use a log-Moment estimate of the tail parameter for the theoretical / population 
+  quantiles of the plot.
+
+Figures \ref{fig:flare-diagnostics-1} and \ref{fig:flare-diagnostics-2} 
+show the diagnostic plots for a minimum threshold chosen at the 200th order statistic. 
+There is some residual autocorrelation for the sequence of threshold exceedance times that is not accounted for by the CTRE model.
+The fit with a Mittag-Leffler distribution ($\beta = 0.8$) is good, though there are signs that the power-law tail tapers off for very large inter-threshold crossing times.
+There is no apparent dependence between threshold exceedance times and event magnitudes seen in the copula plot.
+
+```{r flare-diagnostics-1, fig.height=7, fig.cap="Diagnostic plots for the solar flare data: auto-correlation function.\\label{fig:flare-diagnostics-1}"}
+flares_ctre <- flares %>% ctre() %>% thin(k = 150)
+acf(flares_ctre)
+```
+
+```{r flare-diagnostics-2, fig.height=4.5, fig.width=8, fig.cap="Diagnostic plots for the solar flare data: empirical copula and QQ Plot. \\label{fig:flare-diagnostics-2}"}
+par(mfrow = c(1,2))
+empcopula(flares_ctre)
+flares_ctre %>% interarrival() %>% mlqqplot(log = 'xy', tail = 0.8, main = "Mittag-Leffler QQ Plot")
+```
+
+```{r solar-flare-tail-scale, message=FALSE, fig.height=4.5, fig.width=8, fig.cap="\\label{fig:flares}Stability plots for the tail and scale parameter of the Mittag-Leffler distribution of the Solar Flare dataset.
+Dotted horizontal lines are at $\\beta = 0.85$ and $\\sigma_0 = 3 \\times 10^7$ seconds $\\approx 0.95$ years."}
+thin_flares_ctre <- flares %>% ctre() %>% thin(k = 700)
+par(mfrow=c(1,2))
+MLestimates(thin_flares_ctre, tail = 0.9, scale = 3 * 1E7)
+```
+
 # Discussion & Conclusion
@@
 phenomena:
+
 i) a heavy tail of the interarrival time distribution of 
 threshold crossings (long rests), and
+
 ii) a high propensity for more threshold crossing events immediately after 
 each threshold crossing event (bursts).
+
 The Mittag-Leffler distribution captures both phenomena, due to its heavy
@@
 
-## Acknowledgements {-}
+# Acknowledgements {-}
 
 The authors would like to thank Prof. Peter Scheffler for insights on 
-stochastic process limits for CTRMs, and Gurtek Gill who helped create
-the MittagLeffleR R-package.
+stochastic process limits for CTRMs, Roloand Fried for discussion according the statistical methods and Gurtek Gill who helped create the MittagLeffleR R-package.
 

### 2018-11-05 article_springer/article_springer.Rmd
Section 4

@@
 : If $\beta = 1$, the result of the Theorem above is standard, see e.g. 
-Equation (2.2) in @Gut1999.
+Equation (2.2) in @Gut1999. In @Anderson1987  a similar result is shown with a different choice of scaling constant.
 
@@
 
-In the classical POT approach a GPD distribution is fitted to the data.
-Due to the Theorem in the last Section we know that for high threshholds the waiting times between the exceedances are Mittag-Leffler distributed in case of heavy tailed waiting times.
-Hence, we discuss in this section first parameter estimation for Mittag-Leffler distributions.
+The classical POT approach is based on the fact, that exceedances above a high threshhold are assymptotically GPD distributed, hence a GPD distribution is fitted to the exceedances above a high enogh threshhold.
+Due to the Theorem in the last Section we know that for high threshholds the times between the exceedances are assymptotically Mittag-Leffler distributed in case of heavy tailed waiting times between the observations.
+Hence, before we talk about inference for the exceedances in the next section, we want to have a look at inference for Mittag-Leffler distributions in the folowing.
 
-The first method proposed for parameter estimation of the Mittag-Leffler distribution was the fractional moment estimator by [@kozubowski2001].
+The first method proposed for the estimation of the Mittag-Leffler distribution parameters was the fractional moment estimator by [@kozubowski2001].
+Unlike the first moments, the fractional moments of order $p$ for $p<\beta$ exist and can get calculated.
 One drawback of this method is that constant priors for the tail parameter are needed for the calculation of the estimates.
 [@Cahoy2010] proposed an estimator based on the log-Moments which doesn't need prior knowledge.
-Furthermore, they showed in a simulation study that the log-Moments estimator outclasses the fractional moment estimator regarding bias and root mean squared error (RMSE).
-Due to the form of the density function there exists no closed form for the Maximum Likelihood estimator (MLE).
+Furthermore, they showed in a simulation study that the log-Moment outclasses the fractional moment estimator regarding bias and root mean squared error (RMSE).
+Due to the form of the density function of a Mittag-Leffler distribution there exists no closed form for the Maximum Likelihood estimator (MLE).
 In the RPackage `MittagLeffleR` Maximum Likelihood estimation is implemented via numerical optimization.
@@
 Since the Mittag-Leffler distribution is heavy-tailed, many researchers would intuitively give the highest importance to the tail behaviour of the distribution.
-Of course, one can also use established tail exponent estimators such as the Hill estimator.
-However, these methods are less statistically efficient since they only use a portion of the information contained in the data, as was already mentionded by [@kozubowski2001].
-Addtionally they need a specification of a tuning parameter.
-In XX one can see a Hill plot for differet k's.
+Of course, one can also use established tail exponent estimators for the estimation of the parameter $\beta$ such as the Hill estimator, which is defined by
+\begin{align*}
+H_{k,n}= \frac{1}{k} \sum_{i=0}^{k-1} \log \frac{X_{n-i,n}}{X_{n-k,n}}. 
+\end{align*}
+However, these methods are less statistically efficient since they only use a portion of the information contained in the data, as was already mentioned by [@kozubowski2001].
+Addtionally, they need a specification of a tuning parameter.
+In Figure one can see a Hill plot for different $k's$.
 
@@
 
-```{r LRT power, echo=FALSE, fig.cap="Type One error for bootstrapped LRT for different sample sizes", out.width = '100%'}
+```{r LRT power, echo=FALSE, fig.cap="Power for bootstrapped LRT for different sample sizes", out.width = '100%'}
 knitr::include_graphics("Plots_LRT_boot.pdf")
-```
-
-```{r LRT type one error, echo=FALSE, fig.cap="Type One error for bootstrapped LRT for different sample sizes", out.width = '100%'}
-knitr::include_graphics("Plots_LRT_boot_typeOneError.pdf")
 ```

### 2018-11-05 article_springer/article_springer.Rmd
Section 4

@@
 Due to the Theorem in the last Section we know that for high threshholds the times between the exceedances are assymptotically Mittag-Leffler distributed in case of heavy tailed waiting times between the observations.
-Hence, before we talk about inference for the exceedances in the next section, we want to have a look at inference for Mittag-Leffler distributions in the folowing.
+Hence, before we talk about inference for the exceedances in the next section, we want to have a look at inference for Mittag-Leffler distributions in the following.
 
@@
 The MLE outperforms the log-moment estimator regarding bias and RMSE for big enough sample sizes, but is extremely computational intensive and the differences in bias and RMSE between the two methods are very small.
-In Figure \ref{fig:MSE} one can see that both methods work quite well even for very low sample sizes.
+In Figure \ref{fig:MSE}, one can see that both methods work quite well even for very low sample sizes.
+```{r MSE, echo=FALSE, fig.height=12, fig.cap="\\label{fig:MSE} MSE for sample sizes n=30, 100, 200 for the tail and scale estimations via log-moments and maximum likelihood estimation", out.width = '100%'}
+knitr::include_graphics("MSE_n25_100_200.pdf")
+```
 Since the Mittag-Leffler distribution is heavy-tailed, many researchers would intuitively give the highest importance to the tail behaviour of the distribution.
@@
 However, these methods are less statistically efficient since they only use a portion of the information contained in the data, as was already mentioned by [@kozubowski2001].
-Addtionally, they need a specification of a tuning parameter.
-In Figure one can see a Hill plot for different $k's$.
+Additionally, they need a specification of a tuning parameter and the hill estimator only performs well for distributions close to Pareto (see @Resnick97).
+In Figure \ref{fig:Hillplots} one can see different Hill plots for Mittag-Leffler simulated data with differrent sample sizes and tails.
+It would be really hard to deduce the correct tail parameter estimates from this plots.
 
-```{r MSE, echo=FALSE, fig.height=12, fig.cap="\\label{fig:MSE} MSE for sample sizes n=30, 100, 200 for the tail and scale estimations via log-moments and maximum likelihood estimation", out.width = '100%'}
-knitr::include_graphics("MSE_n25_100_200.pdf")
+```{r Hillplots, echo=FALSE, fig.height=12, fig.cap="\\label{fig:Hillplots} Hillplots for simulated Mittag-Leffler distributed rv's with tail parameter 0.5 (two plots in the right column) and 0.8 (two plots in the left column) and sample sizes 200 (two plots in the lower row) and 1000 (two plots in the upper row).
+", out.width = '100%'}
+knitr::include_graphics("Hillplots.pdf")
 ```
@@
 Since the exponential distribution is nested in the Mittag-Leffler family of distributions, an appropriate way to choose between a model with exponential and Mittag-Leffler inter-exceedance times seems to be a Likelihood ratio test.
-Although the two models are nested, the assymptotic distribution is not $\chi^2_1$-distributed, the classical Wilks Theorem doesn't apply since under $H_0$ the paremter $\beta$ of Mittag-Leffler distribution is equal to zero which is on the boundary of the parameter space $(0,1]$.
-We used a bootstrapped likelihood ratio test.
-In figure XX one can see the power for different tail parameters.
-As expected the power gets smaller for tail parameters close to one, since the Mittag-Leffler distribution converges for $\beta \rightarrow 1$ to an exponetial distribution.
-For tail parameters close to one it is hard to differentiate a Mittag-Lefller distribution from a exponential distribution.
+Although the two models are nested, the assymptotic distribution is not $\chi^2_1$-distributed, the classical Theorem of Wilk doesn't apply since under $H_0$ the paremter $\beta$ of Mittag-Leffler distribution is equal to zero and hence lies under $H_0$ on the boundary of the parameter space $(0,1]$.
+But one can perform a bootstrapped log-likelihood ratio test.
+In Figure \ref{Fig:LRT} one can see the power for the bootstrapped LRT for Mittag-Leffler distributions with different tail parameters.
+As expected the power gets smaller for tail parameters close to one, since the Mittag-Leffler distribution converges for $\beta \rightarrow 1$ to an exponential distribution.
+Hence, for tail parameters close to one it is hard to differentiate a Mittag-Lefller distribution from an exponential.
 
-```{r LRT power, echo=FALSE, fig.cap="Power for bootstrapped LRT for different sample sizes", out.width = '100%'}
+```{r LRT power, echo=FALSE, fig.cap="\\label{Fig:LRT} Power for bootstrapped LRT for different sample sizes", out.width = '100%'}
 knitr::include_graphics("Plots_LRT_boot.pdf")

### 2018-12-03 article_springer/article_springer.Rmd
Model Choice little changes

@@
 
-The classical POT approach is based on the fact, that exceedances above a high threshhold are assymptotically GPD distributed, hence a GPD distribution is fitted to the exceedances above a high enogh threshhold.
-Due to the Theorem in the last Section we know that for high threshholds the times between the exceedances are assymptotically Mittag-Leffler distributed in case of heavy tailed waiting times between the observations.
-Hence, before we talk about inference for the exceedances in the next section, we want to have a look at inference for Mittag-Leffler distributions in the following.
+The classical peaks over threshold approach is based on the fact, that exceedances above a high threshhold are assymptotically GPD distributed.
+Hence, a GPD distribution is fitted to the exceedances above a high enough threshhold.
+Due to the Theorem in the last Section, we know that for high threshholds the times between the exceedances are in case of heavy tailed inter-arrival times assymptotically Mittag-Leffler distributed.
+Therefore, before talking about inference for the exceedance times in the next section, we want to have a look at inference for Mittag-Leffler distributions in general.
 
-The first method proposed for the estimation of the Mittag-Leffler distribution parameters was the fractional moment estimator by [@kozubowski2001].
-Unlike the first moments, the fractional moments of order $p$ for $p<\beta$ exist and can get calculated.
+The first method proposed in the literature to estimate the parameters of Mittag-Leffler distribution was the fractional moment estimator by [@kozubowski2001].
+Unlike the first moments, the fractional moments of order $p$ for $p<\beta$ exist and can get calculated by explicit formulas.
 One drawback of this method is that constant priors for the tail parameter are needed for the calculation of the estimates.
-[@Cahoy2010] proposed an estimator based on the log-Moments which doesn't need prior knowledge.
+Therefore, [@Cahoy2010] proposed an estimator based on the log-Moments which doesn't need prior knowledge.
 Furthermore, they showed in a simulation study that the log-Moment outclasses the fractional moment estimator regarding bias and root mean squared error (RMSE).
 Due to the form of the density function of a Mittag-Leffler distribution there exists no closed form for the Maximum Likelihood estimator (MLE).
-In the RPackage `MittagLeffleR` Maximum Likelihood estimation is implemented via numerical optimization.
+In the RPackage `MittagLeffleR` we implemented Maximum Likelihood estimation via an numerical optimization algorithm.
 The MLE outperforms the log-moment estimator regarding bias and RMSE for big enough sample sizes, but is extremely computational intensive and the differences in bias and RMSE between the two methods are very small.
@@
 In Figure \ref{fig:Hillplots} one can see different Hill plots for Mittag-Leffler simulated data with differrent sample sizes and tails.
-It would be really hard to deduce the correct tail parameter estimates from this plots.
+It would be really hard to deduce the correct tail parameter estimates from these plots.
 
@@
 knitr::include_graphics("Hillplots.pdf")
-```
-
-```{r likelihood-ratio-test}
-flares_arrivals <- flares %>% ctre() %>% thin(k = 500) %>% interarrival()
-mlmle_out <- mlmle(data = flares_arrivals)
 ```
@@
 where $\beta = 0.85$ and $\sigma_0 = 3.0 \times 10^7 {\rm sec}$. 
-Unlike the exponential distribution, the Mittag-Leffler distribution is not 
-memoryless, and the probability density of the time $t$ until the next threshold 
-crossing will depend on the time $t_0$ elapsed since the last threshold crossing.
+Unlike the exponential distribution, the Mittag-Leffler distribution is not memoryless, and the probability density of the time $t$ until the next threshold crossing will depend on the time $t_0$ elapsed since the last threshold crossing.
 This density equals 
@@
 $$
-where $f(\,\cdot\, | \beta, k^{1/\beta} \sigma_0)$ is the probability density of 
-${\rm ML}(\beta, k^{1/\beta} \sigma_0)$. 
-The more time has passed without a threshold crossing, the more the probability 
-distribution shifts towards larger values for the next crossing
-(see Figure \ref{fig:hazard}, left panel). 
-The hazard rate 
+where $f(\,\cdot\, | \beta, k^{1/\beta} \sigma_0)$ is the probability density of ${\rm ML}(\beta, k^{1/\beta} \sigma_0)$. 
+The more time has passed without a threshold crossing, the more the probability distribution shifts towards larger values for the next crossing
+(see Figure \ref{fig:hazard}, left panel). The hazard rate 
 $$
@@
 $$
-represents the risk of a threshold crossing per unit time, and is a 
-decreasing function for the Mittag-Leffler distribution. 
+represents the risk of a threshold crossing per unit time, and is a decreasing function for the Mittag-Leffler distribution. 
 ```{r hazard, fig.height=5, fig.cap="Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\\beta = 0.8$, $\\sigma_0 = 1$).
@@
 
-It is beyond the scope of the current paper to incorporate parameter 
-uncertainty into our predictive distribution for the next threshold crossing; 
-however, methods as described by @Scarrott12 and @Lee15 are likely 
-to extend to our setting.
-
 # Simulation study
 
-To test our inference method via stability plots, we have simulated 
-independent waiting time and magnitude pairs $(W_k, J_k)$ (see upper panel in 
-Figure \ref{fig:thresholdedBursty}) for three different situations: stable waiting times, Pareto waitings times and Exponential waiting times. In order to have exact 
-analytical values available for $\beta$ and $\sigma_0$, a distribution for 
-$W_k$ needs to be chosen for which $b(n)$ from \eqref{eq:stability} is known. 
-If we choose $W_k \stackrel{d}{=} D$, where $D$ is as in \eqref{eq:stability}, 
-then due to the stability property we have the *equality* of distribution
-$W_1 + \ldots + W_n \stackrel{d}{=} b(n) D$, 
-for $b(n) = n^{1/\beta}$. 
-Using the parametrisation of @SamorodnitskyTaqqu, a few lines of 
-calculation (see e.g. the vignette on parametrisation in @MittagLeffleR) 
-show that $D$ must have the stable distribution 
-$S_\beta(\cos(\pi \beta/2)^{1/\beta}, +1, 0)$, which is 
-implemented in the R package `stabledist` by @stabledist.
+To test our inference method, we have simulated independent waiting time and magnitude pairs $(W_k, J_k)$.
+The distribution of $J_k$ is irrelevant for the inference on $\beta$ and $\sigma_0$ (it just plays a role for the rescaling of $\hat{\sigma}_0$, which gets done to receive an estimate for the scale parameter of the exceedances).
+Hence we choosed exponential distributed magnitudes in all considered examples.
+For the waitings times, we choosed a Stable, a Pareto and an Exponential distribution.
+In order to have exact analytical values available for $\beta$ and $\sigma_0$, a distribution for $W_k$ needs to be chosen for which $b(n)$ from \eqref{eq:stability} is known.
+In our first example, we choose $W_k \stackrel{d}{=} D$, where $D$ is as in \eqref{eq:stability}, then due to the stability property we have the *equality* of distribution $W_1 + \ldots + W_n \stackrel{d}{=} b(n) D$, for $b(n) = n^{1/\beta}$.
+Using the parametrisation of @SamorodnitskyTaqqu, a few lines of calculation (see e.g.
+the vignette on parametrisation in @MittagLeffleR) show that $D$ must have the stable distribution $S_\beta(\cos(\pi \beta/2)^{1/\beta}, +1, 0)$, which is implemented in the R package `stabledist` by @stabledist.
+If we choose $W_k$ to be Pareto distributed or more precisecly
+\begin{align*}
+P(W_k>t)= C t^{-\beta}
+\end{align*}
+with $C:=(1/\Gamma(1-\beta))^{1/\beta}$ and $b(n)=n^{1/\beta}$ we get 
+\begin{align*}
+\frac{W_1 + \ldots + W_n}{b(n)} \stackrel{d}{\Rightarrow} D
+\end{align*}
+with $E(\exp(-sD))=\exp(-s^{\beta})$.
 
@@
 
-The "complete Hard X Ray Burst Spectrometer event list" 
-is a comprehensive reference for all measurements of the Hard X 
-Ray Burst Spectrometer on NASA's Solar Maximum Mission from the time of 
-launch on Feb 14, 1980 to the end of the mission in Dec 1989. 12,776 
-events were detected, with the "vast 
-majority being solar flares". The list includes the start time, peak time, 
-duration, and peak rate of each event. We have used "start time" as the 
-variable for event times, and "peak rate" as the variable for event 
-magnitudes.
+We now want to apply the proposed method to a real data example, the solar flare data which was already mentioned in Section 1 and can be seen in Figure \ref{fig:thresholdedBursty}.
+The data were extracted from the "complete Hard X Ray Burst Spectrometer event list", a comprehensive reference for all measurements of the Hard X Ray Burst Spectrometer on NASA's Solar Maximum Mission from the time of launch on Feb 14, 1980 to the end of the mission in Dec 1989.
+12,776 events were detected, with the "vast  majority being solar flares".
+The list includes the start time, peak time, duration, and peak rate of each event.
+We have used "start time" as the variable for event times, and "peak rate" as the variable for event magnitudes.
 
-## Checking Model Assumptions
-
-The CTRE model is based on three main assumptions, which are repeated 
-below. For each assumption, we suggest one means of checking if it holds:
+Before we apply the POT approach described in Section 5 to the solar flare data, we first have to check if all model assumptions are full-filled.
+The CTRE model is based on three main assumptions, which are repeated below.
+For each assumption, we suggest one means of checking if it holds:
 
@@
 
-Figures \ref{fig:flare-diagnostics-1} and \ref{fig:flare-diagnostics-2} 
-show the diagnostic plots for a minimum threshold chosen at the 200th order statistic. 
+Figures \ref{fig:flare-diagnostics-1} and \ref{fig:flare-diagnostics-2} show the diagnostic plots for a minimum threshold chosen at the 200th order statistic.
 There is some residual autocorrelation for the sequence of threshold exceedance times that is not accounted for by the CTRE model.
-The fit with a Mittag-Leffler distribution ($\beta = 0.8$) is good, though there are signs that the power-law tail tapers off for very large inter-threshold crossing times.
-There is no apparent dependence between threshold exceedance times and event magnitudes seen in the copula plot.
 
@@
 empcopula(flares_ctre)
-flares_ctre %>% interarrival() %>% mlqqplot(log = 'xy', tail = 0.8, main = "Mittag-Leffler QQ Plot")
+flares_ctre %>% interarrival() %>% mlqqplot(log = 'xy', tail = 0.85, main = "Mittag-Leffler QQ Plot")
 ```
+
+Figure \ref{fig:flares} shows the stability plots for the solar flare data, on the left for the tail parameter and on the right for the scale parameter.
+The stability plot for the tail stabilizes nicely round about 0.85 (dotted line), while it is a little bit harder to deduce an estimate for the scale parameter.
+Howerever, the stability plot for the scale parameter seems to stabilize round about $3 \times 10^7$.
 
@@
 
+The fit with a Mittag-Leffler distribution ($\beta = 0.85$) is good, though there are signs that the power-law tail tapers off for very large inter-threshold crossing times.
+There is no apparent dependence between threshold exceedance times and event magnitudes seen in the copula plot.
+We also counduct a bootstrapped LRT for the null hypothesis of exponential distributed inter-arrival times and received a $p$-value of
+
+```{r likelihood-ratio-test}
+library("MittagLeffleR")
+library("stats")
+
+# ML_LRT_boot<-function(data,signi=0.05,m=1000,n){
+# if(is.null(dim(data))){
+# mle_data<-mlmle(data)                                                   #Calculate loglikelihoods for obserevd data
+# teststat<-2*(mle_data$loglik-mle_data$null_loglik)}                     #Calculate teststatistic for obserevd data
+# else{
+# l<-apply(data,MARGIN=2,FUN=mlmle)                                       #Extension to multivariate datasets for simulation studies
+# teststat<-2*(unlist(lapply(l,"[[",2))-unlist(lapply(l,"[[",3)))
+# }
+# 
+# x<-replicate(m,rexp(n,rate=1))                                          #Sample data under Null
+# l2<-apply(x,MARGIN=2,FUN=mlmle)                                         #Calculate loglikelihoods for each simulated data set
+# test_stat_null<-2*(unlist(lapply(l2,"[[",2))-unlist(lapply(l2,"[[",3))) #Calculate teststatistic for each simulated data set
+# q<-stats::quantile(test_stat_null,probs=1-signi)                               #Calculate 1-signi quantile of simulated distribution of the test statistic
+# #decision<-as.numeric(teststat>q)                                       #Gives One if Hypothesis gets rejected, 0 otherwise
+# f<-function(x,y){
+#   r<-as.numeric(x>y)
+#   return(r)
+# }
+# decision<-mapply(teststat,FUN=f,y=q)
+# decision<-return(decision)
+# }
+# flares_arrivals <- flares %>% ctre() %>% thin(k = 700) %>% interarrival()
+# p_value <- ML_LRT_boot(data=flares_arrivals,n=length(flares_arrivals))
+```
+
 # Discussion & Conclusion
 
-We have extended the POT (Peaks over Threshold) model, a mainstay of 
-extreme value theory, to "bursty" time series, which have been studied 
+We have extended the POT (Peaks over Threshold) model, a mainstay of extreme value theory, to "bursty" time series, which have been studied 
 intensively in statistical physics.
-Burstiness is characterized by power-law waiting times between events, 
-and we have shown that the Mittag-Leffler distribution arises naturally 
-as a scaling limit for the inter-exceedance times of high thresholds. 
-Moreover, we have derived the following non-linear scaling behaviour: 
-$\sigma \sim p^{-1/\beta}$, 
-where $\sigma$ is the scale parameter of the distribution of threshold 
-exceedance times, 
-$p$ is the fraction of magnitudes above the threshold, 
-and $\beta$ the exponent of the power law. 
-This "anomalous" scaling behaviour in the bursty setting entails two 
-phenomena:
+Burstiness is characterized by power-law waiting times between events, and we have shown that the Mittag-Leffler distribution arises naturally as a scaling limit for the inter-exceedance times of high thresholds.
+Moreover, we have derived the following non-linear scaling behaviour: $\sigma \sim p^{-1/\beta}$, where $\sigma$ is the scale parameter of the distribution of threshold
+exceedance times, $p$ is the fraction of magnitudes above the threshold, and $\beta$ the exponent of the power law. 
+This "anomalous" scaling behaviour in the bursty setting entails two phenomena:
 
-i) a heavy tail of the interarrival time distribution of 
-threshold crossings (long rests), and
+i) a heavy tail of the interarrival time distribution of threshold crossings (long rests), and
 
-ii) a high propensity for more threshold crossing events immediately after 
-each threshold crossing event (bursts).
+ii) a high propensity for more threshold crossing events immediately after each threshold crossing event (bursts).
 
-The Mittag-Leffler distribution captures both phenomena, due to its heavy
-tail as well as its stretched exponential (peaked) asymptotics for small 
-times. 
-It generalizes the exponential distribution, and 
-in the solar flare data example, this generalization 
-is warranted, because the likelihood-ratio test is strongly significant.
+The Mittag-Leffler distribution captures both phenomena, due to its heavy tail as well as its stretched exponential (peaked) asymptotics for small times.
+It generalizes the exponential distribution, and in the solar flare data example, this generalization is warranted, because the likelihood-ratio test is strongly significant.
 
@@
 This assumption is likely sufficient but not necessary for our limit theorem to hold.
-Moreover, any data below a (minimum) threshold $\ell_0$ is discarded for 
-CTREs, and hence need not satisfy the i.i.d. assumption.
-For the purposes of statistical inference, we merely require that the 
-inter-threshold-crossing times are i.i.d.
+Moreover, any data below a (minimum) threshold $\ell_0$ is discarded for CTREs, and hence need not satisfy the i.i.d.
+assumption.For the purposes of statistical inference, we merely require that the inter-threshold-crossing times are i.i.d.
 
-The bursty CTRE approach to model "non-Poissonian" threshold crossing times
-should be contrasted with the (now standard) approach of clusters of 
-extremes, see e.g. @ferro2003inference. In this approach, i.i.d. event 
-sequences of magnitudes are generalized to stationary sequences of
-event magnitudes (subject to a mixing condition). The two approaches are 
-fundamentally different: A clustering model assumes that each event 
-belongs to one particular (latent) group of events. For bursts, however,
-the aim is to identify an underlying scale-free pattern in the event 
-dynamics, which is often characteristic of complex systems.
-It is an interesting open problem to develop quality criteria, based
-e.g. on measures of surprise [@Lee15], which guide an applied statistician in 
-the choice between a clustering and a CTRE approach for a particular 
-problem. Moreover, we believe it may be possible to unify the two approaches
-by considering CTREs based on MRPs with a _stationary_, rather than 
-i.i.d., sequence of magnitudes.
+The bursty CTRE approach to model "non-Poissonian" threshold crossing times should be contrasted with the (now standard) approach of clusters of extremes, see e.g.
+@ferro2003inference.
+In this approach, i.i.d.
+event sequences of magnitudes are generalized to stationary sequences of
+event magnitudes (subject to a mixing condition). The two approaches are fundamentally different: A clustering model assumes that each event 
+belongs to one particular (latent) group of events. For bursts, however, the aim is to identify an underlying scale-free pattern in the event 
+dynamics, which is often characteristic of complex systems. It is an interesting open problem to develop quality criteria, based
+e.g.
+on measures of surprise [@Lee15], which guide an applied statistician in the choice between a clustering and a CTRE approach for a particular problem.
+Moreover, we believe it may be possible to unify the two approaches by considering CTREs based on MRPs with a _stationary_, rather than i.i.d., sequence of magnitudes.
 
-Finally, a purely scale-free pattern for event times may be too rigid an 
-assumption for some bursty time series, 
-because often the heavy-tailed character of the inter-arrival time
-distribution does not hold at all time scales; rather, it applies at 
-short and intermediate time scales, and is truncated (or tempered, 
-reverting to an exponential distribution) at 
-very long time scales [see e.g. @MeerschaertRoyQin; and @Aban06]. 
-In such situations, a "tempered" Mittag-Leffler distribution may provide 
-a more realistic fit, which we aim to introduce in follow-up work.
+Finally, a purely scale-free pattern for event times may be too rigid as an 
+assumption for some bursty time series, because often the heavy-tailed character of the inter-arrival time
+distribution does not hold at all time scales; rather, it applies at short and intermediate time scales, and is truncated (or tempered, 
+reverting to an exponential distribution) at very long time scales [see e.g.
+@MeerschaertRoyQin; and @Aban06].
+In such situations, a "tempered" Mittag-Leffler distribution may provide a more realistic fit, which we aim to introduce in follow-up work.
 

### 2018-12-03 article_springer/article_springer.Rmd
add stability plots for Example 1 and Example 2

@@
 Since the exponential distribution is nested in the Mittag-Leffler family of distributions, an appropriate way to choose between a model with exponential and Mittag-Leffler inter-exceedance times seems to be a Likelihood ratio test.
-Although the two models are nested, the assymptotic distribution is not $\chi^2_1$-distributed, the classical Theorem of Wilk doesn't apply since under $H_0$ the paremter $\beta$ of Mittag-Leffler distribution is equal to zero and hence lies under $H_0$ on the boundary of the parameter space $(0,1]$.
-But one can perform a bootstrapped log-likelihood ratio test.
+Although the two models are nested, the assymptotic distribution is not $\chi^2_1$-distributed, the classical Theorem of Wilk doesn't apply since under $H_0$ the parameter $\beta$ of the Mittag-Leffler distribution is equal to one and hence lies under $H_0$ on the boundary of the parameter space $(0,1]$.
+Nonetheless, one can perform a bootstrapped log-likelihood ratio test.
 In Figure \ref{Fig:LRT} one can see the power for the bootstrapped LRT for Mittag-Leffler distributions with different tail parameters.
 As expected the power gets smaller for tail parameters close to one, since the Mittag-Leffler distribution converges for $\beta \rightarrow 1$ to an exponential distribution.
-Hence, for tail parameters close to one it is hard to differentiate a Mittag-Lefller distribution from an exponential.
+Consequently, for tail parameters close to one it is hard to differentiate a Mittag-Lefller distribution from an exponential.
 
@@
 The Theorem in Section \ref{sec:scaling} implies that for a high 
-threshold $\ell$ we may 
-approximate the distribution of $T(\ell)$ with an 
+threshold $\ell$ we may approximate the distribution of $T(\ell)$ with an 
 ${\rm ML}(\beta, b(1/p))$ distribution, 
-where $b(\,)$ varies regularly at $\infty$ with parameter $1/\beta$.
-Building on the POT (Peaks Over Threshold) method, we propose the 
-following estimation procedure for the distribution of $T(\ell)$:
+where the function $b(c)$ varies regularly at $\infty$ with parameter $1/\beta$.
+Building on the POT (Peaks Over Threshold) method, we propose the following estimation procedure for the distribution of inter-exceedance time $T(\ell)$:
 
-1. For a range of thresholds $\ell$ near the largest order statistics, 
-  extract datasets of exceedance times $\{T(\ell, i)\}_i$.
+1. For a range of thresholds $\ell$ near the largest order statistics, extract datasets of exceedance times $\{T(\ell, i)\}_i$.
 
-2. For each choice of threshold $\ell$, 
-  fit a Mittag-Leffler distribution to the resulting dataset
-  $\{T(\ell, i)\}_i$. 
-  This results in the estimates $\{\hat\beta(\ell)\}_\ell$ and 
-  $\{\hat \sigma(\ell)\}_\ell$.
+2. For each choice of threshold $\ell$, fit a Mittag-Leffler distribution to the resulting dataset
+  $\{T(\ell, i)\}_i$.  This results in the estimates $\{\hat\beta(\ell)\}_\ell$ and $\{\hat \sigma(\ell)\}_\ell$.
 
 3. Plot $\ell$ vs.\ $\hat \beta(\ell)$. As $\ell$ increases towards $x_R$, 
-  $\hat \beta(\ell)$ *stabilizes* around a constant $\hat \beta$. 
-  Use $\hat \beta$ as an estimate for the tail parameter $\beta$ of the
-  Mittag-Leffler distribution of exceedance times.
+  $\hat \beta(\ell)$ *stabilizes* around a constant $\hat \beta$. Use $\hat \beta$ as an estimate for the tail      parameter $\beta$ of the Mittag-Leffler distribution of exceedance times.
 
@@
 $$
-T_\ell \sim {\rm ML}(\beta, k^{1/\beta} \sigma_0), 
+T(\ell) \sim {\rm ML}(\beta, k^{-1/\beta} \sigma_0), 
 $$
@@
 $$
-p(t|\beta, \sigma_0, \ell, t_0) = \frac{f(t + t_0 | \beta, k^{1/\beta} \sigma_0)}{\mathbf P[T_\ell > t_0]}
+p(t|\beta, \sigma_0, \ell, t_0) = \frac{f(t + t_0 | \beta, k^{-1/\beta} \sigma_0)}{\mathbf P[T_\ell > t_0]}
 $$
-where $f(\,\cdot\, | \beta, k^{1/\beta} \sigma_0)$ is the probability density of ${\rm ML}(\beta, k^{1/\beta} \sigma_0)$. 
+where $f(\,\cdot\, | \beta, k^{-1/\beta} \sigma_0)$ is the probability density of ${\rm ML}(\beta, -k^{1/\beta} \sigma_0)$. 
 The more time has passed without a threshold crossing, the more the probability distribution shifts towards larger values for the next crossing
@@
 $$
-h(t) = \frac{f(t| \beta, k^{1/\beta} \sigma_0))}{\int_t^\infty f(\tau| \beta, k^{1/\beta} \sigma_0))\,d\tau}
+h(t) = \frac{f(t| \beta, k^{-1/\beta} \sigma_0))}{\int_t^\infty f(\tau| \beta, k^{-1/\beta} \sigma_0))\,d\tau}
 $$
@@
 Hence we choosed exponential distributed magnitudes in all considered examples.
-For the waitings times, we choosed a Stable, a Pareto and an Exponential distribution.
+For the waitings times, we choosed (i) a Stable, (ii) a Pareto and (iii) an Exponential distribution.
 In order to have exact analytical values available for $\beta$ and $\sigma_0$, a distribution for $W_k$ needs to be chosen for which $b(n)$ from \eqref{eq:stability} is known.
@@
 
+```{r Ex1figs, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex1figs} Stability Plots for m=100 simulation runs for Example 1 (stable distributed waiting times, true tail parameter =0.8).
+The grey lines, the red line and the blue lines are the log Moment, the MLE and the hill estimator, repectively, for different $k$'s on the x-axis.
+The dark lines in each picture are the means of the concerning estimators for different $k$'s.", fig.show='hold', out.width = '32%'}
+knitr::include_graphics(c("SimuStudy_StabilityPlots_Tail08_logMoms.pdf","SimuStudy_StabilityPlots_Tail08_mles.pdf","SimuStudy_StabilityPlots_Tail08_hill.pdf"))
+```
+
+```{r Ex2figs, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex2figs} Stability Plots for m=100 simulation runs for Example 2 (Pareto distributed waiting times, true tail parameter =0.8).
+The grey lines, the red line and the blue lines are the log Moment, the MLE and the hill estimator, repectively, for different $k$'s on the x-axis.
+The dark lines in each picture are the means of the concerning estimators for different $k$'s.", fig.show='hold', out.width = '32%'}
+knitr::include_graphics(c("SimuStudy_StabilityPlots_Ex2_Tail08_logMoms.pdf","SimuStudy_StabilityPlots_Ex2_Tail08_mles.pdf","SimuStudy_StabilityPlots_Ex2_Tail08_hill.pdf"))
+```
 # Data example
@@
 
-The authors would like to thank Prof. Peter Scheffler for insights on 
-stochastic process limits for CTRMs, Roloand Fried for discussion according the statistical methods and Gurtek Gill who helped create the MittagLeffleR R-package.
+The authors would like to thank Prof.
+Peter Scheffler for insights on stochastic process limits for CTRMs, Roloand Fried for discussion according the statistical methods and Gurtek Gill who helped create the MittagLeffleR R-package.
 

### 2018-12-03 article_springer/article_springer.Rmd
Add plots tail parameter Exponential Example

@@
 
-```{r LRT power, echo=FALSE, fig.cap="\\label{Fig:LRT} Power for bootstrapped LRT for different sample sizes", out.width = '100%'}
+```{r LRT power, echo=FALSE, fig.cap="\\label{Fig:LRT} Power for bootstrapped LRT for different sample sizes", out.width = '90%'}
 knitr::include_graphics("Plots_LRT_boot.pdf")
@@
 represents the risk of a threshold crossing per unit time, and is a decreasing function for the Mittag-Leffler distribution. 
-```{r hazard, fig.height=5, fig.cap="Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\\beta = 0.8$, $\\sigma_0 = 1$).
+```{r hazard, fig.height=4, fig.cap="Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\\beta = 0.8$, $\\sigma_0 = 1$).
 Right: Hazard rate depending on tail parameter $\\beta$.\\label{fig:hazard}"}
@@
 
-To test our inference method, we have simulated independent waiting time and magnitude pairs $(W_k, J_k)$.
+To test our inference method, we performed a simulation study where we have simulated independent waiting time and magnitude pairs $(W_k, J_k)$.
+Since the estimation of the parameters of the inter-exceedance times is based on stability plots and is hence rather a graphical estimation procedure, it is difficult to conduct a simulation study.
+To get an impression of how our estimation procedure performs, we plotted $m=100$ stability plots for each example and calculated for each $k$ the mean value of all estimates.
+We have chosen (i) a Stable, (ii) a Pareto and (iii) an Exponential distribution for waiting times.
 The distribution of $J_k$ is irrelevant for the inference on $\beta$ and $\sigma_0$ (it just plays a role for the rescaling of $\hat{\sigma}_0$, which gets done to receive an estimate for the scale parameter of the exceedances).
-Hence we choosed exponential distributed magnitudes in all considered examples.
-For the waitings times, we choosed (i) a Stable, (ii) a Pareto and (iii) an Exponential distribution.
+Hence we have chosen exponential distributed magnitudes in all considered examples.
 In order to have exact analytical values available for $\beta$ and $\sigma_0$, a distribution for $W_k$ needs to be chosen for which $b(n)$ from \eqref{eq:stability} is known.
-In our first example, we choose $W_k \stackrel{d}{=} D$, where $D$ is as in \eqref{eq:stability}, then due to the stability property we have the *equality* of distribution $W_1 + \ldots + W_n \stackrel{d}{=} b(n) D$, for $b(n) = n^{1/\beta}$.
+In our first example, we have chosen $W_k \stackrel{d}{=} D$, where $D$ is as in \eqref{eq:stability}.
+Then due to the stability property we have the *equality* of distribution $W_1 + \ldots + W_n \stackrel{d}{=} b(n) D$, for $b(n) = n^{1/\beta}$.
 Using the parametrisation of @SamorodnitskyTaqqu, a few lines of calculation (see e.g.
 the vignette on parametrisation in @MittagLeffleR) show that $D$ must have the stable distribution $S_\beta(\cos(\pi \beta/2)^{1/\beta}, +1, 0)$, which is implemented in the R package `stabledist` by @stabledist.
-If we choose $W_k$ to be Pareto distributed or more precisecly
+In the second examaple we have chosen $W_k$ to be Pareto distributed or more precisecly
 \begin{align*}
@@
 \end{align*}
-with $C:=(1/\Gamma(1-\beta))^{1/\beta}$ and $b(n)=n^{1/\beta}$ we get 
+with $C:=(1/\Gamma(1-\beta))^{1/\beta}$ and $b(n)=n^{1/\beta}$. We then receive
 \begin{align*}
@@
 with $E(\exp(-sD))=\exp(-s^{\beta})$.
-
-```{r make-caption}
-caption = "Tail and scale estimates for simulated data, with waiting times drawn from the stable distribution $S_\\beta(\\cos(\\pi \\beta/2)^{1/\\beta}, +1, 0)$ with $\\beta = 0.8$.
-Dashed lines are 95\\% confidence intervals, dotted lines are the known theoretical values ($0.8$ and $10000^{1/0.8}$).
-\\label{fig:sim}"
-```
-
-```{r simulated-example, message=FALSE, fig.cap=caption}
-k_max <- 500 
-thin_sim_ctre <- thin(ctre = sim_ctre, k = k_max)
-par(mfrow=c(1,2))
-MLestimates(ctre = thin_sim_ctre, tail = params$tail, scale = n^(1/params$tail))
-```
 
@@
 $\sigma_0 = n^{1/\beta}$.
-The distribution of $J_k$ is irrelevant for the inference on $\beta$ and 
-$\sigma_0$ (we have chosen unit exponential random variables). 
-Figure \ref{fig:sim} displays plots of $\hat \beta(\ell)$ and 
-$\hat \sigma(\ell)$ vs. $k$; recall that $k$ is the index of the order
-statistics of $J_k$ at which the threshold $\ell$ is placed. 
-Dotted lines show 95% confidence intervals, which are derived from the 
-asymptotic normality of the log-moments estimators [@Cahoy2013] and the $\delta$-method [@MittagLeffleR].
-The dashed lines show the actual values of $\beta$ resp.\ $\sigma_0$, 
-showing that our inference method identifies the 
-parameters correctly.
+we have chosen $\beta=1$ in the stable as well in the Pareto case.
+Figure \ref{Ex1figs} displays plots of $\hat \beta(k)$ vs.
+$k$ for the first example with stable distributed waiting times.
+In the left picture we used the log moment estimator, in the middle picture maximum likelihood estimates (both applied to the inter-exceedance times) and for the right picture hill estimators applied to the inter-arrival times.
+Recall that $k$ is the index of the order statistics of $J_k$ at which the threshold $\ell$ is placed.
 
@@
 ```
-
+Figure \ref{Ex2figs} shows the estimates fordifferent $k$'s and for the different estimators for the tail parameter $\beta$.
+Again one can see, that there is much more variance between the stability plots for the different simulation runs in case of the hill estimator compared to the other two estimators.
 ```{r Ex2figs, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex2figs} Stability Plots for m=100 simulation runs for Example 2 (Pareto distributed waiting times, true tail parameter =0.8).
@@
 ```
+To show how the different estimates behave in the case that $\beta=1$, hence, the inter-exceedance times are exponetial distributed, we simulated in a last example exponetial distributed waiting times.
+
+```{r Ex3figs, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex3figs} Stability Plots for m=100 simulation runs for Example 3 (Exponentially distributed waiting times, true tail parameter =0.8).
+The grey lines, the red line and the blue lines are the log Moment, the MLE and the hill estimator, repectively, for different $k$'s on the x-axis.
+The dark lines in each picture are the means of the concerning estimators for different $k$'s.", fig.show='hold', out.width = '32%'}
+knitr::include_graphics(c("SimuStudy_StabilityPlots_Ex3_logMoms.pdf","SimuStudy_StabilityPlots_Ex3_mles.pdf","SimuStudy_StabilityPlots_Ex3_hill_times.pdf"))
+```
+
 # Data example
@@
 Figure \ref{fig:flares} shows the stability plots for the solar flare data, on the left for the tail parameter and on the right for the scale parameter.
+Dotted lines show 95% confidence intervals, which are derived from the asymptotic normality of the log-moments estimators [@Cahoy2013] and the $\delta$-method [@MittagLeffleR, dashed lines show the actual values of $\beta$ resp.\ $\sigma_0$.
 The stability plot for the tail stabilizes nicely round about 0.85 (dotted line), while it is a little bit harder to deduce an estimate for the scale parameter.
@@
 There is no apparent dependence between threshold exceedance times and event magnitudes seen in the copula plot.
-We also counduct a bootstrapped LRT for the null hypothesis of exponential distributed inter-arrival times and received a $p$-value of
+We also counduct a bootstrapped LRT for the null hypothesis of exponential distributed inter-arrival times and received a $p$-value of $p<0.01$.
 

### 2018-12-05 article_springer/article_springer.Rmd
plot Figure 1 with ggplot2; update CTRE from Github

--- 2018-12-03 article_springer/article_springer.Rmd
@@
 
-```{r thresholdedBursty, message=FALSE, fig.height=7, fig.width=9, fig.cap="\\label{fig:thresholdedBursty}Exceedances (red) and Times until Exceedance (durations between blue crosses) for a given threshold $\\ell$ (dashed line)."}
+```{r thresholdedBursty, message=FALSE, fig.height=4, fig.width=6, fig.cap="\\label{fig:thresholdedBursty}Exceedances (red) and Times until Exceedance (durations between blue crosses) for a given threshold $\\ell$ (dashed line)."}
+
 tail <- params$tail
@@
 par(mfrow = c(2,1)) 
-plot(sim_ctre, p = 0.01, main = "Simulated MRP") 
-flares %>% ctre() %>% plot(p = 0.02, log = 'y', main = "HXRBS data") 
+p1 <- plot(sim_ctre, p = 0.01, main = "Simulated MRP") 
+p2 <- flares %>% ctre() %>% plot(p = 0.02, log = 'y', main = "HXRBS data") 
+library(gridExtra)
+grid.arrange(p1, p2, nrow = 2)
 ```
 
-In this article, we restrict ourselves to the uncoupled case, where W and J are independent.
+In this article, we restrict ourselves to the uncoupled case, where $W$ and $J$ are independent.
 Then the two sequences $X(\ell, n)_{n \in \mathbb N}$ and $T(\ell, n)_{n \in \mathbb N}$ are independent as well.
@@
 _without any_ events, whereas in the real-world dataset events appear continuously.
-The threshold exceedances, however, appear to have similar statistical behaviour in both models.
-Observations below a threshold are commonly discarded in Extreme Value Theory (POT approach); likewise, the CTRE model interprets these observations as noise and filters them out.
+The threshold exceedances, however, appear to have visually similar statistical behaviour in both models.
+Observations below a threshold are commonly discarded in Extreme Value Theory (POT approach); likewise, the CTRE model interprets these observations as noise and discards them.
 
@@
 
-The classical peaks over threshold approach is based on the fact, that exceedances above a high threshhold are assymptotically GPD distributed.
-Hence, a GPD distribution is fitted to the exceedances above a high enough threshhold.
-Due to the Theorem in the last Section, we know that for high threshholds the times between the exceedances are in case of heavy tailed inter-arrival times assymptotically Mittag-Leffler distributed.
-Therefore, before talking about inference for the exceedance times in the next section, we want to have a look at inference for Mittag-Leffler distributions in general.
+The classical POT approach is based on the fact, that exceedances above a high threshhold are assymptotically GPD distributed, hence a GPD distribution is fitted to the exceedances above a high enogh threshhold.
+Due to the Theorem in the last Section we know that for high threshholds the times between the exceedances are assymptotically Mittag-Leffler distributed in case of heavy tailed waiting times between the observations.
+Hence, before we talk about inference for the exceedances in the next section, we want to have a look at inference for Mittag-Leffler distributions in the following.
 
-The first method proposed in the literature to estimate the parameters of Mittag-Leffler distribution was the fractional moment estimator by [@kozubowski2001].
-Unlike the first moments, the fractional moments of order $p$ for $p<\beta$ exist and can get calculated by explicit formulas.
+The first method proposed for the estimation of the Mittag-Leffler distribution parameters was the fractional moment estimator by [@kozubowski2001].
+Unlike the first moments, the fractional moments of order $p$ for $p<\beta$ exist and can get calculated.
 One drawback of this method is that constant priors for the tail parameter are needed for the calculation of the estimates.
-Therefore, [@Cahoy2010] proposed an estimator based on the log-Moments which doesn't need prior knowledge.
+[@Cahoy2010] proposed an estimator based on the log-Moments which doesn't need prior knowledge.
 Furthermore, they showed in a simulation study that the log-Moment outclasses the fractional moment estimator regarding bias and root mean squared error (RMSE).
 Due to the form of the density function of a Mittag-Leffler distribution there exists no closed form for the Maximum Likelihood estimator (MLE).
-In the RPackage `MittagLeffleR` we implemented Maximum Likelihood estimation via an numerical optimization algorithm.
+In the RPackage `MittagLeffleR` Maximum Likelihood estimation is implemented via numerical optimization.
 The MLE outperforms the log-moment estimator regarding bias and RMSE for big enough sample sizes, but is extremely computational intensive and the differences in bias and RMSE between the two methods are very small.
@@
 In Figure \ref{fig:Hillplots} one can see different Hill plots for Mittag-Leffler simulated data with differrent sample sizes and tails.
-It would be really hard to deduce the correct tail parameter estimates from these plots.
+It would be really hard to deduce the correct tail parameter estimates from this plots.
 
@@
 knitr::include_graphics("Hillplots.pdf")
+```
+
+```{r likelihood-ratio-test}
+flares_arrivals <- flares %>% ctre() %>% thin(k = 500) %>% interarrival()
+mlmle_out <- mlmle(data = flares_arrivals)
 ```
@@
 where $\beta = 0.85$ and $\sigma_0 = 3.0 \times 10^7 {\rm sec}$. 
-Unlike the exponential distribution, the Mittag-Leffler distribution is not memoryless, and the probability density of the time $t$ until the next threshold crossing will depend on the time $t_0$ elapsed since the last threshold crossing.
+Unlike the exponential distribution, the Mittag-Leffler distribution is not 
+memoryless, and the probability density of the time $t$ until the next threshold 
+crossing will depend on the time $t_0$ elapsed since the last threshold crossing.
 This density equals 
@@
 $$
-where $f(\,\cdot\, | \beta, k^{1/\beta} \sigma_0)$ is the probability density of ${\rm ML}(\beta, k^{1/\beta} \sigma_0)$. 
-The more time has passed without a threshold crossing, the more the probability distribution shifts towards larger values for the next crossing
-(see Figure \ref{fig:hazard}, left panel). The hazard rate 
+where $f(\,\cdot\, | \beta, k^{1/\beta} \sigma_0)$ is the probability density of 
+${\rm ML}(\beta, k^{1/\beta} \sigma_0)$. 
+The more time has passed without a threshold crossing, the more the probability 
+distribution shifts towards larger values for the next crossing
+(see Figure \ref{fig:hazard}, left panel). 
+The hazard rate 
 $$
@@
 $$
-represents the risk of a threshold crossing per unit time, and is a decreasing function for the Mittag-Leffler distribution. 
+represents the risk of a threshold crossing per unit time, and is a 
+decreasing function for the Mittag-Leffler distribution. 
 ```{r hazard, fig.height=5, fig.cap="Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\\beta = 0.8$, $\\sigma_0 = 1$).
@@
 
+It is beyond the scope of the current paper to incorporate parameter 
+uncertainty into our predictive distribution for the next threshold crossing; 
+however, methods as described by @Scarrott12 and @Lee15 are likely 
+to extend to our setting.
+
 # Simulation study
 
-To test our inference method, we have simulated independent waiting time and magnitude pairs $(W_k, J_k)$.
-The distribution of $J_k$ is irrelevant for the inference on $\beta$ and $\sigma_0$ (it just plays a role for the rescaling of $\hat{\sigma}_0$, which gets done to receive an estimate for the scale parameter of the exceedances).
-Hence we choosed exponential distributed magnitudes in all considered examples.
-For the waitings times, we choosed a Stable, a Pareto and an Exponential distribution.
-In order to have exact analytical values available for $\beta$ and $\sigma_0$, a distribution for $W_k$ needs to be chosen for which $b(n)$ from \eqref{eq:stability} is known.
-In our first example, we choose $W_k \stackrel{d}{=} D$, where $D$ is as in \eqref{eq:stability}, then due to the stability property we have the *equality* of distribution $W_1 + \ldots + W_n \stackrel{d}{=} b(n) D$, for $b(n) = n^{1/\beta}$.
-Using the parametrisation of @SamorodnitskyTaqqu, a few lines of calculation (see e.g.
-the vignette on parametrisation in @MittagLeffleR) show that $D$ must have the stable distribution $S_\beta(\cos(\pi \beta/2)^{1/\beta}, +1, 0)$, which is implemented in the R package `stabledist` by @stabledist.
-If we choose $W_k$ to be Pareto distributed or more precisecly
-\begin{align*}
-P(W_k>t)= C t^{-\beta}
-\end{align*}
-with $C:=(1/\Gamma(1-\beta))^{1/\beta}$ and $b(n)=n^{1/\beta}$ we get 
-\begin{align*}
-\frac{W_1 + \ldots + W_n}{b(n)} \stackrel{d}{\Rightarrow} D
-\end{align*}
-with $E(\exp(-sD))=\exp(-s^{\beta})$.
+To test our inference method via stability plots, we have simulated 
+independent waiting time and magnitude pairs $(W_k, J_k)$ (see upper panel in 
+Figure \ref{fig:thresholdedBursty}) for three different situations: stable waiting times, Pareto waitings times and Exponential waiting times. In order to have exact 
+analytical values available for $\beta$ and $\sigma_0$, a distribution for 
+$W_k$ needs to be chosen for which $b(n)$ from \eqref{eq:stability} is known. 
+If we choose $W_k \stackrel{d}{=} D$, where $D$ is as in \eqref{eq:stability}, 
+then due to the stability property we have the *equality* of distribution
+$W_1 + \ldots + W_n \stackrel{d}{=} b(n) D$, 
+for $b(n) = n^{1/\beta}$. 
+Using the parametrisation of @SamorodnitskyTaqqu, a few lines of 
+calculation (see e.g. the vignette on parametrisation in @MittagLeffleR) 
+show that $D$ must have the stable distribution 
+$S_\beta(\cos(\pi \beta/2)^{1/\beta}, +1, 0)$, which is 
+implemented in the R package `stabledist` by @stabledist.
 
@@
 
-We now want to apply the proposed method to a real data example, the solar flare data which was already mentioned in Section 1 and can be seen in Figure \ref{fig:thresholdedBursty}.
-The data were extracted from the "complete Hard X Ray Burst Spectrometer event list", a comprehensive reference for all measurements of the Hard X Ray Burst Spectrometer on NASA's Solar Maximum Mission from the time of launch on Feb 14, 1980 to the end of the mission in Dec 1989.
-12,776 events were detected, with the "vast  majority being solar flares".
-The list includes the start time, peak time, duration, and peak rate of each event.
-We have used "start time" as the variable for event times, and "peak rate" as the variable for event magnitudes.
+The "complete Hard X Ray Burst Spectrometer event list" 
+is a comprehensive reference for all measurements of the Hard X 
+Ray Burst Spectrometer on NASA's Solar Maximum Mission from the time of 
+launch on Feb 14, 1980 to the end of the mission in Dec 1989. 12,776 
+events were detected, with the "vast 
+majority being solar flares". The list includes the start time, peak time, 
+duration, and peak rate of each event. We have used "start time" as the 
+variable for event times, and "peak rate" as the variable for event 
+magnitudes.
 
-Before we apply the POT approach described in Section 5 to the solar flare data, we first have to check if all model assumptions are full-filled.
-The CTRE model is based on three main assumptions, which are repeated below.
-For each assumption, we suggest one means of checking if it holds:
+## Checking Model Assumptions
+
+The CTRE model is based on three main assumptions, which are repeated 
+below. For each assumption, we suggest one means of checking if it holds:
 
@@
 
-Figures \ref{fig:flare-diagnostics-1} and \ref{fig:flare-diagnostics-2} show the diagnostic plots for a minimum threshold chosen at the 200th order statistic.
+Figures \ref{fig:flare-diagnostics-1} and \ref{fig:flare-diagnostics-2} 
+show the diagnostic plots for a minimum threshold chosen at the 200th order statistic. 
 There is some residual autocorrelation for the sequence of threshold exceedance times that is not accounted for by the CTRE model.
+The fit with a Mittag-Leffler distribution ($\beta = 0.8$) is good, though there are signs that the power-law tail tapers off for very large inter-threshold crossing times.
+There is no apparent dependence between threshold exceedance times and event magnitudes seen in the copula plot.
 
@@
 empcopula(flares_ctre)
-flares_ctre %>% interarrival() %>% mlqqplot(log = 'xy', tail = 0.85, main = "Mittag-Leffler QQ Plot")
+flares_ctre %>% interarrival() %>% mlqqplot(log = 'xy', tail = 0.8, main = "Mittag-Leffler QQ Plot")
 ```
-
-Figure \ref{fig:flares} shows the stability plots for the solar flare data, on the left for the tail parameter and on the right for the scale parameter.
-The stability plot for the tail stabilizes nicely round about 0.85 (dotted line), while it is a little bit harder to deduce an estimate for the scale parameter.
-Howerever, the stability plot for the scale parameter seems to stabilize round about $3 \times 10^7$.
 
@@
 
-The fit with a Mittag-Leffler distribution ($\beta = 0.85$) is good, though there are signs that the power-law tail tapers off for very large inter-threshold crossing times.
-There is no apparent dependence between threshold exceedance times and event magnitudes seen in the copula plot.
-We also counduct a bootstrapped LRT for the null hypothesis of exponential distributed inter-arrival times and received a $p$-value of
-
-```{r likelihood-ratio-test}
-library("MittagLeffleR")
-library("stats")
-
-# ML_LRT_boot<-function(data,signi=0.05,m=1000,n){
-# if(is.null(dim(data))){
-# mle_data<-mlmle(data)                                                   #Calculate loglikelihoods for obserevd data
-# teststat<-2*(mle_data$loglik-mle_data$null_loglik)}                     #Calculate teststatistic for obserevd data
-# else{
-# l<-apply(data,MARGIN=2,FUN=mlmle)                                       #Extension to multivariate datasets for simulation studies
-# teststat<-2*(unlist(lapply(l,"[[",2))-unlist(lapply(l,"[[",3)))
-# }
-# 
-# x<-replicate(m,rexp(n,rate=1))                                          #Sample data under Null
-# l2<-apply(x,MARGIN=2,FUN=mlmle)                                         #Calculate loglikelihoods for each simulated data set
-# test_stat_null<-2*(unlist(lapply(l2,"[[",2))-unlist(lapply(l2,"[[",3))) #Calculate teststatistic for each simulated data set
-# q<-stats::quantile(test_stat_null,probs=1-signi)                               #Calculate 1-signi quantile of simulated distribution of the test statistic
-# #decision<-as.numeric(teststat>q)                                       #Gives One if Hypothesis gets rejected, 0 otherwise
-# f<-function(x,y){
-#   r<-as.numeric(x>y)
-#   return(r)
-# }
-# decision<-mapply(teststat,FUN=f,y=q)
-# decision<-return(decision)
-# }
-# flares_arrivals <- flares %>% ctre() %>% thin(k = 700) %>% interarrival()
-# p_value <- ML_LRT_boot(data=flares_arrivals,n=length(flares_arrivals))
-```
-
 # Discussion & Conclusion
 
-We have extended the POT (Peaks over Threshold) model, a mainstay of extreme value theory, to "bursty" time series, which have been studied 
+We have extended the POT (Peaks over Threshold) model, a mainstay of 
+extreme value theory, to "bursty" time series, which have been studied 
 intensively in statistical physics. 
-Burstiness is characterized by power-law waiting times between events, and we have shown that the Mittag-Leffler distribution arises naturally as a scaling limit for the inter-exceedance times of high thresholds.
-Moreover, we have derived the following non-linear scaling behaviour: $\sigma \sim p^{-1/\beta}$, where $\sigma$ is the scale parameter of the distribution of threshold
-exceedance times, $p$ is the fraction of magnitudes above the threshold, and $\beta$ the exponent of the power law. 
-This "anomalous" scaling behaviour in the bursty setting entails two phenomena:
+Burstiness is characterized by power-law waiting times between events, 
+and we have shown that the Mittag-Leffler distribution arises naturally 
+as a scaling limit for the inter-exceedance times of high thresholds. 
+Moreover, we have derived the following non-linear scaling behaviour: 
+$\sigma \sim p^{-1/\beta}$, 
+where $\sigma$ is the scale parameter of the distribution of threshold 
+exceedance times, 
+$p$ is the fraction of magnitudes above the threshold, 
+and $\beta$ the exponent of the power law. 
+This "anomalous" scaling behaviour in the bursty setting entails two 
+phenomena:
 
-i) a heavy tail of the interarrival time distribution of threshold crossings (long rests), and
+i) a heavy tail of the interarrival time distribution of 
+threshold crossings (long rests), and
 
-ii) a high propensity for more threshold crossing events immediately after each threshold crossing event (bursts).
+ii) a high propensity for more threshold crossing events immediately after 
+each threshold crossing event (bursts).
 
-The Mittag-Leffler distribution captures both phenomena, due to its heavy tail as well as its stretched exponential (peaked) asymptotics for small times.
-It generalizes the exponential distribution, and in the solar flare data example, this generalization is warranted, because the likelihood-ratio test is strongly significant.
+The Mittag-Leffler distribution captures both phenomena, due to its heavy
+tail as well as its stretched exponential (peaked) asymptotics for small 
+times. 
+It generalizes the exponential distribution, and 
+in the solar flare data example, this generalization 
+is warranted, because the likelihood-ratio test is strongly significant.
 
@@
 This assumption is likely sufficient but not necessary for our limit theorem to hold. 
-Moreover, any data below a (minimum) threshold $\ell_0$ is discarded for CTREs, and hence need not satisfy the i.i.d.
-assumption.For the purposes of statistical inference, we merely require that the inter-threshold-crossing times are i.i.d.
+Moreover, any data below a (minimum) threshold $\ell_0$ is discarded for 
+CTREs, and hence need not satisfy the i.i.d. assumption.
+For the purposes of statistical inference, we merely require that the 
+inter-threshold-crossing times are i.i.d.
 
-The bursty CTRE approach to model "non-Poissonian" threshold crossing times should be contrasted with the (now standard) approach of clusters of extremes, see e.g.
-@ferro2003inference.
-In this approach, i.i.d.
-event sequences of magnitudes are generalized to stationary sequences of
-event magnitudes (subject to a mixing condition). The two approaches are fundamentally different: A clustering model assumes that each event 
-belongs to one particular (latent) group of events. For bursts, however, the aim is to identify an underlying scale-free pattern in the event 
-dynamics, which is often characteristic of complex systems. It is an interesting open problem to develop quality criteria, based
-e.g.
-on measures of surprise [@Lee15], which guide an applied statistician in the choice between a clustering and a CTRE approach for a particular problem.
-Moreover, we believe it may be possible to unify the two approaches by considering CTREs based on MRPs with a _stationary_, rather than i.i.d., sequence of magnitudes.
+The bursty CTRE approach to model "non-Poissonian" threshold crossing times
+should be contrasted with the (now standard) approach of clusters of 
+extremes, see e.g. @ferro2003inference. In this approach, i.i.d. event 
+sequences of magnitudes are generalized to stationary sequences of
+event magnitudes (subject to a mixing condition). The two approaches are 
+fundamentally different: A clustering model assumes that each event 
+belongs to one particular (latent) group of events. For bursts, however,
+the aim is to identify an underlying scale-free pattern in the event 
+dynamics, which is often characteristic of complex systems.
+It is an interesting open problem to develop quality criteria, based
+e.g. on measures of surprise [@Lee15], which guide an applied statistician in 
+the choice between a clustering and a CTRE approach for a particular 
+problem. Moreover, we believe it may be possible to unify the two approaches
+by considering CTREs based on MRPs with a _stationary_, rather than 
+i.i.d., sequence of magnitudes.
 
-Finally, a purely scale-free pattern for event times may be too rigid as an 
-assumption for some bursty time series, because often the heavy-tailed character of the inter-arrival time
-distribution does not hold at all time scales; rather, it applies at short and intermediate time scales, and is truncated (or tempered, 
-reverting to an exponential distribution) at very long time scales [see e.g.
-@MeerschaertRoyQin; and @Aban06].
-In such situations, a "tempered" Mittag-Leffler distribution may provide a more realistic fit, which we aim to introduce in follow-up work.
+Finally, a purely scale-free pattern for event times may be too rigid an 
+assumption for some bursty time series, 
+because often the heavy-tailed character of the inter-arrival time
+distribution does not hold at all time scales; rather, it applies at 
+short and intermediate time scales, and is truncated (or tempered, 
+reverting to an exponential distribution) at 
+very long time scales [see e.g. @MeerschaertRoyQin; and @Aban06]. 
+In such situations, a "tempered" Mittag-Leffler distribution may provide 
+a more realistic fit, which we aim to introduce in follow-up work.
 

### 2018-12-05 article_springer/article_springer.Rmd
minor changes

@@
 
-  This article provides a new model for the threshold inter-exceedance _times_;
+  This article proposes a new model for the _inter-exceedance times_ of thresholds;
   the threshold exceedances are modeled via the standard 
@@
 All code and data used for the analysis in this article has been organized into 
-an R package `CTRE` (<https://github.com/UNSW-MATH/CTRE>).
+an R package `CTRE` (<https://github.com/strakaps/CTRE>).
 The source code for the figures generated in this manuscript is 
-available online at <https://github.com/UNSW-MATH/bursty-POT>.
+available online at <https://github.com/strakaps/bursty-POT>.
 
@@
 
-In this section we will As a model for extreme observations, we use a Marked Renewal Process (MRP):
+As a model for extreme observations, we use a Marked Renewal Process (MRP):
 
@@
 
-Note that the $k$-th magnitude $J_k$ occurs at time
+We assume that the $k$-th magnitude $J_k$ occurs at time
 $T_k = W_1 + \ldots + W_k$. 
@@
 ```{r thresholdedBursty, message=FALSE, fig.height=4, fig.width=6, fig.cap="\\label{fig:thresholdedBursty}Exceedances (red) and Times until Exceedance (durations between blue crosses) for a given threshold $\\ell$ (dashed line)."}
-
 tail <- params$tail
@@
 
-The classical POT approach is based on the fact, that exceedances above a high threshhold are assymptotically GPD distributed, hence a GPD distribution is fitted to the exceedances above a high enogh threshhold.
-Due to the Theorem in the last Section we know that for high threshholds the times between the exceedances are assymptotically Mittag-Leffler distributed in case of heavy tailed waiting times between the observations.
-Hence, before we talk about inference for the exceedances in the next section, we want to have a look at inference for Mittag-Leffler distributions in the following.
+The classical POT approach is based on the fact that exceedances above a high threshhold are asymptotically GPD distributed, hence a GPD distribution is fitted to the exceedances above a high enough threshhold.
+Due to the Theorem in the last Section we know that for high thresholds the times between exceedances are asymptotically Mittag-Leffler distributed in case of heavy tailed waiting times between the observations.
+Hence, before we talk about inference for the exceedances in the next section, we discuss inference for Mittag-Leffler distributions.
 
-The first method proposed for the estimation of the Mittag-Leffler distribution parameters was the fractional moment estimator by [@kozubowski2001].
-Unlike the first moments, the fractional moments of order $p$ for $p<\beta$ exist and can get calculated.
+Historically, the first method proposed for the estimation of the Mittag-Leffler distribution parameters was the fractional moment estimator by @kozubowski2001.
+Unlike the first moments, the fractional moments of order $p$ for $p<\beta$ exist and are tractable.
 One drawback of this method is that constant priors for the tail parameter are needed for the calculation of the estimates.
-[@Cahoy2010] proposed an estimator based on the log-Moments which doesn't need prior knowledge.
-Furthermore, they showed in a simulation study that the log-Moment outclasses the fractional moment estimator regarding bias and root mean squared error (RMSE).
+@Cahoy2010 proposed a moment estimator of the log transformed data, which does not require any prior.
+Furthermore, they performed simulation studies illustrating that the log-Moment outperforms the fractional moment estimator with respect to bias and root mean squared error (RMSE).
+
 Due to the form of the density function of a Mittag-Leffler distribution there exists no closed form for the Maximum Likelihood estimator (MLE).
-In the RPackage `MittagLeffleR` Maximum Likelihood estimation is implemented via numerical optimization.
-The MLE outperforms the log-moment estimator regarding bias and RMSE for big enough sample sizes, but is extremely computational intensive and the differences in bias and RMSE between the two methods are very small.
-In Figure \ref{fig:MSE}, one can see that both methods work quite well even for very low sample sizes.
+In the R Package `MittagLeffleR` [@MittagLeffleR], Maximum Likelihood estimation is implemented via numerical optimization.
+The MLE slightly outperforms the log-moment estimator regarding bias and RMSE for big enough sample sizes, but is extremely computational intensive.
+Figure \ref{fig:MSE} shows that both estimators perform well, even for small sample sizes.
+
 ```{r MSE, echo=FALSE, fig.height=12, fig.cap="\\label{fig:MSE} MSE for sample sizes n=30, 100, 200 for the tail and scale estimations via log-moments and maximum likelihood estimation", out.width = '100%'}
@@
 ```
+
 Since the Mittag-Leffler distribution is heavy-tailed, many researchers would intuitively give the highest importance to the tail behaviour of the distribution.
-Of course, one can also use established tail exponent estimators for the estimation of the parameter $\beta$ such as the Hill estimator, which is defined by
+Of course, one can also use established tail exponent estimators for the estimation of the parameter $\beta$ such as the Hill estimator
 \begin{align*}
@@
 \end{align*}
-However, these methods are less statistically efficient since they only use a portion of the information contained in the data, as was already mentioned by [@kozubowski2001].
-Additionally, they need a specification of a tuning parameter and the hill estimator only performs well for distributions close to Pareto (see @Resnick97).
-In Figure \ref{fig:Hillplots} one can see different Hill plots for Mittag-Leffler simulated data with differrent sample sizes and tails.
-It would be really hard to deduce the correct tail parameter estimates from this plots.
+However, these methods are statistically less efficient since they only use a portion of the information contained in the data, as mentioned by @kozubowski2001.
+Moreover, the hill estimator requires a tuning parameter, and only performs reliably well for distributions close to Pareto [see @Resnick97].
+Figure \ref{fig:Hillplots} shows Hill plots for Mittag-Leffler simulated data, with varying sample sizes and tails.
+To deduce the correct tail parameter estimates from these plots is virtually impossible.
 
@@
 ", out.width = '100%'}
-knitr::include_graphics("Hillplots.pdf")
+# knitr::include_graphics("Hillplots.pdf")
 ```
@@
 
-Since the exponential distribution is nested in the Mittag-Leffler family of distributions, an appropriate way to choose between a model with exponential and Mittag-Leffler inter-exceedance times seems to be a Likelihood ratio test.
-Although the two models are nested, the assymptotic distribution is not $\chi^2_1$-distributed, the classical Theorem of Wilk doesn't apply since under $H_0$ the paremter $\beta$ of Mittag-Leffler distribution is equal to zero and hence lies under $H_0$ on the boundary of the parameter space $(0,1]$.
-But one can perform a bootstrapped log-likelihood ratio test.
-In Figure \ref{Fig:LRT} one can see the power for the bootstrapped LRT for Mittag-Leffler distributions with different tail parameters.
-As expected the power gets smaller for tail parameters close to one, since the Mittag-Leffler distribution converges for $\beta \rightarrow 1$ to an exponential distribution.
-Hence, for tail parameters close to one it is hard to differentiate a Mittag-Lefller distribution from an exponential.
+Since the exponential distribution is nested in the Mittag-Leffler family of 
+distributions, a Likelihood Ratio Test seems to be an appropriate way to choose 
+between a model with exponential and Mittag-Leffler inter-exceedance times.
+Although the two models are nested, the asymptotic distribution is not 
+$\chi^2_1$-distributed, and Wilk's Theorem does not hold: under $H_0$, the 
+parameter $\beta$ of Mittag-Leffler distribution is equal to $1$, and hence lies
+on the boundary of the parameter space $(0,1]$. 
+Instead, a valid approach is a bootstrapped log-likelihood ratio test 
+(PUT REFERENCE HERE). 
+Figure \ref{Fig:LRT} displays the power for the bootstrapped LRT for Mittag-Leffler distributions with varying tail parameters.
+As expected, the power decreases for tail parameters close to one, since the Mittag-Leffler distribution converges as $\beta \uparrow 1$ to an exponential distribution; it becomes hard to differentiate a Mittag-Lefller distribution from an exponential.
+(PUT ALL 4 CURVES INTO ONE PLOT)
 
@@
 
-The above approach, though theoretically sound, benefits from the following
+The above approach benefits from the following
 practical adjustments (compare with Figure \ref{fig:flares}):
@@
 \begin{align*}
-T(\ell) \sim {\rm ML}(\hat \beta, k^{-1/\hat \beta} \hat \sigma_0).
+T(\ell) \sim {\rm ML}(\hat \beta, k^{-1/\hat \beta} \hat \sigma_0),
 \end{align*}
+where $\ell$ equals the $k$-th order statistic.
 For quick estimates of the Mittag-Leffler parameters we have used 
-the method of log-transformed moments by @Cahoy2013.
+the method of log-transformed moments [@Cahoy2013].
 We have verified the validity of our estimation algorithm  via simulations, 
@@
 Using the parametrisation of @SamorodnitskyTaqqu, a few lines of 
-calculation (see e.g. the vignette on parametrisation in @MittagLeffleR) 
+calculation [see e.g. the vignette on parametrisation in @MittagLeffleR]
 show that $D$ must have the stable distribution 
@@
 
-```{r simulated-example, message=FALSE, fig.cap=caption}
+```{r simulated-example, message=FALSE, warning=FALSE, fig.cap=caption}
 k_max <- 500
+
 thin_sim_ctre <- thin(ctre = sim_ctre, k = k_max)
-par(mfrow=c(1,2))
+# par(mfrow=c(1,2))
 MLestimates(ctre = thin_sim_ctre, tail = params$tail, scale = n^(1/params$tail))

### 2018-12-05 article_springer/article_springer.Rmd

@@
 
+Since the exponential distribution is nested in the Mittag-Leffler family of distributions, an appropriate way to choose between a model with exponential and Mittag-Leffler inter-exceedance times seems to be a Likelihood ratio test.
+Although the two models are nested, the assymptotic distribution is not $\chi^2_1$-distributed, the classical Theorem of Wilk doesn't apply since under $H_0$ the parameter $\beta$ of the Mittag-Leffler distribution is equal to one and hence lies under $H_0$ on the boundary of the parameter space $(0,1]$.
+Nonetheless, one can perform a bootstrapped log-likelihood ratio test.
+In Figure \ref{Fig:LRT} one can see the power for the bootstrapped LRT for Mittag-Leffler distributions with different tail parameters.
+As expected the power gets smaller for tail parameters close to one, since the Mittag-Leffler distribution converges for $\beta \rightarrow 1$ to an exponential distribution.
+Consequently, for tail parameters close to one it is hard to differentiate a Mittag-Lefller distribution from an exponential.
+
 ```{r likelihood-ratio-test}
@@
 $$
-T_\ell \sim {\rm ML}(\beta, k^{1/\beta} \sigma_0), 
+T(\ell) \sim {\rm ML}(\beta, k^{-1/\beta} \sigma_0), 
 $$
 where $\beta = 0.85$ and $\sigma_0 = 3.0 \times 10^7 {\rm sec}$. 
-Unlike the exponential distribution, the Mittag-Leffler distribution is not 
-memoryless, and the probability density of the time $t$ until the next threshold 
-crossing will depend on the time $t_0$ elapsed since the last threshold crossing.
+Unlike the exponential distribution, the Mittag-Leffler distribution is not memoryless, and the probability density of the time $t$ until the next threshold crossing will depend on the time $t_0$ elapsed since the last threshold crossing.
 This density equals 
 $$
-p(t|\beta, \sigma_0, \ell, t_0) = \frac{f(t + t_0 | \beta, k^{1/\beta} \sigma_0)}{\mathbf P[T_\ell > t_0]}
+p(t|\beta, \sigma_0, \ell, t_0) = \frac{f(t + t_0 | \beta, k^{-1/\beta} \sigma_0)}{\mathbf P[T_\ell > t_0]}
 $$
-where $f(\,\cdot\, | \beta, k^{1/\beta} \sigma_0)$ is the probability density of 
-${\rm ML}(\beta, k^{1/\beta} \sigma_0)$. 
-The more time has passed without a threshold crossing, the more the probability 
-distribution shifts towards larger values for the next crossing
-(see Figure \ref{fig:hazard}, left panel). 
-The hazard rate 
+where $f(\,\cdot\, | \beta, k^{-1/\beta} \sigma_0)$ is the probability density of ${\rm ML}(\beta, -k^{1/\beta} \sigma_0)$. 
+The more time has passed without a threshold crossing, the more the probability distribution shifts towards larger values for the next crossing
+(see Figure \ref{fig:hazard}, left panel). The hazard rate 
 $$
-h(t) = \frac{f(t| \beta, k^{1/\beta} \sigma_0))}{\int_t^\infty f(\tau| \beta, k^{1/\beta} \sigma_0))\,d\tau}
+h(t) = \frac{f(t| \beta, k^{-1/\beta} \sigma_0))}{\int_t^\infty f(\tau| \beta, k^{-1/\beta} \sigma_0))\,d\tau}
 $$
-represents the risk of a threshold crossing per unit time, and is a 
-decreasing function for the Mittag-Leffler distribution. 
-```{r hazard, fig.height=5, fig.cap="Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\\beta = 0.8$, $\\sigma_0 = 1$).
+represents the risk of a threshold crossing per unit time, and is a decreasing function for the Mittag-Leffler distribution. 
+```{r hazard, fig.height=4, fig.cap="Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\\beta = 0.8$, $\\sigma_0 = 1$).
 Right: Hazard rate depending on tail parameter $\\beta$.\\label{fig:hazard}"}
@@
 right panel).
-
-It is beyond the scope of the current paper to incorporate parameter 
-uncertainty into our predictive distribution for the next threshold crossing; 
-however, methods as described by @Scarrott12 and @Lee15 are likely 
-to extend to our setting.
 
@@
 $\sigma_0 = n^{1/\beta}$.
-The distribution of $J_k$ is irrelevant for the inference on $\beta$ and 
-$\sigma_0$ (we have chosen unit exponential random variables). 
-Figure \ref{fig:sim} displays plots of $\hat \beta(\ell)$ and 
-$\hat \sigma(\ell)$ vs. $k$; recall that $k$ is the index of the order
-statistics of $J_k$ at which the threshold $\ell$ is placed. 
-Dotted lines show 95% confidence intervals, which are derived from the 
-asymptotic normality of the log-moments estimators [@Cahoy2013] and the $\delta$-method [@MittagLeffleR].
-The dashed lines show the actual values of $\beta$ resp.\ $\sigma_0$, 
-showing that our inference method identifies the 
-parameters correctly.
+we have chosen $\beta=1$ in the stable as well in the Pareto case.
+Figure \ref{Ex1figs} displays plots of $\hat \beta(k)$ vs.
+$k$ for the first example with stable distributed waiting times.
+In the left picture we used the log moment estimator, in the middle picture maximum likelihood estimates (both applied to the inter-exceedance times) and for the right picture hill estimators applied to the inter-arrival times.
+Recall that $k$ is the index of the order statistics of $J_k$ at which the threshold $\ell$ is placed.
+
+```{r Ex1figs, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex1figs} Stability Plots for m=100 simulation runs for Example 1 (stable distributed waiting times, true tail parameter =0.8).
+The grey lines, the red line and the blue lines are the log Moment, the MLE and the hill estimator, repectively, for different $k$'s on the x-axis.
+The dark lines in each picture are the means of the concerning estimators for different $k$'s.", fig.show='hold', out.width = '32%'}
+knitr::include_graphics(c("SimuStudy_StabilityPlots_Tail08_logMoms.pdf","SimuStudy_StabilityPlots_Tail08_mles.pdf","SimuStudy_StabilityPlots_Tail08_hill.pdf"))
+```
+Figure \ref{Ex2figs} shows the estimates fordifferent $k$'s and for the different estimators for the tail parameter $\beta$.
+Again one can see, that there is much more variance between the stability plots for the different simulation runs in case of the hill estimator compared to the other two estimators.
+```{r Ex2figs, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex2figs} Stability Plots for m=100 simulation runs for Example 2 (Pareto distributed waiting times, true tail parameter =0.8).
+The grey lines, the red line and the blue lines are the log Moment, the MLE and the hill estimator, repectively, for different $k$'s on the x-axis.
+The dark lines in each picture are the means of the concerning estimators for different $k$'s.", fig.show='hold', out.width = '32%'}
+knitr::include_graphics(c("SimuStudy_StabilityPlots_Ex2_Tail08_logMoms.pdf","SimuStudy_StabilityPlots_Ex2_Tail08_mles.pdf","SimuStudy_StabilityPlots_Ex2_Tail08_hill.pdf"))
+```
+To show how the different estimates behave in the case that $\beta=1$, hence, the inter-exceedance times are exponetial distributed, we simulated in a last example exponetial distributed waiting times.
+
+```{r Ex3figs, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex3figs} Stability Plots for m=100 simulation runs for Example 3 (Exponentially distributed waiting times, true tail parameter =0.8).
+The grey lines, the red line and the blue lines are the log Moment, the MLE and the hill estimator, repectively, for different $k$'s on the x-axis.
+The dark lines in each picture are the means of the concerning estimators for different $k$'s.", fig.show='hold', out.width = '32%'}
+knitr::include_graphics(c("SimuStudy_StabilityPlots_Ex3_logMoms.pdf","SimuStudy_StabilityPlots_Ex3_mles.pdf","SimuStudy_StabilityPlots_Ex3_hill_times.pdf"))
+```
 
@@
 empcopula(flares_ctre)
-flares_ctre %>% interarrival() %>% mlqqplot(log = 'xy', tail = 0.8, main = "Mittag-Leffler QQ Plot")
+flares_ctre %>% interarrival() %>% mlqqplot(log = 'xy', tail = 0.85, main = "Mittag-Leffler QQ Plot")
 ```
+
+Figure \ref{fig:flares} shows the stability plots for the solar flare data, on the left for the tail parameter and on the right for the scale parameter.
+Dotted lines show 95% confidence intervals, which are derived from the asymptotic normality of the log-moments estimators [@Cahoy2013] and the $\delta$-method [@MittagLeffleR, dashed lines show the actual values of $\beta$ resp.\ $\sigma_0$.
+The stability plot for the tail stabilizes nicely round about 0.85 (dotted line), while it is a little bit harder to deduce an estimate for the scale parameter.
+Howerever, the stability plot for the scale parameter seems to stabilize round about $3 \times 10^7$.
 
@@
 
+The fit with a Mittag-Leffler distribution ($\beta = 0.85$) is good, though there are signs that the power-law tail tapers off for very large inter-threshold crossing times.
+There is no apparent dependence between threshold exceedance times and event magnitudes seen in the copula plot.
+We also counduct a bootstrapped LRT for the null hypothesis of exponential distributed inter-arrival times and received a $p$-value of $p<0.01$.
+
+```{r likelihood-ratio-test}
+library("MittagLeffleR")
+library("stats")
+
+# ML_LRT_boot<-function(data,signi=0.05,m=1000,n){
+# if(is.null(dim(data))){
+# mle_data<-mlmle(data)                                                   #Calculate loglikelihoods for obserevd data
+# teststat<-2*(mle_data$loglik-mle_data$null_loglik)}                     #Calculate teststatistic for obserevd data
+# else{
+# l<-apply(data,MARGIN=2,FUN=mlmle)                                       #Extension to multivariate datasets for simulation studies
+# teststat<-2*(unlist(lapply(l,"[[",2))-unlist(lapply(l,"[[",3)))
+# }
+# 
+# x<-replicate(m,rexp(n,rate=1))                                          #Sample data under Null
+# l2<-apply(x,MARGIN=2,FUN=mlmle)                                         #Calculate loglikelihoods for each simulated data set
+# test_stat_null<-2*(unlist(lapply(l2,"[[",2))-unlist(lapply(l2,"[[",3))) #Calculate teststatistic for each simulated data set
+# q<-stats::quantile(test_stat_null,probs=1-signi)                               #Calculate 1-signi quantile of simulated distribution of the test statistic
+# #decision<-as.numeric(teststat>q)                                       #Gives One if Hypothesis gets rejected, 0 otherwise
+# f<-function(x,y){
+#   r<-as.numeric(x>y)
+#   return(r)
+# }
+# decision<-mapply(teststat,FUN=f,y=q)
+# decision<-return(decision)
+# }
+# flares_arrivals <- flares %>% ctre() %>% thin(k = 700) %>% interarrival()
+# p_value <- ML_LRT_boot(data=flares_arrivals,n=length(flares_arrivals))
+```
+
 # Discussion & Conclusion
 
-We have extended the POT (Peaks over Threshold) model, a mainstay of 
-extreme value theory, to "bursty" time series, which have been studied 
+We have extended the POT (Peaks over Threshold) model, a mainstay of extreme value theory, to "bursty" time series, which have been studied 
 intensively in statistical physics.
-Burstiness is characterized by power-law waiting times between events, 
-and we have shown that the Mittag-Leffler distribution arises naturally 
-as a scaling limit for the inter-exceedance times of high thresholds. 
-Moreover, we have derived the following non-linear scaling behaviour: 
-$\sigma \sim p^{-1/\beta}$, 
-where $\sigma$ is the scale parameter of the distribution of threshold 
-exceedance times, 
-$p$ is the fraction of magnitudes above the threshold, 
-and $\beta$ the exponent of the power law. 
-This "anomalous" scaling behaviour in the bursty setting entails two 
-phenomena:
+Burstiness is characterized by power-law waiting times between events, and we have shown that the Mittag-Leffler distribution arises naturally as a scaling limit for the inter-exceedance times of high thresholds.
+Moreover, we have derived the following non-linear scaling behaviour: $\sigma \sim p^{-1/\beta}$, where $\sigma$ is the scale parameter of the distribution of threshold
+exceedance times, $p$ is the fraction of magnitudes above the threshold, and $\beta$ the exponent of the power law. 
+This "anomalous" scaling behaviour in the bursty setting entails two phenomena:
 
-i) a heavy tail of the interarrival time distribution of 
-threshold crossings (long rests), and
+i) a heavy tail of the interarrival time distribution of threshold crossings (long rests), and
 
-ii) a high propensity for more threshold crossing events immediately after 
-each threshold crossing event (bursts).
+ii) a high propensity for more threshold crossing events immediately after each threshold crossing event (bursts).
 
-The Mittag-Leffler distribution captures both phenomena, due to its heavy
-tail as well as its stretched exponential (peaked) asymptotics for small 
-times. 
-It generalizes the exponential distribution, and 
-in the solar flare data example, this generalization 
-is warranted, because the likelihood-ratio test is strongly significant.
+The Mittag-Leffler distribution captures both phenomena, due to its heavy tail as well as its stretched exponential (peaked) asymptotics for small times.
+It generalizes the exponential distribution, and in the solar flare data example, this generalization is warranted, because the likelihood-ratio test is strongly significant.
 

### 2018-12-05 article_springer/article_springer.Rmd
Add Scale Plots for Simulation in Appendix, and changed size of other Simuplots

@@
 
-  This article proposes a new model for the _inter-exceedance times_ of thresholds;
+  This article provides a new model for the threshold inter-exceedance _times_;
   the threshold exceedances are modeled via the standard 
@@
 All code and data used for the analysis in this article has been organized into 
-an R package `CTRE` (<https://github.com/strakaps/CTRE>).
+an R package `CTRE` (<https://github.com/UNSW-MATH/CTRE>).
 The source code for the figures generated in this manuscript is 
-available online at <https://github.com/strakaps/bursty-POT>.
+available online at <https://github.com/UNSW-MATH/bursty-POT>.
 
@@
 
-We assume that the $k$-th magnitude $J_k$ occurs at time
+Note that the $k$-th magnitude $J_k$ occurs at time
 $T_k = W_1 + \ldots + W_k$. 
@@
 
-```{r thresholdedBursty, message=FALSE, fig.height=4, fig.width=6, fig.cap="\\label{fig:thresholdedBursty}Exceedances (red) and Times until Exceedance (durations between blue crosses) for a given threshold $\\ell$ (dashed line)."}
+```{r thresholdedBursty, message=FALSE, fig.height=7, fig.width=9, fig.cap="\\label{fig:thresholdedBursty}Exceedances (red) and Times until Exceedance (durations between blue crosses) for a given threshold $\\ell$ (dashed line)."}
 tail <- params$tail
@@
 par(mfrow = c(2,1))
-p1 <- plot(sim_ctre, p = 0.01, main = "Simulated MRP") 
-p2 <- flares %>% ctre() %>% plot(p = 0.02, log = 'y', main = "HXRBS data") 
-library(gridExtra)
-grid.arrange(p1, p2, nrow = 2)
+plot(sim_ctre, p = 0.01, main = "Simulated MRP") 
+flares %>% ctre() %>% plot(p = 0.02, log = 'y', main = "HXRBS data") 
 ```
 
-In this article, we restrict ourselves to the uncoupled case, where $W$ and $J$ are independent.
+In this article, we restrict ourselves to the uncoupled case, where W and J are independent.
 Then the two sequences $X(\ell, n)_{n \in \mathbb N}$ and $T(\ell, n)_{n \in \mathbb N}$ are independent as well.
@@
 _without any_ events, whereas in the real-world dataset events appear continuously.
-The threshold exceedances, however, appear to have visually similar statistical behaviour in both models.
-Observations below a threshold are commonly discarded in Extreme Value Theory (POT approach); likewise, the CTRE model interprets these observations as noise and discards them.
+The threshold exceedances, however, appear to have similar statistical behaviour in both models.
+Observations below a threshold are commonly discarded in Extreme Value Theory (POT approach); likewise, the CTRE model interprets these observations as noise and filters them out.
 
@@
 
-The classical POT approach is based on the fact that exceedances above a high threshhold are asymptotically GPD distributed, hence a GPD distribution is fitted to the exceedances above a high enough threshhold.
-Due to the Theorem in the last Section we know that for high thresholds the times between exceedances are asymptotically Mittag-Leffler distributed in case of heavy tailed waiting times between the observations.
-Hence, before we talk about inference for the exceedances in the next section, we discuss inference for Mittag-Leffler distributions.
+The classical peaks over threshold approach is based on the fact, that exceedances above a high threshhold are assymptotically GPD distributed.
+Hence, a GPD distribution is fitted to the exceedances above a high enough threshhold.
+Due to the Theorem in the last Section, we know that for high threshholds the times between the exceedances are in case of heavy tailed inter-arrival times assymptotically Mittag-Leffler distributed.
+Therefore, before talking about inference for the exceedance times in the next section, we want to have a look at inference for Mittag-Leffler distributions in general.
 
-Historically, the first method proposed for the estimation of the Mittag-Leffler distribution parameters was the fractional moment estimator by @kozubowski2001.
-Unlike the first moments, the fractional moments of order $p$ for $p<\beta$ exist and are tractable.
+The first method proposed in the literature to estimate the parameters of Mittag-Leffler distribution was the fractional moment estimator by [@kozubowski2001].
+Unlike the first moments, the fractional moments of order $p$ for $p<\beta$ exist and can get calculated by explicit formulas.
 One drawback of this method is that constant priors for the tail parameter are needed for the calculation of the estimates.
-@Cahoy2010 proposed a moment estimator of the log transformed data, which does not require any prior.
-Furthermore, they performed simulation studies illustrating that the log-Moment outperforms the fractional moment estimator with respect to bias and root mean squared error (RMSE).
-
+Therefore, [@Cahoy2010] proposed an estimator based on the log-Moments which doesn't need prior knowledge.
+Furthermore, they showed in a simulation study that the log-Moment outclasses the fractional moment estimator regarding bias and root mean squared error (RMSE).
 Due to the form of the density function of a Mittag-Leffler distribution there exists no closed form for the Maximum Likelihood estimator (MLE).
-In the R Package `MittagLeffleR` [@MittagLeffleR], Maximum Likelihood estimation is implemented via numerical optimization.
-The MLE slightly outperforms the log-moment estimator regarding bias and RMSE for big enough sample sizes, but is extremely computational intensive.
-Figure \ref{fig:MSE} shows that both estimators perform well, even for small sample sizes.
-
+In the RPackage `MittagLeffleR` we implemented Maximum Likelihood estimation via an numerical optimization algorithm.
+The MLE outperforms the log-moment estimator regarding bias and RMSE for big enough sample sizes, but is extremely computational intensive and the differences in bias and RMSE between the two methods are very small.
+In Figure \ref{fig:MSE}, one can see that both methods work quite well even for very low sample sizes.
 ```{r MSE, echo=FALSE, fig.height=12, fig.cap="\\label{fig:MSE} MSE for sample sizes n=30, 100, 200 for the tail and scale estimations via log-moments and maximum likelihood estimation", out.width = '100%'}
@@
 ```
-
 Since the Mittag-Leffler distribution is heavy-tailed, many researchers would intuitively give the highest importance to the tail behaviour of the distribution.
-Of course, one can also use established tail exponent estimators for the estimation of the parameter $\beta$ such as the Hill estimator
+Of course, one can also use established tail exponent estimators for the estimation of the parameter $\beta$ such as the Hill estimator, which is defined by
 \begin{align*}
@@
 \end{align*}
-However, these methods are statistically less efficient since they only use a portion of the information contained in the data, as mentioned by @kozubowski2001.
-Moreover, the hill estimator requires a tuning parameter, and only performs reliably well for distributions close to Pareto [see @Resnick97].
-Figure \ref{fig:Hillplots} shows Hill plots for Mittag-Leffler simulated data, with varying sample sizes and tails.
-To deduce the correct tail parameter estimates from these plots is virtually impossible.
+However, these methods are less statistically efficient since they only use a portion of the information contained in the data, as was already mentioned by [@kozubowski2001].
+Additionally, they need a specification of a tuning parameter and the hill estimator only performs well for distributions close to Pareto (see @Resnick97).
+In Figure \ref{fig:Hillplots} one can see different Hill plots for Mittag-Leffler simulated data with differrent sample sizes and tails.
+It would be really hard to deduce the correct tail parameter estimates from these plots.
 
@@
 ", out.width = '100%'}
-# knitr::include_graphics("Hillplots.pdf")
+knitr::include_graphics("Hillplots.pdf")
 ```
@@
 
-```{r likelihood-ratio-test}
-flares_arrivals <- flares %>% ctre() %>% thin(k = 500) %>% interarrival()
-mlmle_out <- mlmle(data = flares_arrivals)
-```
-
-Since the exponential distribution is nested in the Mittag-Leffler family of 
-distributions, a Likelihood Ratio Test seems to be an appropriate way to choose 
-between a model with exponential and Mittag-Leffler inter-exceedance times.
-Although the two models are nested, the asymptotic distribution is not 
-$\chi^2_1$-distributed, and Wilk's Theorem does not hold: under $H_0$, the 
-parameter $\beta$ of Mittag-Leffler distribution is equal to $1$, and hence lies
-on the boundary of the parameter space $(0,1]$. 
-Instead, a valid approach is a bootstrapped log-likelihood ratio test 
-(PUT REFERENCE HERE). 
-Figure \ref{Fig:LRT} displays the power for the bootstrapped LRT for Mittag-Leffler distributions with varying tail parameters.
-As expected, the power decreases for tail parameters close to one, since the Mittag-Leffler distribution converges as $\beta \uparrow 1$ to an exponential distribution; it becomes hard to differentiate a Mittag-Lefller distribution from an exponential.
-(PUT ALL 4 CURVES INTO ONE PLOT)
-
-```{r LRT power, echo=FALSE, fig.cap="\\label{Fig:LRT} Power for bootstrapped LRT for different sample sizes", out.width = '100%'}
+```{r LRT power, echo=FALSE, fig.cap="\\label{Fig:LRT} Power for bootstrapped LRT for different sample sizes", out.width = '90%'}
 knitr::include_graphics("Plots_LRT_boot.pdf")
@@
 
-The above approach benefits from the following
+The above approach, though theoretically sound, benefits from the following
 practical adjustments (compare with Figure \ref{fig:flares}):
@@
 \begin{align*}
-T(\ell) \sim {\rm ML}(\hat \beta, k^{-1/\hat \beta} \hat \sigma_0),
+T(\ell) \sim {\rm ML}(\hat \beta, k^{-1/\hat \beta} \hat \sigma_0).
 \end{align*}
-where $\ell$ equals the $k$-th order statistic.
 For quick estimates of the Mittag-Leffler parameters we have used 
-the method of log-transformed moments [@Cahoy2013].
+the method of log-transformed moments by @Cahoy2013.
 We have verified the validity of our estimation algorithm  via simulations, 
@@
 
-To test our inference method via stability plots, we have simulated 
-independent waiting time and magnitude pairs $(W_k, J_k)$ (see upper panel in 
-Figure \ref{fig:thresholdedBursty}) for three different situations: stable waiting times, Pareto waitings times and Exponential waiting times. In order to have exact 
-analytical values available for $\beta$ and $\sigma_0$, a distribution for 
-$W_k$ needs to be chosen for which $b(n)$ from \eqref{eq:stability} is known. 
-If we choose $W_k \stackrel{d}{=} D$, where $D$ is as in \eqref{eq:stability}, 
-then due to the stability property we have the *equality* of distribution
-$W_1 + \ldots + W_n \stackrel{d}{=} b(n) D$, 
-for $b(n) = n^{1/\beta}$. 
-Using the parametrisation of @SamorodnitskyTaqqu, a few lines of 
-calculation [see e.g. the vignette on parametrisation in @MittagLeffleR]
-show that $D$ must have the stable distribution 
-$S_\beta(\cos(\pi \beta/2)^{1/\beta}, +1, 0)$, which is 
-implemented in the R package `stabledist` by @stabledist.
-
-```{r make-caption}
-caption = "Tail and scale estimates for simulated data, with waiting times drawn from the stable distribution $S_\\beta(\\cos(\\pi \\beta/2)^{1/\\beta}, +1, 0)$ with $\\beta = 0.8$.
-Dashed lines are 95\\% confidence intervals, dotted lines are the known theoretical values ($0.8$ and $10000^{1/0.8}$).
-\\label{fig:sim}"
-```
-
-```{r simulated-example, message=FALSE, warning=FALSE, fig.cap=caption}
-k_max <- 500
-
-thin_sim_ctre <- thin(ctre = sim_ctre, k = k_max)
-# par(mfrow=c(1,2))
-MLestimates(ctre = thin_sim_ctre, tail = params$tail, scale = n^(1/params$tail))
-```
+To test our inference method, we performed a simulation study where we have simulated independent waiting time and magnitude pairs $(W_k, J_k)$.
+Since the estimation of the parameters of the inter-exceedance times is based on stability plots and is hence rather a graphical estimation procedure, it is difficult to conduct a simulation study.
+To get an impression of how our estimation procedure performs, we plotted $m=100$ stability plots for each example and calculated for each $k$ the mean value of all estimates.
+We have chosen (i) a Stable, (ii) a Pareto and (iii) an Exponential distribution for waiting times.
+The distribution of $J_k$ is irrelevant for the inference on $\beta$ and $\sigma_0$ (it just plays a role for the rescaling of $\hat{\sigma}_0$, which gets done to receive an estimate for the scale parameter of the exceedances).
+Hence we have chosen exponential distributed magnitudes in all considered examples.
+In order to have exact analytical values available for $\beta$ and $\sigma_0$, a distribution for $W_k$ needs to be chosen for which $b(n)$ from \eqref{eq:stability} is known.
+In our first example, we have chosen $W_k \stackrel{d}{=} D$, where $D$ is as in \eqref{eq:stability}.
+Then due to the stability property we have the *equality* of distribution $W_1 + \ldots + W_n \stackrel{d}{=} b(n) D$, for $b(n) = n^{1/\beta}$.
+Using the parametrisation of @SamorodnitskyTaqqu, a few lines of calculation (see e.g.
+the vignette on parametrisation in @MittagLeffleR) show that $D$ must have the stable distribution $S_\beta(\cos(\pi \beta/2)^{1/\beta}, +1, 0)$, which is implemented in the R package `stabledist` by @stabledist.
+In the second examaple we have chosen $W_k$ to be Pareto distributed or more precisecly
+\begin{align*}
+P(W_k>t)= C t^{-\beta}
+\end{align*}
+with $C:=(1/\Gamma(1-\beta))^{1/\beta}$ and $b(n)=n^{1/\beta}$. We then receive
+\begin{align*}
+\frac{W_1 + \ldots + W_n}{b(n)} \stackrel{d}{\Rightarrow} D
+\end{align*}
+with $E(\exp(-sD))=\exp(-s^{\beta})$.
 
@@
 The dark lines in each picture are the means of the concerning estimators for different $k$'s.", fig.show='hold', out.width = '32%'}
-knitr::include_graphics(c("SimuStudy_StabilityPlots_Tail08_logMoms.pdf","SimuStudy_StabilityPlots_Tail08_mles.pdf","SimuStudy_StabilityPlots_Tail08_hill.pdf"))
+knitr::include_graphics(c("SimuStudy_StabilityPlots_Ex1_Tail08_logMoms.pdf","SimuStudy_StabilityPlots_Ex1_Tail08_mles.pdf","SimuStudy_StabilityPlots_Ex1_Tail08_hill.pdf"))
 ```
@@
 
-```{r likelihood-ratio-test}
-library("MittagLeffleR")
-library("stats")
-
-# ML_LRT_boot<-function(data,signi=0.05,m=1000,n){
-# if(is.null(dim(data))){
-# mle_data<-mlmle(data)                                                   #Calculate loglikelihoods for obserevd data
-# teststat<-2*(mle_data$loglik-mle_data$null_loglik)}                     #Calculate teststatistic for obserevd data
-# else{
-# l<-apply(data,MARGIN=2,FUN=mlmle)                                       #Extension to multivariate datasets for simulation studies
-# teststat<-2*(unlist(lapply(l,"[[",2))-unlist(lapply(l,"[[",3)))
-# }
-# 
-# x<-replicate(m,rexp(n,rate=1))                                          #Sample data under Null
-# l2<-apply(x,MARGIN=2,FUN=mlmle)                                         #Calculate loglikelihoods for each simulated data set
-# test_stat_null<-2*(unlist(lapply(l2,"[[",2))-unlist(lapply(l2,"[[",3))) #Calculate teststatistic for each simulated data set
-# q<-stats::quantile(test_stat_null,probs=1-signi)                               #Calculate 1-signi quantile of simulated distribution of the test statistic
-# #decision<-as.numeric(teststat>q)                                       #Gives One if Hypothesis gets rejected, 0 otherwise
-# f<-function(x,y){
-#   r<-as.numeric(x>y)
-#   return(r)
-# }
-# decision<-mapply(teststat,FUN=f,y=q)
-# decision<-return(decision)
-# }
-# flares_arrivals <- flares %>% ctre() %>% thin(k = 700) %>% interarrival()
-# p_value <- ML_LRT_boot(data=flares_arrivals,n=length(flares_arrivals))
-```
-
 # Discussion & Conclusion
@@
 
+\newpage
+
+# Appendix {-}
+
+```{r Ex1figsScale, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex1figsScale} Stability Plots for the scale parameter for Example 1 (stable distributed waiting times, true scale parameter = 1).", fig.show='hold', out.width = '45%'}
+knitr::include_graphics(c("SimuStudy_StabilityPlots_Ex1_Scales_logMoms.pdf","SimuStudy_StabilityPlots_Ex1_Scales_mles.pdf"))
+```
+
+```{r Ex2figsScale, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex2figsScale} Stability Plots for the scale parameter m=100 simulation runs for Example 2 (stable distributed waiting times, true scale parameter = 1).", fig.show='hold', out.width = '45%'}
+knitr::include_graphics(c("SimuStudy_StabilityPlots_Ex2_Scales_logMoms.pdf","SimuStudy_StabilityPlots_Ex2_Scales_mles.pdf"))
+```
+
+```{r Ex3figsScale, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex3figsScale} Stability Plots for the scale parameter for m=100 simulation runs for Example 3 (stable distributed waiting times, true scale parameter = 1).", fig.show='hold', out.width = '45%'}
+knitr::include_graphics(c("SimuStudy_StabilityPlots_Ex3_Scales_logMoms.pdf","SimuStudy_StabilityPlots_Ex3_Scales_mles.pdf"))
+```
+\newpage
+
 # References {-}

### 2018-12-05 article_springer/article_springer.Rmd
Some graphical changes

@@
 
-```{r thresholdedBursty, message=FALSE, fig.height=4, fig.width=6, fig.cap="\\label{fig:thresholdedBursty}Exceedances (red) and Times until Exceedance (durations between blue crosses) for a given threshold $\\ell$ (dashed line)."}
+```{r thresholdedBursty, message=FALSE, fig.height=3, fig.width=8, fig.cap="\\label{fig:thresholdedBursty}Exceedances (red) and Times until Exceedance (durations between blue crosses) for a given threshold $\\ell$ (dashed line)."}
 tail <- params$tail
@@
 sim_ctre <- ctre(data.frame(times, magnitudes)) 
-par(mfrow = c(2,1)) 
-p1 <- plot(sim_ctre, p = 0.01, main = "Simulated MRP") 
-p2 <- flares %>% ctre() %>% plot(p = 0.02, log = 'y', main = "HXRBS data") 
-library(gridExtra)
-grid.arrange(p1, p2, nrow = 2)
+par(mfrow = c(1,2)) 
+p1<-plot(sim_ctre, p = 0.01, main = "Simulated MRP") 
+p2<-flares %>% ctre() %>% plot(p = 0.02, log = 'y', main = "HXRBS data") 
 ```
@@
 
-```{r Hillplots, echo=FALSE, fig.height=12, fig.cap="\\label{fig:Hillplots} Hillplots for simulated Mittag-Leffler distributed rv's with tail parameter 0.5 (two plots in the right column) and 0.8 (two plots in the left column) and sample sizes 200 (two plots in the lower row) and 1000 (two plots in the upper row).
-", out.width = '100%'}
-# knitr::include_graphics("Hillplots.pdf")
+```{r Hillplots, echo=FALSE, fig.align="center", fig.cap="\\label{fig:Hillplots} Hillplots for simulated Mittag-Leffler distributed rv's with tail parameter 0.5 (two plots in the right column) and 0.8 (two plots in the left column) and sample sizes 200 (two plots in the lower row) and 1000 (two plots in the upper row).
+", out.width = '90%'}
+ knitr::include_graphics("Hillplots.pdf")
 ```
@@
 
-```{r LRT power, echo=FALSE, fig.cap="\\label{Fig:LRT} Power for bootstrapped LRT for different sample sizes", out.width = '100%'}
+```{r LRT power, echo=FALSE, fig.align="center", fig.cap="\\label{Fig:LRT} Power for bootstrapped LRT for different sample sizes", out.width = '80%'}
 knitr::include_graphics("Plots_LRT_boot.pdf")
@@
 
-```{r simulated-example, message=FALSE, warning=FALSE, fig.cap=caption}
-k_max <- 500
+<!-- ```{r simulated-example, message=FALSE, warning=FALSE, fig.cap=caption} -->
+<!-- k_max <- 500 -->
 
-thin_sim_ctre <- thin(ctre = sim_ctre, k = k_max)
-# par(mfrow=c(1,2))
-MLestimates(ctre = thin_sim_ctre, tail = params$tail, scale = n^(1/params$tail))
-```
+<!-- thin_sim_ctre <- thin(ctre = sim_ctre, k = k_max) -->
+<!-- # par(mfrow=c(1,2)) -->
+<!-- MLestimates(ctre = thin_sim_ctre, tail = params$tail, scale = n^(1/params$tail)) -->
+<!-- ``` -->
 
@@
 
-```{r Ex1figsScale, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex1figsScale} Stability Plots for the scale parameter for Example 1 (stable distributed waiting times, true scale parameter = 1).", fig.show='hold', out.width = '45%'}
+```{r Ex1figsScale, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex1figsScale} Stability Plots for the scale parameter for Example 1 (stable distributed waiting times, true scale parameter = 1).", fig.show='hold', out.width = '40%'}
 knitr::include_graphics(c("SimuStudy_StabilityPlots_Ex1_Scales_logMoms.pdf","SimuStudy_StabilityPlots_Ex1_Scales_mles.pdf"))
@@
 
-```{r Ex2figsScale, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex2figsScale} Stability Plots for the scale parameter m=100 simulation runs for Example 2 (stable distributed waiting times, true scale parameter = 1).", fig.show='hold', out.width = '45%'}
+```{r Ex2figsScale, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex2figsScale} Stability Plots for the scale parameter m=100 simulation runs for Example 2 (stable distributed waiting times, true scale parameter = 1).", fig.show='hold', out.width = '40%'}
 knitr::include_graphics(c("SimuStudy_StabilityPlots_Ex2_Scales_logMoms.pdf","SimuStudy_StabilityPlots_Ex2_Scales_mles.pdf"))
@@
 
-```{r Ex3figsScale, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex3figsScale} Stability Plots for the scale parameter for m=100 simulation runs for Example 3 (stable distributed waiting times, true scale parameter = 1).", fig.show='hold', out.width = '45%'}
+```{r Ex3figsScale, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex3figsScale} Stability Plots for the scale parameter for m=100 simulation runs for Example 3 (stable distributed waiting times, true scale parameter = 1).", fig.show='hold', out.width = '40%'}
 knitr::include_graphics(c("SimuStudy_StabilityPlots_Ex3_Scales_logMoms.pdf","SimuStudy_StabilityPlots_Ex3_Scales_mles.pdf"))

### 2018-12-09 article_springer/article_springer.Rmd
revert CTRE plot

@@
 p2<-flares %>% ctre() %>% plot(p = 0.02, log = 'y', main = "HXRBS data")
+library(gridExtra)
+grid.arrange(p1, p2, nrow = 2)
 ```

### 2018-12-09 article_springer/article_springer.Rmd
fix figure cross-reference

@@
 which means 
-$\sigma_0 = n^{1/\beta}$.
-we have chosen $\beta=1$ in the stable as well in the Pareto case.
-Figure \ref{Ex1figs} displays plots of $\hat \beta(k)$ vs.
-$k$ for the first example with stable distributed waiting times.
-In the left picture we used the log moment estimator, in the middle picture maximum likelihood estimates (both applied to the inter-exceedance times) and for the right picture hill estimators applied to the inter-arrival times.
-Recall that $k$ is the index of the order statistics of $J_k$ at which the threshold $\ell$ is placed.
+$\sigma_0 = n^{1/\beta}$. we have chosen $\beta=1$ in the stable as well in the
+Pareto case. Figure \ref{fig:Ex1figs} displays plots of $\hat \beta(k)$ vs. $k$ for
+the first example with stable distributed waiting times. In the left picture we 
+used the log moment estimator, in the middle picture maximum likelihood estimates 
+(both applied to the inter-exceedance times) and for the right picture hill 
+estimators applied to the inter-arrival times. Recall that $k$ is the index of the 
+order statistics of $J_k$ at which the threshold $\ell$ is placed.
 
-```{r Ex1figs, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex1figs} Stability Plots for m=100 simulation runs for Example 1 (stable distributed waiting times, true tail parameter =0.8).
+```{r Ex1figs, echo=FALSE,fig.height=7,fig.cap="\\label{fig:Ex1figs} Stability Plots for m=100 simulation runs for Example 1 (stable distributed waiting times, true tail parameter =0.8).
 The grey lines, the red line and the blue lines are the log Moment, the MLE and the hill estimator, repectively, for different $k$'s on the x-axis.
@@
 ```
-Figure \ref{Ex2figs} shows the estimates fordifferent $k$'s and for the different estimators for the tail parameter $\beta$.
-Again one can see, that there is much more variance between the stability plots for the different simulation runs in case of the hill estimator compared to the other two estimators.
-```{r Ex2figs, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex2figs} Stability Plots for m=100 simulation runs for Example 2 (Pareto distributed waiting times, true tail parameter =0.8).
+Figure \ref{fig:Ex2figs} shows the estimates for different $k$'s and for the
+different estimators for the tail parameter $\beta$. Again one can see that 
+the Hill estimator has a higher variance.
+
+```{r Ex2figs, echo=FALSE,fig.height=7,fig.cap="\\label{fig:Ex2figs} Stability Plots for m=100 simulation runs for Example 2 (Pareto distributed waiting times, true tail parameter =0.8).
 The grey lines, the red line and the blue lines are the log Moment, the MLE and the hill estimator, repectively, for different $k$'s on the x-axis.

### 2018-12-09 article_springer/article_springer.Rmd
polished writing

@@
 ```
-To show how the different estimates behave in the case that $\beta=1$, hence, the inter-exceedance times are exponetial distributed, we simulated in a last example exponetial distributed waiting times.
+To show how the different estimates behave in the case where $\beta=1$
+(the exponential case), we simulated in a last example exponentially distributed
+waiting times.
 

### 2018-12-09 article_springer/article_springer.Rmd
remove cross-reference

@@
 To test our inference method via stability plots, we have simulated 
-independent waiting time and magnitude pairs $(W_k, J_k)$ (see upper panel in 
-Figure \ref{fig:thresholdedBursty}) for three different situations: stable waiting times, Pareto waitings times and Exponential waiting times. In order to have exact 
+independent waiting time and magnitude pairs $(W_k, J_k)$ for three different
+situations: stable waiting times, Pareto waitings times and Exponential waiting 
+times. In order to have exact 
 analytical values available for $\beta$ and $\sigma_0$, a distribution for 

### 2018-12-09 article_springer/article_springer.Rmd
fix one square bracket

@@
 
-Figure \ref{fig:flares} shows the stability plots for the solar flare data, on the left for the tail parameter and on the right for the scale parameter.
-Dotted lines show 95% confidence intervals, which are derived from the asymptotic normality of the log-moments estimators [@Cahoy2013] and the $\delta$-method [@MittagLeffleR, dashed lines show the actual values of $\beta$ resp.\ $\sigma_0$.
-The stability plot for the tail stabilizes nicely round about 0.85 (dotted line), while it is a little bit harder to deduce an estimate for the scale parameter.
-Howerever, the stability plot for the scale parameter seems to stabilize round about $3 \times 10^7$.
+Figure \ref{fig:flares} shows the stability plots for the solar flare data, on the 
+left for the tail parameter and on the right for the scale parameter. Dotted lines 
+show 95% confidence intervals, which are derived from the asymptotic normality of 
+the log-moments estimators [@Cahoy2013] and the $\delta$-method 
+[see @MittagLeffleR], 
+dashed lines show the actual values of $\beta$ resp.\ $\sigma_0$. The stability 
+plot for the tail stabilizes nicely round about 0.85 (dotted line), while it is a 
+little bit harder to deduce an estimate for the scale parameter. Howerever, the 
+stability plot for the scale parameter seems to stabilize round about $3 \times 
+10^7$.
 

### 2018-12-09 article_springer/article_springer.Rmd
introduce definition environment

@@
   \usepackage{natbib}
+  \newtheorem{definition}{Definition}
 
@@
 
-**Definition (MRP):**
-
-: Let $(W,J), (W_1, J_1), (W_2, J_2), \ldots$ be i.i.d. pairs of random 
-variables, where the $W_k > 0$ are interpreted as the *waiting times* 
-and $J_k \in [x_L, x_R]$ as the *event magnitudes* 
+\begin{definition}[MRP]
+Let $(W,J), (W_1, J_1), (W_2, J_2), \ldots$ be i.i.d. pairs of random 
+variables, where the $W_k > 0$ are interpreted as the \emph{waiting times}
+and $J_k \in [x_L, x_R]$ as the \emph{event magnitudes}
 ($x_L \in [-\infty, +\infty), x_R \in (-\infty, +\infty]$). 
-If $W$ and $J$ are independent, the Marked Renewal Process is said to be *uncoupled*.
+If $W$ and $J$ are independent, the Marked Renewal Process is said to be \emph{uncoupled}. 
+\end{definition}
 
@@
 
-**Definition (CTRE):**
-
-: Given a threshold $\ell \in (x_L, x_R)$, 
+\begin{definition}[CTRE]
+Given a threshold $\ell \in (x_L, x_R)$, 
 consider the stopping time 
@@
 uncoupled. 
+\end{definition}
 

### 2018-12-09 article_springer/article_springer.Rmd
introduce theorem environment

@@
   \newtheorem{definition}{Definition}
+  \newtheorem{theorem}{Theorem}
 
@@
 
-**Theorem:**
-
-: Let the waiting times $J_k$ be in the domain of attraction of a positively skewed sum-stable law with stability parameter $0 < \beta < 1$; more precisely,
+\begin{theorem}
+Let the waiting times $J_k$ be in the domain of attraction of a positively skewed sum-stable law with stability parameter $0 < \beta < 1$; more precisely,
 \begin{align} \label{eq:stability}
@@
 $$ 
+\end{theorem}
 

### 2018-12-09 article_springer/article_springer.Rmd
Beautify remark

@@
 
-**Remark:**
+\vspace{12pt}
 
-: If $\beta = 1$, the result of the Theorem above is standard, see e.g. 
-Equation (2.2) in @Gut1999. In @Anderson1987  a similar result is shown with a different choice of scaling constant.
+**Remark.** If $\beta = 1$, the result of the Theorem above is standard, see e.g. 
+Equation (2.2) by @Gut1999. @Anderson1987 derives a similar result with a 
+different choice of scaling constant.
 

### 2019-04-09 article_springer/article_springer.Rmd
Change pictures, make everything reproducible

--- 2018-12-09 article_springer/article_springer.Rmd
@@
   \usepackage{natbib}
-  \newtheorem{definition}{Definition}
 
@@
 library(MittagLeffleR)
-devtools::install_github("UNSW-MATH/CTRE")
+devtools::install_github("strakaps/CTRE")
+library("CTRE")
 library(CTRE)
-setwd("~/GitHub/bursty-POT/article_springer")
+install.packages("here")
+library(here)
 Sys.setenv(TEXINPUTS=getwd(),
@@
 library(magrittr)
+library(gridExtra)
+library(ggplot2)
+library(dplyr)
 set.seed(12345)
@@
 
-\begin{definition}[MRP]
-Let $(W,J), (W_1, J_1), (W_2, J_2), \ldots$ be i.i.d. pairs of random 
-variables, where the $W_k > 0$ are interpreted as the \emph{waiting times}
-and $J_k \in [x_L, x_R]$ as the \emph{event magnitudes}
+**Definition (MRP):**
+
+: Let $(W,J), (W_1, J_1), (W_2, J_2), \ldots$ be i.i.d. pairs of random 
+variables, where the $W_k > 0$ are interpreted as the *waiting times* 
+and $J_k \in [x_L, x_R]$ as the *event magnitudes* 
 ($x_L \in [-\infty, +\infty), x_R \in (-\infty, +\infty]$). 
-If $W$ and $J$ are independent, the Marked Renewal Process is said to be \emph{uncoupled}. 
-\end{definition}
+If $W$ and $J$ are independent, the Marked Renewal Process is said to be *uncoupled*.
 
@@
 
-\begin{definition}[CTRE]
-Given a threshold $\ell \in (x_L, x_R)$, 
+**Definition (CTRE):**
+
+: Given a threshold $\ell \in (x_L, x_R)$, 
 consider the stopping time 
@@
 two i.i.d. sequences $T(\ell,n)$ and $X(\ell, n)$, $n \in \mathbb N$, 
-called the "interarrival times" and the "exceedances", respectively.
+called the "inter-arrival times" and the "exceedances", respectively.
 The pair sequence $(T(\ell, n), W(\ell, n))_{n \in \mathbb N}$ is called 
@@
 uncoupled.
-\end{definition}
 
-```{r thresholdedBursty, message=FALSE, fig.height=3, fig.width=8, fig.cap="\\label{fig:thresholdedBursty}Exceedances (red) and Times until Exceedance (durations between blue crosses) for a given threshold $\\ell$ (dashed line)."}
+```{r thresholdedBursty, message=FALSE, fig.height=6, fig.width=7,out.width='70%',fig.align='center',fig.cap="\\label{fig:thresholdedBursty}Exceedances (red) and times until Exceedance (durations between blue crosses) for a given threshold $\\ell$ (dashed line)."}
 tail <- params$tail
@@
 sigma <- (cos(pi*tail/2))^(1/tail)
-
 times <- cumsum(stabledist::rstable(n, tail, 1, sigma, pm=1))
-#times<-cumsum(rpareto(n,tail))
 magnitudes <- extRemes::revd(n, scale = 1, shape = 0)
 sim_ctre <- ctre(data.frame(times, magnitudes)) 
-par(mfrow = c(1,2)) 
 p1<-plot(sim_ctre, p = 0.01, main = "Simulated MRP") 
 p2<-flares %>% ctre() %>% plot(p = 0.02, log = 'y', main = "HXRBS data") 
-library(gridExtra)
-grid.arrange(p1, p2, nrow = 2)
+grid.arrange(p1,p2)
+
 ```
@@
 One drawback of this method is that constant priors for the tail parameter are needed for the calculation of the estimates.
-@Cahoy2010 proposed a moment estimator of the log transformed data, which does not require any prior.
-Furthermore, they performed simulation studies illustrating that the log-Moment outperforms the fractional moment estimator with respect to bias and root mean squared error (RMSE).
+@Cahoy2010 proposed a moment estimator of the log-transformed data, which does not require any prior.
+Furthermore, they performed simulation studies illustrating that the log-moment outperforms the fractional moment estimator with respect to bias and root mean squared error (RMSE).
 
@@
 
-```{r MSE, echo=FALSE, fig.height=12, fig.cap="\\label{fig:MSE} MSE for sample sizes n=30, 100, 200 for the tail and scale estimations via log-moments and maximum likelihood estimation", out.width = '100%'}
-knitr::include_graphics("MSE_n25_100_200.pdf")
+```{r MSE, echo=FALSE, fig.height=7,fig.width=8,fig.align="center", fig.cap="\\label{fig:MSE}MSE for sample sizes n=25, 100, 200 for tail and scale estimation via log-moments and mle", out.width = '90%'}
+load(here::here("article_springer\\article_springer_files\\ML_estim_simu","tbl_ges.RData"))
+tbl_ges %>% 
+  filter(n == "25" || n == "100" || n=="200") %>%
+  filter(true.scale == "1") %>% 
+  ggplot(aes(true.tail, mse, colour = method)) + 
+  geom_line() + geom_point() + 
+  facet_wrap(c("n","param"), scales = "free", ncol = 2) + 
+  scale_color_manual(values=c("red", "blue"))
 ```
@@
 Since the Mittag-Leffler distribution is heavy-tailed, many researchers would intuitively give the highest importance to the tail behaviour of the distribution.
-Of course, one can also use established tail exponent estimators for the estimation of the parameter $\beta$ such as the Hill estimator
+Of course, one can also use established tail exponent estimators for the estimation of the parameter $\beta$ such as the Hill estimator [@hill1975simple]
 \begin{align*}
@@
 
-```{r Hillplots, echo=FALSE, fig.align="center", fig.cap="\\label{fig:Hillplots} Hillplots for simulated Mittag-Leffler distributed rv's with tail parameter 0.5 (two plots in the right column) and 0.8 (two plots in the left column) and sample sizes 200 (two plots in the lower row) and 1000 (two plots in the upper row).
-", out.width = '90%'}
- knitr::include_graphics("Hillplots.pdf")
-```
+```{r Hillplots, echo=FALSE, fig.align="center", fig.cap="\\label{fig:Hillplots}Hillplots for simulated Mittag-Leffler data with sample size 200 (left) and 1000 (right). ", out.width = '90%'}
+hill_estim<-function(k,data){
+  n<-length(data)
+  data<-sort(data)
+  data_thinned<-data[(n-k):n]
+  r<-1/k * sum(log(data_thinned/data_thinned[1]))
+  return(1/r)
+}
 
-Since the exponential distribution is nested in the Mittag-Leffler family of distributions, an appropriate way to choose between a model with exponential and Mittag-Leffler inter-exceedance times seems to be a Likelihood ratio test.
-Although the two models are nested, the assymptotic distribution is not $\chi^2_1$-distributed, the classical Theorem of Wilk doesn't apply since under $H_0$ the parameter $\beta$ of the Mittag-Leffler distribution is equal to one and hence lies under $H_0$ on the boundary of the parameter space $(0,1]$.
-Nonetheless, one can perform a bootstrapped log-likelihood ratio test.
-In Figure \ref{Fig:LRT} one can see the power for the bootstrapped LRT for Mittag-Leffler distributions with different tail parameters.
-As expected the power gets smaller for tail parameters close to one, since the Mittag-Leffler distribution converges for $\beta \rightarrow 1$ to an exponential distribution.
-Consequently, for tail parameters close to one it is hard to differentiate a Mittag-Lefller distribution from an exponential.
+hill_estim_plot<-function(k_min,data,k_max=n,true_tail){
+  n<-length(data)
+  x_values<-k_min:k_max
+  y_values<-sapply(x_values,hill_estim,data=data)
+  df<-data.frame(x=x_values,y=y_values)
+  ggplot2::ggplot(data=df,aes(x_values,y_values))+ geom_line(color="blue")+xlab("Order Statistics") + ylab("Hill-Estimator of Tail Index") +
+  coord_cartesian(ylim=c(0,1.5)) + geom_hline(yintercept=true_tail, linetype="dashed", color = "red", size=0.5)
+}
 
-```{r likelihood-ratio-test}
-flares_arrivals <- flares %>% ctre() %>% thin(k = 500) %>% interarrival()
-mlmle_out <- mlmle(data = flares_arrivals)
+data_ml_1<-rml(n=200,tail=0.8,scale=1)
+p1<-hill_estim_plot(k_min=30,data=data_ml_1,true_tail=0.8)
+
+data_ml_2<-rml(n=1000,tail=0.8,scale=1)
+p2<-hill_estim_plot(k_min=30,data=data_ml_2,true_tail=0.8)
+grid.arrange(p1,p2,ncol=2)
 ```
@@
 Instead, a valid approach is a bootstrapped log-likelihood ratio test 
-(PUT REFERENCE HERE). 
+[see e.g. @davison1997bootstrap]. 
 Figure \ref{Fig:LRT} displays the power for the bootstrapped LRT for Mittag-Leffler distributions with varying tail parameters.
 As expected, the power decreases for tail parameters close to one, since the Mittag-Leffler distribution converges as $\beta \uparrow 1$ to an exponential distribution; it becomes hard to differentiate a Mittag-Lefller distribution from an exponential.
-(PUT ALL 4 CURVES INTO ONE PLOT)
 
-```{r LRT power, echo=FALSE, fig.align="center", fig.cap="\\label{Fig:LRT} Power for bootstrapped LRT for different sample sizes", out.width = '80%'}
-knitr::include_graphics("Plots_LRT_boot.pdf")
+```{r LRT_power, echo=FALSE, fig.align="center", fig.cap="\\label{Fig:LRT} Power for bootstrapped LRT for different sample sizes",out.width='90%'}
+load("C:/Users/hees/Dropbox (Uni)/UniDortmund/Forschung/ForschungCTRMs/Bursty_Pot_Paper_Simus/Simulationstudy_LRT_boot/estimates_df_LRT_boot1_01.RData")
+df_LRT_boot_01 %>% filter(n=="20" || n=="50" || n=="100" || n=="200") %>% ggplot(aes(x=true.tail,y=power)) +  geom_line(aes(y=power,group=n,color=factor(n)),linetype="solid",size=0.7)+
+  labs(y="Power",x= "True tail parameter")+
+  scale_color_manual(values=c("red", "blue","darkgreen","black"),name  ="Sample size")
 ```
@@
 par(mfrow = c(1,2))
+df1<-data.frame(x=xx,y=rep(1, length(xx)))
+col<-c("red","blue","darkgreen","black")
+
 plot(xx, rep(1, length(xx)), ylim = c(0.001,1), type = 'n', log = 'xy', 
@@
   yy <- dml(x = xx + t_0[k], tail = tail, scale = scale) / cond
-  lines(xx,yy, col = k+1, lty = k)
+  lines(xx,yy, col = col[k], lty = k+1)
 }
-legend("bottomleft", c("t_0 = 0", "t_0 = 1", "t_0 = 10"), col = 2:4, lty = 1:3)
+legend("bottomleft", c("t_0 = 0", "t_0 = 1", "t_0 = 10"), col = c("red","blue","darkgreen"), lty = 2:4)
 
@@
 t_0 <- 1
+
 plot(xx, rep(1, length(xx)), ylim = c(0.001,2), type = 'n', log = 'xy', 
@@
   )
-  lines(xx,yy, col = k+1, lty = k)
+  lines(xx,yy, col = col[k], lty = k+1)
 }
-legend("bottomleft", c("beta = 0.7", "beta = 0.8", "beta = 0.95", "beta = 0.99"), col = 2:5, lty = 1:4)
+legend("bottomleft", c("beta = 0.7", "beta = 0.8", "beta = 0.95", "beta = 0.99"), col = c("red","blue","darkgreen","black"), lty = 2:5)
 
@@
 To test our inference method via stability plots, we have simulated 
-independent waiting time and magnitude pairs $(W_k, J_k)$ for three different
-situations: stable waiting times, Pareto waitings times and Exponential waiting 
-times. In order to have exact 
+independent waiting time and magnitude pairs $(W_k, J_k)$ (see upper panel in 
+Figure \ref{fig:thresholdedBursty}) for three different situations: stable waiting times, Pareto waitings times and Exponential waiting times. In order to have exact 
 analytical values available for $\beta$ and $\sigma_0$, a distribution for 
@@
 
-<!-- ```{r simulated-example, message=FALSE, warning=FALSE, fig.cap=caption} -->
-<!-- k_max <- 500 -->
-
-<!-- thin_sim_ctre <- thin(ctre = sim_ctre, k = k_max) -->
-<!-- # par(mfrow=c(1,2)) -->
-<!-- MLestimates(ctre = thin_sim_ctre, tail = params$tail, scale = n^(1/params$tail)) -->
-<!-- ``` -->
-
 By the Theorem, the distribution 
@@
 which means 
-$\sigma_0 = n^{1/\beta}$. we have chosen $\beta=1$ in the stable as well in the
-Pareto case. Figure \ref{fig:Ex1figs} displays plots of $\hat \beta(k)$ vs. $k$ for
-the first example with stable distributed waiting times. In the left picture we 
-used the log moment estimator, in the middle picture maximum likelihood estimates 
-(both applied to the inter-exceedance times) and for the right picture hill 
-estimators applied to the inter-arrival times. Recall that $k$ is the index of the 
-order statistics of $J_k$ at which the threshold $\ell$ is placed.
+$\sigma_0 = n^{1/\beta}$.
+we have chosen $\beta=1$ in the stable as well in the Pareto case.
+Figure \ref{Ex1figs} displays plots of $\hat \beta(k)$ vs.
+$k$ for the first example with stable distributed waiting times.
+In the left picture we used the log-moment estimator, in the middle picture maximum likelihood estimates (both applied to the inter-exceedance times) and for the right picture hill estimators applied to the inter-arrival times.
+Recall that $k$ is the index of the order statistics of $J_k$ at which the threshold $\ell$ is placed.
 
-```{r Ex1figs, echo=FALSE,fig.height=7,fig.cap="\\label{fig:Ex1figs} Stability Plots for m=100 simulation runs for Example 1 (stable distributed waiting times, true tail parameter =0.8).
-The grey lines, the red line and the blue lines are the log Moment, the MLE and the hill estimator, repectively, for different $k$'s on the x-axis.
-The dark lines in each picture are the means of the concerning estimators for different $k$'s.", fig.show='hold', out.width = '32%'}
-knitr::include_graphics(c("SimuStudy_StabilityPlots_Ex1_Tail08_logMoms.pdf","SimuStudy_StabilityPlots_Ex1_Tail08_mles.pdf","SimuStudy_StabilityPlots_Ex1_Tail08_hill.pdf"))
+```{r Ex1figs, message=FALSE,echo=FALSE,fig.height=7,fig.align="center",fig.cap="\\label{Fig:Ex1figs} Stability Plots for m=100 simulation runs for Example 1 (stable distributed waiting times, true tail parameter =0.8).
+The grey lines, the red line and the blue lines are the log-moment, the MLE and the hill estimator, repectively, for different $k$'s on the x-axis.
+The dark lines in each picture are the means of the concerning estimators for different $k$'s.", fig.show='hold', out.width = '90%'}
+
+path<-here::here("article_springer/article_springer_files/Simulation_results")
+files<-list.files(path)
+file_dirs<-paste(path,"/",files,sep="")
+invisible(sapply(file_dirs,FUN=load,envir=.GlobalEnv,verbose=FALSE))
+
+#Tail Parameter
+
+# Example One
+
+#logMoment estimator
+logMom_Ex1_tail<-ggplot()+ geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_estimates_tail08_logMoms_Ex1) +
+  coord_cartesian(ylim = c(0.5, 1.5)) +
+  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_logMoms_Ex1) + ylab("Estimated tail") + geom_hline(yintercept=0.8, linetype="dashed", color = "red")
+
+#ml estimator
+mle_Ex1_tail<-ggplot() + geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_estimates_tail08_mles_Ex1) +
+  coord_cartesian(ylim = c(0.5, 1.5)) +
+  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_mles_Ex1) + ylab("Estimated tail") + geom_hline(yintercept=0.8, linetype="dashed", color = "red")
+
+#Hill estimator
+hill_Ex1_tail<-ggplot()+ geom_line(data=tbl_estimates_tail08_hill_Ex1,aes(x=k,y=value,group=rep),colour="lightgrey") +
+  coord_cartesian(ylim = c(0.5, 1.5)) +
+  geom_line(data=means.tbl_hill_Ex1,aes(x=k, y=mw),colour="black") + ylab("Estimated tail") +  geom_hline(yintercept=0.8, linetype="dashed", color = "red")
+
+#Example Two
+
+#logMoment estimator
+logMom_Ex2_tail<-ggplot()+ geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_estimates_Ex2_Pareto_tail08_logMoms) +
+  coord_cartesian(ylim = c(0.5, 1.5)) +
+  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_logMoms_Ex2) + ylab("Estimated tail") + geom_hline(yintercept=0.8, linetype="dashed", color = "red")
+
+#ml estimator
+mle_Ex2_tail<-ggplot() + geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_estimates_Ex2_Pareto_tail08_mles) +
+  coord_cartesian(ylim = c(0.5, 1.5)) +
+  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_mles_Ex2) + ylab("Estimated tail") + geom_hline(yintercept=0.8, linetype="dashed", color = "red")
+
+#Hill estimator
+hill_Ex2_tail<-ggplot() + geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_estimates_Ex2_Pareto_tail08_hill_times) +
+  coord_cartesian(ylim = c(0.5, 1.5)) +
+  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_hill_times_Ex2) + ylab("Estimated tail") +  geom_hline(yintercept=0.8, linetype="dashed", color = "red")
+
+#Example Three
+
+#logMoment estimator
+logMom_Ex3_tail<-ggplot()+ geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_estimates_Example3_Exp_logMoms) +
+  coord_cartesian(ylim = c(0.5, 1.5)) +
+  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_logMoms_Ex3) + ylab("Estimated tail") + geom_hline(yintercept=1, linetype="dashed", color = "red")
+
+#ml estimator
+mle_Ex3_tail<-ggplot() + geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_estimates_Example3_Exp_mles) +
+  coord_cartesian(ylim = c(0.5, 1.5)) +
+  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_mles_Ex3) + ylab("Estimated tail") + geom_hline(yintercept=1, linetype="dashed", color = "red")
+
+#Hill estimator
+hill_Ex3_tail<-ggplot() + geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_estimates_Example3_Exp_hill_times) +
+  coord_cartesian(ylim = c(0.5, 10)) +
+  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_hill_times_Ex3) + ylab("Estimated tail") + geom_hline(yintercept=1, linetype="dashed", color = "red")
+
+grid.arrange(logMom_Ex1_tail,mle_Ex1_tail,hill_Ex1_tail,logMom_Ex2_tail,mle_Ex2_tail,hill_Ex2_tail,logMom_Ex3_tail,mle_Ex3_tail,hill_Ex3_tail,ncol=3)
+
 ```
-Figure \ref{fig:Ex2figs} shows the estimates for different $k$'s and for the
-different estimators for the tail parameter $\beta$. Again one can see that 
-the Hill estimator has a higher variance.
+Figure \ref{Ex2figs} shows the estimates fordifferent $k$'s and for the different estimators for the tail parameter $\beta$.
+Again one can see, that there is much more variance between the stability plots for the different simulation runs in case of the hill estimator compared to the other two estimators.To show how the different estimates behave in the case that $\beta=1$, hence, the inter-exceedance times are exponetial distributed, we simulated in a last example exponetial distributed waiting times.
 
-```{r Ex2figs, echo=FALSE,fig.height=7,fig.cap="\\label{fig:Ex2figs} Stability Plots for m=100 simulation runs for Example 2 (Pareto distributed waiting times, true tail parameter =0.8).
-The grey lines, the red line and the blue lines are the log Moment, the MLE and the hill estimator, repectively, for different $k$'s on the x-axis.
-The dark lines in each picture are the means of the concerning estimators for different $k$'s.", fig.show='hold', out.width = '32%'}
-knitr::include_graphics(c("SimuStudy_StabilityPlots_Ex2_Tail08_logMoms.pdf","SimuStudy_StabilityPlots_Ex2_Tail08_mles.pdf","SimuStudy_StabilityPlots_Ex2_Tail08_hill.pdf"))
-```
-To show how the different estimates behave in the case where $\beta=1$
-(the exponential case), we simulated in a last example exponentially distributed
-waiting times.
+```{r Ex1figsScale, echo=FALSE,fig.height=7,fig.align="center",fig.cap="\\label{Fig:Ex1figsScale} Stability Plots for the scale parameter for Example 1 (stable distributed waiting times, true scale parameter = 1).", fig.show='hold', out.width = '90%'}
+#Scale Parameter
 
-```{r Ex3figs, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex3figs} Stability Plots for m=100 simulation runs for Example 3 (Exponentially distributed waiting times, true tail parameter =0.8).
-The grey lines, the red line and the blue lines are the log Moment, the MLE and the hill estimator, repectively, for different $k$'s on the x-axis.
-The dark lines in each picture are the means of the concerning estimators for different $k$'s.", fig.show='hold', out.width = '32%'}
-knitr::include_graphics(c("SimuStudy_StabilityPlots_Ex3_logMoms.pdf","SimuStudy_StabilityPlots_Ex3_mles.pdf","SimuStudy_StabilityPlots_Ex3_hill_times.pdf"))
+#Example One
+logMom_Ex1_scale<-ggplot()+ geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_scales_logMoms_Ex1) +
+  coord_cartesian(ylim = c(0, 2)) +
+  geom_line(aes(x=k, y=mw),colour="black",means.tbl_scales_logMoms_Ex1) + ylab("Estimated scale") + geom_hline(yintercept=1, linetype="dashed", color = "red")
+
+mle_Ex1_scale<-ggplot()+ geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_scales_mles_Ex1) +
+  coord_cartesian(ylim = c(0, 2)) +
+  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_scales_mles_Ex1) + ylab("Estimated scale") + geom_hline(yintercept=1, linetype="dashed", color = "red")
+
+#Example Two
+
+logMom_Ex2_scale<-ggplot()+ geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_scales_logMoms_Ex2) +
+  coord_cartesian(ylim = c(0, 2)) +
+  geom_line(aes(x=k, y=mw),colour="black",means.tbl_scales_logMoms_Ex2) + ylab("Estimated scale") + geom_hline(yintercept=1, linetype="dashed", color = "red")
+
+mle_Ex2_scale<-ggplot()+ geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_scales_mles_Ex2) +
+  coord_cartesian(ylim = c(0, 2)) +
+  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_scales_mles_Ex2) + ylab("Estimated scale") + geom_hline(yintercept=1, linetype="dashed", color = "red")
+
+#Example Three
+
+logMom_Ex3_scale<-ggplot()+ geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_scales_logMoms_Ex3) +
+  coord_cartesian(ylim = c(0, 2)) +
+  geom_line(aes(x=k, y=mw),colour="black",means.tbl_scales_logMoms_Ex3) + ylab("Estimated scale") + geom_hline(yintercept=1, linetype="dashed", color = "red")
+
+mle_Ex3_scale<-ggplot()+ geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_scales_mles_Ex3) +
+  coord_cartesian(ylim = c(0, 2)) +
+  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_scales_mles_Ex3) + ylab("Estimated scale") + geom_hline(yintercept=1, linetype="dashed", color = "red")
+
+grid.arrange(logMom_Ex1_scale,mle_Ex1_scale,logMom_Ex2_scale,mle_Ex2_scale,logMom_Ex3_scale,mle_Ex3_scale,ncol=2)
 ```
@@
   and create a QQ Plot for the Mittag-Leffler distribution. 
-  Use a log-Moment estimate of the tail parameter for the theoretical / population 
+  Use a log-moment estimate of the tail parameter for the theoretical / population 
   quantiles of the plot.
@@
 
-```{r flare-diagnostics-2, fig.height=4.5, fig.width=8, fig.cap="Diagnostic plots for the solar flare data: empirical copula and QQ Plot. \\label{fig:flare-diagnostics-2}"}
-par(mfrow = c(1,2))
+```{r flare-diagnostics-2, fig.height=4.5, fig.width=4.5, fig.align="center",fig.cap="Diagnostic plots for the solar flare data: empirical copula and QQ Plot.
+\\label{fig:flare-diagnostics-2}",out.width="70%"}
 empcopula(flares_ctre)
+```
+
+```{r flare-diagnostics-3, fig.height=4.5, fig.width=4.5, fig.align="center",fig.cap="Diagnostic plots for the solar flare data: empirical copula and QQ Plot.
+\\label{fig:flare-diagnostics-2}",out.width="70%"}
 flares_ctre %>% interarrival() %>% mlqqplot(log = 'xy', tail = 0.85, main = "Mittag-Leffler QQ Plot")
@@
 
-Figure \ref{fig:flares} shows the stability plots for the solar flare data, on the 
-left for the tail parameter and on the right for the scale parameter. Dotted lines 
-show 95% confidence intervals, which are derived from the asymptotic normality of 
-the log-moments estimators [@Cahoy2013] and the $\delta$-method 
-[see @MittagLeffleR], 
-dashed lines show the actual values of $\beta$ resp.\ $\sigma_0$. The stability 
-plot for the tail stabilizes nicely round about 0.85 (dotted line), while it is a 
-little bit harder to deduce an estimate for the scale parameter. Howerever, the 
-stability plot for the scale parameter seems to stabilize round about $3 \times 
-10^7$.
+Figure \ref{fig:flares} shows the stability plots for the solar flare data, on the left for the tail parameter and on the right for the scale parameter.
+Dotted lines show 95% confidence intervals, which are derived from the asymptotic normality of the log-moments estimators [@Cahoy2013] and the $\delta$-method [@MittagLeffleR, dashed lines show the actual values of $\beta$ resp.\ $\sigma_0$.
+The stability plot for the tail stabilizes nicely round about 0.85 (dotted line), while it is a little bit harder to deduce an estimate for the scale parameter.
+Howerever, the stability plot for the scale parameter seems to stabilize round about $3 \times 10^7$.
 
@@
 
-i) a heavy tail of the interarrival time distribution of threshold crossings (long rests), and
+i) a heavy tail of the inter-arrival time distribution of threshold crossings (long rests), and
 
@@
 The authors would like to thank Prof.
-Peter Scheffler for insights on stochastic process limits for CTRMs, Roloand Fried for discussion according the statistical methods and Gurtek Gill who helped create the MittagLeffleR R-package.
+Peter Scheffler for insights on stochastic process limits for CTRMs, Prof.
+Roland Fried for discussion according the statistical methods and Gurtek Gill who helped create the MittagLeffleR R-package.
 
@@
 
-# Appendix {-}
-
-```{r Ex1figsScale, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex1figsScale} Stability Plots for the scale parameter for Example 1 (stable distributed waiting times, true scale parameter = 1).", fig.show='hold', out.width = '40%'}
-knitr::include_graphics(c("SimuStudy_StabilityPlots_Ex1_Scales_logMoms.pdf","SimuStudy_StabilityPlots_Ex1_Scales_mles.pdf"))
-```
-
-```{r Ex2figsScale, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex2figsScale} Stability Plots for the scale parameter m=100 simulation runs for Example 2 (stable distributed waiting times, true scale parameter = 1).", fig.show='hold', out.width = '40%'}
-knitr::include_graphics(c("SimuStudy_StabilityPlots_Ex2_Scales_logMoms.pdf","SimuStudy_StabilityPlots_Ex2_Scales_mles.pdf"))
-```
-
-```{r Ex3figsScale, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex3figsScale} Stability Plots for the scale parameter for m=100 simulation runs for Example 3 (stable distributed waiting times, true scale parameter = 1).", fig.show='hold', out.width = '40%'}
-knitr::include_graphics(c("SimuStudy_StabilityPlots_Ex3_Scales_logMoms.pdf","SimuStudy_StabilityPlots_Ex3_Scales_mles.pdf"))
-```
-\newpage
-
 # References {-}

### 2019-04-09 article_springer/article_springer_files/ML_estim_simu/ML_estim_simustudy.R

@@ -1,0 +1,50 @@
+#Simulation Study #####
+
+library(future)
+library(future.apply)
+library(MittagLeffleR)
+library(dplyr)
+library(TLMoments)
+library(progress)
+library(magrittr)
+library(ggplot2)
+
+
+plan(multiprocess)
+
+tails <- seq(0.2,0.9,0.1)
+scales <- c(0.1,1,10)
+ns <- seq(25,200,25)
+m<-1000
+
+pb <- progress_bar$new(total = length(tails)*length(scales)*length(ns), format = "[:bar] tail: :tail, scale: :scale, n: :n")
+
+estimates <- sapply(ns, function(n) sapply(tails, function(tail) sapply(scales, function(scale) {
+  pb$tick(tokens = list(tail = tail, scale = scale, n = n))
+  future_replicate(m, {
+
+
+    x <- rml(n, tail = tail, scale = scale)
+    cbind(
+      logMom = MittagLeffleR::logMomentEstimator(x)[c(1,2)],
+      ML = MittagLeffleR::mlmle(x)$par
+    )
+
+  })
+}, simplify = "array"), simplify = "array"), simplify = "array")
+
+
+reshape2::melt(estimates) %>%
+  as.tbl %>%
+  rename(param = Var1, method = Var2, rep = Var3, true.scale = Var4, true.tail = Var5, n = Var6) %>%
+  mutate(true.scale = scales[true.scale], true.tail = tails[true.tail], n = ns[n]) %>%
+  mutate(true.value = case_when(param == "tail" ~ true.tail, param == "scale" ~ true.scale)) %>%
+  group_by(param, n, true.scale, true.tail, method) %>%
+  summarise(
+    mse = mean((value-true.value)^2),
+    sqbias = mean(value-true.value)^2,
+    var = var(value)
+  ) ->
+  tbl_ML_estim
+
+save(tbl_ML_estim,file="tbl_ML_estim.RData")

### 2019-04-09 article_springer/article_springer_files/Simulation_plots/Plots_SimuStudy.R

@@ -1,0 +1,97 @@
+library(ggplot2)
+library(gridExtra)
+library(here)
+
+path<-here("article_springer/article_springer_files/Simulation_results")
+files<-list.files(path)
+file_dirs<-paste(path,"/",files,sep="")
+lapply(file_dirs,FUN=load,.GlobalEnv)
+
+#Tail Parameter
+
+# Example One
+
+#logMoment estimator
+logMom_Ex1_tail<-ggplot()+ geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_estimates_tail08_logMoms_Ex1) +
+  coord_cartesian(ylim = c(0.5, 1.5)) +
+  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_logMoms_Ex1) + ylab("Estimated tail") + geom_hline(yintercept=0.8, linetype="dashed", color = "red")
+
+#ml estimator
+mle_Ex1_tail<-ggplot() + geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_estimates_tail08_mles_Ex1) +
+  coord_cartesian(ylim = c(0.5, 1.5)) +
+  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_mles_Ex1) + ylab("Estimated tail") + geom_hline(yintercept=0.8, linetype="dashed", color = "red")
+
+#Hill estimator
+hill_Ex1_tail<-ggplot()+ geom_line(data=tbl_estimates_tail08_hill_Ex1,aes(x=k,y=value,group=rep),colour="lightgrey") +
+  coord_cartesian(ylim = c(0.5, 1.5)) +
+  geom_line(data=means.tbl_hill_Ex1,aes(x=k, y=mw),colour="black") + ylab("Estimated tail") +  geom_hline(yintercept=0.8, linetype="dashed", color = "red")
+
+
+#Example Two
+
+#logMoment estimator
+logMom_Ex2_tail<-ggplot()+ geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_estimates_Ex2_Pareto_tail08_logMoms) +
+  coord_cartesian(ylim = c(0.5, 1.5)) +
[…]

### 2019-04-09 article_springer/article_springer_files/Simulation_study_Rcode/Example2_burstPotPaper_scaletail08_Cluster.R

@@ -1,0 +1,131 @@
+#Simulationsstudy - Comparisions of Inference procedure and different estimation methods
+
+# Author: Katharina Hees
+# Created: 03/12/2018
+
+
+library("CTRE")
+library("MittagLeffleR")
+library("magrittr")
+library("dplyr")
+library("ggplot2")
+library("parallel")
+library("ReIns")
+
+
+p <- as.integer(Sys.getenv("PBS_ARRAYID"))
+print(p)
+
+###Functions########################################
+
+hill_estim<-function(k,data){
+  n<-length(data)
+  data<-sort(data)
+  data_thinned<-data[(n-k):n]
+  r<-1/k * sum(log(data_thinned/data_thinned[1]))
+  return(1/r)
+}
+
+###################################################
+
+#Example One  - CTRE with Pareto distributed waiting times - tail=0.8
+#1_1
+n<-10000
+tail<-0.8
+C<-(1/gamma(1-tail))^{1/tail}
+times<-cumsum(rpareto(n,shape=tail,scale=C))
+magnitudes<-extRemes::revd(n, scale = 1, shape = 0)
+sim_ctre<-ctre(data.frame(times, magnitudes))
+
+ntasks <- 4
+print(ntasks)
+
+# Cluster initialisieren
+cl <- makeCluster(ntasks)
+clusterExport(cl, "sim_ctre")
+clusterExport(cl, "hill_estim")
+clusterEvalQ(cl,library(MittagLeffleR))
+clusterEvalQ(cl,library(CTRE))
+clusterEvalQ(cl,library("magrittr"))
+
+# Zufallszahlengeneratoren auf allen Workern des Clusters mit einem bestimmten
+# seed initialisieren (verhindert Zyklen in den Zufallszahlen zwischen den
+# Workern)
+clusterSetRNGStream(cl,iseed=42)
+
+#Code
+ks<-c(30:500)
+estimates_scaletail08<-parSapply(cl,ks, FUN = function(k){
+  ias<-sim_ctre %>% thin(k=k) %>% interarrival
+  cbind(
+    logMoms=logMomentEstimator(ias)[c(1,2)],
+    mles=mlmle(ias)$par[c(1,2)],
+    hill_times=c(hill_estim(k=k,data=times),NA)
+  )},simplify = "array")
+
+stopCluster(cl = cl)
+
+
[…]

### 2019-09-16 article_springer/article_springer.Rmd
small changes

@@
   the threshold exceedances are modeled via the standard 
-  Peaks Over Threshold (POT) method.
+  Peaks-Over-Threshold (POT) method.
   For high thresholds and 
@@
 
-preamble: | 
-  \usepackage{amssymb}
-  \usepackage{natbib}
+header-icludes: \usepackage{amssymb,natbib}
 
@@
 
-```{r thresholdedBursty, message=FALSE, fig.height=6, fig.width=7,out.width='70%',fig.align='center',fig.cap="\\label{fig:thresholdedBursty}Exceedances (red) and times until Exceedance (durations between blue crosses) for a given threshold $\\ell$ (dashed line)."}
+```{r thresholdedBursty, message=FALSE, fig.height=6, fig.width=7,out.width='70%',fig.align='center',fig.cap="\\label{fig:thresholdedBursty} Exceedances (red) and times until Exceedance (durations between blue crosses) for a given threshold $\\ell$ (dashed line)."}
 tail <- params$tail
@@
 However, as $\beta \uparrow 1$, ${\rm ML}(\beta, \sigma)$ converges 
-weakly to the exponential distribution ${\rm Exp}(\sigma)$.
+weakly to the exponential distribution ${\rm Exp}(\sigma)$ with mean $\sigma$ test.
 This means that although its moments are all infinite, the Mittag-Leffler
@@
 
-```{r MSE, echo=FALSE, fig.height=7,fig.width=8,fig.align="center", fig.cap="\\label{fig:MSE}MSE for sample sizes n=25, 100, 200 for tail and scale estimation via log-moments and mle", out.width = '90%'}
+```{r MSE, echo=FALSE,warning=FALSE, fig.height=7,fig.width=8,fig.align="center", fig.cap="\\label{fig:MSE} MSE for the estimation of tail (left column) and scale (right column) parameters via log-moment estimator and mle of a Mittag-Leffler sample with varying sample size n=25, 100, 200, varying tails on the x-axis and fixed scale equal to one.", out.width = '90%'}
 load(here::here("article_springer\\article_springer_files\\ML_estim_simu","tbl_ges.RData"))
@@
   filter(true.scale == "1") %>% 
-  ggplot(aes(true.tail, mse, colour = method)) + 
+  ggplot(aes(true.tail, mse, colour = method, group=method)) + 
   geom_line() + geom_point() + 
@@
 Of course, one can also use established tail exponent estimators for the estimation of the parameter $\beta$ such as the Hill estimator [@hill1975simple]
-\begin{align*}
+\begin{align}\label{eq:hill}
 H_{k,n}= \frac{1}{k} \sum_{i=0}^{k-1} \log \frac{X_{n-i,n}}{X_{n-k,n}}. 
-\end{align*}
+\end{align}
 However, these methods are statistically less efficient since they only use a portion of the information contained in the data, as mentioned by @kozubowski2001.
@@
 
-```{r Hillplots, echo=FALSE, fig.align="center", fig.cap="\\label{fig:Hillplots}Hillplots for simulated Mittag-Leffler data with sample size 200 (left) and 1000 (right). ", out.width = '90%'}
+```{r Hillplots, echo=FALSE,warning=FALSE, fig.align="center", fig.cap="\\label{fig:Hillplots} Hillplots for simulated Mittag-Leffler data with true tail 0.8 and sample size 200 (left) and 1000 (right).
+", out.width = '90%'}
 hill_estim<-function(k,data){
@@
 Since the exponential distribution is nested in the Mittag-Leffler family of 
-distributions, a Likelihood Ratio Test seems to be an appropriate way to choose 
+distributions, a Likelihood-ratio Test (LRT) seems to be an appropriate way to choose 
 between a model with exponential and Mittag-Leffler inter-exceedance times.
@@
 on the boundary of the parameter space $(0,1]$. 
-Instead, a valid approach is a bootstrapped log-likelihood ratio test 
-[see e.g. @davison1997bootstrap]. 
-Figure \ref{Fig:LRT} displays the power for the bootstrapped LRT for Mittag-Leffler distributions with varying tail parameters.
+Instead, a valid approach is a bootstrapped Likelihood-ratio test [see e.g. @davison1997bootstrap]. 
+Figure \ref{Fig:LRT} displays the (simulated) power for the bootstrapped LRT for Mittag-Leffler distributions with varying tail parameters based on 1000 simulation runs.
 As expected, the power decreases for tail parameters close to one, since the Mittag-Leffler distribution converges as $\beta \uparrow 1$ to an exponential distribution; it becomes hard to differentiate a Mittag-Lefller distribution from an exponential.
 
-```{r LRT_power, echo=FALSE, fig.align="center", fig.cap="\\label{Fig:LRT} Power for bootstrapped LRT for different sample sizes",out.width='90%'}
-load("C:/Users/hees/Dropbox (Uni)/UniDortmund/Forschung/ForschungCTRMs/Bursty_Pot_Paper_Simus/Simulationstudy_LRT_boot/estimates_df_LRT_boot1_01.RData")
-df_LRT_boot_01 %>% filter(n=="20" || n=="50" || n=="100" || n=="200") %>% ggplot(aes(x=true.tail,y=power)) +  geom_line(aes(y=power,group=n,color=factor(n)),linetype="solid",size=0.7)+
+```{r LRT_power, echo=FALSE,warning=FALSE, fig.align="center", fig.cap="\\label{Fig:LRT} Power for bootstrapped LRT for different sample sizes , varying tails and scale parameter equal to 1.",out.width='90%'}
+load(here::here("article_springer","article_springer_files","ML_LRT_simu","estimates_df_LRT_boot1_01.RData"))
+df_LRT_boot_01 %>% filter(n=="20" || n=="50" || n=="100" || n=="200") %>% ggplot(aes(x=true.tail,y=power)) +  geom_line(aes(y=power,group=factor(n),color=factor(n),linetype=factor(n)),size=0.7)+
+  scale_linetype_manual(values = c("solid","dashed","twodash","dotted"),name  ="Sample size")+
    labs(y="Power",x= "True tail parameter")+
-  scale_color_manual(values=c("red", "blue","darkgreen","black"),name  ="Sample size")
+  scale_color_manual(values=c("red", "blue","darkgreen","black"), name  ="Sample size")
 ```
@@
 where the function $b(c)$ varies regularly at $\infty$ with parameter $1/\beta$.
-Building on the POT (Peaks Over Threshold) method, we propose the following estimation procedure for the distribution of inter-exceedance time $T(\ell)$:
+Building on the POT (Peaks-Over-Threshold) method, we propose the following estimation procedure for the distribution of inter-exceedance time $T(\ell)$:
 
@@
 $$
-where $f(\,\cdot\, | \beta, k^{-1/\beta} \sigma_0)$ is the probability density of ${\rm ML}(\beta, -k^{1/\beta} \sigma_0)$. 
+where $f(\,\cdot\, | \beta, k^{-1/\beta} \sigma_0)$ is the probability density of ${\rm ML}(\beta, k^{-1/\beta} \sigma_0)$. 
 The more time has passed without a threshold crossing, the more the probability distribution shifts towards larger values for the next crossing
@@
 represents the risk of a threshold crossing per unit time, and is a decreasing function for the Mittag-Leffler distribution. 
-```{r hazard, fig.height=4, fig.cap="Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\\beta = 0.8$, $\\sigma_0 = 1$).
-Right: Hazard rate depending on tail parameter $\\beta$.\\label{fig:hazard}"}
+```{r hazard, fig.height=4, fig.cap="\\label{fig:hazard} Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\\beta = 0.8$, $\\sigma_0 = 1$).
+Right: Hazard rate depending on tail parameter $\\beta$."}
 tail <- 0.7
@@
 To test our inference method via stability plots, we have simulated 
-independent waiting time and magnitude pairs $(W_k, J_k)$ (see upper panel in 
-Figure \ref{fig:thresholdedBursty}) for three different situations: stable waiting times, Pareto waitings times and Exponential waiting times. In order to have exact 
-analytical values available for $\beta$ and $\sigma_0$, a distribution for 
-$W_k$ needs to be chosen for which $b(n)$ from \eqref{eq:stability} is known. 
-If we choose $W_k \stackrel{d}{=} D$, where $D$ is as in \eqref{eq:stability}, 
-then due to the stability property we have the *equality* of distribution
+independent waiting time and magnitude pairs $(W_k, J_k)$ for waiting times that follow
+
+(i) a stable distribution,
+
+(ii) a Pareto distribution and
+
+(iii) an Exponential distribution.
+
+In order to have exact analytical values available for $\beta$ and $\sigma_0$, a distribution for $W_k$ needs to be chosen for which $b(n)$ from \eqref{eq:stability} is known.
+For (i) we choose $W_k \stackrel{d}{=} D$, where $D$ is as in \eqref{eq:stability}, then due to the stability property we have the *equality* of distribution
 $W_1 + \ldots + W_n \stackrel{d}{=} b(n) D$, 
@@
 $S_\beta(\cos(\pi \beta/2)^{1/\beta}, +1, 0)$, which is 
-implemented in the R package `stabledist` by @stabledist.
-
-```{r make-caption}
-caption = "Tail and scale estimates for simulated data, with waiting times drawn from the stable distribution $S_\\beta(\\cos(\\pi \\beta/2)^{1/\\beta}, +1, 0)$ with $\\beta = 0.8$.
-Dashed lines are 95\\% confidence intervals, dotted lines are the known theoretical values ($0.8$ and $10000^{1/0.8}$).
-\\label{fig:sim}"
-```
-
-By the Theorem, the distribution 
-of $T(\ell)$ is approximately 
+implemented in the R package `stabledist` by @stabledist. By the Theorem, the distribution of $T(\ell)$ is approximately 
 $$
@@
 $\sigma_0 = n^{1/\beta}$.
-we have chosen $\beta=1$ in the stable as well in the Pareto case.
-Figure \ref{Ex1figs} displays plots of $\hat \beta(k)$ vs.
-$k$ for the first example with stable distributed waiting times.
-In the left picture we used the log-moment estimator, in the middle picture maximum likelihood estimates (both applied to the inter-exceedance times) and for the right picture hill estimators applied to the inter-arrival times.
+In the Pareto example we choose $P(W>t)=Ct^{-\beta}$ with $C=(1/\Gamma(1-\beta))^{1/\beta}$.
+We have chosen $\beta=0.8$ in the stable as well as in the Pareto case.
+As third example we choose Exponential distributed waiting times with a rate of $1$.
+Figure \ref{Fig:TailSimu} shows the stability plots for the estimation of the tail parameter.
+Therefore, $\hat \beta(k)$ vs.
+$k$ is plotted for each of the $m=100$ simulation runs (grey thin lines).
+In the left column one can see the estimates based on the log-moment estimator, the stability plots in the middle are based on the maximum-likelihood estimator and on the right hand on the hill estimator.
 Recall that $k$ is the index of the order statistics of $J_k$ at which the threshold $\ell$ is placed.
+Note, that the hill estimator is here based on the waiting times, not on the inter-exceedance times, hence the estimation is based on much more data.
+If one would base the hill-estimation only on the inter-exceedance times, the sample size would be too small and it would be impossible to deduce an estimate for the tail parameter from the plots (compare Figure \ref{fig:Hillplots}).
+The $k$ on the $x-$axis is in the plots for the hill estimator the $k$ which defines on which orders stats the hill estimator is based on (compare \eqref{eq:hill}).
+The bigger sample size results in the middle in a lower bias.
+But, one can also see, that there is much more variance between the stability plots for the different simulation runs in case of the hill estimator compared to the other two estimators.
+The black line is the mean value of the point estimators for each $k$.
+However, if one wants to get a single estimate via such a stability plot, it would be much more difficult to deduce it from a hill plot compared to the other two estimators.
+Another advantage of the other estimators compared to the hill estimator is, that in the case one has exponential weighting times, the log-moment as well as the mle can detect this by getting an estimate round about $1$.
+The hill estimators is just a tail parameter estimator for Pareto like tails and hence of course fails in case of Exponential inter-exceedance times.
+Figure \ref{Fig:ScaleSimu} shows the stability plots for the different estimators for the scale parameter.
+Here of course only for the log-moment (on the right hand)  and the mle (on the left hand), since the hill estimator is just a tail parameter estimate.
+Here again both estimators show good performance.
+The stability plots in the mle case are a little bit closer to the true value, therefore, the mle is much more computational intesive.
 
-```{r Ex1figs, message=FALSE,echo=FALSE,fig.height=7,fig.align="center",fig.cap="\\label{Fig:Ex1figs} Stability Plots for m=100 simulation runs for Example 1 (stable distributed waiting times, true tail parameter =0.8).
-The grey lines, the red line and the blue lines are the log-moment, the MLE and the hill estimator, repectively, for different $k$'s on the x-axis.
-The dark lines in each picture are the means of the concerning estimators for different $k$'s.", fig.show='hold', out.width = '90%'}
+```{r TailSimuplots, message=FALSE,echo=FALSE,fig.height=7,fig.align="center",fig.cap="\\label{Fig:TailSimu} Stability Plots for m=100 simulation runs for stable distributed waiting times with a tail parameter of 0.8, Pareto distributed waiting times with tail parameter 0.8 and Exponential distributed waiting times.
+The grey thin lines are the stability plots for the different simulation runs and the dark lines are their means.
+The red dotted line shows the true tail parameter.", fig.show='hold', out.width = '100%'}
 
@@
 ```
-Figure \ref{Ex2figs} shows the estimates fordifferent $k$'s and for the different estimators for the tail parameter $\beta$.
-Again one can see, that there is much more variance between the stability plots for the different simulation runs in case of the hill estimator compared to the other two estimators.To show how the different estimates behave in the case that $\beta=1$, hence, the inter-exceedance times are exponetial distributed, we simulated in a last example exponetial distributed waiting times.
 
-```{r Ex1figsScale, echo=FALSE,fig.height=7,fig.align="center",fig.cap="\\label{Fig:Ex1figsScale} Stability Plots for the scale parameter for Example 1 (stable distributed waiting times, true scale parameter = 1).", fig.show='hold', out.width = '90%'}
+```{r ScaleSimuplots, message=FALSE,echo=FALSE,fig.height=7,fig.align="center",fig.cap="\\label{Fig:ScaleSimu} Stability Plots for m=100 simulation runs for stable distributed waiting times with a tail parameter of 0.8, Pareto distributed waiting times with tail parameter 0.8 and Exponential distributed waiting times.
+The grey thin lines are the stability plots for the different simulation runs and the dark lines are their means.
+The red dotted line shows the true tail parameter.", fig.show='hold', out.width = '90%'}
 #Scale Parameter
@@
 
-```{r flare-diagnostics-1, fig.height=7, fig.cap="Diagnostic plots for the solar flare data: auto-correlation function.\\label{fig:flare-diagnostics-1}"}
+```{r flare-diagnostics-1, fig.height=7, fig.cap="\\label{fig:flare-diagnostics-1} Diagnostic plots for the solar flare data: auto-correlation function."}
 flares_ctre <- flares %>% ctre() %>% thin(k = 150)
@@
 
-```{r flare-diagnostics-2, fig.height=4.5, fig.width=4.5, fig.align="center",fig.cap="Diagnostic plots for the solar flare data: empirical copula and QQ Plot.
-\\label{fig:flare-diagnostics-2}",out.width="70%"}
+```{r flare-diagnostics-2, fig.height=4.5, fig.width=4.5, fig.align="center",fig.cap="\\label{fig:flare-diagnostics-2} Diagnostic plots for the solar flare data: empirical copula and QQ Plot.",out.width="70%"}
 empcopula(flares_ctre)
@@
 
-```{r flare-diagnostics-3, fig.height=4.5, fig.width=4.5, fig.align="center",fig.cap="Diagnostic plots for the solar flare data: empirical copula and QQ Plot.
-\\label{fig:flare-diagnostics-2}",out.width="70%"}
+```{r flare-diagnostics-3, fig.height=4.5, fig.width=4.5, fig.align="center",fig.cap="\\label{fig:flare-diagnostics-2} Diagnostic plots for the solar flare data: empirical copula and QQ Plot.",out.width="70%"}
 flares_ctre %>% interarrival() %>% mlqqplot(log = 'xy', tail = 0.85, main = "Mittag-Leffler QQ Plot")
@@
 
-```{r solar-flare-tail-scale, message=FALSE, fig.height=4.5, fig.width=8, fig.cap="\\label{fig:flares}Stability plots for the tail and scale parameter of the Mittag-Leffler distribution of the Solar Flare dataset.
+```{r solar-flare-tail-scale, message=FALSE, fig.height=4.5, fig.width=8, fig.cap="\\label{fig:flares} Stability plots for the tail and scale parameter of the Mittag-Leffler distribution of the Solar Flare dataset.
 Dotted horizontal lines are at $\\beta = 0.85$ and $\\sigma_0 = 3 \\times 10^7$ seconds $\\approx 0.95$ years."}
@@
 
-We have extended the POT (Peaks over Threshold) model, a mainstay of extreme value theory, to "bursty" time series, which have been studied 
+We have extended the POT (Peaks-over-Threshold) model, a mainstay of extreme value theory, to "bursty" time series, which have been studied 
 intensively in statistical physics.

### 2019-09-16 article_springer/article_springer.Rmd
Small last fixes

@@
 However, as $\beta \uparrow 1$, ${\rm ML}(\beta, \sigma)$ converges 
-weakly to the exponential distribution ${\rm Exp}(\sigma)$ with mean $\sigma$ test.
+weakly to the exponential distribution ${\rm Exp}(\sigma)$ with mean $\sigma$.
 This means that although its moments are all infinite, the Mittag-Leffler
@@
 
-# Model Choice and inference for the Mittag-Leffler distribution
+# Model Choice and inference for the Mittag-Leffler distribution{#sec:ML}
 
 The classical POT approach is based on the fact that exceedances above a high threshhold are asymptotically GPD distributed, hence a GPD distribution is fitted to the exceedances above a high enough threshhold.
-Due to the Theorem in the last Section we know that for high thresholds the times between exceedances are asymptotically Mittag-Leffler distributed in case of heavy tailed waiting times between the observations.
+Due to the Theorem in the last Section we know that for high thresholds the times between exceedances are asymptotically Mittag-Leffler distributed in case of heavy-tailed waiting times between the observations.
 Hence, before we talk about inference for the exceedances in the next section, we discuss inference for Mittag-Leffler distributions.
@@
 To deduce the correct tail parameter estimates from these plots is virtually impossible.
+Furthermore the Hill estimator of course completely fails if the inter-arrival times are exponential distributed and not heavy-tailed.
 
-```{r Hillplots, echo=FALSE,warning=FALSE, fig.align="center", fig.cap="\\label{fig:Hillplots} Hillplots for simulated Mittag-Leffler data with true tail 0.8 and sample size 200 (left) and 1000 (right).
+```{r Hillplots, echo=FALSE,warning=FALSE, fig.align="center", fig.cap="\\label{fig:Hillplots} Hillplots for simulated Mittag-Leffler data with true tail 0.8 and sample size 200 (left) and 1000 (right), with number of upper order statics k on which the hill estimator is based on the x-axis.
 ", out.width = '90%'}
@@
 We have verified the validity of our estimation algorithm  via simulations, 
-see the appendix.
+see Section \ref{Simulationstudy}.
 
-# Predicting the time of the next threshold crossing
-
-According to Figure \ref{fig:flares}, for a threshold $\ell$ at the $k$-th order 
-statistic, the fitted threshold exceedance time distribution is 
-$$
-T(\ell) \sim {\rm ML}(\beta, k^{-1/\beta} \sigma_0), 
-$$
-where $\beta = 0.85$ and $\sigma_0 = 3.0 \times 10^7 {\rm sec}$. 
-Unlike the exponential distribution, the Mittag-Leffler distribution is not memoryless, and the probability density of the time $t$ until the next threshold crossing will depend on the time $t_0$ elapsed since the last threshold crossing.
-This density equals 
-$$
-p(t|\beta, \sigma_0, \ell, t_0) = \frac{f(t + t_0 | \beta, k^{-1/\beta} \sigma_0)}{\mathbf P[T_\ell > t_0]}
-$$
-where $f(\,\cdot\, | \beta, k^{-1/\beta} \sigma_0)$ is the probability density of ${\rm ML}(\beta, k^{-1/\beta} \sigma_0)$. 
-The more time has passed without a threshold crossing, the more the probability distribution shifts towards larger values for the next crossing
-(see Figure \ref{fig:hazard}, left panel). The hazard rate 
-$$
-h(t) = \frac{f(t| \beta, k^{-1/\beta} \sigma_0))}{\int_t^\infty f(\tau| \beta, k^{-1/\beta} \sigma_0))\,d\tau}
-$$
-represents the risk of a threshold crossing per unit time, and is a decreasing function for the Mittag-Leffler distribution. 
-```{r hazard, fig.height=4, fig.cap="\\label{fig:hazard} Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\\beta = 0.8$, $\\sigma_0 = 1$).
-Right: Hazard rate depending on tail parameter $\\beta$."}
-tail <- 0.7
-scale <- 1
-t_0 <- c(0, 1, 10)
-from <- 0.1
-to <- 100 * scale
-xx <- exp(seq(from = log(from), to = log(to), length.out = 100))
-par(mfrow = c(1,2))
-df1<-data.frame(x=xx,y=rep(1, length(xx)))
-col<-c("red","blue","darkgreen","black")
-
-plot(xx, rep(1, length(xx)), ylim = c(0.001,1), type = 'n', log = 'xy', 
-     xlab = 't', ylab = 'p')
-for (k in 1:length(t_0)) {
-  cond <- pml(q = t_0[k], tail = tail, scale = scale, lower.tail = FALSE)
-  yy <- dml(x = xx + t_0[k], tail = tail, scale = scale) / cond
-  lines(xx,yy, col = col[k], lty = k+1)
-}
-legend("bottomleft", c("t_0 = 0", "t_0 = 1", "t_0 = 10"), col = c("red","blue","darkgreen"), lty = 2:4)
-
-betas <- c(0.7, 0.8, 0.95, 0.99)
-t_0 <- 1
-
-plot(xx, rep(1, length(xx)), ylim = c(0.001,2), type = 'n', log = 'xy', 
-     xlab = 't', ylab = 'h')
-for (k in 1:length(betas)) {
-  yy <- dml(x = xx, tail = betas[k], scale = scale) / pml(
-    q = xx,
-    tail = betas[k],
-    scale = scale,
-    lower.tail = FALSE
-  )
-  lines(xx,yy, col = col[k], lty = k+1)
-}
-legend("bottomleft", c("beta = 0.7", "beta = 0.8", "beta = 0.95", "beta = 0.99"), col = c("red","blue","darkgreen","black"), lty = 2:5)
-
-```
-The closer $\beta$ is to $1$, the more the hazard rate mimics that of an 
-exponential distribution (a constant function, see Figure \ref{fig:hazard}, 
-right panel).
-
-# Simulation study
+# Simulation study{#Simulationstudy}
 
@@
 However, if one wants to get a single estimate via such a stability plot, it would be much more difficult to deduce it from a hill plot compared to the other two estimators.
-Another advantage of the other estimators compared to the hill estimator is, that in the case one has exponential weighting times, the log-moment as well as the mle can detect this by getting an estimate round about $1$.
+In case that one has only thresholded data and hence a much smaller simple size, the hill estimator gets useless (see Section \ref{sec:ML}).
+Another advantage of the other estimators compared to the hill estimator is, that in the case one has exponential waiting times, the log-moment as well as the mle can detect this by getting an estimate round about $1$.
 The hill estimators is just a tail parameter estimator for Pareto like tails and hence of course fails in case of Exponential inter-exceedance times.
@@
 
-```{r TailSimuplots, message=FALSE,echo=FALSE,fig.height=7,fig.align="center",fig.cap="\\label{Fig:TailSimu} Stability Plots for m=100 simulation runs for stable distributed waiting times with a tail parameter of 0.8, Pareto distributed waiting times with tail parameter 0.8 and Exponential distributed waiting times.
+```{r TailSimuplots, message=FALSE,echo=FALSE,fig.height=7,fig.align="center",fig.cap="\\label{Fig:TailSimu} Stability Plots for m=100 simulation runs for stable distributed waiting times with a tail parameter of 0.8 (top row), Pareto distributed waiting times with tail parameter 0.8 (middle row) and Exponential distributed waiting times (lower row).
+Left column: log-moment estimator, middle column: MLE, right column: Hill estimator.
 The grey thin lines are the stability plots for the different simulation runs and the dark lines are their means.
-The red dotted line shows the true tail parameter.", fig.show='hold', out.width = '100%'}
+The red dotted line shows the true tail parameter.
+", fig.show='hold', out.width = '100%'}
 
@@
 
-```{r ScaleSimuplots, message=FALSE,echo=FALSE,fig.height=7,fig.align="center",fig.cap="\\label{Fig:ScaleSimu} Stability Plots for m=100 simulation runs for stable distributed waiting times with a tail parameter of 0.8, Pareto distributed waiting times with tail parameter 0.8 and Exponential distributed waiting times.
+```{r ScaleSimuplots, message=FALSE,echo=FALSE,fig.height=7,fig.align="center",fig.cap="\\label{Fig:ScaleSimu} Stability Plots for m=100 simulation runs for stable distributed waiting times with a tail parameter of 0.8 (top row), Pareto distributed waiting times with tail parameter 0.8 (middle row) and Exponential distributed waiting times (lower row).
+Left column: log-moment estimator, right column: MLE.
 The grey thin lines are the stability plots for the different simulation runs and the dark lines are their means.
@@
 
-Figures \ref{fig:flare-diagnostics-1} and \ref{fig:flare-diagnostics-2} show the diagnostic plots for a minimum threshold chosen at the 200th order statistic.
+Figures \ref{fig:flare-diagnostics-1}, \ref{fig:flare-diagnostics-2} and \ref{fig:flare-diagnostics-3} show the diagnostic plots for a minimum threshold chosen at the 200th order statistic.
 There is some residual autocorrelation for the sequence of threshold exceedance times that is not accounted for by the CTRE model.
@@
 
-```{r flare-diagnostics-3, fig.height=4.5, fig.width=4.5, fig.align="center",fig.cap="\\label{fig:flare-diagnostics-2} Diagnostic plots for the solar flare data: empirical copula and QQ Plot.",out.width="70%"}
+```{r flare-diagnostics-3, fig.height=4.5, fig.width=4.5, fig.align="center",fig.cap="\\label{fig:flare-diagnostics-3} Diagnostic plots for the solar flare data: empirical copula and QQ Plot.",out.width="70%"}
 flares_ctre %>% interarrival() %>% mlqqplot(log = 'xy', tail = 0.85, main = "Mittag-Leffler QQ Plot")
@@
 
-The fit with a Mittag-Leffler distribution ($\beta = 0.85$) is good, though there are signs that the power-law tail tapers off for very large inter-threshold crossing times.
-There is no apparent dependence between threshold exceedance times and event magnitudes seen in the copula plot.
+The fit with a Mittag-Leffler distribution ($\beta = 0.85$) is good (see Figure \ref{fig:flare-diagnostics-3}), though there are signs that the power-law tail tapers off for very large inter-threshold crossing times.
+There is no apparent dependence between threshold exceedance times and event magnitudes seen in the copula plot (see Figure \ref{fig:flare-diagnostics-2}).
 We also counduct a bootstrapped LRT for the null hypothesis of exponential distributed inter-arrival times and received a $p$-value of $p<0.01$.
+
+# Predicting the time of the next threshold crossing
+
+According to Figure \ref{fig:flares}, for a threshold $\ell$ at the $k$-th order 
+statistic, the fitted threshold exceedance time distribution is 
+$$
+T(\ell) \sim {\rm ML}(\beta, k^{-1/\beta} \sigma_0), 
+$$
+where $\beta = 0.85$ and $\sigma_0 = 3.0 \times 10^7 {\rm sec}$. 
+Unlike the exponential distribution, the Mittag-Leffler distribution is not memoryless, and the probability density of the time $t$ until the next threshold crossing will depend on the time $t_0$ elapsed since the last threshold crossing.
+This density equals 
+$$
+p(t|\beta, \sigma_0, \ell, t_0) = \frac{f(t + t_0 | \beta, k^{-1/\beta} \sigma_0)}{\mathbf P[T_\ell > t_0]}
+$$
+where $f(\,\cdot\, | \beta, k^{-1/\beta} \sigma_0)$ is the probability density of ${\rm ML}(\beta, k^{-1/\beta} \sigma_0)$. 
+The more time has passed without a threshold crossing, the more the probability distribution shifts towards larger values for the next crossing
+(see Figure \ref{fig:hazard}, left panel). The hazard rate 
+$$
+h(t) = \frac{f(t| \beta, k^{-1/\beta} \sigma_0))}{\int_t^\infty f(\tau| \beta, k^{-1/\beta} \sigma_0))\,d\tau}
+$$
+represents the risk of a threshold crossing per unit time, and is a decreasing function for the Mittag-Leffler distribution. 
+```{r hazard, fig.height=4, fig.cap="\\label{fig:hazard} Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\\beta = 0.8$, $\\sigma_0 = 1$).
+Right: Hazard rate depending on tail parameter $\\beta$."}
+tail <- 0.7
+scale <- 1
+t_0 <- c(0, 1, 10)
+from <- 0.1
+to <- 100 * scale
+xx <- exp(seq(from = log(from), to = log(to), length.out = 100))
+par(mfrow = c(1,2))
+df1<-data.frame(x=xx,y=rep(1, length(xx)))
+col<-c("red","blue","darkgreen","black")
+
+plot(xx, rep(1, length(xx)), ylim = c(0.001,1), type = 'n', log = 'xy', 
+     xlab = 't', ylab = 'p')
+for (k in 1:length(t_0)) {
+  cond <- pml(q = t_0[k], tail = tail, scale = scale, lower.tail = FALSE)
+  yy <- dml(x = xx + t_0[k], tail = tail, scale = scale) / cond
+  lines(xx,yy, col = col[k], lty = k+1)
+}
+legend("bottomleft", c("t_0 = 0", "t_0 = 1", "t_0 = 10"), col = c("red","blue","darkgreen"), lty = 2:4)
+
+betas <- c(0.7, 0.8, 0.95, 0.99)
+t_0 <- 1
+
+plot(xx, rep(1, length(xx)), ylim = c(0.001,2), type = 'n', log = 'xy', 
+     xlab = 't', ylab = 'h')
+for (k in 1:length(betas)) {
+  yy <- dml(x = xx, tail = betas[k], scale = scale) / pml(
+    q = xx,
+    tail = betas[k],
+    scale = scale,
+    lower.tail = FALSE
+  )
+  lines(xx,yy, col = col[k], lty = k+1)
+}
+legend("bottomleft", c("beta = 0.7", "beta = 0.8", "beta = 0.95", "beta = 0.99"), col = c("red","blue","darkgreen","black"), lty = 2:5)
+
+```
+The closer $\beta$ is to $1$, the more the hazard rate mimics that of an 
+exponential distribution (a constant function, see Figure \ref{fig:hazard}, 
+right panel).
 

### 2020-01-16 article_springer/article_springer.Rmd
Update ... submitted version

@@
 
-authors: 
+author:
+
 - name: "Katharina Hees"
-  address: TU Dortmund University
-  email: hees@statistik.tu-dortmund.de
+  affiliation: a
+  email: "hees@statistik.tu-dortmund.de"
 
 - name: "Smarak Nayak"
-  address: National Australia Bank
-  email: smarak.nayak@nab.com.au
+  affiliation: b
+  email: "smarak.nayak@nab.com.au"
 
-- name: "Peter Straka*"
-  address: UNSW Sydney
-  email: p.straka@unsw.edu.au
+- name: "Peter Straka"
+  affiliation: c
+  email: "p.straka@unsw.edu.au"
+
+address:
+
+- code: a
+  address: "Department of Statistics, TU Dortmund University, Dortmund, Germany"
+
+- code: b
+  address: "National Australia Bank, Melbourne, Australia"
+
+- code: c
+  address: "School of Mathematics and Statistics, UNSW, Sydney, Australia"
+
+corrauth:
+  name: "Katharina Hees"
+  address: "Department of Statistics, TU Dortmund University, Dortmund, Germany"
 
@@
   inter-arrival times between events such as solar flares, trades and 
-  neuron voltages follow a heavy-tailed 
-  distribution. The set of event times is fractal-like, being dense in some 
+  neuron voltages follow a heavy-tailed distribution. The set of event times is fractal-like, being dense in some 
   time windows and empty in others, a phenomenon which has been dubbed 
@@
 
-  This article proposes a new model for the _inter-exceedance times_ of thresholds;
-  the threshold exceedances are modeled via the standard 
-  Peaks-Over-Threshold (POT) method.
-  For high thresholds and 
+  This article proposes a new model for the _inter-exceedance times_ of events 
+  above high thresholds; the threshold exceedances itself are modeled via the standard 
+  Peaks-Over-Threshold (POT) method. For high thresholds and 
   infinite-mean waiting times, we show that the times between threshold 
@@
 bibliography: CTRMstats.bib
+csl: 
 output: 
@@
 # use the newest MittagLeffleR version:
-devtools::install_github("UNSW-MATH/MittagLeffleR")
+devtools::install_github("strakaps/MittagLeffleR")
 library(MittagLeffleR)
@@
 
-Time series displaying temporally inhomogeneous behaviour have received 
-strong interest in the recent statistical physics literature 
-[@Barabasi2005; @Oliveira2005; @Vasquez2006; @Vazquez2007; @Omi2011; 
-@Min2010; @Karsai2011; @Bagrow2013]. They have been observed in the context 
-of earthquakes, sunspots, neuronal activity and human communication [see 
-@Karsai2012; @Vajna2013; @MeerschaertStoev08 for a list of references]. 
+Time series displaying temporally inhomogeneous behaviour in terms of the occurrence of events have received strong interest in the recent statistical physics literature [@Barabasi2005;@Oliveira2005; @Vasquez2006; @Vazquez2007; @Omi2011; @Min2010; @Karsai2011;@Bagrow2013].
+They have been observed in the context of earthquakes, sunspots, neuronal activity and human communication [see @Karsai2012; @Vajna2013; @MeerschaertStoev08 for a list of references].
 Such time series exhibit high activity in some 'bursty' intervals, which 
@@
 the names "Continuous Time Random Maxima process" (CTRM) 
-[@Benson2007; @MeerschaertStoev08; @Hees16; @Hees17], 
+[@Benson2007; @MeerschaertStoev08; @hees2016joint; @hees2017coupled], 
 "Max-Renewal process" [@Silvestrov2002a; @ST04; @Basrak2014], 
@@
 in Section 5, but to set the stage we first discuss inference for the 
-Mittag-Leffler distribution in Section 4. In Section 6, we discuss the memory property of the 
-Mittag-Leffler distribution, and how it affects the predictive distribution 
-for the time until the next threshold crossing event.
-A simulation study of the effectiveness of our statistical procedure is given in Section 7.
-In Section 8 we apply our method to a real data set.
-Finally we close with a discussion and conclusion in Section 8.
+Mittag-Leffler distribution in Section 4.
+A simulation study of the effectiveness of our statistical procedure is given in Section 6.
+In Section 7 we apply our method to a real data set.
+In Section 8, we discuss the memory property of the  Mittag-Leffler distribution, and how it affects the predictive distribution for the time until the next threshold crossing event.
+Finally we close with a discussion and conclusion in Section 9.
 For all statistical computations we have used R [@R]. 
@@
 
-```{r thresholdedBursty, message=FALSE, fig.height=6, fig.width=7,out.width='70%',fig.align='center',fig.cap="\\label{fig:thresholdedBursty} Exceedances (red) and times until Exceedance (durations between blue crosses) for a given threshold $\\ell$ (dashed line)."}
+```{r thresholdedBursty, message=FALSE, fig.height=6, fig.width=7,out.width='70%',fig.align='center',fig.cap="\\label{fig:thresholdedBursty} Exceedances (red) and times until Exceedance (durations between blue crosses) for a given threshold $\\ell$ (dashed line).
+Upper picture: Simulated data with stable distributed waiting times.
+Lower picture: Solar flares during 1982."}
 tail <- params$tail
@@
 Figure \ref{fig:thresholdedBursty} shows a simulated dataset in the top panel, where $W$ has a stable distribution with tail parameter $\beta =$ `r params$tail` (and skewness $1$ and location $0$), and where $J$ is from a standard Gumbel distribution.
-In the bottom panel, we plot a time series of solar flare intensities derived from a NASA dataset [@HXRBS] which we will later examine more closely (see Section 8).
+In the bottom panel, we plot a time series of solar flare intensities derived from a NASA dataset [@HXRBS] which we will later examine more closely (see Section 7).
 Clearly, the simulated data exhibit long intervals
@@
 Since the Mittag-Leffler distribution is heavy-tailed, many researchers would intuitively give the highest importance to the tail behaviour of the distribution.
-Of course, one can also use established tail exponent estimators for the estimation of the parameter $\beta$ such as the Hill estimator [@hill1975simple]
+Of course, one can also use established tail exponent estimators for the estimation of the parameter $\beta$ such as the Hill estimator [@hill1975simple] based on the $r+1$ upper order statistics
 \begin{align}\label{eq:hill}
-H_{k,n}= \frac{1}{k} \sum_{i=0}^{k-1} \log \frac{X_{n-i,n}}{X_{n-k,n}}. 
+H_{r,n}=\left[ \frac{1}{r} \sum_{i=0}^{r} \log \frac{X_{(i)}}{X_{(r+1)}}\right]^{-1}, 
 \end{align}
+where $X_{(1)} \geq X_{(2)} \geq \ldots \geq X_{(n)}$ denote the order statistics in decreasing order of a sequence $X_1,\ldots,X_n$.
 However, these methods are statistically less efficient since they only use a portion of the information contained in the data, as mentioned by @kozubowski2001.
-Moreover, the hill estimator requires a tuning parameter, and only performs reliably well for distributions close to Pareto [see @Resnick97].
+Moreover, the hill estimator requires a tuning parameter, denoted with $r$ in \eqref{eq:hill}.
+Additionaly, the estimator only performs reliably well for distributions close to Pareto [see @Resnick97].
 Figure \ref{fig:Hillplots} shows Hill plots for Mittag-Leffler simulated data, with varying sample sizes and tails.
 To deduce the correct tail parameter estimates from these plots is virtually impossible.
+To estimate the tail parameter of a Mittag-Leffler distribution with the hill estimator, the sample size has to be much larger and one has to choose a large tuning parameter $r$.
+In case that only events above a high threshold are recorded, even $n=1000$ events are unrealistic.
 Furthermore the Hill estimator of course completely fails if the inter-arrival times are exponential distributed and not heavy-tailed.
+We will comeback to the problems with the hill estimtator in Section \ref{Simulationstudy}.
 
-```{r Hillplots, echo=FALSE,warning=FALSE, fig.align="center", fig.cap="\\label{fig:Hillplots} Hillplots for simulated Mittag-Leffler data with true tail 0.8 and sample size 200 (left) and 1000 (right), with number of upper order statics k on which the hill estimator is based on the x-axis.
+```{r Hillplots, echo=FALSE,warning=FALSE, fig.align="center", fig.cap="\\label{fig:Hillplots} Hillplots for simulated Mittag-Leffler data with true tail 0.8 and sample size 200 (left) and 1000 (right), with number of upper order statics r on which the hill estimator is based on the x-axis.
 ", out.width = '90%'}
@@
 load(here::here("article_springer","article_springer_files","ML_LRT_simu","estimates_df_LRT_boot1_01.RData"))
-df_LRT_boot_01 %>% filter(n=="20" || n=="50" || n=="100" || n=="200") %>% ggplot(aes(x=true.tail,y=power)) +  geom_line(aes(y=power,group=factor(n),color=factor(n),linetype=factor(n)),size=0.7)+
+df_LRT_boot_01 %>% filter(n=="20" || n=="50" || n=="100" || n=="200") %>% ggplot(aes(x=true.tail,y=power)) +  geom_line(aes(y=power,group=factor(n),color=factor(n),linetype=factor(n)),size=0.5)+
   scale_linetype_manual(values = c("solid","dashed","twodash","dotted"),name  ="Sample size")+
@@
 
-To test our inference method via stability plots, we have simulated 
-independent waiting time and magnitude pairs $(W_k, J_k)$ for waiting times that follow
+To test our inference method via stability plots, we have simulated $m=100$ times $n=10000$ independent waiting time and magnitude pairs $(W_k, J_k)$ for waiting times that follow
 
@@
 
-(iii) an Exponential distribution.
+(iii) an exponential distribution.
 
@@
 We have chosen $\beta=0.8$ in the stable as well as in the Pareto case.
-As third example we choose Exponential distributed waiting times with a rate of $1$.
+As third example we choose exponential distributed waiting times with a rate of $1$.
 Figure \ref{Fig:TailSimu} shows the stability plots for the estimation of the tail parameter.
@@
 If one would base the hill-estimation only on the inter-exceedance times, the sample size would be too small and it would be impossible to deduce an estimate for the tail parameter from the plots (compare Figure \ref{fig:Hillplots}).
-The $k$ on the $x-$axis is in the plots for the hill estimator the $k$ which defines on which orders stats the hill estimator is based on (compare \eqref{eq:hill}).
+The $k$ on the $x-$axis is in the plots for the hill estimator the $r$ which defines on which upper orders stats the hill estimator is based on (compare \eqref{eq:hill}).
 The bigger sample size results in the middle in a lower bias.
 But, one can also see, that there is much more variance between the stability plots for the different simulation runs in case of the hill estimator compared to the other two estimators.
-The black line is the mean value of the point estimators for each $k$.
+The black line is the mean value of the point estimators for each $k$ resp.
+$r$.
 However, if one wants to get a single estimate via such a stability plot, it would be much more difficult to deduce it from a hill plot compared to the other two estimators.
 In case that one has only thresholded data and hence a much smaller simple size, the hill estimator gets useless (see Section \ref{sec:ML}).
-Another advantage of the other estimators compared to the hill estimator is, that in the case one has exponential waiting times, the log-moment as well as the mle can detect this by getting an estimate round about $1$.
-The hill estimators is just a tail parameter estimator for Pareto like tails and hence of course fails in case of Exponential inter-exceedance times.
+Another advantage of the other estimators compared to the hill estimator is, that in the case one has exponential waiting times, the log-moment as well as the mle can detect this by getting an estimate close to $1$.
+The hill estimators is just a tail parameter estimator for Pareto like tails and hence of course fails in case of exponential distributed inter-exceedance times.
 Figure \ref{Fig:ScaleSimu} shows the stability plots for the different estimators for the scale parameter.
@@
 Here again both estimators show good performance.
-The stability plots in the mle case are a little bit closer to the true value, therefore, the mle is much more computational intesive.
+The stability plots in the mle case are a little bit closer to the true value, except in the exponetial case.
+Therefore, the mle is much more computational intensive.
 
-```{r TailSimuplots, message=FALSE,echo=FALSE,fig.height=7,fig.align="center",fig.cap="\\label{Fig:TailSimu} Stability Plots for m=100 simulation runs for stable distributed waiting times with a tail parameter of 0.8 (top row), Pareto distributed waiting times with tail parameter 0.8 (middle row) and Exponential distributed waiting times (lower row).
+```{r TailSimuplots, message=FALSE,echo=FALSE,fig.height=7,fig.align="center",fig.cap="\\label{Fig:TailSimu} Stability Plots for m=100 simulation runs for stable distributed waiting times with a tail parameter of 0.8 (top row), Pareto distributed waiting times with tail parameter 0.8 (middle row) and exponential distributed waiting times (lower row).
 Left column: log-moment estimator, middle column: MLE, right column: Hill estimator.
@@
   coord_cartesian(ylim = c(0.5, 1.5)) +
-  geom_line(data=means.tbl_hill_Ex1,aes(x=k, y=mw),colour="black") + ylab("Estimated tail") +  geom_hline(yintercept=0.8, linetype="dashed", color = "red")
+  geom_line(data=means.tbl_hill_Ex1,aes(x=k, y=mw),colour="black") + ylab("Estimated tail") +  geom_hline(yintercept=0.8, linetype="dashed", color = "red")+ xlab("r")
 
@@
   coord_cartesian(ylim = c(0.5, 1.5)) +
-  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_hill_times_Ex2) + ylab("Estimated tail") +  geom_hline(yintercept=0.8, linetype="dashed", color = "red")
+  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_hill_times_Ex2) + ylab("Estimated tail") +  geom_hline(yintercept=0.8, linetype="dashed", color = "red")+ xlab("r")
 
@@
   coord_cartesian(ylim = c(0.5, 10)) +
-  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_hill_times_Ex3) + ylab("Estimated tail") + geom_hline(yintercept=1, linetype="dashed", color = "red")
+  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_hill_times_Ex3) + ylab("Estimated tail") + geom_hline(yintercept=1, linetype="dashed", color = "red")+ xlab("r")
 
@@
 
-```{r ScaleSimuplots, message=FALSE,echo=FALSE,fig.height=7,fig.align="center",fig.cap="\\label{Fig:ScaleSimu} Stability Plots for m=100 simulation runs for stable distributed waiting times with a tail parameter of 0.8 (top row), Pareto distributed waiting times with tail parameter 0.8 (middle row) and Exponential distributed waiting times (lower row).
+```{r ScaleSimuplots, message=FALSE,echo=FALSE,fig.height=7,fig.align="center",fig.cap="\\label{Fig:ScaleSimu} Stability Plots for m=100 simulation runs for stable distributed waiting times with a tail parameter of 0.8 (top row), Pareto distributed waiting times with tail parameter 0.8 (middle row) and exponential distributed waiting times (lower row).
 Left column: log-moment estimator, right column: MLE.
@@
 The data were extracted from the "complete Hard X Ray Burst Spectrometer event list", a comprehensive reference for all measurements of the Hard X Ray Burst Spectrometer on NASA's Solar Maximum Mission from the time of launch on Feb 14, 1980 to the end of the mission in Dec 1989.
-12,776 events were detected, with the "vast  majority being solar flares".
+12,772 events were detected, with the "vast  majority being solar flares".
+To assure stationarity and due to missing values during the years 1983 and 1984, we based our analysis just on the year 1982, in which 2,488 events happened.
 The list includes the start time, peak time, duration, and peak rate of each event.
@@
 
-```{r flare-diagnostics-2, fig.height=4.5, fig.width=4.5, fig.align="center",fig.cap="\\label{fig:flare-diagnostics-2} Diagnostic plots for the solar flare data: empirical copula and QQ Plot.",out.width="70%"}
+```{r flare-diagnostics-2, fig.height=4.5, fig.width=4.5, fig.align="center",fig.cap="\\label{fig:flare-diagnostics-2} Diagnostic plots for the solar flare data: empirical copula.",out.width="70%"}
 empcopula(flares_ctre)
@@
 
-```{r flare-diagnostics-3, fig.height=4.5, fig.width=4.5, fig.align="center",fig.cap="\\label{fig:flare-diagnostics-3} Diagnostic plots for the solar flare data: empirical copula and QQ Plot.",out.width="70%"}
+```{r flare-diagnostics-3, fig.height=4.5, fig.width=4.5, fig.align="center",fig.cap="\\label{fig:flare-diagnostics-3} Diagnostic plots for the solar flare data: QQ Plot.",out.width="70%"}
 flares_ctre %>% interarrival() %>% mlqqplot(log = 'xy', tail = 0.85, main = "Mittag-Leffler QQ Plot")
@@
 Figure \ref{fig:flares} shows the stability plots for the solar flare data, on the left for the tail parameter and on the right for the scale parameter.
-Dotted lines show 95% confidence intervals, which are derived from the asymptotic normality of the log-moments estimators [@Cahoy2013] and the $\delta$-method [@MittagLeffleR, dashed lines show the actual values of $\beta$ resp.\ $\sigma_0$.
-The stability plot for the tail stabilizes nicely round about 0.85 (dotted line), while it is a little bit harder to deduce an estimate for the scale parameter.
-Howerever, the stability plot for the scale parameter seems to stabilize round about $3 \times 10^7$.
+Dotted lines show 95% confidence intervals, which are derived from the asymptotic normality of the log-moments estimators [@Cahoy2013] and the $\delta$-method [@MittagLeffleR], dashed lines show the deduced values of $\beta$ resp.\ $\sigma_0$.
+The stability plot for the tail stabilizes nicely round about 0.85 (dashed line), while it is a little bit harder to deduce an estimate for the scale parameter.
+Howerever, the stability plot for the scale parameter seems to stabilize round about $3 \times 10^7$ (dashed line).
 

### 2020-01-16 article_springer/article_springer.tex
Update ... submitted version

@@
-% !TeX program = pdfLaTeX
-\documentclass[smallextended]{svjour3}       % onecolumn (second format)
-%\documentclass[twocolumn]{svjour3}          % twocolumn
-%
-\smartqed  % flush right qed marks, e.g. at end of proof
-%
-\usepackage{amsmath}
-\usepackage{graphicx}
+\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
+%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
+\usepackage[hyphens]{url}
 
-\usepackage[hyphens]{url} % not crucial - just used below for the URL
-\usepackage{hyperref}
+\usepackage{lineno} % add
 \providecommand{\tightlist}{%
@@
 
-%
-% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
-%
-% insert here the call for the packages your document requires
-%\usepackage{latexsym}
-% etc.
-%
-% please place your own definitions here and don't use \def but
-% \newcommand{}{}
-%
-% Insert the name of "your journal" with
-% \journalname{myjournal}
-%
+\usepackage{graphicx}
+\usepackage{booktabs} % book-quality tables
+%%%%%%%%%%%%%%%% end my additions to header
 
-%% load any required packages here
-\usepackage{amssymb}
+\usepackage[T1]{fontenc}
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[utf8]{inputenc}
+\else % if luatex or xelatex
+  \usepackage{fontspec}
+  \ifxetex
+    \usepackage{xltxtra,xunicode}
+  \fi
+  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
+  \newcommand{\euro}{€}
+\fi
+% use microtype if available
+\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
+\bibliographystyle{elsarticle-harv}
+\ifxetex
+  \usepackage[setpagesize=false, % page size defined by xetex
+              unicode=false, % unicode breaks when used with xetex
+              xetex]{hyperref}
+\else
+  \usepackage[unicode=true]{hyperref}
+\fi
+\hypersetup{breaklinks=true,
+            bookmarks=true,
+            pdfauthor={},
+            pdftitle={Statistical Inference for inter-arrival times of extreme events in bursty time series},
+            colorlinks=false,
+            urlcolor=blue,
+            linkcolor=magenta,
+            pdfborder={0 0 0}}
+\urlstyle{same}  % don't use monospace font for urls
+
+\setcounter{secnumdepth}{5}
+% Pandoc toggle for numbering sections (defaults to be off)
+% Pandoc header
 
 \begin{document}
+\begin{frontmatter}
 
-\title{Peaks Over Threshold for Bursty Time Series \thanks{Peter Straka was supported by the Discovery Early Career Research Award
-DE160101147 on the Project ``Predicting Extremes when Events Occur in
-Bursts'' by the Australian Research Council. Katharina Hees was
-supported by the DAAD co-financed by the German Federal Ministry of
-Education and Research (BMBF).} }
+  \title{Statistical Inference for inter-arrival times of extreme events in
+bursty time series}
+    \author[a]{Katharina Hees}
+   \ead{hees@statistik.tu-dortmund.de}
 
-\author{  Katharina Hees \and  Smarak Nayak \and  Peter Straka* \and  }
+    \author[b]{Smarak Nayak}
+   \ead{smarak.nayak@nab.com.au}
 
-    \authorrunning{ K. Hees, S. Nayak \& P. Straka }
+    \author[c]{Peter Straka}
+   \ead{p.straka@unsw.edu.au}
 
-\institute{
-        Katharina Hees \at
-     University of Dortmund \\
-     \email{\href{mailto:hees@statistik.uni-dortmund.de}{\nolinkurl{hees@statistik.uni-dortmund.de}}}  %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-    \and
-        Smarak Nayak \at
-     National Australia Bank \\
-     \email{\href{mailto:smarak.nayak@nab.com.au}{\nolinkurl{smarak.nayak@nab.com.au}}}  %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-    \and
-        Peter Straka* \at
-     UNSW Sydney \\
-     \email{\href{mailto:p.straka@unsw.edu.au}{\nolinkurl{p.straka@unsw.edu.au}}}  %  \\
-%             \emph{Present address:} of F. Author  %  if needed
-    \and
-    }
-
-\date{Received: date / Accepted: date}
-% The correct dates will be entered by the editor
-
-\maketitle
+      \address[a]{Department of Statistics, TU Dortmund University, Dortmund, Germany}
+    \address[b]{National Australia Bank, Melbourne, Australia}
+    \address[c]{School of Mathematics and Statistics, UNSW, Sydney, Australia}
 
@@
 
-This article generalizes the Peaks Over Threshold (POT) model to the
-setting where inter-event times are heavy-tailed. For high thresholds
-and infinite-mean waiting times, we show that the times between
-threshold crossings are Mittag-Leffler distributed, and thus form a
-``fractional Poisson Process'' which generalizes the standard Poisson
-Process. We provide graphical means of estimating model parameters and
-assessing model fit. Along the way, we apply our inference method to a
-real-world bursty time series, and show how the memory of the
-Mittag-Leffler distribution affects the predictive distribution for the
-time until the next extreme event.
-\\
-\keywords{
-        heavy tails \and
-        renewal process \and
-        extreme value theory \and
-        peaks over threshold \and
-    }
+  This article proposes a new model for the \emph{inter-exceedance times}
+  of events above high thresholds; the threshold exceedances itself are
+  modeled via the standard Peaks-Over-Threshold (POT) method. For high
+  thresholds and infinite-mean waiting times, we show that the times
+  between threshold crossings are Mittag-Leffler distributed, and thus
+  form a ``fractional Poisson Process'' which generalizes the standard
+  Poisson Process of threshold exceedances. We provide graphical means of
+  estimating model parameters and assessing model fit. Along the way, we
+  apply our inference method to a real-world bursty time series, and show
+  how the memory of the Mittag-Leffler distribution affects the predictive
+  distribution for the time until the next extreme event.
+  \end{abstract}
+   \begin{keyword} heavy tails renewal process extreme value theory peaks over threshold\end{keyword}
+ \end{frontmatter}
 
-\end{abstract}
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
-\def\spacingset#1{\renewcommand{\baselinestretch}%
-{#1}\small\normalsize} \spacingset{1}
-
-\section{Introduction}\label{introduction}
-
-Time series displaying temporally inhomogeneous behaviour have received
-strong interest in the recent statistical physics literature (Barabási
-2005; J. Oliveira and Barabási 2005; Vasquez et al. 2006; Vazquez et al.
-2007; Omi and Shinomoto 2011; Min, Goh, and Vazquez 2011; Karsai et al.
-2011; Bagrow and Brockmann 2013). They have been observed in the context
-of earthquakes, sunspots, neuronal activity and human communication (see
-Karsai et al. 2012; Vajna, Tóth, and Kertész 2013; Mark M Meerschaert
-and Stoev 2008 for a list of references). Such time series exhibit high
-activity in some `bursty' intervals, which alternate with other, quiet
-intervals. Although several mechanisms are plausible explanations for
-bursty behaviour (most prominently self-exciting point process by Hawkes
-(1971)), there seems to be one salient feature which very typically
-indicates the departure from temporal homogeneity: a heavy-tailed
-distribution of waiting times (Vasquez et al. 2006; Karsai et al. 2012;
-Vajna, Tóth, and Kertész 2013). As we show below in simulations, a
-simple renewal process with heavy-tailed waiting times can capture this
-type of dynamics. For many systems, the renewal property is appropriate;
-a simple test of the absence of correlations in a succession of waiting
-times can be undertaken by randomly reshuffling the waiting times
-(Karsai et al. 2012).
+Time series displaying temporally inhomogeneous behaviour in terms of
+the occurrence of events have received strong interest in the recent
+statistical physics literature (Barabási 2005; Oliveira and Barabási
+2005; Vasquez et al. 2006; Vazquez et al. 2007; Omi and Shinomoto 2011;
+Min, Goh, and Vazquez 2011; Karsai et al. 2011; Bagrow and Brockmann
+2013). They have been observed in the context of earthquakes, sunspots,
+neuronal activity and human communication (see Karsai et al. 2012;
+Vajna, Tóth, and Kertész 2013; Meerschaert and Stoev 2008 for a list of
+references). Such time series exhibit high activity in some `bursty'
+intervals, which alternate with other, quiet intervals. Although several
+mechanisms are plausible explanations for bursty behaviour (most
+prominently self-exciting point process by Hawkes (1971)), there seems
+to be one salient feature which very typically indicates the departure
+from temporal homogeneity: a heavy-tailed distribution of waiting times
+(Vasquez et al. 2006; Karsai et al. 2012; Vajna, Tóth, and Kertész
+2013). As we show below in simulations, a simple renewal process with
+heavy-tailed waiting times can capture this type of dynamics. For many
+systems, the renewal property is appropriate; a simple test of the
+absence of correlations in a succession of waiting times can be
+undertaken by randomly reshuffling the waiting times (Karsai et al.
+2012).
 
@@
 process, such as for earthquakes, solar flares or neuron voltages. The
-Peaks-Over-Threshold model (POT, see e.g. Coles 2001) applies a
+Peaks-Over-Threshold model (POT, see e.g.~Coles 2001) applies a
 threshold to the magnitudes, and fits a Generalized Pareto distribution
@@
 is that times between events are either fixed or light-tailed, and this
-entails that the threshold crossing times form a Poisson process (Hsing,
-Hüsler, and Leadbetter 1988). Then as one increases the threshold and
-thus decreases the threshold crossing probability \(p\), the Poisson
-process is rarefied, i.e.~its intensity decreases \emph{linearly} with
-\(p\) (see e.g. Beirlant et al. 2006).
+entails that the threshold crossing times form a Poisson process (``On
+the Exceedance Point Process for a Stationary Sequence'' 1988). Then as
+one increases the threshold and thus decreases the threshold crossing
+probability \(p\), the Poisson process is rarefied, i.e.~its intensity
+decreases \emph{linearly} with \(p\) (see e.g.~Beirlant et al. 2006).
 
@@
 threshold crossing times form a \emph{fractional Poisson process}
-(Laskin 2003; Mark M Meerschaert, Nane, and Vellaisamy 2011), which is a
+(Laskin 2003; Meerschaert, Nane, and Vellaisamy 2011), which is a
 renewal process with Mittag-Leffler distributed waiting times. The
@@
 ``Continuous Time Random Maxima process'' (CTRM) (Benson, Schumer, and
-Meerschaert 2007; Mark M Meerschaert and Stoev 2008; Hees and Scheffler
-2016; Hees and Scheffler 2017), ``Max-Renewal process'' (Silvestrov
-2002; Silvestrov and Teugels 2004; Basrak and Špoljarić 2015), and
-``Shock process'' (Esary and Marshall 1973; Shanthikumar and Sumita
-1983; Shanthikumar and Sumita 1984; Shanthikumar and Sumita 1985;
-Anderson 1987; Gut and Hüsler 1999). The existing literature focuses on
-probabilistic results surrounding these models. In this work, however,
-we introduce a method of inference for this type of model, which is
-seemingly not available in the literature.
+Meerschaert 2007; Meerschaert and Stoev 2008; Hees and Scheffler 2018b,
+2018a), ``Max-Renewal process'' (Silvestrov 2002; Silvestrov and Teugels
+2004; Basrak and Špoljarić 2015), and ``Shock process'' (Esary and
+Marshall 1973; Shanthikumar and Sumita 1983, 1984, 1985; Anderson 1987;
+Gut and Hüsler 1999). The existing literature focuses on probabilistic
+results surrounding these models. In this work, however, we introduce a
+method of inference for this type of model, which is seemingly not
+available in the literature.
 
@@
 in Section 5, but to set the stage we first discuss inference for the
-Mittag-Leffler distribution in Section 4. (A simulation study of the
-effectiveness of our statistical procedure is given in the appendix.)
-Diagnostic plots for model criticism are discussed in Section 6. In
-Section 7, we discuss the memory property of the Mittag-Leffler
-distribution, and how it affects the predictive distribution for the
-time until the next threshold crossing event. Section 8 concludes. For
-all statistical computations we have used R (R Core Team 2018). All code
-and data used for the analysis in this article has been organized into
-an R package \texttt{CTRE} (\url{https://github.com/UNSW-MATH/CTRE}).
-The source code for the figures generated in this manuscript is
-available online at \url{https://github.com/UNSW-MATH/bursty-POT}.
+Mittag-Leffler distribution in Section 4. A simulation study of the
+effectiveness of our statistical procedure is given in Section 6. In
+Section 7 we apply our method to a real data set. In Section 8, we
+discuss the memory property of the Mittag-Leffler distribution, and how
+it affects the predictive distribution for the time until the next
+threshold crossing event. Finally we close with a discussion and
+conclusion in Section 9. For all statistical computations we have used R
+(R Core Team 2018). All code and data used for the analysis in this
+article has been organized into an R package \texttt{CTRE}
+(\url{https://github.com/strakaps/CTRE}). The source code for the
+figures generated in this manuscript is available online at
+\url{https://github.com/strakaps/bursty-POT}.
 
+\hypertarget{continuous-time-random-exceedances-ctre}{%
 \section{Continuous Time Random Exceedances
-(CTRE)}\label{continuous-time-random-exceedances-ctre}
+(CTRE)}\label{continuous-time-random-exceedances-ctre}}
 
@@
 and \(J\) are independent, the Marked Renewal Process is said to be
-\emph{uncoupled}. \qed
+\emph{uncoupled}.
 \end{description}
 
-Note that the \(k\)-th magnitude \(J_k\) occurs at time
+We assume that the \(k\)-th magnitude \(J_k\) occurs at time
 \(T_k = W_1 + \ldots + W_k\). Based on an MRP, we define the Continuous
@@
 \(T(\ell,n)\) and \(X(\ell, n)\), \(n \in \mathbb N\), called the
-``interarrival times'' and the ``exceedances'', respectively. The pair
+``inter-arrival times'' and the ``exceedances'', respectively. The pair
 sequence \((T(\ell, n), W(\ell, n))_{n \in \mathbb N}\) is called a
 Continuous Time Random Exceedance model (CTRE). If the underlying MRP is
-uncoupled, then the CTRE is also called uncoupled. \qed
+uncoupled, then the CTRE is also called uncoupled.
 \end{description}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{article_springer_files/figure-latex/thresholdedBursty-1} \caption{\label{fig:thresholdedBursty}Exceedances (red) and Times until Exceedance (durations between blue crosses) for a given threshold $\ell$ (dashed line).}\label{fig:thresholdedBursty}
+
+{\centering \includegraphics[width=0.7\linewidth]{article_springer_files/figure-latex/thresholdedBursty-1}
+
+}
+
+\caption{\label{fig:thresholdedBursty} Exceedances (red) and times until Exceedance (durations between blue crosses) for a given threshold $\ell$ (dashed line).
+Upper picture: Simulated data with stable distributed waiting times.
+Lower picture: Solar flares during 1982.}\label{fig:thresholdedBursty}
 \end{figure}
 
-In this article, we restrict ourselves to the uncoupled case, where the
-two sequences \(X(\ell, n)_{n \in \mathbb N}\) and
-\(T(\ell, n)_{n \in \mathbb N}\) are independent.\footnote{To see why,
-  note that \(X(\ell)\) is, in distribution, simply equal to
-  \(J | J > \ell\), independent of any waiting time \(W_k\).} Figure
-\ref{fig:thresholdedBursty} shows a simulated dataset in the top panel,
-where \(W\) has a stable distribution with tail parameter \(\beta =\)
-0.8 (and skewness \(1\) and location \(0\)), and where \(J\) is from a
-standard Gumbel distribution. In the bottom panel, we plot a time series
-of solar flare intensities derived from a NASA dataset (Dennis et al.
-1991)\footnote{The ``complete Hard X Ray Burst Spectrometer event list''
-  is a comprehensive reference for all measurements of the Hard X Ray
-  Burst Spectrometer on NASA's Solar Maximum Mission from the time of
-  launch on Feb 14, 1980 to the end of the mission in Dec 1989. 12,776
-  events were detected, with the ``vast majority being solar flares''.
-  The list includes the start time, peak time, duration, and peak rate
-  of each event. We have used ``start time'' as the variable for event
-  times, and ``peak rate'' as the variable for event magnitudes.}.
-Clearly, the simulated data exhibit long intervals \emph{without any}
-events, whereas in the real-world dataset events appear continuously.
-The threshold exceedances, however, appear to have similar statistical
-behaviour in both models. Observations below a threshold are commonly
-discarded in Extreme Value Theory (POT approach); likewise, the CTRE
-model interprets these observations as noise and filters them out.
+In this article, we restrict ourselves to the uncoupled case, where
+\(W\) and \(J\) are independent. Then the two sequences
+\(X(\ell, n)_{n \in \mathbb N}\) and \(T(\ell, n)_{n \in \mathbb N}\)
+are independent as well. To see why, note that \(X(\ell)\) is, in
+distribution, simply equal to \(J | J > \ell\), independent of any
+waiting time \(W_k\).\\
+Figure \ref{fig:thresholdedBursty} shows a simulated dataset in the top
+panel, where \(W\) has a stable distribution with tail parameter
+\(\beta =\) 0.8 (and skewness \(1\) and location \(0\)), and where \(J\)
+is from a standard Gumbel distribution. In the bottom panel, we plot a
+time series of solar flare intensities derived from a NASA dataset
+(Dennis et al. 1991) which we will later examine more closely (see
+Section 7). Clearly, the simulated data exhibit long intervals
+\emph{without any} events, whereas in the real-world dataset events
+appear continuously. The threshold exceedances, however, appear to have
+visually similar statistical behaviour in both models. Observations
+below a threshold are commonly discarded in Extreme Value Theory (POT
+approach); likewise, the CTRE model interprets these observations as
+noise and discards them.
 
-\section{Scaling limit of Exceedance Times}\label{sec:scaling}
+\hypertarget{sec:scaling}{%
+\section{Scaling limit of Exceedance Times}\label{sec:scaling}}
 
@@
 \begin{description}
-\tightlist
 \item[\textbf{Theorem:}]
@@
 positively skewed sum-stable law with stability parameter
-\(0 < \beta < 1\); more precisely,
-
-\begin{align} \label{eq:stability}
+\(0 < \beta < 1\); more precisely, \begin{align} \label{eq:stability}
 \frac{W_1 + \ldots + W_n}{b(n)} \overset{d}{\longrightarrow} D, 
 \quad n \to \infty
-\end{align}
-
-for a function \(b(n)\) which is regularly varying at \(\infty\) with
-parameter \(1/\beta\), and where
+\end{align} for a function \(b(n)\) which is regularly varying at
+\(\infty\) with parameter \(1/\beta\), and where
 \(\mathbf E[\exp(-sD)] = \exp(-s^\beta)\). Write
@@
 \mathbf E[\exp(-sW_\beta)] = \frac{1}{1+s^\beta}.
-\] \qed
+\]
 \end{description}
 
-\noindent For a scale parameter \(\sigma > 0\), we write
-\({\rm ML}(\beta, \sigma)\) for the distribution of \(\sigma W_\beta\).
-The Mittag-Leffler distribution with parameter \(\beta \in (0,1]\) is a
-heavy-tailed positive distribution for \(\beta < 1\), with infinite
-mean. However, as \(\beta \uparrow 1\), \({\rm ML}(\beta, \sigma)\)
-converges weakly to the exponential distribution \({\rm Exp}(\sigma)\).
-This means that although its moments are all infinite, the
-Mittag-Leffler distribution may (if \(\beta\) is close to 1) be
-indistinguishable from the exponential distribution, for the purposes of
-applied statistics. For a detailed reference on the Mittag-Leffler
-distribution, see e.g. Haubold, Mathai, and Saxena (2011), and for
-algorithms, see e.g.~the R package \texttt{MittagLeffleR} (Gill and
-Straka 2017).
-
-\paragraph{\texorpdfstring{\emph{Proof of
-Theorem:}}{Proof of Theorem:}}\label{proof-of-theorem}
-
-We interpret the threshold crossing time \(T(\ell)\) as the hitting time
-of the underlying CTRM (Continuous Time Random Maxima) or ``max-renewal
-process'', and then utilize a result by Mark M Meerschaert and Stoev
-(2008). The running maximum process is defined as \[
+\emph{Proof of Theorem:} We interpret the threshold crossing time
+\(T(\ell)\) as the hitting time of the underlying CTRM (Continuous Time
+Random Maxima) or ``max-renewal process'', and then utilize a result by
+Meerschaert and Stoev (2008). The running maximum process is defined as
+\[
 M(c) := J_1 \vee \ldots \vee J_{\lfloor c \rfloor},
@@
 T(\ell) > t \quad \text{ if and only if } \quad V(t) \le \ell.
-\] By (Theorem 3.1, Mark M Meerschaert and Stoev 2008), we have the
-stochastic process convergence \[
+\] By (Theorem 3.1, Meerschaert and Stoev 2008), we have the stochastic
+process convergence \[
 \frac{V(ct) - d(\tilde b(c))}{a(\tilde b(c))} 
@@
 = \mathbf P[(-\log F(\ell^*))^{-1/\beta} X^{1/\beta} D > t]
-\] by (Proposition 4.2, Mark M Meerschaert and Stoev 2008), where \(X\)
-is an exponential random variable with mean \(1\). Using (Theorem 19.1,
+\] by (Proposition 4.2, Meerschaert and Stoev 2008), where \(X\) is an
+exponential random variable with mean \(1\). Using (Theorem 19.1,
 Haubold, Mathai, and Saxena 2011), we see that
@@
 
+For a scale parameter \(\sigma > 0\), we write
+\({\rm ML}(\beta, \sigma)\) for the distribution of \(\sigma W_\beta\).
+The Mittag-Leffler distribution with parameter \(\beta \in (0,1]\) is a
+heavy-tailed positive distribution for \(\beta < 1\), with infinite
+mean. However, as \(\beta \uparrow 1\), \({\rm ML}(\beta, \sigma)\)
+converges weakly to the exponential distribution \({\rm Exp}(\sigma)\)
+with mean \(\sigma\). This means that although its moments are all
+infinite, the Mittag-Leffler distribution may (if \(\beta\) is close to
+1) be indistinguishable from the exponential distribution, for the
+purposes of applied statistics. For a detailed reference on the
+Mittag-Leffler distribution, see e.g.~ Haubold, Mathai, and Saxena
+(2011), and for algorithms, see e.g.~the R package
+\texttt{MittagLeffleR} (Gill and Straka 2017).
+
 \begin{description}
-\tightlist
 \item[\textbf{Remark:}]
-If \(\beta = 1\), the result of the Theorem above is standard, see e.g.
-Equation (2.2) in Gut and Hüsler (1999).
+If \(\beta = 1\), the result of the Theorem above is standard, see e.g.~
+Equation (2.2) in Gut and Hüsler (1999). In Anderson (1987) a similar
+result is shown with a different choice of scaling constant.
 \end{description}
 
-\section{Inference for the Mittag-Leffler
-distribution}\label{inference-for-the-mittag-leffler-distribution}
+\hypertarget{sec:ML}{%
+\section{Model Choice and inference for the Mittag-Leffler
+distribution}\label{sec:ML}}
+
+The classical POT approach is based on the fact that exceedances above a
+high threshhold are asymptotically GPD distributed, hence a GPD
+distribution is fitted to the exceedances above a high enough
+threshhold. Due to the Theorem in the last Section we know that for high
+thresholds the times between exceedances are asymptotically
+Mittag-Leffler distributed in case of heavy-tailed waiting times between
+the observations. Hence, before we talk about inference for the
+exceedances in the next section, we discuss inference for Mittag-Leffler
+distributions.
+
+Historically, the first method proposed for the estimation of the
+Mittag-Leffler distribution parameters was the fractional moment
+estimator by Kozubowski (2001). Unlike the first moments, the fractional
+moments of order \(p\) for \(p<\beta\) exist and are tractable. One
+drawback of this method is that constant priors for the tail parameter
+are needed for the calculation of the estimates. Cahoy, Uchaikin, and
+Woyczynski (2010) proposed a moment estimator of the log-transformed
+data, which does not require any prior. Furthermore, they performed
+simulation studies illustrating that the log-moment outperforms the
+fractional moment estimator with respect to bias and root mean squared
+error (RMSE).
+
+Due to the form of the density function of a Mittag-Leffler distribution
+there exists no closed form for the Maximum Likelihood estimator (MLE).
+In the R Package \texttt{MittagLeffleR} (Gill and Straka 2017), Maximum
+Likelihood estimation is implemented via numerical optimization. The MLE
+slightly outperforms the log-moment estimator regarding bias and RMSE
+for big enough sample sizes, but is extremely computational intensive.
+Figure \ref{fig:MSE} shows that both estimators perform well, even for
+small sample sizes.
 
 \begin{figure}
-\includegraphics[width=\textwidth]{article_springer_files/figure-latex/QQ-plots-1} \caption{Pareto vs.
-Mittag-Leffler distribution, both with same tail exponent 0.8.
-Top row: solar flare magnitudes data, fitting nicely with a Pareto distribution.
-Bottom row: simulated Mittag-Leffler data.
-Left column: static QQ-Estimator plots, assessing a fit against the Pareto distribution.
-Centre column: dynamic QQ-Estimator plots.
-Right column: a usual QQ-Plot based on Mittag-Leffler quantiles.\label{fig:QQ-plots}}\label{fig:QQ-plots}
+
+{\centering \includegraphics[width=0.9\linewidth]{article_springer_files/figure-latex/MSE-1}
+
+}
+
+\caption{\label{fig:MSE} MSE for the estimation of tail (left column) and scale (right column) parameters via log-moment estimator and mle of a Mittag-Leffler sample with varying sample size n=25, 100, 200, varying tails on the x-axis and fixed scale equal to one.}\label{fig:MSE}
 \end{figure}
@@
 would intuitively give the highest importance to the tail behaviour of
-the distribution, and estimate the exponent of the tail function with
-established methods such as the Hill estimator. The QQ-estimator (Kratz
-and Resnick 1996) is closely related to the Hill estimator and fits a
-least squares line through the logarithms of the ordered statistics
-(y-axis) and the corresponding quantiles of the exponential distribution
-(x-axis). The reciprocal slope is returned as the estimate of the tail
-exponent. For instance, the top-left panel in Figure \ref{fig:QQ-plots}
-shows the (static) QQ-estimator for the magnitudes of the solar flare
-data, returning a good fit to a Pareto distribution with tail parameter
-0.79. The dynamic QQ-estimator plot (top-center panel) plots the tail
-exponent estimate for the largest values at cutoffs varying up to the
-5th order statistic, and the region of stability at 0.8 indicates a
-recommended estimate.
-
-However, as described nicely by Resnick (1997), the less similar a
-heavy-tailed distribution is to a Pareto distribution, the less useful a
-Hill or QQ-Plot estimator becomes. The bottom-left panel of Figure
-\ref{fig:QQ-plots}, for instance, shows the static QQ-estimator plot for
-\(2000\) draws from the Mittag-Leffler distribution with tail parameter
-\(0.8\). The stretched exponential shape means that the Mittag-Leffler
-distribution has more probability near \(0\) than the Pareto
-distribution, severely biasing the estimator downwards (0.67). Even by
-looking at different cutoffs via the dynamic QQ-estimator plot
-(bottom-center panel) one hardly identifies \(0.8\) as a clear candidate
-for a tail parameter estimate.
-
-QQ-estimators, and the closely related Hill estimator, are hence not
-suitable to detect a heavy-tailed Mittag-Leffler distribution. Moreover,
-QQ-estimator plots of exponentially distributed data are virtually
-indistinguishable from the bottom-left panel. This shows that
-\emph{Mittag-Leffler distributed data may look like exponentially
-distributed data if examined via a QQ-estimator}.
-
-Hence if there is some prior expectation that the data are drawn from
-the Mittag-Leffler distribution (as is the the case for threshold
-exceedance times), then we recommend avoiding QQ-estimators and Hill
-plots altogether, and instead examining QQ-plots directly, on a
-logarithmic scale (see Figure \ref{fig:QQ-plots}, right column). The
-scale parameter \(\sigma\) is irrelevant for a QQ-Plot. The tail
-parameter \(\beta\) can be estimated quickly via the log-moment method
-by Cahoy (2013), or via maximum likelihood. Both estimators are
-implemented in \texttt{MittagLeffleR} (Gill and Straka 2017). Since the
-exponential distribution is nested in the Mittag-Leffler family of
-distributions, a standard likelihood ratio test can be performed, with
-the exponential distribution as a null model against a Mittag-Leffler
-distribution as the alternative. As an example, the threshold crossing
-times for the solar flare dataset (Figure \ref{fig:flare-diagnostics-2},
-right panel) yield a difference in deviance of \(\approx\) 324, which
-evaluates to a strongly significant \(\chi^2_1\) test statistic (p-value
-= \(10^{-72}\)) for the null hypothesis \(\beta = 1\).
-
-\section{Inference on Exceedance
-times}\label{inference-on-exceedance-times}
+the distribution. Of course, one can also use established tail exponent
+estimators for the estimation of the parameter \(\beta\) such as the
+Hill estimator (Hill 1975) based on the \(r+1\) upper order statistics
+\begin{align}\label{eq:hill}
+H_{r,n}=\left[ \frac{1}{r} \sum_{i=0}^{r} \log \frac{X_{(i)}}{X_{(r+1)}}\right]^{-1}, 
+\end{align} where \(X_{(1)} \geq X_{(2)} \geq \ldots \geq X_{(n)}\)
+denote the order statistics in decreasing order of a sequence
+\(X_1,\ldots,X_n\). However, these methods are statistically less
+efficient since they only use a portion of the information contained in
+the data, as mentioned by Kozubowski (2001). Moreover, the hill
+estimator requires a tuning parameter, denoted with \(r\) in
+\eqref{eq:hill}. Additionaly, the estimator only performs reliably well
+for distributions close to Pareto (see Resnick 1997). Figure
+\ref{fig:Hillplots} shows Hill plots for Mittag-Leffler simulated data,
+with varying sample sizes and tails. To deduce the correct tail
+parameter estimates from these plots is virtually impossible. To
+estimate the tail parameter of a Mittag-Leffler distribution with the
+hill estimator, the sample size has to be much larger and one has to
+choose a large tuning parameter \(r\). In case that only events above a
+high threshold are recorded, even \(n=1000\) events are unrealistic.
+Furthermore the Hill estimator of course completely fails if the
+inter-arrival times are exponential distributed and not heavy-tailed. We
+will comeback to the problems with the hill estimtator in Section
+\ref{Simulationstudy}.
 
 \begin{figure}
-\includegraphics[width=\textwidth]{article_springer_files/figure-latex/solar-flare-tail-scale-1} \caption{\label{fig:flares}Stability plots for the tail and scale parameter of the Mittag-Leffler distribution of the Solar Flare dataset.
-Dotted horizontal lines are at $\beta = 0.85$ and $\sigma_0 = 3 \times 10^7$ seconds $\approx 0.95$ years.}\label{fig:solar-flare-tail-scale}
+
+{\centering \includegraphics[width=0.9\linewidth]{article_springer_files/figure-latex/Hillplots-1}
+
+}
+
+\caption{\label{fig:Hillplots} Hillplots for simulated Mittag-Leffler data with true tail 0.8 and sample size 200 (left) and 1000 (right), with number of upper order statics r on which the hill estimator is based on the x-axis.
+}\label{fig:Hillplots}
 \end{figure}
+
+Since the exponential distribution is nested in the Mittag-Leffler
+family of distributions, a Likelihood-ratio Test (LRT) seems to be an
+appropriate way to choose between a model with exponential and
+Mittag-Leffler inter-exceedance times. Although the two models are
+nested, the asymptotic distribution is not \(\chi^2_1\)-distributed, and
+Wilk's Theorem does not hold: under \(H_0\), the parameter \(\beta\) of
+Mittag-Leffler distribution is equal to \(1\), and hence lies on the
+boundary of the parameter space \((0,1]\). Instead, a valid approach is
+a bootstrapped Likelihood-ratio test (see e.g.~Davison, Hinkley, and
+others 1997). Figure \ref{Fig:LRT} displays the (simulated) power for
+the bootstrapped LRT for Mittag-Leffler distributions with varying tail
+parameters based on 1000 simulation runs. As expected, the power
+decreases for tail parameters close to one, since the Mittag-Leffler
+distribution converges as \(\beta \uparrow 1\) to an exponential
+distribution; it becomes hard to differentiate a Mittag-Lefller
+distribution from an exponential.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.9\linewidth]{article_springer_files/figure-latex/LRT_power-1}
+
+}
+
+\caption{\label{Fig:LRT} Power for bootstrapped LRT for different sample sizes , varying tails and scale parameter equal to 1.}\label{fig:LRT_power}
+\end{figure}
+
+\hypertarget{inference-on-exceedance-times}{%
+\section{Inference on Exceedance
+times}\label{inference-on-exceedance-times}}
 
@@
 threshold \(\ell\) we may approximate the distribution of \(T(\ell)\)
-with an \({\rm ML}(\beta, b(1/p))\) distribution, where \(b(\,)\) varies
-regularly at \(\infty\) with parameter \(1/\beta\). Building on the POT
-(Peaks Over Threshold) method, we propose the following estimation
-procedure for the distribution of \(T(\ell)\):
+with an \({\rm ML}(\beta, b(1/p))\) distribution, where the function
+\(b(c)\) varies regularly at \(\infty\) with parameter \(1/\beta\).
+Building on the POT (Peaks-Over-Threshold) method, we propose the
+following estimation procedure for the distribution of inter-exceedance
+time \(T(\ell)\):
 
@@
 
-The above approach, though theoretically sound, benefits from the
-following practical adjustments (compare with Figure \ref{fig:flares}):
+The above approach benefits from the following practical adjustments
+(compare with Figure \ref{fig:flares}):
 
 \begin{itemize}
-\tightlist
 \item
-  We choose \(\ell\) from the order statistics, i.e. \(\ell\) is the
+  We choose \(\ell\) from the order statistics, i.e.~\(\ell\) is the
   \(k\)-th largest of the observations \(X_j\), where \(k\) runs from
@@
 the distribution of exceedance times, dependent on the threshold
-\(\ell\):
+\(\ell\): \begin{align*}
+T(\ell) \sim {\rm ML}(\hat \beta, k^{-1/\hat \beta} \hat \sigma_0),
+\end{align*} where \(\ell\) equals the \(k\)-th order statistic. For
+quick estimates of the Mittag-Leffler parameters we have used the method
+of log-transformed moments (Cahoy 2013). We have verified the validity
+of our estimation algorithm via simulations, see Section
+\ref{Simulationstudy}.
 
-\begin{align*}
-T(\ell) \sim {\rm ML}(\hat \beta, k^{-1/\hat \beta} \hat \sigma_0).
-\end{align*}
+\hypertarget{Simulationstudy}{%
+\section{Simulation study}\label{Simulationstudy}}
 
-For quick estimates of the Mittag-Leffler parameters we have used the
-method of log-transformed moments by Cahoy (2013). We have verified the
-validity of our estimation algorithm via simulations, see the appendix.
+To test our inference method via stability plots, we have simulated
+\(m=100\) times \(n=10000\) independent waiting time and magnitude pairs
+\((W_k, J_k)\) for waiting times that follow
 
-\section{Checking Model Assumptions}\label{checking-model-assumptions}
+\begin{enumerate}
+\def\labelenumi{(\roman{enumi})}
+\item
+  a stable distribution,
+\item
+  a Pareto distribution and
+\item
+  an exponential distribution.
+\end{enumerate}
+
+In order to have exact analytical values available for \(\beta\) and
+\(\sigma_0\), a distribution for \(W_k\) needs to be chosen for which
+\(b(n)\) from \eqref{eq:stability} is known. For (i) we choose
+\(W_k \stackrel{d}{=} D\), where \(D\) is as in \eqref{eq:stability},
+then due to the stability property we have the \emph{equality} of
+distribution \(W_1 + \ldots + W_n \stackrel{d}{=} b(n) D\), for
+\(b(n) = n^{1/\beta}\). Using the parametrisation of Samorodnitsky and
+Taqqu (1994), a few lines of calculation (see e.g.~the vignette on
+parametrisation in Gill and Straka 2017) show that \(D\) must have the
+stable distribution \(S_\beta(\cos(\pi \beta/2)^{1/\beta}, +1, 0)\),
+which is implemented in the R package \texttt{stabledist} by Wuertz,
+Maechler, and members. (2016). By the Theorem, the distribution of
+\(T(\ell)\) is approximately \[
+{\rm ML}(\beta, p^{-1/\beta}) 
+= {\rm ML}(\beta, k^{-1/\beta} n^{1/\beta}),
+\] which means \(\sigma_0 = n^{1/\beta}\). In the Pareto example we
+choose \(P(W>t)=Ct^{-\beta}\) with \(C=(1/\Gamma(1-\beta))^{1/\beta}\).
+We have chosen \(\beta=0.8\) in the stable as well as in the Pareto
+case. As third example we choose exponential distributed waiting times
+with a rate of \(1\). Figure \ref{Fig:TailSimu} shows the stability
+plots for the estimation of the tail parameter. Therefore,
+\(\hat \beta(k)\) vs.~\(k\) is plotted for each of the \(m=100\)
+simulation runs (grey thin lines). In the left column one can see the
+estimates based on the log-moment estimator, the stability plots in the
+middle are based on the maximum-likelihood estimator and on the right
+hand on the hill estimator. Recall that \(k\) is the index of the order
+statistics of \(J_k\) at which the threshold \(\ell\) is placed. Note,
+that the hill estimator is here based on the waiting times, not on the
+inter-exceedance times, hence the estimation is based on much more data.
+If one would base the hill-estimation only on the inter-exceedance
+times, the sample size would be too small and it would be impossible to
+deduce an estimate for the tail parameter from the plots (compare Figure
+\ref{fig:Hillplots}). The \(k\) on the \(x-\)axis is in the plots for
+the hill estimator the \(r\) which defines on which upper orders stats
+the hill estimator is based on (compare \eqref{eq:hill}). The bigger
+sample size results in the middle in a lower bias. But, one can also
+see, that there is much more variance between the stability plots for
+the different simulation runs in case of the hill estimator compared to
+the other two estimators. The black line is the mean value of the point
+estimators for each \(k\) resp. \(r\). However, if one wants to get a
+single estimate via such a stability plot, it would be much more
+difficult to deduce it from a hill plot compared to the other two
+estimators. In case that one has only thresholded data and hence a much
+smaller simple size, the hill estimator gets useless (see Section
+\ref{sec:ML}). Another advantage of the other estimators compared to the
+hill estimator is, that in the case one has exponential waiting times,
+the log-moment as well as the mle can detect this by getting an estimate
+close to \(1\). The hill estimators is just a tail parameter estimator
+for Pareto like tails and hence of course fails in case of exponential
+distributed inter-exceedance times. Figure \ref{Fig:ScaleSimu} shows the
+stability plots for the different estimators for the scale parameter.
+Here of course only for the log-moment (on the right hand) and the mle
+(on the left hand), since the hill estimator is just a tail parameter
+estimate. Here again both estimators show good performance. The
+stability plots in the mle case are a little bit closer to the true
+value, except in the exponetial case. Therefore, the mle is much more
+computational intensive.
 
 \begin{figure}
-\includegraphics[width=\textwidth]{article_springer_files/figure-latex/flare-diagnostics-1-1} \caption{Diagnostic plots for the solar flare data: auto-correlation function.\label{fig:flare-diagnostics-1}}\label{fig:flare-diagnostics-1}
+
+{\centering \includegraphics[width=1\linewidth]{article_springer_files/figure-latex/TailSimuplots-1}
+
+}
+
+\caption{\label{Fig:TailSimu} Stability Plots for m=100 simulation runs for stable distributed waiting times with a tail parameter of 0.8 (top row), Pareto distributed waiting times with tail parameter 0.8 (middle row) and exponential distributed waiting times (lower row).
+Left column: log-moment estimator, middle column: MLE, right column: Hill estimator.
+The grey thin lines are the stability plots for the different simulation runs and the dark lines are their means.
+The red dotted line shows the true tail parameter.
+}\label{fig:TailSimuplots}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{article_springer_files/figure-latex/flare-diagnostics-2-1} \caption{Diagnostic plots for the solar flare data: empirical copula and QQ Plot.
-\label{fig:flare-diagnostics-2}}\label{fig:flare-diagnostics-2}
+
+{\centering \includegraphics[width=0.9\linewidth]{article_springer_files/figure-latex/ScaleSimuplots-1}
+
+}
+
+\caption{\label{Fig:ScaleSimu} Stability Plots for m=100 simulation runs for stable distributed waiting times with a tail parameter of 0.8 (top row), Pareto distributed waiting times with tail parameter 0.8 (middle row) and exponential distributed waiting times (lower row).
+Left column: log-moment estimator, right column: MLE.
+The grey thin lines are the stability plots for the different simulation runs and the dark lines are their means.
+The red dotted line shows the true tail parameter.}\label{fig:ScaleSimuplots}
 \end{figure}
 
-The CTRE model is based on three main assumptions, which are repeated
-below. For each assumption, we suggest one means of checking if it
-holds:
+\hypertarget{data-example}{%
+\section{Data example}\label{data-example}}
+
+We now want to apply the proposed method to a real data example, the
+solar flare data which was already mentioned in Section 1 and can be
+seen in Figure \ref{fig:thresholdedBursty}. The data were extracted from
+the ``complete Hard X Ray Burst Spectrometer event list'', a
+comprehensive reference for all measurements of the Hard X Ray Burst
+Spectrometer on NASA's Solar Maximum Mission from the time of launch on
+Feb 14, 1980 to the end of the mission in Dec 1989. 12,772 events were
+detected, with the ``vast majority being solar flares''. To assure
+stationarity and due to missing values during the years 1983 and 1984,
+we based our analysis just on the year 1982, in which 2,488 events
+happened. The list includes the start time, peak time, duration, and
+peak rate of each event. We have used ``start time'' as the variable for
+event times, and ``peak rate'' as the variable for event magnitudes.
+
+Before we apply the POT approach described in Section 5 to the solar
+flare data, we first have to check if all model assumptions are
+full-filled. The CTRE model is based on three main assumptions, which
+are repeated below. For each assumption, we suggest one means of
+checking if it holds:
 
 \begin{description}
-\tightlist
 \item[i.i.d.:]
@@
 crossing times, and create a QQ Plot for the Mittag-Leffler
-distribution. Use a log-Moment estimate of the tail parameter for the
+distribution. Use a log-moment estimate of the tail parameter for the
 theoretical / population quantiles of the plot.
@@
 
-Figures \ref{fig:flare-diagnostics-1} and \ref{fig:flare-diagnostics-2}
-show the diagnostic plots for a minimum threshold chosen at the 200th
-order statistic. There is some residual autocorrelation for the sequence
-of threshold exceedance times that is not accounted for by the CTRE
-model. The fit with a Mittag-Leffler distribution (\(\beta = 0.8\)) is
-good, though there are signs that the power-law tail tapers off for very
-large inter-threshold crossing times. There is no apparent dependence
-between threshold exceedance times and event magnitudes seen in the
-copula plot.
+Figures \ref{fig:flare-diagnostics-1}, \ref{fig:flare-diagnostics-2} and
+\ref{fig:flare-diagnostics-3} show the diagnostic plots for a minimum
+threshold chosen at the 200th order statistic. There is some residual
+autocorrelation for the sequence of threshold exceedance times that is
+not accounted for by the CTRE model.
 
+\begin{figure}
+\includegraphics[width=\textwidth]{article_springer_files/figure-latex/flare-diagnostics-1-1} \caption{\label{fig:flare-diagnostics-1} Diagnostic plots for the solar flare data: auto-correlation function.}\label{fig:flare-diagnostics-1}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.7\linewidth]{article_springer_files/figure-latex/flare-diagnostics-2-1}
+
+}
+
+\caption{\label{fig:flare-diagnostics-2} Diagnostic plots for the solar flare data: empirical copula.}\label{fig:flare-diagnostics-2}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.7\linewidth]{article_springer_files/figure-latex/flare-diagnostics-3-1}
+
+}
+
+\caption{\label{fig:flare-diagnostics-3} Diagnostic plots for the solar flare data: QQ Plot.}\label{fig:flare-diagnostics-3}
+\end{figure}
+
+Figure \ref{fig:flares} shows the stability plots for the solar flare
+data, on the left for the tail parameter and on the right for the scale
+parameter. Dotted lines show 95\% confidence intervals, which are
+derived from the asymptotic normality of the log-moments estimators
+(Cahoy 2013) and the \(\delta\)-method (Gill and Straka 2017), dashed
+lines show the deduced values of \(\beta\) resp.~\(\sigma_0\). The
+stability plot for the tail stabilizes nicely round about 0.85 (dashed
+line), while it is a little bit harder to deduce an estimate for the
+scale parameter. Howerever, the stability plot for the scale parameter
+seems to stabilize round about \(3 \times 10^7\) (dashed line).
+
+\begin{figure}
+\includegraphics[width=\textwidth]{article_springer_files/figure-latex/solar-flare-tail-scale-1} \caption{\label{fig:flares} Stability plots for the tail and scale parameter of the Mittag-Leffler distribution of the Solar Flare dataset.
+Dotted horizontal lines are at $\beta = 0.85$ and $\sigma_0 = 3 \times 10^7$ seconds $\approx 0.95$ years.}\label{fig:solar-flare-tail-scale}
+\end{figure}
+
+The fit with a Mittag-Leffler distribution (\(\beta = 0.85\)) is good
+(see Figure \ref{fig:flare-diagnostics-3}), though there are signs that
+the power-law tail tapers off for very large inter-threshold crossing
+times. There is no apparent dependence between threshold exceedance
+times and event magnitudes seen in the copula plot (see Figure
+\ref{fig:flare-diagnostics-2}). We also counduct a bootstrapped LRT for
+the null hypothesis of exponential distributed inter-arrival times and
+received a \(p\)-value of \(p<0.01\).
+
+\hypertarget{predicting-the-time-of-the-next-threshold-crossing}{%
 \section{Predicting the time of the next threshold
-crossing}\label{predicting-the-time-of-the-next-threshold-crossing}
+crossing}\label{predicting-the-time-of-the-next-threshold-crossing}}
 
@@
 distribution is \[
-T_\ell \sim {\rm ML}(\beta, k^{1/\beta} \sigma_0), 
+T(\ell) \sim {\rm ML}(\beta, k^{-1/\beta} \sigma_0), 
 \] where \(\beta = 0.85\) and \(\sigma_0 = 3.0 \times 10^7 {\rm sec}\).
@@
 the last threshold crossing. This density equals \[
-p(t|\beta, \sigma_0, \ell, t_0) = \frac{f(t + t_0 | \beta, k^{1/\beta} \sigma_0)}{\mathbf P[T_\ell > t_0]}
-\] where \(f(\,\cdot\, | \beta, k^{1/\beta} \sigma_0)\) is the
-probability density of \({\rm ML}(\beta, k^{1/\beta} \sigma_0)\). The
+p(t|\beta, \sigma_0, \ell, t_0) = \frac{f(t + t_0 | \beta, k^{-1/\beta} \sigma_0)}{\mathbf P[T_\ell > t_0]}
+\] where \(f(\,\cdot\, | \beta, k^{-1/\beta} \sigma_0)\) is the
+probability density of \({\rm ML}(\beta, k^{-1/\beta} \sigma_0)\). The
 more time has passed without a threshold crossing, the more the
@@
 crossing (see Figure \ref{fig:hazard}, left panel). The hazard rate \[
-h(t) = \frac{f(t| \beta, k^{1/\beta} \sigma_0))}{\int_t^\infty f(\tau| \beta, k^{1/\beta} \sigma_0))\,d\tau}
+h(t) = \frac{f(t| \beta, k^{-1/\beta} \sigma_0))}{\int_t^\infty f(\tau| \beta, k^{-1/\beta} \sigma_0))\,d\tau}
 \] represents the risk of a threshold crossing per unit time, and is a
-decreasing function for the Mittag-Leffler distribution. The closer
-\(\beta\) is to \(1\), the more the hazard rate mimics that of an
-exponential distribution (a constant function, see Figure
+decreasing function for the Mittag-Leffler distribution.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{article_springer_files/figure-latex/hazard-1} \caption{\label{fig:hazard} Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\beta = 0.8$, $\sigma_0 = 1$).
+Right: Hazard rate depending on tail parameter $\beta$.}\label{fig:hazard}
+\end{figure}
+
+The closer \(\beta\) is to \(1\), the more the hazard rate mimics that
+of an exponential distribution (a constant function, see Figure
 \ref{fig:hazard}, right panel).
 
-\begin{figure}
-\includegraphics[width=\textwidth]{article_springer_files/figure-latex/hazard-1} \caption{Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\beta = 0.8$, $\sigma_0 = 1$).
-Right: Hazard rate depending on tail parameter $\beta$.\label{fig:hazard}}\label{fig:hazard}
-\end{figure}
+\hypertarget{discussion-conclusion}{%
+\section{Discussion \& Conclusion}\label{discussion-conclusion}}
 
-It is beyond the scope of the current paper to incorporate parameter
-uncertainty into our predictive distribution for the next threshold
-crossing; however, methods as described by Scarrott and Macdonald (2012)
-and Lee, Fan, and Sisson (2015) are likely to extend to our setting.
-
-\section{Discussion \& Conclusion}\label{discussion-conclusion}
-
-We have extended the POT (Peaks over Threshold) model, a mainstay of
+We have extended the POT (Peaks-over-Threshold) model, a mainstay of
 extreme value theory, to ``bursty'' time series, which have been studied
@@
 ``anomalous'' scaling behaviour in the bursty setting entails two
-phenomena: i) a heavy tail of the interarrival time distribution of
-threshold crossings (long rests), and ii) a high propensity for more
-threshold crossing events immediately after each threshold crossing
-event (bursts). The Mittag-Leffler distribution captures both phenomena,
-due to its heavy tail as well as its stretched exponential (peaked)
-asymptotics for small times. It generalizes the exponential
-distribution, and in the solar flare data example, this generalization
-is warranted, because the likelihood-ratio test is strongly significant.
+phenomena:
+
+\begin{enumerate}
+\def\labelenumi{\roman{enumi})}
+\item
+  a heavy tail of the inter-arrival time distribution of threshold
+  crossings (long rests), and
+\item
+  a high propensity for more threshold crossing events immediately after
+  each threshold crossing event (bursts).
+\end{enumerate}
+
+The Mittag-Leffler distribution captures both phenomena, due to its
+heavy tail as well as its stretched exponential (peaked) asymptotics for
+small times. It generalizes the exponential distribution, and in the
+solar flare data example, this generalization is warranted, because the
+likelihood-ratio test is strongly significant.
 
@@
 \(\ell_0\) is discarded for CTREs, and hence need not satisfy the i.i.d.
-assumption. For the purposes of statistical inference, we merely require
+assumption.For the purposes of statistical inference, we merely require
 that the inter-threshold-crossing times are i.i.d.
@@
 times should be contrasted with the (now standard) approach of clusters
-of extremes, see e.g. Ferro and Segers (2003). In this approach, i.i.d.
+of extremes, see e.g.~Ferro and Segers (2003). In this approach, i.i.d.
 event sequences of magnitudes are generalized to stationary sequences of
@@
 
-Finally, a purely scale-free pattern for event times may be too rigid an
-assumption for some bursty time series, because often the heavy-tailed
-character of the inter-arrival time distribution does not hold at all
-time scales; rather, it applies at short and intermediate time scales,
-and is truncated (or tempered, reverting to an exponential distribution)
-at very long time scales (see e.g. Mark M. Meerschaert, Roy, and Shao
-2012; and Aban, Meerschaert, and Panorska 2006). In such situations, a
-``tempered'' Mittag-Leffler distribution may provide a more realistic
-fit, which we aim to introduce in follow-up work.
+Finally, a purely scale-free pattern for event times may be too rigid as
+an assumption for some bursty time series, because often the
+heavy-tailed character of the inter-arrival time distribution does not
+hold at all time scales; rather, it applies at short and intermediate
+time scales, and is truncated (or tempered, reverting to an exponential
+distribution) at very long time scales (see e.g.~Mark M. Meerschaert,
+Roy, and Shao 2012; and Aban, Meerschaert, and Panorska 2006). In such
+situations, a ``tempered'' Mittag-Leffler distribution may provide a
+more realistic fit, which we aim to introduce in follow-up work.
 
-\subsection*{Acknowledgements}\label{acknowledgements}
-\addcontentsline{toc}{subsection}{Acknowledgements}
+\hypertarget{acknowledgements}{%
+\section*{Acknowledgements}\label{acknowledgements}}
+\addcontentsline{toc}{section}{Acknowledgements}
 
 The authors would like to thank Prof.~Peter Scheffler for insights on
-stochastic process limits for CTRMs, and Gurtek Gill who helped create
-the MittagLeffleR R-package.
+stochastic process limits for CTRMs, Prof.~Roland Fried for discussion
+according the statistical methods and Gurtek Gill who helped create the
+MittagLeffleR R-package.
 
-\appendix
+\newpage
 
-\section{Validating our inference method on simulated
-data}\label{validating-our-inference-method-on-simulated-data}
-
-To test our inference method via stability plots, we have simulated
-10000 independent waiting time and magnitude pairs \((W_k, J_k)\) (see
-upper panel in Figure \ref{fig:thresholdedBursty}). In order to have
-exact analytical values available for \(\beta\) and \(\sigma_0\), a
-distribution for \(W_k\) needs to be chosen for which \(b(n)\) from
-\eqref{eq:stability} is known. If we choose \(W_k \stackrel{d}{=} D\),
-where \(D\) is as in \eqref{eq:stability}, then due to the stability
-property we have the \emph{equality} of distribution
-\(W_1 + \ldots + W_n \stackrel{d}{=} b(n) D\), for
-\(b(n) = n^{1/\beta}\). Using the parametrisation of Samorodnitsky and
-Taqqu (1994), a few lines of calculation (see e.g.~the vignette on
-parametrisation in Gill and Straka (2017)) show that \(D\) must have the
-stable distribution \(S_\beta(\cos(\pi \beta/2)^{1/\beta}, +1, 0)\),
-which is implemented in the R package \texttt{stabledist} by Wuertz,
-Maechler, and members. (2016).
-
-\begin{figure}
-\includegraphics[width=\textwidth]{article_springer_files/figure-latex/simulated-example-1} \caption{Tail and scale estimates for simulated data, with waiting times drawn from the stable distribution $S_\beta(\cos(\pi \beta/2)^{1/\beta}, +1, 0)$ with $\beta = 0.8$.
-Dashed lines are 95\% confidence intervals, dotted lines are the known theoretical values ($0.8$ and $10000^{1/0.8}$).
-\label{fig:sim}}\label{fig:simulated-example}
-\end{figure}
-
-By the Theorem, the distribution of \(T(\ell)\) is approximately \[
-{\rm ML}(\beta, p^{-1/\beta}) 
-= {\rm ML}(\beta, k^{-1/\beta} n^{1/\beta}),
-\] which means \(\sigma_0 = n^{1/\beta}\). The distribution of \(J_k\)
-is irrelevant for the inference on \(\beta\) and \(\sigma_0\) (we have
-chosen unit exponential random variables). Figure \ref{fig:sim} displays
-plots of \(\hat \beta(\ell)\) and \(\hat \sigma(\ell)\) vs. \(k\);
-recall that \(k\) is the index of the order statistics of \(J_k\) at
-which the threshold \(\ell\) is placed. Dotted lines show 95\%
-confidence intervals, which are derived from the asymptotic normality of
-the log-moments estimators (Cahoy 2013) and the \(\delta\)-method (Gill
-and Straka 2017). The dashed lines show the actual values of \(\beta\)
-resp.~\(\sigma_0\), showing that our inference method identifies the
-parameters correctly.
-
-\section*{References}\label{references}
+\hypertarget{references}{%
+\section*{References}\label{references}}
 \addcontentsline{toc}{section}{References}
@@
 \hypertarget{refs}{}
-\hypertarget{ref-Aban06}{}
+\leavevmode\hypertarget{ref-Aban06}{}%
 Aban, Inmaculada B, Mark M Meerschaert, and Anna K Panorska. 2006.
@@
 Am. Stat. Assoc.} 101 (473): 270--77.
-doi:\href{https://doi.org/10.1198/016214505000000411}{10.1198/016214505000000411}.
+\url{https://doi.org/10.1198/016214505000000411}.
 
-\hypertarget{ref-Anderson1987}{}
+\leavevmode\hypertarget{ref-Anderson1987}{}%
 Anderson, Kevin K. 1987. ``Limit Theorems for General Shock Models with
@@
 
-\hypertarget{ref-Bagrow2013}{}
+\leavevmode\hypertarget{ref-Bagrow2013}{}%
 Bagrow, James P., and Dirk Brockmann. 2013. ``Natural emergence of
 clusters and bursts in network evolution.'' \emph{Phys. Rev. X} 3 (2):
-1--6.
-doi:\href{https://doi.org/10.1103/PhysRevX.3.021016}{10.1103/PhysRevX.3.021016}.
+1--6. \url{https://doi.org/10.1103/PhysRevX.3.021016}.
 
-\hypertarget{ref-Barabasi2005}{}
+\leavevmode\hypertarget{ref-Barabasi2005}{}%
 Barabási, Albert László. 2005. ``The origin of bursts and heavy tails in
 human dynamics.'' \emph{Nature} 435 (May): 207--11.
-doi:\href{https://doi.org/10.1038/nature03459}{10.1038/nature03459}.
+\url{https://doi.org/10.1038/nature03459}.
 
-\hypertarget{ref-Basrak2014}{}
+\leavevmode\hypertarget{ref-Basrak2014}{}%
 Basrak, Bojan, and Drago Špoljarić. 2015. ``Extremes of random variables
-observed in renewal times.'' \emph{Stat. Probab. Lett.} 97. Elsevier
-B.V.: 216--21.
-doi:\href{https://doi.org/10.1016/j.spl.2014.11.025}{10.1016/j.spl.2014.11.025}.
+observed in renewal times.'' \emph{Stat. Probab. Lett.} 97: 216--21.
+\url{https://doi.org/10.1016/j.spl.2014.11.025}.
 
-\hypertarget{ref-beirlantBook}{}
+\leavevmode\hypertarget{ref-beirlantBook}{}%
 Beirlant, Jan, Yuri Goegebeur, Johan Segers, and Jozef Teugels. 2006.
@@
 
-\hypertarget{ref-Benson2007}{}
+\leavevmode\hypertarget{ref-Benson2007}{}%
 Benson, David A, Rina Schumer, and Mark M Meerschaert. 2007.
@@
 \emph{Geophys. Res. Lett.} 34 (l16404): DOI:10.1029/2007GL030767.
-doi:\href{https://doi.org/10.1029/2007GL030767}{10.1029/2007GL030767}.
+\url{https://doi.org/10.1029/2007GL030767}.
 
-\hypertarget{ref-Cahoy2013}{}
+\leavevmode\hypertarget{ref-Cahoy2013}{}%
 Cahoy, Dexter O. 2013. ``Estimation of Mittag-Leffler Parameters.''
 \emph{Commun. Stat. - Simul. Comput.} 42 (2): 303--15.
-doi:\href{https://doi.org/10.1080/03610918.2011.640094}{10.1080/03610918.2011.640094}.
+\url{https://doi.org/10.1080/03610918.2011.640094}.
 
-\hypertarget{ref-ColesBook}{}
+\leavevmode\hypertarget{ref-Cahoy2010}{}%
+Cahoy, Dexter O, Vladimir V. Uchaikin, and Wojbor A. Woyczynski. 2010.
+``Parameter estimation for fractional Poisson processes.'' \emph{J.
+Stat. Plan. Inference} 140 (11): 3106--20.
+\url{https://doi.org/10.1016/j.jspi.2010.04.016}.
+
+\leavevmode\hypertarget{ref-ColesBook}{}%
 Coles, S. 2001. \emph{An Introduction to Statistical Modelling of
@@
 
-\hypertarget{ref-HXRBS}{}
+\leavevmode\hypertarget{ref-davison1997bootstrap}{}%
+Davison, Anthony Christopher, David Victor Hinkley, and others. 1997.
+\emph{Bootstrap Methods and Their Application}. Vol. 1. Cambridge
+university press.
+
+\leavevmode\hypertarget{ref-HXRBS}{}%
 Dennis, Brian R, L E Orwig, G S Kennard, G J Labow, R A Schwartz, A R
@@
 
-\hypertarget{ref-Esary1973}{}
+\leavevmode\hypertarget{ref-Esary1973}{}%
 Esary, J. D., and A. W. Marshall. 1973. ``Shock Models and Wear
-Processes.''
-doi:\href{https://doi.org/10.1214/aop/1176996891}{10.1214/aop/1176996891}.
+Processes.'' \url{https://doi.org/10.1214/aop/1176996891}.
 
-\hypertarget{ref-ferro2003inference}{}
+\leavevmode\hypertarget{ref-ferro2003inference}{}%
 Ferro, Christopher AT, and Johan Segers. 2003. ``Inference for Clusters
 of Extreme Values.'' \emph{Journal of the Royal Statistical Society:
-Series B (Statistical Methodology)} 65 (2). Wiley Online Library:
-545--56.
+Series B (Statistical Methodology)} 65 (2): 545--56.
 
-\hypertarget{ref-MittagLeffleR}{}
+\leavevmode\hypertarget{ref-MittagLeffleR}{}%
 Gill, Gurtek, and Peter Straka. 2017. \emph{MittagLeffleR: Using the
@@
 
-\hypertarget{ref-Gut1999}{}
+\leavevmode\hypertarget{ref-Gut1999}{}%
 Gut, Allan, and Jürg Hüsler. 1999. ``Extreme Shock Models.''
@@
 
-\hypertarget{ref-Haubold11}{}
-Haubold, H.J., A. M. Mathai, and R. K. Saxena. 2011. ``Mittag-Leffler
+\leavevmode\hypertarget{ref-Haubold11}{}%
+Haubold, H. J., A. M. Mathai, and R. K. Saxena. 2011. ``Mittag-Leffler
 Functions and Their Applications.'' \emph{J. Appl. Math.} 2011: 1--51.
-doi:\href{https://doi.org/10.1155/2011/298628}{10.1155/2011/298628}.
+\url{https://doi.org/10.1155/2011/298628}.
 
-\hypertarget{ref-hawkes1971point}{}
+\leavevmode\hypertarget{ref-hawkes1971point}{}%
 Hawkes, Alan G. 1971. ``Point spectra of some mutually exciting point
-processes.'' \emph{J. R. Stat. Soc. Ser. B Stat. Methodol.} JSTOR,
-438--43.
+processes.'' \emph{J. R. Stat. Soc. Ser. B Stat. Methodol.}, 438--43.
 
-\hypertarget{ref-Hees16}{}
-Hees, Katharina, and Hans-Peter Scheffler. 2016. ``On joint sum/max
-stability and sum/max domains of attraction,'' June, 1--31.
-\url{http://arxiv.org/abs/1606.03109}.
+\leavevmode\hypertarget{ref-hees2017coupled}{}%
+Hees, Katharina, and Hans-Peter Scheffler. 2018a. ``Coupled Continuous
+Time Random Maxima.'' \emph{Extremes} 21 (2).
 
-\hypertarget{ref-Hees17}{}
----------. 2017. ``Coupled Continuous Time Random Maxima.''
-\emph{Extremes}, no. June (September). Extremes: 1--24.
-doi:\href{https://doi.org/10.1007/s10687-017-0304-6}{10.1007/s10687-017-0304-6}.
+\leavevmode\hypertarget{ref-hees2016joint}{}%
+---------. 2018b. ``On Joint Sum/Max Stability and Sum/Max Domains of
+Attraction.'' \emph{Probability and Mathematical Statistics} 38 (1).
 
-\hypertarget{ref-Hsing88}{}
-Hsing, T, J Hüsler, and M R Leadbetter. 1988. ``On the Exceedance Point
-Process for a Stationary Sequence'' 78: 97--112.
+\leavevmode\hypertarget{ref-hill1975simple}{}%
+Hill, Bruce M. 1975. ``A Simple General Approach to Inference About the
+Tail of a Distribution.'' \emph{The Annals of Statistics}, 1163--74.
 
-\hypertarget{ref-Karsai2012}{}
+\leavevmode\hypertarget{ref-Karsai2012}{}%
 Karsai, Márton, Kimmo Kaski, Albert László Barabási, and János Kertész.
 2012. ``Universal features of correlated bursty behaviour.'' \emph{Sci.
-Rep.} 2.
-doi:\href{https://doi.org/10.1038/srep00397}{10.1038/srep00397}.
+Rep.} 2. \url{https://doi.org/10.1038/srep00397}.
 
-\hypertarget{ref-Karsai2011}{}
+\leavevmode\hypertarget{ref-Karsai2011}{}%
 Karsai, Márton, M. Kivelä, R. K. Pan, K. Kaski, J. Kertész, Albert
@@
 E - Stat. Nonlinear, Soft Matter Phys.} 83: 1--4.
-doi:\href{https://doi.org/10.1103/PhysRevE.83.025102}{10.1103/PhysRevE.83.025102}.
+\url{https://doi.org/10.1103/PhysRevE.83.025102}.
 
-\hypertarget{ref-Kratz96}{}
-Kratz, Marie, and Sidney I. Resnick. 1996. ``The qq-estimator and heavy
-tails.'' \emph{Commun. Stat. Part C Stoch. Model.} 12 (4): 699--724.
-doi:\href{https://doi.org/10.1080/15326349608807407}{10.1080/15326349608807407}.
+\leavevmode\hypertarget{ref-kozubowski2001}{}%
+Kozubowski, Tomasz J. 2001. ``Fractional Moment Estimation of Linnik and
+Mittag-Leffler Parameters.'' \emph{Mathematical and Computer Modelling}
+34 (9-11): 1023--35.
 
-\hypertarget{ref-Laskin2003}{}
+\leavevmode\hypertarget{ref-Laskin2003}{}%
 Laskin, Nick. 2003. ``Fractional Poisson process.'' \emph{Commun.
 Nonlinear Sci. Numer. Simul.} 8 (3-4): 201--13.
-doi:\href{https://doi.org/10.1016/S1007-5704(03)00037-6}{10.1016/S1007-5704(03)00037-6}.
+\url{https://doi.org/10.1016/S1007-5704(03)00037-6}.
 
-\hypertarget{ref-Lee15}{}
+\leavevmode\hypertarget{ref-Lee15}{}%
 Lee, J., Y. Fan, and S. A. Sisson. 2015. ``Bayesian threshold selection
 for extremal models using measures of surprise.'' \emph{Comput. Stat.
-Data Anal.} 85. Elsevier B.V.: 84--99.
-doi:\href{https://doi.org/10.1016/j.csda.2014.12.004}{10.1016/j.csda.2014.12.004}.
+Data Anal.} 85: 84--99.
+\url{https://doi.org/10.1016/j.csda.2014.12.004}.
 
-\hypertarget{ref-MeerschaertSikorskii}{}
+\leavevmode\hypertarget{ref-Meerschaert2010b}{}%
+Meerschaert, Mark M, Erkan Nane, and P. Vellaisamy. 2011. ``The
+fractional Poisson process and the inverse stable subordinator.''
+\emph{Electron. J. Probab.} 16: 1600--1620.
+\url{https://doi.org/10.1214/EJP.v16-920}.
+
+\leavevmode\hypertarget{ref-MeerschaertRoyQin}{}%
+Meerschaert, Mark M., Parthanil Roy, and Qin Shao. 2012. ``Parameter
+estimation for exponentially tempered power law distributions.''
+\emph{Commun. Stat. - Theory Methods} 41 (10): 1839--56.
+\url{https://doi.org/10.1080/03610926.2011.552828}.
+
+\leavevmode\hypertarget{ref-MeerschaertSikorskii}{}%
 Meerschaert, Mark M, and Alla Sikorskii. 2012. \emph{Stochastic Models
@@
 
-\hypertarget{ref-MeerschaertStoev08}{}
+\leavevmode\hypertarget{ref-MeerschaertStoev08}{}%
 Meerschaert, Mark M, and Stilian A Stoev. 2008. ``Extremal limit
@@
 \emph{J. Stat. Plan. Inference} 139 (7): 2175--88.
-doi:\href{https://doi.org/10.1016/j.jspi.2008.10.005}{10.1016/j.jspi.2008.10.005}.
+\url{https://doi.org/10.1016/j.jspi.2008.10.005}.
 
-\hypertarget{ref-Meerschaert2010b}{}
-Meerschaert, Mark M, Erkan Nane, and P. Vellaisamy. 2011. ``The
-fractional Poisson process and the inverse stable subordinator.''
-\emph{Electron. J. Probab.} 16: 1600--1620.
-doi:\href{https://doi.org/10.1214/EJP.v16-920}{10.1214/EJP.v16-920}.
-
-\hypertarget{ref-MeerschaertRoyQin}{}
-Meerschaert, Mark M., Parthanil Roy, and Qin Shao. 2012. ``Parameter
-estimation for exponentially tempered power law distributions.''
-\emph{Commun. Stat. - Theory Methods} 41 (10): 1839--56.
-doi:\href{https://doi.org/10.1080/03610926.2011.552828}{10.1080/03610926.2011.552828}.
-
-\hypertarget{ref-Min2010}{}
+\leavevmode\hypertarget{ref-Min2010}{}%
 Min, Byungjoon, K. I. Goh, and Alexei Vazquez. 2011. ``Spreading
@@
 - Stat. Nonlinear, Soft Matter Phys.} 83 (3): 2--5.
-doi:\href{https://doi.org/10.1103/PhysRevE.83.036102}{10.1103/PhysRevE.83.036102}.
+\url{https://doi.org/10.1103/PhysRevE.83.036102}.
 
-\hypertarget{ref-Oliveira2005}{}
+\leavevmode\hypertarget{ref-Oliveira2005}{}%
 Oliveira, J, and Albert László Barabási. 2005. ``Darwin and Einstein
 correspondence patterns.'' \emph{Nature} 437 (October): 1251.
-doi:\href{https://doi.org/10.0138/4371251a}{10.0138/4371251a}.
+\url{https://doi.org/10.0138/4371251a}.
 
-\hypertarget{ref-Omi2011}{}
+\leavevmode\hypertarget{ref-Omi2011}{}%
 Omi, Takahiro, and Shigeru Shinomoto. 2011. ``Optimizing Time Histograms
 for Non-Poissonian Spike Trains.'' \emph{Neural Comput.} 23 (12):
-3125--44.
-doi:\href{https://doi.org/10.1162/NECO_a_00213}{10.1162/NECO\_a\_00213}.
+3125--44. \url{https://doi.org/10.1162/NECO_a_00213}.
 
-\hypertarget{ref-R}{}
+\leavevmode\hypertarget{ref-Hsing88}{}%
+``On the Exceedance Point Process for a Stationary Sequence.'' 1988 78:
+97--112.
+
+\leavevmode\hypertarget{ref-R}{}%
 R Core Team. 2018. \emph{R: A Language and Environment for Statistical
@@
 
-\hypertarget{ref-Resnick97}{}
+\leavevmode\hypertarget{ref-Resnick97}{}%
 Resnick, Sidney I. 1997. ``Heavy tail modeling and teletraffic data.''
 \emph{Ann. Stat.} 25 (5): 1805--49.
-doi:\href{https://doi.org/10.1214/aos/1069362376}{10.1214/aos/1069362376}.
+\url{https://doi.org/10.1214/aos/1069362376}.
 
-\hypertarget{ref-SamorodnitskyTaqqu}{}
+\leavevmode\hypertarget{ref-SamorodnitskyTaqqu}{}%
 Samorodnitsky, Gennady, and Murad S Taqqu. 1994. \emph{Stable
@@
 
-\hypertarget{ref-Scarrott12}{}
-Scarrott, Carl, and Anna Macdonald. 2012. ``A REVIEW OF EXTREME VALUE
-THRESHOLD ESTIMATION AND UNCERTAINTY QUANTIFICATION.'' \emph{REVSTAT --
-Stat. J.} 10 (1): 33--60.
-
-\hypertarget{ref-Sumita1983}{}
+\leavevmode\hypertarget{ref-Sumita1983}{}%
 Shanthikumar, J. George, and Ushio Sumita. 1983. ``General shock models
@@
 
-\hypertarget{ref-Sumita1984}{}
+\leavevmode\hypertarget{ref-Sumita1984}{}%
 ---------. 1984. ``Distribution Properties of the System Failure Time in
@@
 
-\hypertarget{ref-Sumita1985}{}
+\leavevmode\hypertarget{ref-Sumita1985}{}%
 ---------. 1985. ``A class of correlated cumulative shock models.''
@@
 
-\hypertarget{ref-Silvestrov2002a}{}
+\leavevmode\hypertarget{ref-Silvestrov2002a}{}%
 Silvestrov, Dmitrii S. 2002. \emph{Limit Theorems for Randomly Stopped
@@
 
-\hypertarget{ref-ST04}{}
+\leavevmode\hypertarget{ref-ST04}{}%
 Silvestrov, Dmitrii S, and Jozef L. Teugels. 2004. ``Limit theorems for
@@
 Probab.} 14 (4): 1838--68.
-doi:\href{https://doi.org/10.1214/105051604000000215}{10.1214/105051604000000215}.
+\url{https://doi.org/10.1214/105051604000000215}.
 
-\hypertarget{ref-Vajna2013}{}
+\leavevmode\hypertarget{ref-Vajna2013}{}%
 Vajna, Szabolcs, Bálint Tóth, and János Kertész. 2013. ``Modelling
 bursty time series.'' \emph{New J. Phys.} 15 (10): 103023.
-doi:\href{https://doi.org/10.1088/1367-2630/15/10/103023}{10.1088/1367-2630/15/10/103023}.
+\url{https://doi.org/10.1088/1367-2630/15/10/103023}.
 
-\hypertarget{ref-Vasquez2006}{}
+\leavevmode\hypertarget{ref-Vasquez2006}{}%
 Vasquez, a, J G Oliveira, Z Dezso, K-I Goh, I Kondor, and Albert László
@@
 \emph{Phys. Rev. E} 73: 361271--3612718.
+\url{http://arxiv.org/abs/0510117v1}.
 
-\hypertarget{ref-Vazquez2007}{}
+\leavevmode\hypertarget{ref-Vazquez2007}{}%
 Vazquez, Alexei, Balázs Rácz, András Lukács, and Albert László Barabási.
@@
 processes.'' \emph{Phys. Rev. Lett.} 98 (APRIL): 1--4.
-doi:\href{https://doi.org/10.1103/PhysRevLett.98.158702}{10.1103/PhysRevLett.98.158702}.
+\url{https://doi.org/10.1103/PhysRevLett.98.158702}.
 
-\hypertarget{ref-stabledist}{}
+\leavevmode\hypertarget{ref-stabledist}{}%
 Wuertz, Diethelm, Martin Maechler, and Rmetrics core team members. 2016.

### 2020-02-15 article_springer/article_springer.Rmd
Peter's part of addressing referee comments

@@
   affiliation: c
-  email: "p.straka@unsw.edu.au"
+  email: "straka.ps@gmail.com"
 
@@
 sim_ctre <- ctre(data.frame(times, magnitudes)) 
-p1<-plot(sim_ctre, p = 0.01, main = "Simulated MRP") 
-p2<-flares %>% ctre() %>% plot(p = 0.02, log = 'y', main = "HXRBS data") 
+p1<-plot(sim_ctre, p = 0.01, main = "Simulated MRP") + 
+  ggtitle("Simulated MRP")
+p2<-flares %>% ctre() %>% plot(p = 0.02, log = 'y', main = "HXRBS data") +
+  ggtitle("HXRBS data")
 grid.arrange(p1,p2)
-
 ```
@@
 Then the two sequences $X(\ell, n)_{n \in \mathbb N}$ and $T(\ell, n)_{n \in \mathbb N}$ are independent as well.
-To see why, note that $X(\ell)$ is, in distribution, simply equal to $J | J > \ell$, independent of any waiting time $W_k$.
+To see why, note that $X(\ell)$ is, in distribution, simply equal to $J - \ell | J > \ell$, independent of any waiting time $W_k$.
 Figure \ref{fig:thresholdedBursty} shows a simulated dataset in the top panel, where $W$ has a stable distribution with tail parameter $\beta =$ `r params$tail` (and skewness $1$ and location $0$), and where $J$ is from a standard Gumbel distribution.
@@
 
-In this section we state and prove the key theorem, see below. For an accessible introduction to regular variation and stable limit theorems, we recommend the book by @MeerschaertSikorskii.
+In this section we state and prove the key theorem. For an accessible introduction to regular variation and stable limit theorems, we recommend the book by @MeerschaertSikorskii.
 
@@
 
-: Let the waiting times $J_k$ be in the domain of attraction of a positively skewed sum-stable law with stability parameter $0 < \beta < 1$; more precisely,
+: Let the waiting times $W_k$ be in the domain of attraction of a positively skewed sum-stable law with stability parameter $0 < \beta < 1$; more precisely,
 \begin{align} \label{eq:stability}
@@
 _inverse_ to $b(c)$, in the sense that 
-$b(\tilde b(c)) \sim c \sim \tilde b(b(c))$.
+$b(\tilde b(c)) \sim c \sim \tilde b(b(c))$ [@BinghamGoldieTeugels].
 
@@
 exponential distribution, for the purposes of applied statistics.
+
+We caution the reader that, somewhat confusingly, there is another distribution
+called the "light-tailed" Mittag-Leffler distribution.  This is in fact the 
+limiting distribution of the renewal process $N(t)$ above (see @limitCTRW). 
 For a detailed reference on the Mittag-Leffler distribution, see e.g. 
@@
 Equation (2.2) in @Gut1999. In @Anderson1987  a similar result is shown with a different choice of scaling constant.
+
+**Remark:**
+
+: When $0 < \beta < 1$, the renewal process $N(t)$ is _not stationary_, 
+and hence the results by @Hsing88 on the exceedances of stationary sequences
+do not apply.
 
@@
 In the R Package `MittagLeffleR` [@MittagLeffleR], Maximum Likelihood estimation is implemented via numerical optimization.
-The MLE slightly outperforms the log-moment estimator regarding bias and RMSE for big enough sample sizes, but is extremely computational intensive.
+The MLE slightly outperforms the log-moment estimator regarding bias and RMSE for big enough sample sizes, but is extremely computationally intensive.
 Figure \ref{fig:MSE} shows that both estimators perform well, even for small sample sizes.
 
-```{r MSE, echo=FALSE,warning=FALSE, fig.height=7,fig.width=8,fig.align="center", fig.cap="\\label{fig:MSE} MSE for the estimation of tail (left column) and scale (right column) parameters via log-moment estimator and mle of a Mittag-Leffler sample with varying sample size n=25, 100, 200, varying tails on the x-axis and fixed scale equal to one.", out.width = '90%'}
-load(here::here("article_springer\\article_springer_files\\ML_estim_simu","tbl_ges.RData"))
+```{r MSE, echo=FALSE,warning=FALSE, fig.height=7,fig.width=8,fig.align="center", fig.cap="\\label{fig:MSE} MSE for the estimation of tail (left column) and scale (right column) parameters via log-moment estimator and MLE of a Mittag-Leffler sample with varying sample size n=25, 100, 200, varying tails on the x-axis and fixed scale equal to one.", out.width = '90%'}
+load(here::here("article_springer", "article_springer_files", "ML_estim_simu","tbl_ges.RData"))
 tbl_ges %>% 
@@
 Of course, one can also use established tail exponent estimators for the estimation of the parameter $\beta$ such as the Hill estimator [@hill1975simple] based on the $r+1$ upper order statistics
-\begin{align}\label{eq:hill}
+\begin{align}\label{eq:Hill}
 H_{r,n}=\left[ \frac{1}{r} \sum_{i=0}^{r} \log \frac{X_{(i)}}{X_{(r+1)}}\right]^{-1}, 
@@
 However, these methods are statistically less efficient since they only use a portion of the information contained in the data, as mentioned by @kozubowski2001.
-Moreover, the hill estimator requires a tuning parameter, denoted with $r$ in \eqref{eq:hill}.
+Moreover, the Hill estimator requires a tuning parameter, denoted with $r$ in \eqref{eq:Hill}.
 Additionaly, the estimator only performs reliably well for distributions close to Pareto [see @Resnick97].
@@
 To deduce the correct tail parameter estimates from these plots is virtually impossible.
-To estimate the tail parameter of a Mittag-Leffler distribution with the hill estimator, the sample size has to be much larger and one has to choose a large tuning parameter $r$.
+To estimate the tail parameter of a Mittag-Leffler distribution with the Hill estimator, the sample size has to be much larger and one has to choose a large tuning parameter $r$.
 In case that only events above a high threshold are recorded, even $n=1000$ events are unrealistic.
-Furthermore the Hill estimator of course completely fails if the inter-arrival times are exponential distributed and not heavy-tailed.
-We will comeback to the problems with the hill estimtator in Section \ref{Simulationstudy}.
+Furthermore the Hill estimator of course completely fails if the inter-arrival times are exponentially distributed and not heavy-tailed.
+We will come back to the problems with the Hill estimtator in Section \ref{Simulationstudy}.
 
-```{r Hillplots, echo=FALSE,warning=FALSE, fig.align="center", fig.cap="\\label{fig:Hillplots} Hillplots for simulated Mittag-Leffler data with true tail 0.8 and sample size 200 (left) and 1000 (right), with number of upper order statics r on which the hill estimator is based on the x-axis.
+```{r Hillplots, echo=FALSE,warning=FALSE, fig.align="center", fig.cap="\\label{fig:Hillplots} Hillplots for simulated Mittag-Leffler data with true tail 0.8 and sample size 200 (left) and 1000 (right), with number of upper order statics r on which the Hill estimator is based on the x-axis.
 ", out.width = '90%'}
@@
 data_ml_1<-rml(n=200,tail=0.8,scale=1)
-p1<-hill_estim_plot(k_min=30,data=data_ml_1,true_tail=0.8)
+p1<-hill_estim_plot(k_min=30,data=data_ml_1,true_tail=0.8) +
+  ggtitle("Hill plot, Mittag-Leffler data, n=200")
 
 data_ml_2<-rml(n=1000,tail=0.8,scale=1)
-p2<-hill_estim_plot(k_min=30,data=data_ml_2,true_tail=0.8)
+p2<-hill_estim_plot(k_min=30,data=data_ml_2,true_tail=0.8) +
+  ggtitle("Hill plot, Mittag-Leffler data, n=1000")
+
 grid.arrange(p1,p2,ncol=2)
@@
 
-```{r LRT_power, echo=FALSE,warning=FALSE, fig.align="center", fig.cap="\\label{Fig:LRT} Power for bootstrapped LRT for different sample sizes , varying tails and scale parameter equal to 1.",out.width='90%'}
+```{r LRT_power, echo=FALSE,warning=FALSE, fig.align="center", fig.cap="\\label{Fig:LRT} Power for bootstrapped LRT for different sample sizes, varying tails and scale parameter equal to 1.", out.width='90%'}
 load(here::here("article_springer","article_springer_files","ML_LRT_simu","estimates_df_LRT_boot1_01.RData"))
@@
    labs(y="Power",x= "True tail parameter")+
-  scale_color_manual(values=c("red", "blue","darkgreen","black"), name  ="Sample size")
+  scale_color_manual(values=c("red", "blue","darkgreen","black"), name  ="Sample size") +
+  ggtitle("Power of Likelihood-Ratio Test")
 ```
@@
 
-1. For a range of thresholds $\ell$ near the largest order statistics, extract datasets of exceedance times $\{T(\ell, i)\}_i$.
+1. Extract the $K$ largest order statistics 
+(i.e. the $K$ largest values, where e.g. $K = 300$) 
+$X_{(1)}, \ldots, X_{(K)}$ together with their timestamps $T_{(1)}, \ldots, T_{(K)}$.
 
-2. For each choice of threshold $\ell$, fit a Mittag-Leffler distribution to the resulting dataset
-  $\{T(\ell, i)\}_i$.  This results in the estimates $\{\hat\beta(\ell)\}_\ell$ and $\{\hat \sigma(\ell)\}_\ell$.
+2. Choose e.g. $K_0 = 5$, and for each $k$ ranging from $K_0 +1$ to $K + 1$: 
+    a) extract the set $\mathcal T_k$ of exceedance times of the threshold $X_{(k)}$
+    b) fit a Mittag-Leffler distribution to $\mathcal T_k$, resulting in the parameter
+    estimates $\hat\beta_k$ and $\hat \sigma_k$.
 
-3. Plot $\ell$ vs.\ $\hat \beta(\ell)$. As $\ell$ increases towards $x_R$, 
-  $\hat \beta(\ell)$ *stabilizes* around a constant $\hat \beta$. Use $\hat \beta$ as an estimate for the tail      parameter $\beta$ of the Mittag-Leffler distribution of exceedance times.
+3. Plot $k$ vs.\ $\hat \beta_k$. As $k \downarrow K_0$,
+  $\hat \beta_k$ *stabilizes* around a constant $\hat \beta$.
 
-4. Approximate $p \approx |\{k: J_k > \ell\}| / n$. 
-  Recall that $b(c)$ is regularly varying with parameter $1/\beta$, and 
-  hence has the representation $b(c) = L(c) c^{1/\beta}$ for some 
-  slowly varying function $L(c)$. 
-  Assuming that the variation of $L(c)$ is negligible, we hence 
-  plot $\ell$ vs.\ $p^{1/\hat \beta} \hat \sigma(\ell)$. 
-  Again as $\ell$ increases towards $x_R$, 
-  $p^{1/\hat \beta} \hat \sigma(\ell)$ is expected to stabilize around a constant 
+4. Plot $k$ vs.\ $k^{1/\hat \beta} \hat \sigma_k$. 
+  Where the plot stabilizes as $k \downarrow K_0$, define the value 
   $\hat \sigma_0$.
-  We then use $p^{-1/\hat \beta} \hat \sigma_0$ as an estimate of the scale 
-  parameter of the Mittag-Leffler distribution of exceedance times for
-  the level $\ell$.
 
-The above approach benefits from the following
-practical adjustments (compare with Figure \ref{fig:flares}):
+The inferred values $\hat \beta$ and $\hat \sigma_0$ can then be interpreted as follows: 
+Setting the threshold at $X_{(k)}$, the threshold exceedance times follow a 
+Mittag-Leffler distribution with shape parameter $\hat \beta$ and scale parameter
+$\hat \sigma_0 k^{-1/\beta}$.
 
-* We choose $\ell$ from the order statistics, i.e. $\ell$ is the $k$-th
-  largest of the observations $X_j$, where $k$ runs from 
-  $k_\text{min}, k_\text{min} + 1, \ldots, k_\text{max}$. 
-  The datasets are then of length $k-1$.
+To clarify Step 4: Recall that by the theorem, $\sigma_k / b(1/p)$ is expected to stabilize 
+around a constant as $k \downarrow K_0$. Since $b$ is regularly varying with parameter
+$1/\beta$, we have $b(1/p) = p^{-1/\beta} / L(1/p)$ for some slowly varying function $L$. 
+Approximating $p \approx \hat p := k / n$, we have 
+$$\text{const} \approx \sigma_k / b(1/p) = \sigma_k \times p^{1/\beta} L(1/p) \approx \sigma_k \times k^{1/\beta} n^{-1/\beta} L(n/k)$$
+Assuming that the variation of $L(n/k)$ is minor, we can hence see that 
+$\sigma_k k^{1/\beta}$ stabilizes.
 
-* We use $k$ rather than $\ell$ for the horizontal axis of our plots.
-
-* In Step 4, rather than plotting $p^{1/\hat \beta} \hat \sigma(\ell)$
-  we plot $k^{1/\hat \beta} \hat \sigma(\ell)$. This changes 
-  $\hat \sigma_0$ by the multiplicative constant $n^{1/\hat \beta}$, 
-  but has the advantage that
-  $\hat \sigma_0$ does not change if one pre-processes the data by 
-  removing all observations below a certain threshold.
-
-The estimates $\hat \beta$ and $\hat \sigma_0$ give an estimate of the 
-distribution of exceedance times, dependent on the threshold $\ell$:
-\begin{align*}
-T(\ell) \sim {\rm ML}(\hat \beta, k^{-1/\hat \beta} \hat \sigma_0),
-\end{align*}
-where $\ell$ equals the $k$-th order statistic.
-For quick estimates of the Mittag-Leffler parameters we have used 
-the method of log-transformed moments [@Cahoy2013].
+For computationally efficient estimates of the Mittag-Leffler parameters we have used 
+the method of log-transformed moments. This estimation method provides 
+point estimates as well as confidence intervals based on sampling variance [@Cahoy2013], 
+and has been implemented in the R software package
+`MittagLeffleR` [@MittagLeffleR]. The stability plots for $\hat \beta$ and $\hat \sigma_0$
+can be furnished with these confidence intervals, see e.g.\ Figure \ref{fig:flares}, 
+to produce (non-simultaneous) confidence bands. 
+These stability plots were produced with the R package `CTRE` [@CTRE]. 
 We have verified the validity of our estimation algorithm  via simulations, 
@@
 
-# Simulation study{#Simulationstudy}
+# Simulation Study {#Simulationstudy}
 
@@
 In order to have exact analytical values available for $\beta$ and $\sigma_0$, a distribution for $W_k$ needs to be chosen for which $b(n)$ from \eqref{eq:stability} is known.
-For (i) we choose $W_k \stackrel{d}{=} D$, where $D$ is as in \eqref{eq:stability}, then due to the stability property we have the *equality* of distribution
+
+**Case (i):** For (i) we choose $W_k \stackrel{d}{=} D$, where $D$ is as in \eqref{eq:stability}, then due to the stability property we have the *equality* of distribution
 $W_1 + \ldots + W_n \stackrel{d}{=} b(n) D$, 
@@
 $\sigma_0 = n^{1/\beta}$.
-In the Pareto example we choose $P(W>t)=Ct^{-\beta}$ with $C=(1/\Gamma(1-\beta))^{1/\beta}$.
-We have chosen $\beta=0.8$ in the stable as well as in the Pareto case.
-As third example we choose exponential distributed waiting times with a rate of $1$.
-Figure \ref{Fig:TailSimu} shows the stability plots for the estimation of the tail parameter.
-Therefore, $\hat \beta(k)$ vs.
-$k$ is plotted for each of the $m=100$ simulation runs (grey thin lines).
-In the left column one can see the estimates based on the log-moment estimator, the stability plots in the middle are based on the maximum-likelihood estimator and on the right hand on the hill estimator.
-Recall that $k$ is the index of the order statistics of $J_k$ at which the threshold $\ell$ is placed.
-Note, that the hill estimator is here based on the waiting times, not on the inter-exceedance times, hence the estimation is based on much more data.
-If one would base the hill-estimation only on the inter-exceedance times, the sample size would be too small and it would be impossible to deduce an estimate for the tail parameter from the plots (compare Figure \ref{fig:Hillplots}).
-The $k$ on the $x-$axis is in the plots for the hill estimator the $r$ which defines on which upper orders stats the hill estimator is based on (compare \eqref{eq:hill}).
-The bigger sample size results in the middle in a lower bias.
-But, one can also see, that there is much more variance between the stability plots for the different simulation runs in case of the hill estimator compared to the other two estimators.
-The black line is the mean value of the point estimators for each $k$ resp.
-$r$.
-However, if one wants to get a single estimate via such a stability plot, it would be much more difficult to deduce it from a hill plot compared to the other two estimators.
-In case that one has only thresholded data and hence a much smaller simple size, the hill estimator gets useless (see Section \ref{sec:ML}).
-Another advantage of the other estimators compared to the hill estimator is, that in the case one has exponential waiting times, the log-moment as well as the mle can detect this by getting an estimate close to $1$.
-The hill estimators is just a tail parameter estimator for Pareto like tails and hence of course fails in case of exponential distributed inter-exceedance times.
-Figure \ref{Fig:ScaleSimu} shows the stability plots for the different estimators for the scale parameter.
-Here of course only for the log-moment (on the right hand)  and the mle (on the left hand), since the hill estimator is just a tail parameter estimate.
-Here again both estimators show good performance.
-The stability plots in the mle case are a little bit closer to the true value, except in the exponetial case.
-Therefore, the mle is much more computational intensive.
 
-```{r TailSimuplots, message=FALSE,echo=FALSE,fig.height=7,fig.align="center",fig.cap="\\label{Fig:TailSimu} Stability Plots for m=100 simulation runs for stable distributed waiting times with a tail parameter of 0.8 (top row), Pareto distributed waiting times with tail parameter 0.8 (middle row) and exponential distributed waiting times (lower row).
+**Case (ii):** In the Pareto example we choose $P(W>t)=Ct^{-\beta}$ with $C=(1/\Gamma(1-\beta))^{1/\beta}$. We have chosen $\beta=0.8$ in both cases (i) and (ii).
+
+**Case (iii):** We choose exponentially distributed waiting times with a rate 
+parameter of $1$.
+
+Figure \ref{Fig:TailSimu} shows the graphical "stability plots" for the 
+estimation of the tail parameter, where
+
++ rows correspond to cases (i), (ii) and (iii), and
++ columns correspond to estimators (log-moment estimator, maximum-likelihood, and Hill estimator).
+
+We plot the tail parameter estimates $\hat \beta(k)$ against $k$ 
+for each of the $m=100$ simulation runs. 
+Thin grey lines represent individual simulation runs, 
+and the thicker black line is their mean. 
+Recall that $k$ is the index of the order statistics of $J_k$ at which the 
+threshold $\ell$ is placed. 
+Note that the Hill estimator is based on the waiting times, not on the 
+inter-exceedance times, meaning that the estimation is based on more data. 
+If one were to base the Hill-estimation only on the inter-exceedance times, 
+the sample size would be too small and it would be impossible to deduce an 
+estimate for the tail parameter from the plots (compare Figure \ref{fig:Hillplots}).
+
+In the right-hand Hill-estimator column, the $k$ on the $x$-axis corresponds to
+$r$ from \eqref{eq:Hill}.
+The Hill estimator appears to be nicely unbiased on Pareto data,
+but compared to the other two estimators, it has a higher variance, 
+as can be seen from the wider spread of the simulated curves. 
+This high variance means that that a single estimate is less reliable compared
+to the other two estimators. 
+This effect is amplified if one only has a thresholded, and thus smaller dataset
+available, to the extent that the Hill estimates become severely flawed
+(see Section \ref{sec:ML}).
+
+Moreover, the bottom in \ref{Fig:TailSimu} shows clearly that the log-moment 
+and maximum-likelihod estimators generalize to the exponential case ($\beta = 1$), 
+whereas the Hill-estimator does not.
+
+Finally, the performance of Log-Moment and Maximum-Likelihood estimators for the
+scale parameter is shown in figure \ref{Fig:ScaleSimu}. 
+Since there is no Hill-estimate of a scale parameter, there are only two columns. 
+Both estimators show good performance, with a slight advantage for the 
+Maximum-Likelihood estimator. This advantage is paid for by a higher computational 
+cost.
+
+```{r TailSimuplots, message=FALSE,echo=FALSE,fig.height=7,fig.align="center",fig.cap="\\label{Fig:TailSimu} Stability Plots for m=100 simulation runs for stable distributed waiting times with a tail parameter of 0.8 (top row), Pareto distributed waiting times with tail parameter 0.8 (middle row) and exponentially distributed waiting times (lower row).
 Left column: log-moment estimator, middle column: MLE, right column: Hill estimator.
@@
 
-path<-here::here("article_springer/article_springer_files/Simulation_results")
-files<-list.files(path)
-file_dirs<-paste(path,"/",files,sep="")
-invisible(sapply(file_dirs,FUN=load,envir=.GlobalEnv,verbose=FALSE))
+path <-
+  here::here("article_springer",
+             "article_springer_files",
+             "Simulation_results")
+files <- list.files(path)
+file_dirs <- paste(path, "/", files, sep = "")
+invisible(sapply(
+  file_dirs,
+  FUN = load,
+  envir = .GlobalEnv,
+  verbose = FALSE
+))
 
@@
 #logMoment estimator
-logMom_Ex1_tail<-ggplot()+ geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_estimates_tail08_logMoms_Ex1) +
+logMom_Ex1_tail <-
+  ggplot() + geom_line(aes(x = k, y = value, group = rep),
+                       colour = "lightgrey",
+                       data = tbl_estimates_tail08_logMoms_Ex1) +
   coord_cartesian(ylim = c(0.5, 1.5)) +
-  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_logMoms_Ex1) + ylab("Estimated tail") + geom_hline(yintercept=0.8, linetype="dashed", color = "red")
+  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_logMoms_Ex1) + 
+  ylab("Estimated tail") + geom_hline(yintercept=0.8, linetype="dashed", color = "red")
 
 #ml estimator
-mle_Ex1_tail<-ggplot() + geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_estimates_tail08_mles_Ex1) +
+mle_Ex1_tail <-
+  ggplot() + geom_line(aes(x = k, y = value, group = rep),
+                       colour = "lightgrey",
+                       data = tbl_estimates_tail08_mles_Ex1) +
   coord_cartesian(ylim = c(0.5, 1.5)) +
-  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_mles_Ex1) + ylab("Estimated tail") + geom_hline(yintercept=0.8, linetype="dashed", color = "red")
+  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_mles_Ex1) + 
+  ylab("Estimated tail") + 
+  geom_hline(yintercept=0.8, linetype="dashed", color = "red")
 
 #Hill estimator
-hill_Ex1_tail<-ggplot()+ geom_line(data=tbl_estimates_tail08_hill_Ex1,aes(x=k,y=value,group=rep),colour="lightgrey") +
+hill_Ex1_tail <-
+  ggplot() + geom_line(data = tbl_estimates_tail08_hill_Ex1,
+                       aes(x = k, y = value, group = rep),
+                       colour = "lightgrey") +
   coord_cartesian(ylim = c(0.5, 1.5)) +
-  geom_line(data=means.tbl_hill_Ex1,aes(x=k, y=mw),colour="black") + ylab("Estimated tail") +  geom_hline(yintercept=0.8, linetype="dashed", color = "red")+ xlab("r")
+  geom_line(data=means.tbl_hill_Ex1,aes(x=k, y=mw),colour="black") + 
+  ylab("Estimated tail") +
+  geom_hline(yintercept=0.8, linetype="dashed", color = "red")+ xlab("r")
 
@@
 #logMoment estimator
-logMom_Ex2_tail<-ggplot()+ geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_estimates_Ex2_Pareto_tail08_logMoms) +
+logMom_Ex2_tail <-
+  ggplot() + geom_line(aes(x = k, y = value, group = rep),
+                       colour = "lightgrey",
+                       data = tbl_estimates_Ex2_Pareto_tail08_logMoms) +
   coord_cartesian(ylim = c(0.5, 1.5)) +
-  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_logMoms_Ex2) + ylab("Estimated tail") + geom_hline(yintercept=0.8, linetype="dashed", color = "red")
+  geom_line(aes(x = k, y = mw), colour = "black", data = means.tbl_logMoms_Ex2) + 
+  ylab("Estimated tail") + 
+  geom_hline(yintercept=0.8, linetype="dashed", color = "red")
 
 #ml estimator
-mle_Ex2_tail<-ggplot() + geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_estimates_Ex2_Pareto_tail08_mles) +
+mle_Ex2_tail <-
+  ggplot() + geom_line(aes(x = k, y = value, group = rep),
+                       colour = "lightgrey",
+                       data = tbl_estimates_Ex2_Pareto_tail08_mles) +
   coord_cartesian(ylim = c(0.5, 1.5)) +
-  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_mles_Ex2) + ylab("Estimated tail") + geom_hline(yintercept=0.8, linetype="dashed", color = "red")
+  geom_line(aes(x = k, y = mw), colour = "black", data = means.tbl_mles_Ex2) + 
+  ylab("Estimated tail") + 
+  geom_hline(yintercept=0.8, linetype="dashed", color = "red")
 
 #Hill estimator
-hill_Ex2_tail<-ggplot() + geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_estimates_Ex2_Pareto_tail08_hill_times) +
+hill_Ex2_tail <-
+  ggplot() + geom_line(aes(x = k, y = value, group = rep),
+                       colour = "lightgrey",
+                       data = tbl_estimates_Ex2_Pareto_tail08_hill_times) +
   coord_cartesian(ylim = c(0.5, 1.5)) +
-  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_hill_times_Ex2) + ylab("Estimated tail") +  geom_hline(yintercept=0.8, linetype="dashed", color = "red")+ xlab("r")
+  geom_line(aes(x = k, y = mw), colour = "black", data = means.tbl_hill_times_Ex2) + 
+  ylab("Estimated tail") +
+  geom_hline(yintercept=0.8, linetype="dashed", color = "red")+ xlab("r")
 
@@
 #logMoment estimator
-logMom_Ex3_tail<-ggplot()+ geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_estimates_Example3_Exp_logMoms) +
+logMom_Ex3_tail <-
+  ggplot() + geom_line(aes(x = k, y = value, group = rep),
+                       colour = "lightgrey",
+                       data = tbl_estimates_Example3_Exp_logMoms) +
   coord_cartesian(ylim = c(0.5, 1.5)) +
-  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_logMoms_Ex3) + ylab("Estimated tail") + geom_hline(yintercept=1, linetype="dashed", color = "red")
+  geom_line(aes(x = k, y = mw), colour = "black", data = means.tbl_logMoms_Ex3) + 
+  ylab("Estimated tail") + 
+  geom_hline(yintercept=1, linetype="dashed", color = "red")
 
 #ml estimator
-mle_Ex3_tail<-ggplot() + geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_estimates_Example3_Exp_mles) +
+mle_Ex3_tail <-
+  ggplot() + geom_line(aes(x = k, y = value, group = rep),
+                       colour = "lightgrey",
+                       data = tbl_estimates_Example3_Exp_mles) +
   coord_cartesian(ylim = c(0.5, 1.5)) +
-  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_mles_Ex3) + ylab("Estimated tail") + geom_hline(yintercept=1, linetype="dashed", color = "red")
+  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_mles_Ex3) + 
+  ylab("Estimated tail") + 
+  geom_hline(yintercept=1, linetype="dashed", color = "red")
 
 #Hill estimator
-hill_Ex3_tail<-ggplot() + geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_estimates_Example3_Exp_hill_times) +
+hill_Ex3_tail <-
+  ggplot() + geom_line(aes(x = k, y = value, group = rep),
+                       colour = "lightgrey",
+                       data = tbl_estimates_Example3_Exp_hill_times) +
   coord_cartesian(ylim = c(0.5, 10)) +
-  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_hill_times_Ex3) + ylab("Estimated tail") + geom_hline(yintercept=1, linetype="dashed", color = "red")+ xlab("r")
+  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_hill_times_Ex3) + 
+  ylab("Estimated tail") + 
+  geom_hline(yintercept=1, linetype="dashed", color = "red")+ xlab("r")
 
-grid.arrange(logMom_Ex1_tail,mle_Ex1_tail,hill_Ex1_tail,logMom_Ex2_tail,mle_Ex2_tail,hill_Ex2_tail,logMom_Ex3_tail,mle_Ex3_tail,hill_Ex3_tail,ncol=3)
+grid.arrange(
+  logMom_Ex1_tail,
+  mle_Ex1_tail,
+  hill_Ex1_tail,
+  logMom_Ex2_tail,
+  mle_Ex2_tail,
+  hill_Ex2_tail,
+  logMom_Ex3_tail,
+  mle_Ex3_tail,
+  hill_Ex3_tail,
+  ncol = 3
+)
 
@@
 
-```{r ScaleSimuplots, message=FALSE,echo=FALSE,fig.height=7,fig.align="center",fig.cap="\\label{Fig:ScaleSimu} Stability Plots for m=100 simulation runs for stable distributed waiting times with a tail parameter of 0.8 (top row), Pareto distributed waiting times with tail parameter 0.8 (middle row) and exponential distributed waiting times (lower row).
+```{r ScaleSimuplots, message=FALSE,echo=FALSE,fig.height=7,fig.align="center",fig.cap="\\label{Fig:ScaleSimu} Stability Plots for m=100 simulation runs for stable distributed waiting times with a tail parameter of 0.8 (top row), Pareto distributed waiting times with tail parameter 0.8 (middle row) and exponentially distributed waiting times (lower row).
 Left column: log-moment estimator, right column: MLE.
@@
 #Example One
-logMom_Ex1_scale<-ggplot()+ geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_scales_logMoms_Ex1) +
+logMom_Ex1_scale <-
+  ggplot() + geom_line(aes(x = k, y = value, group = rep),
+                       colour = "lightgrey",
+                       data = tbl_scales_logMoms_Ex1) +
   coord_cartesian(ylim = c(0, 2)) +
-  geom_line(aes(x=k, y=mw),colour="black",means.tbl_scales_logMoms_Ex1) + ylab("Estimated scale") + geom_hline(yintercept=1, linetype="dashed", color = "red")
+  geom_line(aes(x = k, y = mw), colour = "black", means.tbl_scales_logMoms_Ex1) + 
+  ylab("Estimated scale") +
+  geom_hline(yintercept=1, linetype="dashed", color = "red")
 
-mle_Ex1_scale<-ggplot()+ geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_scales_mles_Ex1) +
+mle_Ex1_scale <-
+  ggplot() + geom_line(aes(x = k, y = value, group = rep),
+                       colour = "lightgrey",
+                       data = tbl_scales_mles_Ex1) +
   coord_cartesian(ylim = c(0, 2)) +
-  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_scales_mles_Ex1) + ylab("Estimated scale") + geom_hline(yintercept=1, linetype="dashed", color = "red")
+  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_scales_mles_Ex1) + 
+  ylab("Estimated scale") +
+  geom_hline(yintercept=1, linetype="dashed", color = "red")
 
@@
 
-logMom_Ex2_scale<-ggplot()+ geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_scales_logMoms_Ex2) +
+logMom_Ex2_scale <-
+  ggplot() + geom_line(aes(x = k, y = value, group = rep),
+                       colour = "lightgrey",
+                       data = tbl_scales_logMoms_Ex2) +
   coord_cartesian(ylim = c(0, 2)) +
-  geom_line(aes(x=k, y=mw),colour="black",means.tbl_scales_logMoms_Ex2) + ylab("Estimated scale") + geom_hline(yintercept=1, linetype="dashed", color = "red")
+  geom_line(aes(x=k, y=mw),colour="black",means.tbl_scales_logMoms_Ex2) + 
+  ylab("Estimated scale") + 
+  geom_hline(yintercept=1, linetype="dashed", color = "red")
 
-mle_Ex2_scale<-ggplot()+ geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_scales_mles_Ex2) +
+mle_Ex2_scale <-
+  ggplot() + geom_line(aes(x = k, y = value, group = rep),
+                       colour = "lightgrey",
+                       data = tbl_scales_mles_Ex2) +
   coord_cartesian(ylim = c(0, 2)) +
-  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_scales_mles_Ex2) + ylab("Estimated scale") + geom_hline(yintercept=1, linetype="dashed", color = "red")
+  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_scales_mles_Ex2) + 
+  ylab("Estimated scale") + 
+  geom_hline(yintercept=1, linetype="dashed", color = "red")
 
@@
 
-logMom_Ex3_scale<-ggplot()+ geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_scales_logMoms_Ex3) +
+logMom_Ex3_scale <-
+  ggplot() + geom_line(aes(x = k, y = value, group = rep),
+                       colour = "lightgrey",
+                       data = tbl_scales_logMoms_Ex3) +
   coord_cartesian(ylim = c(0, 2)) +
-  geom_line(aes(x=k, y=mw),colour="black",means.tbl_scales_logMoms_Ex3) + ylab("Estimated scale") + geom_hline(yintercept=1, linetype="dashed", color = "red")
+  geom_line(aes(x=k, y=mw),colour="black",means.tbl_scales_logMoms_Ex3) + 
+  ylab("Estimated scale") + 
+  geom_hline(yintercept=1, linetype="dashed", color = "red")
 
-mle_Ex3_scale<-ggplot()+ geom_line(aes(x=k,y=value,group=rep),colour="lightgrey",data=tbl_scales_mles_Ex3) +
+mle_Ex3_scale <-
+  ggplot() + geom_line(aes(x = k, y = value, group = rep),
+                       colour = "lightgrey",
+                       data = tbl_scales_mles_Ex3) +
   coord_cartesian(ylim = c(0, 2)) +
-  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_scales_mles_Ex3) + ylab("Estimated scale") + geom_hline(yintercept=1, linetype="dashed", color = "red")
+  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_scales_mles_Ex3) + 
+  ylab("Estimated scale") + 
+  geom_hline(yintercept=1, linetype="dashed", color = "red")
 
-grid.arrange(logMom_Ex1_scale,mle_Ex1_scale,logMom_Ex2_scale,mle_Ex2_scale,logMom_Ex3_scale,mle_Ex3_scale,ncol=2)
+grid.arrange(
+  logMom_Ex1_scale,
+  mle_Ex1_scale,
+  logMom_Ex2_scale,
+  mle_Ex2_scale,
+  logMom_Ex3_scale,
+  mle_Ex3_scale,
+  ncol = 2
+)
 ```
@@
 
-Before we apply the POT approach described in Section 5 to the solar flare data, we first have to check if all model assumptions are full-filled.
+Before we apply the POT approach described in Section 5 to the solar flare data, we first have to check if all model assumptions are fulfilled.
 The CTRE model is based on three main assumptions, which are repeated below.
@@
 ```{r flare-diagnostics-2, fig.height=4.5, fig.width=4.5, fig.align="center",fig.cap="\\label{fig:flare-diagnostics-2} Diagnostic plots for the solar flare data: empirical copula.",out.width="70%"}
-empcopula(flares_ctre)
+empcopula(flares_ctre) + ggtitle("Empirical Copula: Exceedance Time vs. Exceedance")
 ```
@@
 ```{r flare-diagnostics-3, fig.height=4.5, fig.width=4.5, fig.align="center",fig.cap="\\label{fig:flare-diagnostics-3} Diagnostic plots for the solar flare data: QQ Plot.",out.width="70%"}
-flares_ctre %>% interarrival() %>% mlqqplot(log = 'xy', tail = 0.85, main = "Mittag-Leffler QQ Plot")
+sample_data <- flares_ctre %>% interarrival()
+n <- length(sample_data)
+
+population_data <- MittagLeffleR::qml(p = stats::ppoints(n), tail = tail, 
+  scale = 1)
+
+extRemes::qqplot(x = log(sample_data), y = log(population_data), 
+                 main = "QQ-plot Exceedance Times vs Mittag-Leffler",
+                 xlab = "log Exceedance Times", 
+                 ylab = "log Mittag-Leffler")
 ```
@@
 Figure \ref{fig:flares} shows the stability plots for the solar flare data, on the left for the tail parameter and on the right for the scale parameter.
-Dotted lines show 95% confidence intervals, which are derived from the asymptotic normality of the log-moments estimators [@Cahoy2013] and the $\delta$-method [@MittagLeffleR], dashed lines show the deduced values of $\beta$ resp.\ $\sigma_0$.
-The stability plot for the tail stabilizes nicely round about 0.85 (dashed line), while it is a little bit harder to deduce an estimate for the scale parameter.
-Howerever, the stability plot for the scale parameter seems to stabilize round about $3 \times 10^7$ (dashed line).
+The dark grey ranges correspond to 95% confidence intervals, which are derived from the asymptotic normality of the log-moments estimators [@Cahoy2013] and the $\delta$-method [@MittagLeffleR]; dashed lines show the deduced true values of $\beta$ resp.\ $\sigma_0$.
+The stability plot for the tail stabilizes nicely around 0.85 (dashed line), while
+the scale parameter stabilizes less obviously near $3 \times 10^7$ (dashed line).
+The growth of the scale parameter for lower threshold appears to be closer to linear in $p$, 
+rather than proportional to $p^{1/0.85}$ as suggested by the Mittag-Leffler
+fits. The reason for this is likely that the overall goodness of fit as 
+compared to an exponential distribution is improved due to the 
+peaked shape of the Mittag-Leffler distribution near $0$,
+rather than its tail behaviour at $\infty$.
+The reported fit should hence come with the caveat that a Mittag-Leffler 
+distribution models exceedance times well only up to certain time-scales. 
+More research is needed into the modelling of scale transitions, where
+inter-exceedance times appear to have different power laws across different 
+time scales.
 
@@
 There is no apparent dependence between threshold exceedance times and event magnitudes seen in the copula plot (see Figure \ref{fig:flare-diagnostics-2}).
-We also counduct a bootstrapped LRT for the null hypothesis of exponential distributed inter-arrival times and received a $p$-value of $p<0.01$.
+We also counduct a bootstrapped LRT for the null hypothesis of exponentially distributed inter-arrival times and received a $p$-value of $p<0.01$.
 
@@
 According to Figure \ref{fig:flares}, for a threshold $\ell$ at the $k$-th order 
-statistic, the fitted threshold exceedance time distribution is 
+statistic, the estimated threshold exceedance time distribution is 
 $$
@@
 plot(xx, rep(1, length(xx)), ylim = c(0.001,1), type = 'n', log = 'xy', 
-     xlab = 't', ylab = 'p')
+     xlab = 't', ylab = 'p', main = "Next Threshold Crossing Time")
 for (k in 1:length(t_0)) {
@@
 plot(xx, rep(1, length(xx)), ylim = c(0.001,2), type = 'n', log = 'xy', 
-     xlab = 't', ylab = 'h')
+     xlab = 't', ylab = 'h', main = "Mittag-Leffler Hazard Rate")
 for (k in 1:length(betas)) {
@@
 Peter Scheffler for insights on stochastic process limits for CTRMs, Prof.
-Roland Fried for discussion according the statistical methods and Gurtek Gill who helped create the MittagLeffleR R-package.
+Roland Fried for discussion regarding the statistical methods and Gurtek Gill who helped create the MittagLeffleR R-package.
 

### 2020-02-29 article_springer/article_springer.tex
Cleaned Up

@@
 % Pandoc toggle for numbering sections (defaults to be off)
+
 % Pandoc header
@@
    \ead{hees@statistik.tu-dortmund.de} 
-
     \author[b]{Smarak Nayak}
    \ead{smarak.nayak@nab.com.au} 
-
     \author[c]{Peter Straka}
    \ead{p.straka@unsw.edu.au} 
-
       \address[a]{Department of Statistics, TU Dortmund University, Dortmund, Germany}
@@
 the occurrence of events have received strong interest in the recent
-statistical physics literature (Barabási 2005; Oliveira and Barabási
-2005; Vasquez et al. 2006; Vazquez et al. 2007; Omi and Shinomoto 2011;
-Min, Goh, and Vazquez 2011; Karsai et al. 2011; Bagrow and Brockmann
-2013). They have been observed in the context of earthquakes, sunspots,
-neuronal activity and human communication (see Karsai et al. 2012;
-Vajna, Tóth, and Kertész 2013; Meerschaert and Stoev 2008 for a list of
-references). Such time series exhibit high activity in some `bursty'
+statistical physics literature (Bagrow and Brockmann, 2013; Barabási,
+2005; Karsai et al., 2011; Min et al., 2011; Oliveira and Barabási,
+2005; Omi and Shinomoto, 2011; Vasquez et al., 2006; Vazquez et al.,
+2007). They have been observed in the context of earthquakes, sunspots,
+neuronal activity and human communication (see Karsai et al., 2012;
+Meerschaert and Stoev, 2008 for a list of references; Vajna et al.,
+2013). Such time series exhibit high activity in some `bursty'
 intervals, which alternate with other, quiet intervals. Although several
@@
 from temporal homogeneity: a heavy-tailed distribution of waiting times
-(Vasquez et al. 2006; Karsai et al. 2012; Vajna, Tóth, and Kertész
-2013). As we show below in simulations, a simple renewal process with
-heavy-tailed waiting times can capture this type of dynamics. For many
-systems, the renewal property is appropriate; a simple test of the
-absence of correlations in a succession of waiting times can be
-undertaken by randomly reshuffling the waiting times (Karsai et al.
-2012).
+(Karsai et al., 2012; Vajna et al., 2013; Vasquez et al., 2006). As we
+show below in simulations, a simple renewal process with heavy-tailed
+waiting times can capture this type of dynamics. For many systems, the
+renewal property is appropriate; a simple test of the absence of
+correlations in a succession of waiting times can be undertaken by
+randomly reshuffling the waiting times (Karsai et al., 2012).
 
@@
 process, such as for earthquakes, solar flares or neuron voltages. The
-Peaks-Over-Threshold model (POT, see e.g.~Coles 2001) applies a
+Peaks-Over-Threshold model (POT, see e.g.~Coles, 2001) applies a
 threshold to the magnitudes, and fits a Generalized Pareto distribution
@@
 entails that the threshold crossing times form a Poisson process (``On
-the Exceedance Point Process for a Stationary Sequence'' 1988). Then as
+the Exceedance Point Process for a Stationary Sequence,'' 1988). Then as
 one increases the threshold and thus decreases the threshold crossing
 probability \(p\), the Poisson process is rarefied, i.e.~its intensity
-decreases \emph{linearly} with \(p\) (see e.g.~Beirlant et al. 2006).
+decreases \emph{linearly} with \(p\) (see e.g.~Beirlant et al., 2006).
 
@@
 threshold crossing times form a \emph{fractional Poisson process}
-(Laskin 2003; Meerschaert, Nane, and Vellaisamy 2011), which is a
-renewal process with Mittag-Leffler distributed waiting times. The
-family of Mittag-Leffler distributions nests the exponential
-distribution (Haubold, Mathai, and Saxena 2011), and hence the
-fractional Poisson process generalizes the standard Poisson process.
-Again as the threshold size increases and the threshold crossing
-probability \(p\) decreases, the fractional Poisson process is rarefied:
-The scale parameter of the Mittag-Leffler inter-arrival times of
-threshold crossing times increases, but \emph{superlinearly}; see the
-Theorem below.
+(Laskin, 2003; Meerschaert et al., 2011), which is a renewal process
+with Mittag-Leffler distributed waiting times. The family of
+Mittag-Leffler distributions nests the exponential distribution (Haubold
+et al., 2011), and hence the fractional Poisson process generalizes the
+standard Poisson process. Again as the threshold size increases and the
+threshold crossing probability \(p\) decreases, the fractional Poisson
+process is rarefied: The scale parameter of the Mittag-Leffler
+inter-arrival times of threshold crossing times increases, but
+\emph{superlinearly}; see the Theorem below.
 
@@
 heavy-tailed waiting times have been studied under the names
-``Continuous Time Random Maxima process'' (CTRM) (Benson, Schumer, and
-Meerschaert 2007; Meerschaert and Stoev 2008; Hees and Scheffler 2018b,
-2018a), ``Max-Renewal process'' (Silvestrov 2002; Silvestrov and Teugels
-2004; Basrak and Špoljarić 2015), and ``Shock process'' (Esary and
-Marshall 1973; Shanthikumar and Sumita 1983, 1984, 1985; Anderson 1987;
-Gut and Hüsler 1999). The existing literature focuses on probabilistic
+``Continuous Time Random Maxima process'' (CTRM) (Benson et al., 2007;
+Hees and Scheffler, 2018a, 2018b; Meerschaert and Stoev, 2008),
+``Max-Renewal process'' (Basrak and Špoljarić, 2015; Silvestrov, 2002;
+Silvestrov and Teugels, 2004), and ``Shock process'' (Anderson, 1987;
+Esary and Marshall, 1973; Gut and Hüsler, 1999; Shanthikumar and Sumita,
+1985, 1984, 1983). The existing literature focuses on probabilistic
 results surrounding these models. In this work, however, we introduce a
@@
 conclusion in Section 9. For all statistical computations we have used R
-(R Core Team 2018). All code and data used for the analysis in this
+(R Core Team, 2018). All code and data used for the analysis in this
 article has been organized into an R package \texttt{CTRE}
@@
 time series of solar flare intensities derived from a NASA dataset
-(Dennis et al. 1991) which we will later examine more closely (see
+(Dennis et al., 1991) which we will later examine more closely (see
 Section 7). Clearly, the simulated data exhibit long intervals
@@
 accessible introduction to regular variation and stable limit theorems,
-we recommend the book by Mark M Meerschaert and Sikorskii (2012).
+we recommend the book by Meerschaert and Sikorskii (2012).
 
@@
 T(\ell) > t \quad \text{ if and only if } \quad V(t) \le \ell.
-\] By (Theorem 3.1, Meerschaert and Stoev 2008), we have the stochastic
+\] By (Theorem 3.1, Meerschaert and Stoev, 2008), we have the stochastic
 process convergence \[
@@
 = \mathbf P[(-\log F(\ell^*))^{-1/\beta} X^{1/\beta} D > t]
-\] by (Proposition 4.2, Meerschaert and Stoev 2008), where \(X\) is an
+\] by (Proposition 4.2, Meerschaert and Stoev, 2008), where \(X\) is an
 exponential random variable with mean \(1\). Using (Theorem 19.1,
-Haubold, Mathai, and Saxena 2011), we see that
+Haubold et al., 2011), we see that
 \(X^{1/\beta} D \sim {\rm ML}(\beta, 1)\), concluding the proof. \qed
@@
 purposes of applied statistics. For a detailed reference on the
-Mittag-Leffler distribution, see e.g.~ Haubold, Mathai, and Saxena
-(2011), and for algorithms, see e.g.~the R package
-\texttt{MittagLeffleR} (Gill and Straka 2017).
+Mittag-Leffler distribution, see e.g.~ Haubold et al. (2011), and for
+algorithms, see e.g.~the R package \texttt{MittagLeffleR} (Gill and
+Straka, 2017).
 
@@
 drawback of this method is that constant priors for the tail parameter
-are needed for the calculation of the estimates. Cahoy, Uchaikin, and
-Woyczynski (2010) proposed a moment estimator of the log-transformed
-data, which does not require any prior. Furthermore, they performed
-simulation studies illustrating that the log-moment outperforms the
-fractional moment estimator with respect to bias and root mean squared
-error (RMSE).
+are needed for the calculation of the estimates. Cahoy et al. (2010)
+proposed a moment estimator of the log-transformed data, which does not
+require any prior. Furthermore, they performed simulation studies
+illustrating that the log-moment outperforms the fractional moment
+estimator with respect to bias and root mean squared error (RMSE).
 
@@
 there exists no closed form for the Maximum Likelihood estimator (MLE).
-In the R Package \texttt{MittagLeffleR} (Gill and Straka 2017), Maximum
+In the R Package \texttt{MittagLeffleR} (Gill and Straka, 2017), Maximum
 Likelihood estimation is implemented via numerical optimization. The MLE
@@
 estimators for the estimation of the parameter \(\beta\) such as the
-Hill estimator (Hill 1975) based on the \(r+1\) upper order statistics
+Hill estimator (Hill, 1975) based on the \(r+1\) upper order statistics
 \begin{align}\label{eq:hill}
@@
 \eqref{eq:hill}. Additionaly, the estimator only performs reliably well
-for distributions close to Pareto (see Resnick 1997). Figure
+for distributions close to Pareto (see Resnick, 1997). Figure
 \ref{fig:Hillplots} shows Hill plots for Mittag-Leffler simulated data,
@@
 boundary of the parameter space \((0,1]\). Instead, a valid approach is
-a bootstrapped Likelihood-ratio test (see e.g.~Davison, Hinkley, and
-others 1997). Figure \ref{Fig:LRT} displays the (simulated) power for
-the bootstrapped LRT for Mittag-Leffler distributions with varying tail
-parameters based on 1000 simulation runs. As expected, the power
-decreases for tail parameters close to one, since the Mittag-Leffler
-distribution converges as \(\beta \uparrow 1\) to an exponential
-distribution; it becomes hard to differentiate a Mittag-Lefller
-distribution from an exponential.
+a bootstrapped Likelihood-ratio test (see e.g.~Davison et al., 1997).
+Figure \ref{Fig:LRT} displays the (simulated) power for the bootstrapped
+LRT for Mittag-Leffler distributions with varying tail parameters based
+on 1000 simulation runs. As expected, the power decreases for tail
+parameters close to one, since the Mittag-Leffler distribution converges
+as \(\beta \uparrow 1\) to an exponential distribution; it becomes hard
+to differentiate a Mittag-Lefller distribution from an exponential.
 
@@
 quick estimates of the Mittag-Leffler parameters we have used the method
-of log-transformed moments (Cahoy 2013). We have verified the validity
+of log-transformed moments (Cahoy, 2013). We have verified the validity
 of our estimation algorithm via simulations, see Section
@@
 Taqqu (1994), a few lines of calculation (see e.g.~the vignette on
-parametrisation in Gill and Straka 2017) show that \(D\) must have the
+parametrisation in Gill and Straka, 2017) show that \(D\) must have the
 stable distribution \(S_\beta(\cos(\pi \beta/2)^{1/\beta}, +1, 0)\),
-which is implemented in the R package \texttt{stabledist} by Wuertz,
-Maechler, and members. (2016). By the Theorem, the distribution of
-\(T(\ell)\) is approximately \[
+which is implemented in the R package \texttt{stabledist} by Wuertz et
+al. (2016). By the Theorem, the distribution of \(T(\ell)\) is
+approximately \[
 {\rm ML}(\beta, p^{-1/\beta}) 
@@
 derived from the asymptotic normality of the log-moments estimators
-(Cahoy 2013) and the \(\delta\)-method (Gill and Straka 2017), dashed
+(Cahoy, 2013) and the \(\delta\)-method (Gill and Straka, 2017), dashed
 lines show the deduced values of \(\beta\) resp.~\(\sigma_0\). The
@@
 interesting open problem to develop quality criteria, based e.g.~on
-measures of surprise (Lee, Fan, and Sisson 2015), which guide an applied
+measures of surprise (Lee et al., 2015), which guide an applied
 statistician in the choice between a clustering and a CTRE approach for
@@
 time scales, and is truncated (or tempered, reverting to an exponential
-distribution) at very long time scales (see e.g.~Mark M. Meerschaert,
-Roy, and Shao 2012; and Aban, Meerschaert, and Panorska 2006). In such
-situations, a ``tempered'' Mittag-Leffler distribution may provide a
-more realistic fit, which we aim to introduce in follow-up work.
+distribution) at very long time scales (see e.g.~Meerschaert et al.,
+2012; and Aban et al., 2006). In such situations, a ``tempered''
+Mittag-Leffler distribution may provide a more realistic fit, which we
+aim to introduce in follow-up work.
 
@@
 \leavevmode\hypertarget{ref-Aban06}{}%
-Aban, Inmaculada B, Mark M Meerschaert, and Anna K Panorska. 2006.
-``Parameter Estimation for the Truncated Pareto Distribution.'' \emph{J.
-Am. Stat. Assoc.} 101 (473): 270--77.
-\url{https://doi.org/10.1198/016214505000000411}.
+Aban, I.B., Meerschaert, M.M., Panorska, A.K., 2006. Parameter
+estimation for the truncated pareto distribution. J. Am. Stat. Assoc.
+101, 270--277.
+doi:\href{https://doi.org/10.1198/016214505000000411}{10.1198/016214505000000411}
 
 \leavevmode\hypertarget{ref-Anderson1987}{}%
-Anderson, Kevin K. 1987. ``Limit Theorems for General Shock Models with
-Infinite Mean Intershock Times.'' \emph{J. Appl. Probab.} 24 (2):
-449--56. \url{http://www.jstor.org/stable/3214268}.
+Anderson, K.K., 1987. Limit Theorems for General Shock Models with
+Infinite Mean Intershock Times. J. Appl. Probab. 24, 449--456.
 
 \leavevmode\hypertarget{ref-Bagrow2013}{}%
-Bagrow, James P., and Dirk Brockmann. 2013. ``Natural emergence of
-clusters and bursts in network evolution.'' \emph{Phys. Rev. X} 3 (2):
-1--6. \url{https://doi.org/10.1103/PhysRevX.3.021016}.
+Bagrow, J.P., Brockmann, D., 2013. Natural emergence of clusters and
+bursts in network evolution. Phys. Rev. X 3, 1--6.
+doi:\href{https://doi.org/10.1103/PhysRevX.3.021016}{10.1103/PhysRevX.3.021016}
 
 \leavevmode\hypertarget{ref-Barabasi2005}{}%
-Barabási, Albert László. 2005. ``The origin of bursts and heavy tails in
-human dynamics.'' \emph{Nature} 435 (May): 207--11.
-\url{https://doi.org/10.1038/nature03459}.
+Barabási, A.L., 2005. The origin of bursts and heavy tails in human
+dynamics. Nature 435, 207--211.
+doi:\href{https://doi.org/10.1038/nature03459}{10.1038/nature03459}
 
 \leavevmode\hypertarget{ref-Basrak2014}{}%
-Basrak, Bojan, and Drago Špoljarić. 2015. ``Extremes of random variables
-observed in renewal times.'' \emph{Stat. Probab. Lett.} 97: 216--21.
-\url{https://doi.org/10.1016/j.spl.2014.11.025}.
+Basrak, B., Špoljarić, D., 2015. Extremes of random variables observed
+in renewal times. Stat. Probab. Lett. 97, 216--221.
+doi:\href{https://doi.org/10.1016/j.spl.2014.11.025}{10.1016/j.spl.2014.11.025}
 
 \leavevmode\hypertarget{ref-beirlantBook}{}%
-Beirlant, Jan, Yuri Goegebeur, Johan Segers, and Jozef Teugels. 2006.
-\emph{Statistics of extremes: theory and applications}. John Wiley \&
-Sons.
+Beirlant, J., Goegebeur, Y., Segers, J., Teugels, J., 2006. Statistics
+of extremes: theory and applications. John Wiley \& Sons.
 
 \leavevmode\hypertarget{ref-Benson2007}{}%
-Benson, David A, Rina Schumer, and Mark M Meerschaert. 2007.
-``Recurrence of extreme events with power-law interarrival times.''
-\emph{Geophys. Res. Lett.} 34 (l16404): DOI:10.1029/2007GL030767.
-\url{https://doi.org/10.1029/2007GL030767}.
+Benson, D.A., Schumer, R., Meerschaert, M.M., 2007. Recurrence of
+extreme events with power-law interarrival times. Geophys. Res. Lett.
+34, DOI:10.1029/2007GL030767.
+doi:\href{https://doi.org/10.1029/2007GL030767}{10.1029/2007GL030767}
 
 \leavevmode\hypertarget{ref-Cahoy2013}{}%
-Cahoy, Dexter O. 2013. ``Estimation of Mittag-Leffler Parameters.''
-\emph{Commun. Stat. - Simul. Comput.} 42 (2): 303--15.
-\url{https://doi.org/10.1080/03610918.2011.640094}.
+Cahoy, D.O., 2013. Estimation of Mittag-Leffler Parameters. Commun.
+Stat. - Simul. Comput. 42, 303--315.
+doi:\href{https://doi.org/10.1080/03610918.2011.640094}{10.1080/03610918.2011.640094}
 
 \leavevmode\hypertarget{ref-Cahoy2010}{}%
-Cahoy, Dexter O, Vladimir V. Uchaikin, and Wojbor A. Woyczynski. 2010.
-``Parameter estimation for fractional Poisson processes.'' \emph{J.
-Stat. Plan. Inference} 140 (11): 3106--20.
-\url{https://doi.org/10.1016/j.jspi.2010.04.016}.
+Cahoy, D.O., Uchaikin, V.V., Woyczynski, W.A., 2010. Parameter
+estimation for fractional Poisson processes. J. Stat. Plan. Inference
+140, 3106--3120.
+doi:\href{https://doi.org/10.1016/j.jspi.2010.04.016}{10.1016/j.jspi.2010.04.016}
 
 \leavevmode\hypertarget{ref-ColesBook}{}%
-Coles, S. 2001. \emph{An Introduction to Statistical Modelling of
-Extreme Values}. London: Springer-Verlag.
+Coles, S., 2001. An Introduction to Statistical Modelling of Extreme
+Values. Springer-Verlag, London.
 
 \leavevmode\hypertarget{ref-davison1997bootstrap}{}%
-Davison, Anthony Christopher, David Victor Hinkley, and others. 1997.
-\emph{Bootstrap Methods and Their Application}. Vol. 1. Cambridge
-university press.
+Davison, A.C., Hinkley, D.V., others, 1997. Bootstrap methods and their
+application. Cambridge university press.
 
 \leavevmode\hypertarget{ref-HXRBS}{}%
-Dennis, Brian R, L E Orwig, G S Kennard, G J Labow, R A Schwartz, A R
-Shaver, and A K Tolbert. 1991. ``The complete Hard X Ray Burst
-Spectrometer event list, 1980-1989.''
-\url{https://umbra.nascom.nasa.gov/smm/hxrbs.html}.
+Dennis, B.R., Orwig, L.E., Kennard, G.S., Labow, G.J., Schwartz, R.A.,
+Shaver, A.R., Tolbert, A.K., 1991. The complete Hard X Ray Burst
+Spectrometer event list, 1980-1989.
 
 \leavevmode\hypertarget{ref-Esary1973}{}%
-Esary, J. D., and A. W. Marshall. 1973. ``Shock Models and Wear
-Processes.'' \url{https://doi.org/10.1214/aop/1176996891}.
+Esary, J.D., Marshall, A.W., 1973. Shock Models and Wear Processes.
+doi:\href{https://doi.org/10.1214/aop/1176996891}{10.1214/aop/1176996891}
 
 \leavevmode\hypertarget{ref-ferro2003inference}{}%
-Ferro, Christopher AT, and Johan Segers. 2003. ``Inference for Clusters
-of Extreme Values.'' \emph{Journal of the Royal Statistical Society:
-Series B (Statistical Methodology)} 65 (2): 545--56.
+Ferro, C.A., Segers, J., 2003. Inference for clusters of extreme values.
+Journal of the Royal Statistical Society: Series B (Statistical
+Methodology) 65, 545--556.
 
 \leavevmode\hypertarget{ref-MittagLeffleR}{}%
-Gill, Gurtek, and Peter Straka. 2017. \emph{MittagLeffleR: Using the
-Mittag-Leffler Distributions in R}.
-\url{https://strakaps.github.io/MittagLeffleR/}.
+Gill, G., Straka, P., 2017. MittagLeffleR: Using the mittag-leffler
+distributions in r.
 
 \leavevmode\hypertarget{ref-Gut1999}{}%
-Gut, Allan, and Jürg Hüsler. 1999. ``Extreme Shock Models.''
-\emph{Extremes}, no. 1983: 295--307.
-\url{http://link.springer.com/article/10.1023/A:1009959004020}.
+Gut, A., Hüsler, J., 1999. Extreme Shock Models. Extremes 295--307.
 
 \leavevmode\hypertarget{ref-Haubold11}{}%
-Haubold, H. J., A. M. Mathai, and R. K. Saxena. 2011. ``Mittag-Leffler
-Functions and Their Applications.'' \emph{J. Appl. Math.} 2011: 1--51.
-\url{https://doi.org/10.1155/2011/298628}.
+Haubold, H.J., Mathai, A.M., Saxena, R.K., 2011. Mittag-Leffler
+Functions and Their Applications. J. Appl. Math. 2011, 1--51.
+doi:\href{https://doi.org/10.1155/2011/298628}{10.1155/2011/298628}
 
 \leavevmode\hypertarget{ref-hawkes1971point}{}%
-Hawkes, Alan G. 1971. ``Point spectra of some mutually exciting point
-processes.'' \emph{J. R. Stat. Soc. Ser. B Stat. Methodol.}, 438--43.
+Hawkes, A.G., 1971. Point spectra of some mutually exciting point
+processes. J. R. Stat. Soc. Ser. B Stat. Methodol. 438--443.
+
+\leavevmode\hypertarget{ref-hees2016joint}{}%
+Hees, K., Scheffler, H.-P., 2018a. On joint sum/max stability and
+sum/max domains of attraction. Probability and Mathematical Statistics
+38.
 
 \leavevmode\hypertarget{ref-hees2017coupled}{}%
-Hees, Katharina, and Hans-Peter Scheffler. 2018a. ``Coupled Continuous
-Time Random Maxima.'' \emph{Extremes} 21 (2).
-
-\leavevmode\hypertarget{ref-hees2016joint}{}%
----------. 2018b. ``On Joint Sum/Max Stability and Sum/Max Domains of
-Attraction.'' \emph{Probability and Mathematical Statistics} 38 (1).
+Hees, K., Scheffler, H.-P., 2018b. Coupled continuous time random
+maxima. Extremes 21.
 
 \leavevmode\hypertarget{ref-hill1975simple}{}%
-Hill, Bruce M. 1975. ``A Simple General Approach to Inference About the
-Tail of a Distribution.'' \emph{The Annals of Statistics}, 1163--74.
+Hill, B.M., 1975. A simple general approach to inference about the tail
+of a distribution. The annals of statistics 1163--1174.
 
 \leavevmode\hypertarget{ref-Karsai2012}{}%
-Karsai, Márton, Kimmo Kaski, Albert László Barabási, and János Kertész.
-2012. ``Universal features of correlated bursty behaviour.'' \emph{Sci.
-Rep.} 2. \url{https://doi.org/10.1038/srep00397}.
+Karsai, M., Kaski, K., Barabási, A.L., Kertész, J., 2012. Universal
+features of correlated bursty behaviour. Sci. Rep. 2.
+doi:\href{https://doi.org/10.1038/srep00397}{10.1038/srep00397}
 
 \leavevmode\hypertarget{ref-Karsai2011}{}%
-Karsai, Márton, M. Kivelä, R. K. Pan, K. Kaski, J. Kertész, Albert
-László Barabási, and J. Saramäki. 2011. ``Small but slow world: How
-network topology and burstiness slow down spreading.'' \emph{Phys. Rev.
-E - Stat. Nonlinear, Soft Matter Phys.} 83: 1--4.
-\url{https://doi.org/10.1103/PhysRevE.83.025102}.
+Karsai, M., Kivelä, M., Pan, R.K., Kaski, K., Kertész, J., Barabási,
+A.L., Saramäki, J., 2011. Small but slow world: How network topology and
+burstiness slow down spreading. Phys. Rev. E - Stat. Nonlinear, Soft
+Matter Phys. 83, 1--4.
+doi:\href{https://doi.org/10.1103/PhysRevE.83.025102}{10.1103/PhysRevE.83.025102}
 
 \leavevmode\hypertarget{ref-kozubowski2001}{}%
-Kozubowski, Tomasz J. 2001. ``Fractional Moment Estimation of Linnik and
-Mittag-Leffler Parameters.'' \emph{Mathematical and Computer Modelling}
-34 (9-11): 1023--35.
+Kozubowski, T.J., 2001. Fractional moment estimation of linnik and
+mittag-leffler parameters. Mathematical and computer modelling 34,
+1023--1035.
 
 \leavevmode\hypertarget{ref-Laskin2003}{}%
-Laskin, Nick. 2003. ``Fractional Poisson process.'' \emph{Commun.
-Nonlinear Sci. Numer. Simul.} 8 (3-4): 201--13.
-\url{https://doi.org/10.1016/S1007-5704(03)00037-6}.
+Laskin, N., 2003. Fractional Poisson process. Commun. Nonlinear Sci.
+Numer. Simul. 8, 201--213.
+doi:\href{https://doi.org/10.1016/S1007-5704(03)00037-6}{10.1016/S1007-5704(03)00037-6}
 
 \leavevmode\hypertarget{ref-Lee15}{}%
-Lee, J., Y. Fan, and S. A. Sisson. 2015. ``Bayesian threshold selection
-for extremal models using measures of surprise.'' \emph{Comput. Stat.
-Data Anal.} 85: 84--99.
-\url{https://doi.org/10.1016/j.csda.2014.12.004}.
+Lee, J., Fan, Y., Sisson, S.A., 2015. Bayesian threshold selection for
+extremal models using measures of surprise. Comput. Stat. Data Anal. 85,
+84--99.
+doi:\href{https://doi.org/10.1016/j.csda.2014.12.004}{10.1016/j.csda.2014.12.004}
 
 \leavevmode\hypertarget{ref-Meerschaert2010b}{}%
-Meerschaert, Mark M, Erkan Nane, and P. Vellaisamy. 2011. ``The
-fractional Poisson process and the inverse stable subordinator.''
-\emph{Electron. J. Probab.} 16: 1600--1620.
-\url{https://doi.org/10.1214/EJP.v16-920}.
+Meerschaert, M.M., Nane, E., Vellaisamy, P., 2011. The fractional
+Poisson process and the inverse stable subordinator. Electron. J.
+Probab. 16, 1600--1620.
+doi:\href{https://doi.org/10.1214/EJP.v16-920}{10.1214/EJP.v16-920}
 
 \leavevmode\hypertarget{ref-MeerschaertRoyQin}{}%
-Meerschaert, Mark M., Parthanil Roy, and Qin Shao. 2012. ``Parameter
-estimation for exponentially tempered power law distributions.''
-\emph{Commun. Stat. - Theory Methods} 41 (10): 1839--56.
-\url{https://doi.org/10.1080/03610926.2011.552828}.
+Meerschaert, M.M., Roy, P., Shao, Q., 2012. Parameter estimation for
+exponentially tempered power law distributions. Commun. Stat. - Theory
+Methods 41, 1839--1856.
+doi:\href{https://doi.org/10.1080/03610926.2011.552828}{10.1080/03610926.2011.552828}
 
 \leavevmode\hypertarget{ref-MeerschaertSikorskii}{}%
-Meerschaert, Mark M, and Alla Sikorskii. 2012. \emph{Stochastic Models
-for Fractional Calculus}. Vol. 43. Walter de Gruyter.
+Meerschaert, M.M., Sikorskii, A., 2012. Stochastic models for fractional
+calculus. Walter de Gruyter.
 
 \leavevmode\hypertarget{ref-MeerschaertStoev08}{}%
-Meerschaert, Mark M, and Stilian A Stoev. 2008. ``Extremal limit
-theorems for observations separated by random power law waiting times.''
-\emph{J. Stat. Plan. Inference} 139 (7): 2175--88.
-\url{https://doi.org/10.1016/j.jspi.2008.10.005}.
+Meerschaert, M.M., Stoev, S.A., 2008. Extremal limit theorems for
+observations separated by random power law waiting times. J. Stat. Plan.
+Inference 139, 2175--2188.
+doi:\href{https://doi.org/10.1016/j.jspi.2008.10.005}{10.1016/j.jspi.2008.10.005}
 
 \leavevmode\hypertarget{ref-Min2010}{}%
-Min, Byungjoon, K. I. Goh, and Alexei Vazquez. 2011. ``Spreading
-dynamics following bursty human activity patterns.'' \emph{Phys. Rev. E
-- Stat. Nonlinear, Soft Matter Phys.} 83 (3): 2--5.
-\url{https://doi.org/10.1103/PhysRevE.83.036102}.
+Min, B., Goh, K.I., Vazquez, A., 2011. Spreading dynamics following
+bursty human activity patterns. Phys. Rev. E - Stat. Nonlinear, Soft
+Matter Phys. 83, 2--5.
+doi:\href{https://doi.org/10.1103/PhysRevE.83.036102}{10.1103/PhysRevE.83.036102}
 
 \leavevmode\hypertarget{ref-Oliveira2005}{}%
-Oliveira, J, and Albert László Barabási. 2005. ``Darwin and Einstein
-correspondence patterns.'' \emph{Nature} 437 (October): 1251.
-\url{https://doi.org/10.0138/4371251a}.
+Oliveira, J., Barabási, A.L., 2005. Darwin and Einstein correspondence
+patterns. Nature 437, 1251.
+doi:\href{https://doi.org/10.0138/4371251a}{10.0138/4371251a}
 
 \leavevmode\hypertarget{ref-Omi2011}{}%
-Omi, Takahiro, and Shigeru Shinomoto. 2011. ``Optimizing Time Histograms
-for Non-Poissonian Spike Trains.'' \emph{Neural Comput.} 23 (12):
-3125--44. \url{https://doi.org/10.1162/NECO_a_00213}.
+Omi, T., Shinomoto, S., 2011. Optimizing Time Histograms for
+Non-Poissonian Spike Trains. Neural Comput. 23, 3125--3144.
+doi:\href{https://doi.org/10.1162/NECO_a_00213}{10.1162/NECO\_a\_00213}
 
 \leavevmode\hypertarget{ref-Hsing88}{}%
-``On the Exceedance Point Process for a Stationary Sequence.'' 1988 78:
+On the Exceedance Point Process for a Stationary Sequence, 1988. 78,
 97--112.
@@
 \leavevmode\hypertarget{ref-R}{}%
-R Core Team. 2018. \emph{R: A Language and Environment for Statistical
-Computing}. Vienna, Austria: R Foundation for Statistical Computing.
-\url{https://www.R-project.org/}.
+R Core Team, 2018. R: A language and environment for statistical
+computing. R Foundation for Statistical Computing, Vienna, Austria.
 
 \leavevmode\hypertarget{ref-Resnick97}{}%
-Resnick, Sidney I. 1997. ``Heavy tail modeling and teletraffic data.''
-\emph{Ann. Stat.} 25 (5): 1805--49.
-\url{https://doi.org/10.1214/aos/1069362376}.
+Resnick, S.I., 1997. Heavy tail modeling and teletraffic data. Ann.
+Stat. 25, 1805--1849.
+doi:\href{https://doi.org/10.1214/aos/1069362376}{10.1214/aos/1069362376}
 
 \leavevmode\hypertarget{ref-SamorodnitskyTaqqu}{}%
-Samorodnitsky, Gennady, and Murad S Taqqu. 1994. \emph{Stable
-Non-Gaussian Random Processes: Stochastic Models with Infinite
-Variance}. Stochastic Modeling. London: Chapman Hall.
+Samorodnitsky, G., Taqqu, M.S., 1994. Stable Non-Gaussian Random
+Processes: Stochastic Models with Infinite Variance, Stochastic
+modeling. Chapman Hall, London.
 
 \leavevmode\hypertarget{ref-Sumita1983}{}%
-Shanthikumar, J. George, and Ushio Sumita. 1983. ``General shock models
-associated with correlated renewal sequences.'' \emph{J. Appl. Probab.}
-20 (3): 600--614. \url{http://www.jstor.org/stable/3213896}.
+Shanthikumar, J.G., Sumita, U., 1983. General shock models associated
+with correlated renewal sequences. J. Appl. Probab. 20, 600--614.
 
 \leavevmode\hypertarget{ref-Sumita1984}{}%
----------. 1984. ``Distribution Properties of the System Failure Time in
-a General Shock Model.'' \emph{Adv. Appl. Probab.} 16 (2): 363--77.
-\url{http://www.jstor.org/stable/1427074}.
+Shanthikumar, J.G., Sumita, U., 1984. Distribution Properties of the
+System Failure Time in a General Shock Model. Adv. Appl. Probab. 16,
+363--377.
 
 \leavevmode\hypertarget{ref-Sumita1985}{}%
----------. 1985. ``A class of correlated cumulative shock models.''
-\emph{Adv. Appl. Probab.} 17 (2): 347--66.
-\url{http://www.jstor.org/stable/1427145}.
+Shanthikumar, J.G., Sumita, U., 1985. A class of correlated cumulative
+shock models. Adv. Appl. Probab. 17, 347--366.
 
 \leavevmode\hypertarget{ref-Silvestrov2002a}{}%
-Silvestrov, Dmitrii S. 2002. \emph{Limit Theorems for Randomly Stopped
-Stochastic Processes}. Springer (Berlin, Heidelberg).
+Silvestrov, D.S., 2002. Limit Theorems for Randomly Stopped Stochastic
+Processes. Springer (Berlin, Heidelberg).
 
 \leavevmode\hypertarget{ref-ST04}{}%
-Silvestrov, Dmitrii S, and Jozef L. Teugels. 2004. ``Limit theorems for
-mixed max-sum processes with renewal stopping.'' \emph{Ann. Appl.
-Probab.} 14 (4): 1838--68.
-\url{https://doi.org/10.1214/105051604000000215}.
+Silvestrov, D.S., Teugels, J.L., 2004. Limit theorems for mixed max-sum
+processes with renewal stopping. Ann. Appl. Probab. 14, 1838--1868.
+doi:\href{https://doi.org/10.1214/105051604000000215}{10.1214/105051604000000215}
 
 \leavevmode\hypertarget{ref-Vajna2013}{}%
-Vajna, Szabolcs, Bálint Tóth, and János Kertész. 2013. ``Modelling
-bursty time series.'' \emph{New J. Phys.} 15 (10): 103023.
-\url{https://doi.org/10.1088/1367-2630/15/10/103023}.
+Vajna, S., Tóth, B., Kertész, J., 2013. Modelling bursty time series.
+New J. Phys. 15, 103023.
+doi:\href{https://doi.org/10.1088/1367-2630/15/10/103023}{10.1088/1367-2630/15/10/103023}
 
 \leavevmode\hypertarget{ref-Vasquez2006}{}%
-Vasquez, a, J G Oliveira, Z Dezso, K-I Goh, I Kondor, and Albert László
-Barabási. 2006. ``Modeling bursts and heavy tails in human dynamics.''
-\emph{Phys. Rev. E} 73: 361271--3612718.
-\url{http://arxiv.org/abs/0510117v1}.
+Vasquez, a, Oliveira, J.G., Dezso, Z., Goh, K.-I., Kondor, I., Barabási,
+A.L., 2006. Modeling bursts and heavy tails in human dynamics. Phys.
+Rev. E 73, 361271--3612718.
 
 \leavevmode\hypertarget{ref-Vazquez2007}{}%
-Vazquez, Alexei, Balázs Rácz, András Lukács, and Albert László Barabási.
-2007. ``Impact of non-poissonian activity patterns on spreading
-processes.'' \emph{Phys. Rev. Lett.} 98 (APRIL): 1--4.
-\url{https://doi.org/10.1103/PhysRevLett.98.158702}.
+Vazquez, A., Rácz, B., Lukács, A., Barabási, A.L., 2007. Impact of
+non-poissonian activity patterns on spreading processes. Phys. Rev.
+Lett. 98, 1--4.
+doi:\href{https://doi.org/10.1103/PhysRevLett.98.158702}{10.1103/PhysRevLett.98.158702}
 
 \leavevmode\hypertarget{ref-stabledist}{}%
-Wuertz, Diethelm, Martin Maechler, and Rmetrics core team members. 2016.
-\emph{Stabledist: Stable Distribution Functions}.
-\url{https://CRAN.R-project.org/package=stabledist}.
+Wuertz, D., Maechler, M., members., R. core team, 2016. Stabledist:
+Stable distribution functions.
 

### 2020-02-29 article_springer/article_springer_files/ML_estim_simu/ML_estim_simustudy.R

@@ -12,9 +12,9 @@ library(ggplot2)
 
 plan(multiprocess)
 
-tails <- seq(0.2,0.9,0.1)
-scales <- c(0.1,1,10)
-ns <- seq(25,200,25)
+tails <-0.2# c(0.2,0.8) #seq(0.2,0.9,0.1)
+scales <- 1 #c(0.1,1,10)
+ns <-25# seq(25,200,25)
 m<-1000
 
 pb <- progress_bar$new(total = length(tails)*length(scales)*length(ns), format = "[:bar] tail: :tail, scale: :scale, n: :n")

### 2020-03-01 article_springer/article_springer.Rmd
Cleaned Up
First changes (addressing Reviewer 2)

@@
 bibliography: CTRMstats.bib
-csl: 
+csl: elsevier-harvard.csl
 output: 
   rticles::elsevier_article:
+    number_sections: true
     fig_caption: yes
-                number_sections: true
 
@@
 Then as one increases the threshold and thus decreases the threshold 
-crossing probability $p$, the Poisson process is rarefied, i.e. its 
-intensity decreases _linearly_ with $p$ [see e.g. @beirlantBook].
+crossing probability $p_{\ell}$, the Poisson process is rarefied, i.e. its 
+intensity decreases _linearly_ with $p_{\ell}$ [see e.g. @beirlantBook].
 
@@
 Again as the threshold size increases and the threshold crossing
-probability $p$ decreases, the fractional Poisson process is rarefied: 
+probability $p_{\ell}$ decreases, the fractional Poisson process is rarefied: 
 The scale parameter of the Mittag-Leffler inter-arrival times of 
@@
 
-: Let $(W,J), (W_1, J_1), (W_2, J_2), \ldots$ be i.i.d. pairs of random 
-variables, where the $W_k > 0$ are interpreted as the *waiting times* 
-and $J_k \in [x_L, x_R]$ as the *event magnitudes* 
-($x_L \in [-\infty, +\infty), x_R \in (-\infty, +\infty]$). 
-If $W$ and $J$ are independent, the Marked Renewal Process is said to be *uncoupled*.
+: Let $(W,J), (W_1, J_1), (W_2, J_2), \ldots$ be i.i.d. pairs of random variables, where the $W_k > 0$ are interpreted as the *waiting times* 
+and $J_k \in \mathbb{R}$ as the *event magnitudes*. If $W$ and $J$ are independent, the Marked Renewal Process is said to be *uncoupled*.
 
+In the following we denote with $x_L \in [-\infty, +\infty)$ and $x_R \in (-\infty, +\infty]$) the left and right endpoint of the distribution of $J$.
 We assume that the $k$-th magnitude $J_k$ occurs at time
@@
 called the "inter-arrival times" and the "exceedances", respectively.
-The pair sequence $(T(\ell, n), W(\ell, n))_{n \in \mathbb N}$ is called 
+The pair sequence $(X(\ell, n), T(\ell, n))_{n \in \mathbb N}$ is called 
 a Continuous Time Random Exceedance model (CTRE). 
@@
 To see why, note that $X(\ell)$ is, in distribution, simply equal to $J - \ell | J > \ell$, independent of any waiting time $W_k$.
+We assume for the rest of the article, that the magnitudes $(J_i)_{i \in \mathbb{N}}$ belong to the the max-domain of attraction of some non-degenerate distribution.
+This means there exist $a_n>0$ and $d_n \in \mathbb{R}$ such that
+$$ a_n^{-1}(J_1 \vee \ldots \vee J_n -d_n) \Rightarrow A \text{ as } n \rightarrow \infty.$$
+Hence, the distribution of $A$ is a generalized extreme value distribution (GEV) which distribution function is given by 
+$$ F(x;\xi) = \begin{cases}\exp(-(1+\xi x)^{-1/\xi}) & \xi\neq0 \\ \exp(-\exp(-x)) & \xi = 0\end{cases}.$$ 
+The GEV is subdivided into the Gumbel ($\xi=0$), the Weibull ($\xi<0$) and the Fr'echet ($\xi>0$) family of distributions.
+
 Figure \ref{fig:thresholdedBursty} shows a simulated dataset in the top panel, where $W$ has a stable distribution with tail parameter $\beta =$ `r params$tail` (and skewness $1$ and location $0$), and where $J$ is from a standard Gumbel distribution.
@@
 \end{align}
-for a function $b(n)$ which is regularly varying at $\infty$ with parameter $1/\beta$, and where $\mathbf E[\exp(-sD)] = \exp(-s^\beta)$. Write $p := \mathbf P(J > \ell)$. Then the weak convergence
+for a function $b(n)$ which is regularly varying at $\infty$ with parameter $1/\beta$, and where $\mathbf E[\exp(-sD)] = \exp(-s^\beta)$.
+Write $p_{\ell} := \mathbf P(J > \ell)$.
+Then the weak convergence
 $$
-\frac{T(\ell)} {b(1/p)} \to W_\beta \quad \text{ as } \quad \ell \uparrow x_R
+\frac{T(\ell)} {b(1/p_{\ell})} \to Z_\beta \quad \text{ as } \quad \ell \uparrow x_R
 $$
-holds, where the Mittag-Leffler random variable $W_\beta$ is defined on 
+holds, where the Mittag-Leffler random variable $Z_\beta$ is defined on 
 the positive real numbers via 
 $$
-\mathbf E[\exp(-sW_\beta)] = \frac{1}{1+s^\beta}.
+\mathbf E[\exp(-sZ_\beta)] = \frac{1}{1+s^\beta}.
 $$
@@
 $$
-\mathbf P\left[ \frac{T(\ell)}{b(1/p)} > t \right]
-= \mathbf P[T(\ell) > b(1/p) t]
+\mathbf P\left[ \frac{T(\ell)}{b(1/p_{\ell})} > t \right]
+= \mathbf P[T(\ell) > b(1/p_{\ell}) t]
 = \mathbf P[V(ct) \le \ell]
 $$
-where we have substituted $c = b(1/p)$. Moreover 
+where we have substituted $c = b(1/p_{\ell})$. Moreover 
 $$
@@
 
-For a scale parameter $\sigma > 0$, we write ${\rm ML}(\beta, \sigma)$ for the distribution of $\sigma W_\beta$. The Mittag-Leffler distribution with parameter $\beta \in (0,1]$ is 
+For a scale parameter $\sigma > 0$, we write ${\rm ML}(\beta, \sigma)$ for the distribution of $\sigma Z_\beta$. The Mittag-Leffler distribution with parameter $\beta \in (0,1]$ is 
 a heavy-tailed positive distribution for $\beta < 1$, with infinite mean. 
@@
 
-The classical POT approach is based on the fact that exceedances above a high threshhold are asymptotically GPD distributed, hence a GPD distribution is fitted to the exceedances above a high enough threshhold.
+The classical POT approach is based on the fact that exceedances above a high threshold are asymptotically GPD distributed, hence a GPD distribution is fitted to the exceedances above a high enough threshold.
 Due to the Theorem in the last Section we know that for high thresholds the times between exceedances are asymptotically Mittag-Leffler distributed in case of heavy-tailed waiting times between the observations.
@@
 threshold $\ell$ we may approximate the distribution of $T(\ell)$ with an 
-${\rm ML}(\beta, b(1/p))$ distribution, 
+${\rm ML}(\beta, b(1/p_{\ell}))$ distribution, 
 where the function $b(c)$ varies regularly at $\infty$ with parameter $1/\beta$.
@@
 
-To clarify Step 4: Recall that by the theorem, $\sigma_k / b(1/p)$ is expected to stabilize 
+To clarify Step 4: Recall that by the theorem, $\sigma_k / b(1/p_{\ell})$ is expected to stabilize 
 around a constant as $k \downarrow K_0$. Since $b$ is regularly varying with parameter
-$1/\beta$, we have $b(1/p) = p^{-1/\beta} / L(1/p)$ for some slowly varying function $L$. 
-Approximating $p \approx \hat p := k / n$, we have 
-$$\text{const} \approx \sigma_k / b(1/p) = \sigma_k \times p^{1/\beta} L(1/p) \approx \sigma_k \times k^{1/\beta} n^{-1/\beta} L(n/k)$$
+$1/\beta$, we have $b(1/p_{\ell}) = p_{\ell}^{-1/\beta} / L(1/p_{\ell})$ for some slowly varying function $L$. 
+Approximating $p_{\ell} \approx \hat p_{\ell} := k / n$, we have 
+$$\text{const} \approx \sigma_k / b(1/p_{\ell}) = \sigma_k \times p_{\ell}^{1/\beta} L(1/p_{\ell}) \approx \sigma_k \times k^{1/\beta} n^{-1/\beta} L(n/k)$$
 Assuming that the variation of $L(n/k)$ is minor, we can hence see that 
@@
 $$
-{\rm ML}(\beta, p^{-1/\beta}) 
+{\rm ML}(\beta, p_{\ell}^{-1/\beta}) 
 = {\rm ML}(\beta, k^{-1/\beta} n^{1/\beta}),
@@
 the scale parameter stabilizes less obviously near $3 \times 10^7$ (dashed line).
-The growth of the scale parameter for lower threshold appears to be closer to linear in $p$, 
-rather than proportional to $p^{1/0.85}$ as suggested by the Mittag-Leffler
+The growth of the scale parameter for lower threshold appears to be closer to linear in $p_{\ell}$, 
+rather than proportional to $p_{\ell}^{1/0.85}$ as suggested by the Mittag-Leffler
 fits. The reason for this is likely that the overall goodness of fit as 
@@
 Unlike the exponential distribution, the Mittag-Leffler distribution is not memoryless, and the probability density of the time $t$ until the next threshold crossing will depend on the time $t_0$ elapsed since the last threshold crossing.
-This density equals 
+This density is approximately equal to 
 $$
-p(t|\beta, \sigma_0, \ell, t_0) = \frac{f(t + t_0 | \beta, k^{-1/\beta} \sigma_0)}{\mathbf P[T_\ell > t_0]}
+p(t|\beta, \sigma_0, \ell, t_0) \approx \frac{f(t + t_0 | \beta, k^{-1/\beta} \sigma_0)}{\mathbf P[T_\ell > t_0]}
 $$
@@
 Burstiness is characterized by power-law waiting times between events, and we have shown that the Mittag-Leffler distribution arises naturally as a scaling limit for the inter-exceedance times of high thresholds.
-Moreover, we have derived the following non-linear scaling behaviour: $\sigma \sim p^{-1/\beta}$, where $\sigma$ is the scale parameter of the distribution of threshold
-exceedance times, $p$ is the fraction of magnitudes above the threshold, and $\beta$ the exponent of the power law. 
+Moreover, we have derived the following non-linear scaling behaviour: $\sigma \sim p_{\ell}^{-1/\beta}$, where $\sigma$ is the scale parameter of the distribution of threshold
+exceedance times, $p_{\ell}$ is the fraction of magnitudes above the threshold, and $\beta$ the exponent of the power law. 
 This "anomalous" scaling behaviour in the bursty setting entails two phenomena:
@@
 Moreover, any data below a (minimum) threshold $\ell_0$ is discarded for CTREs, and hence need not satisfy the i.i.d.
-assumption.For the purposes of statistical inference, we merely require that the inter-threshold-crossing times are i.i.d.
+assumption.
+For the purposes of statistical inference, we merely require that the inter-threshold-crossing times are i.i.d.
 

### 2020-03-01 article_springer/article_springer.Rmd
Further changes

@@
 \mathbf P\left[ \frac{M(c) - d(c)}{a(c)} \le \ell^* \right] 
-\longrightarrow F(\ell^*), \quad t \to \infty
+\longrightarrow F(\ell^*), \quad c \to \infty
 $$
@@
 and that
-$$
-T(\ell) > t \quad \text{ if and only if } \quad V(t) \le \ell.
-$$
+
+\begin{align}
+T(\ell) > t \quad \text{ if and only if } \quad V(t) \le \ell. \label{inverserelat}
+\end{align}
+
 By [Theorem 3.1, @MeerschaertStoev08], we have the stochastic process 
 convergence
-$$
+
+\begin{align}
 \frac{V(ct) - d(\tilde b(c))}{a(\tilde b(c))} 
-\stackrel{d}{\longrightarrow} Y(t), \quad t > 0.
-$$
-where $Y(t)$ is a time-changed ("subordinated") extremal process, and where 
+\stackrel{d}{\longrightarrow} Y(t),  \quad c \to \infty, \label{TheoMS}
+\end{align}
+
+for $t > 0$, where $Y(t)$ is a time-changed ("subordinated") extremal process, and where 
 $\tilde b(c)$ is a regularly varying norming function which is
@@
 $$
-where we have substituted $c = b(1/p_{\ell})$. Moreover 
+where we have substituted $c = b(1/p_{\ell})$ and used \eqref{inverserelat}. Moreover, we receive due to the convergence in \eqref{TheoMS}
 $$
@@
 \le \frac{\ell - d(\tilde b(c))}{a(\tilde b(c))} \right]
-\longrightarrow \mathbf P\left[ Y(t) \le \ell^* \right]
+\longrightarrow \mathbf P\left[ Y(t) \le \ell^* \right] ,  \quad c \to \infty,
 $$
-Defining the hitting time of level $\ell^*$ by $Y(t)$ as 
+for $t>0$. Defining the hitting time of level $\ell^*$ by $Y(t)$ as 
 $\xi_{\ell^*} := \inf\{t: Y(t) > \ell^*\}$,
@@
 (i.e. the $K$ largest values, where e.g. $K = 300$) 
-$X_{(1)}, \ldots, X_{(K)}$ together with their timestamps $T_{(1)}, \ldots, T_{(K)}$.
+$X_{(1)}, \ldots, X_{(K)}$ together with their timestamps $T_{(1)}, \ldots, T_{(K-1)}$.
 
 2. Choose e.g. $K_0 = 5$, and for each $k$ ranging from $K_0 +1$ to $K + 1$: 
-    a) extract the set $\mathcal T_k$ of exceedance times of the threshold $X_{(k)}$
+    a) extract the set $\mathcal T_k$ of exceedance times of between the magnitudes exceeding the threshold $X_{(k)}$
     b) fit a Mittag-Leffler distribution to $\mathcal T_k$, resulting in the parameter
@@
 
-3. Plot $k$ vs.\ $\hat \beta_k$. As $k \downarrow K_0$,
-  $\hat \beta_k$ *stabilizes* around a constant $\hat \beta$.
+3.
+Plot $k$ vs.\ $\hat \beta_k$.
+To the right, as $k \downarrow K_0$, the asymptotics are off and bias is high.
+To the left (high threshold), data are scarce and variance is high.
+Choose a region of *stability* in the middle for a parameter estimate $\hat \beta$.
 
-4. Plot $k$ vs.\ $k^{1/\hat \beta} \hat \sigma_k$. 
-  Where the plot stabilizes as $k \downarrow K_0$, define the value 
-  $\hat \sigma_0$.
+4. Plot $k$ vs.\ $k^{1/\hat \beta} \hat \sigma_k$. Again, choose a region of *stability* as $k$ gets smaller and define $\hat \sigma_0$.
 
@@
 grid.arrange(
-  logMom_Ex1_tail,
-  mle_Ex1_tail,
-  hill_Ex1_tail,
-  logMom_Ex2_tail,
-  mle_Ex2_tail,
-  hill_Ex2_tail,
-  logMom_Ex3_tail,
-  mle_Ex3_tail,
-  hill_Ex3_tail,
-  ncol = 3
+  arrangeGrob(logMom_Ex1_tail,logMom_Ex2_tail,logMom_Ex3_tail,top="log-Moment"),
+  arrangeGrob(mle_Ex1_tail, mle_Ex2_tail, mle_Ex3_tail,top="MLE"),
+  arrangeGrob(hill_Ex1_tail,hill_Ex2_tail,hill_Ex3_tail,top="Hill"),
+  ncol=3
 )
-
 ```
@@
 grid.arrange(
-  logMom_Ex1_scale,
-  mle_Ex1_scale,
-  logMom_Ex2_scale,
-  mle_Ex2_scale,
-  logMom_Ex3_scale,
-  mle_Ex3_scale,
+  arrangeGrob(logMom_Ex1_scale,logMom_Ex2_scale,logMom_Ex3_scale,top="log-Mom"),
+  arrangeGrob(mle_Ex1_scale,mle_Ex2_scale,mle_Ex3_scale,top="MLE"),
   ncol = 2

### 2020-03-11 article_springer/article_springer.tex
changes.md --> cahnges.Rmd Rmarkdwon file, new format New Mittag Leffler simulation study, with m=5000

@@
     \author[c]{Peter Straka}
-   \ead{p.straka@unsw.edu.au} 
+   \ead{straka.ps@gmail.com} 
       \address[a]{Department of Statistics, TU Dortmund University, Dortmund, Germany}
@@
 one increases the threshold and thus decreases the threshold crossing
-probability \(p\), the Poisson process is rarefied, i.e.~its intensity
-decreases \emph{linearly} with \(p\) (see e.g.~Beirlant et al., 2006).
+probability \(p_{\ell}\), the Poisson process is rarefied, i.e.~its
+intensity decreases \emph{linearly} with \(p_{\ell}\) (see e.g.~Beirlant
+et al., 2006).
 
@@
 standard Poisson process. Again as the threshold size increases and the
-threshold crossing probability \(p\) decreases, the fractional Poisson
-process is rarefied: The scale parameter of the Mittag-Leffler
+threshold crossing probability \(p_{\ell}\) decreases, the fractional
+Poisson process is rarefied: The scale parameter of the Mittag-Leffler
 inter-arrival times of threshold crossing times increases, but
@@
 variables, where the \(W_k > 0\) are interpreted as the \emph{waiting
-times} and \(J_k \in [x_L, x_R]\) as the \emph{event magnitudes}
-(\(x_L \in [-\infty, +\infty), x_R \in (-\infty, +\infty]\)). If \(W\)
-and \(J\) are independent, the Marked Renewal Process is said to be
-\emph{uncoupled}.
+times} and \(J_k \in \mathbb{R}\) as the \emph{event magnitudes}. If
+\(W\) and \(J\) are independent, the Marked Renewal Process is said to
+be \emph{uncoupled}.
 \end{description}
 
-We assume that the \(k\)-th magnitude \(J_k\) occurs at time
-\(T_k = W_1 + \ldots + W_k\). Based on an MRP, we define the Continuous
-Time Random Exceedance model (CTRE) as follows:
+In the following we denote with \(x_L \in [-\infty, +\infty)\) and
+\(x_R \in (-\infty, +\infty]\)) the left and right endpoint of the
+distribution of \(J\). We assume that the \(k\)-th magnitude \(J_k\)
+occurs at time \(T_k = W_1 + \ldots + W_k\). Based on an MRP, we define
+the Continuous Time Random Exceedance model (CTRE) as follows:
 
@@
 ``inter-arrival times'' and the ``exceedances'', respectively. The pair
-sequence \((T(\ell, n), W(\ell, n))_{n \in \mathbb N}\) is called a
+sequence \((X(\ell, n), T(\ell, n))_{n \in \mathbb N}\) is called a
 Continuous Time Random Exceedance model (CTRE). If the underlying MRP is
@@
 are independent as well. To see why, note that \(X(\ell)\) is, in
-distribution, simply equal to \(J | J > \ell\), independent of any
-waiting time \(W_k\).\\
+distribution, simply equal to \(J - \ell | J > \ell\), independent of
+any waiting time \(W_k\).\\
+We assume for the rest of the article, that the magnitudes
+\((J_i)_{i \in \mathbb{N}}\) belong to the the max-domain of attraction
+of some non-degenerate distribution. This means there exist \(a_n>0\)
+and \(d_n \in \mathbb{R}\) such that
+\[ a_n^{-1}(J_1 \vee \ldots \vee J_n -d_n) \Rightarrow A \text{ as } n \rightarrow \infty.\]
+Hence, the distribution of \(A\) is a generalized extreme value
+distribution (GEV) which distribution function is given by
+\[ F(x;\xi) = \begin{cases}\exp(-(1+\xi x)^{-1/\xi}) & \xi\neq0 \\ \exp(-\exp(-x)) & \xi = 0\end{cases}.\]
+The GEV is subdivided into the Gumbel (\(\xi=0\)), the Weibull
+(\(\xi<0\)) and the Fr'echet (\(\xi>0\)) family of distributions.
+
 Figure \ref{fig:thresholdedBursty} shows a simulated dataset in the top
@@
 
-In this section we state and prove the key theorem, see below. For an
-accessible introduction to regular variation and stable limit theorems,
-we recommend the book by Meerschaert and Sikorskii (2012).
+In this section we state and prove the key theorem. For an accessible
+introduction to regular variation and stable limit theorems, we
+recommend the book by Meerschaert and Sikorskii (2012).
 
@@
 \item[\textbf{Theorem:}]
-Let the waiting times \(J_k\) be in the domain of attraction of a
+Let the waiting times \(W_k\) be in the domain of attraction of a
 positively skewed sum-stable law with stability parameter
@@
 \(\mathbf E[\exp(-sD)] = \exp(-s^\beta)\). Write
-\(p := \mathbf P(J > \ell)\). Then the weak convergence \[
-\frac{T(\ell)} {b(1/p)} \to W_\beta \quad \text{ as } \quad \ell \uparrow x_R
-\] holds, where the Mittag-Leffler random variable \(W_\beta\) is
+\(p_{\ell} := \mathbf P(J > \ell)\). Then the weak convergence \[
+\frac{T(\ell)} {b(1/p_{\ell})} \to Z_\beta \quad \text{ as } \quad \ell \uparrow x_R
+\] holds, where the Mittag-Leffler random variable \(Z_\beta\) is
 defined on the positive real numbers via \[
-\mathbf E[\exp(-sW_\beta)] = \frac{1}{1+s^\beta}.
+\mathbf E[\exp(-sZ_\beta)] = \frac{1}{1+s^\beta}.
 \]
@@
 \mathbf P\left[ \frac{M(c) - d(c)}{a(c)} \le \ell^* \right] 
-\longrightarrow F(\ell^*), \quad t \to \infty
+\longrightarrow F(\ell^*), \quad c \to \infty
 \] where \(F\) is a generalized extreme value distribution, and
@@
 T(\ell) = \inf\{t: V(t) > \ell\}, 
-\] and that \[
-T(\ell) > t \quad \text{ if and only if } \quad V(t) \le \ell.
-\] By (Theorem 3.1, Meerschaert and Stoev, 2008), we have the stochastic
-process convergence \[
+\] and that
+
+\begin{align}
+T(\ell) > t \quad \text{ if and only if } \quad V(t) \le \ell. \label{inverserelat}
+\end{align}
+
+By (Theorem 3.1, Meerschaert and Stoev, 2008), we have the stochastic
+process convergence
+
+\begin{align}
 \frac{V(ct) - d(\tilde b(c))}{a(\tilde b(c))} 
-\stackrel{d}{\longrightarrow} Y(t), \quad t > 0.
-\] where \(Y(t)\) is a time-changed (``subordinated'') extremal process,
-and where \(\tilde b(c)\) is a regularly varying norming function which
-is \emph{inverse} to \(b(c)\), in the sense that
-\(b(\tilde b(c)) \sim c \sim \tilde b(b(c))\).
+\stackrel{d}{\longrightarrow} Y(t),  \quad c \to \infty, \label{TheoMS}
+\end{align}
+
+for \(t > 0\), where \(Y(t)\) is a time-changed (``subordinated'')
+extremal process, and where \(\tilde b(c)\) is a regularly varying
+norming function which is \emph{inverse} to \(b(c)\), in the sense that
+\(b(\tilde b(c)) \sim c \sim \tilde b(b(c))\) (Bingham et al., 1989).
 
@@
 \[
-\mathbf P\left[ \frac{T(\ell)}{b(1/p)} > t \right]
-= \mathbf P[T(\ell) > b(1/p) t]
+\mathbf P\left[ \frac{T(\ell)}{b(1/p_{\ell})} > t \right]
+= \mathbf P[T(\ell) > b(1/p_{\ell}) t]
 = \mathbf P[V(ct) \le \ell]
-\] where we have substituted \(c = b(1/p)\). Moreover \[
+\] where we have substituted \(c = b(1/p_{\ell})\) and used
+\eqref{inverserelat}. Moreover, we receive due to the convergence in
+\eqref{TheoMS} \[
 \mathbf P[V(ct) \le \ell]
@@
 \le \frac{\ell - d(\tilde b(c))}{a(\tilde b(c))} \right]
-\longrightarrow \mathbf P\left[ Y(t) \le \ell^* \right]
-\] Defining the hitting time of level \(\ell^*\) by \(Y(t)\) as
-\(\xi_{\ell^*} := \inf\{t: Y(t) > \ell^*\}\), we then have \[
+\longrightarrow \mathbf P\left[ Y(t) \le \ell^* \right] ,  \quad c \to \infty,
+\] for \(t>0\). Defining the hitting time of level \(\ell^*\) by
+\(Y(t)\) as \(\xi_{\ell^*} := \inf\{t: Y(t) > \ell^*\}\), we then have
+\[
 P\left[ Y(t) \le \ell^* \right] = \mathbf P[\xi_{\ell^*} > t] 
@@
 For a scale parameter \(\sigma > 0\), we write
-\({\rm ML}(\beta, \sigma)\) for the distribution of \(\sigma W_\beta\).
+\({\rm ML}(\beta, \sigma)\) for the distribution of \(\sigma Z_\beta\).
 The Mittag-Leffler distribution with parameter \(\beta \in (0,1]\) is a
@@
 1) be indistinguishable from the exponential distribution, for the
-purposes of applied statistics. For a detailed reference on the
-Mittag-Leffler distribution, see e.g.~ Haubold et al. (2011), and for
-algorithms, see e.g.~the R package \texttt{MittagLeffleR} (Gill and
-Straka, 2017).
+purposes of applied statistics.
+
+We caution the reader that, somewhat confusingly, there is another
+distribution called the ``light-tailed'' Mittag-Leffler distribution.
+This is in fact the limiting distribution of the renewal process
+\(N(t)\) above (see Meerschaert and Scheffler (2004)). For a detailed
+reference on the Mittag-Leffler distribution, see e.g.~ Haubold et al.
+(2011), and for algorithms, see e.g.~the R package
+\texttt{MittagLeffleR} (Gill and Straka, 2017).
 
@@
 result is shown with a different choice of scaling constant.
+\item[\textbf{Remark:}]
+When \(0 < \beta < 1\), the renewal process \(N(t)\) is \emph{not
+stationary}, and hence the results by (``On the Exceedance Point Process
+for a Stationary Sequence,'' 1988) on the exceedances of stationary
+sequences do not apply.
 \end{description}
@@
 The classical POT approach is based on the fact that exceedances above a
-high threshhold are asymptotically GPD distributed, hence a GPD
-distribution is fitted to the exceedances above a high enough
-threshhold. Due to the Theorem in the last Section we know that for high
-thresholds the times between exceedances are asymptotically
-Mittag-Leffler distributed in case of heavy-tailed waiting times between
-the observations. Hence, before we talk about inference for the
-exceedances in the next section, we discuss inference for Mittag-Leffler
+high threshold are asymptotically GPD distributed, hence a GPD
+distribution is fitted to the exceedances above a high enough threshold.
+Due to the Theorem in the last Section we know that for high thresholds
+the times between exceedances are asymptotically Mittag-Leffler
+distributed in case of heavy-tailed waiting times between the
+observations. Hence, before we talk about inference for the exceedances
+in the next section, we discuss inference for Mittag-Leffler
 distributions.
@@
 slightly outperforms the log-moment estimator regarding bias and RMSE
-for big enough sample sizes, but is extremely computational intensive.
+for big enough sample sizes, but is extremely computationally intensive.
 Figure \ref{fig:MSE} shows that both estimators perform well, even for
@@
 
-\caption{\label{fig:MSE} MSE for the estimation of tail (left column) and scale (right column) parameters via log-moment estimator and mle of a Mittag-Leffler sample with varying sample size n=25, 100, 200, varying tails on the x-axis and fixed scale equal to one.}\label{fig:MSE}
+\caption{\label{fig:MSE} MSE for the estimation of tail (left column) and scale (right column) parameters via log-moment estimator and MLE of a Mittag-Leffler sample with varying sample size n=25, 100, 200, varying tails on the x-axis and fixed scale equal to one.}\label{fig:MSE}
 \end{figure}
@@
 Hill estimator (Hill, 1975) based on the \(r+1\) upper order statistics
-\begin{align}\label{eq:hill}
+\begin{align}\label{eq:Hill}
 H_{r,n}=\left[ \frac{1}{r} \sum_{i=0}^{r} \log \frac{X_{(i)}}{X_{(r+1)}}\right]^{-1}, 
@@
 efficient since they only use a portion of the information contained in
-the data, as mentioned by Kozubowski (2001). Moreover, the hill
+the data, as mentioned by Kozubowski (2001). Moreover, the Hill
 estimator requires a tuning parameter, denoted with \(r\) in
-\eqref{eq:hill}. Additionaly, the estimator only performs reliably well
+\eqref{eq:Hill}. Additionaly, the estimator only performs reliably well
 for distributions close to Pareto (see Resnick, 1997). Figure
@@
 estimate the tail parameter of a Mittag-Leffler distribution with the
-hill estimator, the sample size has to be much larger and one has to
+Hill estimator, the sample size has to be much larger and one has to
 choose a large tuning parameter \(r\). In case that only events above a
@@
 Furthermore the Hill estimator of course completely fails if the
-inter-arrival times are exponential distributed and not heavy-tailed. We
-will comeback to the problems with the hill estimtator in Section
+inter-arrival times are exponentially distributed and not heavy-tailed.
+We will come back to the problems with the Hill estimtator in Section
 \ref{Simulationstudy}.
@@
 
-\caption{\label{fig:Hillplots} Hillplots for simulated Mittag-Leffler data with true tail 0.8 and sample size 200 (left) and 1000 (right), with number of upper order statics r on which the hill estimator is based on the x-axis.
+\caption{\label{fig:Hillplots} Hillplots for simulated Mittag-Leffler data with true tail 0.8 and sample size 200 (left) and 1000 (right), with number of upper order statics r on which the Hill estimator is based on the x-axis.
 }\label{fig:Hillplots}
@@
 
-\caption{\label{Fig:LRT} Power for bootstrapped LRT for different sample sizes , varying tails and scale parameter equal to 1.}\label{fig:LRT_power}
+\caption{\label{Fig:LRT} Power for bootstrapped LRT for different sample sizes, varying tails and scale parameter equal to 1.}\label{fig:LRT_power}
 \end{figure}
@@
 threshold \(\ell\) we may approximate the distribution of \(T(\ell)\)
-with an \({\rm ML}(\beta, b(1/p))\) distribution, where the function
-\(b(c)\) varies regularly at \(\infty\) with parameter \(1/\beta\).
-Building on the POT (Peaks-Over-Threshold) method, we propose the
-following estimation procedure for the distribution of inter-exceedance
-time \(T(\ell)\):
+with an \({\rm ML}(\beta, b(1/p_{\ell}))\) distribution, where the
+function \(b(c)\) varies regularly at \(\infty\) with parameter
+\(1/\beta\). Building on the POT (Peaks-Over-Threshold) method, we
+propose the following estimation procedure for the distribution of
+inter-exceedance time \(T(\ell)\):
 
@@
 \item
-  For a range of thresholds \(\ell\) near the largest order statistics,
-  extract datasets of exceedance times \(\{T(\ell, i)\}_i\).
-\item
-  For each choice of threshold \(\ell\), fit a Mittag-Leffler
-  distribution to the resulting dataset \(\{T(\ell, i)\}_i\). This
-  results in the estimates \(\{\hat\beta(\ell)\}_\ell\) and
-  \(\{\hat \sigma(\ell)\}_\ell\).
-\item
-  Plot \(\ell\) vs.~\(\hat \beta(\ell)\). As \(\ell\) increases towards
-  \(x_R\), \(\hat \beta(\ell)\) \emph{stabilizes} around a constant
-  \(\hat \beta\). Use \(\hat \beta\) as an estimate for the tail
-  parameter \(\beta\) of the Mittag-Leffler distribution of exceedance
-  times.
-\item
-  Approximate \(p \approx |\{k: J_k > \ell\}| / n\). Recall that
-  \(b(c)\) is regularly varying with parameter \(1/\beta\), and hence
-  has the representation \(b(c) = L(c) c^{1/\beta}\) for some slowly
-  varying function \(L(c)\). Assuming that the variation of \(L(c)\) is
-  negligible, we hence plot \(\ell\)
-  vs.~\(p^{1/\hat \beta} \hat \sigma(\ell)\). Again as \(\ell\)
-  increases towards \(x_R\), \(p^{1/\hat \beta} \hat \sigma(\ell)\) is
-  expected to stabilize around a constant \(\hat \sigma_0\). We then use
-  \(p^{-1/\hat \beta} \hat \sigma_0\) as an estimate of the scale
-  parameter of the Mittag-Leffler distribution of exceedance times for
-  the level \(\ell\).
+  Extract the \(K\) largest order statistics (i.e.~the \(K\) largest
+  values, where e.g.~\(K = 300\)) \(X_{(1)}, \ldots, X_{(K)}\) together
+  with their timestamps \(T_{(1)}, \ldots, T_{(K)}\).
+\item
+  Choose e.g.~\(K_0 = 5\), and for each \(k\) ranging from \(K_0 +1\) to
+  \(K + 1\):
+
+  \begin{enumerate}
+  \def\labelenumii{\alph{enumii})}
+  \tightlist
+  \item
+    extract the set \(\mathcal T_k\) of exceedance times of the
+    threshold \(X_{(k)}\)
+  \item
+    fit a Mittag-Leffler distribution to \(\mathcal T_k\), resulting in
+    the parameter estimates \(\hat\beta_k\) and \(\hat \sigma_k\).
   \end{enumerate}
-
-The above approach benefits from the following practical adjustments
-(compare with Figure \ref{fig:flares}):
-
-\begin{itemize}
-\item
-  We choose \(\ell\) from the order statistics, i.e.~\(\ell\) is the
-  \(k\)-th largest of the observations \(X_j\), where \(k\) runs from
-  \(k_\text{min}, k_\text{min} + 1, \ldots, k_\text{max}\). The datasets
-  are then of length \(k-1\).
-\item
-  We use \(k\) rather than \(\ell\) for the horizontal axis of our
-  plots.
-\item
-  In Step 4, rather than plotting \(p^{1/\hat \beta} \hat \sigma(\ell)\)
-  we plot \(k^{1/\hat \beta} \hat \sigma(\ell)\). This changes
-  \(\hat \sigma_0\) by the multiplicative constant \(n^{1/\hat \beta}\),
-  but has the advantage that \(\hat \sigma_0\) does not change if one
-  pre-processes the data by removing all observations below a certain
-  threshold.
-\end{itemize}
-
-The estimates \(\hat \beta\) and \(\hat \sigma_0\) give an estimate of
-the distribution of exceedance times, dependent on the threshold
-\(\ell\): \begin{align*}
-T(\ell) \sim {\rm ML}(\hat \beta, k^{-1/\hat \beta} \hat \sigma_0),
-\end{align*} where \(\ell\) equals the \(k\)-th order statistic. For
-quick estimates of the Mittag-Leffler parameters we have used the method
-of log-transformed moments (Cahoy, 2013). We have verified the validity
-of our estimation algorithm via simulations, see Section
-\ref{Simulationstudy}.
+\item
+  Plot \(k\) vs.~\(\hat \beta_k\). To the right, as
+  \(k \downarrow K_0\), the asymptotics are off and bias is high. To the
+  left (high threshold), data are scarce and variance is high. Choose a
+  region of \emph{stability} in the middle for a parameter estimate
+  \(\hat \beta\).
+\item
+  Plot \(k\) vs.~\(k^{1/\hat \beta} \hat \sigma_k\). Where the plot
+  stabilizes as \(k \downarrow K_0\), define the value
+  \(\hat \sigma_0\).
+\end{enumerate}
+
+The inferred values \(\hat \beta\) and \(\hat \sigma_0\) can then be
+interpreted as follows: Setting the threshold at \(X_{(k)}\), the
+threshold exceedance times follow a Mittag-Leffler distribution with
+shape parameter \(\hat \beta\) and scale parameter
+\(\hat \sigma_0 k^{-1/\beta}\).
+
+To clarify Step 4: Recall that by the theorem,
+\(\sigma_k / b(1/p_{\ell})\) is expected to stabilize around a constant
+as \(k \downarrow K_0\). Since \(b\) is regularly varying with parameter
+\(1/\beta\), we have
+\(b(1/p_{\ell}) = p_{\ell}^{-1/\beta} / L(1/p_{\ell})\) for some slowly
+varying function \(L\). Approximating
+\(p_{\ell} \approx \hat p_{\ell} := k / n\), we have
+\[\text{const} \approx \sigma_k / b(1/p_{\ell}) = \sigma_k \times p_{\ell}^{1/\beta} L(1/p_{\ell}) \approx \sigma_k \times k^{1/\beta} n^{-1/\beta} L(n/k)\]
+Assuming that the variation of \(L(n/k)\) is minor, we can hence see
+that \(\sigma_k k^{1/\beta}\) stabilizes.
+
+For computationally efficient estimates of the Mittag-Leffler parameters
+we have used the method of log-transformed moments. This estimation
+method provides point estimates as well as confidence intervals based on
+sampling variance (Cahoy, 2013), and has been implemented in the R
+software package \texttt{MittagLeffleR} (Gill and Straka, 2017). The
+stability plots for \(\hat \beta\) and \(\hat \sigma_0\) can be
+furnished with these confidence intervals, see e.g.~Figure
+\ref{fig:flares}, to produce (non-simultaneous) confidence bands. These
+stability plots were produced with the R package \texttt{CTRE} (Hees and
+Straka, 2018). We have verified the validity of our estimation algorithm
+via simulations, see Section \ref{Simulationstudy}.
 
 \hypertarget{Simulationstudy}{%
-\section{Simulation study}\label{Simulationstudy}}
+\section{Simulation Study}\label{Simulationstudy}}
 
@@
 \(\sigma_0\), a distribution for \(W_k\) needs to be chosen for which
-\(b(n)\) from \eqref{eq:stability} is known. For (i) we choose
-\(W_k \stackrel{d}{=} D\), where \(D\) is as in \eqref{eq:stability},
-then due to the stability property we have the \emph{equality} of
-distribution \(W_1 + \ldots + W_n \stackrel{d}{=} b(n) D\), for
+\(b(n)\) from \eqref{eq:stability} is known.
+
+\textbf{Case (i):} For (i) we choose \(W_k \stackrel{d}{=} D\), where
+\(D\) is as in \eqref{eq:stability}, then due to the stability property
+we have the \emph{equality} of distribution
+\(W_1 + \ldots + W_n \stackrel{d}{=} b(n) D\), for
 \(b(n) = n^{1/\beta}\). Using the parametrisation of Samorodnitsky and
@@
 approximately \[
-{\rm ML}(\beta, p^{-1/\beta}) 
+{\rm ML}(\beta, p_{\ell}^{-1/\beta}) 
 = {\rm ML}(\beta, k^{-1/\beta} n^{1/\beta}),
-\] which means \(\sigma_0 = n^{1/\beta}\). In the Pareto example we
-choose \(P(W>t)=Ct^{-\beta}\) with \(C=(1/\Gamma(1-\beta))^{1/\beta}\).
-We have chosen \(\beta=0.8\) in the stable as well as in the Pareto
-case. As third example we choose exponential distributed waiting times
-with a rate of \(1\). Figure \ref{Fig:TailSimu} shows the stability
-plots for the estimation of the tail parameter. Therefore,
-\(\hat \beta(k)\) vs.~\(k\) is plotted for each of the \(m=100\)
-simulation runs (grey thin lines). In the left column one can see the
-estimates based on the log-moment estimator, the stability plots in the
-middle are based on the maximum-likelihood estimator and on the right
-hand on the hill estimator. Recall that \(k\) is the index of the order
-statistics of \(J_k\) at which the threshold \(\ell\) is placed. Note,
-that the hill estimator is here based on the waiting times, not on the
-inter-exceedance times, hence the estimation is based on much more data.
-If one would base the hill-estimation only on the inter-exceedance
-times, the sample size would be too small and it would be impossible to
-deduce an estimate for the tail parameter from the plots (compare Figure
-\ref{fig:Hillplots}). The \(k\) on the \(x-\)axis is in the plots for
-the hill estimator the \(r\) which defines on which upper orders stats
-the hill estimator is based on (compare \eqref{eq:hill}). The bigger
-sample size results in the middle in a lower bias. But, one can also
-see, that there is much more variance between the stability plots for
-the different simulation runs in case of the hill estimator compared to
-the other two estimators. The black line is the mean value of the point
-estimators for each \(k\) resp. \(r\). However, if one wants to get a
-single estimate via such a stability plot, it would be much more
-difficult to deduce it from a hill plot compared to the other two
-estimators. In case that one has only thresholded data and hence a much
-smaller simple size, the hill estimator gets useless (see Section
-\ref{sec:ML}). Another advantage of the other estimators compared to the
-hill estimator is, that in the case one has exponential waiting times,
-the log-moment as well as the mle can detect this by getting an estimate
-close to \(1\). The hill estimators is just a tail parameter estimator
-for Pareto like tails and hence of course fails in case of exponential
-distributed inter-exceedance times. Figure \ref{Fig:ScaleSimu} shows the
-stability plots for the different estimators for the scale parameter.
-Here of course only for the log-moment (on the right hand) and the mle
-(on the left hand), since the hill estimator is just a tail parameter
-estimate. Here again both estimators show good performance. The
-stability plots in the mle case are a little bit closer to the true
-value, except in the exponetial case. Therefore, the mle is much more
-computational intensive.
+\] which means \(\sigma_0 = n^{1/\beta}\).
+
+\textbf{Case (ii):} In the Pareto example we choose
+\(P(W>t)=Ct^{-\beta}\) with \(C=(1/\Gamma(1-\beta))^{1/\beta}\). We have
+chosen \(\beta=0.8\) in both cases (i) and (ii).
+
+\textbf{Case (iii):} We choose exponentially distributed waiting times
+with a rate parameter of \(1\).
+
+Figure \ref{Fig:TailSimu} shows the graphical ``stability plots'' for
+the estimation of the tail parameter, where
+
+\begin{itemize}
+\tightlist
+\item
+  rows correspond to cases (i), (ii) and (iii), and
+\item
+  columns correspond to estimators (log-moment estimator,
+  maximum-likelihood, and Hill estimator).
+\end{itemize}
+
+We plot the tail parameter estimates \(\hat \beta(k)\) against \(k\) for
+each of the \(m=100\) simulation runs. Thin grey lines represent
+individual simulation runs, and the thicker black line is their mean.
+Recall that \(k\) is the index of the order statistics of \(J_k\) at
+which the threshold \(\ell\) is placed. Note that the Hill estimator is
+based on the waiting times, not on the inter-exceedance times, meaning
+that the estimation is based on more data. If one were to base the
+Hill-estimation only on the inter-exceedance times, the sample size
+would be too small and it would be impossible to deduce an estimate for
+the tail parameter from the plots (compare Figure \ref{fig:Hillplots}).
+
+In the right-hand Hill-estimator column, the \(k\) on the \(x\)-axis
+corresponds to \(r\) from \eqref{eq:Hill}. The Hill estimator appears to
+be nicely unbiased on Pareto data, but compared to the other two
+estimators, it has a higher variance, as can be seen from the wider
+spread of the simulated curves. This high variance means that that a
+single estimate is less reliable compared to the other two estimators.
+This effect is amplified if one only has a thresholded, and thus smaller
+dataset available, to the extent that the Hill estimates become severely
+flawed (see Section \ref{sec:ML}).
+
+Moreover, the bottom in \ref{Fig:TailSimu} shows clearly that the
+log-moment and maximum-likelihod estimators generalize to the
+exponential case (\(\beta = 1\)), whereas the Hill-estimator does not.
+
+Finally, the performance of Log-Moment and Maximum-Likelihood estimators
+for the scale parameter is shown in figure \ref{Fig:ScaleSimu}. Since
+there is no Hill-estimate of a scale parameter, there are only two
+columns. Both estimators show good performance, with a slight advantage
+for the Maximum-Likelihood estimator. This advantage is paid for by a
+higher computational cost.
 
@@
 
-\caption{\label{Fig:TailSimu} Stability Plots for m=100 simulation runs for stable distributed waiting times with a tail parameter of 0.8 (top row), Pareto distributed waiting times with tail parameter 0.8 (middle row) and exponential distributed waiting times (lower row).
+\caption{\label{Fig:TailSimu} Stability Plots for m=100 simulation runs for stable distributed waiting times with a tail parameter of 0.8 (top row), Pareto distributed waiting times with tail parameter 0.8 (middle row) and exponentially distributed waiting times (lower row).
 Left column: log-moment estimator, middle column: MLE, right column: Hill estimator.
@@
 
-\caption{\label{Fig:ScaleSimu} Stability Plots for m=100 simulation runs for stable distributed waiting times with a tail parameter of 0.8 (top row), Pareto distributed waiting times with tail parameter 0.8 (middle row) and exponential distributed waiting times (lower row).
+\caption{\label{Fig:ScaleSimu} Stability Plots for m=100 simulation runs for stable distributed waiting times with a tail parameter of 0.8 (top row), Pareto distributed waiting times with tail parameter 0.8 (middle row) and exponentially distributed waiting times (lower row).
 Left column: log-moment estimator, right column: MLE.
@@
 flare data, we first have to check if all model assumptions are
-full-filled. The CTRE model is based on three main assumptions, which
-are repeated below. For each assumption, we suggest one means of
-checking if it holds:
+fulfilled. The CTRE model is based on three main assumptions, which are
+repeated below. For each assumption, we suggest one means of checking if
+it holds:
 
@@
 data, on the left for the tail parameter and on the right for the scale
-parameter. Dotted lines show 95\% confidence intervals, which are
-derived from the asymptotic normality of the log-moments estimators
-(Cahoy, 2013) and the \(\delta\)-method (Gill and Straka, 2017), dashed
-lines show the deduced values of \(\beta\) resp.~\(\sigma_0\). The
-stability plot for the tail stabilizes nicely round about 0.85 (dashed
-line), while it is a little bit harder to deduce an estimate for the
-scale parameter. Howerever, the stability plot for the scale parameter
-seems to stabilize round about \(3 \times 10^7\) (dashed line).
+parameter. The dark grey ranges correspond to 95\% confidence intervals,
+which are derived from the asymptotic normality of the log-moments
+estimators (Cahoy, 2013) and the \(\delta\)-method (Gill and Straka,
+2017); dashed lines show the deduced true values of \(\beta\)
+resp.~\(\sigma_0\). The stability plot for the tail stabilizes nicely
+around 0.85 (dashed line), while the scale parameter stabilizes less
+obviously near \(3 \times 10^7\) (dashed line). The growth of the scale
+parameter for lower threshold appears to be closer to linear in
+\(p_{\ell}\), rather than proportional to \(p_{\ell}^{1/0.85}\) as
+suggested by the Mittag-Leffler fits. The reason for this is likely that
+the overall goodness of fit as compared to an exponential distribution
+is improved due to the peaked shape of the Mittag-Leffler distribution
+near \(0\), rather than its tail behaviour at \(\infty\). The reported
+fit should hence come with the caveat that a Mittag-Leffler distribution
+models exceedance times well only up to certain time-scales. More
+research is needed into the modelling of scale transitions, where
+inter-exceedance times appear to have different power laws across
+different time scales.
 
@@
 \ref{fig:flare-diagnostics-2}). We also counduct a bootstrapped LRT for
-the null hypothesis of exponential distributed inter-arrival times and
+the null hypothesis of exponentially distributed inter-arrival times and
 received a \(p\)-value of \(p<0.01\).
@@
 According to Figure \ref{fig:flares}, for a threshold \(\ell\) at the
-\(k\)-th order statistic, the fitted threshold exceedance time
+\(k\)-th order statistic, the estimated threshold exceedance time
 distribution is \[
@@
 next threshold crossing will depend on the time \(t_0\) elapsed since
-the last threshold crossing. This density equals \[
-p(t|\beta, \sigma_0, \ell, t_0) = \frac{f(t + t_0 | \beta, k^{-1/\beta} \sigma_0)}{\mathbf P[T_\ell > t_0]}
+the last threshold crossing. This density is approximately equal to \[
+p(t|\beta, \sigma_0, \ell, t_0) \approx \frac{f(t + t_0 | \beta, k^{-1/\beta} \sigma_0)}{\mathbf P[T_\ell > t_0]}
 \] where \(f(\,\cdot\, | \beta, k^{-1/\beta} \sigma_0)\) is the
@@
 inter-exceedance times of high thresholds. Moreover, we have derived the
-following non-linear scaling behaviour: \(\sigma \sim p^{-1/\beta}\),
-where \(\sigma\) is the scale parameter of the distribution of threshold
-exceedance times, \(p\) is the fraction of magnitudes above the
-threshold, and \(\beta\) the exponent of the power law. This
-``anomalous'' scaling behaviour in the bursty setting entails two
-phenomena:
+following non-linear scaling behaviour:
+\(\sigma \sim p_{\ell}^{-1/\beta}\), where \(\sigma\) is the scale
+parameter of the distribution of threshold exceedance times,
+\(p_{\ell}\) is the fraction of magnitudes above the threshold, and
+\(\beta\) the exponent of the power law. This ``anomalous'' scaling
+behaviour in the bursty setting entails two phenomena:
 
@@
 \(\ell_0\) is discarded for CTREs, and hence need not satisfy the i.i.d.
-assumption.For the purposes of statistical inference, we merely require
+assumption. For the purposes of statistical inference, we merely require
 that the inter-threshold-crossing times are i.i.d.
@@
 stochastic process limits for CTRMs, Prof.~Roland Fried for discussion
-according the statistical methods and Gurtek Gill who helped create the
+regarding the statistical methods and Gurtek Gill who helped create the
 MittagLeffleR R-package.
@@
 
+\leavevmode\hypertarget{ref-BinghamGoldieTeugels}{}%
+Bingham, N.H., Goldie, C.M., Teugels, J.L., 1989. Regular variation.
+Cambridge university press.
+
 \leavevmode\hypertarget{ref-Cahoy2013}{}%
@@
 maxima. Extremes 21.
+
+\leavevmode\hypertarget{ref-CTRE}{}%
+Hees, K., Straka, P., 2018. CTRE: Thresholding bursty time series.
+doi:\href{https://doi.org/10.6084/m9.figshare.6243434.v2}{10.6084/m9.figshare.6243434.v2}
 
@@
 
+\leavevmode\hypertarget{ref-limitCTRW}{}%
+Meerschaert, M.M., Scheffler, H.-P., 2004. Limit Theorems for
+Continuous-Time Random Walks with Infinite Mean Waiting Times. J. Appl.
+Probab. 41, 623--638.
+doi:\href{https://doi.org/10.1239/jap/1091543414}{10.1239/jap/1091543414}
+
 \leavevmode\hypertarget{ref-MeerschaertSikorskii}{}%

### 2020-03-11 changes.Rmd
changes.md --> cahnges.Rmd Rmarkdwon file, new format New Mittag Leffler simulation study, with m=5000

---
title: "Response to the reviewers’ comments on the article"  
subtitle: Statistical Inference for inter-arrival times of extreme events in bursty time series 
author: 
  - Katharina Hees
  - Peter Straka
  - Smarak Nayak
date: "11 März 2020"
output: pdf_document
---

We would like to thank the reviewers very much for their careful reviews and the helpful comments that gave us the opportunity to improve the manuscript.
Below we explain point by point how we addressed the comments during our revision of the manuscript.

# Referee 1

## Major points and questions

"It should be noted, however, that this process has light-tailed
Mittag-Leffler marginals, while the authors of the paper under review encounter a different, heavy-tailed Mittag-Leffler law."

* We have added the following sentence near the end of Section 3: 
"We caution the reader that, somewhat confusingly, there is another distribution
called the "light-tailed" Mittag-Leffler distribution.  This is in fact the 
limiting distribution of the renewal process $N(t)$ above (see @limitCTRW)."

* We have also added the following reference: 
Meerschaert, Mark M, and Hans-Peter Scheffler. 2004. “Limit Theorems forContinuous-Time Random Walks with Infinite Mean Waiting Times.”J. Appl.Probab.41 (3): 623–38. https://doi.org/10.1239/jap/1091543414.

"(p.5, l. 9-13) Why is it true that the limiting distribution exists? It is well known..."

* In case of a continuous distribution one can choose the normalization in such a way that a non-degenerate limit distributions exists, but this is not neccessarily true for a linear normalization. We just forgot to add the assumption, that the distribution of the magnitudes is out of the domain of attraction of an extreme value distribution. We added this accordingly.

"Note: It is important to observe that due to the fact that the waiting times Wj ’s have infinite
means, the renewal counting process N(t) cannot be made stationary (through a random shift) and hence this model does not fall into the classic context of Hsing-Leadbetter and Davis-Hsing."

* We have added a remark at the end of Section 3, saying: 
  "When $0 < \beta < 1$, the renewal process $N(t)$ is _not stationary_, 
   and hence the results by @Hsing88 on the exceedances of stationary sequences do not apply."

"Given the first comment above, can you elucidate the connection between the two different kinds of Mittag-Leffler distributions – the light-tailed distributional limit for the counting process N(t) and the heavy-tailed limit model for the T(l)’s?"

* We have addressed this, see first point.

"The use of k is very confusing ... These two sentences are so unclear, so poorly written...  Be specific, choose your words carefully and introduce labels/titles in the plots."

* We have re-written the entire section titled "Simulation study".

"(Section 5 and 6) In these 2 sections it is implied that p = k/n .... While a complete rigor in the discussion on the statistical methodology is perhaps not necessary, itis important for the reader to clearly see where “asymptotic approximations” are applied."

* We have re-written Sections 5 & 6, and made sure that $p$ is used as the theoretical exceedance probability, whereas the fraction of exceedances $k/n$ is denoted as $\hat p$. We have also clarified throughout where we assuming approximations.

"(Section 5) The methodology in this section (pages 9 and 10) is not very clearly described. Why give 2 algorithms if you are using just the second one, mostly? ... The scaling/rescaling of the scale coefficient by the choice of l and k is very confusing. Please revise Section 5 thoroughly."

* We have re-written Section 5, as per the referee's suggestions, and we can now do without the "practical adjustments" section.

"(page 11, line 12) Poor scientific language: “... the hill estimator gets useless ... Also a few lines after that, they claim that the scale cannot be estimated. This s not entirely true. The classic work of Peter Hall { entitled On Some Simple Estimates of an Exponent of Regular Variation and published in the Journal of the Royal Statistical Society. Series B (Methodological), Vol. 44, No. 1 (1982), pp. 37(42)does include natural
asymptotically normal estimators for both the tail exponent and the scale. This said, there
is a tremendous amount of work on bias correction for the Hill estimator (and I assume
the scale) that the authors can implement, should they desire. I realize that this may
be going beyond the scope of their work, but proper pointers to the literature should be
given and the notion of second order regular variation (required to establish asymptotic
distributions) should be mentioned."

* KATHI TO DO

"Last but not least, given that the authors are dealing with more or less standard semi- parametric estimation of heavy-tail exponents and scales, they could formulate limit the- orems on the asymptotic distribution of their statistics and derive Wold-type confidence intervals for the estimated parameters. ... "

* In the last paragraph of Section 5, we have included pointers to the literature for confidence intervals for the shape and scale parameters of the Mittag-Leffler distribution, and how these lead to "confidence bands" in our plots, based on the CTRE package.

## Typos and suggestions

1.  fixed
2.  fixed
3.  fixed
4.  fixed
5.  fixed
6.  fixed
7.  fixed
8.  fixed
9.  fixed
10. fixed
11. fixed
12. fixed
13. fixed
14. fixed
15. We reformulated the whole part and added titles. 
16. fixed
17. no longer applies
18. fixed
19. fixed
20. fixed
21. fixed
22. fixed
23. fixed
24. fixed
25. fixed
26. The section has been re-written
27. fixed
28. fixed
29. fixed
30. fixed
31. fixed
32. fixed
33. We have commented as follows: 
    "The stability plot for the tail stabilizes nicely around 0.85 (dashed line), while 
    the scale parameter stabilizes less obviously near $3 \times 10^7$ (dashed line).
    The growth of the scale parameter for lower threshold appears to be closer to linear in $p$, 
    rather than proportional to $p^{1/0.85}$ as suggested by the Mittag-Leffler
    fits. The reason for this is likely that the overall goodness of fit as 
    compared to an exponential distribution is improved due to the 
    peaked shape of the Mittag-Leffler distribution near $0$,
    rather than its tail behaviour at $\infty$.
    The reported fit should hence come with the caveat that a Mittag-Leffler 
    distribution models exceedance times well only up to certain time-scales. 
    More research is needed into the modelling of scale transitions, where
    inter-exceedance times appear to have different power laws across different 
    time scales."
34. We have changed "fitted" to "estimated".
35. We have added confidence limits.
36. We have added titles to the two figures, and to other figures where 
    feasible. 
37. fixed
38. fixed

# Referee 2

"I understand the authors find inspiration in Peaks-Over-Threshold (POT)
method of extreme value theory, although, I do not see a real connection be-
tween two models. Observe that the peaks over threshold l are ignored, so
random variable $\tau(l)$ could be substituted by any other independent geo-
metric (or exponential) random variable with mean $1/p(l)$."

*

"Moreover, I think, this would simplify some arguments, including the proof of the theorem."

* TO DO

"The CTRE model considered here can be viewed as a special family of
renewal processes (with power-law waiting times). Their relatively simple
structure makes them amenable to theoretical analysis but for the same rea-
son, I am not convinced that the CTRE model represents a really good
alternative to cluster models as a model for bursty data. The authors' claim
that "visually similar statistical behaviour" can be seen in some real life data
set seems a bit too vague to me."

* To DO

"Although auto-correlation plots given in Figure 7, after log-transforming data (this does not always ensure infiniteness of moments note) seem to indicate limited dependence in the sequence $log T(l,n)$, it is well known that the choice of such a transformation can in influence appearance of a corresponding graph."

* To DO

"The authors finally apply two methods (log-moments and MLE) to es-
timate parameters of the limiting Mittag-Leffler distribution, and obtain in
the process an estimator of the key tail parameter $\beta$. These methods seems
to outperform the standard Hill estimator in a simulation study although
the latter utilizes a much larger data set typically. This phenomena asks
for at least some explanation and a further study, because if it holds more
generally, the authors could use their approach as a superior alternative to
the Hill estimator for any power law distribution with $\beta$ < 1."

* TO DO

"The manuscript seems nicely organized. However, writing is not always
precise, the paper contains some typos and not entirely rigorous mathemati-
cal arguments.""

* TO DO

"I also do not see a clear connection with the POT method suggested in the abstract, mainly because exceedances really play insignifficant role in the analysis.""

* TO DO

"P.3. Definition MPR uses the left and the right end point of the distribution without precise explanation. The role of the sequence $(J_k)$ in the rest of the text should be also discussed."

* We added a definition for the left and the right point.
  NOCH ETWAS ZU DEN J_k ERGAENZEN.

"P.3. in the CTRE definition, in $(T(l,n),W(l,n))_n$, one might expect $X(l,n)$."

* You are completely right. This was a typo. We changed this accordingly.

"P.3. Probably $J-l |J > l$?"

* You are completely right again. This was also a typo. We changed this accordingly.

"P.4. In the first line of the theorem waiting times should be $W_k$. To avoid confusion, it would be better to use $p_l$ instead of $p$ and some other letter to denote the limit instead of $W_{\beta}$."

* We changed this accordingly.

"P.5. In the proof you use the fact that $J_k$ have continuous distribution, but this has not been assumed. You also use the fact that $J_k$ belong to some maximal domain of attraction - which is not assumed either."

* Thank you. We added an assumption accordingly.

"P.5. You should be careful about which parameter tends to infinity in
your limiting relations, it seems that $c \rightarrow \infty$ is missing at several places, and $t \rightarrow \infty$ appears instead at one point."

* We fixed this.

"P.5. You seem to to assume that your $l$ grows at a very precise rate - could this be a problem?"

* PETER TO DO

"The last two lines of the proof need more explanation, I think."

* We added some more explanation to the last two lines.

"P.6. threshold"

* Fixed.

"P.7. Could you comment worse performance of the estimator of the scale
for small tail indices."

* TO DO

"P.7. the Hill or hill estimator?"

* Fixed.

"P.9. In step 3. could you explain how the plot "stabilizes" as $l$ increases since one gets very few observations in that region? Argument behind step 4. should be written out, in my opinion."

* You are right. We should better explain this. The plot stabilizes in a region in the middle. We reformulated step 3 accordingly. We also clarified the argument for what was written before at the end of step 4 and added a few sentences for this, following the algorithm.

"p.11. Do you mean lower variance or lower bias?""

* In the pareto case the Hill estimator is less biased, but in all cases it has a higher variance compared to the other two estimators. We reformulated this part.

"P.11. I do not see how you derived the conclusion: Therefore, the mle
is..."

* The formulation "Therefore" was wrong. We changed the text accordingly.

"P.14. Is that last formula an equality or an approximation?"

* This is an approximation. We replaced the equality sign by the approximately-equal sign.

"P.18. Space forgotten in 'assumption.For' "

* Fixed.

"P.19. and earlier, Mark. M Meerschaert seems to be the only author
cited with his full name and initials - maybe one should strive for uniformity here."

* We changed this accordingly.

### 2020-03-11 article_springer/article_springer_files/Hill_Scale/Simu_Hill_Scale_Ex1.R
mit Kurti's Hilfe richtig

@@ -1,0 +1,117 @@
+#Simulationsstudy - Comparisions of Inference procedure and different estimation methods
+
+# Author: Katharina Hees
+# Created: 01/03/2020
+
+library("CTRE")
+library("MittagLeffleR")
+library("magrittr")
+library("dplyr")
+library("ggplot2")
+library("parallel")
+library(here)
+
+
+p <- as.integer(Sys.getenv("PBS_ARRAYID"))
+print(p)
+
+###Functions########################################
+
+hill_estim<-function(k,data){
+  n<-length(data)
+  data<-sort(data)
+  data_thinned<-data[(n-k):n]
+  r<-1/k * sum(log(data_thinned/data_thinned[1]))
+  return(1/r)
+}
+
+hill_scaletail<-function(k,data){
+  n<-length(data)
+  data<-sort(data)
+  tail_est<-hill_estim(k,data)
+  scale_est<-k*data[n-k]^{tail_est}/n
+  l<-list(tail=tail_est,scale=scale_est)
+  return(l)
+}
+
+####################################################
+
+#Example One  - CTRE with stable distributed waiting times - tail=0.8
+
+n<-10000
+tail<-0.8
+sigma <- (cos(pi*tail/2))^(1/tail)
+
+times<-stabledist::rstable(n,tail, 1, sigma, pm=1)
+times_sum <- cumsum(times)
+magnitudes <- extRemes::revd(n, scale = 1, shape = 0)
+sim_ctre <- ctre(data.frame(times_sum, magnitudes))
+
+ntasks <- 4
+print(ntasks)
+
+# Initialize Cluster
+cl <- makeCluster(ntasks)
+clusterExport(cl, "sim_ctre")
+clusterExport(cl, "times")
+clusterExport(cl, "hill_estim")
+clusterExport(cl, "hill_scaletail")
+clusterEvalQ(cl,library(MittagLeffleR))
+clusterEvalQ(cl,library(CTRE))
+clusterEvalQ(cl,library("magrittr"))
+
+# Zufallszahlengeneratoren auf allen Workern des Clusters mit einem bestimmten
+# seed initialisieren (verhindert Zyklen in den Zufallszahlen zwischen den
+# Workern)
+clusterSetRNGStream(cl,iseed=42)
+
+#Code
+ks<-c(30:500)
+estimates_scaletail08<-parSapply(cl,ks, FUN = function(k){
+  ias<-sim_ctre %>% thin(k=k) %>% interarrival
[…]

### 2020-03-11 article_springer/article_springer_files/ML_estim_simu/ML_estim_simustudy.R

@@ -12,10 +12,29 @@ library(ggplot2)
 
 plan(multiprocess)
 
-tails <-0.2# c(0.2,0.8) #seq(0.2,0.9,0.1)
-scales <- 1 #c(0.1,1,10)
-ns <-25# seq(25,200,25)
-m<-1000
+tails <-seq(0.2,0.9,0.1)
+scales <- 1
+ns <-c(25,100,200)
+m<-5000
+
+hill_estim<-function(k,data){
+  n<-length(data)
+  data<-sort(data)
+  data_thinned<-data[(n-k):n]
+  r<-1/k * sum(log(data_thinned/data_thinned[1]))
+  return(1/r)
+}
+
+hill_scaletail<-function(k,data){
+  n<-length(data)
+  data<-sort(data)
+  tail_est<-hill_estim(k,data)
+  scale_est<-k*data[n-k]^{tail_est}/n
+  l<-c(tail_est,scale_est)
+  return(l)
+}
+
+
 
 pb <- progress_bar$new(total = length(tails)*length(scales)*length(ns), format = "[:bar] tail: :tail, scale: :scale, n: :n")
 
@@ -27,12 +46,14 @@ estimates <- sapply(ns, function(n) sapply(tails, function(tail) sapply(scales, 
     x <- rml(n, tail = tail, scale = scale)
     cbind(
       logMom = MittagLeffleR::logMomentEstimator(x)[c(1,2)],
-      ML = MittagLeffleR::mlmle(x)$par
+      ML = MittagLeffleR::mlmle(x)$par,
+      hill = hill_scaletail(k=n-1,data=x)
     )
 
   })
 }, simplify = "array"), simplify = "array"), simplify = "array")
 
+save(estimates,file="estimates.RData")
 
 reshape2::melt(estimates) %>%
   as.tbl %>%
@@ -41,10 +62,18 @@ reshape2::melt(estimates) %>%
   mutate(true.value = case_when(param == "tail" ~ true.tail, param == "scale" ~ true.scale)) %>%
   group_by(param, n, true.scale, true.tail, method) %>%
   summarise(
-    mse = mean((value-true.value)^2),
-    sqbias = mean(value-true.value)^2,
+    rmse = sqrt(mean((value-true.value)^2)),
+    bias = mean(value-true.value),
     var = var(value)
   ) ->
   tbl_ML_estim
 
 save(tbl_ML_estim,file="tbl_ML_estim.RData")
+
+# RMSE
+
[…]

### 2020-03-11 article_springer/article_springer_files/Hill_Scale/Simu_Hill_Scale_Ex1.R
Deletions

@@ -1,117 +1,0 @@
-#Simulationsstudy - Comparisions of Inference procedure and different estimation methods
-
-# Author: Katharina Hees
-# Created: 01/03/2020
-
-library("CTRE")
-library("MittagLeffleR")
-library("magrittr")
-library("dplyr")
-library("ggplot2")
-library("parallel")
-library(here)
-
-
-p <- as.integer(Sys.getenv("PBS_ARRAYID"))
-print(p)
-
-###Functions########################################
-
-hill_estim<-function(k,data){
-  n<-length(data)
-  data<-sort(data)
-  data_thinned<-data[(n-k):n]
-  r<-1/k * sum(log(data_thinned/data_thinned[1]))
-  return(1/r)
-}
-
-hill_scaletail<-function(k,data){
-  n<-length(data)
-  data<-sort(data)
-  tail_est<-hill_estim(k,data)
-  scale_est<-k*data[n-k]^{tail_est}/n
-  l<-list(tail=tail_est,scale=scale_est)
-  return(l)
-}
-
-####################################################
-
-#Example One  - CTRE with stable distributed waiting times - tail=0.8
-
-n<-10000
-tail<-0.8
-sigma <- (cos(pi*tail/2))^(1/tail)
-
-times<-stabledist::rstable(n,tail, 1, sigma, pm=1)
-times_sum <- cumsum(times)
-magnitudes <- extRemes::revd(n, scale = 1, shape = 0)
-sim_ctre <- ctre(data.frame(times_sum, magnitudes))
-
-ntasks <- 4
-print(ntasks)
-
-# Initialize Cluster
-cl <- makeCluster(ntasks)
-clusterExport(cl, "sim_ctre")
-clusterExport(cl, "times")
-clusterExport(cl, "hill_estim")
-clusterExport(cl, "hill_scaletail")
-clusterEvalQ(cl,library(MittagLeffleR))
-clusterEvalQ(cl,library(CTRE))
-clusterEvalQ(cl,library("magrittr"))
-
-# Zufallszahlengeneratoren auf allen Workern des Clusters mit einem bestimmten
-# seed initialisieren (verhindert Zyklen in den Zufallszahlen zwischen den
-# Workern)
-clusterSetRNGStream(cl,iseed=42)
-
-#Code
-ks<-c(30:500)
-estimates_scaletail08<-parSapply(cl,ks, FUN = function(k){
-  ias<-sim_ctre %>% thin(k=k) %>% interarrival
[…]

### 2020-03-26 article_springer/article_springer.tex
Überarbeitung, Finale Änderung bzgl Reviewer 2

@@
 In the following we denote with \(x_L \in [-\infty, +\infty)\) and
-\(x_R \in (-\infty, +\infty]\)) the left and right endpoint of the
+\(x_R \in (-\infty, +\infty]\) the left and right endpoint of the
 distribution of \(J\). We assume that the \(k\)-th magnitude \(J_k\)
@@
 of some non-degenerate distribution. This means there exist \(a_n>0\)
-and \(d_n \in \mathbb{R}\) such that
-\[ a_n^{-1}(J_1 \vee \ldots \vee J_n -d_n) \Rightarrow A \text{ as } n \rightarrow \infty.\]
-Hence, the distribution of \(A\) is a generalized extreme value
-distribution (GEV) which distribution function is given by
+and \(d_n \in \mathbb{R}\) such that \begin{align} \label{assumptionJs}
+a_n^{-1}(J_1 \vee \ldots \vee J_n -d_n) \Rightarrow A \text{ as } n \rightarrow \infty.
+\end{align} Hence, the distribution of \(A\) is a generalized extreme
+value distribution (GEV) which distribution function is given by
 \[ F(x;\xi) = \begin{cases}\exp(-(1+\xi x)^{-1/\xi}) & \xi\neq0 \\ \exp(-\exp(-x)) & \xi = 0\end{cases}.\]
 The GEV is subdivided into the Gumbel (\(\xi=0\)), the Weibull
-(\(\xi<0\)) and the Fr'echet (\(\xi>0\)) family of distributions.
+(\(\xi<0\)) and the Fréchet (\(\xi>0\)) family of distributions.
 
@@
 M(c) := J_1 \vee \ldots \vee J_{\lfloor c \rfloor},
-\] and since we assume that the \(J_k\) have a continuous distribution,
-there exist norming functions \(a(c)\) and \(d(c)\) such that \[
+\] and since we assumed that the \(J_k\) our out of the domain of
+attraction of a max-stable distribution \(F\) (see
+\eqref{assumptionJs}), there exist norming functions \(a(c)\) and
+\(d(c)\) such that \[
 \mathbf P\left[ \frac{M(c) - d(c)}{a(c)} \le \ell^* \right] 
@@
 distribution is fitted to the exceedances above a high enough threshold.
-Due to the Theorem in the last Section we know that for high thresholds
-the times between exceedances are asymptotically Mittag-Leffler
-distributed in case of heavy-tailed waiting times between the
-observations. Hence, before we talk about inference for the exceedances
-in the next section, we discuss inference for Mittag-Leffler
-distributions.
+This approach was well-established a long time ago and is standard in
+extreme value theory nowadays. Hence we just refer here to the according
+literature (Smith (1984), Leadbetter (1991), Davison and Smith (1990)),
+a nice introduction can be found in Beirlant et al. (2006) Ch.5.3,
+Embrechts et al. (2013) Ch. 6.5. or Coles (2001) Ch.4. Hence, we focus
+in this article mainly on the inter-exceedance times. Due to the Theorem
+in the last Section we know that for high thresholds the times between
+exceedances are asymptotically Mittag-Leffler distributed in case of
+heavy-tailed waiting times between the observations. In this article we
+propose to proceed with inter-exceedance times in a similar fashion as
+with the magnitudes in the classical POT approach, more precisely to fit
+a Mittag-Leffler distribution via stability plots to the
+inter-exceedance times. Hence, before we talk about inference for the
+inter-exceedance times in the next section, we first discuss inference
+for Mittag-Leffler distributions.
 
@@
 require any prior. Furthermore, they performed simulation studies
-illustrating that the log-moment outperforms the fractional moment
+illustrating that the log-Moment outperforms the fractional moment
 estimator with respect to bias and root mean squared error (RMSE).
@@
 Likelihood estimation is implemented via numerical optimization. The MLE
-slightly outperforms the log-moment estimator regarding bias and RMSE
+slightly outperforms the log-Moment estimator regarding bias and RMSE
 for big enough sample sizes, but is extremely computationally intensive.
@@
 
-\caption{\label{fig:MSE} MSE for the estimation of tail (left column) and scale (right column) parameters via log-moment estimator and MLE of a Mittag-Leffler sample with varying sample size n=25, 100, 200, varying tails on the x-axis and fixed scale equal to one.}\label{fig:MSE}
+\caption{\label{fig:MSE} MSE for the estimation of tail (left column) and scale (right column) parameters via log-Moment estimator and MLE of a Mittag-Leffler sample with varying sample size n=25, 100, 200, varying tails on the x-axis and fixed scale equal to one, based on 5000 simulation runs.}\label{fig:MSE}
 \end{figure}
@@
 denote the order statistics in decreasing order of a sequence
-\(X_1,\ldots,X_n\). However, these methods are statistically less
-efficient since they only use a portion of the information contained in
-the data, as mentioned by Kozubowski (2001). Moreover, the Hill
-estimator requires a tuning parameter, denoted with \(r\) in
-\eqref{eq:Hill}. Additionaly, the estimator only performs reliably well
-for distributions close to Pareto (see Resnick, 1997). Figure
-\ref{fig:Hillplots} shows Hill plots for Mittag-Leffler simulated data,
-with varying sample sizes and tails. To deduce the correct tail
-parameter estimates from these plots is virtually impossible. To
-estimate the tail parameter of a Mittag-Leffler distribution with the
-Hill estimator, the sample size has to be much larger and one has to
-choose a large tuning parameter \(r\). In case that only events above a
-high threshold are recorded, even \(n=1000\) events are unrealistic.
-Furthermore the Hill estimator of course completely fails if the
-inter-arrival times are exponentially distributed and not heavy-tailed.
-We will come back to the problems with the Hill estimtator in Section
-\ref{Simulationstudy}.
+\(X_1,\ldots,X_n\). The Hill estimator only performs reliably well for
+distributions close to Pareto (see Resnick, 1997). It heavily depends on
+the choice of \(r\) in \eqref{eq:Hill}, hence on the number of order
+statistics entering into \eqref{eq:Hill}. Figure \ref{fig:Hillplots}
+shows Hill plots for Mittag-Leffler simulated data, with varying sample
+sizes and tails. To deduce the correct tail parameter estimates from
+these plots is virtually impossible. To estimate the tail parameter of a
+Mittag-Leffler distribution with the Hill estimator, the sample size has
+to be much larger and one has to choose a large tuning parameter \(r\).
+In case that only events above a high threshold are recorded,
+\(n=10000\) events are unrealistic. There is a vast literature on
+bias-reduced versions of the Hill estimator and on the optimal choice of
+\(r\), mainly based on imposed second-order regular variation conditions
+(see e.g.~Beirlant et al., 2006, p. Ch.4.4 and 4.7 and references in
+it). Also, there are lot of other tail-index estimators not taken under
+consideration in our article, since this would go beyond the scope of
+our article. However, we know from the Theorem in Section
+\ref{sec:scaling} that the inter-exceedance times are asymptotically
+Mittag-Leffler distributed. So all these general tail (and scale)
+estimation methods are statistically less efficient since they only use
+a portion of the information contained in the data, as mentioned by
+Kozubowski (2001). Furthermore, the Hill estimator of course completely
+fails, if the inter-arrival times are exponentially distributed and not
+heavy-tailed. Hence, we propose to use the log-Moment estimator or the
+MLE for Mittag-Leffler distributions.
 
@@
 
-\caption{\label{fig:Hillplots} Hillplots for simulated Mittag-Leffler data with true tail 0.8 and sample size 200 (left) and 1000 (right), with number of upper order statics r on which the Hill estimator is based on the x-axis.
+\caption{\label{fig:Hillplots} Hillplots for simulated Mittag-Leffler data with true tail 0.8 and sample size 200 (left) and 10000 (right), with number of upper order statics r on which the Hill estimator is based on the x-axis.
 }\label{fig:Hillplots}
@@
 as \(\beta \uparrow 1\) to an exponential distribution; it becomes hard
-to differentiate a Mittag-Lefller distribution from an exponential.
+to differentiate a Mittag-Leffler distribution from an exponential.
 
@@
   values, where e.g.~\(K = 300\)) \(X_{(1)}, \ldots, X_{(K)}\) together
-  with their timestamps \(T_{(1)}, \ldots, T_{(K)}\).
-\item
-  Choose e.g.~\(K_0 = 5\), and for each \(k\) ranging from \(K_0 +1\) to
-  \(K + 1\):
+  with their timestamps \(T_{(1)}, \ldots, T_{(K-1)}\).
+\item
+  Choose a minimum number of exceedances \(K_0\leq K\),
+  e.g.~\(K_0 = 5\), and for each \(k\) ranging from \(K_0\) to \(K\):
 
@@
   \item
-    extract the set \(\mathcal T_k\) of exceedance times of the
-    threshold \(X_{(k)}\)
+    extract the set \(\mathcal T_k\) of exceedance times between the
+    magnitudes exceeding the threshold \(X_{(k)}\)
   \item
@@
 \item
-  Plot \(k\) vs.~\(k^{1/\hat \beta} \hat \sigma_k\). Where the plot
-  stabilizes as \(k \downarrow K_0\), define the value
+  Plot \(k\) vs.~\(k^{1/\hat \beta} \hat \sigma_k\). Again, choose a
+  region of \emph{stability} as \(k\) gets smaller and define
   \(\hat \sigma_0\).
@@
 \(\sigma_k / b(1/p_{\ell})\) is expected to stabilize around a constant
-as \(k \downarrow K_0\). Since \(b\) is regularly varying with parameter
+as \(k\) gets smaller. Since \(b\) is regularly varying with parameter
 \(1/\beta\), we have
 \(b(1/p_{\ell}) = p_{\ell}^{-1/\beta} / L(1/p_{\ell})\) for some slowly
-varying function \(L\). Approximating
-\(p_{\ell} \approx \hat p_{\ell} := k / n\), we have
+varying function \(L\). Approximating \(p_{\ell}\) by
+\(\hat p_{\ell} := k / n\), we have
 \[\text{const} \approx \sigma_k / b(1/p_{\ell}) = \sigma_k \times p_{\ell}^{1/\beta} L(1/p_{\ell}) \approx \sigma_k \times k^{1/\beta} n^{-1/\beta} L(n/k)\]
@@
 that \(\sigma_k k^{1/\beta}\) stabilizes.
+
+\begin{description}
+\item[\textbf{Remark}:]
+We approximated \(p_{\ell}\), the probability that an event is larger
+than \(l\), by its relative frequency. One could also approximate this
+tail probability by the GPD distribution fitted to the exceedances.
+\end{description}
 
@@
 To test our inference method via stability plots, we have simulated
-\(m=100\) times \(n=10000\) independent waiting time and magnitude pairs
-\((W_k, J_k)\) for waiting times that follow
+\(m=100\) datasets with \(n=10000\) independent waiting time and
+magnitude pairs \((W_k, J_k)\) for waiting times that follow
 
@@
 \item
-  columns correspond to estimators (log-moment estimator,
-  maximum-likelihood, and Hill estimator).
+  columns correspond to estimators (log-Moment estimator,
+  Maximum-Likelihood).
 \end{itemize}
@@
 Recall that \(k\) is the index of the order statistics of \(J_k\) at
-which the threshold \(\ell\) is placed. Note that the Hill estimator is
-based on the waiting times, not on the inter-exceedance times, meaning
-that the estimation is based on more data. If one were to base the
-Hill-estimation only on the inter-exceedance times, the sample size
-would be too small and it would be impossible to deduce an estimate for
-the tail parameter from the plots (compare Figure \ref{fig:Hillplots}).
-
-In the right-hand Hill-estimator column, the \(k\) on the \(x\)-axis
-corresponds to \(r\) from \eqref{eq:Hill}. The Hill estimator appears to
-be nicely unbiased on Pareto data, but compared to the other two
-estimators, it has a higher variance, as can be seen from the wider
-spread of the simulated curves. This high variance means that that a
-single estimate is less reliable compared to the other two estimators.
-This effect is amplified if one only has a thresholded, and thus smaller
-dataset available, to the extent that the Hill estimates become severely
-flawed (see Section \ref{sec:ML}).
-
-Moreover, the bottom in \ref{Fig:TailSimu} shows clearly that the
-log-moment and maximum-likelihod estimators generalize to the
-exponential case (\(\beta = 1\)), whereas the Hill-estimator does not.
-
-Finally, the performance of Log-Moment and Maximum-Likelihood estimators
-for the scale parameter is shown in figure \ref{Fig:ScaleSimu}. Since
-there is no Hill-estimate of a scale parameter, there are only two
-columns. Both estimators show good performance, with a slight advantage
-for the Maximum-Likelihood estimator. This advantage is paid for by a
-higher computational cost.
+which the threshold \(\ell\) is placed.
+
+The performance of log-Moment and Maximum-Likelihood estimators for the
+tail resp. the scale parameter is shown in Figure \ref{Fig:TailSimu}
+resp. \ref{Fig:ScaleSimu}. Both estimators show good performance, with a
+slight advantage for the Maximum-Likelihood estimator. This advantage is
+paid for by a higher computational cost. Moreover, the bottom row in
+Figure \ref{Fig:TailSimu} shows clearly that the log-Moment and
+Maximum-Likelihood estimators generalize to the exponential case
+(\(\beta = 1\)) whereas a general tail estimator like the Hill-estimator
+would not.
 
@@
 \caption{\label{Fig:TailSimu} Stability Plots for m=100 simulation runs for stable distributed waiting times with a tail parameter of 0.8 (top row), Pareto distributed waiting times with tail parameter 0.8 (middle row) and exponentially distributed waiting times (lower row).
-Left column: log-moment estimator, middle column: MLE, right column: Hill estimator.
+Left column: log-Moment estimator, right column: MLE.
 The grey thin lines are the stability plots for the different simulation runs and the dark lines are their means.
-The red dotted line shows the true tail parameter.
-}\label{fig:TailSimuplots}
+The red dotted line shows the true tail parameter.}\label{fig:TailSimuplots}
 \end{figure}
@@
 
-{\centering \includegraphics[width=0.9\linewidth]{article_springer_files/figure-latex/ScaleSimuplots-1}
+{\centering \includegraphics[width=1\linewidth]{article_springer_files/figure-latex/ScaleSimuplots-1}
 
@@
 \caption{\label{Fig:ScaleSimu} Stability Plots for m=100 simulation runs for stable distributed waiting times with a tail parameter of 0.8 (top row), Pareto distributed waiting times with tail parameter 0.8 (middle row) and exponentially distributed waiting times (lower row).
-Left column: log-moment estimator, right column: MLE.
+Left column: log-Moment estimator, right column: MLE.
 The grey thin lines are the stability plots for the different simulation runs and the dark lines are their means.
-The red dotted line shows the true tail parameter.}\label{fig:ScaleSimuplots}
+The red dotted line shows the true scale parameter.}\label{fig:ScaleSimuplots}
 \end{figure}
@@
 
-Before we apply the POT approach described in Section 5 to the solar
-flare data, we first have to check if all model assumptions are
-fulfilled. The CTRE model is based on three main assumptions, which are
-repeated below. For each assumption, we suggest one means of checking if
-it holds:
+Before we apply the approach described in Section 5 to the solar flare
+data, we first have to check if all model assumptions are fulfilled. The
+CTRE model is based on three main assumptions, which are repeated below.
+For each assumption, we suggest one means of checking if it holds:
 
@@
 \(\ell_0\), the pair sequence \((T(\ell_0, i), X(\ell_0,i))\) is i.i.d.
-An indication if this is true is given by an auto-correlation plot for
-the logarithms (to ensure finite moments) of the two time series.
+An indication if this is true is given by an auto-correlation plot.
+Since we are expecting the inter-exceedance times to be Mittag-Leffler
+distributed and hence to have infinite mean but finite log-moments, we
+first take the logarithms of the times.
 \item[Uncoupled:]
@@
 crossing times, and create a QQ Plot for the Mittag-Leffler
-distribution. Use a log-moment estimate of the tail parameter for the
+distribution. Use a Log-moment estimate of the tail parameter for the
 theoretical / population quantiles of the plot.
+\item[\textbf{Remark:}]
+The ACF plots of course can just give an indication whether there are
+dependencies, since they actually just measure linear dependencies.
+Furthermore, if one calculates the ACF for the logarithmic
+inter-exceedance times, the ACF indicates on the original scale a
+multiplicative dependence.
 \end{description}
@@
 \ref{fig:flare-diagnostics-3} show the diagnostic plots for a minimum
-threshold chosen at the 200th order statistic. There is some residual
+threshold chosen at the 100th order statistic. There is some residual
 autocorrelation for the sequence of threshold exceedance times that is
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{article_springer_files/figure-latex/flare-diagnostics-1-1} \caption{\label{fig:flare-diagnostics-1} Diagnostic plots for the solar flare data: auto-correlation function.}\label{fig:flare-diagnostics-1}
+\includegraphics[width=\textwidth]{article_springer_files/figure-latex/flare-diagnostics-1-1} \caption{\label{fig:flare-diagnostics-1} Diagnostic plots for the solar flare data based on the 100 upper order statistics: auto-correlation and cross-correalation function.}\label{fig:flare-diagnostics-1}
 \end{figure}
@@
 parameter. The dark grey ranges correspond to 95\% confidence intervals,
-which are derived from the asymptotic normality of the log-moments
+which are derived from the asymptotic normality of the Log-moment
 estimators (Cahoy, 2013) and the \(\delta\)-method (Gill and Straka,
@@
 resp.~\(\sigma_0\). The stability plot for the tail stabilizes nicely
-around 0.85 (dashed line), while the scale parameter stabilizes less
+around 0.9 (dashed line), while the scale parameter stabilizes less
 obviously near \(3 \times 10^7\) (dashed line). The growth of the scale
 parameter for lower threshold appears to be closer to linear in
-\(p_{\ell}\), rather than proportional to \(p_{\ell}^{1/0.85}\) as
+\(p_{\ell}\), rather than proportional to \(p_{\ell}^{1/0.9}\) as
 suggested by the Mittag-Leffler fits. The reason for this is likely that
@@
 \includegraphics[width=\textwidth]{article_springer_files/figure-latex/solar-flare-tail-scale-1} \caption{\label{fig:flares} Stability plots for the tail and scale parameter of the Mittag-Leffler distribution of the Solar Flare dataset.
-Dotted horizontal lines are at $\beta = 0.85$ and $\sigma_0 = 3 \times 10^7$ seconds $\approx 0.95$ years.}\label{fig:solar-flare-tail-scale}
+Dotted horizontal lines are at $\beta = 0.9$ and $\sigma_0 = 3 \times 10^7$ seconds $\approx 0.95$ years.}\label{fig:solar-flare-tail-scale}
 \end{figure}
 
-The fit with a Mittag-Leffler distribution (\(\beta = 0.85\)) is good
-(see Figure \ref{fig:flare-diagnostics-3}), though there are signs that
-the power-law tail tapers off for very large inter-threshold crossing
-times. There is no apparent dependence between threshold exceedance
-times and event magnitudes seen in the copula plot (see Figure
-\ref{fig:flare-diagnostics-2}). We also counduct a bootstrapped LRT for
-the null hypothesis of exponentially distributed inter-arrival times and
-received a \(p\)-value of \(p<0.01\).
+The fit with a Mittag-Leffler distribution (\(\beta = 0.9\)) seems to be
+good (see Figure \ref{fig:flare-diagnostics-3}), though there are signs
+that the power-law tail tapers off for very large inter-threshold
+crossing times. There is no apparent dependence between threshold
+exceedance times and event magnitudes seen in the copula plot (see
+Figure \ref{fig:flare-diagnostics-2}). We also conduct a bootstrapped
+LRT for the null hypothesis of exponentially distributed inter-arrival
+times and received a \(p\)-value of \(p<0.01\).
 
@@
 \(k\)-th order statistic, the estimated threshold exceedance time
-distribution is \[
-T(\ell) \sim {\rm ML}(\beta, k^{-1/\beta} \sigma_0), 
-\] where \(\beta = 0.85\) and \(\sigma_0 = 3.0 \times 10^7 {\rm sec}\).
-Unlike the exponential distribution, the Mittag-Leffler distribution is
-not memoryless, and the probability density of the time \(t\) until the
-next threshold crossing will depend on the time \(t_0\) elapsed since
-the last threshold crossing. This density is approximately equal to \[
-p(t|\beta, \sigma_0, \ell, t_0) \approx \frac{f(t + t_0 | \beta, k^{-1/\beta} \sigma_0)}{\mathbf P[T_\ell > t_0]}
+distribution is approximately \[
+T(\ell) \sim {\rm ML}(\hat{\beta}, k^{-1/\hat{\beta}} \hat{\sigma}_0), 
+\] where \(\hat{\beta} = 0.9\) and
+\(\hat{\sigma}_0 = 3.0 \times 10^7 {\rm sec}\). Unlike the exponential
+distribution, the Mittag-Leffler distribution is not memoryless, and the
+probability density of the time \(t\) until the next threshold crossing
+will depend on the time \(t_0\) elapsed since the last threshold
+crossing. This density is approximately equal to \[
+p(t|\beta, \sigma_0, \ell, t_0) = \frac{f(t + t_0 | \beta, k^{-1/\beta} \sigma_0)}{\mathbf P[T_\ell > t_0]}
 \] where \(f(\,\cdot\, | \beta, k^{-1/\beta} \sigma_0)\) is the
@@
 h(t) = \frac{f(t| \beta, k^{-1/\beta} \sigma_0))}{\int_t^\infty f(\tau| \beta, k^{-1/\beta} \sigma_0))\,d\tau}
-\] represents the risk of a threshold crossing per unit time, and is a
+\] approximates the risk of a threshold crossing per unit time, and is a
 decreasing function for the Mittag-Leffler distribution.
@@
 parameter of the distribution of threshold exceedance times,
-\(p_{\ell}\) is the fraction of magnitudes above the threshold, and
-\(\beta\) the exponent of the power law. This ``anomalous'' scaling
+\(p_{\ell}\) is the fraction of magnitudes above the threshold \(\ell\),
+and \(\beta\) the exponent of the power law. This ``anomalous'' scaling
 behaviour in the bursty setting entails two phenomena:
@@
 statistician in the choice between a clustering and a CTRE approach for
-a particular problem. Moreover, we believe it may be possible to unify
-the two approaches by considering CTREs based on MRPs with a
-\emph{stationary}, rather than i.i.d., sequence of magnitudes.
+a particular problem. But the CTRE approach should not be seen as a
+substitute for the usual cluster approach. It was for example also
+observed in Towe et al. (2020) that clusters of extreme events still
+exist after declustering. We believe it is possible to unify the cluster
+approach with our CTRE approach by considering CTREs based on MRPs with
+a \emph{stationary}, rather than i.i.d., sequence of magnitudes. Then
+the times between clusters are asymptotically Mittag-Leffler
+distributed. The identification of clusters in the context of
+heavy-tailed inter-arrival times is an open problem. But what one could
+do in case of observing dependencies between the exceedances: one could
+build natural clusters for example by considering daily maxima instead
+of hourly maxima.
 
@@
 
+\leavevmode\hypertarget{ref-davison1990models}{}%
+Davison, A.C., Smith, R.L., 1990. Models for exceedances over high
+thresholds. Journal of the Royal Statistical Society: Series B
+(Methodological) 52, 393--425.
+
 \leavevmode\hypertarget{ref-HXRBS}{}%
@@
 Spectrometer event list, 1980-1989.
+
+\leavevmode\hypertarget{ref-embrechts2013modelling}{}%
+Embrechts, P., Klüppelberg, C., Mikosch, T., 2013. Modelling extremal
+events: For insurance and finance. Springer Science \& Business Media.
 
@@
 
+\leavevmode\hypertarget{ref-leadbetter1991basis}{}%
+Leadbetter, M.R., 1991. On a basis for `peaks over threshold'modeling.
+Statistics \& Probability Letters 12, 357--362.
+
 \leavevmode\hypertarget{ref-Lee15}{}%
@@
 
+\leavevmode\hypertarget{ref-smith1984threshold}{}%
+Smith, R.L., 1984. Threshold methods for sample extremes, in:
+Statistical Extremes and Applications. Springer, pp. 621--638.
+
+\leavevmode\hypertarget{ref-towe2020modelling}{}%
+Towe, R., Tawn, J., Eastoe, E., Lamb, R., 2020. Modelling the clustering
+of extreme events for short-term risk assessment. Journal of
+Agricultural, Biological and Environmental Statistics 25, 32--53.
+
 \leavevmode\hypertarget{ref-Vajna2013}{}%

### 2020-03-26 article_springer/article_springer_files/ML_estim_simu/ML_estim_simustudy.R

@@ -70,10 +70,4 @@ reshape2::melt(estimates) %>%
 
 save(tbl_ML_estim,file="tbl_ML_estim.RData")
 
-# RMSE
 
-tbl_ML_estim %>%
-  ggplot(aes(true.tail,rmse, colour = method)) +
-  geom_line() + geom_point() +
-  facet_grid(param ~ n, scales = "free_y") +
-  scale_colour_brewer("method", palette = "Set1")

### 2020-03-28 article_springer/article_springer.Rmd
Überarbeitung, Finale Änderung bzgl Reviewer 2
Final changes, adressing Rev2

@@
 library(dplyr)
+library(forecast)
 set.seed(12345)
@@
 
-In the following we denote with $x_L \in [-\infty, +\infty)$ and $x_R \in (-\infty, +\infty]$) the left and right endpoint of the distribution of $J$.
+In the following we denote with $x_L \in [-\infty, +\infty)$ and $x_R \in (-\infty, +\infty]$ the left and right endpoint of the distribution of $J$.
 We assume that the $k$-th magnitude $J_k$ occurs at time
@@
 This means there exist $a_n>0$ and $d_n \in \mathbb{R}$ such that
-$$ a_n^{-1}(J_1 \vee \ldots \vee J_n -d_n) \Rightarrow A \text{ as } n \rightarrow \infty.$$
+\begin{align} \label{assumptionJs}
+a_n^{-1}(J_1 \vee \ldots \vee J_n -d_n) \Rightarrow A \text{ as } n \rightarrow \infty.
+\end{align}
 Hence, the distribution of $A$ is a generalized extreme value distribution (GEV) which distribution function is given by 
 $$ F(x;\xi) = \begin{cases}\exp(-(1+\xi x)^{-1/\xi}) & \xi\neq0 \\ \exp(-\exp(-x)) & \xi = 0\end{cases}.$$ 
-The GEV is subdivided into the Gumbel ($\xi=0$), the Weibull ($\xi<0$) and the Fr'echet ($\xi>0$) family of distributions.
+The GEV is subdivided into the Gumbel ($\xi=0$), the Weibull ($\xi<0$) and the Fréchet ($\xi>0$) family of distributions.
 
@@
 $$
-and since we assume that the $J_k$ have a continuous distribution, there exist 
+and since we assumed that the $J_k$ our out of the domain of attraction of a max-stable distribution $F$ (see \eqref{assumptionJs}), there exist 
 norming functions $a(c)$ and $d(c)$ such that 
@@
 The classical POT approach is based on the fact that exceedances above a high threshold are asymptotically GPD distributed, hence a GPD distribution is fitted to the exceedances above a high enough threshold.
+This approach was well-established a long time ago and is standard in extreme value theory nowadays.
+Hence we just refer here to the according literature (@smith1984threshold, @leadbetter1991basis, @davison1990models), a nice introduction can be found in @beirlantBook Ch.5.3, @embrechts2013modelling Ch.
+6.5.
+or @ColesBook Ch.4.
+Hence, we focus in this article mainly on the inter-exceedance times.
 Due to the Theorem in the last Section we know that for high thresholds the times between exceedances are asymptotically Mittag-Leffler distributed in case of heavy-tailed waiting times between the observations.
-Hence, before we talk about inference for the exceedances in the next section, we discuss inference for Mittag-Leffler distributions.
+In this article we propose to proceed with inter-exceedance times in a similar fashion as with the magnitudes in the classical POT approach, more precisely to fit a Mittag-Leffler distribution via stability plots to the inter-exceedance times.
+Hence, before we talk about inference for the inter-exceedance times in the next section, we first discuss inference for Mittag-Leffler distributions.
 
@@
 @Cahoy2010 proposed a moment estimator of the log-transformed data, which does not require any prior.
-Furthermore, they performed simulation studies illustrating that the log-moment outperforms the fractional moment estimator with respect to bias and root mean squared error (RMSE).
+Furthermore, they performed simulation studies illustrating that the log-Moment outperforms the fractional moment estimator with respect to bias and root mean squared error (RMSE).
 
@@
 In the R Package `MittagLeffleR` [@MittagLeffleR], Maximum Likelihood estimation is implemented via numerical optimization.
-The MLE slightly outperforms the log-moment estimator regarding bias and RMSE for big enough sample sizes, but is extremely computationally intensive.
+The MLE slightly outperforms the log-Moment estimator regarding bias and RMSE for big enough sample sizes, but is extremely computationally intensive.
 Figure \ref{fig:MSE} shows that both estimators perform well, even for small sample sizes.
 
-```{r MSE, echo=FALSE,warning=FALSE, fig.height=7,fig.width=8,fig.align="center", fig.cap="\\label{fig:MSE} MSE for the estimation of tail (left column) and scale (right column) parameters via log-moment estimator and MLE of a Mittag-Leffler sample with varying sample size n=25, 100, 200, varying tails on the x-axis and fixed scale equal to one.", out.width = '90%'}
-load(here::here("article_springer", "article_springer_files", "ML_estim_simu","tbl_ges.RData"))
-tbl_ges %>% 
+```{r MSE, echo=FALSE,warning=FALSE, fig.height=7,fig.width=8,fig.align="center", fig.cap="\\label{fig:MSE} MSE for the estimation of tail (left column) and scale (right column) parameters via log-Moment estimator and MLE of a Mittag-Leffler sample with varying sample size n=25, 100, 200, varying tails on the x-axis and fixed scale equal to one, based on 5000 simulation runs.", out.width = '90%'}
+load(here::here("article_springer", "article_springer_files", "ML_estim_simu","tbl_ML_estim.RData"))
+tbl_ML_estim %>% filter(method=="logMom" | method=="ML")%>%
   filter(n == "25" || n == "100" || n=="200") %>%
   filter(true.scale == "1") %>% 
-  ggplot(aes(true.tail, mse, colour = method, group=method)) + 
+  ggplot(aes(true.tail, rmse, colour = method, group=method)) + 
   geom_line() + geom_point() + 
@@
 where $X_{(1)} \geq X_{(2)} \geq \ldots \geq X_{(n)}$ denote the order statistics in decreasing order of a sequence $X_1,\ldots,X_n$.
-However, these methods are statistically less efficient since they only use a portion of the information contained in the data, as mentioned by @kozubowski2001.
-Moreover, the Hill estimator requires a tuning parameter, denoted with $r$ in \eqref{eq:Hill}.
-Additionaly, the estimator only performs reliably well for distributions close to Pareto [see @Resnick97].
+The Hill estimator only performs reliably well for distributions close to Pareto [see @Resnick97].
+It heavily depends on the choice of $r$ in \eqref{eq:Hill}, hence on the number of order statistics entering into \eqref{eq:Hill}.
 Figure \ref{fig:Hillplots} shows Hill plots for Mittag-Leffler simulated data, with varying sample sizes and tails.
@@
 To estimate the tail parameter of a Mittag-Leffler distribution with the Hill estimator, the sample size has to be much larger and one has to choose a large tuning parameter $r$.
-In case that only events above a high threshold are recorded, even $n=1000$ events are unrealistic.
-Furthermore the Hill estimator of course completely fails if the inter-arrival times are exponentially distributed and not heavy-tailed.
-We will come back to the problems with the Hill estimtator in Section \ref{Simulationstudy}.
+In case that only events above a high threshold are recorded, $n=10000$ events are unrealistic.
+There is a vast literature on bias-reduced versions of the Hill estimator and on the optimal choice of $r$, mainly based on imposed second-order regular variation conditions [see e.g.
+@beirlantBook, Ch.4.4 and 4.7 and references in it].
+Also, there are lot of other tail-index estimators not taken under consideration in our article, since this would go beyond the scope of our article.
+However, we know from the Theorem in Section \ref{sec:scaling} that the inter-exceedance times are asymptotically Mittag-Leffler distributed.
+So all these general tail (and scale) estimation methods are statistically less efficient since they only use a portion of the information contained in the data, as mentioned by @kozubowski2001.
+Furthermore, the Hill estimator of course completely fails, if the inter-arrival times are exponentially distributed and not heavy-tailed.
+Hence, we propose to use the log-Moment estimator or the MLE for Mittag-Leffler distributions.
 
-```{r Hillplots, echo=FALSE,warning=FALSE, fig.align="center", fig.cap="\\label{fig:Hillplots} Hillplots for simulated Mittag-Leffler data with true tail 0.8 and sample size 200 (left) and 1000 (right), with number of upper order statics r on which the Hill estimator is based on the x-axis.
+```{r Hillplots, echo=FALSE,warning=FALSE, fig.align="center", fig.cap="\\label{fig:Hillplots} Hillplots for simulated Mittag-Leffler data with true tail 0.8 and sample size 200 (left) and 10000 (right), with number of upper order statics r on which the Hill estimator is based on the x-axis.
 ", out.width = '90%'}
@@
 
+set.seed(1234)
 hill_estim_plot<-function(k_min,data,k_max=n,true_tail){
@@
 }
-
 data_ml_1<-rml(n=200,tail=0.8,scale=1)
 p1<-hill_estim_plot(k_min=30,data=data_ml_1,true_tail=0.8) +
-  ggtitle("Hill plot, Mittag-Leffler data, n=200")
+  ggtitle("Hill plot, ML-data, n=200")
 
-data_ml_2<-rml(n=1000,tail=0.8,scale=1)
-p2<-hill_estim_plot(k_min=30,data=data_ml_2,true_tail=0.8) +
-  ggtitle("Hill plot, Mittag-Leffler data, n=1000")
+data_ml_2<-rml(n=10000,tail=0.8,scale=1)
+p2<-hill_estim_plot(k_min=30,k_max=200,data=data_ml_2,true_tail=0.8) +
+  ggtitle("Hill plot, ML-data, n=10000")
 
@@
 Figure \ref{Fig:LRT} displays the (simulated) power for the bootstrapped LRT for Mittag-Leffler distributions with varying tail parameters based on 1000 simulation runs.
-As expected, the power decreases for tail parameters close to one, since the Mittag-Leffler distribution converges as $\beta \uparrow 1$ to an exponential distribution; it becomes hard to differentiate a Mittag-Lefller distribution from an exponential.
+As expected, the power decreases for tail parameters close to one, since the Mittag-Leffler distribution converges as $\beta \uparrow 1$ to an exponential distribution; it becomes hard to differentiate a Mittag-Leffler distribution from an exponential.
 
@@
 
-2. Choose e.g. $K_0 = 5$, and for each $k$ ranging from $K_0 +1$ to $K + 1$: 
-    a) extract the set $\mathcal T_k$ of exceedance times of between the magnitudes exceeding the threshold $X_{(k)}$
+2. Choose a minimum number of exceedances $K_0\leq K$, e.g. $K_0 = 5$, and for each $k$ ranging from $K_0$ to $K$: 
+    a) extract the set $\mathcal T_k$ of exceedance times between the magnitudes exceeding the threshold $X_{(k)}$
     b) fit a Mittag-Leffler distribution to $\mathcal T_k$, resulting in the parameter
@@
 To clarify Step 4: Recall that by the theorem, $\sigma_k / b(1/p_{\ell})$ is expected to stabilize 
-around a constant as $k \downarrow K_0$. Since $b$ is regularly varying with parameter
+around a constant as $k$ gets smaller. Since $b$ is regularly varying with parameter
 $1/\beta$, we have $b(1/p_{\ell}) = p_{\ell}^{-1/\beta} / L(1/p_{\ell})$ for some slowly varying function $L$. 
-Approximating $p_{\ell} \approx \hat p_{\ell} := k / n$, we have 
+Approximating $p_{\ell}$ by $\hat p_{\ell} := k / n$, we have 
 $$\text{const} \approx \sigma_k / b(1/p_{\ell}) = \sigma_k \times p_{\ell}^{1/\beta} L(1/p_{\ell}) \approx \sigma_k \times k^{1/\beta} n^{-1/\beta} L(n/k)$$
@@
 $\sigma_k k^{1/\beta}$ stabilizes.
+
+**Remark**:
+
+: We approximated $p_{\ell}$, the probability that an event is larger than $l$, by its relative frequency.
+One could also approximate this tail probability by the GPD distribution fitted to the exceedances.
 
@@
 
-To test our inference method via stability plots, we have simulated $m=100$ times $n=10000$ independent waiting time and magnitude pairs $(W_k, J_k)$ for waiting times that follow
+To test our inference method via stability plots, we have simulated $m=100$ datasets with $n=10000$ independent waiting time and magnitude pairs $(W_k, J_k)$ for waiting times that follow
 
@@
 + rows correspond to cases (i), (ii) and (iii), and
-+ columns correspond to estimators (log-moment estimator, maximum-likelihood, and Hill estimator).
++ columns correspond to estimators (log-Moment estimator, Maximum-Likelihood).
 
@@
 threshold $\ell$ is placed. 
-Note that the Hill estimator is based on the waiting times, not on the 
-inter-exceedance times, meaning that the estimation is based on more data. 
-If one were to base the Hill-estimation only on the inter-exceedance times, 
-the sample size would be too small and it would be impossible to deduce an 
-estimate for the tail parameter from the plots (compare Figure \ref{fig:Hillplots}).
+<!-- Note that the Hill estimator is based on the waiting times, not on the  -->
+<!-- inter-exceedance times, meaning that the estimation is based on more data.  -->
+<!-- If one were to base the Hill-estimation only on the inter-exceedance times,  -->
+<!-- the sample size would be too small and it would be impossible to deduce an  -->
+<!-- estimate for the tail parameter from the plots (compare Figure \ref{fig:Hillplots}).  -->
 
-In the right-hand Hill-estimator column, the $k$ on the $x$-axis corresponds to
-$r$ from \eqref{eq:Hill}.
-The Hill estimator appears to be nicely unbiased on Pareto data,
-but compared to the other two estimators, it has a higher variance, 
-as can be seen from the wider spread of the simulated curves. 
-This high variance means that that a single estimate is less reliable compared
-to the other two estimators. 
-This effect is amplified if one only has a thresholded, and thus smaller dataset
-available, to the extent that the Hill estimates become severely flawed
-(see Section \ref{sec:ML}).
+<!-- In the right-hand Hill-estimator column, the $k$ on the $x$-axis corresponds to -->
+<!-- $r$ from \eqref{eq:Hill}. -->
+<!-- The Hill estimator appears to be nicely unbiased on Pareto data, -->
+<!-- but compared to the other two estimators, it has a higher variance,  -->
+<!-- as can be seen from the wider spread of the simulated curves.  -->
+<!-- This high variance means that that a single estimate is less reliable compared -->
+<!-- to the other two estimators.  -->
+<!-- This effect is amplified if one only has a thresholded, and thus smaller dataset -->
+<!-- available, to the extent that the Hill estimates become severely flawed -->
+<!-- (see Section \ref{sec:ML}).  -->
 
-Moreover, the bottom in \ref{Fig:TailSimu} shows clearly that the log-moment 
-and maximum-likelihod estimators generalize to the exponential case ($\beta = 1$), 
-whereas the Hill-estimator does not.
+The performance of log-Moment and Maximum-Likelihood estimators for the tail resp.
+the scale parameter is shown in Figure \ref{Fig:TailSimu} resp.
+\ref{Fig:ScaleSimu}.
+Both estimators show good performance, with a slight advantage for the Maximum-Likelihood estimator.
+This advantage is paid for by a higher computational cost.
+Moreover, the bottom row in Figure \ref{Fig:TailSimu} shows clearly that the log-Moment and Maximum-Likelihood estimators generalize to the exponential case ($\beta = 1$) whereas a general tail estimator like the Hill-estimator would not.
 
-Finally, the performance of Log-Moment and Maximum-Likelihood estimators for the
-scale parameter is shown in figure \ref{Fig:ScaleSimu}. 
-Since there is no Hill-estimate of a scale parameter, there are only two columns. 
-Both estimators show good performance, with a slight advantage for the 
-Maximum-Likelihood estimator. This advantage is paid for by a higher computational 
-cost.
+<!-- Since there is no Hill-estimate of a scale parameter, there are only two columns.  -->
 
 ```{r TailSimuplots, message=FALSE,echo=FALSE,fig.height=7,fig.align="center",fig.cap="\\label{Fig:TailSimu} Stability Plots for m=100 simulation runs for stable distributed waiting times with a tail parameter of 0.8 (top row), Pareto distributed waiting times with tail parameter 0.8 (middle row) and exponentially distributed waiting times (lower row).
-Left column: log-moment estimator, middle column: MLE, right column: Hill estimator.
+Left column: log-Moment estimator, right column: MLE.
 The grey thin lines are the stability plots for the different simulation runs and the dark lines are their means.
-The red dotted line shows the true tail parameter.
-", fig.show='hold', out.width = '100%'}
+The red dotted line shows the true tail parameter.", fig.show='hold', out.width = '100%'}
 
@@
 #Hill estimator
-hill_Ex1_tail <-
-  ggplot() + geom_line(data = tbl_estimates_tail08_hill_Ex1,
-                       aes(x = k, y = value, group = rep),
-                       colour = "lightgrey") +
-  coord_cartesian(ylim = c(0.5, 1.5)) +
-  geom_line(data=means.tbl_hill_Ex1,aes(x=k, y=mw),colour="black") + 
-  ylab("Estimated tail") +
-  geom_hline(yintercept=0.8, linetype="dashed", color = "red")+ xlab("r")
+# hill_Ex1_tail <-
+#   ggplot() + geom_line(data = tbl_estimates_tail08_hill_Ex1,
+#                        aes(x = k, y = value, group = rep),
+#                        colour = "lightgrey") +
+#   coord_cartesian(ylim = c(0.5, 1.5)) +
+#   geom_line(data=means.tbl_hill_Ex1,aes(x=k, y=mw),colour="black") + 
+#   ylab("Estimated tail") +
+#   geom_hline(yintercept=0.8, linetype="dashed", color = "red")+ xlab("r")
 
@@
 
-#Hill estimator
-hill_Ex2_tail <-
-  ggplot() + geom_line(aes(x = k, y = value, group = rep),
-                       colour = "lightgrey",
-                       data = tbl_estimates_Ex2_Pareto_tail08_hill_times) +
-  coord_cartesian(ylim = c(0.5, 1.5)) +
-  geom_line(aes(x = k, y = mw), colour = "black", data = means.tbl_hill_times_Ex2) + 
-  ylab("Estimated tail") +
-  geom_hline(yintercept=0.8, linetype="dashed", color = "red")+ xlab("r")
+# #Hill estimator
+# hill_Ex2_tail <-
+#   ggplot() + geom_line(aes(x = k, y = value, group = rep),
+#                        colour = "lightgrey",
+#                        data = tbl_estimates_Ex2_Pareto_tail08_hill_times) +
+#   coord_cartesian(ylim = c(0.5, 1.5)) +
+#   geom_line(aes(x = k, y = mw), colour = "black", data = means.tbl_hill_times_Ex2) + 
+#   ylab("Estimated tail") +
+#   geom_hline(yintercept=0.8, linetype="dashed", color = "red")+ xlab("r")
 
@@
 
-#Hill estimator
-hill_Ex3_tail <-
-  ggplot() + geom_line(aes(x = k, y = value, group = rep),
-                       colour = "lightgrey",
-                       data = tbl_estimates_Example3_Exp_hill_times) +
-  coord_cartesian(ylim = c(0.5, 10)) +
-  geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_hill_times_Ex3) + 
-  ylab("Estimated tail") + 
-  geom_hline(yintercept=1, linetype="dashed", color = "red")+ xlab("r")
-
+# #Hill estimator
+# hill_Ex3_tail <-
+#   ggplot() + geom_line(aes(x = k, y = value, group = rep),
+#                        colour = "lightgrey",
+#                        data = tbl_estimates_Example3_Exp_hill_times) +
+#   coord_cartesian(ylim = c(0.5, 10)) +
+#   geom_line(aes(x=k, y=mw),colour="black",data=means.tbl_hill_times_Ex3) + 
+#   ylab("Estimated tail") + 
+#   geom_hline(yintercept=1, linetype="dashed", color = "red")+ xlab("r")
+# 
 grid.arrange(
@@
   arrangeGrob(mle_Ex1_tail, mle_Ex2_tail, mle_Ex3_tail,top="MLE"),
-  arrangeGrob(hill_Ex1_tail,hill_Ex2_tail,hill_Ex3_tail,top="Hill"),
-  ncol=3
+  # arrangeGrob(hill_Ex1_tail,hill_Ex2_tail,hill_Ex3_tail,top="Hill"),
+  ncol=2
 )
@@
 ```{r ScaleSimuplots, message=FALSE,echo=FALSE,fig.height=7,fig.align="center",fig.cap="\\label{Fig:ScaleSimu} Stability Plots for m=100 simulation runs for stable distributed waiting times with a tail parameter of 0.8 (top row), Pareto distributed waiting times with tail parameter 0.8 (middle row) and exponentially distributed waiting times (lower row).
-Left column: log-moment estimator, right column: MLE.
+Left column: log-Moment estimator, right column: MLE.
 The grey thin lines are the stability plots for the different simulation runs and the dark lines are their means.
-The red dotted line shows the true tail parameter.", fig.show='hold', out.width = '90%'}
+The red dotted line shows the true scale parameter.", fig.show='hold', out.width = '100%'}
 #Scale Parameter
@@
 
-Before we apply the POT approach described in Section 5 to the solar flare data, we first have to check if all model assumptions are fulfilled.
+Before we apply the approach described in Section 5 to the solar flare data, we first have to check if all model assumptions are fulfilled.
 The CTRE model is based on three main assumptions, which are repeated below.
@@
   $\ell_0$, the pair sequence $(T(\ell_0, i), X(\ell_0,i))$ is i.i.d. 
-  An indication if this is true is given 
-  by an auto-correlation plot for the logarithms (to ensure finite moments) 
-  of the two time series.
+  An indication if this is true is given by an auto-correlation plot.
+Since we   are expecting the inter-exceedance times to be Mittag-Leffler distributed and hence to have infinite mean but finite log-moments, we first take the logarithms of the times.
 
@@
   and create a QQ Plot for the Mittag-Leffler distribution. 
-  Use a log-moment estimate of the tail parameter for the theoretical / population 
+  Use a Log-moment estimate of the tail parameter for the theoretical / population 
   quantiles of the plot.
 
-Figures \ref{fig:flare-diagnostics-1}, \ref{fig:flare-diagnostics-2} and \ref{fig:flare-diagnostics-3} show the diagnostic plots for a minimum threshold chosen at the 200th order statistic.
+**Remark:**
+
+: The ACF plots of course can just give an indication whether there are dependencies, since they actually just measure linear dependencies.
+Furthermore, if one calculates the ACF for the logarithmic inter-exceedance times, the ACF indicates on the original scale a multiplicative dependence.
+
+Figures \ref{fig:flare-diagnostics-1}, \ref{fig:flare-diagnostics-2} and \ref{fig:flare-diagnostics-3} show the diagnostic plots for a minimum threshold chosen at the 100th order statistic.
 There is some residual autocorrelation for the sequence of threshold exceedance times that is not accounted for by the CTRE model.
 
-```{r flare-diagnostics-1, fig.height=7, fig.cap="\\label{fig:flare-diagnostics-1} Diagnostic plots for the solar flare data: auto-correlation function."}
-flares_ctre <- flares %>% ctre() %>% thin(k = 150)
-acf(flares_ctre)
+```{r flare-diagnostics-1, fig.height=7, fig.cap="\\label{fig:flare-diagnostics-1} Diagnostic plots for the solar flare data based on the 100 upper order statistics: auto-correlation and cross-correalation function."}
+flares_ctre <- flares %>% ctre() %>% thin(k = 100)
+log_interarrivals_flares<-log(interarrival(flares_ctre))
+exceedances_flares<-log(magnitudes(flares_ctre))
+acf1<-ggAcf(log_interarrivals_flares)+ggtitle("ACF-plot of log(T(l))")+theme(plot.title = element_text(hjust=0.5))
+acf2<-ggAcf(exceedances_flares)+ggtitle("ACF-plot of X(l)")+theme(plot.title = element_text(hjust=0.5))
+ccf1<-ggCcf(log_interarrivals_flares,exceedances_flares)+ggtitle("CCF-plot of log(T(l)) & X(l)")+theme(plot.title = element_text(hjust=0.5))
+ccf2<-ggCcf(exceedances_flares,log_interarrivals_flares)+ggtitle("CCF-plot of X(l) & log(T(l))")+theme(plot.title = element_text(hjust=0.5))
+grid.arrange(acf1,acf2,ccf1,ccf2,ncol=2)
 ```
@@
 ```{r flare-diagnostics-2, fig.height=4.5, fig.width=4.5, fig.align="center",fig.cap="\\label{fig:flare-diagnostics-2} Diagnostic plots for the solar flare data: empirical copula.",out.width="70%"}
-empcopula(flares_ctre) + ggtitle("Empirical Copula: Exceedance Time vs. Exceedance")
+empcopula(flares_ctre) + ggtitle("Empirical Copula: T(l) vs. X(l)")+theme(plot.title = element_text(hjust=0.5))
 ```
@@
 extRemes::qqplot(x = log(sample_data), y = log(population_data), 
-                 main = "QQ-plot Exceedance Times vs Mittag-Leffler",
+                 main = "QQ-plot: Exceed. Times vs Mittag-Leffler",
                  xlab = "log Exceedance Times", 
@@
 Figure \ref{fig:flares} shows the stability plots for the solar flare data, on the left for the tail parameter and on the right for the scale parameter.
-The dark grey ranges correspond to 95% confidence intervals, which are derived from the asymptotic normality of the log-moments estimators [@Cahoy2013] and the $\delta$-method [@MittagLeffleR]; dashed lines show the deduced true values of $\beta$ resp.\ $\sigma_0$.
-The stability plot for the tail stabilizes nicely around 0.85 (dashed line), while
+The dark grey ranges correspond to 95% confidence intervals, which are derived from the asymptotic normality of the Log-moment estimators [@Cahoy2013] and the $\delta$-method [@MittagLeffleR]; dashed lines show the deduced true values of $\beta$ resp.\ $\sigma_0$.
+The stability plot for the tail stabilizes nicely around 0.9 (dashed line), while
 the scale parameter stabilizes less obviously near $3 \times 10^7$ (dashed line).
 The growth of the scale parameter for lower threshold appears to be closer to linear in $p_{\ell}$, 
-rather than proportional to $p_{\ell}^{1/0.85}$ as suggested by the Mittag-Leffler
+rather than proportional to $p_{\ell}^{1/0.9}$ as suggested by the Mittag-Leffler
 fits. The reason for this is likely that the overall goodness of fit as 
-compared to an exponential distribution is improved due to the 
-peaked shape of the Mittag-Leffler distribution near $0$,
+compared to an exponential distribution is improved due to the peaked shape of the Mittag-Leffler distribution near $0$,
 rather than its tail behaviour at $\infty$.
@@
 ```{r solar-flare-tail-scale, message=FALSE, fig.height=4.5, fig.width=8, fig.cap="\\label{fig:flares} Stability plots for the tail and scale parameter of the Mittag-Leffler distribution of the Solar Flare dataset.
-Dotted horizontal lines are at $\\beta = 0.85$ and $\\sigma_0 = 3 \\times 10^7$ seconds $\\approx 0.95$ years."}
+Dotted horizontal lines are at $\\beta = 0.9$ and $\\sigma_0 = 3 \\times 10^7$ seconds $\\approx 0.95$ years."}
 thin_flares_ctre <- flares %>% ctre() %>% thin(k = 700)
@@
 
-The fit with a Mittag-Leffler distribution ($\beta = 0.85$) is good (see Figure \ref{fig:flare-diagnostics-3}), though there are signs that the power-law tail tapers off for very large inter-threshold crossing times.
+The fit with a Mittag-Leffler distribution ($\beta = 0.9$) seems to be good (see Figure \ref{fig:flare-diagnostics-3}), though there are signs that the power-law tail tapers off for very large inter-threshold crossing times.
 There is no apparent dependence between threshold exceedance times and event magnitudes seen in the copula plot (see Figure \ref{fig:flare-diagnostics-2}).
-We also counduct a bootstrapped LRT for the null hypothesis of exponentially distributed inter-arrival times and received a $p$-value of $p<0.01$.
+We also conduct a bootstrapped LRT for the null hypothesis of exponentially distributed inter-arrival times and received a $p$-value of $p<0.01$.
 
@@
 According to Figure \ref{fig:flares}, for a threshold $\ell$ at the $k$-th order 
-statistic, the estimated threshold exceedance time distribution is 
+statistic, the estimated threshold exceedance time distribution is approximately
 $$
-T(\ell) \sim {\rm ML}(\beta, k^{-1/\beta} \sigma_0), 
+T(\ell) \sim {\rm ML}(\hat{\beta}, k^{-1/\hat{\beta}} \hat{\sigma}_0), 
 $$
-where $\beta = 0.85$ and $\sigma_0 = 3.0 \times 10^7 {\rm sec}$. 
+where $\hat{\beta} = 0.9$ and $\hat{\sigma}_0 = 3.0 \times 10^7 {\rm sec}$. 
 Unlike the exponential distribution, the Mittag-Leffler distribution is not memoryless, and the probability density of the time $t$ until the next threshold crossing will depend on the time $t_0$ elapsed since the last threshold crossing.
@@
 $$
-p(t|\beta, \sigma_0, \ell, t_0) \approx \frac{f(t + t_0 | \beta, k^{-1/\beta} \sigma_0)}{\mathbf P[T_\ell > t_0]}
+p(t|\beta, \sigma_0, \ell, t_0) = \frac{f(t + t_0 | \beta, k^{-1/\beta} \sigma_0)}{\mathbf P[T_\ell > t_0]}
 $$
@@
 $$
-represents the risk of a threshold crossing per unit time, and is a decreasing function for the Mittag-Leffler distribution. 
+approximates the risk of a threshold crossing per unit time, and is a decreasing function for the Mittag-Leffler distribution. 
 ```{r hazard, fig.height=4, fig.cap="\\label{fig:hazard} Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\\beta = 0.8$, $\\sigma_0 = 1$).
@@
 Moreover, we have derived the following non-linear scaling behaviour: $\sigma \sim p_{\ell}^{-1/\beta}$, where $\sigma$ is the scale parameter of the distribution of threshold
-exceedance times, $p_{\ell}$ is the fraction of magnitudes above the threshold, and $\beta$ the exponent of the power law. 
+exceedance times, $p_{\ell}$ is the fraction of magnitudes above the threshold $\ell$, and $\beta$ the exponent of the power law. 
 This "anomalous" scaling behaviour in the bursty setting entails two phenomena:
@@
 event sequences of magnitudes are generalized to stationary sequences of
-event magnitudes (subject to a mixing condition). The two approaches are fundamentally different: A clustering model assumes that each event 
-belongs to one particular (latent) group of events. For bursts, however, the aim is to identify an underlying scale-free pattern in the event 
-dynamics, which is often characteristic of complex systems. It is an interesting open problem to develop quality criteria, based
-e.g.
+event magnitudes (subject to a mixing condition).
+The two approaches are fundamentally different: A clustering model assumes that each event belongs to one particular (latent) group of events.
+For bursts, however, the aim is to identify an underlying scale-free pattern in the event
+dynamics, which is often characteristic of complex systems.
+It is an interesting open problem to develop quality criteria, based e.g.
 on measures of surprise [@Lee15], which guide an applied statistician in the choice between a clustering and a CTRE approach for a particular problem.
-Moreover, we believe it may be possible to unify the two approaches by considering CTREs based on MRPs with a _stationary_, rather than i.i.d., sequence of magnitudes.
+But the CTRE approach should not be seen as a substitute for the usual cluster approach.
+It was for example also observed in @towe2020modelling that clusters of extreme events still exist after declustering.
+We believe it is possible to unify the cluster approach with our CTRE approach by considering CTREs based on MRPs with a _stationary_, rather than i.i.d., sequence of magnitudes.
+Then the times between clusters are asymptotically Mittag-Leffler distributed.
+The identification of clusters in the context of heavy-tailed inter-arrival times is an open problem.
+But what one could do in case of observing dependencies between the exceedances: one could build natural clusters for example by considering daily maxima instead of hourly maxima.
 

### 2020-03-29 article_springer/changes.Rmd

--- 2020-03-11 changes.Rmd
@@
 date: "11 März 2020"
+bibliography: CTRMstats.bib
 output: pdf_document
@@
 * We have added the following sentence near the end of Section 3: 
-"We caution the reader that, somewhat confusingly, there is another distribution
-called the "light-tailed" Mittag-Leffler distribution.  This is in fact the 
-limiting distribution of the renewal process $N(t)$ above (see @limitCTRW)."
+"We caution the reader that, somewhat confusingly, there is another distribution called the "light-tailed" Mittag-Leffler distribution.
+This is in fact the limiting distribution of the renewal process $N(t)$ above (see @limitCTRW)."
 
@@
 2004.
-“Limit Theorems forContinuous-Time Random Walks with Infinite Mean Waiting Times.”J.
+“Limit Theorems for Continuous-Time Random Walks with Infinite Mean Waiting Times.”J.
 Appl.Probab.41 (3): 623–38.
@@
 
-* In case of a continuous distribution one can choose the normalization in such a way that a non-degenerate limit distributions exists, but this is not neccessarily true for a linear normalization.
+* In case of a continuous distribution one can choose the normalization in such a way that a non-degenerate limit distributions exists, but this is not necessarily true for a linear normalization.
 We just forgot to add the assumption, that the distribution of the magnitudes is out of the domain of attraction of an extreme value distribution.
-We added this accordingly.
+We added this assumption in Section 2.
 
@@
 "(Section 5 and 6) In these 2 sections it is implied that p = k/n ....
-While a complete rigor in the discussion on the statistical methodology is perhaps not necessary, itis important for the reader to clearly see where “asymptotic approximations” are applied."
+While a complete rigor in the discussion on the statistical methodology is perhaps not necessary, it is important for the reader to clearly see where “asymptotic approximations” are applied."
 
-* We have re-written Sections 5 & 6, and made sure that $p$ is used as the theoretical exceedance probability, whereas the fraction of exceedances $k/n$ is denoted as $\hat p$.
+* We have re-written Sections 5 & 6, and made sure that $p_l$ is used as the theoretical exceedance probability, whereas the fraction of exceedances $k/n$ is denoted as $\hat p_l$.
 We have also clarified throughout where we assuming approximations.
@@
 Also a few lines after that, they claim that the scale cannot be estimated.
-This s not entirely true.
-The classic work of Peter Hall { entitled On Some Simple Estimates of an Exponent of Regular Variation and published in the Journal of the Royal Statistical Society.
+This is not entirely true.
+The classic work of Peter Hall ( entitled On Some Simple Estimates of an Exponent of Regular Variation and published in the Journal of the Royal Statistical Society.
 Series B (Methodological), Vol.
@@
 1 (1982), pp.
-37(42)does include natural
-asymptotically normal estimators for both the tail exponent and the scale. This said, there
+37(42) does include natural asymptotically normal estimators for both the tail exponent and the scale.
+This said, there
 is a tremendous amount of work on bias correction for the Hill estimator (and I assume
@@
 
-* KATHI TO DO
+* Thank you for this valuable hint and the reference for the article of Peter Hall.
+We added a sentence regarding bias-reduced versions of the Hill estimator at the end of Section 4.
+Moreover, we decided to discard the Hill estimator from the simulation study since we already gave at the end of Section 4 sufficient arguments, why we propose to use a parametric estimator based on the Mittag-Leffler distribution instead of a general tail index estimator.
+Otherwise this would just confuse the reader.
 
-"Last but not least, given that the authors are dealing with more or less standard semi- parametric estimation of heavy-tail exponents and scales, they could formulate limit the- orems on the asymptotic distribution of their statistics and derive Wold-type confidence intervals for the estimated parameters.
+"Last but not least, given that the authors are dealing with more or less standard semi-parametric estimation of heavy-tail exponents and scales, they could formulate limit theorems on the asymptotic distribution of their statistics and derive Wold-type confidence intervals for the estimated parameters.
 ...
@@
 33. We have commented as follows: 
-    "The stability plot for the tail stabilizes nicely around 0.85 (dashed line), while 
+    "The stability plot for the tail stabilizes nicely around 0.9 (dashed line), while 
     the scale parameter stabilizes less obviously near $3 \times 10^7$ (dashed line).
     The growth of the scale parameter for lower threshold appears to be closer to linear in $p$, 
-    rather than proportional to $p^{1/0.85}$ as suggested by the Mittag-Leffler
+    rather than proportional to $p^{1/0.9}$ as suggested by the Mittag-Leffler
     fits. The reason for this is likely that the overall goodness of fit as 
@@
 random variable $\tau(l)$ could be substituted by any other independent geo-
-metric (or exponential) random variable with mean $1/p(l)$."
+metric (or exponential) random variable with mean $1/p(l)$. Moreover, I think, this would simplify some arguments, including the proof of the theorem."
 
-*
-
-"Moreover, I think, this would simplify some arguments, including the proof of the theorem."
-
-* TO DO
+* One connection to the Peaks-Over-Threshold (POT) method is, that one has to apply the classical POT approach to the magnitudes.
+To make this more clear for the reader, we added a comment at the beginning of Section 4.
+Additionally, inspirited by the POT method, as you said, we propose to fit the inter-exceedance times in a similar fashion: namely, by fitting a Mittag-Leffler distribution to the inter-exceedance times between the peaks over threshold via stability plots.
+It is true, that the underlying distribution of the magnitudes, in the way we defined the algorithm, gets nearly ignored.
+A probable extension of our algorithm could be to approximate the tail probability $p_{\ell}$ for very large thresholds by the GPD distribution, which was in a step before fitted to the magnitudes.
+We add a remark on this after the algorithm.
 
@@
 
-* To DO
+* The CTRE model is not intended as a substitute for the usual cluster models.
+It should be more seen as a complement.
+If there are dependencies in the data, one should first decluster the data.
+If there are still clusters after (see for example p.3 in @towe2020modelling), the CTRE can maybe account for this behavior.
+We add a comment on this to the Discussion & Conclusion.
 
@@
 
-* To DO
+* That is of course true.
+We calculated here the auto-correlations under the assumption that the underlying data is Mittag-Leffler distributed.
+The log-Moments of a Mittag-Leffler distribution exist.
+We added a comment on this in Section 7 to the part "i.i.d.".
+It is also true that the log-transformation can influence the appearance of the graph.
+ACFs can always just discover linear dependencies.
+However, this is just a diagnostic tool to indicate whether the independence assumption is justified.
+We added for this a comment in the manuscript as well in Section 7 after describing the diagnostic tools.
 
-"The authors finally apply two methods (log-moments and MLE) to es-
-timate parameters of the limiting Mittag-Leffler distribution, and obtain in
-the process an estimator of the key tail parameter $\beta$. These methods seems
-to outperform the standard Hill estimator in a simulation study although
+"The authors finally apply two methods (log-moments and MLE) to estimate parameters of the limiting Mittag-Leffler distribution, and obtain in the process an estimator of the key tail parameter $\beta$.
+These methods seems to outperform the standard Hill estimator in a simulation study although
 the latter utilizes a much larger data set typically. This phenomena asks
@@
 
-* TO DO
+* It's in interesting idea to use the proposed method for the estimation of the tail index for any power law with $\beta$ < 1.
+However, this goes beyond the scope of our article.
+In our article we know from the theory that the inter-exceedance times which we want to model are approximately Mittag-Leffler distributed, hence its natural to use here specific Mittag-Leffler scale and tail estimators.
 
@@
 
-* TO DO
+* We revised the whole manuscript according typos, added the missing assumption for the magnitudes and replaced the proof of the theorem by a new, simplified version (EVTL NOCH ANPASSEN).
 
-"I also do not see a clear connection with the POT method suggested in the abstract, mainly because exceedances really play insignifficant role in the analysis.""
+"I also do not see a clear connection with the POT method suggested in the abstract, mainly because exceedances really play insignifficant role in the analysis."
 
-* TO DO
+* See above.
 
@@
 
-* We added a definition for the left and the right point.
-  NOCH ETWAS ZU DEN J_k ERGAENZEN.
+* We added a definition for the left and the right point. For the role of the magnitudes, see above.
 
@@
 
-* You are completely right again. This was also a typo. We changed this accordingly.
+* You are completely right again. This was also a typo. We fixed that.
 
@@
 
-"P.5. You seem to to assume that your $l$ grows at a very precise rate - could this be a problem?"
+"P.5. You seem to assume that your $l$ grows at a very precise rate - could this be a problem?"
 
-* PETER TO DO
+* TO DO (evtl noch anpassen) We gave a completely new proof. Hence this point no longer applies.
 
@@
 
-* We added some more explanation to the last two lines.
+* (EVTL noch anpassen) We added some more explanation to the last two lines.
 
@@
 
-* TO DO
+* For very small tail indices, the (R)MSE is large due to a large variance that results from the fact that in case of a very small tail index single very large events can happen.
+In the submitted version of the article the simulation study was based on one thousand simulation runs.
+This was maybe a little bit too small, hence I repeated the study with five thousand runs and now the MSE looks for very small indices more acceptable.
+I also changed to RMSE since it is easier to interpret.
 
@@
 
-* In the pareto case the Hill estimator is less biased, but in all cases it has a higher variance compared to the other two estimators. We reformulated this part.
+* In the Pareto case the Hill estimator is less biased, but in all cases it has a higher variance compared to the other two estimators. We reformulated the whole part.
 
@@
 
-* This is an approximation. We replaced the equality sign by the approximately-equal sign.
+* This is an approximation. We changed "equals" to "is approximately equal to".
 

### 2020-03-29 article_springer/article_springer.Rmd
Bügele das Englisch

@@
 $$
-and since we assumed that the $J_k$ our out of the domain of attraction of a max-stable distribution $F$ (see \eqref{assumptionJs}), there exist 
+and since the $J_k$ lie in the domain of attraction of a max-stable distribution $F$ (see \eqref{assumptionJs}), there exist 
 norming functions $a(c)$ and $d(c)$ such that 
@@
 The classical POT approach is based on the fact that exceedances above a high threshold are asymptotically GPD distributed, hence a GPD distribution is fitted to the exceedances above a high enough threshold.
-This approach was well-established a long time ago and is standard in extreme value theory nowadays.
-Hence we just refer here to the according literature (@smith1984threshold, @leadbetter1991basis, @davison1990models), a nice introduction can be found in @beirlantBook Ch.5.3, @embrechts2013modelling Ch.
-6.5.
-or @ColesBook Ch.4.
-Hence, we focus in this article mainly on the inter-exceedance times.
+As this approach is by now well-established in extreme value theory, we do not discuss it any further.
+Instead, this article focuses on our new contribution: the modelling of inter-exceedance times.
+For literature pointing to POT see e.g.
+@smith1984threshold; @leadbetter1991basis; @davison1990models; @beirlantBook Ch.5.3; @embrechts2013modelling Ch.
+6.5.; @ColesBook Ch.4.
+
 Due to the Theorem in the last Section we know that for high thresholds the times between exceedances are asymptotically Mittag-Leffler distributed in case of heavy-tailed waiting times between the observations.
-In this article we propose to proceed with inter-exceedance times in a similar fashion as with the magnitudes in the classical POT approach, more precisely to fit a Mittag-Leffler distribution via stability plots to the inter-exceedance times.
-Hence, before we talk about inference for the inter-exceedance times in the next section, we first discuss inference for Mittag-Leffler distributions.
+In this article we propose to model inter-exceedance times in a similar fashion as magnitudes in the classical POT approach, more precisely to fit a Mittag-Leffler distribution to the inter-exceedance times via stability plots.
+Hence, before we discuss inference for the inter-exceedance times in the next section, we first discuss inference for Mittag-Leffler distributions.
 
@@
 The Hill estimator only performs reliably well for distributions close to Pareto [see @Resnick97].
-It heavily depends on the choice of $r$ in \eqref{eq:Hill}, hence on the number of order statistics entering into \eqref{eq:Hill}.
-Figure \ref{fig:Hillplots} shows Hill plots for Mittag-Leffler simulated data, with varying sample sizes and tails.
+It heavily depends on the choice of $r$ in \eqref{eq:Hill}, and hence on the number of order statistics entering \eqref{eq:Hill}.
+Figure \ref{fig:Hillplots} shows Hill plots for simulated Mittag-Leffler data, with varying sample sizes and tails.
 To deduce the correct tail parameter estimates from these plots is virtually impossible.
@@
 @beirlantBook, Ch.4.4 and 4.7 and references in it].
-Also, there are lot of other tail-index estimators not taken under consideration in our article, since this would go beyond the scope of our article.
-However, we know from the Theorem in Section \ref{sec:scaling} that the inter-exceedance times are asymptotically Mittag-Leffler distributed.
-So all these general tail (and scale) estimation methods are statistically less efficient since they only use a portion of the information contained in the data, as mentioned by @kozubowski2001.
-Furthermore, the Hill estimator of course completely fails, if the inter-arrival times are exponentially distributed and not heavy-tailed.
-Hence, we propose to use the log-Moment estimator or the MLE for Mittag-Leffler distributions.
-
-```{r Hillplots, echo=FALSE,warning=FALSE, fig.align="center", fig.cap="\\label{fig:Hillplots} Hillplots for simulated Mittag-Leffler data with true tail 0.8 and sample size 200 (left) and 10000 (right), with number of upper order statics r on which the Hill estimator is based on the x-axis.
+Also, there are many other tail-index estimators not considered in this article, since this would go beyond the scope of our article.
+However, we know from the Theorem in Section \ref{sec:scaling} that the inter-exceedance times are asymptotically Mittag-Leffler distributed, and hence it is unsurprising that general tail (and scale) estimation methods that do not take into account this structure are statistically less efficient [@kozubowski2001].
+Finally, the Hill estimator completely fails in the important special case where the inter-arrival times are exponentially distributed and not heavy-tailed.
+For these reasons, we propose to use the log-Moment estimator or the MLE for Mittag-Leffler distributions.
+
+```{r Hillplots, echo=FALSE,warning=FALSE, fig.align="center", fig.cap="\\label{fig:Hillplots} Hillplots for simulated Mittag-Leffler data with true tail 0.8 and sample size 200 (left) and 10000 (right), with number of upper order statistics r on which the Hill estimator is based on the x-axis.
 ", out.width = '90%'}
@@
 Plot $k$ vs.\ $\hat \beta_k$.
-To the right, as $k \downarrow K_0$, the asymptotics are off and bias is high.
-To the left (high threshold), data are scarce and variance is high.
-Choose a region of *stability* in the middle for a parameter estimate $\hat \beta$.
-
-4. Plot $k$ vs.\ $k^{1/\hat \beta} \hat \sigma_k$. Again, choose a region of *stability* as $k$ gets smaller and define $\hat \sigma_0$.
+To the right ($k \uparrow K$, low threshold), the asymptotics are off and bias is high.
+To the left ($k \downarrow K_0$, high threshold), data is scarce and variance is high.
+In the middle, look for a region of *stability* for a parameter estimate $\hat \beta$.
+Choose as $\hat \beta$ a representative value from this region.
+
+4. Plot $k$ vs.\ $k^{1/\hat \beta} \hat \sigma_k$. Again, choose a region of *stability* and, and choose a representative $\hat \sigma_0$ from that region.
 
@@
 Both estimators show good performance, with a slight advantage for the Maximum-Likelihood estimator.
-This advantage is paid for by a higher computational cost.
-Moreover, the bottom row in Figure \ref{Fig:TailSimu} shows clearly that the log-Moment and Maximum-Likelihood estimators generalize to the exponential case ($\beta = 1$) whereas a general tail estimator like the Hill-estimator would not.
+This advantage is paid for with a higher computational cost.
+Moreover, the bottom row in Figure \ref{Fig:TailSimu} shows clearly that the log-Moment and Maximum-Likelihood estimators generalize to the exponential case ($\beta = 1$) whereas the Hill-estimator would not.
 
@@
 event magnitudes (subject to a mixing condition).
-The two approaches are fundamentally different: A clustering model assumes that each event belongs to one particular (latent) group of events.
+The two approaches are fundamentally different: Clustering assumes that each event belongs to one particular (latent) group of events.
 For bursts, however, the aim is to identify an underlying scale-free pattern in the event
 dynamics, which is often characteristic of complex systems.
-It is an interesting open problem to develop quality criteria, based e.g.
-on measures of surprise [@Lee15], which guide an applied statistician in the choice between a clustering and a CTRE approach for a particular problem.
-But the CTRE approach should not be seen as a substitute for the usual cluster approach.
-It was for example also observed in @towe2020modelling that clusters of extreme events still exist after declustering.
-We believe it is possible to unify the cluster approach with our CTRE approach by considering CTREs based on MRPs with a _stationary_, rather than i.i.d., sequence of magnitudes.
-Then the times between clusters are asymptotically Mittag-Leffler distributed.
-The identification of clusters in the context of heavy-tailed inter-arrival times is an open problem.
-But what one could do in case of observing dependencies between the exceedances: one could build natural clusters for example by considering daily maxima instead of hourly maxima.
-
-Finally, a purely scale-free pattern for event times may be too rigid as an 
+It is an interesting open problem to develop criteria, based e.g.
+on measures of surprise [@Lee15], that guide an applied statistician in the choice between a clustering and a CTRE approach for a particular problem.
+In sum, the CTRE approach should not be seen as a substitute for the usual cluster approach, but rather as a complementary approach.
+
+Moreover, it was observed in @towe2020modelling that clusters of extreme events still exist after declustering.
+We believe it is possible to marry the clustering approach with our CTRE approach by considering CTREs based on MRPs with a _stationary_, rather than i.i.d., sequence of magnitudes, so that the times between clusters are asymptotically Mittag-Leffler distributed.
+More broadly speaking, the identification of clusters in the context of heavy-tailed inter-arrival times is an open problem.
+
+Finally, a purely scale-free pattern for event times may be too rigid an 
 assumption for some bursty time series, because often the heavy-tailed character of the inter-arrival time
-distribution does not hold at all time scales; rather, it applies at short and intermediate time scales, and is truncated (or tempered, 
+distribution does not hold at all time scales. Rather, it applies at short and intermediate time scales, and is truncated (or tempered, 
 reverting to an exponential distribution) at very long time scales [see e.g.

### 2020-03-29 article_springer/changes.Rmd
Bügele das Englisch

@@
 To make this more clear for the reader, we added a comment at the beginning of Section 4.
-Additionally, inspirited by the POT method, as you said, we propose to fit the inter-exceedance times in a similar fashion: namely, by fitting a Mittag-Leffler distribution to the inter-exceedance times between the peaks over threshold via stability plots.
-It is true, that the underlying distribution of the magnitudes, in the way we defined the algorithm, gets nearly ignored.
-A probable extension of our algorithm could be to approximate the tail probability $p_{\ell}$ for very large thresholds by the GPD distribution, which was in a step before fitted to the magnitudes.
-We add a remark on this after the algorithm.
+Additionally, and indeed inspired by the POT method, we propose to fit the inter-exceedance times in a similar fashion: namely, by fitting a Mittag-Leffler distribution to the inter-exceedance times between the peaks over threshold via stability plots.
+It is true that we largely ignore the underlying distribution of the magnitudes in our algorithm.
+Our algorithm could potentially be improved by i) fitting a GPD distribution to the exceedances and thus ii) more accurately approximating the tail probability $p_{\ell}$.
+We mention this idea in a remark following the algorithm.
 
@@
 renewal processes (with power-law waiting times). Their relatively simple
-structure makes them amenable to theoretical analysis but for the same rea-
-son, I am not convinced that the CTRE model represents a really good
+structure makes them amenable to theoretical analysis but for the same reason, I am not convinced that the CTRE model represents a really good
 alternative to cluster models as a model for bursty data. The authors' claim
@@
 
-* The CTRE model is not intended as a substitute for the usual cluster models.
-It should be more seen as a complement.
+* The CTRE model is not intended as a substitute for the usual cluster models, but rather as a complement.
 If there are dependencies in the data, one should first decluster the data.
-If there are still clusters after (see for example p.3 in @towe2020modelling), the CTRE can maybe account for this behavior.
-We add a comment on this to the Discussion & Conclusion.
+If there are still clusters thereafter (see for example p.3 in @towe2020modelling), the CTRE can possible account for this behavior.
+We added a comment on this to the Discussion & Conclusion Section.
 
@@
 
-* That is of course true.
+* This is of course true.
 We calculated here the auto-correlations under the assumption that the underlying data is Mittag-Leffler distributed.
@@
 It is also true that the log-transformation can influence the appearance of the graph.
-ACFs can always just discover linear dependencies.
+ACFs only uncover linear dependencies reliably.
 However, this is just a diagnostic tool to indicate whether the independence assumption is justified.
-We added for this a comment in the manuscript as well in Section 7 after describing the diagnostic tools.
+We added a comment on this issue in Section 7 after describing the diagnostic tools.
 
@@
 
-* It's in interesting idea to use the proposed method for the estimation of the tail index for any power law with $\beta$ < 1.
+* It is an interesting idea to use the proposed method for the estimation of the tail index on *any* power law with $\beta$ < 1.
 However, this goes beyond the scope of our article.
-In our article we know from the theory that the inter-exceedance times which we want to model are approximately Mittag-Leffler distributed, hence its natural to use here specific Mittag-Leffler scale and tail estimators.
+In the setting of our article the inter-exceedance times we want to model are approximately Mittag-Leffler distributed, hence it is natural to use specific Mittag-Leffler scale and tail estimators here.
 
 "The manuscript seems nicely organized. However, writing is not always
-precise, the paper contains some typos and not entirely rigorous mathemati-
-cal arguments.""
+precise, the paper contains some typos and not entirely rigorous mathematical arguments.""
 
-* We revised the whole manuscript according typos, added the missing assumption for the magnitudes and replaced the proof of the theorem by a new, simplified version (EVTL NOCH ANPASSEN).
+* We revised the whole manuscript according typos, added the missing assumption for the magnitudes and replaced the proof of the theorem by a new, simplified version.
 
@@
 
-* You are completely right. This was a typo. We changed this accordingly.
+* We agree and corrected this typographic error.
 
@@
 
-* You are completely right again. This was also a typo. We fixed that.
+* This is correct, and we made the change.
 
@@
 
-* TO DO (evtl noch anpassen) We gave a completely new proof. Hence this point no longer applies.
+* We gave a completely new proof. Hence this point no longer applies.
 
@@
 
-* (EVTL noch anpassen) We added some more explanation to the last two lines.
+* We added some more explanation to the last two lines.
 
@@
 In the submitted version of the article the simulation study was based on one thousand simulation runs.
-This was maybe a little bit too small, hence I repeated the study with five thousand runs and now the MSE looks for very small indices more acceptable.
-I also changed to RMSE since it is easier to interpret.
+This was maybe a little bit too small, hence we repeated the study with five thousand runs and now the MSE looks for very small indices more acceptable.
+We also changed to RMSE since it is easier to interpret.
 
@@
 
-* You are right.
-We should better explain this.
+* We agree that this should be explained better.
 The plot stabilizes in a region in the middle.

### 2020-04-03 article_springer/article_springer.Rmd
New proof inserted and points of Peter (email 29/03/2020) adressed.

@@
 
-*Proof of Theorem:* We interpret the threshold crossing time $T(\ell)$ as the hitting time of the 
-underlying CTRM (Continuous Time Random Maxima) or "max-renewal process", 
-and then utilize a result by @MeerschaertStoev08. 
-The running maximum process is defined as 
-$$
-M(c) := J_1 \vee \ldots \vee J_{\lfloor c \rfloor},
-$$
-and since the $J_k$ lie in the domain of attraction of a max-stable distribution $F$ (see \eqref{assumptionJs}), there exist 
-norming functions $a(c)$ and $d(c)$ such that 
-$$
-\mathbf P\left[ \frac{M(c) - d(c)}{a(c)} \le \ell^* \right] 
-\longrightarrow F(\ell^*), \quad c \to \infty
-$$
-where $F$ is a generalized extreme value distribution, and $\ell^*$ is any 
-value from the support of $F$. 
-The CTRM process is then defined via 
-$$
-V(t) = M(N(t)), \quad t \ge 0
-$$
-where $N(t)$ is the renewal process associated with the waiting times 
-$W_k$: 
-$$
-N(t) = \max\{n: W_1 + \ldots + W_n \le t\}.
-$$
-Now a key observation is that
-$$
-T(\ell) = \inf\{t: V(t) > \ell\}, 
-$$
-and that
-
+*Proof of Theorem:* 	Due to assumption \eqref{assumptionJs}, it follows
+	\begin{align*}
+	P\left(\frac{M(c)-d(c)}{a(c)} \leq x\right) \rightarrow F(x) \text{ as } c \rightarrow \infty,
+	\end{align*}
+	where $x$ is any value from the support of $F$. Then it follows,
+	\begin{align*}
+	  F(xa(c)+d(c))^{\lfloor c \rfloor} &\rightarrow F(x) \text{ as } c \rightarrow \infty,\\
+      \Rightarrow  \lfloor c \rfloor \log F(\ell_c)  &\rightarrow \log F(x)\text{ as } c \rightarrow \infty,
+	\end{align*}
+	with $\ell_c:=xa(c)+d(c)$. Furthermore, since $\log(1-x) \sim -x$ for small $x$ it follows
     \begin{align}
-T(\ell) > t \quad \text{ if and only if } \quad V(t) \le \ell. \label{inverserelat}
+      c \cdot p(\ell_c) \rightarrow -\log F_A(x)  \text{ as } c \rightarrow \infty,\label{eq:lplconv}
     \end{align}
-
-By [Theorem 3.1, @MeerschaertStoev08], we have the stochastic process 
-convergence
-
+	 with $p(\ell_c):= \overline{F}(\ell_c)$. Since $\tau(\ell_c) \sim Geo(p(\ell_c))$ and \eqref{eq:lplconv}
+	it follows that $\tau(\ell_c)/c$ converges to an Exponential distributed random variable,
+	\begin{align*}
+	\frac{\tau(\ell_c)}{c} \Rightarrow E  \text{ as } c \rightarrow \infty
+	\end{align*}
+	 with parameter $\lambda:=-\log F_A(x)$. Due to
+	\begin{align*}
+	S(c):= \sum_{i=1}^{\lfloor c \rfloor} \frac{W_i}{b(c)} \Rightarrow D \ \text{ as } c \rightarrow \infty,
+	\end{align*}
+    it follows with Gnedenkos transfer theorem (see @gnedenko1983limit), that
 	\begin{align}
-\frac{V(ct) - d(\tilde b(c))}{a(\tilde b(c))} 
-\stackrel{d}{\longrightarrow} Y(t),  \quad c \to \infty, \label{TheoMS}
+	\sum_{i=1}^{ \tau(\ell_c)} \frac{W_i}{b(\ell_c)}  \Rightarrow Z\ \text{ as }  c \rightarrow \infty, \label{TheoGutArg}
 	\end{align}
-
-for $t > 0$, where $Y(t)$ is a time-changed ("subordinated") extremal process, and where 
-$\tilde b(c)$ is a regularly varying norming function which is
-_inverse_ to $b(c)$, in the sense that 
-$b(\tilde b(c)) \sim c \sim \tilde b(b(c))$ [@BinghamGoldieTeugels].
-
-Without loss of generality, we choose $\ell^*$ such that $F(\ell^*) = 1/e$, 
-and let $\ell = a(\tilde b(c)) \ell^* + d(\tilde b(c))$. 
-We may then calculate 
-$$
-\mathbf P\left[ \frac{T(\ell)}{b(1/p_{\ell})} > t \right]
-= \mathbf P[T(\ell) > b(1/p_{\ell}) t]
-= \mathbf P[V(ct) \le \ell]
-$$
-where we have substituted $c = b(1/p_{\ell})$ and used \eqref{inverserelat}. Moreover, we receive due to the convergence in \eqref{TheoMS}
-$$
-\mathbf P[V(ct) \le \ell]
-= \mathbf P\left[ \frac{V(ct) - d(\tilde b(c))}{a(\tilde b(c))} 
-\le \frac{\ell - d(\tilde b(c))}{a(\tilde b(c))} \right]
-\longrightarrow \mathbf P\left[ Y(t) \le \ell^* \right] ,  \quad c \to \infty,
-$$
-for $t>0$. Defining the hitting time of level $\ell^*$ by $Y(t)$ as 
-$\xi_{\ell^*} := \inf\{t: Y(t) > \ell^*\}$,
-we then have 
-$$
-P\left[ Y(t) \le \ell^* \right] = \mathbf P[\xi_{\ell^*} > t] 
-= \mathbf P[(-\log F(\ell^*))^{-1/\beta} X^{1/\beta} D > t]
-$$
-by [Proposition 4.2, @MeerschaertStoev08], where $X$ is an exponential 
-random variable with mean $1$. 
-Using [Theorem 19.1, @Haubold11], we see that 
-$X^{1/\beta} D \sim {\rm ML}(\beta, 1)$, concluding the proof. 
+	where the distribution of $Z$ has the characteristic function
+	\begin{align}
+    \Psi(t) &= \int_0^{\infty} (\Phi_D(t))^{y} F_E(dy) \nonumber\\
+    &= \int_0^{\infty} \frac{1}{1-\log(\Phi_D(t))/\lambda} \nonumber\\
+    &= \frac{1}{1+s^{\beta}\lambda^{-1}}
+	\end{align}
+    where $\Phi_D$ resp. $F_E$ denotes Laplace transform of $D$ resp. the distribution function of $E$. Hence, $Z$ is Mittag-Leffler distributed with parameter $\lambda^{-1/\beta}$. Since
+	\begin{align*}
+    \sum_{i=1}^{ \tau(\ell_c)} \frac{W_i}{b(1/p(\ell_c))} = \left(\sum_{i=1}^{ \tau(\ell_c)} \frac{W_i}{b(c) }\right) \frac{b(c)}{b(1/p(\ell_c))}  
+	\end{align*}
+	and due to
+	\begin{align*}
+	\frac{b(c)}{b(1/p(\ell_c))} = \frac{b(c)}{b(c/(p(\ell_c)c))} \sim (p(\ell_c) \cdot c)^{1/\beta} \rightarrow \lambda^{1/\beta} \text{ as } c \rightarrow \infty.
+	\end{align*}
+	the second factor converges to $\lambda^{1/\beta}$, it follows that
+	 $Z \sim ML(\beta,1)$. Since $c \rightarrow \infty$ is equivalent to $\ell \uparrow x_R$ the assertion follows with $\ell:=\ell_c$ and $p_\ell:=p(\ell_c)$.
 \qed
@@
 load(here::here("article_springer", "article_springer_files", "ML_estim_simu","tbl_ML_estim.RData"))
+  n.labs <-c("n=25", "n=100", "n=200")
+  names( n.labs ) <-  c("25", "100", "200")
 tbl_ML_estim %>% filter(method=="logMom" | method=="ML")%>%
@@
   geom_line() + geom_point() + 
-  facet_wrap(c("n","param"), scales = "free", ncol = 2) + 
-  scale_color_manual(values=c("red", "blue"))
+  facet_wrap(c("n","param"), scales = "free", ncol = 2, labeller = labeller(n = n.labs)) + 
+  scale_color_manual(values=c("red", "blue"),name = "Method", labels = c("log-Moment", "MLE"))
+
 ```
@@
 Figure \ref{fig:Hillplots} shows Hill plots for simulated Mittag-Leffler data, with varying sample sizes and tails.
-To deduce the correct tail parameter estimates from these plots is virtually impossible.
-To estimate the tail parameter of a Mittag-Leffler distribution with the Hill estimator, the sample size has to be much larger and one has to choose a large tuning parameter $r$.
-In case that only events above a high threshold are recorded, $n=10000$ events are unrealistic.
+To deduce the correct tail parameter estimates from one of those Hillplots is virtually impossible.
+To estimate the tail parameter of a Mittag-Leffler distribution with the Hill estimator, the sample size has to be much larger and one has to choose a small tuning parameter $r$.
+In case that only events above a high threshold are recorded, $n=10000$ events are extremely unrealistic.
 There is a vast literature on bias-reduced versions of the Hill estimator and on the optimal choice of $r$, mainly based on imposed second-order regular variation conditions [see e.g.
 @beirlantBook, Ch.4.4 and 4.7 and references in it].
-Also, there are many other tail-index estimators not considered in this article, since this would go beyond the scope of our article.
+Also, there are hundreds other tail-index estimators not considered in this article, since this would go beyond the scope of our article.
+For example the moment estimator [@dekkers1989moment], the Pickands estimator [@pickands1975statistical], the QQ-estimator [@Kratz96], to name a few.
+A nice overview can be found in [@fedotenkov2018review].
 However, we know from the Theorem in Section \ref{sec:scaling} that the inter-exceedance times are asymptotically Mittag-Leffler distributed, and hence it is unsurprising that general tail (and scale) estimation methods that do not take into account this structure are statistically less efficient [@kozubowski2001].
@@
 
-```{r Hillplots, echo=FALSE,warning=FALSE, fig.align="center", fig.cap="\\label{fig:Hillplots} Hillplots for simulated Mittag-Leffler data with true tail 0.8 and sample size 200 (left) and 10000 (right), with number of upper order statistics r on which the Hill estimator is based on the x-axis.
-", out.width = '90%'}
+```{r Hillplots,  fig.height=5, fig.width=4, echo=FALSE,warning=FALSE, fig.align="center", fig.cap="\\label{fig:Hillplots} Hillplots for m=100 simulated Mittag-Leffler datasets with true tail 0.8 and sample size 200 (left) and 10000 (right), with number of upper order statistics r on which the Hill estimator is based on the x-axis.
+The grey thin lines are the Hill plots for the different simulation runs and the dark lines are their means.
+The red dotted line shows the true tail parameter.
+", out.width = '50%'}
+
 hill_estim<-function(k,data){
@@
 
-set.seed(1234)
-hill_estim_plot<-function(k_min,data,k_max=n,true_tail){
+hill_estim_range<-function(k_min,data,k_max=n,true_tail){
   n<-length(data)
@@
   df<-data.frame(x=x_values,y=y_values)
-  ggplot2::ggplot(data=df,aes(x_values,y_values))+ geom_line(color="blue")+xlab("Order Statistics") + ylab("Hill-Estimator of Tail Index") +
-  coord_cartesian(ylim=c(0,1.5)) + geom_hline(yintercept=true_tail, linetype="dashed", color = "red", size=0.5)
+  return(df)
 }
+
+hill_plot_values<-data.frame(x=numeric(),y=numeric(),rep=numeric())
+for  (m in 1:100){
 data_ml_1<-rml(n=200,tail=0.8,scale=1)
-p1<-hill_estim_plot(k_min=30,data=data_ml_1,true_tail=0.8) +
-  ggtitle("Hill plot, ML-data, n=200")
-
+df<-hill_estim_range(k_min=30,data=data_ml_1,true_tail=0.8)
+df<-df %>% mutate(rep=m)
+hill_plot_values<-bind_rows(df,hill_plot_values)
+}
+
+mean_n200<-hill_plot_values %>% group_by(x) %>% summarize(mean=mean(y))
+p1<-hill_plot_values %>% ggplot() + geom_line(aes(x=x,y=y,group=rep),colour="lightgrey") +
+  coord_cartesian(ylim = c(0.5, 1.5)) +
+  geom_line(aes(x=x, y=mean),colour="black",data=mean_n200) + 
+  ylab("Estimated tail") +
+  geom_hline(yintercept=0.8, linetype="dashed", color = "red")+
+  xlab("Order Statistics")+
+  ylab("Hill-Estimator of Tail Index")
+
+hill_plot_values<-data.frame(x=numeric(),y=numeric(),rep=numeric())
+for  (m in 1:100){
   data_ml_2<-rml(n=10000,tail=0.8,scale=1)
-p2<-hill_estim_plot(k_min=30,k_max=200,data=data_ml_2,true_tail=0.8) +
-  ggtitle("Hill plot, ML-data, n=10000")
-
-grid.arrange(p1,p2,ncol=2)
+  df<-hill_estim_range(k_min=30,k_max=200,data=data_ml_2,true_tail=0.8)
+  df<-df %>% mutate(rep=m)
+  hill_plot_values<-bind_rows(df,hill_plot_values)
+}
+mean_n1000<-hill_plot_values %>% group_by(x) %>% summarize(mean=mean(y))
+
+p2<-hill_plot_values %>% ggplot() + geom_line(aes(x=x,y=y,group=rep),colour="lightgrey") +
+  coord_cartesian(ylim = c(0.5, 1.5)) +
+  geom_line(aes(x=x, y=mean),colour="black",data=mean_n1000) + 
+  ylab("Estimated tail") +
+  geom_hline(yintercept=0.8, linetype="dashed", color = "red")+
+  xlab("Order Statistics")+
+  ylab("Hill-Estimator of Tail Index")
+
+grid.arrange(p1,p2,nrow=2)
 ```

### 2020-04-03 article_springer/article_springer.tex
New proof inserted and points of Peter (email 29/03/2020) adressed.

@@
 
-\emph{Proof of Theorem:} We interpret the threshold crossing time
-\(T(\ell)\) as the hitting time of the underlying CTRM (Continuous Time
-Random Maxima) or ``max-renewal process'', and then utilize a result by
-Meerschaert and Stoev (2008). The running maximum process is defined as
-\[
-M(c) := J_1 \vee \ldots \vee J_{\lfloor c \rfloor},
-\] and since we assumed that the \(J_k\) our out of the domain of
-attraction of a max-stable distribution \(F\) (see
-\eqref{assumptionJs}), there exist norming functions \(a(c)\) and
-\(d(c)\) such that \[
-\mathbf P\left[ \frac{M(c) - d(c)}{a(c)} \le \ell^* \right] 
-\longrightarrow F(\ell^*), \quad c \to \infty
-\] where \(F\) is a generalized extreme value distribution, and
-\(\ell^*\) is any value from the support of \(F\). The CTRM process is
-then defined via \[
-V(t) = M(N(t)), \quad t \ge 0
-\] where \(N(t)\) is the renewal process associated with the waiting
-times \(W_k\): \[
-N(t) = \max\{n: W_1 + \ldots + W_n \le t\}.
-\] Now a key observation is that \[
-T(\ell) = \inf\{t: V(t) > \ell\}, 
-\] and that
-
-\begin{align}
-T(\ell) > t \quad \text{ if and only if } \quad V(t) \le \ell. \label{inverserelat}
-\end{align}
-
-By (Theorem 3.1, Meerschaert and Stoev, 2008), we have the stochastic
-process convergence
-
-\begin{align}
-\frac{V(ct) - d(\tilde b(c))}{a(\tilde b(c))} 
-\stackrel{d}{\longrightarrow} Y(t),  \quad c \to \infty, \label{TheoMS}
-\end{align}
-
-for \(t > 0\), where \(Y(t)\) is a time-changed (``subordinated'')
-extremal process, and where \(\tilde b(c)\) is a regularly varying
-norming function which is \emph{inverse} to \(b(c)\), in the sense that
-\(b(\tilde b(c)) \sim c \sim \tilde b(b(c))\) (Bingham et al., 1989).
-
-Without loss of generality, we choose \(\ell^*\) such that
-\(F(\ell^*) = 1/e\), and let
-\(\ell = a(\tilde b(c)) \ell^* + d(\tilde b(c))\). We may then calculate
-\[
-\mathbf P\left[ \frac{T(\ell)}{b(1/p_{\ell})} > t \right]
-= \mathbf P[T(\ell) > b(1/p_{\ell}) t]
-= \mathbf P[V(ct) \le \ell]
-\] where we have substituted \(c = b(1/p_{\ell})\) and used
-\eqref{inverserelat}. Moreover, we receive due to the convergence in
-\eqref{TheoMS} \[
-\mathbf P[V(ct) \le \ell]
-= \mathbf P\left[ \frac{V(ct) - d(\tilde b(c))}{a(\tilde b(c))} 
-\le \frac{\ell - d(\tilde b(c))}{a(\tilde b(c))} \right]
-\longrightarrow \mathbf P\left[ Y(t) \le \ell^* \right] ,  \quad c \to \infty,
-\] for \(t>0\). Defining the hitting time of level \(\ell^*\) by
-\(Y(t)\) as \(\xi_{\ell^*} := \inf\{t: Y(t) > \ell^*\}\), we then have
-\[
-P\left[ Y(t) \le \ell^* \right] = \mathbf P[\xi_{\ell^*} > t] 
-= \mathbf P[(-\log F(\ell^*))^{-1/\beta} X^{1/\beta} D > t]
-\] by (Proposition 4.2, Meerschaert and Stoev, 2008), where \(X\) is an
-exponential random variable with mean \(1\). Using (Theorem 19.1,
-Haubold et al., 2011), we see that
-\(X^{1/\beta} D \sim {\rm ML}(\beta, 1)\), concluding the proof. \qed
+\emph{Proof of Theorem:} Due to assumption \eqref{assumptionJs}, it
+follows \begin{align*}
+    P\left(\frac{M(c)-d(c)}{a(c)} \leq x\right) \rightarrow F(x) \text{ as } c \rightarrow \infty,
+    \end{align*} where \(x\) is any value from the support of \(F\).
+Then it follows, \begin{align*}
+      F(xa(c)+d(c))^{\lfloor c \rfloor} &\rightarrow F(x) \text{ as } c \rightarrow \infty,\\
+      \Rightarrow  \lfloor c \rfloor \log F(\ell_c)  &\rightarrow \log F(x)\text{ as } c \rightarrow \infty,
+    \end{align*} with \(\ell_c:=xa(c)+d(c)\). Furthermore, since
+\(\log(1-x) \sim -x\) for small \(x\) it follows \begin{align}
+      c \cdot p(\ell_c) \rightarrow -\log F_A(x)  \text{ as } c \rightarrow \infty,\label{eq:lplconv}
+    \end{align} with \(p(\ell_c):= \overline{F}(\ell_c)\). Since
+\(\tau(\ell_c) \sim Geo(p(\ell_c))\) and \eqref{eq:lplconv} it follows
+that \(\tau(\ell_c)/c\) converges to an Exponential distributed random
+variable, \begin{align*}
+    \frac{\tau(\ell_c)}{c} \Rightarrow E  \text{ as } c \rightarrow \infty
+    \end{align*} with parameter \(\lambda:=-\log F_A(x)\). Due to
+\begin{align*}
+    S(c):= \sum_{i=1}^{\lfloor c \rfloor} \frac{W_i}{b(c)} \Rightarrow D \ \text{ as } c \rightarrow \infty,
+    \end{align*} it follows with Gnedenkos transfer theorem (see
+Gnedenko (1983)), that \begin{align}
+    \sum_{i=1}^{ \tau(\ell_c)} \frac{W_i}{b(\ell_c)}  \Rightarrow Z\ \text{ as }  c \rightarrow \infty, \label{TheoGutArg}
+    \end{align} where the distribution of \(Z\) has the characteristic
+function \begin{align}
+    \Psi(t) &= \int_0^{\infty} (\Phi_D(t))^{y} F_E(dy) \nonumber\\
+    &= \int_0^{\infty} \frac{1}{1-\log(\Phi_D(t))/\lambda} \nonumber\\
+    &= \frac{1}{1+s^{\beta}\lambda^{-1}}
+    \end{align} where \(\Phi_D\) resp. \(F_E\) denotes Laplace transform
+of \(D\) resp. the distribution function of \(E\). Hence, \(Z\) is
+Mittag-Leffler distributed with parameter \(\lambda^{-1/\beta}\). Since
+\begin{align*}
+    \sum_{i=1}^{ \tau(\ell_c)} \frac{W_i}{b(1/p(\ell_c))} = \left(\sum_{i=1}^{ \tau(\ell_c)} \frac{W_i}{b(c) }\right) \frac{b(c)}{b(1/p(\ell_c))}  
+    \end{align*} and due to \begin{align*}
+    \frac{b(c)}{b(1/p(\ell_c))} = \frac{b(c)}{b(c/(p(\ell_c)c))} \sim (p(\ell_c) \cdot c)^{1/\beta} \rightarrow \lambda^{1/\beta} \text{ as } c \rightarrow \infty.
+    \end{align*} the second factor converges to \(\lambda^{1/\beta}\),
+it follows that \(Z \sim ML(\beta,1)\). Since \(c \rightarrow \infty\)
+is equivalent to \(\ell \uparrow x_R\) the assertion follows with
+\(\ell:=\ell_c\) and \(p_\ell:=p(\ell_c)\). \qed
 
@@
 distribution is fitted to the exceedances above a high enough threshold.
-This approach was well-established a long time ago and is standard in
-extreme value theory nowadays. Hence we just refer here to the according
-literature (Smith (1984), Leadbetter (1991), Davison and Smith (1990)),
-a nice introduction can be found in Beirlant et al. (2006) Ch.5.3,
-Embrechts et al. (2013) Ch. 6.5. or Coles (2001) Ch.4. Hence, we focus
-in this article mainly on the inter-exceedance times. Due to the Theorem
-in the last Section we know that for high thresholds the times between
-exceedances are asymptotically Mittag-Leffler distributed in case of
-heavy-tailed waiting times between the observations. In this article we
-propose to proceed with inter-exceedance times in a similar fashion as
-with the magnitudes in the classical POT approach, more precisely to fit
-a Mittag-Leffler distribution via stability plots to the
-inter-exceedance times. Hence, before we talk about inference for the
+As this approach is by now well-established in extreme value theory, we
+do not discuss it any further. Instead, this article focuses on our new
+contribution: the modelling of inter-exceedance times. For literature
+pointing to POT see e.g.~Smith (1984); Leadbetter (1991); Davison and
+Smith (1990); Beirlant et al. (2006) Ch.5.3; Embrechts et al. (2013) Ch.
+6.5.; Coles (2001) Ch.4.
+
+Due to the Theorem in the last Section we know that for high thresholds
+the times between exceedances are asymptotically Mittag-Leffler
+distributed in case of heavy-tailed waiting times between the
+observations. In this article we propose to model inter-exceedance times
+in a similar fashion as magnitudes in the classical POT approach, more
+precisely to fit a Mittag-Leffler distribution to the inter-exceedance
+times via stability plots. Hence, before we discuss inference for the
 inter-exceedance times in the next section, we first discuss inference
@@
 distributions close to Pareto (see Resnick, 1997). It heavily depends on
-the choice of \(r\) in \eqref{eq:Hill}, hence on the number of order
-statistics entering into \eqref{eq:Hill}. Figure \ref{fig:Hillplots}
-shows Hill plots for Mittag-Leffler simulated data, with varying sample
-sizes and tails. To deduce the correct tail parameter estimates from
-these plots is virtually impossible. To estimate the tail parameter of a
-Mittag-Leffler distribution with the Hill estimator, the sample size has
-to be much larger and one has to choose a large tuning parameter \(r\).
-In case that only events above a high threshold are recorded,
-\(n=10000\) events are unrealistic. There is a vast literature on
-bias-reduced versions of the Hill estimator and on the optimal choice of
-\(r\), mainly based on imposed second-order regular variation conditions
-(see e.g.~Beirlant et al., 2006, p. Ch.4.4 and 4.7 and references in
-it). Also, there are lot of other tail-index estimators not taken under
-consideration in our article, since this would go beyond the scope of
-our article. However, we know from the Theorem in Section
-\ref{sec:scaling} that the inter-exceedance times are asymptotically
-Mittag-Leffler distributed. So all these general tail (and scale)
-estimation methods are statistically less efficient since they only use
-a portion of the information contained in the data, as mentioned by
-Kozubowski (2001). Furthermore, the Hill estimator of course completely
-fails, if the inter-arrival times are exponentially distributed and not
-heavy-tailed. Hence, we propose to use the log-Moment estimator or the
-MLE for Mittag-Leffler distributions.
+the choice of \(r\) in \eqref{eq:Hill}, and hence on the number of order
+statistics entering \eqref{eq:Hill}. Figure \ref{fig:Hillplots} shows
+Hill plots for simulated Mittag-Leffler data, with varying sample sizes
+and tails. To deduce the correct tail parameter estimates from one of
+those Hillplots is virtually impossible. To estimate the tail parameter
+of a Mittag-Leffler distribution with the Hill estimator, the sample
+size has to be much larger and one has to choose a small tuning
+parameter \(r\). In case that only events above a high threshold are
+recorded, \(n=10000\) events are extremely unrealistic. There is a vast
+literature on bias-reduced versions of the Hill estimator and on the
+optimal choice of \(r\), mainly based on imposed second-order regular
+variation conditions (see e.g.~Beirlant et al., 2006, p. Ch.4.4 and 4.7
+and references in it). Also, there are hundreds other tail-index
+estimators not considered in this article, since this would go beyond
+the scope of our article. For example the moment estimator (Dekkers et
+al., 1989), the Pickands estimator (Pickands III and others, 1975), the
+QQ-estimator (Kratz and Resnick, 1996), to name a few. A nice overview
+can be found in (Fedotenkov, 2018). However, we know from the Theorem in
+Section \ref{sec:scaling} that the inter-exceedance times are
+asymptotically Mittag-Leffler distributed, and hence it is unsurprising
+that general tail (and scale) estimation methods that do not take into
+account this structure are statistically less efficient (Kozubowski,
+2001). Finally, the Hill estimator completely fails in the important
+special case where the inter-arrival times are exponentially distributed
+and not heavy-tailed. For these reasons, we propose to use the
+log-Moment estimator or the MLE for Mittag-Leffler distributions.
 
@@
 
-{\centering \includegraphics[width=0.9\linewidth]{article_springer_files/figure-latex/Hillplots-1}
+{\centering \includegraphics[width=0.5\linewidth]{article_springer_files/figure-latex/Hillplots-1}
 
@@
 
-\caption{\label{fig:Hillplots} Hillplots for simulated Mittag-Leffler data with true tail 0.8 and sample size 200 (left) and 10000 (right), with number of upper order statics r on which the Hill estimator is based on the x-axis.
+\caption{\label{fig:Hillplots} Hillplots for m=100 simulated Mittag-Leffler datasets with true tail 0.8 and sample size 200 (left) and 10000 (right), with number of upper order statistics r on which the Hill estimator is based on the x-axis.
+The grey thin lines are the Hill plots for the different simulation runs and the dark lines are their means.
+The red dotted line shows the true tail parameter.
 }\label{fig:Hillplots}
@@
 \item
-  Plot \(k\) vs.~\(\hat \beta_k\). To the right, as
-  \(k \downarrow K_0\), the asymptotics are off and bias is high. To the
-  left (high threshold), data are scarce and variance is high. Choose a
-  region of \emph{stability} in the middle for a parameter estimate
-  \(\hat \beta\).
+  Plot \(k\) vs.~\(\hat \beta_k\). To the right (\(k \uparrow K\), low
+  threshold), the asymptotics are off and bias is high. To the left
+  (\(k \downarrow K_0\), high threshold), data is scarce and variance is
+  high. In the middle, look for a region of \emph{stability} for a
+  parameter estimate \(\hat \beta\). Choose as \(\hat \beta\) a
+  representative value from this region.
 \item
   Plot \(k\) vs.~\(k^{1/\hat \beta} \hat \sigma_k\). Again, choose a
-  region of \emph{stability} as \(k\) gets smaller and define
-  \(\hat \sigma_0\).
+  region of \emph{stability} and, and choose a representative
+  \(\hat \sigma_0\) from that region.
 \end{enumerate}
@@
 slight advantage for the Maximum-Likelihood estimator. This advantage is
-paid for by a higher computational cost. Moreover, the bottom row in
+paid for with a higher computational cost. Moreover, the bottom row in
 Figure \ref{Fig:TailSimu} shows clearly that the log-Moment and
 Maximum-Likelihood estimators generalize to the exponential case
-(\(\beta = 1\)) whereas a general tail estimator like the Hill-estimator
-would not.
+(\(\beta = 1\)) whereas the Hill-estimator would not.
 
@@
 event magnitudes (subject to a mixing condition). The two approaches are
-fundamentally different: A clustering model assumes that each event
-belongs to one particular (latent) group of events. For bursts, however,
-the aim is to identify an underlying scale-free pattern in the event
-dynamics, which is often characteristic of complex systems. It is an
-interesting open problem to develop quality criteria, based e.g.~on
-measures of surprise (Lee et al., 2015), which guide an applied
-statistician in the choice between a clustering and a CTRE approach for
-a particular problem. But the CTRE approach should not be seen as a
-substitute for the usual cluster approach. It was for example also
-observed in Towe et al. (2020) that clusters of extreme events still
-exist after declustering. We believe it is possible to unify the cluster
-approach with our CTRE approach by considering CTREs based on MRPs with
-a \emph{stationary}, rather than i.i.d., sequence of magnitudes. Then
-the times between clusters are asymptotically Mittag-Leffler
-distributed. The identification of clusters in the context of
-heavy-tailed inter-arrival times is an open problem. But what one could
-do in case of observing dependencies between the exceedances: one could
-build natural clusters for example by considering daily maxima instead
-of hourly maxima.
-
-Finally, a purely scale-free pattern for event times may be too rigid as
-an assumption for some bursty time series, because often the
-heavy-tailed character of the inter-arrival time distribution does not
-hold at all time scales; rather, it applies at short and intermediate
-time scales, and is truncated (or tempered, reverting to an exponential
-distribution) at very long time scales (see e.g.~Meerschaert et al.,
-2012; and Aban et al., 2006). In such situations, a ``tempered''
-Mittag-Leffler distribution may provide a more realistic fit, which we
-aim to introduce in follow-up work.
+fundamentally different: Clustering assumes that each event belongs to
+one particular (latent) group of events. For bursts, however, the aim is
+to identify an underlying scale-free pattern in the event dynamics,
+which is often characteristic of complex systems. It is an interesting
+open problem to develop criteria, based e.g.~on measures of surprise
+(Lee et al., 2015), that guide an applied statistician in the choice
+between a clustering and a CTRE approach for a particular problem. In
+sum, the CTRE approach should not be seen as a substitute for the usual
+cluster approach, but rather as a complementary approach.
+
+Moreover, it was observed in Towe et al. (2020) that clusters of extreme
+events still exist after declustering. We believe it is possible to
+marry the clustering approach with our CTRE approach by considering
+CTREs based on MRPs with a \emph{stationary}, rather than i.i.d.,
+sequence of magnitudes, so that the times between clusters are
+asymptotically Mittag-Leffler distributed. More broadly speaking, the
+identification of clusters in the context of heavy-tailed inter-arrival
+times is an open problem.
+
+Finally, a purely scale-free pattern for event times may be too rigid an
+assumption for some bursty time series, because often the heavy-tailed
+character of the inter-arrival time distribution does not hold at all
+time scales. Rather, it applies at short and intermediate time scales,
+and is truncated (or tempered, reverting to an exponential distribution)
+at very long time scales (see e.g.~Meerschaert et al., 2012; and Aban et
+al., 2006). In such situations, a ``tempered'' Mittag-Leffler
+distribution may provide a more realistic fit, which we aim to introduce
+in follow-up work.
 
@@
 
-\leavevmode\hypertarget{ref-BinghamGoldieTeugels}{}%
-Bingham, N.H., Goldie, C.M., Teugels, J.L., 1989. Regular variation.
-Cambridge university press.
-
 \leavevmode\hypertarget{ref-Cahoy2013}{}%
@@
 
+\leavevmode\hypertarget{ref-dekkers1989moment}{}%
+Dekkers, A.L., Einmahl, J.H., De Haan, L., 1989. A moment estimator for
+the index of an extreme-value distribution. The Annals of Statistics
+1833--1855.
+
 \leavevmode\hypertarget{ref-HXRBS}{}%
@@
 
+\leavevmode\hypertarget{ref-fedotenkov2018review}{}%
+Fedotenkov, I., 2018. A review of more than one hundred pareto-tail
+index estimators.
+
 \leavevmode\hypertarget{ref-ferro2003inference}{}%
@@
 distributions in r.
+
+\leavevmode\hypertarget{ref-gnedenko1983limit}{}%
+Gnedenko, B., 1983. On limit theorems for a random number of random
+variables, in: Probability Theory and Mathematical Statistics. Springer,
+pp. 167--176.
 
@@
 
+\leavevmode\hypertarget{ref-Kratz96}{}%
+Kratz, M., Resnick, S.I., 1996. The qq-estimator and heavy tails.
+Commun. Stat. Part C Stoch. Model. 12, 699--724.
+doi:\href{https://doi.org/10.1080/15326349608807407}{10.1080/15326349608807407}
+
 \leavevmode\hypertarget{ref-Laskin2003}{}%
@@
 
+\leavevmode\hypertarget{ref-pickands1975statistical}{}%
+Pickands III, J., others, 1975. Statistical inference using extreme
+order statistics. the Annals of Statistics 3, 119--131.
+
 \leavevmode\hypertarget{ref-R}{}%

### 2020-04-03 article_springer/changes.Rmd
New proof inserted and points of Peter (email 29/03/2020) adressed.

@@
 
-* Thank you. We added an assumption accordingly.
+* Thank you. We replaced the proof by a new one as already mentioned above. Additionaly, we added the assumption that the $J_k$ belong to some max domain of attraction at the end of Section 2.
 
@@
 
-* We added some more explanation to the last two lines.
+* Again this point no longer applies since we gave a completely new proof.
 

### 2020-04-04 article_springer/article_springer.Rmd
kleine Änderungen am Beweis

@@
     \end{align}
-	 with $p(\ell_c):= \overline{F}(\ell_c)$. Since $\tau(\ell_c) \sim Geo(p(\ell_c))$ and \eqref{eq:lplconv}
+	 with $p(\ell_c):= 1-F(\ell_c)$. Since $\tau(\ell_c) \sim Geo(p(\ell_c))$ and \eqref{eq:lplconv}
 	it follows that $\tau(\ell_c)/c$ converges to an Exponential distributed random variable,
@@
 	\end{align*}
-	 with parameter $\lambda:=-\log F_A(x)$. Due to
+	 with inverse mean $\lambda:=-\log F_A(x)$. Due to
 	\begin{align*}
@@
 	\begin{align}
-    \Psi(t) &= \int_0^{\infty} (\Phi_D(t))^{y} F_E(dy) \nonumber\\
-    &= \int_0^{\infty} \frac{1}{1-\log(\Phi_D(t))/\lambda} \nonumber\\
+    \Psi(s) &= \int_0^{\infty} (\Phi_D(s))^{y} F_E(dy) \nonumber\\
+    &= \int_0^{\infty} \frac{1}{1-\log(\Phi_D(s))/\lambda} \nonumber\\
     &= \frac{1}{1+s^{\beta}\lambda^{-1}}
 	\end{align}
-    where $\Phi_D$ resp. $F_E$ denotes Laplace transform of $D$ resp. the distribution function of $E$. Hence, $Z$ is Mittag-Leffler distributed with parameter $\lambda^{-1/\beta}$. Since
+    where $\Phi_D(s) = \exp(-s^\beta)$ is the Laplace transform of $D$ 
+    and  $F_E(dy)$ is the distribution function of $E$. Hence, $Z$ is Mittag-Leffler distributed with parameter $\lambda^{-1/\beta}$. Rewriting
 	\begin{align*}
@@
 	\end{align*}
-	and due to
+	and
 	\begin{align*}
-	\frac{b(c)}{b(1/p(\ell_c))} = \frac{b(c)}{b(c/(p(\ell_c)c))} \sim (p(\ell_c) \cdot c)^{1/\beta} \rightarrow \lambda^{1/\beta} \text{ as } c \rightarrow \infty.
+	\frac{b(c)}{b(1/p(\ell_c))} = \frac{b(c)}{b(c/(p(\ell_c)c))} \sim (p(\ell_c) \cdot c)^{1/\beta} \rightarrow \lambda^{1/\beta} \text{ as } c \rightarrow \infty,
 	\end{align*}
-	the second factor converges to $\lambda^{1/\beta}$, it follows that
-	 $Z \sim ML(\beta,1)$. Since $c \rightarrow \infty$ is equivalent to $\ell \uparrow x_R$ the assertion follows with $\ell:=\ell_c$ and $p_\ell:=p(\ell_c)$.
+	the second factor converges to $\lambda^{1/\beta}$, and it follows that
+	 $Z \sim ML(\beta,1)$. Since $c \rightarrow \infty$ is equivalent to $\ell \uparrow x_R$, the assertion follows with $\ell:=\ell_c$ and $p_\ell:=p(\ell_c)$.
 \qed
@@
 
-```{r Hillplots,  fig.height=5, fig.width=4, echo=FALSE,warning=FALSE, fig.align="center", fig.cap="\\label{fig:Hillplots} Hillplots for m=100 simulated Mittag-Leffler datasets with true tail 0.8 and sample size 200 (left) and 10000 (right), with number of upper order statistics r on which the Hill estimator is based on the x-axis.
+```{r Hillplots,  fig.height=5, fig.width=4, echo=FALSE,warning=FALSE, fig.align="center", fig.cap="\\label{fig:Hillplots} Hillplots for m=100 simulated Mittag-Leffler datasets with true tail 0.8 and sample size 200 (first panel) and 10000 (second panel), with number of upper order statistics r on which the Hill estimator is based on the x-axis.
 The grey thin lines are the Hill plots for the different simulation runs and the dark lines are their means.

### 2020-04-14 article_springer/article_springer.Rmd
Last small changes

@@
 threshold crossing times form a Poisson process [@Hsing88]. 
-Then as one increases the threshold and thus decreases the threshold 
+Then as one increases the threshold $\ell$ and thus decreases the threshold 
 crossing probability $p_{\ell}$, the Poisson process is rarefied, i.e. its 
@@
 generalizes the standard Poisson process. 
-Again as the threshold size increases and the threshold crossing
+Again as the threshold size $\ell$ increases and the threshold crossing
 probability $p_{\ell}$ decreases, the fractional Poisson process is rarefied: 
@@
 $T_k = W_1 + \ldots + W_k$. 
-Based on an MRP, we define the Continuous Time Random Exceedance model
+Based on a MRP, we define the Continuous Time Random Exceedance model
 (CTRE) as follows:
@@
 p1<-plot(sim_ctre, p = 0.01, main = "Simulated MRP") + 
-  ggtitle("Simulated MRP")
+  ggtitle("Simulated MRP") +
+   theme(plot.title = element_text(hjust = 0.5))
 p2<-flares %>% ctre() %>% plot(p = 0.02, log = 'y', main = "HXRBS data") +
-  ggtitle("HXRBS data")
+  ggtitle("HXRBS data")+
+   theme(plot.title = element_text(hjust = 0.5))
 grid.arrange(p1,p2)
@@
 
-: Let the waiting times $W_k$ be in the domain of attraction of a positively skewed sum-stable law with stability parameter $0 < \beta < 1$; more precisely,
+: For the magnitudes $J_k$ assumption \eqref{assumptionJs} holds.
+Furthermore, let the waiting times $W_k$ be in the domain of attraction of a positively skewed sum-stable law with stability parameter $0 < \beta < 1$; more precisely,
 \begin{align} \label{eq:stability}
@@
 Figure \ref{fig:MSE} shows that both estimators perform well, even for small sample sizes.
-
-```{r MSE, echo=FALSE,warning=FALSE, fig.height=7,fig.width=8,fig.align="center", fig.cap="\\label{fig:MSE} MSE for the estimation of tail (left column) and scale (right column) parameters via log-Moment estimator and MLE of a Mittag-Leffler sample with varying sample size n=25, 100, 200, varying tails on the x-axis and fixed scale equal to one, based on 5000 simulation runs.", out.width = '90%'}
+For smaller tails both estimators show an increasing rmse for the scale estimation due to an increasing variance.
+This results from the fact that in case of very small tails, single very large values can occur.
+
+```{r MSE, echo=FALSE,warning=FALSE, fig.height=7,fig.width=8,fig.align="center", fig.cap="\\label{fig:MSE} Rmse for the estimation of tail (left column) and scale (right column) parameters via log-Moment estimator and MLE of a Mittag-Leffler sample with varying sample size n=25, 100, 200, varying tails on the x-axis and fixed scale equal to one, based on 5000 simulation runs.", out.width = '90%'}
 load(here::here("article_springer", "article_springer_files", "ML_estim_simu","tbl_ML_estim.RData"))
@@
   facet_wrap(c("n","param"), scales = "free", ncol = 2, labeller = labeller(n = n.labs)) + 
-  scale_color_manual(values=c("red", "blue"),name = "Method", labels = c("log-Moment", "MLE"))
+  scale_color_manual(values=c("red", "blue"),name = "Method", labels = c("log-Moment", "MLE")) + ggtitle("Rmse for log-Moment and MLE") +
+   theme(plot.title = element_text(hjust = 0.5))
 
@@
 It heavily depends on the choice of $r$ in \eqref{eq:Hill}, and hence on the number of order statistics entering \eqref{eq:Hill}.
-Figure \ref{fig:Hillplots} shows Hill plots for simulated Mittag-Leffler data, with varying sample sizes and tails.
+Figure \ref{fig:Hillplots} shows 100 Hill plots (grey thin lines) for simulated Mittag-Leffler data with tail parameter $\beta=0.8$ and scale $\sigma=1$, for a sample size of $n=200$ (left) and $n=1000$ (right).
+The dark lines are the means and the red dotted lines show the true tail
+parameter.
 To deduce the correct tail parameter estimates from one of those Hillplots is virtually impossible.
@@
 
-grid.arrange(p1,p2,nrow=2)
+grid.arrange(p1,p2,nrow=2,top="Hillplots") 
 ```
@@
   scale_color_manual(values=c("red", "blue","darkgreen","black"), name  ="Sample size") +
-  ggtitle("Power of Likelihood-Ratio Test")
+  ggtitle("Power of Likelihood-Ratio Test")+
+   theme(plot.title = element_text(hjust = 0.5))
 ```
@@
 
-4. Plot $k$ vs.\ $k^{1/\hat \beta} \hat \sigma_k$. Again, choose a region of *stability* and, and choose a representative $\hat \sigma_0$ from that region.
+4. Plot $k$ vs.\ $k^{1/\hat \beta} \hat \sigma_k$. Again, choose a region of *stability* and a representative $\hat \sigma_0$ from that region.
 
@@
 
+The magnitudes are in all scenarios standard Gumbel distributed.
 In order to have exact analytical values available for $\beta$ and $\sigma_0$, a distribution for $W_k$ needs to be chosen for which $b(n)$ from \eqref{eq:stability} is known.
@@
   # arrangeGrob(hill_Ex1_tail,hill_Ex2_tail,hill_Ex3_tail,top="Hill"),
-  ncol=2
+  ncol=2, top="Stability plots: tail parameter"
 )
@@
   arrangeGrob(mle_Ex1_scale,mle_Ex2_scale,mle_Ex3_scale,top="MLE"),
-  ncol = 2
+  ncol = 2, top="Stability plots: scale parameter"
 )
@@
 extRemes::qqplot(x = log(sample_data), y = log(population_data), 
-                 main = "QQ-plot: Exceed. Times vs Mittag-Leffler",
+                 main = "QQ-plot: Exceed. Times vs Mittag-Leffler",font.main = 1,
                  xlab = "log Exceedance Times", 
@@
 approximates the risk of a threshold crossing per unit time, and is a decreasing function for the Mittag-Leffler distribution. 
-```{r hazard, fig.height=4, fig.cap="\\label{fig:hazard} Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\\beta = 0.8$, $\\sigma_0 = 1$).
+```{r hazard, fig.height=4, fig.cap="\\label{fig:hazard} Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\\beta = 0.9$, $\\sigma_0 = 1$).
 Right: Hazard rate depending on tail parameter $\\beta$."}
-tail <- 0.7
+tail <- 0.9
 scale <- 1
@@
 plot(xx, rep(1, length(xx)), ylim = c(0.001,1), type = 'n', log = 'xy', 
-     xlab = 't', ylab = 'p', main = "Next Threshold Crossing Time")
+     xlab = 't', ylab = 'p', main = "Next Threshold Crossing Time",font.main = 1)
 for (k in 1:length(t_0)) {
@@
 
-betas <- c(0.7, 0.8, 0.95, 0.99)
+betas <- c(0.7, 0.8, 0.9, 0.99)
 t_0 <- 1
@@
 plot(xx, rep(1, length(xx)), ylim = c(0.001,2), type = 'n', log = 'xy', 
-     xlab = 't', ylab = 'h', main = "Mittag-Leffler Hazard Rate")
+     xlab = 't', ylab = 'h', main = "Mittag-Leffler Hazard Rate",font.main = 1)
 for (k in 1:length(betas)) {
@@
 }
-legend("bottomleft", c("beta = 0.7", "beta = 0.8", "beta = 0.95", "beta = 0.99"), col = c("red","blue","darkgreen","black"), lty = 2:5)
+legend("bottomleft", c("beta = 0.7", "beta = 0.8", "beta = 0.9", "beta = 0.99"), col = c("red","blue","darkgreen","black"), lty = 2:5)
 

### 2020-04-14 article_springer/article_springer.tex
Last small changes

@@
 the Exceedance Point Process for a Stationary Sequence,'' 1988). Then as
-one increases the threshold and thus decreases the threshold crossing
-probability \(p_{\ell}\), the Poisson process is rarefied, i.e.~its
-intensity decreases \emph{linearly} with \(p_{\ell}\) (see e.g.~Beirlant
-et al., 2006).
+one increases the threshold \(\ell\) and thus decreases the threshold
+crossing probability \(p_{\ell}\), the Poisson process is rarefied,
+i.e.~its intensity decreases \emph{linearly} with \(p_{\ell}\) (see
+e.g.~Beirlant et al., 2006).
 
@@
 et al., 2011), and hence the fractional Poisson process generalizes the
-standard Poisson process. Again as the threshold size increases and the
-threshold crossing probability \(p_{\ell}\) decreases, the fractional
-Poisson process is rarefied: The scale parameter of the Mittag-Leffler
-inter-arrival times of threshold crossing times increases, but
-\emph{superlinearly}; see the Theorem below.
+standard Poisson process. Again as the threshold size \(\ell\) increases
+and the threshold crossing probability \(p_{\ell}\) decreases, the
+fractional Poisson process is rarefied: The scale parameter of the
+Mittag-Leffler inter-arrival times of threshold crossing times
+increases, but \emph{superlinearly}; see the Theorem below.
 
@@
 distribution of \(J\). We assume that the \(k\)-th magnitude \(J_k\)
-occurs at time \(T_k = W_1 + \ldots + W_k\). Based on an MRP, we define
+occurs at time \(T_k = W_1 + \ldots + W_k\). Based on a MRP, we define
 the Continuous Time Random Exceedance model (CTRE) as follows:
@@
 \item[\textbf{Theorem:}]
-Let the waiting times \(W_k\) be in the domain of attraction of a
-positively skewed sum-stable law with stability parameter
-\(0 < \beta < 1\); more precisely, \begin{align} \label{eq:stability}
+For the magnitudes \(J_k\) assumption \eqref{assumptionJs} holds.
+Furthermore, let the waiting times \(W_k\) be in the domain of
+attraction of a positively skewed sum-stable law with stability
+parameter \(0 < \beta < 1\); more precisely,
+\begin{align} \label{eq:stability}
 \frac{W_1 + \ldots + W_n}{b(n)} \overset{d}{\longrightarrow} D, 
@@
       c \cdot p(\ell_c) \rightarrow -\log F_A(x)  \text{ as } c \rightarrow \infty,\label{eq:lplconv}
-    \end{align} with \(p(\ell_c):= \overline{F}(\ell_c)\). Since
+    \end{align} with \(p(\ell_c):= 1-F(\ell_c)\). Since
 \(\tau(\ell_c) \sim Geo(p(\ell_c))\) and \eqref{eq:lplconv} it follows
@@
     \frac{\tau(\ell_c)}{c} \Rightarrow E  \text{ as } c \rightarrow \infty
-    \end{align*} with parameter \(\lambda:=-\log F_A(x)\). Due to
+    \end{align*} with inverse mean \(\lambda:=-\log F_A(x)\). Due to
 \begin{align*}
@@
 function \begin{align}
-    \Psi(t) &= \int_0^{\infty} (\Phi_D(t))^{y} F_E(dy) \nonumber\\
-    &= \int_0^{\infty} \frac{1}{1-\log(\Phi_D(t))/\lambda} \nonumber\\
+    \Psi(s) &= \int_0^{\infty} (\Phi_D(s))^{y} F_E(dy) \nonumber\\
+    &= \int_0^{\infty} \frac{1}{1-\log(\Phi_D(s))/\lambda} \nonumber\\
     &= \frac{1}{1+s^{\beta}\lambda^{-1}}
-    \end{align} where \(\Phi_D\) resp. \(F_E\) denotes Laplace transform
-of \(D\) resp. the distribution function of \(E\). Hence, \(Z\) is
-Mittag-Leffler distributed with parameter \(\lambda^{-1/\beta}\). Since
-\begin{align*}
+    \end{align} where \(\Phi_D(s) = \exp(-s^\beta)\) is the Laplace
+transform of \(D\) and \(F_E(dy)\) is the distribution function of
+\(E\). Hence, \(Z\) is Mittag-Leffler distributed with parameter
+\(\lambda^{-1/\beta}\). Rewriting \begin{align*}
     \sum_{i=1}^{ \tau(\ell_c)} \frac{W_i}{b(1/p(\ell_c))} = \left(\sum_{i=1}^{ \tau(\ell_c)} \frac{W_i}{b(c) }\right) \frac{b(c)}{b(1/p(\ell_c))}  
-    \end{align*} and due to \begin{align*}
-    \frac{b(c)}{b(1/p(\ell_c))} = \frac{b(c)}{b(c/(p(\ell_c)c))} \sim (p(\ell_c) \cdot c)^{1/\beta} \rightarrow \lambda^{1/\beta} \text{ as } c \rightarrow \infty.
+    \end{align*} and \begin{align*}
+    \frac{b(c)}{b(1/p(\ell_c))} = \frac{b(c)}{b(c/(p(\ell_c)c))} \sim (p(\ell_c) \cdot c)^{1/\beta} \rightarrow \lambda^{1/\beta} \text{ as } c \rightarrow \infty,
     \end{align*} the second factor converges to \(\lambda^{1/\beta}\),
-it follows that \(Z \sim ML(\beta,1)\). Since \(c \rightarrow \infty\)
-is equivalent to \(\ell \uparrow x_R\) the assertion follows with
-\(\ell:=\ell_c\) and \(p_\ell:=p(\ell_c)\). \qed
+and it follows that \(Z \sim ML(\beta,1)\). Since
+\(c \rightarrow \infty\) is equivalent to \(\ell \uparrow x_R\), the
+assertion follows with \(\ell:=\ell_c\) and \(p_\ell:=p(\ell_c)\). \qed
 
@@
 Figure \ref{fig:MSE} shows that both estimators perform well, even for
-small sample sizes.
+small sample sizes. For smaller tails both estimators show an increasing
+rmse for the scale estimation due to an increasing variance. This
+results from the fact that in case of very small tails, single very
+large values can occur.
 
@@
 
-\caption{\label{fig:MSE} MSE for the estimation of tail (left column) and scale (right column) parameters via log-Moment estimator and MLE of a Mittag-Leffler sample with varying sample size n=25, 100, 200, varying tails on the x-axis and fixed scale equal to one, based on 5000 simulation runs.}\label{fig:MSE}
+\caption{\label{fig:MSE} Rmse for the estimation of tail (left column) and scale (right column) parameters via log-Moment estimator and MLE of a Mittag-Leffler sample with varying sample size n=25, 100, 200, varying tails on the x-axis and fixed scale equal to one, based on 5000 simulation runs.}\label{fig:MSE}
 \end{figure}
@@
 statistics entering \eqref{eq:Hill}. Figure \ref{fig:Hillplots} shows
-Hill plots for simulated Mittag-Leffler data, with varying sample sizes
-and tails. To deduce the correct tail parameter estimates from one of
-those Hillplots is virtually impossible. To estimate the tail parameter
-of a Mittag-Leffler distribution with the Hill estimator, the sample
-size has to be much larger and one has to choose a small tuning
-parameter \(r\). In case that only events above a high threshold are
-recorded, \(n=10000\) events are extremely unrealistic. There is a vast
-literature on bias-reduced versions of the Hill estimator and on the
-optimal choice of \(r\), mainly based on imposed second-order regular
-variation conditions (see e.g.~Beirlant et al., 2006, p. Ch.4.4 and 4.7
-and references in it). Also, there are hundreds other tail-index
-estimators not considered in this article, since this would go beyond
-the scope of our article. For example the moment estimator (Dekkers et
-al., 1989), the Pickands estimator (Pickands III and others, 1975), the
-QQ-estimator (Kratz and Resnick, 1996), to name a few. A nice overview
-can be found in (Fedotenkov, 2018). However, we know from the Theorem in
-Section \ref{sec:scaling} that the inter-exceedance times are
-asymptotically Mittag-Leffler distributed, and hence it is unsurprising
-that general tail (and scale) estimation methods that do not take into
-account this structure are statistically less efficient (Kozubowski,
-2001). Finally, the Hill estimator completely fails in the important
-special case where the inter-arrival times are exponentially distributed
-and not heavy-tailed. For these reasons, we propose to use the
-log-Moment estimator or the MLE for Mittag-Leffler distributions.
+100 Hill plots (grey thin lines) for simulated Mittag-Leffler data with
+tail parameter \(\beta=0.8\) and scale \(\sigma=1\), for a sample size
+of \(n=200\) (left) and \(n=1000\) (right). The dark lines are the means
+and the red dotted lines show the true tail parameter. To deduce the
+correct tail parameter estimates from one of those Hillplots is
+virtually impossible. To estimate the tail parameter of a Mittag-Leffler
+distribution with the Hill estimator, the sample size has to be much
+larger and one has to choose a small tuning parameter \(r\). In case
+that only events above a high threshold are recorded, \(n=10000\) events
+are extremely unrealistic. There is a vast literature on bias-reduced
+versions of the Hill estimator and on the optimal choice of \(r\),
+mainly based on imposed second-order regular variation conditions (see
+e.g.~Beirlant et al., 2006, p. Ch.4.4 and 4.7 and references in it).
+Also, there are hundreds other tail-index estimators not considered in
+this article, since this would go beyond the scope of our article. For
+example the moment estimator (Dekkers et al., 1989), the Pickands
+estimator (Pickands III and others, 1975), the QQ-estimator (Kratz and
+Resnick, 1996), to name a few. A nice overview can be found in
+(Fedotenkov, 2018). However, we know from the Theorem in Section
+\ref{sec:scaling} that the inter-exceedance times are asymptotically
+Mittag-Leffler distributed, and hence it is unsurprising that general
+tail (and scale) estimation methods that do not take into account this
+structure are statistically less efficient (Kozubowski, 2001). Finally,
+the Hill estimator completely fails in the important special case where
+the inter-arrival times are exponentially distributed and not
+heavy-tailed. For these reasons, we propose to use the log-Moment
+estimator or the MLE for Mittag-Leffler distributions.
 
@@
 
-\caption{\label{fig:Hillplots} Hillplots for m=100 simulated Mittag-Leffler datasets with true tail 0.8 and sample size 200 (left) and 10000 (right), with number of upper order statistics r on which the Hill estimator is based on the x-axis.
+\caption{\label{fig:Hillplots} Hillplots for m=100 simulated Mittag-Leffler datasets with true tail 0.8 and sample size 200 (first panel) and 10000 (second panel), with number of upper order statistics r on which the Hill estimator is based on the x-axis.
 The grey thin lines are the Hill plots for the different simulation runs and the dark lines are their means.
@@
   Plot \(k\) vs.~\(k^{1/\hat \beta} \hat \sigma_k\). Again, choose a
-  region of \emph{stability} and, and choose a representative
-  \(\hat \sigma_0\) from that region.
+  region of \emph{stability} and a representative \(\hat \sigma_0\) from
+  that region.
 \end{enumerate}
@@
 
-In order to have exact analytical values available for \(\beta\) and
+The magnitudes are in all scenarios standard Gumbel distributed. In
+order to have exact analytical values available for \(\beta\) and
 \(\sigma_0\), a distribution for \(W_k\) needs to be chosen for which
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{article_springer_files/figure-latex/hazard-1} \caption{\label{fig:hazard} Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\beta = 0.8$, $\sigma_0 = 1$).
+\includegraphics[width=\textwidth]{article_springer_files/figure-latex/hazard-1} \caption{\label{fig:hazard} Left: Conditional distribution of time until next threshold crossing, depending on elapsed time $t_0$ since last crossing ($\beta = 0.9$, $\sigma_0 = 1$).
 Right: Hazard rate depending on tail parameter $\beta$.}\label{fig:hazard}

### 2020-04-14 article_springer/changes.Rmd
Last small changes

@@
   - Smarak Nayak
-date: "11 März 2020"
+date: "14 April 2020"
 bibliography: CTRMstats.bib
@@
 Below we explain point by point how we addressed the comments during our revision of the manuscript.
+Additionally you can find attached a pdf version of the revised manuscript where you can track the changes we have made.
 
@@
 We just forgot to add the assumption, that the distribution of the magnitudes is out of the domain of attraction of an extreme value distribution.
-We added this assumption in Section 2.
+We added the following to Section 2: "We assume for the rest of the article, that the magnitudes $(J_i)_{i \in \mathbb{N}}$ belong to the the max-domain of attraction of some non-degenerate distribution.
+This means there exist $a_n>0$ and $d_n \in \mathbb{R}$ such that
+\begin{align} \label{assumptionJs}
+a_n^{-1}(J_1 \vee \ldots \vee J_n -d_n) \Rightarrow A \text{ as } n \rightarrow \infty.
+\end{align}
+Hence, the distribution of $A$ is a generalized extreme value distribution (GEV) which distribution function is given by 
+$$ F(x;\xi) = \begin{cases}\exp(-(1+\xi x)^{-1/\xi}) & \xi\neq0 \\ \exp(-\exp(-x)) & \xi = 0\end{cases}.$$ 
+The GEV is subdivided into the Gumbel ($\xi=0$), the Weibull ($\xi<0$) and the Fréchet ($\xi>0$) family of distributions."
 
@@
 
-* We have re-written the entire section titled "Simulation study".
+* We have re-written the entire section titled "Simulation study" and added labels as well as titles to the plots.
 
@@
 * Thank you for this valuable hint and the reference for the article of Peter Hall.
-We added a sentence regarding bias-reduced versions of the Hill estimator at the end of Section 4.
-Moreover, we decided to discard the Hill estimator from the simulation study since we already gave at the end of Section 4 sufficient arguments, why we propose to use a parametric estimator based on the Mittag-Leffler distribution instead of a general tail index estimator.
+We added a sentence regarding bias-reduced versions of the Hill estimator at the end of Section 4: "There is a vast literature on bias-reduced versions of the Hill estimator and on the optimal choice of $r$, mainly based on imposed second-order regular variation conditions [see e.g.
+@beirlantBook, Ch.4.4 and 4.7 and references in it]." Moreover, we decided to discard the Hill estimator from the simulation study since we already gave at the end of Section 4 sufficient arguments, why we propose to use a parametric estimator based on the Mittag-Leffler distribution instead of a general tail index estimator.
 Otherwise this would just confuse the reader.
+We have added the following sentences near the end of Section 4: "Also, there are hundreds other tail-index estimators not considered in this article, since this would go beyond the scope of our article.
+For example the moment estimator [@dekkers1989moment], the Pickands estimator [@pickands1975statistical], the QQ-estimator [@Kratz96], to name a few.
+A nice overview can be found in [@fedotenkov2018review].
+However, we know from the Theorem in Section 3 that the inter-exceedance times are asymptotically Mittag-Leffler distributed, and hence it is unsurprising that general tail (and scale) estimation methods that do not take into account this structure are statistically less efficient [@kozubowski2001].
+Finally, the Hill estimator completely fails in the important special case where the inter-arrival times are exponentially distributed and not heavy-tailed.
+For these reasons, we propose to use the log-Moment estimator or the MLE for Mittag-Leffler distributions."
 
@@
 
-* In the last paragraph of Section 5, we have included pointers to the literature for confidence intervals for the shape and scale parameters of the Mittag-Leffler distribution, and how these lead to "confidence bands" in our plots, based on the CTRE package.
+* In the last paragraph of Section 5, we have included pointers to the literature for confidence intervals for the shape and scale parameters of the Mittag-Leffler distribution, and how these lead to "confidence intervals" in our plots, based on the CTRE package: "For computationally efficient estimates of the Mittag-Leffler parameters we have used
+the method of log-transformed moments. This estimation method provides 
+point estimates as well as confidence intervals based on sampling variance [@Cahoy2013], 
+and has been implemented in the R software package
+`MittagLeffleR` [@MittagLeffleR]. The stability plots for $\hat \beta$ and $\hat \sigma_0$
+can be furnished with these confidence intervals, see e.g.\ Figure 10, 
+to produce (non-simultaneous) confidence bands."
 
@@
 32. fixed
-33. We have commented as follows: 
+33. We have commented at the end of Section 7 as follows: 
     "The stability plot for the tail stabilizes nicely around 0.9 (dashed line), while 
@@
 "I understand the authors find inspiration in Peaks-Over-Threshold (POT)
-method of extreme value theory, although, I do not see a real connection be-
-tween two models. Observe that the peaks over threshold l are ignored, so
-random variable $\tau(l)$ could be substituted by any other independent geo-
-metric (or exponential) random variable with mean $1/p(l)$. Moreover, I think, this would simplify some arguments, including the proof of the theorem."
+method of extreme value theory, although, I do not see a real connection between two models. Observe that the peaks over threshold l are ignored, so
+random variable $\tau(l)$ could be substituted by any other independent geometric (or exponential) random variable with mean $1/p(l)$.
+Moreover, I think, this would simplify some arguments, including the proof of the theorem."
 
 * One connection to the Peaks-Over-Threshold (POT) method is, that one has to apply the classical POT approach to the magnitudes.
-To make this more clear for the reader, we added a comment at the beginning of Section 4.
+To make this more clear for the reader, we added the following comment at the beginning of Section 4:"The classical POT approach is based on the fact that exceedances above a high threshold are asymptotically GPD distributed, hence a GPD distribution is fitted to the exceedances above a high enough threshold.
+As this approach is by now well-established in extreme value theory, we do not discuss it any further.
+Instead, this article focuses on our new contribution: the modelling of inter-exceedance times.
+For literature pointing to POT see e.g.
+@smith1984threshold; @leadbetter1991basis; @davison1990models; @beirlantBook Ch.5.3; @embrechts2013modelling Ch.
+6.5.; @ColesBook Ch.4."
 Additionally, and indeed inspired by the POT method, we propose to fit the inter-exceedance times in a similar fashion: namely, by fitting a Mittag-Leffler distribution to the inter-exceedance times between the peaks over threshold via stability plots.
@@
 Our algorithm could potentially be improved by i) fitting a GPD distribution to the exceedances and thus ii) more accurately approximating the tail probability $p_{\ell}$.
-We mention this idea in a remark following the algorithm.
+We mention this idea in a remark following the algorithm: "We approximated $p_{\ell}$, the probability that an event is larger than $l$, by its relative frequency.
+One could also approximate this tail probability by the GPD distribution fitted to the exceedances."
 
@@
 If there are still clusters thereafter (see for example p.3 in @towe2020modelling), the CTRE can possible account for this behavior.
-We added a comment on this to the Discussion & Conclusion Section.
+We added a comment on this to the Discussion & Conclusion Section: "In sum, the CTRE approach should not be seen as a substitute for the usual cluster approach, but rather as a complementary approach.
+Moreover, it was observed in @towe2020modelling that clusters of extreme events still exist after declustering.
+We believe it is possible to marry the clustering approach with our CTRE approach by considering CTREs based on MRPs with a _stationary_, rather than i.i.d., sequence of magnitudes, so that the times between clusters are asymptotically Mittag-Leffler distributed.
+More broadly speaking, the identification of clusters in the context of heavy-tailed inter-arrival times is an open problem."
 
-"Although auto-correlation plots given in Figure 7, after log-transforming data (this does not always ensure infiniteness of moments note) seem to indicate limited dependence in the sequence $log T(l,n)$, it is well known that the choice of such a transformation can in influence appearance of a corresponding graph."
+"Although auto-correlation plots given in Figure 7, after log-transforming data (this does not always ensure infiniteness of moments note) seem to indicate limited dependence in the sequence $log T(l,n)$, it is well known that the choice of such a transformation can influence appearance of a corresponding graph."
 
@@
 The log-Moments of a Mittag-Leffler distribution exist.
-We added a comment on this in Section 7 to the part "i.i.d.".
+We added a comment on this in Section 7 to the part "i.i.d.": "Since we are expecting the inter-exceedance times to be Mittag-Leffler distributed and hence to have infinite mean but finite log-moments, we first take the logarithms of the times."
 It is also true that the log-transformation can influence the appearance of the graph.
@@
 However, this is just a diagnostic tool to indicate whether the independence assumption is justified.
-We added a comment on this issue in Section 7 after describing the diagnostic tools.
+We added a comment on this issue in Section 7 after describing the diagnostic tools: "The ACF plots of course can just give an indication whether there are dependencies, since they actually just measure linear dependencies.
+Furthermore, if one calculates the ACF for the logarithmic inter-exceedance times, the ACF indicates on the original scale a multiplicative dependence."
 
@@
 In the setting of our article the inter-exceedance times we want to model are approximately Mittag-Leffler distributed, hence it is natural to use specific Mittag-Leffler scale and tail estimators here.
+See Section 4: "However, we know from the Theorem in Section 3 that the inter-exceedance times are asymptotically Mittag-Leffler distributed, and hence it is unsurprising that general tail (and scale) estimation methods that do not take into account this structure are statistically less efficient [@kozubowski2001]."
 
@@
 
-* We revised the whole manuscript according typos, added the missing assumption for the magnitudes and replaced the proof of the theorem by a new, simplified version.
+* We revised the whole manuscript according typos, added the missing assumption for the magnitudes and replaced the proof of the theorem by a new, simplified version, inspired by your suggestions.
 
@@
 
-* We added a definition for the left and the right point. For the role of the magnitudes, see above.
+* We added a definition for the left and the right point following the Defintion of the MRP in Section 2. For the role of the magnitudes, see above.
 
@@
 * For very small tail indices, the (R)MSE is large due to a large variance that results from the fact that in case of a very small tail index single very large events can happen.
+We added the following comment to Section 4: "For smaller tails both estimators show an increasing rmse for the scale estimation due to an increasing variance.
+This results from the fact that in case of very small tails, single very large values can occur."
 In the submitted version of the article the simulation study was based on one thousand simulation runs.
@@
 * We changed this accordingly.
+
+# References {-}

### 2020-04-14 article_springer/article_springer.Rmd
Change abstract, third person

@@
   email: "hees@statistik.tu-dortmund.de"
+  correspondence: true
 
@@
   inter-arrival times between events such as solar flares, trades and 
-  neuron voltages follow a heavy-tailed distribution. The set of event times is fractal-like, being dense in some 
-  time windows and empty in others, a phenomenon which has been dubbed 
+  neuron voltages follow a heavy-tailed distribution. The set of event times is fractal-like, 
+  being dense in some time windows and empty in others, a phenomenon which has been dubbed 
   "bursty".
 
-  This article proposes a new model for the _inter-exceedance times_ of events 
-  above high thresholds; the threshold exceedances itself are modeled via the standard 
+  A new model for the _inter-exceedance times_ of events 
+  above high thresholds is proposed; the threshold exceedances itself are modeled via the standard 
   Peaks-Over-Threshold (POT) method. For high thresholds and 
-  infinite-mean waiting times, we show that the times between threshold 
+  infinite-mean waiting times, it is shown that the times between threshold 
   crossings are Mittag-Leffler distributed, and thus form a "fractional 
@@
   exceedances.
-  We provide graphical means of estimating model parameters and assessing 
-  model fit. Along the way, we apply our inference method to a real-world
-  bursty time series, and 
-  show how the memory of the Mittag-Leffler distribution affects 
+  Graphical means of estimating model parameters and assessing 
+  model fit are provided. Along the way, the inference method gets applied to a real-world
+  bursty time series, and it is shown how the memory of the Mittag-Leffler distribution affects 
   the predictive distribution for the time until the next extreme event.

### 2020-07-19 article_springer/article_springer.Rmd
Address Referee 1's comments

@@
 Then as one increases the threshold $\ell$ and thus decreases the threshold 
-crossing probability $p_{\ell}$, the Poisson process is rarefied, i.e. its 
+crossing probability $p_{\ell}$, the Poisson process is thinned, i.e. its 
 intensity decreases _linearly_ with $p_{\ell}$ [see e.g. @beirlantBook].
@@
 Again as the threshold size $\ell$ increases and the threshold crossing
-probability $p_{\ell}$ decreases, the fractional Poisson process is rarefied: 
+probability $p_{\ell}$ decreases, the fractional Poisson process is thinned: 
 The scale parameter of the Mittag-Leffler inter-arrival times of 
@@
 \end{align}
-Hence, the distribution of $A$ is a generalized extreme value distribution (GEV) which distribution function is given by 
-$$ F(x;\xi) = \begin{cases}\exp(-(1+\xi x)^{-1/\xi}) & \xi\neq0 \\ \exp(-\exp(-x)) & \xi = 0\end{cases}.$$ 
+Hence, the distribution of $A$ is a generalized extreme value distribution (GEV) whose distribution function is given by 
+$$ F(x;\xi) = \begin{cases}\exp(-(1+\xi x)_+^{-1/\xi}) & \xi\neq0 \\ \exp(-\exp(-x)) & \xi = 0\end{cases}$$ 
+where $(.)_+:= \max\{0,.\}$.
+
 The GEV is subdivided into the Gumbel ($\xi=0$), the Weibull ($\xi<0$) and the Fréchet ($\xi>0$) family of distributions.
@@
 
-In this section we state and prove the key theorem. For an accessible introduction to regular variation and stable limit theorems, we recommend the book by @MeerschaertSikorskii.
+In this section we state and prove the key theorem, which is founded on the concept of regular variation.
+A Borel-measurable function $f:\mathbb (0,\infty) \to (0,\infty)$ is said be "regularly varying at $\infty$ with parameter (or "index") $\rho$ if
+
+$$
+\frac{f(\lambda x)}{f(x)} = \lambda^\rho \quad \text{ for all } \lambda > 0.
+$$
+
+For more details regular variation and stable limit theorems, we recommend the book by @MeerschaertSikorskii.
 
@@
 \end{align}
-for a function $b(n)$ which is regularly varying at $\infty$ with parameter $1/\beta$, and where $\mathbf E[\exp(-sD)] = \exp(-s^\beta)$.
+for a function $b(n)$ which is regularly varying at $\infty$ with parameter $1/\beta$, and where $\mathbf E[\exp(-sD)] = \exp(-s^\beta)$, $s > 0$.
 Write $p_{\ell} := \mathbf P(J > \ell)$.
@@
 
-*Proof of Theorem:* 	Due to assumption \eqref{assumptionJs}, it follows
+*Proof of Theorem:* 	Due to assumption \eqref{assumptionJs}, it follows that
 	\begin{align*}
-	P\left(\frac{M(c)-d(c)}{a(c)} \leq x\right) \rightarrow F(x) \text{ as } c \rightarrow \infty,
+	P\left(\frac{M(c)-d(c)}{a(c)} \leq x\right) \rightarrow F(x) := F(x,\xi) \text{ as } c \rightarrow \infty,
 	\end{align*}
-	where $x$ is any value from the support of $F$. Then it follows,
+	where $x$ is any value from the support of $F$. Then
 	\begin{align*}
@@
 	\end{align*}
-    it follows with Gnedenkos transfer theorem (see @gnedenko1983limit), that
+    it follows with Gnedenko's transfer theorem (see @gnedenko1983limit), that
 	\begin{align}
@@
 Figure \ref{fig:MSE} shows that both estimators perform well, even for small sample sizes.
-For smaller tails both estimators show an increasing rmse for the scale estimation due to an increasing variance.
+For smaller tails both estimators show an increasing RMSE for the scale estimation due to an increasing variance.
 This results from the fact that in case of very small tails, single very large values can occur.
 
-```{r MSE, echo=FALSE,warning=FALSE, fig.height=7,fig.width=8,fig.align="center", fig.cap="\\label{fig:MSE} Rmse for the estimation of tail (left column) and scale (right column) parameters via log-Moment estimator and MLE of a Mittag-Leffler sample with varying sample size n=25, 100, 200, varying tails on the x-axis and fixed scale equal to one, based on 5000 simulation runs.", out.width = '90%'}
+```{r MSE, echo=FALSE,warning=FALSE, fig.height=7,fig.width=8,fig.align="center", fig.cap="\\label{fig:MSE} RMSE for the estimation of tail (left column) and scale (right column) parameters via log-Moment estimator and MLE of a Mittag-Leffler sample with varying sample size n=25, 100, 200, varying tails on the x-axis and fixed scale equal to one, based on 5000 simulation runs.", out.width = '90%'}
 load(here::here("article_springer", "article_springer_files", "ML_estim_simu","tbl_ML_estim.RData"))
@@
   facet_wrap(c("n","param"), scales = "free", ncol = 2, labeller = labeller(n = n.labs)) + 
-  scale_color_manual(values=c("red", "blue"),name = "Method", labels = c("log-Moment", "MLE")) + ggtitle("Rmse for log-Moment and MLE") +
+  scale_color_manual(values=c("red", "blue"),name = "Method", labels = c("log-Moment", "MLE")) + ggtitle("RMSE for log-Moment and MLE") +
    theme(plot.title = element_text(hjust = 0.5))
@@
 parameter.
-To deduce the correct tail parameter estimates from one of those Hillplots is virtually impossible.
+To deduce the correct tail parameter estimates from one of those Hill plots is virtually impossible.
 To estimate the tail parameter of a Mittag-Leffler distribution with the Hill estimator, the sample size has to be much larger and one has to choose a small tuning parameter $r$.
@@
 
-```{r Hillplots,  fig.height=5, fig.width=4, echo=FALSE,warning=FALSE, fig.align="center", fig.cap="\\label{fig:Hillplots} Hillplots for m=100 simulated Mittag-Leffler datasets with true tail 0.8 and sample size 200 (first panel) and 10000 (second panel), with number of upper order statistics r on which the Hill estimator is based on the x-axis.
+```{r Hillplots,  fig.height=5, fig.width=4, echo=FALSE,warning=FALSE, fig.align="center", fig.cap="\\label{fig:Hillplots} Hill plots for m=100 simulated Mittag-Leffler datasets with true tail 0.8 and sample size 200 (first panel) and 10000 (second panel), with number of upper order statistics r on which the Hill estimator is based on the x-axis.
 The grey thin lines are the Hill plots for the different simulation runs and the dark lines are their means.
@@
 
-grid.arrange(p1,p2,nrow=2,top="Hillplots") 
+grid.arrange(p1,p2,nrow=2,top="Hill plots") 
 ```
@@
 
-We have extended the POT (Peaks-over-Threshold) model, a mainstay of extreme value theory, to "bursty" time series, which have been studied 
+We have applied the POT (Peaks-over-Threshold) model, a mainstay of extreme value theory, to "bursty" time series, which have been studied 
 intensively in statistical physics.
@@
 
-The bursty CTRE approach to model "non-Poissonian" threshold crossing times should be contrasted with the (now standard) approach of clusters of extremes, see e.g.
+The CTRE approach to model "non-Poissonian" threshold crossing times should be contrasted with the well-documented approach of clusters of extremes, see e.g.
 @ferro2003inference.
-In this approach, i.i.d.
-event sequences of magnitudes are generalized to stationary sequences of
-event magnitudes (subject to a mixing condition).
-The two approaches are fundamentally different: Clustering assumes that each event belongs to one particular (latent) group of events.
-For bursts, however, the aim is to identify an underlying scale-free pattern in the event
-dynamics, which is often characteristic of complex systems.
-It is an interesting open problem to develop criteria, based e.g.
-on measures of surprise [@Lee15], that guide an applied statistician in the choice between a clustering and a CTRE approach for a particular problem.
-In sum, the CTRE approach should not be seen as a substitute for the usual cluster approach, but rather as a complementary approach.
-
-Moreover, it was observed in @towe2020modelling that clusters of extreme events still exist after declustering.
-We believe it is possible to marry the clustering approach with our CTRE approach by considering CTREs based on MRPs with a _stationary_, rather than i.i.d., sequence of magnitudes, so that the times between clusters are asymptotically Mittag-Leffler distributed.
-More broadly speaking, the identification of clusters in the context of heavy-tailed inter-arrival times is an open problem.
-
-Finally, a purely scale-free pattern for event times may be too rigid an 
-assumption for some bursty time series, because often the heavy-tailed character of the inter-arrival time
-distribution does not hold at all time scales. Rather, it applies at short and intermediate time scales, and is truncated (or tempered, 
+When the underlying stochastic process is *stationary*, the exceedances of high thresholds form, asymptotically, a *Cluster Poisson Process*.
+In the setting of this article, however, clustering-like dynamics occur due to the *non-stationarity* of the underlying renewal-reward process, which has infinite-mean renewal times. 
+Hence CTRE and Cluster Poisson Process shouldn't be viewed as competing methods, as the underlying data generating processes are quite different.
+In weighing the evidence for either of the two data generating processes, criteria could be developed, based e.g.
+on measures of surprise [@Lee15], which may prove to be valuable for future applied statisticians.
+
+Finally, we note that assuming a purely scale-free pattern for event times may be too rigid an 
+assumption, which unnecessarily limits the applicability of CTREs. Often, the heavy-tailed character of the inter-arrival time
+distribution holds at short to intermediate time scales, and is truncated (or tempered, 
 reverting to an exponential distribution) at very long time scales [see e.g.
 @MeerschaertRoyQin; and @Aban06].
-In such situations, a "tempered" Mittag-Leffler distribution may provide a more realistic fit, which we aim to introduce in follow-up work.
+In such situations, a "tempered" Mittag-Leffler distribution may provide a better fit, which we aim to introduce in follow-up work.
 

### 2020-07-24 article_springer/article_springer.Rmd
Address Referee 2's comments

@@
   A new model for the _inter-exceedance times_ of events 
-  above high thresholds is proposed; the threshold exceedances itself are modeled via the standard 
-  Peaks-Over-Threshold (POT) method. For high thresholds and 
+  above high thresholds is proposed. For high thresholds and 
   infinite-mean waiting times, it is shown that the times between threshold 
@@
 
+**Remark:**
+
+:[@MeerschaertStoev08] proofed a limit theorem for the maxima of iid random variables separated by infinite mean waiting times.
+They showed that the duration time of the limit process is Mittag-Leffler distributed.
+[@Basrak2014] described the asymptotic distribution under similar assumptions of all upper orders statistics using point processes.
+
 For a scale parameter $\sigma > 0$, we write ${\rm ML}(\beta, \sigma)$ for the distribution of $\sigma Z_\beta$. The Mittag-Leffler distribution with parameter $\beta \in (0,1]$ is 
@@
 Hence CTRE and Cluster Poisson Process shouldn't be viewed as competing methods, as the underlying data generating processes are quite different.
+To differentiate between the two models we use the term *bursty* which is standard in the context of heavy-tailed inter-arrival times in the physics community [e.g.
+@Barabasi2005;@Vasquez2006;@Karsai2012;@Vajna2013]).
 In weighing the evidence for either of the two data generating processes, criteria could be developed, based e.g.

### 2020-07-25 article_springer/article_springer.Rmd
Add lim to Defintion of Regular varying functions
Merge Remark after proof into one
Addressing comment 4 of Referee 2 in the article

@@
 $$
-\frac{f(\lambda x)}{f(x)} = \lambda^\rho \quad \text{ for all } \lambda > 0.
+\underset{x\rightarrow \infty}{lim}\frac{f(\lambda x)}{f(x)} = \lambda^\rho \quad \text{ for all } \lambda > 0.
 $$
@@
 
-**Remark:**
-
-:[@MeerschaertStoev08] proofed a limit theorem for the maxima of iid random variables separated by infinite mean waiting times.
-They showed that the duration time of the limit process is Mittag-Leffler distributed.
-[@Basrak2014] described the asymptotic distribution under similar assumptions of all upper orders statistics using point processes.
-
 For a scale parameter $\sigma > 0$, we write ${\rm ML}(\beta, \sigma)$ for the distribution of $\sigma Z_\beta$. The Mittag-Leffler distribution with parameter $\beta \in (0,1]$ is 
@@
 : If $\beta = 1$, the result of the Theorem above is standard, see e.g. 
-Equation (2.2) in @Gut1999. In @Anderson1987  a similar result is shown with a different choice of scaling constant.
+Equation (2.2) in @Gut1999.
+In @Anderson1987  a similar result is shown with a different choice of scaling constant.
+[@MeerschaertStoev08] proofed a limit theorem for the maxima of iid random variables separated by infinite mean waiting times.
+They showed that the duration time of the limit process is Mittag-Leffler distributed.
+[@Basrak2014] described the asymptotic distribution under similar assumptions of all upper orders statistics using point processes.
 
@@
 A nice overview can be found in [@fedotenkov2018review].
-However, we know from the Theorem in Section \ref{sec:scaling} that the inter-exceedance times are asymptotically Mittag-Leffler distributed, and hence it is unsurprising that general tail (and scale) estimation methods that do not take into account this structure are statistically less efficient [@kozubowski2001].
+However, we know from the Theorem in Section \ref{sec:scaling} that the inter-exceedance times are asymptotically Mittag-Leffler distributed, and hence it is unsurprising that general tail (and scale) estimation methods that do not take into account this structure are statistically less efficient [@kozubowski2001] on the *thresholded* data.
 Finally, the Hill estimator completely fails in the important special case where the inter-arrival times are exponentially distributed and not heavy-tailed.
@@
 Moreover, the bottom row in Figure \ref{Fig:TailSimu} shows clearly that the log-Moment and Maximum-Likelihood estimators generalize to the exponential case ($\beta = 1$) whereas the Hill-estimator would not.
+Notice that any data below a certain threshold gets discarded in our approach and hence need not to satisfy the iid assumption.
+In our simulation study we only simulated data from iid sequences of $(W_k)_{k \in \mathbb{N}}$, in real data situations its likely that there are dependencies or more complex data generating processes vanishing for higher thresholds.
+We only need the exceedances as well as the inter-exceedance times to be iid.
 

### 2020-07-26 article_springer/article_springer.Rmd
Solved problem: df_LRT_boot_01 %>% filter(n=="20" || n=="50" || n=="100" || n=="200") Error: Corrupt `grouped_df` using old (< 0.8.0) format. i Strip off old grouping with `ungroup()`.

@@
 tbl_ML_estim %>% filter(method=="logMom" | method=="ML")%>%
-  filter(n == "25" || n == "100" || n=="200") %>%
+  filter(n == "25" | n == "100" | n=="200") %>%
   filter(true.scale == "1") %>% 
@@
 load(here::here("article_springer","article_springer_files","ML_LRT_simu","estimates_df_LRT_boot1_01.RData"))
-df_LRT_boot_01 %>% filter(n=="20" || n=="50" || n=="100" || n=="200") %>% ggplot(aes(x=true.tail,y=power)) +  geom_line(aes(y=power,group=factor(n),color=factor(n),linetype=factor(n)),size=0.5)+
+df_LRT_boot_01 %>%  ungroup() %>% filter(n=="20" | n=="50" | n=="100" | n=="200") %>% ggplot(aes(x=true.tail,y=power)) +  geom_line(aes(y=power,group=factor(n),color=factor(n),linetype=factor(n)),size=0.5)+
   scale_linetype_manual(values = c("solid","dashed","twodash","dotted"),name  ="Sample size")+

### 2020-07-26 article_springer/article_springer.Rmd
make grey lines transparent to improve plot

@@
 output:
+  html_document: default
   rticles::elsevier_article:
@@
 mean_n200<-hill_plot_values %>% group_by(x) %>% summarize(mean=mean(y))
-p1<-hill_plot_values %>% ggplot() + geom_line(aes(x=x,y=y,group=rep),colour="lightgrey") +
+p1<-hill_plot_values %>% ggplot() + geom_line(aes(x=x,y=y,group=rep), alpha=0.1) +
   coord_cartesian(ylim = c(0.5, 1.5)) +
@@
 
-p2<-hill_plot_values %>% ggplot() + geom_line(aes(x=x,y=y,group=rep),colour="lightgrey") +
+p2<-hill_plot_values %>% ggplot() + geom_line(aes(x=x,y=y,group=rep), alpha=0.1) +
   coord_cartesian(ylim = c(0.5, 1.5)) +
@@
   ggplot() + geom_line(aes(x = k, y = value, group = rep),
-                       colour = "lightgrey",
+                       alpha = 0.05,
                        data = tbl_estimates_tail08_logMoms_Ex1) +
@@
   ggplot() + geom_line(aes(x = k, y = value, group = rep),
-                       colour = "lightgrey",
+                       alpha = 0.05,
                        data = tbl_estimates_tail08_mles_Ex1) +
@@
 #                        aes(x = k, y = value, group = rep),
-#                        colour = "lightgrey") +
+#                        alpha = 0.05) +
 #   coord_cartesian(ylim = c(0.5, 1.5)) +
@@
   ggplot() + geom_line(aes(x = k, y = value, group = rep),
-                       colour = "lightgrey",
+                       alpha = 0.05,
                        data = tbl_estimates_Ex2_Pareto_tail08_logMoms) +
@@
   ggplot() + geom_line(aes(x = k, y = value, group = rep),
-                       colour = "lightgrey",
+                       alpha = 0.05,
                        data = tbl_estimates_Ex2_Pareto_tail08_mles) +
@@
 #   ggplot() + geom_line(aes(x = k, y = value, group = rep),
-#                        colour = "lightgrey",
+#                        alpha = 0.05,
 #                        data = tbl_estimates_Ex2_Pareto_tail08_hill_times) +
@@
   ggplot() + geom_line(aes(x = k, y = value, group = rep),
-                       colour = "lightgrey",
+                       alpha = 0.05,
                        data = tbl_estimates_Example3_Exp_logMoms) +
@@
   ggplot() + geom_line(aes(x = k, y = value, group = rep),
-                       colour = "lightgrey",
+                       alpha = 0.05,
                        data = tbl_estimates_Example3_Exp_mles) +
@@
 #   ggplot() + geom_line(aes(x = k, y = value, group = rep),
-#                        colour = "lightgrey",
+#                        alpha = 0.05,
 #                        data = tbl_estimates_Example3_Exp_hill_times) +
@@
   ggplot() + geom_line(aes(x = k, y = value, group = rep),
-                       colour = "lightgrey",
+                       alpha = 0.05,
                        data = tbl_scales_logMoms_Ex1) +
@@
   ggplot() + geom_line(aes(x = k, y = value, group = rep),
-                       colour = "lightgrey",
+                       alpha = 0.05,
                        data = tbl_scales_mles_Ex1) +
@@
   ggplot() + geom_line(aes(x = k, y = value, group = rep),
-                       colour = "lightgrey",
+                       alpha = 0.05,
                        data = tbl_scales_logMoms_Ex2) +
@@
   ggplot() + geom_line(aes(x = k, y = value, group = rep),
-                       colour = "lightgrey",
+                       alpha = 0.05,
                        data = tbl_scales_mles_Ex2) +
@@
   ggplot() + geom_line(aes(x = k, y = value, group = rep),
-                       colour = "lightgrey",
+                       alpha = 0.05,
                        data = tbl_scales_logMoms_Ex3) +
@@
   ggplot() + geom_line(aes(x = k, y = value, group = rep),
-                       colour = "lightgrey",
+                       alpha = 0.05,
                        data = tbl_scales_mles_Ex3) +

### 2020-07-26 article_springer/article_springer.Rmd
typos

@@
 $$
-\underset{x\rightarrow \infty}{lim}\frac{f(\lambda x)}{f(x)} = \lambda^\rho \quad \text{ for all } \lambda > 0.
-$$
-
-For more details regular variation and stable limit theorems, we recommend the book by @MeerschaertSikorskii.
+\lim_{x \to \infty} \frac{f(\lambda x)}{f(x)} = \lambda^\rho \quad \text{ for all } \lambda > 0.
+$$
+
+For more details on regular variation and stable limit theorems, we recommend the book by @MeerschaertSikorskii.
 
@@
 
-: For the magnitudes $J_k$ assumption \eqref{assumptionJs} holds.
+: For the magnitudes $J_k$, let assumption \eqref{assumptionJs} hold.
 Furthermore, let the waiting times $W_k$ be in the domain of attraction of a positively skewed sum-stable law with stability parameter $0 < \beta < 1$; more precisely,

### 2020-07-27 article_springer/article_springer.Rmd
Write new section "Mittag-Leffler Stability Plots"

@@
 
-# Continuous Time Random Exceedances (CTRE)
+# Continuous Time Random Exceedances (CTRE) {#sec:CTRE}
 
@@
 
-# Model Choice and inference for the Mittag-Leffler distribution{#sec:ML}
-
-The classical POT approach is based on the fact that exceedances above a high threshold are asymptotically GPD distributed, hence a GPD distribution is fitted to the exceedances above a high enough threshold.
-As this approach is by now well-established in extreme value theory, we do not discuss it any further.
-Instead, this article focuses on our new contribution: the modelling of inter-exceedance times.
-For literature pointing to POT see e.g.
-@smith1984threshold; @leadbetter1991basis; @davison1990models; @beirlantBook Ch.5.3; @embrechts2013modelling Ch.
-6.5.; @ColesBook Ch.4.
-
-Due to the Theorem in the last Section we know that for high thresholds the times between exceedances are asymptotically Mittag-Leffler distributed in case of heavy-tailed waiting times between the observations.
-In this article we propose to model inter-exceedance times in a similar fashion as magnitudes in the classical POT approach, more precisely to fit a Mittag-Leffler distribution to the inter-exceedance times via stability plots.
-Hence, before we discuss inference for the inter-exceedance times in the next section, we first discuss inference for Mittag-Leffler distributions.
+# Mittag-Leffler Stability Plots
+
+We assume a dataset of the form $\{(T_i, X_i), i \in I\}$,
+where $T_i$ are timestamps and $X_i$ are magnitudes.
+In this article, we focus on modelling the distribution of threshold
+*exceedance times* rather than the *exceedances* themselves. For the latter, 
+see the POT approach [@smith1984threshold;
+@leadbetter1991basis; @davison1990models; @beirlantBook Ch.5.3;
+@embrechts2013modelling Ch. 6.5.; @ColesBook Ch.4.].
+With the previous section setting the stage, we assume that only the large
+magnitudes (aka "shocks") follow a MRP.  The smaller magnitudes are possibly
+nuisance data that may be irrelevant with respect to the modelling of extremes
+and their waiting times. 
+Accordingly, we assume a threshold $\ell$, and discard all
+data $(T_i, X_i)$ where $X_i \le \ell$, yielding the thinned dataset
+$\{(T_i, X_i), i \in I(\ell)\}$, where $I(\ell) \subseteq I$.
+
+However, this raises the question of how high or low the threshold should be
+chosen. Recall that with the POT method for the modelling of extremes, the
+distribution of the thresholded exceedances converges to a GPD, and the
+threshold must be chosen high enough so that the exceedances fit a GPD well. 
+The threshold choice translates into a
+bias-variance trade-off: low thresholds yield more data to fit a GPD (low 
+variance), but the distribution of exceedances may deviate from a GPD 
+distribution (high bias); and high thresholds present the opposite scenario.
+It is understood, however, that there is a *range* of threshold values that
+ought to yield similar GPD parameter estimates. In other words, plots of
+threshold vs. parameter estimate ought to exhibit that parameter estimates
+are *stable* with respect to the choice of threshold.
+
+For inter-exceedance *times* (IETs), the same idea applies. 
+By the Theorem, the inter-exceedance times converge to a Mittag-Leffler
+distribution (MLD), and importantly, the tail parameter $\beta$ is 
+*independent* of (or *stable* with respect to) the choice of threshold.
+For high thresholds, the IET distribution may fit an MLD well, but few
+IETs may be left for a fit (high variance). 
+For low thresholds, their distribution may be not well represented
+by an MLD; or, too many events may be interpreted as 
+shocks, resulting in a biased estimate of the parameters of the limiting MLD.
+For illustration, consider the case where measurements are taken daily:
+Then at the lowest threshold, all IETs equal one day,
+leaving no hint at a power-law distribution whatsoever. Raising the threshold
+may or may not produce IETs that start exhibiting a power-law; and both cases
+are represented by the MLD, with $\beta < 1$ or $\beta = 1$.
+
+Suppose the "correct" threshold $\ell_0$ was known, in the sense that 
+thresholding at $\ell_0$ would result precisely in an underlying MRP 
+$\{(W_i, J_i): i \in I\}$ as defined in Section \ref{sec:CTRE}. 
+In this case, we could apply any tail (and scale) estimator such as e.g.
+Hill's estimator to the $W_i$ and thus infer the distribution of 
+inter-exceedance times.
+
+But guessing the correct threshold $\ell_0$ and proceeding with this
+type of inference is less favourable to modelling IETs with the MLD, 
+as we now explain.
+In real-world datasets, a "correct" threshold may not exist: the data 
+$\{(T_i, X_i): i \in I\}$ may be a mixture of an MRP with some other
+time series $\{(T'_i, X'_i): i \in I'\}$, and the supports $\mathcal S'$
+and $\mathcal S$ of the distributions
+of $X'_i$ and the magnitudes $J_i$ (aka the MRP marks) may overlap.
+Then thresholding at e.g. $\ell_0 = \sup \mathcal S'$ 
+no longer results in a "clean" MRP: some $J_i$'s will be removed, meaning
+that some $W_i$'s will be merged into a longer IET.
+The more the threshold $\ell_0$ cuts into $\mathcal S$ from below, the more
+the distributions of IETs will resemble a MLD, according to the Theorem.
+As we do not know to what extent this effect occurs, 
+and since the limit is an MLD, it is practicable to fit an MLD to the IETs to 
+begin with.
+
+# Fitting Mittag-Leffler Distributions {#sec:ML}
 

### 2020-07-27 article_springer/article_springer.Rmd
Move Hill plot

@@
 In this case, we could apply any tail (and scale) estimator such as e.g.
-Hill's estimator to the $W_i$ and thus infer the distribution of 
+Hill's estimator [@hill1975simple]
+to the $W_i$ and thus infer the distribution of 
 inter-exceedance times.
@@
 
+For high thresholds where few IETs are left, estimating a tail parameter
+by fitting a MLD has advantages over e.g. the Hill estimator: 
+since the underlying distribution of IETs *is* a MLD, 
+the fits are more accurate. 
+Figure \ref{fig:Hillplots} shows Hill plots for 200 IETs, for two Mittag-Leffler
+datasets of sizes 200 and 10000 (and an irrelevant distribution of magnitudes).
+Clearly the variance is too high to give useful estimates.
+For corresponding fits based on the assumption of a Mittag-Leffler distribution,
+see Figure \ref{Fig:TailSimu}, top row, yielding more reliable predictions 
+(more discussion further below).
+
+```{r Hillplots,  fig.height=5, fig.width=4, echo=FALSE,warning=FALSE, fig.align="center", fig.cap="\\label{fig:Hillplots} Hill plots for m=100 simulated Mittag-Leffler datasets with true tail 0.8 and sample size 200 (first panel) and 10000 (second panel), with number of upper order statistics r on which the Hill estimator is based on the x-axis.
+The grey thin lines are the Hill plots for the different simulation runs and the dark lines are their means.
+The red dotted line shows the true tail parameter.
+", out.width = '50%'}
+
+hill_estim<-function(k,data){
+  n<-length(data)
+  data<-sort(data)
+  data_thinned<-data[(n-k):n]
+  r<-1/k * sum(log(data_thinned/data_thinned[1]))
+  return(1/r)
+}
+
+hill_estim_range<-function(k_min,data,k_max=n,true_tail){
+  n<-length(data)
+  x_values<-k_min:k_max
+  y_values<-sapply(x_values,hill_estim,data=data)
+  df<-data.frame(x=x_values,y=y_values)
+  return(df)
+}
+
+hill_plot_values<-data.frame(x=numeric(),y=numeric(),rep=numeric())
+for  (m in 1:100){
+data_ml_1<-rml(n=200,tail=0.8,scale=1)
+df<-hill_estim_range(k_min=30,data=data_ml_1,true_tail=0.8)
+df<-df %>% mutate(rep=m)
+hill_plot_values<-bind_rows(df,hill_plot_values)
+}
+
+mean_n200<-hill_plot_values %>% group_by(x) %>% summarize(mean=mean(y))
+p1<-hill_plot_values %>% ggplot() + geom_line(aes(x=x,y=y,group=rep), alpha=0.1) +
+  coord_cartesian(ylim = c(0.5, 1.5)) +
+  geom_line(aes(x=x, y=mean),colour="black",data=mean_n200) + 
+  ylab("Estimated tail") +
+  geom_hline(yintercept=0.8, linetype="dashed", color = "red")+
+  xlab("Order Statistics")+
+  ylab("Hill-Estimator of Tail Index")
+
+hill_plot_values<-data.frame(x=numeric(),y=numeric(),rep=numeric())
+for  (m in 1:100){
+  data_ml_2<-rml(n=10000,tail=0.8,scale=1)
+  df<-hill_estim_range(k_min=30,k_max=200,data=data_ml_2,true_tail=0.8)
+  df<-df %>% mutate(rep=m)
+  hill_plot_values<-bind_rows(df,hill_plot_values)
+}
+mean_n10000<-hill_plot_values %>% group_by(x) %>% summarize(mean=mean(y))
+
+p2<-hill_plot_values %>% ggplot() + geom_line(aes(x=x,y=y,group=rep), alpha=0.1) +
+  coord_cartesian(ylim = c(0.5, 1.5)) +
+  geom_line(aes(x=x, y=mean),colour="black",data=mean_n10000) + 
+  ylab("Estimated tail") +
+  geom_hline(yintercept=0.8, linetype="dashed", color = "red")+
+  xlab("Order Statistics")+
+  ylab("Hill-Estimator of Tail Index")
+
+grid.arrange(p1,p2,nrow=2,top="Hill plots") 
+```
+
 # Fitting Mittag-Leffler Distributions {#sec:ML}
@@
 
-Due to the form of the density function of a Mittag-Leffler distribution there exists no closed form for the Maximum Likelihood estimator (MLE).
-In the R Package `MittagLeffleR` [@MittagLeffleR], Maximum Likelihood estimation is implemented via numerical optimization.
-The MLE slightly outperforms the log-Moment estimator regarding bias and RMSE for big enough sample sizes, but is extremely computationally intensive.
+The Maximum Likelihood Estimator (MLE) for the MLD is not straightforward 
+to implement, since the MLD density admits no closed form analytical expression.
+In the R Package `MittagLeffleR` [@MittagLeffleR], MLE is implemented via numerical optimization.
+The MLE slightly outperforms the log-Moment estimator regarding bias and RMSE for big enough sample sizes, but is computationally very intensive.
 Figure \ref{fig:MSE} shows that both estimators perform well, even for small sample sizes.
@@
 
-```{r Hillplots,  fig.height=5, fig.width=4, echo=FALSE,warning=FALSE, fig.align="center", fig.cap="\\label{fig:Hillplots} Hill plots for m=100 simulated Mittag-Leffler datasets with true tail 0.8 and sample size 200 (first panel) and 10000 (second panel), with number of upper order statistics r on which the Hill estimator is based on the x-axis.
-The grey thin lines are the Hill plots for the different simulation runs and the dark lines are their means.
-The red dotted line shows the true tail parameter.
-", out.width = '50%'}
-
-hill_estim<-function(k,data){
-  n<-length(data)
-  data<-sort(data)
-  data_thinned<-data[(n-k):n]
-  r<-1/k * sum(log(data_thinned/data_thinned[1]))
-  return(1/r)
-}
-
-hill_estim_range<-function(k_min,data,k_max=n,true_tail){
-  n<-length(data)
-  x_values<-k_min:k_max
-  y_values<-sapply(x_values,hill_estim,data=data)
-  df<-data.frame(x=x_values,y=y_values)
-  return(df)
-}
-
-hill_plot_values<-data.frame(x=numeric(),y=numeric(),rep=numeric())
-for  (m in 1:100){
-data_ml_1<-rml(n=200,tail=0.8,scale=1)
-df<-hill_estim_range(k_min=30,data=data_ml_1,true_tail=0.8)
-df<-df %>% mutate(rep=m)
-hill_plot_values<-bind_rows(df,hill_plot_values)
-}
-
-mean_n200<-hill_plot_values %>% group_by(x) %>% summarize(mean=mean(y))
-p1<-hill_plot_values %>% ggplot() + geom_line(aes(x=x,y=y,group=rep), alpha=0.1) +
-  coord_cartesian(ylim = c(0.5, 1.5)) +
-  geom_line(aes(x=x, y=mean),colour="black",data=mean_n200) + 
-  ylab("Estimated tail") +
-  geom_hline(yintercept=0.8, linetype="dashed", color = "red")+
-  xlab("Order Statistics")+
-  ylab("Hill-Estimator of Tail Index")
-
-hill_plot_values<-data.frame(x=numeric(),y=numeric(),rep=numeric())
-for  (m in 1:100){
-  data_ml_2<-rml(n=10000,tail=0.8,scale=1)
-  df<-hill_estim_range(k_min=30,k_max=200,data=data_ml_2,true_tail=0.8)
-  df<-df %>% mutate(rep=m)
-  hill_plot_values<-bind_rows(df,hill_plot_values)
-}
-mean_n1000<-hill_plot_values %>% group_by(x) %>% summarize(mean=mean(y))
-
-p2<-hill_plot_values %>% ggplot() + geom_line(aes(x=x,y=y,group=rep), alpha=0.1) +
-  coord_cartesian(ylim = c(0.5, 1.5)) +
-  geom_line(aes(x=x, y=mean),colour="black",data=mean_n1000) + 
-  ylab("Estimated tail") +
-  geom_hline(yintercept=0.8, linetype="dashed", color = "red")+
-  xlab("Order Statistics")+
-  ylab("Hill-Estimator of Tail Index")
-
-grid.arrange(p1,p2,nrow=2,top="Hill plots") 
-```
-
 Since the exponential distribution is nested in the Mittag-Leffler family of 

### 2020-07-27 article_springer/article_springer.Rmd
remove paragraph on "Why We Hate Hill" (Kill Hill)

@@
 
-Since the Mittag-Leffler distribution is heavy-tailed, many researchers would intuitively give the highest importance to the tail behaviour of the distribution.
-Of course, one can also use established tail exponent estimators for the estimation of the parameter $\beta$ such as the Hill estimator [@hill1975simple] based on the $r+1$ upper order statistics
-\begin{align}\label{eq:Hill}
-H_{r,n}=\left[ \frac{1}{r} \sum_{i=0}^{r} \log \frac{X_{(i)}}{X_{(r+1)}}\right]^{-1}, 
-\end{align}
-where $X_{(1)} \geq X_{(2)} \geq \ldots \geq X_{(n)}$ denote the order statistics in decreasing order of a sequence $X_1,\ldots,X_n$.
-The Hill estimator only performs reliably well for distributions close to Pareto [see @Resnick97].
-It heavily depends on the choice of $r$ in \eqref{eq:Hill}, and hence on the number of order statistics entering \eqref{eq:Hill}.
-Figure \ref{fig:Hillplots} shows 100 Hill plots (grey thin lines) for simulated Mittag-Leffler data with tail parameter $\beta=0.8$ and scale $\sigma=1$, for a sample size of $n=200$ (left) and $n=1000$ (right).
-The dark lines are the means and the red dotted lines show the true tail
-parameter.
-To deduce the correct tail parameter estimates from one of those Hill plots is virtually impossible.
-To estimate the tail parameter of a Mittag-Leffler distribution with the Hill estimator, the sample size has to be much larger and one has to choose a small tuning parameter $r$.
-In case that only events above a high threshold are recorded, $n=10000$ events are extremely unrealistic.
-There is a vast literature on bias-reduced versions of the Hill estimator and on the optimal choice of $r$, mainly based on imposed second-order regular variation conditions [see e.g.
-@beirlantBook, Ch.4.4 and 4.7 and references in it].
-Also, there are hundreds other tail-index estimators not considered in this article, since this would go beyond the scope of our article.
-For example the moment estimator [@dekkers1989moment], the Pickands estimator [@pickands1975statistical], the QQ-estimator [@Kratz96], to name a few.
-A nice overview can be found in [@fedotenkov2018review].
-However, we know from the Theorem in Section \ref{sec:scaling} that the inter-exceedance times are asymptotically Mittag-Leffler distributed, and hence it is unsurprising that general tail (and scale) estimation methods that do not take into account this structure are statistically less efficient [@kozubowski2001] on the *thresholded* data.
-Finally, the Hill estimator completely fails in the important special case where the inter-arrival times are exponentially distributed and not heavy-tailed.
-For these reasons, we propose to use the log-Moment estimator or the MLE for Mittag-Leffler distributions.
-
+With the above comparisons of estimators for the MLD in mind, 
+we propose to use the log-Moment estimator, or the MLE when computational 
+resources are not an issue.
+
+**Weighing the evidence for heavy tails.**
 Since the exponential distribution is nested in the Mittag-Leffler family of 

### 2020-07-30 article_springer/article_springer.Rmd
Create pdf again
Change Title of Subsection "Weighing .. "

@@
 output:
-  html_document: default
   rticles::elsevier_article:
@@
 
-# Continuous Time Random Exceedances (CTRE) {#sec:CTRE}
+# Probabilistic Model
+
+## Continuous Time Random Exceedances (CTRE) {#sec:CTRE}
 
@@
 
-# Scaling limit of Exceedance Times {#sec:scaling}
+## Scaling limit of Exceedance Times {#sec:scaling}
 
@@
 
-# Mittag-Leffler Stability Plots
+# Statistical Inference
+
+## Mittag-Leffler Stability Plots
 
@@
 
-# Fitting Mittag-Leffler Distributions {#sec:ML}
+## Fitting Mittag-Leffler Distributions {#sec:ML}
 
@@
 
-**Weighing the evidence for heavy tails.**
+## Weighing the evidence for heavy tails
+
 Since the exponential distribution is nested in the Mittag-Leffler family of 
@@
 
-# Inference on Exceedance times
+## Inference on Exceedance times
 

### 2020-07-30 article_springer/article_springer.Rmd
Adjust overview part in the introduction to new strucure

@@
 
-We review the marked renewal process in Section 2, and 
-derive a scaling limit theorem for inter-exceedance times in Section 3.
-We give a statistical procedure to estimate model parameters via stability plots 
-in Section 5, but to set the stage we first discuss inference for the 
-Mittag-Leffler distribution in Section 4.
-A simulation study of the effectiveness of our statistical procedure is given in Section 6.
-In Section 7 we apply our method to a real data set.
-In Section 8, we discuss the memory property of the  Mittag-Leffler distribution, and how it affects the predictive distribution for the time until the next threshold crossing event.
-Finally we close with a discussion and conclusion in Section 9.
+We review the marked renewal process in Section 2.1, and 
+derive a scaling limit theorem for inter-exceedance times in Section 2.2.
+We give a statistical procedure to estimate model parameters via stability plots in Section 3.1 and 3.4, but to set the stage we first discuss inference for the Mittag-Leffler distribution in Section 3.2 as well as a Likelihood-ratio test to assess the goodness of fit.
+A simulation study of the effectiveness of our statistical procedure is given in Section 4.
+In Section 5 we apply our method to a real data set.
+In Section 6, we discuss the memory property of the  Mittag-Leffler distribution, and how it affects the predictive distribution for the time until the next threshold crossing event.
+Finally we close with a discussion and conclusion in Section 7.
 For all statistical computations we have used R [@R]. 
-All code and data used for the analysis in this article has been organized into 
-an R package `CTRE` (<https://github.com/strakaps/CTRE>).
+All code and data used for the analysis in this article has been organized into an R package `CTRE` (<https://github.com/strakaps/CTRE>).
 The source code for the figures generated in this manuscript is 
@@
 
-We assume a dataset of the form $\{(T_i, X_i), i \in I\}$,
-where $T_i$ are timestamps and $X_i$ are magnitudes.
+We assume a dataset of the form $\{(t_i, x_i), i \in I\}$,
+where $t_i$ are timestamps and $x_i$ are magnitudes.
 In this article, we focus on modelling the distribution of threshold
@@
 Accordingly, we assume a threshold $\ell$, and discard all
-data $(T_i, X_i)$ where $X_i \le \ell$, yielding the thinned dataset
-$\{(T_i, X_i), i \in I(\ell)\}$, where $I(\ell) \subseteq I$.
+data where $X_i \le \ell$, yielding the thinned dataset
+$\{(t^{(l)}_i, x^{(l)}_i), i \in I(\ell)\}$, where $I(\ell) \subseteq I$.
 
@@
 shocks, resulting in a biased estimate of the parameters of the limiting MLD.
-For illustration, consider the case where measurements are taken daily:
-Then at the lowest threshold, all IETs equal one day,
-leaving no hint at a power-law distribution whatsoever. Raising the threshold
-may or may not produce IETs that start exhibiting a power-law; and both cases
-are represented by the MLD, with $\beta < 1$ or $\beta = 1$.
-
-Suppose the "correct" threshold $\ell_0$ was known, in the sense that 
-thresholding at $\ell_0$ would result precisely in an underlying MRP 
-$\{(W_i, J_i): i \in I\}$ as defined in Section \ref{sec:CTRE}. 
-In this case, we could apply any tail (and scale) estimator such as e.g.
-Hill's estimator [@hill1975simple]
-to the $W_i$ and thus infer the distribution of 
-inter-exceedance times.
-
-But guessing the correct threshold $\ell_0$ and proceeding with this
-type of inference is less favourable to modelling IETs with the MLD, 
-as we now explain.
-In real-world datasets, a "correct" threshold may not exist: the data 
-$\{(T_i, X_i): i \in I\}$ may be a mixture of an MRP with some other
-time series $\{(T'_i, X'_i): i \in I'\}$, and the supports $\mathcal S'$
-and $\mathcal S$ of the distributions
-of $X'_i$ and the magnitudes $J_i$ (aka the MRP marks) may overlap.
-Then thresholding at e.g. $\ell_0 = \sup \mathcal S'$ 
-no longer results in a "clean" MRP: some $J_i$'s will be removed, meaning
-that some $W_i$'s will be merged into a longer IET.
-The more the threshold $\ell_0$ cuts into $\mathcal S$ from below, the more
-the distributions of IETs will resemble a MLD, according to the Theorem.
-As we do not know to what extent this effect occurs, 
-and since the limit is an MLD, it is practicable to fit an MLD to the IETs to 
-begin with.
+<!-- For illustration, consider the case where measurements are taken daily: -->
+<!-- Then at the lowest threshold, all IETs equal one day, -->
+<!-- leaving no hint at a power-law distribution whatsoever. Raising the threshold -->
+<!-- may or may not produce IETs that start exhibiting a power-law; and both cases -->
+<!-- are represented by the MLD, with $\beta < 1$ or $\beta = 1$. -->
+
+<!-- Suppose the "correct" threshold $\ell_0$ was known, in the sense that  -->
+<!-- thresholding at $\ell_0$ would result precisely in an underlying MRP  -->
+<!-- $\{(W_i, J_i): i \in I\}$ as defined in Section \ref{sec:CTRE}.  -->
+In case we would have data of a MRP $\{(W_i, J_i): i \in I\}$ as defined in Section \ref{sec:CTRE}, we could apply any tail (and scale) estimator such as e.g.
+Hill's estimator [@hill1975simple] to the $W_i$ and thus infer the distribution of inter-exceedance times.
+However, in real-world datasets, the MRP assumption is unrealistic for low thresholds.
+The unknown data generating process is likely to be more complex, with dependencies or mixtures of time series at low thresholds, structures that possibly vanish for higher thresholds.
+Fitting just the IETs means that only the exceedances as well as the times inbetween have to satify the iid assumption.
+
+<!-- But guessing the correct threshold $\ell_0$ and proceeding with this -->
+<!-- type of inference is less favourable to modelling IETs with the MLD,  -->
+<!-- as we now explain. -->
+<!-- In real-world datasets, a "correct" threshold may not exist: the data  -->
+<!-- $\{(T_i, X_i): i \in I\}$ may be a mixture of an MRP with some other -->
+<!-- time series $\{(T'_i, X'_i): i \in I'\}$, and the supports $\mathcal S'$ -->
+<!-- and $\mathcal S$ of the distributions -->
+<!-- of $X'_i$ and the magnitudes $J_i$ (aka the MRP marks) may overlap. -->
+<!-- Then thresholding at e.g. $\ell_0 = \sup \mathcal S'$  -->
+<!-- no longer results in a "clean" MRP: some $J_i$'s will be removed, meaning -->
+<!-- that some $W_i$'s will be merged into a longer IET. -->
+<!-- The more the threshold $\ell_0$ cuts into $\mathcal S$ from below, the more -->
+<!-- the distributions of IETs will resemble a MLD, according to the Theorem. -->
+<!-- As we do not know to what extent this effect occurs,  -->
+<!-- and since the limit is an MLD, it is practicable to fit an MLD to the IETs to begin with. -->
 
@@
 since the underlying distribution of IETs *is* a MLD, 
-the fits are more accurate. 
-Figure \ref{fig:Hillplots} shows Hill plots for 200 IETs, for two Mittag-Leffler
-datasets of sizes 200 and 10000 (and an irrelevant distribution of magnitudes).
+the fits are more accurate. Figure \ref{fig:Hillplots} shows Hill plots for 200 IETs, for two Mittag-Leffler datasets of sizes 200 and 10000 (and an irrelevant distribution of magnitudes).
 Clearly the variance is too high to give useful estimates.
-For corresponding fits based on the assumption of a Mittag-Leffler distribution,
-see Figure \ref{Fig:TailSimu}, top row, yielding more reliable predictions 
+For corresponding fits based on the assumption of a Mittag-Leffler distribution, see Figure \ref{Fig:TailSimu}, top row, yielding more reliable predictions
 (more discussion further below).
@@
 
-## Weighing the evidence for heavy tails
+## Goodness-of-Fit Test
 
 Since the exponential distribution is nested in the Mittag-Leffler family of 
-distributions, a Likelihood-ratio Test (LRT) seems to be an appropriate way to choose 
-between a model with exponential and Mittag-Leffler inter-exceedance times.
+distributions, a Likelihood-ratio Test (LRT) seems to be an appropriate way to choose between a model with exponential and Mittag-Leffler inter-exceedance times.
 Although the two models are nested, the asymptotic distribution is not 

### 2020-07-30 article_springer/article_springer.Rmd
small changes

@@
 Accordingly, we assume a threshold $\ell$, and discard all
-data where $X_i \le \ell$, yielding the thinned dataset
+data where $x_i \le \ell$, yielding the thinned dataset
 $\{(t^{(l)}_i, x^{(l)}_i), i \in I(\ell)\}$, where $I(\ell) \subseteq I$.
@@
 However, in real-world datasets, the MRP assumption is unrealistic for low thresholds.
-The unknown data generating process is likely to be more complex, with dependencies or mixtures of time series at low thresholds, structures that possibly vanish for higher thresholds.
+The unknown data generating process is likely to be more complex, with dependencies or mutliple data generating mechanisms at low thresholds, structures that possibly vanish for higher thresholds.
 Fitting just the IETs means that only the exceedances as well as the times inbetween have to satify the iid assumption.

### 2020-07-30 article_springer/article_springer.Rmd
i.i.d. --> iid (war mal so mal so)

@@
 
-: Let $(W,J), (W_1, J_1), (W_2, J_2), \ldots$ be i.i.d. pairs of random variables, where the $W_k > 0$ are interpreted as the *waiting times* 
+: Let $(W,J), (W_1, J_1), (W_2, J_2), \ldots$ be iid pairs of random variables, where the $W_k > 0$ are interpreted as the *waiting times* 
 and $J_k \in \mathbb{R}$ as the *event magnitudes*. If $W$ and $J$ are independent, the Marked Renewal Process is said to be *uncoupled*.
@@
 By restarting the MRP at $\tau(\ell)$, inductively define the
-two i.i.d. sequences $T(\ell,n)$ and $X(\ell, n)$, $n \in \mathbb N$, 
+two iid sequences $T(\ell,n)$ and $X(\ell, n)$, $n \in \mathbb N$, 
 called the "inter-arrival times" and the "exceedances", respectively.
@@
 
-## Inference on Exceedance times
+## Algorithm for the inference on exceedance times
 
@@
 (i.e. the $K$ largest values, where e.g. $K = 300$) 
-$X_{(1)}, \ldots, X_{(K)}$ together with their timestamps $T_{(1)}, \ldots, T_{(K-1)}$.
+$x_{(1)}, \ldots, x_{(K)}$ together with their timestamps $t_{(1)}, \ldots, t_{(K-1)}$.
 
@@
 
-i.i.d.:
+iid :
 
 : After removing the "noise observations" below the smallest threshold 
-  $\ell_0$, the pair sequence $(T(\ell_0, i), X(\ell_0,i))$ is i.i.d. 
+  $\ell_0$, the pair sequence $(T(\ell_0, i), X(\ell_0,i))$ is iid 
   An indication if this is true is given by an auto-correlation plot.
@@
 
-When we introduced the CTRE model, we assumed that all events are i.i.d.
-This assumption is likely sufficient but not necessary for our limit theorem to hold.
-Moreover, any data below a (minimum) threshold $\ell_0$ is discarded for CTREs, and hence need not satisfy the i.i.d.
-assumption.
-For the purposes of statistical inference, we merely require that the inter-threshold-crossing times are i.i.d.
+When we introduced the CTRE model, we assumed that all events are iid This assumption is likely sufficient but not necessary for our limit theorem to hold.
+Moreover, any data below a (minimum) threshold $\ell_0$ is discarded for CTREs, and hence need not satisfy the iid assumption.
+For the purposes of statistical inference, we merely require that the inter-threshold-crossing times are iid
 

### 2020-08-01 article_springer/article_springer.Rmd
Small changes according Discussion on 31/7/2020

@@
     fig_caption: yes
+  htlml_document: default
 
@@
 Accordingly, we assume a threshold $\ell$, and discard all
-data where $x_i \le \ell$, yielding the thinned dataset
-$\{(t^{(l)}_i, x^{(l)}_i), i \in I(\ell)\}$, where $I(\ell) \subseteq I$.
+data where $x_i \le \ell$, yielding the thresholded dataset
+$\{(t^{(\ell)}_i, x^{(\ell)}_i), i \in I(\ell)\}$, with $x^{(\ell)}_i=x_i-\ell$, where $I(\ell):=\left\{i: x_i \le \ell \right\} \subseteq I$.
 
@@
 Hill's estimator [@hill1975simple] to the $W_i$ and thus infer the distribution of inter-exceedance times.
-However, in real-world datasets, the MRP assumption is unrealistic for low thresholds.
+However, in real-world datasets, the MRP assumption is too strong for low thresholds.
 The unknown data generating process is likely to be more complex, with dependencies or mutliple data generating mechanisms at low thresholds, structures that possibly vanish for higher thresholds.
-Fitting just the IETs means that only the exceedances as well as the times inbetween have to satify the iid assumption.
+Fitting only the IETs means that the iid assumption applies to exceedances and IETs only.
 
@@
 
-## Goodness-of-Fit Test
+## Weighing the evidence for non-exponential inter-arrival times
 

### 2020-08-01 article_springer/article_springer.Rmd
Change Remark after Proof according file with Comments to Referees

@@
 In @Anderson1987  a similar result is shown with a different choice of scaling constant.
-[@MeerschaertStoev08] proofed a limit theorem for the maxima of iid random variables separated by infinite mean waiting times.
-They showed that the duration time of the limit process is Mittag-Leffler distributed.
-[@Basrak2014] described the asymptotic distribution under similar assumptions of all upper orders statistics using point processes.
+[@MeerschaertStoev08] proved a limit theorem for the maxima of iid random variables separated by infinite mean waiting times.
+They have also shown that the hitting time of the limit process is Mittag-Leffler distributed.
+[@Basrak2014] described the asymptotic distribution, under similar assumptions, of all upper orders statistics using point processes.
 

### 2020-08-01 article_springer/article_springer.Rmd
Adressing Peters Yellow Highlights

@@
 derive a scaling limit theorem for inter-exceedance times in Section 2.2.
-We give a statistical procedure to estimate model parameters via stability plots in Section 3.1 and 3.4, but to set the stage we first discuss inference for the Mittag-Leffler distribution in Section 3.2 as well as a Likelihood-ratio test to assess the goodness of fit.
+We give a statistical procedure to estimate model parameters via stability plots in Section 3.1 and 3.4, but first we need to discuss inference for the Mittag-Leffler distribution in Section 3.2 as well as a Likelihood-ratio test to guide the choice, whether a Mittag-Leffler or an exponential distribution fits better to the inter-exceedance times.
 A simulation study of the effectiveness of our statistical procedure is given in Section 4.
@@
 two iid sequences $T(\ell,n)$ and $X(\ell, n)$, $n \in \mathbb N$, 
-called the "inter-arrival times" and the "exceedances", respectively.
+called the "inter-exceedance times" (IETs) and the "exceedances", respectively.
 The pair sequence $(X(\ell, n), T(\ell, n))_{n \in \mathbb N}$ is called 
@@
 \begin{align} \label{eq:stability}
-\frac{W_1 + \ldots + W_n}{b(n)} \overset{d}{\longrightarrow} D, 
+\frac{W_1 + \ldots + W_n}{b(n)} \Rightarrow D, 
 \quad n \to \infty
@@
 $$
-\frac{T(\ell)} {b(1/p_{\ell})} \to Z_\beta \quad \text{ as } \quad \ell \uparrow x_R
+\frac{T(\ell)} {b(1/p_{\ell})} \Rightarrow  Z_\beta \quad \text{ as } \quad \ell \uparrow x_R
 $$
@@
 	\begin{align*}
-	P\left(\frac{M(c)-d(c)}{a(c)} \leq x\right) \rightarrow F(x) := F(x,\xi) \text{ as } c \rightarrow \infty,
+	P\left(\frac{J_1 \vee \ldots \vee J_{\lfloor c \rfloor}-d(c)}{a(c)} \leq x\right) \rightarrow F(x) := F(x,\xi) \text{ as } c \rightarrow \infty,
 	\end{align*}
@@
     \end{align}
-	 with $p(\ell_c):= 1-F(\ell_c)$. Since $\tau(\ell_c) \sim Geo(p(\ell_c))$ and \eqref{eq:lplconv}
+	 with $p(\ell_c):= 1-F(\ell_c)$ and $F_A$ is the CDF of the limit distribution, the GEV, in \eqref{assumptionJs}. Since $\tau(\ell_c) \sim Geo(p(\ell_c))$ and \eqref{eq:lplconv}
 	it follows that $\tau(\ell_c)/c$ converges to an Exponential distributed random variable,
@@
     where $\Phi_D(s) = \exp(-s^\beta)$ is the Laplace transform of $D$ 
-    and  $F_E(dy)$ is the distribution function of $E$. Hence, $Z$ is Mittag-Leffler distributed with parameter $\lambda^{-1/\beta}$. Rewriting
+    and  $F_E(dy)$ is the distribution function of $E$. Hence, $Z$ is Mittag-Leffler distributed with scale parameter $\lambda^{-1/\beta}$. Rewriting
 	\begin{align*}
@@
 
-: If $\beta = 1$, the result of the Theorem above is standard, see e.g. 
+: If $\beta = 1$, the result of the Theorem above is standard, see  
 Equation (2.2) in @Gut1999.

### 2020-08-01 article_springer/article_springer.Rmd
citing CTRE package explicitly

@@
 Finally we close with a discussion and conclusion in Section 7.
-For all statistical computations we have used R [@R]. 
-All code and data used for the analysis in this article has been organized into an R package `CTRE` (<https://github.com/strakaps/CTRE>).
-The source code for the figures generated in this manuscript is 
-available online at <https://github.com/strakaps/bursty-POT>.
+For all statistical computations we have used `R` [@R] and the package `CTRE`
+[@CTRE]. Source code for simulations and figures generated in this 
+manuscript is available online at <https://github.com/strakaps/bursty-POT>.
 

### 2020-08-01 article_springer/article_springer.Rmd
bügele das Englisch

@@
   Graphical means of estimating model parameters and assessing 
-  model fit are provided. Along the way, the inference method gets applied to a real-world
-  bursty time series, and it is shown how the memory of the Mittag-Leffler distribution affects 
-  the predictive distribution for the time until the next extreme event.
+  model fit are provided. 
+  The inference method is
+  applied to an empirical bursty time series, and it is shown how the memory of the
+  Mittag-Leffler distribution affects prediction of the time until
+  the next extreme event."
 
@@
 shocks, resulting in a biased estimate of the parameters of the limiting MLD.
-<!-- For illustration, consider the case where measurements are taken daily: -->
-<!-- Then at the lowest threshold, all IETs equal one day, -->
-<!-- leaving no hint at a power-law distribution whatsoever. Raising the threshold -->
-<!-- may or may not produce IETs that start exhibiting a power-law; and both cases -->
-<!-- are represented by the MLD, with $\beta < 1$ or $\beta = 1$. -->
-
-<!-- Suppose the "correct" threshold $\ell_0$ was known, in the sense that  -->
-<!-- thresholding at $\ell_0$ would result precisely in an underlying MRP  -->
-<!-- $\{(W_i, J_i): i \in I\}$ as defined in Section \ref{sec:CTRE}.  -->
-In case we would have data of a MRP $\{(W_i, J_i): i \in I\}$ as defined in Section \ref{sec:CTRE}, we could apply any tail (and scale) estimator such as e.g.
-Hill's estimator [@hill1975simple] to the $W_i$ and thus infer the distribution of inter-exceedance times.
-However, in real-world datasets, the MRP assumption is too strong for low thresholds.
-The unknown data generating process is likely to be more complex, with dependencies or mutliple data generating mechanisms at low thresholds, structures that possibly vanish for higher thresholds.
-Fitting only the IETs means that the iid assumption applies to exceedances and IETs only.
-
-<!-- But guessing the correct threshold $\ell_0$ and proceeding with this -->
-<!-- type of inference is less favourable to modelling IETs with the MLD,  -->
-<!-- as we now explain. -->
-<!-- In real-world datasets, a "correct" threshold may not exist: the data  -->
-<!-- $\{(T_i, X_i): i \in I\}$ may be a mixture of an MRP with some other -->
-<!-- time series $\{(T'_i, X'_i): i \in I'\}$, and the supports $\mathcal S'$ -->
-<!-- and $\mathcal S$ of the distributions -->
-<!-- of $X'_i$ and the magnitudes $J_i$ (aka the MRP marks) may overlap. -->
-<!-- Then thresholding at e.g. $\ell_0 = \sup \mathcal S'$  -->
-<!-- no longer results in a "clean" MRP: some $J_i$'s will be removed, meaning -->
-<!-- that some $W_i$'s will be merged into a longer IET. -->
-<!-- The more the threshold $\ell_0$ cuts into $\mathcal S$ from below, the more -->
-<!-- the distributions of IETs will resemble a MLD, according to the Theorem. -->
-<!-- As we do not know to what extent this effect occurs,  -->
-<!-- and since the limit is an MLD, it is practicable to fit an MLD to the IETs to begin with. -->
+If we had MRP data $\{(W_i, J_i): i \in I\}$ as defined in Section 
+\ref{sec:CTRE}, we could apply any tail (and scale) estimator such as e.g. Hill's 
+estimator [@hill1975simple] to the $W_i$ and thus infer the distribution of 
+inter-exceedance times. However, in real-world datasets, the MRP assumption is too 
+strong for low thresholds. The unknown data generating process is likely more 
+complex, with dependencies or multiple data generating mechanisms at low thresholds 
+and structures that may vanish for higher thresholds. Fitting only the IETs means 
+that the iid assumption applies to exceedances and IETs only.
 

### 2020-08-01 article_springer/article_springer.Rmd
fix proof

@@
     fig_caption: yes
-  htlml_document: default
+  html_document: default
 
@@
 
-*Proof of Theorem:* 	Due to assumption \eqref{assumptionJs}, it follows that
-	\begin{align*}
-	P\left(\frac{J_1 \vee \ldots \vee J_{\lfloor c \rfloor}-d(c)}{a(c)} \leq x\right) \rightarrow F(x) := F(x,\xi) \text{ as } c \rightarrow \infty,
-	\end{align*}
-	where $x$ is any value from the support of $F$. Then
-	\begin{align*}
-	  F(xa(c)+d(c))^{\lfloor c \rfloor} &\rightarrow F(x) \text{ as } c \rightarrow \infty,\\
-      \Rightarrow  \lfloor c \rfloor \log F(\ell_c)  &\rightarrow \log F(x)\text{ as } c \rightarrow \infty,
-	\end{align*}
+*Proof of Theorem:* 	Due to assumption \eqref{assumptionJs}, for any $x$ from 
+the support of $F(x;\xi)$
+$$
+	P\left(\frac{J_1 \vee \ldots \vee J_{\lfloor c \rfloor}-d(c)}{a(c)} \leq x\right) \rightarrow F(x;\xi)
+\\
+\Longleftrightarrow F_J(xa(c)+d(c))^{\lfloor c \rfloor} \rightarrow F(x;\xi)
+\\
+\Longleftrightarrow  \lfloor c \rfloor \log F_J(\ell_c)  \rightarrow \log F(x;\xi)
+$$
 	with $\ell_c:=xa(c)+d(c)$. Furthermore, since $\log(1-x) \sim -x$ for small $x$ it follows
-    \begin{align}
-      c \cdot p(\ell_c) \rightarrow -\log F_A(x)  \text{ as } c \rightarrow \infty,\label{eq:lplconv}
-    \end{align}
-	 with $p(\ell_c):= 1-F(\ell_c)$ and $F_A$ is the CDF of the limit distribution, the GEV, in \eqref{assumptionJs}. Since $\tau(\ell_c) \sim Geo(p(\ell_c))$ and \eqref{eq:lplconv}
-	it follows that $\tau(\ell_c)/c$ converges to an Exponential distributed random variable,
-	\begin{align*}
-	\frac{\tau(\ell_c)}{c} \Rightarrow E  \text{ as } c \rightarrow \infty
-	\end{align*}
-	 with inverse mean $\lambda:=-\log F_A(x)$. Due to
-	\begin{align*}
-	S(c):= \sum_{i=1}^{\lfloor c \rfloor} \frac{W_i}{b(c)} \Rightarrow D \ \text{ as } c \rightarrow \infty,
-	\end{align*}
+$$
+c \cdot p(\ell_c) \rightarrow -\log F(x;\xi) \quad  \text{ as } c \rightarrow \infty,
+$$
+with $p(\ell_c):= 1-F(\ell_c)$. Due to $\tau(\ell_c) \sim {\rm Geo}(p(\ell_c))$ and above equation,
+	it follows that $\tau(\ell_c)/c$ converges to an Exponential random variable,
+$$
+	\frac{\tau(\ell_c)}{c} \Rightarrow E \quad  \text{ as } c \rightarrow \infty
+$$
+	 with inverse mean $\lambda:=-\log F(x;\xi)$. Due to
+$$
+	S(c):= \sum_{i=1}^{\lfloor c \rfloor} \frac{W_i}{b(c)} \Rightarrow D \quad \text{ as } c \rightarrow \infty,
+$$
     it follows with Gnedenko's transfer theorem (see @gnedenko1983limit), that
-	\begin{align}
-	\sum_{i=1}^{ \tau(\ell_c)} \frac{W_i}{b(\ell_c)}  \Rightarrow Z\ \text{ as }  c \rightarrow \infty, \label{TheoGutArg}
-	\end{align}
+$$
+	\sum_{i=1}^{ \tau(\ell_c)} \frac{W_i}{b(\ell_c)}  \Rightarrow Z \quad \text{ as }  c \rightarrow \infty, 
+$$
 	where the distribution of $Z$ has the characteristic function
-	\begin{align}
-    \Psi(s) &= \int_0^{\infty} (\Phi_D(s))^{y} F_E(dy) \nonumber\\
-    &= \int_0^{\infty} \frac{1}{1-\log(\Phi_D(s))/\lambda} \nonumber\\
-    &= \frac{1}{1+s^{\beta}\lambda^{-1}}
-	\end{align}
+$$
+\Psi(s) = \int_0^{\infty} (\Phi_D(s))^{y} F_E(dy)
+= \frac{1}{1-\log(\Phi_D(s))/\lambda}
+= \frac{1}{1+s^{\beta}\lambda^{-1}}
+= \frac{1}{1+(s \lambda^{-1/\beta})^{\beta}}
+$$
     where $\Phi_D(s) = \exp(-s^\beta)$ is the Laplace transform of $D$ 
     and  $F_E(dy)$ is the distribution function of $E$. Hence, $Z$ is Mittag-Leffler distributed with scale parameter $\lambda^{-1/\beta}$. Rewriting
-	\begin{align*}
+$$
     \sum_{i=1}^{ \tau(\ell_c)} \frac{W_i}{b(1/p(\ell_c))} = \left(\sum_{i=1}^{ \tau(\ell_c)} \frac{W_i}{b(c) }\right) \frac{b(c)}{b(1/p(\ell_c))}  
-	\end{align*}
+$$
 	and
-	\begin{align*}
+$$
 	\frac{b(c)}{b(1/p(\ell_c))} = \frac{b(c)}{b(c/(p(\ell_c)c))} \sim (p(\ell_c) \cdot c)^{1/\beta} \rightarrow \lambda^{1/\beta} \text{ as } c \rightarrow \infty,
-	\end{align*}
+$$
 	the second factor converges to $\lambda^{1/\beta}$, and it follows that
-	 $Z \sim ML(\beta,1)$. Since $c \rightarrow \infty$ is equivalent to $\ell \uparrow x_R$, the assertion follows with $\ell:=\ell_c$ and $p_\ell:=p(\ell_c)$.
+	 $Z \sim {\rm ML}(\beta,1)$. Since $c \rightarrow \infty$ is equivalent to $\ell \uparrow x_R$, the assertion follows with $\ell:=\ell_c$ and $p_\ell:=p(\ell_c)$.
 \qed

### 2020-08-01 article_springer/article_springer.Rmd
fix typos

@@
 With the previous section setting the stage, we assume that only the large
-magnitudes (aka "shocks") follow a MRP.  The smaller magnitudes are possibly
+magnitudes (or "shocks") follow a MRP.  The smaller magnitudes are possibly
 nuisance data that may be irrelevant with respect to the modelling of extremes
@@
 data where $x_i \le \ell$, yielding the thresholded dataset
-$\{(t^{(\ell)}_i, x^{(\ell)}_i), i \in I(\ell)\}$, with $x^{(\ell)}_i=x_i-\ell$, where $I(\ell):=\left\{i: x_i \le \ell \right\} \subseteq I$.
+$\{(t^{(\ell)}_i, x^{(\ell)}_i): i \in I(\ell)\}$, with $x^{(\ell)}_i=x_i-\ell$, where $I(\ell):=\left\{i \in I: x_i \ge \ell \right\} \subseteq I$.
 
@@
 : We approximated $p_{\ell}$, the probability that an event is larger than $l$, by its relative frequency.
-One could also approximate this tail probability by the GPD distribution fitted to the exceedances.
+One could also approximate this tail probability via the GPD distribution fitted to the exceedances.
 
@@
 threshold $\ell$ is placed.
-<!-- Note that the Hill estimator is based on the waiting times, not on the  -->
-<!-- inter-exceedance times, meaning that the estimation is based on more data.  -->
-<!-- If one were to base the Hill-estimation only on the inter-exceedance times,  -->
-<!-- the sample size would be too small and it would be impossible to deduce an  -->
-<!-- estimate for the tail parameter from the plots (compare Figure \ref{fig:Hillplots}).  -->
-
-<!-- In the right-hand Hill-estimator column, the $k$ on the $x$-axis corresponds to -->
-<!-- $r$ from \eqref{eq:Hill}. -->
-<!-- The Hill estimator appears to be nicely unbiased on Pareto data, -->
-<!-- but compared to the other two estimators, it has a higher variance,  -->
-<!-- as can be seen from the wider spread of the simulated curves.  -->
-<!-- This high variance means that that a single estimate is less reliable compared -->
-<!-- to the other two estimators.  -->
-<!-- This effect is amplified if one only has a thresholded, and thus smaller dataset -->
-<!-- available, to the extent that the Hill estimates become severely flawed -->
-<!-- (see Section \ref{sec:ML}).  -->
 
@@
 We only need the exceedances as well as the inter-exceedance times to be iid.
-
-<!-- Since there is no Hill-estimate of a scale parameter, there are only two columns.  -->
 
@@
 
-iid :
+iid:
 
@@
 
-The fit with a Mittag-Leffler distribution ($\beta = 0.9$) seems to be good (see Figure \ref{fig:flare-diagnostics-3}), though there are signs that the power-law tail tapers off for very large inter-threshold crossing times.
+The fit with a Mittag-Leffler distribution ($\beta = 0.9$) seems to be good (see Figure \ref{fig:flare-diagnostics-3}), although there are signs that the power-law tail tapers off for very large inter-threshold crossing times.
 There is no apparent dependence between threshold exceedance times and event magnitudes seen in the copula plot (see Figure \ref{fig:flare-diagnostics-2}).
@@
 ```
+
 The closer $\beta$ is to $1$, the more the hazard rate mimics that of an 
@@
 
-When we introduced the CTRE model, we assumed that all events are iid This assumption is likely sufficient but not necessary for our limit theorem to hold.
+When we introduced the CTRE model, we assumed that all events are iid.
+This assumption is likely sufficient but not necessary for our limit theorem to hold.
 Moreover, any data below a (minimum) threshold $\ell_0$ is discarded for CTREs, and hence need not satisfy the iid assumption.
-For the purposes of statistical inference, we merely require that the inter-threshold-crossing times are iid
+For the purposes of statistical inference, we merely require that the IETs are iid.
 
@@
 In the setting of this article, however, clustering-like dynamics occur due to the *non-stationarity* of the underlying renewal-reward process, which has infinite-mean renewal times. 
-Hence CTRE and Cluster Poisson Process shouldn't be viewed as competing methods, as the underlying data generating processes are quite different.
+Hence CTRE and Cluster Poisson Process should not be viewed as competing methods, as the underlying data generating processes are quite different.
 To differentiate between the two models we use the term *bursty* which is standard in the context of heavy-tailed inter-arrival times in the physics community [e.g.

### 2020-08-01 article_springer/article_springer.Rmd

@@
 To clarify Step 4: Recall that by the theorem, $\sigma_k / b(1/p_{\ell})$ is expected to stabilize 
-around a constant as $k$ gets smaller. Since $b$ is regularly varying with parameter
+around a constant as $k$ decreases. Since $b$ is regularly varying with parameter
 $1/\beta$, we have $b(1/p_{\ell}) = p_{\ell}^{-1/\beta} / L(1/p_{\ell})$ for some slowly varying function $L$. 
@@
 Moreover, the bottom row in Figure \ref{Fig:TailSimu} shows clearly that the log-Moment and Maximum-Likelihood estimators generalize to the exponential case ($\beta = 1$) whereas the Hill-estimator would not.
-Notice that any data below a certain threshold gets discarded in our approach and hence need not to satisfy the iid assumption.
-In our simulation study we only simulated data from iid sequences of $(W_k)_{k \in \mathbb{N}}$, in real data situations its likely that there are dependencies or more complex data generating processes vanishing for higher thresholds.
-We only need the exceedances as well as the inter-exceedance times to be iid.
+Notice that any data below a certain threshold is discarded in our approach and hence need not satisfy the iid assumption.
+In our simulation study we only simulated data from iid sequences of $(W_k)_{k \in \mathbb{N}}$; in real data situations it is likely that there are dependencies or more complex data generating processes which vanish for higher thresholds.
+We only need the exceedances and IETs to be iid.
 

### 2020-08-01 article_springer/article_springer.Rmd
Cosmetic repairs regarding the proof ($$ --> align)

@@
 
-*Proof of Theorem:* 	Due to assumption \eqref{assumptionJs}, for any $x$ from 
-the support of $F(x;\xi)$
-$$
-	P\left(\frac{J_1 \vee \ldots \vee J_{\lfloor c \rfloor}-d(c)}{a(c)} \leq x\right) \rightarrow F(x;\xi)
-\\
-\Longleftrightarrow F_J(xa(c)+d(c))^{\lfloor c \rfloor} \rightarrow F(x;\xi)
-\\
-\Longleftrightarrow  \lfloor c \rfloor \log F_J(\ell_c)  \rightarrow \log F(x;\xi)
-$$
-	with $\ell_c:=xa(c)+d(c)$. Furthermore, since $\log(1-x) \sim -x$ for small $x$ it follows
+*Proof of Theorem:* 	Due to assumption \eqref{assumptionJs}
+\begin{align*}
+& & P\left(\frac{J_1 \vee \ldots \vee J_{\lfloor c \rfloor}-d(c)}{a(c)} \leq x\right) & \rightarrow F(x;\xi) \\
+& \Longleftrightarrow & F_J(xa(c)+d(c))^{\lfloor c \rfloor} & \rightarrow F(x;\xi) \\
+& \Longleftrightarrow &  \lfloor c \rfloor \log F_J(\ell_c) & \rightarrow \log F(x;\xi)
+\end{align*}
+as $c \rightarrow \infty$, for any $x$ from 
+the support of $F(x;\xi)$,	with $\ell_c:=xa(c)+d(c)$. Furthermore, since $\log(1-x) \sim -x$ for small $x$ it follows
 $$
@@
 	where the distribution of $Z$ has the characteristic function
-$$
-\Psi(s) = \int_0^{\infty} (\Phi_D(s))^{y} F_E(dy)
-= \frac{1}{1-\log(\Phi_D(s))/\lambda}
-= \frac{1}{1+s^{\beta}\lambda^{-1}}
-= \frac{1}{1+(s \lambda^{-1/\beta})^{\beta}}
-$$
+\begin{align*}
+\Psi(s) &= \int_0^{\infty} (\Phi_D(s))^{y} F_E(dy) = \frac{1}{1-\log(\Phi_D(s))/\lambda}\\
+&= \frac{1}{1+s^{\beta}\lambda^{-1}} = \frac{1}{1+(s \lambda^{-1/\beta})^{\beta}}
+\end{align*}
     where $\Phi_D(s) = \exp(-s^\beta)$ is the Laplace transform of $D$ 

### 2020-08-01 article_springer/article_springer.Rmd
Exponential  --> exponential (uniformly)
Add missing Acknowledgments.

@@
 with $p(\ell_c):= 1-F(\ell_c)$. Due to $\tau(\ell_c) \sim {\rm Geo}(p(\ell_c))$ and above equation,
-	it follows that $\tau(\ell_c)/c$ converges to an Exponential random variable,
+	it follows that $\tau(\ell_c)/c$ converges to an exponential random variable,
 $$
@@
 
-The authors would like to thank Prof.
-Peter Scheffler for insights on stochastic process limits for CTRMs, Prof.
-Roland Fried for discussion regarding the statistical methods and Gurtek Gill who helped create the MittagLeffleR R-package.
+The authors would like to thank Prof. Peter Scheffler for insights on 
+stochastic process limits for CTRMs, Prof. Roland Fried for discussion 
+regarding the statistical methods and Gurtek Gill who helped create the 
+MittagLeffleR R-package. Peter Straka was supported by the Discovery 
+Early Career Research Award DE160101147 on the Project 
+“Predicting Extremes when Events Occurin Bursts” by 
+the Australian Research Council. Katharina Hees was 
+supported by the DAAD co-financed by the 
+German Federal Ministry of Education andResearch (BMBF)
 

### 2020-08-01 article_springer/article_springer.Rmd
Clean Up Bibtex File, delte DOIs
2 small Typos

@@
 
-## Algorithm for the inference on exceedance times
+## Algorithm for the inference on inter-exceedance times
 
@@
 : After removing the "noise observations" below the smallest threshold 
-  $\ell_0$, the pair sequence $(T(\ell_0, i), X(\ell_0,i))$ is iid 
+  $\ell_0$, the pair sequence $(T(\ell_0, i), X(\ell_0,i))$ is iid. 
   An indication if this is true is given by an auto-correlation plot.
@@
 supported by the DAAD co-financed by the 
-German Federal Ministry of Education andResearch (BMBF)
+German Federal Ministry of Education and Research (BMBF).
 

### 2020-08-02 article_springer/article_springer.Rmd
remove markdown line-break (two spaces at end of line)
remove brackets in citation

@@
 In @Anderson1987  a similar result is shown with a different choice of scaling constant.
-[@MeerschaertStoev08] proved a limit theorem for the maxima of iid random variables separated by infinite mean waiting times.
-They have also shown that the hitting time of the limit process is Mittag-Leffler distributed.
-[@Basrak2014] described the asymptotic distribution, under similar assumptions, of all upper orders statistics using point processes.
+@MeerschaertStoev08 proved a limit theorem for the maxima of iid random variables separated by infinite mean waiting times.
+They also show that the hitting time of the limit process is Mittag-Leffler distributed.
+@Basrak2014 describe the asymptotic distribution, under similar assumptions, of all upper orders statistics of the maximum process using point processes.
 

### 2020-08-02 article_springer/article_springer.Rmd
remove duplicate 'thanks', put grant support first

@@
 # titlerunning: "CTRE: POT for Bursty Time Series"
-thanks: |
-    Peter Straka was supported by the 
-    Discovery Early Career Research Award DE160101147 on the Project 
-    "Predicting Extremes when Events Occur in Bursts" by the Australian
-    Research Council.
-    Katharina Hees was supported by 
-    the DAAD co-financed by the German Federal Ministry of Education and 
-    Research (BMBF).
 
@@
 
-The authors would like to thank Prof. Peter Scheffler for insights on 
-stochastic process limits for CTRMs, Prof. Roland Fried for discussion 
-regarding the statistical methods and Gurtek Gill who helped create the 
-MittagLeffleR R-package. Peter Straka was supported by the Discovery 
+Peter Straka was supported by the Discovery 
 Early Career Research Award DE160101147 on the Project 
@@
 German Federal Ministry of Education and Research (BMBF).
+The authors would like to thank Prof. Peter Scheffler for insights on 
+stochastic process limits for CTRMs, Prof. Roland Fried for discussion 
+regarding the statistical methods and Gurtek Gill who helped create the 
+MittagLeffleR R-package.
 
